### 2021-04-27 sample-authordraft.tex
Initial Overleaf Import

%%
%% This is file `sample-authordraft.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `authordraft')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-authordraft.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[acmconf,authordraft,anonymous,review]{acmart}
\usepackage{todonotes}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{listings}

\newcommand{\tristan}[1]{\color{orange}\textbf{From Tristan:}#1\color{black}}
\newcommand{\Yohan}[1]{\todo[inline,backgroundcolor=green]{YC:#1}}

%% NOTE that a single column version may be required for 
%% submission and peer review. This can be done by changing
%% the \doucmentclass[...]{acmart} in this template to 
%% \documentclass[manuscript,screen,review]{acmart}
%% 
%% To ensure 100% compatibility, please check the white list of
%% approved LaTeX packages to be used with the Master Article Template at
%% https://www.acm.org/publications/taps/whitelist-of-latex-packages 
%% before creating your document. The white list page provides 
%% information on how to submit additional LaTeX packages for 
%% review and adoption.
%% Fonts used in the template cannot be substituted; margin 
%% adjustments are not allowed.
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Supercomputing '21]{Supercomputing '21: The International Conference for High Performance
Computing, Networking, Storage, and Analysis}{November 16--18, 2021}{St. Louis, MO}
\acmPrice{}
\acmISBN{}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{PyTracer: Detecting numerical instabilities in Python using Monte Carlo Arithmetic \tristan{title sounds like PyTracer is an MCA tool, emphasis should be put on comparing MCA traces. ``without instrumentation" or ``automatic" could also appear in the title.}}
\title{PyTracer: Automatically profiling numerical instabilities in Python}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ben Trovato}
\authornote{Both authors contributed equally to this research.}
\email{trovato@corporation.com}
\orcid{1234-5678-9012}
\author{G.K.M. Tobin}
\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin}
  \state{Ohio}
  \country{USA}
  \postcode{43017-6221}
}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato and Tobin, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX\ document is presented as an
  article formatted for publication by ACM in a conference proceedings
  or journal publication. Based on the ``acmart'' document class, this
  article presents and explains many of the common variations, as well
  as many of the formatting elements an author may use in the
  preparation of the documentation of their work.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{datasets, neural networks, gaze detection, text tagging}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}

Although it has been an intense subject of research since the early days of computer science, the analysis of numerical instabilities recurrently comes to the forefront in every field that is confronted with it.
Indeed numerical instabilities are inherent to numerical computations and have been studied from a mathematical
point of view through the numerical analysis. However, the increasing complexity 
of nowadays computation codes makes pen and paper proofs not always sufficient to understand the overall 
numerical quality of computed results. In addition to the traditional floating-point model, backward error and 
condition number analyses, they are the library updates, parallelization schemes and hardware innovations.

This complexity requires new tools to estimate the numerical quality of computations that
must be adapted to new languages like Python. Indeed, Python, especially 
scientific python (Scipy) is critical to scientific computing but 
is under studied due to lack of tools.

\begin{itemize}
    \item Numerical instabilities are inherent to numerical computations \tristan{not only to HPC, also software updates, small perturbations in parameters or data}
    \item 
    \item Neuroimaging tools are facing reproducibility issues, one factor of which is numerical stability \tristan{neuroimaging should be an illustration, your intro should rather focus on Python in general, it's much more impactful} 
    \item Detecting those instabilities is challenging: large data sets, large pipeline, long computation time, complex physics \tristan{Here you could illustrate the point with neuroimaging pipelines}
    \item Needs tools for automatically detecting these instabilities
    \item Needs tools to quickly identify unstable functions among large number of calls
\end{itemize}

\tristan{explain that it can be used with any type of perturbation, including random seed, input noise, etc}

\subsection{Contributions}
\begin{itemize}
    \item Pytracer, a tool to automatically instrument Python functions 
    to trace their inputs and outputs fidelity over time
    \item A visualizer that allows visualizing large traces 
    \item A graph-based summary view to easily identify numerically unstable functions 
    \item \tristan{An evaluation of the above tools on Scipy libraries}
\end{itemize}

\section{Motivating example}

\Yohan{Find motivating example}
%\tristan{Could be Greg's pipeline and paper}

\tristan{weave in intro. Logic could be: scientific python (SciPy) is critical to scientific computing, numerical stability is critical but it's under studied in python due to lack of tools. Mention a list of references on numerical stability issues, from various application domains (beam, greg's, numpy/scipy, sklearn, etc). Numerical perturbations can be triggered from various computational factors (OS, parallelization, hardware, etc).}

\section{Background}

Several methods exist to assess the numerical quality of a code.
Among them, the stochastic arithmetic proposes to modelize round-off errors 
of the floating-point arithmetic by a random variable. This method exists 
in two major flavors: the Discrete Stochastic Arithmetic~\cite{vignes2004discrete} (DSA)
and the Monte Carlo Arithmetic~\cite{parker1997monte} (MCA).

\subsection{Tools for assessing the numerical quality}

It exist several tools in the literature for detecting or assessing numerical quality.
Most of these tools are dedicated to C,C++ or FORTRAN codes even if Dynamic Binary Instrumentation (DBI)
technique allows examining any binary executable and are thus languages agnostic.
CADNA~\cite{jezequel2008cadna} is a library for C,C++ and Fortran codes implementing
the CESTAC~\cite{vignes1993stochastic} method. 
CraftHPC~\cite{lam2013dynamic} uses DBI to detect catastrophic cancellations at runtime.
Verrou~\cite{fevotte2016verrou} is a Valgrind~\cite{nethercote2007valgrind} based tool 
thus language agnostic that uses stochastic arithmetic.
Veritracer~\cite{chatelain2018veritracer} is an extension of Verificarlo
that aims at visualizing the numerical stability over time for C,C++ and Fortran codes.
Verificarlo~\cite{denis2015verificarlo} is compiler based upon clang that 
allows replacing floating point operations by generic calls to 
different alternative floating-point arithmetic, including MCA.
Shaman \cite{demeure_phd} is C++ library that uses a first order error model for 
propagating numerical error. 
Herbgring~\cite{sanchez2017finding} is a Valgrind based tool for detecting 
numerical instabilities in code. It uses a shadow memory to do computations  
in high precision by using MPFR~\cite{fousse2007mpfr} and compare this results with the actual one
for detecting precision losses. It is combines with a symbolic computation for backtracking the root of the error.
Anteater~\cite{faust2019anteater} is Python tracer tool that aims at debugging python application. 
It operates source transformation at AST level and deals with native numeric python types only.
While DBI solutions can be used for python code because they are language agnostic, 
they are not intended to analyze Python code. Moreover, few tools embed a visualizer for 
analyzing numerical quality over time letting the postprocessing to the user.

Existing tools for tracing Python code are dedicated to performance profiling, for time (cProfile) 
or memory consumption (memprofile). 
To the best of our knowledge, there is currently no tool dedicated to numerical analysis.
We can however compare the methodology used by these tools against the one used in Pytracer.
These tools use an instrumentation based on decorator, a Python mechanism allowing 
to wrap a function by adding a line over a function declaration.
If this method is useful for targeting specific functions, it becomes time consuming 
when applying to all functions of a code. Moreover, this technique becomes intractable
when the target code is a Python package like numpy due to the several modules to instrument
multiply by the different version targeted.

\tristan{Refer to cprofile, memprofile, explain why pytracer is different (e.g. trace density/resolution). Decorator vs systematic instrumentation. Explain the differences.}

\subsection{Monte Carlo Arithmetic}
MCA simulates round-off errors by introducing random perturbations in floating point computations. Each floating point number is replaced by its MCA counterparts:
\[
inexact(x) =  x + \beta^{e_x - t}\xi
\]
where $\beta$ is the basis, $t$ the virtual precision and $\xi \in (-\frac{1}{2},\frac{1}{2})$ a random variable.
Virtual precision is one strength of the MCA method since it allows simulating 
reduced working precision.
MCA comes with three modes: Random Rounding (RR), Precision Bounding (PB) and FullMCA where either the output, either the inputs or both are perturbed with the $inexact$ function.
While the RR mode is equivalent to stochastic rounding, PB mode allows identifying 
catastrophic cancellations.

MCA provides a formula to compute the number of significant digits:
\[
s = -\log_{\beta}{ \left| \dfrac{\sigma}{\mu} \right|}
\]
where $\sigma$ and $\mu$ are respectively the empirical standard deviation and expected value of a variable $x$ evaluating several times with MCA. 
Note that this formula gives an approximation of the real $s$ and 
one can refer to~\cite{sohier2018confidence} to obtain associated rigorous confidence intervals.

\subsection{Fuzzy environment}

\tristan{move to experimental design}

We use the fuzzy~\cite{kiar2020comparing} environment to use MCA in Python.
The fuzzy ecosystem provides a Python interpreter recompiled with Verificarlo.
Verificarlo~\cite{denis2015verificarlo} is a compiler based upon clang~\cite{lattner2008llvm}
that replaces all floating-point operations by a generic call. 
The user can then link these generic calls with different floating-point models 
(called backends) during the execution. Verificarlo propose several 
backends~\cite{chatelain2019automatic,chatelain2019outils} including for MCA.

The main advantage of the fuzzy ecosystem is its transparency for the user.
One can directly use its python code with the fuzzy python interpreter
without manual interventions. Moreover, the fuzzy ecosystem is intended to be
modular by providing fuzzy version of numpy, scipy and scikit-learn modules.
One can thus choose the fuzzy stack desired.

\section{Design principles}

Pytracer follows a three step approach. First, selected functions are automatically
instrumented before executing the targeted application. During the execution, instrumented
functions will dump their inputs and outputs in a file called a trace. 
The idea is to profile several times the application to measure discrepancies between runs.
Based on the set of traces obtained from multiple executions, Pytracer 
will gather them into one trace containing statistics about each traced variables.
With all information gathered, the user can visualize and interact with it through a Ploty/Dash server.

\subsection{Pytracer workflow}

\Yohan{Add figure for the workflow}

\begin{itemize}
    \item Trace application
    \item Merge traces
    \item Visualize trace
\end{itemize}

\subsection{Instrumentation}
Pytracer dynamically instruments the Python modules selected by the user
without requiring modifications of the targeted application.
To do so, Pytracer creates a new version of each selected module 
by preserving the attributes' signature, allowing to use them
transparently in the original application.
If by default Pytracer instruments all attributes present
in a given module, except the special attributes of the form \texttt{\_\_*\_\_},
the wrapping is not always be feasible as detailed in section ?.
The original attributes are then preserved and the user is warned.
The user can also restrict the list of attributes to trace through
a mechanism of inclusion/exclusion.

\subsubsection{Module functions}

The module function is the simplest case to deal with.
For each function encountered in a module, Pytracer
creates a wrapper around this function that is dynamically compiled with the \textit{compile}
builtin function. The original function is then replaced by its wrapped counterpart.

\begin{figure}
    \centering
\begin{lstlisting}
wrapper_code = f"""
def {function_wrapper_name}(*args, **kwargs):
    return generic_wrapper({info},*args,**kwargs)"""
\end{lstlisting}
    \caption{Caption}
    \label{fig:my_label}
\end{figure}

\subsubsection{Class}

Overriding python classes is similar to module functions.
Pytracer goes through the attributes and replaces each callable attribute (method) by its wrapped counterpart.
The resulting class has the same type as the original one, avoiding type conflicts.
However, Python forbids overwriting classes that are a base type. 
In Python, classes are type creators that will produce new instances.
However, Python restricts the inheritance of base type.

    Some classes forbid overwriting attributes of their instances \tristan{why do you need to edit attributes and not just functions?}.
The solution consisting in replacing function by a wrapper cannot be applied here.
\begin{itemize}
    \item Class is not a base type, i.e. can be inherited, we create a new class from the original class by filling its namespace with the callable attributes being replaced by their wrapper counterpart.
    \item Class is a base type, as for \texttt{numpy ufunc}, no 
    general solution can be provided since heritage is forbidden.
    Solutions on a case-by-case basis are provided. 
    \item \texttt{numpy.frompyfunc} can cause errors since signature is not preserved. The function wrapped with this technique always returns \texttt{Python Object} that cause \texttt{TypeError} when the numpy array
    over witch the function is applied is used for indexing another array.
    Tracing \texttt{ufunc} instances can be disabled by the user.
\end{itemize}

\subsection{Detecting instabilities}

\subsection{Visualization}

\subsubsection{Plotly}

\section{Use cases}

\subsection{Numpy}
\subsection{Scikit learn}
\subsection{Dipy}

\section{Performance evaluation}
\subsection{Overhead}
\subsection{Postprocessing}

\section{Discussion}

\section{Conclusion}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\end{document}
\endinput
%%
%% End of file `sample-authordraft.tex'.

### 2021-07-16 paper.tex
Update background tools section

\documentclass[11pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{todonotes}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{color}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{pifont}
\usepackage{xcolor,colortbl}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=black,citecolor=blue,filecolor=black,urlcolor=blue}
\usepackage{amsmath}

\newcommand{\tristan}[1]{\color{orange}\textbf{From Tristan:}#1\color{black}}
\newcommand{\Yohan}[1]{\todo[inline,backgroundcolor=green]{YC:#1}}
\newcommand{\cross}[0]{\cellcolor{red!65}\ding{53}}
\newcommand{\valid}[0]{\cellcolor{green!75!black}\ding{51}}
\newcommand{\warn}[0]{\cellcolor{orange!75}?}

\lstdefinestyle{customPython}{
  belowcaptionskip=1\baselineskip,
  breaklines=true,
  xleftmargin=\parindent,
  language=Python,
  showstringspaces=false,
  basicstyle=\scriptsize\ttfamily,
  keywordstyle=\bfseries\color[rgb]{0.580, 0.000, 0.827},
  %{purple!40!lightgray},
  commentstyle=\itshape\color{green!40!black},
  identifierstyle=\bfseries\color{cyan!75!black},
  stringstyle=\color{orange},
  deletekeywords={double,float},
  classoffset=1, % starting new class
  otherkeywords={double,float},
  morekeywords={double,float},
  keywordstyle=\bfseries\color{green!55!black},
  classoffset=0
}

\begin{document}

\title{PyTracer: Automatically profiling numerical instabilities in Python}
\author{Yohan Chatelain$^1$, Gregory Kiar$^2$, Nigel Young$^1$, Tristan Glatard$^1$\\
$^1$Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada\\
$^2$Center for the Developing Brain, Child Mind Institute, New York, NY, USA}
\date{}
\maketitle

\begin{abstract}
[abstract goes here]
\end{abstract}

\section{Introduction}

The scientific Python ecosystem is a central ingredient of scientific
analyses due to its rich offering of data manipulation, array programming,
numerical analysis, and visualization tools. In particular, libraries such
as NumPy~\cite{harris2020array}, SciPy~\cite{virtanen2020scipy}, scikit-learn~\cite{pedregosa2011scikit} or PyTorch~\cite{paszke2019pytorch} are used in hundreds of publications every year, providing a reference set of high-quality open-source core scientific libraries. Numerous domain-specific data analysis pipelines were built from this ecosystem by diverse research groups, leveraging Python's simplicity and expressivity.

Numerical stability is a crucial requirement of reliable scientific data
processing. In unstable analyses, tiny numerical perturbations introduced
by data noise, software and hardware updates, or parallelization lead to
substantial deviations in final results and potentially different scientific conclusions, threatening the reliability of computational analyses. To address this issue, numerical stability analyses need to be conducted systematically. However, no practical tool currently exists to conduct such analyses on Python programs.

We present PyTracer, a numerical stability analyzer for Python programs.
PyTracer adopts a dynamic approach that evaluates numerical stability using program execution traces, allowing scaling to large programs without manual intervention. In contrast, theoretical approaches based on condition number or backward error analyses require detailed modelling of the program and its numerical implementation. Similarly, static code analysis techniques such as Frama-C~\cite{cuoq2012frama}, Gappa~\cite{de2010certifying} or Flocq~\cite{boldo2011flocq} hardly scale to large codebases, particularly in dynamically-typed languages such as Python.

PyTracer estimates the significant digits of Python floating-point variables by combining program traces obtained with different numerical perturbations, which requires (1) tracing floating-point computations along program executions, (2) generating numerically-perturbed executions, and (3) visualizing stability evaluations. PyTracer addresses these requirements with (1) dynamic instrumentation of Python functions, modules and classes through meta-programming, (2) a ``fuzzy" Python interpreter instrumented with Monte-Carlo arithmetic, and (3) an interactive Plotly dashboard to visualize stability measures throughout program executions.

Through stability evaluations of 
SciPy, scikit-learn, and pyAFQ~\cite{kruper2021evaluating} --- an analysis toolbox for diffusion magnetic resonance imaging --- we demonstrate PyTracer as a practical solution to review the numerical stability of extensive code bases. The remainder of this manuscript describes related approaches, presents the design of PyTracer, and demonstrates its potential on various use cases.

% \begin{itemize}
%     \item Numerical instabilities are inherent to numerical computations \tristan{not only to HPC, also software updates, small perturbations in parameters or data}
%     \item 
%     \item Neuroimaging tools are facing reproducibility issues, one factor of which is numerical stability \tristan{neuroimaging should be an illustration, your intro should rather focus on Python in general, it's much more impactful} 
%     \item Detecting those instabilities is challenging: large data sets, large pipeline, long computation time, complex physics \tristan{Here you could illustrate the point with neuroimaging pipelines}
%     \item Needs tools for automatically detecting these instabilities
%     \item Needs tools to quickly identify unstable functions among large number of calls
% \end{itemize}

\section{Related work}

In this section, we review tools and theoretical frameworks related to Pytracer components.
We start by reviewing state-of-the-art dynamic tools for detecting numerical instabilities.
Then, we focus on existing theoretical approaches for perturbations-based techniques to detect numerical instabilities,
Pytracer being agnostic to perturbation technique used. Finally, we review visualization tools 
aiming at detecting numerical instabilities over execution time.

\label{sec:soa}
\subsection{Numerical assessment tools}

Several tools have been and continue to be developed to assess numerical quality.
Those tools can be divided in two main categories: static VS dynamic analysis.
Static analysis focuses on safety and soundness of error bounds provided 
while dynamic analysis rather provides proof-less numerical quality estimations.
The main drawback of static analysis tools is the poor scalability that confine them to small programs.
Pytracer falls into the second category by targeting real Python use cases.
In this section, we will hence review the most known tools based on dynamic analysis.
We divide the tools in three sections starting by tools dedicated to non Python codes, then 
tools using Dynamic Binary Instrumentation and finally tools dedicated to Python codes.

Following the languages mainly used in HPC or embedded systems, 
most the tools are dedicated to C, C++ or FORTRAN codes. 
Those tools are either source-to-source or compiler based transformations.
CADNA~\cite{jezequel2008cadna} is a library for C, C++ and Fortran codes implementing
the CESTAC~\cite{vignes1993stochastic} method, a stochastic arithmetic used for detecting round-off
errors by introducing numerical instabilities in floating-point computations.
Verificarlo~\cite{verificarlo} is a compiler that instruments floating point operations
to replace them by generic call to Verificarlo API, providing several backends implementations including one for 
Monte Carlo Arithmetic (MCA) (cf.~\ref{sec:mca}), another stochastic arithmetic.
Bao et al. ~\cite{bao2013fly} modifies gcc to track local floating-point error across execution.
pLiner~\cite{guo2020pliner} is root cause analyzer based upon clang that detects floating point operations 
responsible of result variability. 
It uses source-to-source transformation at AST level to rewrite parts of code with higher precision and to compare the result with
the original one. PFPSanatizer~\cite{chowdhary2021parallel} is a compiler that uses parallel shadow execution to detect numerical issues
by using higher precision. 
Shaman~\cite{demeure_phd} is a C++ library that uses a first-order error model to propagate numerical error. 
FLiT~\cite{sawaya2017flit} is framework to detect variability induced by compilers and their optimizations.
Tang et al.~\cite{tang2016software} propose a source-to-source framework for executing targeted code 
in infinite and fixed precision with and without using stochastic arithmetic.

The main other existing approach uses Dynamic Binary Instrumentation (DBI) to perform analysis at the binary level,
removing the language barrier and allowing to analyze any binary without needing the source code. This approach
is particularly relevant on closed-source software. However, working at binary level loses high-level information useful
for debugging and understanding the source code semantic and logic.
CraftHPC~\cite{lam2013dynamic} uses DBI to detect catastrophic cancellations at runtime.
Verrou~\cite{fevotte2016verrou} is a Valgrind~\cite{nethercote2007valgrind} based tool that replaces on-the-fly
floating-point operations by their stochastic arithmetic counterparts. FPDebug~\cite{benz2012dynamic} uses DBI to detect numerical 
inaccuracies by using shadow computations with a higher precision.
Herbgring~\cite{sanchez2017finding} is a Valgrind-based tool to detect
numerical instabilities. It uses a shadow memory to do detect precision losses by comparison with results obtained with the high-precision 
MPFR library~\cite{fousse2007mpfr}. It is combined with symbolic computation to backtrack the root of the error.

Existing tools for tracing Python code are dedicated to performance profiling, for time (cProfile) 
or memory consumption (memprofile). 
To the best of our knowledge, there is currently no tool dedicated to numerical analysis.
We can nevertheless mention Anteater~\cite{faust2019anteater} a Python tracer tool that aims at debugging Python application. 
It operates source transformation at AST level but only deals with native numeric Python types.
However, we can compare the methodology used by these tools against the one used in Pytracer.
These tools use an instrumentation based on decorators, a Python mechanism allowing 
to wrap a function by adding a line over a function declaration.
While this method is useful when targeting specific functions, it becomes time consuming 
when applied to a large number of functions since one need to tag functions by hand,
which clearly not tractable for large codes like numpy. Moreover, the user has most of the time no clues
about where numerical instability comes from and must therefore all functions as potentially suspect. 
This issue enforces the need to use automatic approaches.
It's worth mentioning that DBI based tools can be used for Python because they are language agnostic but
they are not intended to analyze Python code and do not take into account high-level information about 
types being used or detailed stack trace. Moreover, few tools embed a visualizer for 
analyzing numerical quality over time letting the postprocessing to the user.

\tristan{The content of this section is excellent but the structure is a bit messy. Would you like to restructure in 3 paragraphs as follows? (1) There's no numerical instrumentation tools in Python (your last paragraph + anteater), (2) DBI tools could be used but won't provide a detailed stack trace, (3) tools for other languages.}

\subsection{Detecting instabilities}

We review here the existing theoretical framework that might be used to detect numerical instabilities.

\label{sec:mca}
\subsubsection{Monte Carlo Arithmetic}
\tristan{Add a sentence to connect this part to the previous one. Something like: We use Monte-Carlo arithmetic to detect numerical instabilities. You could also summarize what the other options would be.} \tristan{cite \cite{parker1997monte}}

MCA simulates round-off errors by introducing random perturbations in floating point computations. Each floating point number is replaced by its MCA counterparts:
\[
inexact(x) =  x + \beta^{e_x - t}\xi
\]
where $\beta$ is the basis, $t$ the virtual precision and $\xi \in (-\frac{1}{2},\frac{1}{2})$ a random variable.
Virtual precision is one strength of the MCA method since it allows simulating 
reduced working precision.
MCA comes with three modes: Random Rounding (RR), Precision Bounding (PB) and FullMCA where either the output, either the inputs or both are perturbed with the $inexact$ function.
While the RR mode is equivalent to stochastic rounding, PB mode allows identifying 
catastrophic cancellations.

MCA provides a formula to compute the number of significant digits:
\[
s = -\log_{\beta}{ \left| \dfrac{\sigma}{\mu} \right|}
\]
where $\sigma$ and $\mu$ are respectively the empirical standard deviation and expected value of a variable $x$ evaluating several times with MCA. 
Note that this formula gives an approximation of the real $s$ and 
one can refer to~\cite{sohier2018confidence} to obtain associated rigorous confidence intervals.

\subsection{Visualization}

SHAMAN, CADNATrace;
Veritracer~\cite{chatelain2018veritracer} is an extension of Verificarlo~\cite{verificarlo} that aims 
at visualizing the numerical stability over time for C, C++ and Fortran codes.

\section{PyTracer design}

% \subsection{Pytracer workflow}

PyTracer follows a three step approach. First, selected functions are automatically
instrumented before executing the targeted application. During the execution, instrumented
functions will dump their inputs and outputs in a file called a trace. 
The idea is to profile several times the application to measure discrepancies between runs.
Based on the set of traces obtained from multiple executions, Pytracer 
will gather them into one trace containing statistics about each traced variables.
With all information gathered, the user can visualize and interact with it through a Ploty/Dash server.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figure/workflow.pdf}
    \caption{Pytracer workflow \tristan{Excellent figure but fuzzy should appear}}
    \label{fig:workflow}
\end{figure}

\subsection{Instrumentation}

Pytracer dynamically instruments the Python modules selected by the user
without requiring modifications of the targeted application.
To do so, Pytracer creates a new version of each selected module 
by preserving the attributes' signature, allowing to use them
transparently in the original application.
If by default Pytracer instruments all attributes present
in a given module, except the special attributes of the form \texttt{\_\_*\_\_},
the wrapping is not always be feasible as detailed in section ?.
The original attributes are then preserved and the user is warned.
The user can also restrict the list of attributes to trace through
a mechanism of inclusion/exclusion.

The main advantage of this method is its transparency for the user
since this latter only needs to select which modules to trace and Pytracer instrument them for him.
Moreover, the code does not need to be changed contrary to the method based on decorators, allowing
to use instrument functions when the source code is not available or editable, like for instance
in singularity containers or when running on HPC cluster.

\subsection{Module import interception}

Modules in Python are loaded through the import mechanism by the \texttt{import} keyword.
During this process, Python is looking for module path file in the default system paths and those provided by
the user (with \texttt{PYTHONPATH}). When the selected module is found, Python executes it for triggering 
instructions in the \texttt{\_\_init\_\_.py} file and stores it in the \texttt{sys.modules} map,
acting as a cache.

Pytracer intercepts the module loaded by using the \texttt{Finder} and \texttt{Loader} mechanism.
The Finder is responsible for finding the loader for a module that is being imported while the 
Loader loads and initializes the module. We add a new Finder and Loader on top of the default ones
to intercept imports and to wrap modules selected by the user. This mechanism allows returning 
the original module in the wrapper code and returning the wrapped one in the targeted application
without modifying the actual code.

\subsubsection{Module functions}

The module function is the simplest case to deal with.
For each function encountered in a module, Pytracer
creates a wrapper around this function that is dynamically compiled with the \textit{compile}
builtin function. The original function is then replaced by its wrapped counterpart.

However, this technique cannot be applied for all functions, especially for 
callable instances, which are instances of class that can be called like traditional functions
but that contain attributes. Indeed, using a wrapper would 1) modify the type of the instance
that could cause semantic bugs 2) hide attributes that causes \texttt{AttributeError} exceptions.

\begin{figure}
    \centering
\begin{lstlisting}[language=Python,style=customPython]
def getwrapperfunction(function_module, function_name, function, function_wrapper_name):
    function_wrapper_name = f
    function_id = id(function)
    info = (function_id, function_module, function_name)
    wrapper_code = f"""
    def {function_wrapper_name}(*args, **kwargs):
        return generic_wrapper({info},*args,**kwargs)"""
    return wrapper_code
\end{lstlisting}
    \caption{Caption}
    \label{fig:wrapper_code}
\end{figure}

\subsubsection{Classes}

Overriding Python classes is similar to module functions.
Pytracer goes through the attributes and replaces each callable attribute (method) by its wrapped counterpart.
The resulting class has the same type as the original one, avoiding type conflicts.
However, some classes forbid overwriting attributes of their instances, in particular the `\_\_call\_\_` operator
allowing to call an instance as a function.
Moreover, no general solution can be provided since some Python classes are non-inheritable 
like \texttt{bool},\texttt{NoneType} or \textit{universal functions} in numpy (\texttt{ufunc})
and thus cannot be inherited to overload operators.
The solution consisting in replacing function by a wrapper cannot be applied here.

This issue was mostly encountered with numpy ufunc that are intensively used in numpy. Universal functions are vectorized element-wise operators on
multidimensional arrays (\texttt{ndarrays}). They are implemented in C code with target specialized versions to achieve best performance.
One should then implement subclassing mechanism in C, which is contrary to Pytracer philosophy to be as non-intrusive and portable as possible.
However, since \texttt{ufunc} are intensively used in scientific computational codes (elementary mathematical functions are ufunc in numpy),
we implement a special treatment for them. Numpy provides the \texttt{frompyfunc} helper function to create \texttt{ufunc} from arbitrary function.
The main problem with this approach is that the output type is \texttt{PyObject} representing abstract object that conflicts 
when used as index. Figure illustrates this issue. As a last resort, user may disable \texttt{ufunc} tracing by Pytracer.

\begin{figure*}
\begin{minipage}[t]{0.4\linewidth}
    \begin{lstlisting}[language=Python,style=customPython]
>>> import numpy as np
>>> x = np.array(range(10))
>>> index = np.array([1,-1],dtype=int)
>>> x[index]
>>> array([1, 9])
    \end{lstlisting}
    \label{fig:wrapper_code}
\end{minipage}
\begin{minipage}[t]{0.4\linewidth}
    \begin{lstlisting}[language=Python,style=customPython]
>>> import numpy as np
>>> x = np.array(range(10))
>>> index = np.array([1,-1], dtype=object)
>>> x[index]
Traceback (most recent call last):
  File "<stdin>", line 1, in <module>
IndexError: arrays used as indices must be of integer (or boolean) type
    \end{lstlisting}
    \label{fig:wrapper_code}
\end{minipage}
\caption{Illustration of the issue of using \texttt{frompyfunc} function to convert function to \texttt{ufunc}.}
\end{figure*}

\subsection{Detecting instabilities}

\subsubsection{Fuzzy environment}

We use the fuzzy~\cite{kiar2020comparing} environment to use MCA in Python.
The fuzzy ecosystem provides a Python interpreter recompiled with Verificarlo.
Verificarlo~\cite{verificarlo} is a compiler based upon clang~\cite{lattner2008llvm}
that replaces all floating-point operations by a generic call. 
The user can then link these generic calls with different floating-point models 
(called backends) during the execution. Verificarlo proposes several 
backends~\cite{chatelain2019automatic,chatelain2019outils} including for MCA.

The main advantage of the fuzzy ecosystem is its transparency for the user.
One can directly use its python code with the fuzzy python interpreter
without manual interventions. Moreover, the fuzzy ecosystem is intended to be
modular by providing fuzzy version of numpy, scipy and scikit-learn modules.
One can thus choose the fuzzy stack desired.

\subsection{Interactively visualization}

\subsubsection{Plotly}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figure/pytracer_layout.pdf}
    \caption{Pytracer visualization layout.}
    \label{fig:my_label}
\end{figure}

\section{Use cases}

\subsection{SciPy}

We tested Pytracer on SciPy~\cite{virtanen2020scipy} examples provided in the Tutorial website section.
SciPy is organized in several libraries targeting specific computing domains.
We focused on the following packages:
\begin{itemize}
    \item \texttt{fftpack}: Fast Fourier Transform routines
    \item \texttt{interpolate}: Interpolation and smoothing splines
    \item \texttt{optimize}: Optimization and root-finding routines
    \item \texttt{integration}: Integration and ordinary differential equation solvers
\end{itemize}

% \begin{table}[]
%     \centering
%     \begin{tabular}{|c|c|c|c|c||c|c|c|c|}
%     \hline
%     \multirow{3}{5em}{Application} & \multicolumn{4}{|c||}{RR} & \multicolumn{4}{|c|}{MCA} \\\cline{2-9}
%                 & \multicolumn{2}{|c|}{numpy} &  \multicolumn{2}{|c||}{no numpy} & \multicolumn{2}{|c|}{numpy} & \multicolumn{2}{|c|}{no numpy} \\\cline{2-9}
%                 & run & parse &  run & parse & run & parse & run & parse \\
%     \hline
%     %        &               RR                 &                 MCA               \\
%     %        &  numpy         &   no numpy      &      numpy      &     no numpy    \\
%     %        & run   & parse  &  run   &  parse &  run   & parse  & run    & parse  \\
%     \multirow{4}{5em}{Interpolate}
%     \multirow{12}{5em}{Optimize}
%     \multirow{3}{5em}{FFT}
%     Adaboost & \warn & \valid & \valid & \valid & \warn & \cross & \cross & \cross \\
%     Bayesian Ridge Regression & \warn & \valid & \valid & \valid & \cross & \cross & \cross & \cross \\
%     Online classifier comparison & \valid & \valid & \valid & \valid & \cross & \cross & \cross & \cross  \\
%     Cluster Iris & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
%     Covariance estimation & \valid & \cross & \valid & \cross & \cross & \cross & \valid & \cross \\
%     Decision Tree Regression & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
%     Digits Classification & \warn & \valid & \valid & \valid & \warn & \cross & \cross & \cross \\
%     Face Recognition & \cross & \valid & \cross & \valid & \cross & \cross & \cross & \cross \\
%     L1 Penalty & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \valid \\
%     Lasso and elastic net & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \cross \\
%     Separating hyperplan & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
%     MNIST classification & \warn & \valid & \valid & \valid & \valid & \cross & \valid & \valid \\
%     Multitask Lasso & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \valid \\
%     Orthogonal matching & \warn & \valid & \valid & \valid & \cross & \valid & \cross & \valid \\
%     PCA decomposition & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \cross \\
%     Robust Linear Regression & \valid & \valid & \valid & \valid & \warn & \cross & \valid & \cross \\
%     Segmentation toy & \warn & \valid & \valid & \cross & \warn & \cross & \cross & \cross \\
%     SVM & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
%     Tomography & \warn & \valid & \valid & \cross & \warn & \cross & \cross & \cross \\
%     Weighted samples & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
%     \hline
%     \end{tabular}
%     \caption{Pytracer executions summary}
%     \label{tab:pytracer_sklearn_results_summary}
% \end{table}

\subsection{Scikit learn}

We tested Pytracer on Scikit-learn~\cite{pedregosa2011scikit}, a "Python module integrating a wide range of state-of-the-art machine learning algorithms for medium-scale supervised and unsupervised problems".
Scikit-learn offers a well supplied and documented list of examples that facilitates its using with Pytracer.
Among the several available examples, we choose the following representative set:
\href{https://scikit-learn.org/stable/auto_examples/ensemble/plot_adaboost_regression.html#sphx-glr-auto-examples-ensemble-plot-adaboost-regression-py}{Decision Tree Regression with AdaBoost},
\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_bayesian_ridge.html#sphx-glr-auto-examples-linear-model-plot-bayesian-ridge-py}{Bayesian Ridge Regression}, 
\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_sgd_comparison.html#sphx-glr-auto-examples-linear-model-plot-sgd-comparison-py}{Comparing various online solvers}, 
\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_sgd_comparison.html#sphx-glr-auto-examples-linear-model-plot-sgd-comparison-py}{K-means Clustering},
\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_sgd_comparison.html#sphx-glr-auto-examples-linear-model-plot-sgd-comparison-py}{Recognizing hand-written digits},
\href{https://scikit-learn.org/stable/auto_examples/decomposition/plot_faces_decomposition.html#sphx-glr-auto-examples-decomposition-plot-faces-decomposition-py}{Faces dataset decompositions},
\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_logistic_l1_l2_sparsity.html#sphx-glr-auto-examples-linear-model-plot-logistic-l1-l2-sparsity-py}{L1 Penalty and Sparsity in Logistic Regression},
\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_lasso_and_elasticnet.html#sphx-glr-auto-examples-linear-model-plot-lasso-and-elasticnet-py}{Lasso and Elastic Net for Sparse Signals},
\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_sgd_separating_hyperplane.html#sphx-glr-auto-examples-linear-model-plot-sgd-separating-hyperplane-py}{SGD: Maximum margin separating hyperplane},
\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_sparse_logistic_regression_mnist.html#sphx-glr-auto-examples-linear-model-plot-sparse-logistic-regression-mnist-py}{MNIST classification using multinomial logistic + L1},
\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_sgd_iris.html#sphx-glr-auto-examples-linear-model-plot-sgd-iris-py}{Plot multi-class SGD on the iris dataset},
\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_multi_task_lasso_support.html#sphx-glr-auto-examples-linear-model-plot-multi-task-lasso-support-py}{Joint feature selection with multi-task Lasso},
\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_omp.html#sphx-glr-auto-examples-linear-model-plot-omp-py}{Orthogonal Matching Pursuit},
\href{https://scikit-learn.org/stable/auto_examples/decomposition/plot_pca_iris.html#sphx-glr-auto-examples-decomposition-plot-pca-iris-py}{PCA example with Iris Data-set},
\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_poisson_regression_non_normal_loss.html#sphx-glr-auto-examples-linear-model-plot-poisson-regression-non-normal-loss-py}{Poisson regression and non-normal loss},
\href{https://scikit-learn.org/stable/auto_examples/cluster/plot_segmentation_toy.html#sphx-glr-auto-examples-cluster-plot-segmentation-toy-py}{Spectral clustering for image segmentation},
\href{https://scikit-learn.org/stable/auto_examples/svm/plot_separating_hyperplane_unbalanced.html#sphx-glr-auto-examples-svm-plot-separating-hyperplane-unbalanced-py}{SVM: Separating hyperplane for unbalanced classes},
\href{https://scikit-learn.org/stable/auto_examples/applications/plot_tomography_l1_reconstruction.html#sphx-glr-auto-examples-applications-plot-tomography-l1-reconstruction-py}{Compressive sensing: tomography reconstruction with L1 prior (Lasso)},
\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_tweedie_regression_insurance_claims.html#sphx-glr-auto-examples-linear-model-plot-tweedie-regression-insurance-claims-py}{Tweedie regression on insurance claims},
\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_sgd_weighted_samples.html#sphx-glr-auto-examples-linear-model-plot-sgd-weighted-samples-py}{SGD: Weighted samples}.

We used the fuzzy environment with numpy, scipy and scitkit-learn instrumented. 
We tested two perturbations modes: Random Rounding (RR) and Full MCA (MCA).

\begin{table}[]
    \centering
    \begin{tabular}{|c|c|c|c|c||c|c|c|c|}
    \hline
    \multirow{3}{5em}{Application} & \multicolumn{4}{|c||}{RR} & \multicolumn{4}{|c|}{MCA} \\\cline{2-9}
                & \multicolumn{2}{|c|}{numpy} &  \multicolumn{2}{|c||}{no numpy} & \multicolumn{2}{|c|}{numpy} & \multicolumn{2}{|c|}{no numpy} \\\cline{2-9}
                & run & parse &  run & parse & run & parse & run & parse \\
    \hline
    %        &               RR                 &                 MCA               \\
    %        &  numpy         &   no numpy      &      numpy      &     no numpy    \\
    %        & run   & parse  &  run   &  parse &  run   & parse  & run    & parse  \\
    Adaboost & \warn & \valid & \valid & \valid & \warn & \cross & \cross & \cross \\
    Bayesian Ridge Regression & \warn & \valid & \valid & \valid & \cross & \cross & \cross & \cross \\
    Online classifier comparison & \valid & \valid & \valid & \valid & \cross & \cross & \cross & \cross  \\
    Cluster Iris & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
    Covariance estimation & \valid & \cross & \valid & \cross & \cross & \cross & \valid & \cross \\
    Decision Tree Regression & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
    Digits Classification & \warn & \valid & \valid & \valid & \warn & \cross & \cross & \cross \\
    Face Recognition & \cross & \valid & \cross & \valid & \cross & \cross & \cross & \cross \\
    L1 Penalty & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \valid \\
    Lasso and elastic net & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \cross \\
    Separating hyperplan & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
    MNIST classification & \warn & \valid & \valid & \valid & \valid & \cross & \valid & \valid \\
    Multitask Lasso & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \valid \\
    Orthogonal matching & \warn & \valid & \valid & \valid & \cross & \valid & \cross & \valid \\
    PCA decomposition & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \cross \\
    Robust Linear Regression & \valid & \valid & \valid & \valid & \warn & \cross & \valid & \cross \\
    Segmentation toy & \warn & \valid & \valid & \cross & \warn & \cross & \cross & \cross \\
    SVM & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
    Tomography & \warn & \valid & \valid & \cross & \warn & \cross & \cross & \cross \\
    Weighted samples & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
    \hline
    \end{tabular}
    \caption{Pytracer executions summary}
    \label{tab:pytracer_sklearn_results_summary}
\end{table}

Table~\ref{tab:pytracer_sklearn_results_summary} summaries sklearn experiments with Pytracer.

\subsubsection{Decision Tree Regression with AdaBoost}

A decision tree is boosted using the AdaBoost.R2~\cite{drucker1997improving} 
algorithm on a 1D sinusoidal dataset with a small amount of Gaussian noise. 
299 boosts (300 decision trees) is compared with a single decision tree regressor. 
As the number of boosts is increased the regressor can fit more detail. 
The execution with Pytracer reveals a numerical stability.

\begin{figure}
    \centering
    \caption{Caption}
    \includegraphics[width=\linewidth]{figure/adaboost/predict_adaboost_s.png}
    \caption{Number of significant digits of predicted values array.}
    \label{fig:adaboost_predict_s}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figure/adaboost/adaboost_boost_mean.png}
    \caption{Mean values of boost function.}
    \label{fig:adaboost_boost_mean}
\end{figure}

\begin{figure}
    \centering
    \caption{Caption}
    \includegraphics[width=\linewidth]{figure/adaboost/predict_adaboost_zoom_s.png}
    \caption{Average number of significant digits of prediction over estimator}
    \label{fig:adaboost_predict_zoom_s}
\end{figure}

\begin{figure}
\begin{minipage}{0.4\linewidth}
    \includegraphics[width=\linewidth]{figure/adaboost/to_predict_adaboost_mean.png}
    \caption{Values to predict}
    \label{fig:adaboost_to_predict_mean}
\end{minipage}
\begin{minipage}{0.4\linewidth}
    \includegraphics[width=\linewidth]{figure/adaboost/predict_adaboost_zoom_mean.png}
    \caption{Predicted values}
    \label{fig:adaboost_predicted_mean}
\end{minipage}
\caption{Comparison between original (fig.~\ref{fig:adaboost_to_predict_mean}) and predicted (fig.~\ref{fig:adaboost_predicted_mean}) values}
\end{figure}

\subsubsection{Bayesian Ridge Regression}

"\texttt{BayesianRidge} estimates a probabilistic model of the regression problem as described above. 
The prior for the coefficient  is given by a spherical Gaussian:
\[
    p(w|\lambda)=\mathcal{N}(w|0,\lambda^{-1}\mathbf{I}_p)
\]
The priors over  and  are chosen to be gamma distributions, the conjugate prior for the precision of the Gaussian. 
The resulting model is called Bayesian Ridge Regression, and is similar to the classical Ridge.
The parameters, and are estimated jointly during the fit of the model, 
the regularization parameters and being estimated by maximizing the log marginal likelihood. 
The scikit-learn implementation is based on the algorithm~\cite{tipping2001sparse}."

Both execution with RR and MCA modes failed but two different errors. 
Execution in RR mode raises an error due to an invalid value encountered in the \texttt{sqrt} function
while the MCA mode execution raises an error due to an issue with the Singular Value Decomposition (SVD) divergence.

RR executions fail with an invalid value in the \texttt{sqrt} function 
used in the \texttt{\_update\_coef\_} method of the \texttt{BayesianRidge} class.
This method updates the posterior mean and compute the corresponding Root-Mean-Square-Error (rmse).

When we backtrack the error propagation, we see that

MCA executions show the limit of Pytracer since the SVD decomposition in scipy is a wrapper around the 
\texttt{gesdd} or \texttt{gesvd} LAPACK~\cite{anderson1999lapack} functions. 
Numerical instabilities that are coming from this kernel are opaque for Pytracer since it works 
at the Python level. Tools working on C/FORTAN codes 
like Veritracer~\cite{chatelain2018veritracer} can be used to zoom in on these functions.
Nevertheless, Pytracer provides have a visualization of the input used by the SVD and several
metrics used in numerical analysis, like the condition number, that can help to understand.

\subsection{Classifier comparisions}

This test compares the performance of 6 online solvers on the hand-written digits dataset.
These 6 solvers are:
\begin{itemize}
    \item Stochastic Gradient Descent 
    \item Averaged Stochastic Gradient Decent
    \item Perceptron
    \item Passive-Aggressive I \& II
    \item SAG: Minimizing Finite Sums with the Stochastic Average Gradient
\end{itemize}

Each solver is trained and predicts 20 times on 6 different training size ratio.

Figure~\ref{fig:classifier_comparisons_general} shows the all functions
traced by Pytracer over time. We can see the estimated number of significant digits varies a lot between 
values from 1 to 80 bits. Figure~\ref{fig:classifier_comparisons_mean_predictions} shows 
the average prediction score for each classifiers. The yellow points 
represent the average correct prediction score for one round and one classifier (line. 48) while blue points
tshows average predictions over the 20 rounds (line. 49).
We can see that precision is pretty low with an average solution below 10 significant bits, with 
an exception for values between the 24k and 32k invocation that correspond to the Perceptron
classifier. Indeed, this classifier is pretty stable with an average number of significant digits around 52 bits.

\begin{figure}
    \begin{lstlisting}[language=Python,style=customPython,numbers=left, firstnumber=19]
    heldout = [0.95, 0.90, 0.75, 0.50, 0.01]
    rounds = 20
    X, y = datasets.load_digits(return_X_y=True)

    classifiers = [
        ("SGD", SGDClassifier(max_iter=100)),
        ("ASGD", SGDClassifier(average=True)),
        ("Perceptron", Perceptron()),
        ("Passive-Aggressive I", PassiveAggressiveClassifier(loss='hinge',
                                                             C=1.0, tol=1e-4)),
        ("Passive-Aggressive II", PassiveAggressiveClassifier(loss='squared_hinge',
                                                              C=1.0, tol=1e-4)),
        ("SAG", LogisticRegression(
            solver='sag', tol=1e-1, C=1.e4 / X.shape[0]))
    ]

    xx = 1. - np.array(heldout)

    for name, clf in classifiers:
        print("training %s" % name)
        rng = np.random.RandomState(42)
        yy = []
        for i in heldout:
            yy_ = []
            for r in range(rounds):
                X_train, X_test, y_train, y_test = \
                    train_test_split(X, y, test_size=i, random_state=rng)
                clf.fit(X_train, y_train)
                y_pred = clf.predict(X_test)
                yy_.append(1 - np.mean(y_pred == y_test))
            yy.append(np.mean(yy_))
        plt.plot(xx, yy, label=name)
    \end{lstlisting}
    \label{fig:wrapper_code}
\caption{Illustration of the issue of using \texttt{frompyfunc} function to convert function to \texttt{ufunc}.}
\end{figure}

\begin{figure}
    \centering
    \caption{Caption}
    \includegraphics[width=\linewidth]{figure/classifier_comparisons/general.png}
    \caption{Number of significant digits (General view).}
    \label{fig:classifier_comparisons_general}
\end{figure}

\begin{figure}
    \centering
    \caption{Caption}
    \includegraphics[width=\linewidth]{figure/classifier_comparisons/mean_predicition_s.png}
    \caption{Number of significant digits (General view).}
    \label{fig:classifier_comparisons_mean_predictions}
\end{figure}

\begin{figure}
    \centering
    \caption{Caption}
    \includegraphics[width=\linewidth]{figure/classifier_comparisons/SAG_predicition_s.png}
    \caption{Number of significant digits (General view).}
    \label{fig:classifier_comparisons_general}
\end{figure}

\begin{figure}
    \centering
    \caption{Caption}
    \includegraphics[width=\linewidth]{figure/classifier_comparisons/zoom_SAG_fit_coef_s.png}
    \caption{Number of significant digits (General view).}
    \label{fig:classifier_comparisons_general}
\end{figure}

\subsection{Cluster IRIS}

\begin{figure}
    \centering
    \caption{Caption}
    \includegraphics[width=\linewidth]{figure/cluster_iris/general.png}
    \caption{Number of significant digits (General view).}
    \label{fig:cluster_iris_general}
\end{figure}

\subsection{PyAFQ}

PyAFQ is Python package for Automated Fiber Quantification.
It aims at finding delineation of the major fiber tracts in individual human brains, and quantification of the tissue properties within the tracts.

\section{Performance evaluation}

In this section, we review the performance overhead of the Pytracer's instrumentation cost
and the time spent during the postprocessing analysis.

\subsection{Overhead}

Pytracer instrumentation overhead comes from the time spent to instrument module (initialization overhead)
before executing the targeted application plus the cost for dumping the data during the execution (running overhead).
However, initialization overhead is amortized when traced applications are above ....
Table~\ref{tab:pytracer_overhead} summaries the slowdown measure on pyAFQ test.
We can see that Pytracer only a gives reasonable slowdown of $\times 6$.

\begin{table}[]
    \centering
    \begin{tabular}{c|c|c|c|c}
         Pytracer & Verificarlo Instrumentation & Backend & Time (hours:minutes:seconds) & Overhead \\
         \hline 
         No & No & - & 00:30:51 & 1 \\
         No & Yes & IEEE & 01:32:56 & 3 \\
         No & Yes & RR & 16:52:08 & 32 \\
         Yes & No & - & 03:11:07 & 6  \\
         Yes & Yes & IEEE & 11:14:33 & 22 \\
         Yes & Yes & RR & 25:05:54 & 48 \\
    \end{tabular}
    \caption{Caption}
    \label{tab:pytracer_overhead}
\end{table}

% \begin{table}[]
%     \centering
%     \begin{tabular}{c|c|c|c|c}
%          Pytracer & Verificarlo Instrumentation & Backend & Time (hours:minutes:seconds) & Overhead \\
%          \hline 
%          No & No & - & 15 & 1 \\
%          No & Yes & IEEE & 49 & 3 \\
%          No & Yes & RR &  & 441 & 29 \\
%          Yes & No & - & 03:11:07 & 6  \\
%          Yes & Yes & IEEE & 11:14:33 & 22 \\
%          Yes & Yes & RR & 25:05:54 & 48 \\
%     \end{tabular}
%     \caption{Caption}
%     \label{tab:pytracer_overhead}
% \end{table}

\subsection{Postprocessing}

\section{Discussion}

\begin{itemize}
    \item Control flow divergence
    \item MCA mode -> semantic bugs
    \item Pytracer is flexible and works with any type of perturbations (uncertainty quantification, internal randomness, parallel sections).

\end{itemize}

\section{Conclusion}

\bibliographystyle{abbrv}
\bibliography{biblio}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\end{document}
\endinput
%%
%% End of file `sample-authordraft.tex'.

### 2021-09-21 paper.tex
Tristan's review on sections 3 and 4.1.1

@@
 \usepackage{amsmath}
+\usepackage{xspace}
+\usepackage{makecell}
+\usepackage{ulem} % provides sout
+\usepackage{minted} % Provides listing environment
 
-\newcommand{\tristan}[1]{\color{orange}\textbf{From Tristan:}#1\color{black}}
-\newcommand{\Yohan}[1]{\todo[inline,backgroundcolor=green]{YC:#1}}
+\newcommand{\tristan}[1]{\color{orange}\textbf{From Tristan:} #1\color{black}\xspace}
+\newcommand{\tristanmod}[2]{\color{orange}\sout{#1} #2\color{black}\xspace}
+
+\newcommand{\Yohan}[1]{\color{green!75!black}\textbf{Yohan:} #1\color{black}\xspace}
 \newcommand{\cross}[0]{\cellcolor{red!65}\ding{53}}
@@
 \newcommand{\warn}[0]{\cellcolor{orange!75}?}
+\newcommand{\pytracer}[0]{PyTracer\xspace}
+
+\usepackage{tabularx} % provides tabularx to adjust table column sizes to page size
+% define thickline for use in tables
+\makeatletter
+\newcommand{\thickhline}{%
+    \noalign {\ifnum 0=`}\fi \hrule height 1pt
+    \futurelet \reserved@a \@xhline
+}
+\newcolumntype{"}{@{\hskip\tabcolsep\vrule width 1pt\hskip\tabcolsep}}
+\makeatother
 
@@
 
+\lstdefinestyle{customC}{
+  belowcaptionskip=1\baselineskip,
+  breaklines=true,
+  xleftmargin=\parindent,
+  language=C,
+  showstringspaces=false,
+  basicstyle=\scriptsize\ttfamily,
+  keywordstyle=\bfseries\color[rgb]{0.580, 0.000, 0.827},
+  %{purple!40!lightgray},
+  commentstyle=\itshape\color{green!40!black},
+  identifierstyle=\bfseries\color{cyan!75!black},
+  stringstyle=\color{orange},
+  deletekeywords={double,float},
+  classoffset=1, % starting new class
+  otherkeywords={double,float},
+  morekeywords={double,float},
+  keywordstyle=\bfseries\color{green!55!black},
+  classoffset=0
+}
+
 \begin{document}
+
+\makeatletter
+\let\orig@lstnumber=\thelstnumber
+\newcommand\lstsetnumber[1]{\gdef\thelstnumber{#1}}
+\newcommand\lstresetnumber{\global\let\thelstnumber=\orig@lstnumber}
+\makeatother
 
@@
 
-The scientific Python ecosystem is a central ingredient of scientific
+The scientific Python ecosystem is a central component of scientific
 analyses due to its rich offering of data manipulation, array programming,
@@
 Numerical stability is a crucial requirement of reliable scientific data
-processing. In unstable analyses, tiny numerical perturbations introduced
+processing. In unstable analyses, small numerical perturbations introduced
 by data noise, software and hardware updates, or parallelization lead to
@@
 We present PyTracer, a numerical stability analyzer for Python programs.
-PyTracer adopts a dynamic approach that evaluates numerical stability using program execution traces, allowing scaling to large programs without manual intervention.
+PyTracer adopts a dynamic approach that evaluates numerical stability using program execution traces, enabling scaling to large programs without manual intervention.
 In contrast, theoretical approaches based on condition number or backward error analyses require detailed modelling of the program and its numerical implementation.
@@
 
-In this section, we review tools and theoretical frameworks related to Pytracer components.
-We start by reviewing state-of-the-art dynamic tools for detecting numerical instabilities.
-Then, we focus on existing theoretical approaches for perturbations-based techniques to detect numerical instabilities,
-Pytracer being agnostic to perturbation technique used. Finally, we review visualization tools 
-aiming at detecting numerical instabilities over execution time.
+Several tools have been and continue to be developed to assess numerical quality. Those tools can be divided in two main categories depending whether they adopt a static or a dynamic approach.
+Static analysis produces theoretically-valid error bounds 
+while dynamic analysis is generally more scalable although it only provides experimental estimations.
+\pytracer adopts the dynamic approach, due to its scalability to large existing code bases.
+Dynamic approaches typically rely on the tracing of floating-point computations to detect instabilities and visualize them.
+The remainder of this section reviews existing approaches for each of these three steps.
+
+% In this section, we review tools and theoretical frameworks related to \pytracer components.
+% We start by reviewing state-of-the-art dynamic tools for detecting numerical instabilities.
+% Then, we focus on existing theoretical approaches for perturbations-based techniques to detect numerical instabilities,
+% \pytracer being agnostic to perturbation technique used. Finally, we review visualization tools 
+% aiming at detecting numerical instabilities over execution time.
 
 \label{sec:soa}
-\subsection{Numerical assessment tools}
+\subsection{Numerical tracing techniques}
 
-Several tools have been and continue to be developed to assess numerical quality.
-Those tools can be divided in two main categories: static VS dynamic analysis.
-Static analysis focuses on safety and soundness of error bounds provided 
-while dynamic analysis rather provides proof-less numerical quality estimations.
-The main drawback of static analysis tools is the poor scalability that confine them to small programs.
-Pytracer falls into the second category by targeting real Python use cases.
-In this section, we will hence review the most known tools based on dynamic analysis.
-We divide the tools in three sections starting by tools dedicated to non Python codes, then 
-tools using Dynamic Binary Instrumentation and finally tools dedicated to Python codes.
-
-Following the languages mainly used in HPC or embedded systems, 
-most the tools are dedicated to C, C++ or FORTRAN codes. 
-Those tools are either source-to-source or compiler based transformations.
-CADNA~\cite{jezequel2008cadna} is a library for C, C++ and Fortran codes implementing
-the CESTAC~\cite{vignes1993stochastic} method, a stochastic arithmetic used for detecting round-off
-errors by introducing numerical instabilities in floating-point computations.
-Verificarlo~\cite{verificarlo} is a compiler that instruments floating point operations
-to replace them by generic call to Verificarlo API, providing several backends implementations including one for 
-Monte Carlo Arithmetic (MCA) (cf.~\ref{sec:mca}), another stochastic arithmetic.
-Bao et al. ~\cite{bao2013fly} modifies gcc to track local floating-point error across execution.
-pLiner~\cite{guo2020pliner} is root cause analyzer based upon clang that detects floating point operations 
-responsible of result variability. 
-It uses source-to-source transformation at AST level to rewrite parts of code with higher precision and to compare the result with
-the original one. PFPSanatizer~\cite{chowdhary2021parallel} is a compiler that uses parallel shadow execution to detect numerical issues
-by using higher precision. 
+Many tools  are dedicated to the tracing of floating-point computations in C, C++ or FORTRAN programs due to the prevalence of these languages in High-Performance Computing (HPC). 
+The main tracing techniques are source-to-source and compiler based transformations.
+\tristan{Re-organize the following in two paragraphs, (1) source-to-source, (2) compiler-based.
+For each paragraph, define the technique in 1 sentence, then list the tools}
+CADNA~\cite{jezequel2008cadna} is a library for C, C++ and Fortran  implementing the
+CESTAC~\cite{vignes1993stochastic} stochastic arithmetic \tristan{is it source-to-source or compiler-based?}.
+Verificarlo~\cite{verificarlo} is a compiler that supports different types of arithmetic instrumentations, including
+Monte Carlo Arithmetic (MCA)~\cite{parker1997monte}.
+The work in ~\cite{bao2013fly} modified the GNU Compiler Collection (GCC) to track local floating-point errors across executions.
+pLiner~\cite{guo2020pliner} is a root cause analyzer based on the Clang compiler that detects floating-point operations
+responsible for result variability. 
+pLiner uses source-to-source transformation at the AST \tristan{expand acronym} level  to rewrite parts of code with higher precision.
+PFPSanitizer~\cite{chowdhary2020debugging,chowdhary2021parallel}, is a compiler that uses parallel shadow execution to detect numerical issues using higher precision.
 Shaman~\cite{demeure_phd} is a C++ library that uses a first-order error model to propagate numerical error. 
 FLiT~\cite{sawaya2017flit} is framework to detect variability induced by compilers and their optimizations.
-Tang et al.~\cite{tang2016software} propose a source-to-source framework for executing targeted code 
+The work in~\cite{tang2016software} proposed a source-to-source framework for executing targeted code 
 in infinite and fixed precision with and without using stochastic arithmetic.
+The work in~\cite{wang2012development} proposes a numerical debugger based on GDB~\cite{stallman1988debugging} for 
+Discrete Stochastic Arithmetic (DSA) on FPGA as an Eclipse plugging. Similarly, Cadtrace~\cite{jezequel2008cadna}
+and Shaman propose a GDB based tool to respectively use the CADNA and Shaman libraries with GDB.
 
-The main other existing approach uses Dynamic Binary Instrumentation (DBI) to perform analysis at the binary level,
-removing the language barrier and allowing to analyze any binary without needing the source code. This approach
-is particularly relevant on closed-source software. However, working at binary level loses high-level information useful
-for debugging and understanding the source code semantic and logic.
+Another technique, Dynamic Binary Instrumentation (DBI), evaluates numerical stability at the binary level,
+enabling the analysis of any binary regardless of the programming language. However, working at binary level makes it difficult to access high-level information needed
+for debugging and understanding the source code logic. In particular, analyzing Python code with DBI is feasible but provides very limited insights on the stability of specific Python code sections.
 CraftHPC~\cite{lam2013dynamic} uses DBI to detect catastrophic cancellations at runtime.
@@
 MPFR library~\cite{fousse2007mpfr}. It is combined with symbolic computation to backtrack the root of the error.
+We can note that all methods based on a high-precision oracle suppose that computing with
+a large number of bits is sufficient to obtain an accurate result, which is not always true, see for example the famous Muller's sequence ~\cite{chatelain2018veritracer}.
 
+To the best of our knowledge, there is currently no tool dedicated to numerical analysis of Python code.
 Existing tools for tracing Python code are dedicated to performance profiling, for time (cProfile)
 or memory consumption (memprofile). 
-To the best of our knowledge, there is currently no tool dedicated to numerical analysis.
-We can nevertheless mention Anteater~\cite{faust2019anteater} a Python tracer tool that aims at debugging Python application. 
+Anteater~\cite{faust2019anteater} is a Python tracer tool that aims at debugging Python application. 
 It operates source transformation at AST level but only deals with native numeric Python types.
-However, we can compare the methodology used by these tools against the one used in Pytracer.
+Moreover, the user needs to manually tag each variable to trace. Finally, according to the authors,
+Anteater do not scale to large traces.
+However, we can compare the methodology used by these tools \tristan{are you referring to Anteater here?
+if so, it should be "this" tool.
+Otherwise, list which tools you're referring to.} against the one used in Pytracer.
 These tools use an instrumentation based on decorators, a Python mechanism allowing 
-to wrap a function by adding a line over a function declaration.
+to instrument a function by adding a line over a function declaration.
 While this method is useful when targeting specific functions, it becomes time consuming 
-when applied to a large number of functions since one need to tag functions by hand,
-which clearly not tractable for large codes like numpy. Moreover, the user has most of the time no clues
-about where numerical instability comes from and must therefore all functions as potentially suspect. 
-This issue enforces the need to use automatic approaches.
-It's worth mentioning that DBI based tools can be used for Python because they are language agnostic but
-they are not intended to analyze Python code and do not take into account high-level information about 
-types being used or detailed stack trace. Moreover, few tools embed a visualizer for 
-analyzing numerical quality over time letting the postprocessing to the user.
+when applied to a large number of functions since one needs to tag functions manually,
+which is not feasible for large code bases where potentially unstable code sections are not known.
 
-\tristan{The content of this section is excellent but the structure is a bit messy.
+% Moreover, the user has most of the time no clues
+% about where numerical instability comes from and must therefore all functions as potentially suspect. 
+% This issue enforces the need to use automatic approaches.
+%  Moreover, few tools embed a visualizer for 
+% analyzing numerical quality over time letting the postprocessing to the user.
+
+% \tristan{The content of this section is excellent but the structure is a bit messy.
 Would you like to restructure in 3 paragraphs as follows?
@@
 
-\subsection{Detecting instabilities}
+\label{sec:detecting-instabilities}
+\subsection{Detecting numerical instabilities}
 
-We review here the existing theoretical framework that might be used to detect numerical instabilities.
+Three main approaches exist to detect numerical instabilities once floating-point computations are traced: stochastic arithmetic, uncertainty or sensitivity analysis, and random seed analysis.
+The main techniques for each approach are reviewed below.
+
+% We review here the existing theoretical framework that might be used to detect numerical instabilities.
+% Our experiments rely on the Monte Carlo Arithmetic (MCA), a stochastic arithmetic allowing 
+% to detect numerical errors by adding random perturbations in the floating-point computations.
+% However, Pytracer do not rely on any assumption about the perturbation model used and thus leaves the user free to use
+% an alternative model. As such, we describe two others options that we thought might be beneficial and complementary to MCA: 
+% input data uncertainty analysis and random seed sensitivity.
 
 \label{sec:mca}
-\subsubsection{Monte Carlo Arithmetic}
-\tristan{Add a sentence to connect this part to the previous one.
-Something like: We use Monte-Carlo arithmetic to detect numerical instabilities.
-You could also summarize what the other options would be.} \tristan{cite \cite{parker1997monte}}
+\subsubsection{Stochastic Arithmetic}
 
-MCA simulates round-off errors by introducing random perturbations in floating point computations. Each floating point number is replaced by its MCA counterparts:
+% The Monte Carlo Arithmetic is a variant of so-called stochastic arithmetic, whose purpose is to model round-off errors by a random variable.
+
+Stochastic arithmetic is a theoretical model that exploits randomness to estimate the floating-point format's numerical instabilities.
+The idea is to treat round-off errors as a random variable for then using classical statistical tools to study them.
+
+The first published complete stochastic arithmetic framework is CESTAC~\cite{vignes1993stochastic}.
+Each floating-point computation is run multiple times in this method, switching the rounding mode to either round-up or round-down with
+an equal probability.
+From these stochastic samples, one can then derive the number of significant digits in the computed result.
+In addition, the Discrete Stochastic Arithmetic (DSA~\cite{vignes2004discrete}) extends the CESTAC method to comparison operators implemented in the CADNA library.
+
+The Monte Carlo Arithmetic works on the same principle but introduces two differences:
+a virtual precision parameter allowing to simulate reduced working precision and different \texttt{modes} to introduce perturbations
+on the inputs or the output.
+MCA simulates round-off errors by introducing random perturbations in floating-point computations and replaces each floating-point number with its stochastic counterpart:
 \[
@@
 where $\beta$ is the basis, $t$ the virtual precision and $\xi \in (-\frac{1}{2},\frac{1}{2})$ a random variable.
-Virtual precision is one strength of the MCA method since it allows simulating 
-reduced working precision.
-MCA comes with three modes: Random Rounding (RR), Precision Bounding (PB) and FullMCA where either the output, either the inputs or both are perturbed with the $inexact$ function.
-While the RR mode is equivalent to stochastic rounding, PB mode allows identifying 
-catastrophic cancellations.
+Virtual precision is one strength of the MCA method since it allows simulating reduced working precision.
+MCA comes with three modes: Random Rounding (RR), Precision Bounding (PB), and FullMCA, which perturb either the output, the inputs, or both with the $inexact$ function.
+While the RR mode is equivalent to stochastic rounding, PB mode allows identifying catastrophic cancellations.
 
-MCA provides a formula to compute the number of significant digits:
-\[
-s = -\log_{\beta}{ \left| \dfrac{\sigma}{\mu} \right|}
-\]
-where $\sigma$ and $\mu$ are respectively the empirical standard deviation and expected value of a variable $x$ evaluating several times with MCA. 
-Note that this formula gives an approximation of the real $s$ and 
-one can refer to~\cite{sohier2018confidence} to obtain associated rigorous confidence intervals.
+MCA provides a formula \tristan{is this formula specific to MCA or can it also be applied to CESTAC?} \Yohan{Yes, CESTAC supposes that the random variable is normal and so use a different formulation} to compute the number of significant digits:
+\begin{equation}
+s = -\log_{\beta}{ \left| \dfrac{\sigma}{\mu} \right|} \label{eq:sig-digits}
+\end{equation}
+where $\sigma$ and $\mu$ are respectively the empirical standard deviation and expected value of a variable $x$ evaluating 
+several times with MCA. 
+Note that this formula gives an approximation of the real. Recently, Sohier et al. ~\cite{sohier2018confidence} introduced a 
+general theoretical framework that includes DSA and MCA formulae and allows to obtain associated rigorous confidence intervals on the number of significant digits estimated.
+
+\subsubsection{Uncertainty and sensitivity analysis}
+
+Uncertainty analysis (UA) is a method to derive the output distribution response from an input distribution.
+The idea is to model uncertainty on data due to limited precision measurement for example by a probability distribution and 
+to estimate the impact on the result. 
+Sensitivity analysis (SA) is quite close to uncertainty analysis but differs from the scale observed.
+While uncertainty analysis attempts to describe the whole output distribution, sensitivity analysis 
+measure the local response to a small perturbation~\cite{loucks2017water}. 
+Several approaches for UA and SA exist among them differential analysis, response surface methodology, Monte Carlo analysis
+and variance decomposition (see~\cite{helton2006survey}). In particular, Monte Carlo Analysis is a sampling-based technique
+that samples inputs space to estimate output response.
+Monte Carlo analysis shares similarities with Monte Carlo Arithmetic.
+For instance, the PRECISE framework~\cite{chaitin1996lectures} shares with MCA the idea of varying virtual precision to estimate output sensitivity.
+
+\subsubsection{Random seed sensitivity}
+
+The quality of a Random Number Generator is a key characteristic when dealing with stochastic model and differ from cryptography requirements.
+For numerical simulation a RNG of quality must have a good tradeoff between performance, period, correlation or uniformity~\cite{james2020review}.
+Poor quality RNGs may have a substantial impact on results~\cite{click2011quality}. As a first step, measuring variation induced by seed is 
+a good indicator about the program stability that can be compared against variability induced by floating-point arithmetic.
+\Yohan{This section lacks of strong arguments. Needs improvement}
 
@@
 
-SHAMAN, CADNATrace;
-Veritracer~\cite{chatelain2018veritracer} is an extension of Verificarlo~\cite{verificarlo} that aims 
-at visualizing the numerical stability over time for C, C++ and Fortran codes.
+Visualization covers a wide range of specific domains in the numerical simulation area, from general purpose numerical visualization with tools
+like VTK~\cite{schroeder2000visualizing},
+to topological data analysis~\cite{tierny2018topological}, including matrix~\cite{wu2008matrix} or tensor~\cite{kindlmann2006diffusion} visualization.
+We review here tools dedicated to the analysis of the numerical variability induced by the floating-point model.
+We can first highlight the fact that despite the large number of existing tools dedicated to pinpoint 
+source code instructions, few of them allow the user to have a global view of the numerical accuracy of their computations
+or compare several executions of the same program under various perturbations.
+% Indeed, all methods based on an high-precision oracles cannot capture variability between several executions as they only refer 
+% to one oracle. In other words, the actual computation is compared against the same computation with higher-precision by 
+% using the same inputs data in a synchronous way.
 
-\section{PyTracer design}
+Veritracer~\cite{chatelain2018veritracer} was the first tool to propose an embedded visualizer to 
+visualize the numerical stability over time for C, C++ and Fortran codes.
+It is a trace-based tool built as an extension of Verificarlo~\cite{verificarlo} that offers contextual 
+information about variables traced to allow the user to quickly identify instabilities.
+However, it does not offer a dynamic interface neither takes into account information about 
+high-level structures like \texttt{struct} or \texttt{array}.
+FPAvizual~\cite{gu2014fpavisual} is a tool for visualizing effects of floating-point arithmetic but only for educational purposes.
+Anteater~\cite{faust2019anteater} proposes a visualizer for Python codes but as mentioned previously,
+it only deals with native Python types and the user needs to manually select variables to trace. 
+However, Anteater provides a real reflection around visual debugging beyond floating-point 
+analysis, which has inspired the design of \pytracer's visualization interface.
+
+\section{\pytracer design}
 
@@
 
-PyTracer follows a three step approach. First, selected functions are automatically
-instrumented before executing the targeted application. During the execution, instrumented
-functions will dump their inputs and outputs in a file called a trace. 
-The idea is to profile several times the application to measure discrepancies between runs.
-Based on the set of traces obtained from multiple executions, Pytracer 
-will gather them into one trace containing statistics about each traced variables.
-With all information gathered, the user can visualize and interact with it through a Ploty/Dash server.
+The PyTracer workflow follows a three step approach (Figure~\ref{fig:workflow}).
+When a Python application is loaded, \pytracer instruments it using ``monkey patching", a technique to modify Python programs without editing their source code.
+The instrumentation replaces all the functions with a wrapper that saves their arguments and outputs in a trace file using ``pickle", Python's object serialization mechanism.
+\pytracer then aggregates trace files obtained from multiple perturbed executions, computing summary statistics about each traced variable.
+Finally, a Plotly dashboard provides interactive visualizations highlighting unstable code sections.
+
+% \tristan{mention monkey patching}
 
@@
     \includegraphics[width=\linewidth]{figure/workflow.pdf}
-    \caption{Pytracer workflow \tristan{Excellent figure but fuzzy should appear}}
+    \caption{Pytracer workflow \tristan{move the execution and noise injection to step 2}}
     \label{fig:workflow}
@@
 
-\subsection{Instrumentation}
+\subsection{Python code instrumentation}
 
-Pytracer dynamically instruments the Python modules selected by the user
-without requiring modifications of the targeted application.
-To do so, Pytracer creates a new version of each selected module 
-by preserving the attributes' signature, allowing to use them
-transparently in the original application.
-If by default Pytracer instruments all attributes present
-in a given module, except the special attributes of the form \texttt{\_\_*\_\_},
-the wrapping is not always be feasible as detailed in section ?.
-The original attributes are then preserved and the user is warned.
-The user can also restrict the list of attributes to trace through
-a mechanism of inclusion/exclusion.
+%\tristan{``Instrumentation" should appear in Figure 1}
 
-The main advantage of this method is its transparency for the user
-since this latter only needs to select which modules to trace and Pytracer instrument them for him.
-Moreover, the code does not need to be changed contrary to the method based on decorators, allowing
-to use instrument functions when the source code is not available or editable, like for instance
-in singularity containers or when running on HPC cluster.
+\pytracer dynamically instruments Python modules
+without requiring source code modifications in the application.
+To do so, it creates a new, instrumented version of each module that preserves its original attributes so that the original application can transparently use it.
+By default, \pytracer instruments all the attributes
+in a given module \tristan{not only the functions?} \Yohan{No, you can have class definitions or instances that need to be wrapped}, except the special ones of the form \texttt{\_\_*\_\_}.
+However, some attributes are not writable; in this case, \pytracer preservers the original attributes and warns the user. The user can also restrict the list of attributes to trace through
+an inclusion/exclusion mechanism.
+The main advantage of this instrumentation approach is the lack of required modification in the application source code, in contrast with decorator-based approaches, which enable instrumentation in read-only environments such as Singularity containers or HPC clusters.
 
-\subsection{Module import interception}
+\subsubsection{Intercepting module import}
 
-Modules in Python are loaded through the import mechanism by the \texttt{import} keyword.
-During this process, Python is looking for module path file in the default system paths and those provided by
-the user (with \texttt{PYTHONPATH}). When the selected module is found, Python executes it for triggering 
-instructions in the \texttt{\_\_init\_\_.py} file and stores it in the \texttt{sys.modules} map,
-acting as a cache.
+Python loads modules through an import mechanism triggered by the \texttt{import} keyword, using two objects: \texttt{finders} and \texttt{loaders}.
+The \texttt{finder} is responsible for finding the package (or 
+namespace\footnote{Python makes a distinction between \texttt{regular} and \texttt{namespace} packages.
+A regular package is a directory that contains a \_\_init\_\_.py file and potentially subdirectories (sub-packages) 
+that contain themselves a \_\_init\_\_.py file and so on recursively. 
+The package hierarchy follows those of the directory. 
+Namespace packages introduced in Python 3.3 (\href{https://www.python.org/dev/peps/pep-0420/}{PEP 420}) do not contain an
+\_\_init\_\_.py file and allow for flexible directory structures.
+Hence, parts of the package can be located in zip files, on the network, or in separated directories.
+There are no functional differences between both types of packages.}) from its fully qualified name, whether it is located on the local storage, such as standard packages installed through the pip package manager, or on a distant server.
+\texttt{Finders} do not load the modules; they return a specification (\texttt{spec} object) encapsulating 
+information on where to find it and how to load it.
+The \texttt{loader} creates and initializes a module object, filling the import-related attributes 
+such as \texttt{\_\_spec\_\_}. 
+Then, the \texttt{loader} executes the module and populates its namespace. Finally, the module is bound to its import name in the \texttt{sys.modules} dictionary.
 
-Pytracer intercepts the module loaded by using the \texttt{Finder} and \texttt{Loader} mechanism.
-The Finder is responsible for finding the loader for a module that is being imported while the 
-Loader loads and initializes the module. We add a new Finder and Loader on top of the default ones
-to intercept imports and to wrap modules selected by the user. This mechanism allows returning 
-the original module in the wrapper code and returning the wrapped one in the targeted application
-without modifying the actual code.
+Python implements default \tristanmod{\texttt{importers}}{\texttt{finder} and \texttt{loader}} classes as well as search paths for importing a module, but it also provides a way to create custom \texttt{finder} and \texttt{loader} classes.
+To register a new \texttt{finder} class, one needs to add it to the \texttt{sys.meta\_path} list.
+When an \texttt{import} statement is encountered, Python first looks for a binding in the \texttt{sys.modules}
+and then iterates over \texttt{sys.meta\_path}.
+Python queries each \texttt{finder} class successively until it finds the module or it reaches the end of the list, raising a \texttt{ModuleNotFoundError}.
+\pytracer adds  a custom \texttt{finder} class at the head of the list that intercepts
+the module import and creates the module with a custom \texttt{loader} class.
 
-\subsubsection{Module functions}
+\pytracer's \texttt{loader} class first loads the original module, then copies it as a new instance of the \texttt{ModuleType} class.
+It then calls the appropriate instrumentation function for each module attribute depending on its type (function, class or submodule). Once all the attributes are instrumented, 
+\pytracer replaces the original module by its instrumented counterpart
+in the \texttt{sys.modules} map \tristan{is the non-instrumented version ever added to sys.modules?
+If so, could this lead to race conditions?
+If not, replace with ``adds the instrumented module to the sys.modules map"}.
+Hence, the calling convention remains unchanged and the application will transparently call
+the instrumented module.
 
-The module function is the simplest case to deal with.
-For each function encountered in a module, Pytracer
-creates a wrapper around this function that is dynamically compiled with the \textit{compile}
-builtin function. The original function is then replaced by its wrapped counterpart.
+% \pytracer intercepts the modules loaded with the \texttt{Finder} and \texttt{Loader} mechanisms \tristan{is it restrictive? Are there other mechanisms?}.
+% The Finder searches the loader of a module that is being imported while the 
+% Loader loads and initializes the module. \pytracer adds \tristan{overrides?} a new Finder and Loader on top of the default ones
+% to intercept imports and to instrument modules selected by the user. This mechanism allows returning 
+% the original module in the instrumentation code and returning the instrumented module in the targeted application
+% without modifying its actual code.
 
-However, this technique cannot be applied for all functions, especially for 
-callable instances, which are instances of class that can be called like traditional functions
-but that contain attributes. Indeed, using a wrapper would 1) modify the type of the instance
-that could cause semantic bugs 2) hide attributes that causes \texttt{AttributeError} exceptions.
+\subsubsection{Instrumenting module functions}
 
-\begin{figure}
+Module functions are the simplest case to deal with.
+For each function, \pytracer's \texttt{loader} class
+creates a wrapper function, dynamically compiles it with the \texttt{compile}
+builtin function, and substitutes it for the original module function.
+However, this technique cannot be applied to
+callable class instances, i.e., class instances that have the \texttt{\_\_call\_\_} attribute but are not of the \texttt{FunctionType} type.
+Indeed, applying the wrapper technique would 1) modify the type of the class instance to \texttt{FunctionType},
+which could cause semantic bugs, and 2) mask class attributes, leading to \texttt{AttributeError} exceptions.
+To overcome this issue, \pytracer overrides the \texttt{\_\_call\_\_} attribute with the wrapper function when 
+possible. When the \texttt{\_\_call\_\_} attribute is not writable,  
+the class is not instrumented and a warning is returned.
+Listings~\ref{fig:wrapper_creation} and ~\ref{fig:generic_wrapper} show \pytracer's wrapper creation function \tristan{add docstrings to all Python code examples and clarify captions accordingly: you don't need to explain the meaning of each attribute in the caption if it's in the docstring.
+The caption can focus on the main functionality, reusing the text currently in 3.1.5.}.
+
+%
+% we can employ a case by case strategy depending on the class (i.e. numpy ufunc) or simply ignore
+% the instrumentation and let the original one.
+% \tristan{add a sentence to explain how callable instances are instrumented}
+
+\begin{listing}
     \centering
 \begin{lstlisting}[language=Python,style=customPython]
-def getwrapperfunction(function_module, function_name, function, function_wrapper_name):
-    function_wrapper_name = f
+def get_wrapper_function(function_module, function_qualified_name, function, function_wrapper_name):
     function_id = id(function)
-    info = (function_id, function_module, function_name)
+    info = (function_id, function_module, function_qualified_name)
     wrapper_code = f"""
@@
 \end{lstlisting}
-    \caption{Caption}
-    \label{fig:wrapper_code}
-\end{figure}
+    \caption{Function to create the instrumented version of a function. 
+    This function returns the instrumented function as a string (\texttt{wrapper\_code}) that 
+    will be turned into a Python object with the \texttt{compile} built-in function.}
+    \label{fig:wrapper_creation}
+\end{listing}
 
-\subsubsection{Classes}
+\begin{listing}
+    \centering
+\begin{lstlisting}[language=Python,style=customPython,]
+def generic_wrapper(self, info, *args, **kwargs):
+    fid, fmodule, fname = info
+    function = original_function_cache.id_dict[fid]
+    bind = Binding(function, *args, **kwargs)
+    stack = self.backtrace()
+    time = elements()
+    self.inputs(time=time,
+                module_name=fmodule,
+                function_name=fname,
+                function=function,
+                args=bind.arguments,
+                backtrace=stack)
+    outputs = function(*bind.args, **bind.kwargs)
+    self.outputs(time=time,
+                 module_name=fmodule,
+                 function_name=fname,
+                 function=function,
+                 args=outputs,
+                 backtrace=stack)
+    return outputs
+\end{lstlisting}
+    \caption{\pytracer's wrapper function. 
+    The \texttt{original\_function\_cache} maintains a mapping between the original function and its identifier (available through 
+    \texttt{id} built-in function). Once the original function retrieved, the arguments are saved to the traces (through function 
+    \texttt{self.inputs}). The actual function is called and the result is saved (function \texttt{self.outputs}) then returned.
+    }
+    \label{fig:generic_wrapper}
+\end{listing}
 
-Overriding Python classes is similar to module functions.
-Pytracer goes through the attributes and replaces each callable attribute (method) by its wrapped counterpart.
-The resulting class has the same type as the original one, avoiding type conflicts.
-However, some classes forbid overwriting attributes of their instances, in particular the `\_\_call\_\_` operator
-allowing to call an instance as a function.
-Moreover, no general solution can be provided since some Python classes are non-inheritable 
-like \texttt{bool},\texttt{NoneType} or \textit{universal functions} in numpy (\texttt{ufunc})
-and thus cannot be inherited to overload operators.
-The solution consisting in replacing function by a wrapper cannot be applied here.
+\subsubsection{Instrumenting classes}
 
-This issue was mostly encountered with numpy ufunc that are intensively used in numpy. Universal functions are vectorized element-wise operators on
-multidimensional arrays (\texttt{ndarrays}). They are implemented in C code with target specialized versions to achieve best performance.
-One should then implement subclassing mechanism in C, which is contrary to Pytracer philosophy to be as non-intrusive and portable as possible.
-However, since \texttt{ufunc} are intensively used in scientific computational codes (elementary mathematical functions are ufunc in numpy),
-we implement a special treatment for them. Numpy provides the \texttt{frompyfunc} helper function to create \texttt{ufunc} from arbitrary function.
-The main problem with this approach is that the output type is \texttt{PyObject} representing abstract object that conflicts 
-when used as index. Figure illustrates this issue. As a last resort, user may disable \texttt{ufunc} tracing by Pytracer.
+\pytracer instruments classes by wrapping their callable attributes as described previously. 
+This instrumentation preserves class types, avoiding type mismatches in the instrumented application.
+However, some classes, in particular base types, contain read-only attributes that cannot be instrumented.
+By default, \pytracer returns a warning when it encounters such classes, but it treats NumPy's universal functions (\texttt{ufuncs}) specifically since they are ubiquitous in scientific computing.
+NumPy's \texttt{ufuncs} are vectorized element-wise operators that apply to multidimensional arrays.
+In particular, all the element-wise elementary mathematical functions are \texttt{ufuncs}.
+To increase performance, \texttt{ufuncs} are implemented in C which prevents their instrumentation using the technique described previously.
+Instead, \pytracer uses
+NumPy's \texttt{frompyfunc} helper function to create an instrumented \texttt{ufunc} that wraps the original one.
+This approach works in many cases but it requires the instrumented function to return objects of type \texttt{PyObject}, which may create errors (Listing~\ref{fig:numpy_array_index_issue}). 
+As a last resort, the user may disable \texttt{ufunc} tracing in Pytracer.
 
-\begin{figure*}
+\subsubsection{Instrumenting iterators}
+
+In functional programming, iterators traverse containers lazily, meaning that the next element in the sequence is only computed when it is used by the application.
+This allows for the manipulation of virtually infinite sequences within finite memory.
+However, it implies that there is no full mapping of the container returned by an iterator in memory since each element is computed on the fly.
+Therefore, iterators are not serializable and \pytracer cannot save them to output traces.
+A workaround would be to convert iterators into explicit containers, and then return a new iterator on the explicit container.
+However, this would increase the memory footprint, possibly very importantly, and \pytracer therefore does not instrument iterators.
+
+\subsubsection{Instrumented code}
+\tristan{this text should be in 3.1.2. Given that it's quite specific to the code shown in the Listings, I think it could be part of the listing captions. }
+Listing~\ref{fig:wrapper_creation} shows how functions are instrumented.
+This function takes as inputs the information about the function to instrument (module name and full qualified name),
+the function itself and the actual name of the function. It then creates a wrapper around the actual wrapper
+(\texttt{generic\_wrapper}) that will dump the values. Instead of passing the function, we pass the identifier of 
+the function, which an unique 64-bits integer that references each Python object. This identifier is available
+with the \texttt{id} builtin function. it allows to get rid of aliases and to avoid instrumenting functions twice.
+
+Listing~\ref{fig:generic_wrapper} shows what the instrumented code does. 
+It first unpack function's information to get function's identifier to retrieve the original function.
+Then arguments are bound by creating a mapping from positional and keyword arguments to parameters, avoiding 
+conflicts and mispositioning. It also allows to get names of arguments for the visualization.
+Once arguments bound, they are dumped in the pickle file through the help of the \texttt{inputs} function.
+The function is then called with the right arguments and its returned valued dumped.
+Finally, the result of the original function is returned.
+
+\begin{listing}
 \begin{minipage}[t]{0.4\linewidth}
@@
     \end{lstlisting}
-    \label{fig:wrapper_code}
 \end{minipage}
@@
     \end{lstlisting}
-    \label{fig:wrapper_code}
 \end{minipage}
-\caption{Illustration of the issue of using \texttt{frompyfunc} function to convert function to \texttt{ufunc}.}
-\end{figure*}
+\caption{Illustration of the issue of using \texttt{frompyfunc} function to convert function to \texttt{ufunc}.
+Left: original code.
+Right: instrumented code.
+\tristan{This needs more explanation: where is the ufunc, what is the type returned by the original ufunc, and why does it crash in the instrumented version.}}
+    \label{fig:numpy_array_index_issue}
+\end{listing}
 
-\subsection{Detecting instabilities}
+\subsection{Detecting numerical instabilities}
 
-\subsubsection{Fuzzy environment}
+\pytracer detects numerical instabilities by computing summary statistics across multiple application executions perturbed with numerical noise.
+While \pytracer's instrumentation, trace aggregation and visualization are applicable to various types of numerical noise, we experimented primarily with Monte-Carlo Arithmetic (MCA) as it is the most accurate model for floating-point errors.
 
-We use the fuzzy~\cite{kiar2020comparing} environment to use MCA in Python.
-The fuzzy ecosystem provides a Python interpreter recompiled with Verificarlo.
-Verificarlo~\cite{verificarlo} is a compiler based upon clang~\cite{lattner2008llvm}
-that replaces all floating-point operations by a generic call. 
-The user can then link these generic calls with different floating-point models 
-(called backends) during the execution. Verificarlo proposes several 
-backends~\cite{chatelain2019automatic,chatelain2019outils} including for MCA.
+\subsubsection{Noise injection}
+\label{sec:fuzzy}
 
-The main advantage of the fuzzy ecosystem is its transparency for the user.
-One can directly use its python code with the fuzzy python interpreter
-without manual interventions. Moreover, the fuzzy ecosystem is intended to be
-modular by providing fuzzy version of numpy, scipy and scikit-learn modules.
-One can thus choose the fuzzy stack desired.
+We enable MCA in Python programs via Verificarlo~\cite{verificarlo}, a clang-based compiler~\cite{lattner2008llvm}
+that replaces floating-point operations by a generic call to
+a configurable floating-point model. Several floating-point models, also called
+backends, are available~\cite{chatelain2019automatic,chatelain2019outils}.
+We leverage the fuzzy~\cite{kiar2020comparing} environment, a collection of software tools recompiled with Verificarlo.
+In particular, fuzzy provides MCA-instrumented versions of the Python interpreter as well as BLAS, LAPACK, NumPy, SciPy and scikit-learn,
+which allows for the injection of MCA perturbations to a wide range of existing scientific Python programs.
+Fuzzy is available in Verificarlo's GitHub organization at \href{https://github.com/verificarlo/fuzzy}{\url{github.com/verificarlo/fuzzy}}
+and provides Docker images for each MCA-enabled tools.
 
-\subsection{Interactively visualization}
+% As the time of writing this article, fuzzy provides 5 levels of instrumentation (each level N including the lower levels):
+% \begin{enumerate}
+%     \item BLAS + LAPACK
+%     \item Python interpreter
+%     \item Numpy
+%     \item SciPy
+%     \item Scikit-learn
+% \end{enumerate}
 
-\subsubsection{Plotly}
+\subsubsection{Trace format}
+
+\pytracer stores traces in the pickle format, a compressed binary Python format to serialize Python objects.
+The main advantages of the pickle format compared to other serialization approaches such as marshal or JSON are its ability to serialize most Python objects, and its native compression.
+In addition, pickle writes Python objects sequentially according to their serialization order, which preserves the temporal ordering required by subsequent trace analyses.
+
+Traces record numerical values at the granularity of a function.
+When the application invokes a function, \pytracer saves a call input object containing contextual information (function's name, module's function, stacktrace) and the values of the function arguments.
+When the function returns, \pytracer saves a similar call output object containing the returned value.
+
+\subsubsection{Trace aggregation}
+
+Once traces are available, \pytracer sequentially parses them and computes the mean, standard deviation and
+number of significant digits (using Equation~\ref{eq:sig-digits}) of all saved values. These summary statistics are saved in an HDF5 file,
+a hierarchical format that facilitates browsing during the visualization.
+This operation critically relies on the ordering of call input and output objects in the traces.
+It assumes that the application is deterministic, and in particular that it is single threaded and that the control flow does not depend on a random state.
+Techniques to overcome this limitation are discussed in the discussion section.
 
@@
     \centering
-    \includegraphics[width=\linewidth]{figure/pytracer_layout.pdf}
+    \includegraphics[width=\textwidth]{figure/pytracer_layout.pdf}
     \caption{Pytracer visualization layout.}
-    \label{fig:my_label}
+    \label{fig:visu-layout}
 \end{figure}
 
-\section{Use cases}
+To aggregate traces, \pytracer successively unpickles call objects in each trace, checks
+that the call objects refer to the same function and stacktrace, and terminates the parsing otherwise.
+For each matching call object, \pytracer stores function arguments or returned values in a NumPy array from which statistics are computed. 
+For compound objects such as tuples, dictionaries, or objects, it recursively parses the fields until finding
+numeric types or NumPy arrays of numeric types.
+
+\subsection{Interactive visualization}
+
+The third main component of \pytracer is its interactive trace visualizer built with Plotly Dash~\cite{plotly}, a Python framework for web visualization.
+Plotly Dash abstracts the low-level details of web applications in a highly customizable development interface allowing to offload heavy computations to a server. 
+\subsubsection{General layout}
+Figure~\ref{fig:visu-layout} presents the general layout of the \pytracer visualizer, divided into 5 sub-components:
+\begin{enumerate}
+ \item Timeline view: This view displays the values of each inputs and outputs for a given function at a given
+    invocation. By default, \pytracer shows the number of significant digits computed across the traces but the user 
+    can switch to the mean or the standard deviation. To differentiate inputs from outputs, the visualizer
+    uses an upper triangle for inputs and a down triangle for outputs. \pytracer represents internally all values 
+    as NumPy arrays.
+    In the case of non-scalar values or types that 
+    cannot be trivially cast into NumPy arrays, \pytracer splits the value in several variables. Hence, a class containing
+    $n$ floating point parameters will be transformed into $n$ variables. Each variable is prefixed with the original value
+    and postfixed with the name of the parameter. 
+    Finally, for non-scalar values (vectors or matrices), \pytracer shows the average of elements for non-scalar value (like vectors or matrices).
+Non-scalar values can be inspected with the Zoom view (see below).
+ \item Gantt chart view: This view displays the call graph as a Gantt chart representing the instrumented functions. Each function call
+    is represented with a bar starting and ending at the function call and return.
+    The caller/callee relation is then determined by looking at the time overlaps.
+    For example, in the figure, \texttt{function1} calls \texttt{function2} that itself calls \texttt{function4} and \texttt{function5}. 
+    This view provides insights on the calling context for each function since the same function can be called from different 
+    parents, which may influence numerical stability. 
+ \item  Source code view: This view displays the source code file of the variable hovered in the timeline view. 
+ \item  Zoom view: This view allows to closely examine non-scalar values, which is useful to see local differences that might
+    be masked by the averaging done in the timeline view. For example, a matrix can have instabilities around its diagonal but not in other regions.
+    The visualizer also provides metrics about the value, such as the array shape, infinite norm, or condition number.
+\item  Functions list view: This view allows the user to select the functions to plot in the timeline view.
+\end{enumerate}
+
+\section{Numerical evaluations}
+
+We evaluated \pytracer on widely-used Python libraries, namely SciPy, scikit-learn, and PyAFQ, demonstrating its its scalability and usability for real-world Python programs.
+For SciPy and Scikit-learn, we traced each application 5 times \tristanmod{by using the level 5 of the fuzzy ecosystem (cf.
+section~\ref{sec:fuzzy})}{ having activated MCA in the Python interpreter, BLAS, LAPACK, [CHECK THIS LIST]}.
+We repeated the experiment with two MCA modes, Random Rounding (RR) and Full MCA, and having enabled or disabled the instrumentation of NumPy's universal functions (\texttt{ufuncs}),
+resulting in 4 experiments for each application.
+We used the default virtual precision in Verificarlo, namely 24 bits for single-precision floating point values and 53 bits for double-precision values, which simulate machine error.
+For each library, we executed the software tests provided in the GitHub repositories \tristan{add a sentence for each library to summarize what they contain}.
+
+\subsection{Results overview}
+
+Tables~\ref{tab:pytracer_scipy_results_summary} and~\ref{tab:pytracer_sklearn_results_summary} summarize 
+the outcome of \pytracer experiments on SciPy and Scikit-learn.
+Each table reports on the tracing and trace aggregation steps with three possible outcomes: green for success, red for numerical error in the application, and orange for errors in the fuzzy noise injection or due to the instrumentation of NumPy \texttt{ufuncs}.
+Overall, the tracing and parsing of SciPy and scikit-learn tests in Random Rounding mode and without \texttt{ufunc} instrumentation was entirely successful (tracing and parsing steps) for 31/40 tests.
+The remaining tests failed due to numerical errors in the libraries, which we discuss hereafter.
+The instrumentation with Full MCA is more invasive and reduced the number of successful executions without \texttt{ufunc} instrumentation to 11/40.
+The instrumentation of \texttt{ufuncs} also reduced the success rate substantially, to 17/40 in Random Rounding mode and to 8/40 in Full MCA.
+
+\begin{table}[]
+    \centering
+    \begin{tabular}{|ll|c|c|c|c||c|c|c|c|}
+    \hline
+    \multicolumn{2}{|c}{ \multirow{3}{*}{Application} } & \multicolumn{4}{|c||}{Random Rounding (RR)} & \multicolumn{4}{c|}{Full MCA} \\\cline{3-10}
+         &   & \multicolumn{2}{c|}{\texttt{ufunc}} & \multicolumn{2}{c||}{no \texttt{ufunc}} & \multicolumn{2}{c|}{\texttt{ufunc}} & \multicolumn{2}{c|}{no \texttt{ufunc}} \\\cline{3-10}
+    & & trace & parse &  trace & parse & trace & parse & trace & parse \\
+    \hline
+    %        &               RR                 &                 MCA               \\
+    %        &  numpy         &   no numpy      &      numpy      &     no numpy    \\
+    %        & run   & parse  &  run   &  parse &  run   & parse  & run    & parse  \\
+
+    \multicolumn{1}{|c|}{ \multirow{3}{2em}{ \rotatebox{90}{FFT} } }
+    & discrete\_cosine\_transform & \valid & \valid & \valid & \valid & \valid & \valid & \warn & \cross \\ 
+    \multicolumn{1}{|c|}{} & fft\_1D & \warn & \valid & \valid & \valid & \warn & \cross & \warn & \cross \\
+    \multicolumn{1}{|c|}{} & fft\_2D & \valid & \valid & \valid & \valid & \valid & \valid & \valid & \valid \\
+    \hline 
+    \multicolumn{1}{|c|}{  \multirow{5}{2em}{ \rotatebox{90}{Interpolation} } }
+    & interpolation\_1D & \valid & \valid & \valid & \valid & \valid & \cross & \warn & \cross  \\
+    \multicolumn{1}{|c|}{} & multivariate\_data & \valid & \valid & \valid & \valid & \valid & \cross & \warn & \cross \\
+     \multicolumn{1}{|c|}{} & bspline & \valid & \valid & \valid & \valid & \valid & \valid & \valid & \valid \\
+     \multicolumn{1}{|c|}{} & spline\_1D & \warn & \valid & \valid & \cross & \warn & \cross & \warn & \cross \\
+     \multicolumn{1}{|c|}{} & spline\_2D & \warn & \valid & \valid & \valid & \warn & \cross & \warn & \cross \\
+    \hline
+     \multicolumn{1}{|c|}{ \multirow{12}{2em}{ \rotatebox{90}{Optimization} } }
+    & broyden\_fletcher\_goldfarb\_shanno & \valid & \valid & \valid & \valid & \valid & \valid & \valid & \valid \\
+     \multicolumn{1}{|c|}{} & global\_optimization & \warn & \valid & \warn & \valid & \warn & \cross & \cross & \cross \\
+    \multicolumn{1}{|c|}{}  & slsqp & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \cross \\
+     \multicolumn{1}{|c|}{} & least\_square\_minimization & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \valid \\
+     \multicolumn{1}{|c|}{} & nelder\_mead\_simplex & \valid & \valid & \valid & \valid & \valid & \valid & \valid & \valid \\
+     \multicolumn{1}{|c|}{} & newton\_conjugate\_gradient & \valid & \cross & \valid & \cross & \valid & \cross & \valid & \cross \\
+     \multicolumn{1}{|c|}{} & root\_finding\_large\_preconditionned & \valid & \cross & \valid & \cross & \warn & \cross & \valid & \cross \\
+    \multicolumn{1}{|c|}{}  & root\_finding\_large & \warn & \valid & \valid & \cross & \valid & \cross & \valid & \cross \\
+     \multicolumn{1}{|c|}{} & root\_findings & \warn & \valid & \valid & \valid & \warn & \valid & \warn & \cross \\
+    \multicolumn{1}{|c|}{}  & trust\_region\_exact & \valid & \valid & \valid & \valid & \valid & \valid & \valid & \valid \\
+     \multicolumn{1}{|c|}{} & trust\_region\_truncated\_generalized\_lanczos & \valid & \valid & \valid & \valid & \valid & \valid & \valid & \valid \\
+    \multicolumn{1}{|c|}{}  & trust\_region\_newton\_conjugate\_gradient & \valid & \valid & \valid & \valid & \valid & \valid & \valid & \valid \\
+    \hline
+    \end{tabular}
+    \caption{\pytracer execution summary on SciPy tests.\\RR: Random Rounding.
+\texttt{ufunc}: instrumentation of NumPy \texttt{ufuncs}.
+trace: outcome of \pytracer tracing, parse: outcome of \pytracer trace parsing and aggregation.
+\valid: successful run, \warn: error in fuzzy noise injection or due to the instrumentation of NumPy \texttt{ufuncs}, \cross: numerical error.}
+    \label{tab:pytracer_scipy_results_summary}
+\end{table}
+
+\begin{table}[]
+    \centering
+    \begin{tabular}{|c|c|c|c|c||c|c|c|c|}
+    \hline
+    \multirow{3}{5em}{Application} & \multicolumn{4}{|c||}{Random Rounding (RR)} & \multicolumn{4}{|c|}{Full MCA} \\\cline{2-9}
+                & \multicolumn{2}{|c|}{\texttt{ufunc}} &  \multicolumn{2}{|c||}{no \texttt{ufunc}} & \multicolumn{2}{|c|}{\texttt{ufunc}} & \multicolumn{2}{|c|}{no \texttt{ufunc}} \\\cline{2-9}
+                & trace & parse &  trace & parse & trace & parse & trace & parse \\
+    \hline
+    %        &               RR                 &                 MCA               \\
+    %        &  numpy         &   no numpy      &      numpy      &     no numpy    \\
+    %        & run   & parse  &  run   &  parse &  run   & parse  & run    & parse  \\
+    Adaboost & \warn & \valid & \valid & \valid & \warn & \cross & \cross & \cross \\
+    Bayesian Ridge Regression & \warn & \valid & \valid & \valid & \cross & \cross & \cross & \cross \\
+    Online classifier comparison & \valid & \valid & \valid & \valid & \cross & \cross & \cross & \cross  \\
+    Cluster Iris & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
+    Covariance estimation & \valid & \cross & \valid & \cross & \cross & \cross & \valid & \cross \\
+    Decision Tree Regression & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
+    Digits Classification & \warn & \valid & \valid & \valid & \warn & \cross & \cross & \cross \\
+    Face Recognition & \cross & \valid & \cross & \valid & \cross & \cross & \cross & \cross \\
+    L1 Penalty & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \valid \\
+    Lasso and elastic net & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \cross \\
+    Separating hyperplan & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
+    MNIST classification & \warn & \valid & \valid & \valid & \valid & \cross & \valid & \valid \\
+    Multitask Lasso & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \valid \\
+    Orthogonal matching & \warn & \valid & \valid & \valid & \cross & \valid & \cross & \valid \\
+    PCA decomposition & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \cross \\
+    Robust Linear Regression & \valid & \valid & \valid & \valid & \warn & \cross & \valid & \cross \\
+    Segmentation toy & \warn & \valid & \valid & \cross & \warn & \cross & \cross & \cross \\
+    SVM & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
+    Tomography & \warn & \valid & \valid & \cross & \warn & \cross & \cross & \cross \\
+    Weighted samples & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
+    \hline
+    \end{tabular}
+    \caption{\pytracer execution summary on Scikit-learn tests.
+\\RR: Random Rounding.
+\texttt{ufunc}: instrumentation of NumPy \texttt{ufuncs}.
+trace: outcome of \pytracer tracing, parse: outcome of \pytracer trace parsing and aggregation.
+\valid: successful run, \warn: error in fuzzy noise injection or due to the instrumentation of NumPy \texttt{ufuncs}, \cross: numerical error.}
+    \label{tab:pytracer_sklearn_results_summary}
+\end{table}
+
+\subsubsection{Effect of MCA modes}
+\label{sec:impact_mca_modes}
+
+Random Rounding perturbs only on the result of a floating-point operation while 
+Full MCA mode perturbs both the inputs and the result or the operation. 
+Therefore, full MCA mode may trigger catastrophic cancellations while Random Rounding only introduces round-off errors which generally have a lesser impact.
+\Yohan{It is a strong assertion and I do not have literature to support it.
+Should be more precautionary.
+Even if, I believe, it's true.} \tristan{See how I reworded it.} Moreover, Random Rounding preserves exact operations,
+i.e., operations where the result can be exactly represented on the virtual precision, while Full MCA does not.
+
+\pytracer can only aggregate traces obtained from the same control flow path.
+In particular program branches triggered by an unstable floating-point comparison 
+lead to different control flows and result in parsing errors. 
+For example, comparing a residual error to a strict threshold in an iterative scheme or comparing the distance between two points generally results in unstable branches. 
+With Full MCA, even exact values such as integers represented with floating-point values are perturbed, which leads to a number of execution failures.
+For instance,  the \texttt{fft1} test from SciPy raised an \texttt{ValueError: operands could not be broadcast together with shapes (601,) (600,)} error due to an array shape mismatch.
+A closer inspection showed that one of the arrays involved in the error is created with the NumPy function \texttt{linspace} \tristan{I removed the linspace code, I think the most interesting part is what's going on in arange.
+Feel free to add it back if it's really necessary.} that itself calls function
+\texttt{arange} (Listing~\ref{fig:pyarray_range_code}).
+As can be seen in lines  3174-3178, the array size is stored in a floating-point value which will therefore be perturbed in Full MCA mode, as shown in Table~\ref{tab:mca_result_linspace}, resulting in array sizes that fluctuate
+between N and N+1. 
+It is worth noting that 78\% of execution issues encountered in Full MCA mode without \texttt{ufunc} instrumentation
+are due to this type of ``typing" errors.
+While they do not lead to any numerical issue, such typing errors should still be fixed to preserve code quality \tristan{Check this last sentence, we need to provide some sort of recommendations}.
+\tristan{how about opening a PR in numpy to fix this error?}
+
+% \begin{figure}
+%     \begin{lstlisting}[language=Python,style=customPython,numbers=left, firstnumber=11]
+% # Number of sample points
+% N = 600
+% # sample spacing
+% T = 1.0 / 800.0
+% x = np.linspace(0.0, N*T, N, endpoint=False)
+% y = np.sin(50.0 * 2.0*np.pi*x) + 0.5*np.sin(80.0 * 2.0*np.pi*x)
+% yf = fft(y)
+% w = blackman(N)
+% ywf = fft(y*w)
+%     \end{lstlisting}
+%     \label{fig:fft1_code}
+% \caption{Code snippet from \texttt{fft\_1D} illustrating issue arising when using Full MCA mode.
+% Line 19 raises \texttt{ValueError: operands could not be broadcast together with shapes (601,) (600,)} since
+% arrays \texttt{y} and \texttt{w} do not have the same shape. This is due to random errors introduces by 
+% Full MCA mode in the \texttt{linspace} function.
+% }
+% \end{figure}
+
+% \begin{figure}
+%     \begin{lstlisting}[language=Python,style=customPython,numbers=left, firstnumber=1, mathescape=true]
+% def linspace(start, stop, num=50, endpoint=True, retstep=False, dtype=None,
+%              axis=0):
+%     num = operator.index(num) // 3 $\lstsetnumber{\ldots}$
+%     ...$\lstresetnumber\setcounter{lstnumber}{5}$
+%     div = (num - 1) if endpoint else num // 6  $\lstsetnumber{\ldots}$
+%     ...$\lstresetnumber\setcounter{lstnumber}{13}$
+%     delta = stop - start // 14
+%     y = _nx.arange(0, num, dtype=dt).reshape((-1,) + (1,) * ndim(delta)) // 15
+%     \end{lstlisting}
+%     \label{fig:linspace_code}
+% \caption{Code snippet from \texttt{linspace} function from numpy package. 
+%     It uses the \textit{arange} function implemented as a Cython function (fig.~\ref{fig:pyarray_range_code}) to create the array. 
+% }
+% \end{figure}
+
+\begin{listing}
+    \begin{lstlisting}[language=C,style=customC,numbers=left, firstnumber=3163, mathescape=true]
+/*NUMPY_API
+  Arange,
+*/
+NPY_NO_EXPORT PyObject *
+PyArray_Arange(double start, double stop, double step /* default 1 */, int type_num) 
+{
+    npy_intp length; 
+    PyArrayObject *range; $\lstsetnumber{\ldots}$
+    ...$\lstresetnumber\setcounter{lstnumber}{3173}$
+    double delta, tmp_len; $\lstsetnumber{\ldots}$
+    ...$\lstresetnumber\setcounter{lstnumber}{3176}$
+    delta = stop - start; 
+    tmp_len = delta/step; $\lstsetnumber{\ldots}$
+    ...$\lstresetnumber\setcounter{lstnumber}{3189}$
+        length = _arange_safe_ceil_to_intp(tmp_len); $\lstsetnumber{\ldots}$
+    ...$\lstresetnumber\setcounter{lstnumber}{3201}$
+    range = (PyArrayObject *)PyArray_New(&PyArray_Type, 1, &length, type_num, $\lstsetnumber{}$
+                        NULL, NULL, 0, 0, NULL);
+    \end{lstlisting}
+\caption{Source code of the \texttt{PyArray\_Range} Cython function called by NumPy function \texttt{linspace} to create an array of equally spaced elements.
+The temporary array size assigned in line 3178 is stored as a floating-point value and is therefore perturbed in Full MCA mode, leading to differences amplified by the use of ceil rounding at line 3190 and resulting in different array sizes across MCA-perturbed executions.
+See also Table~\ref{tab:mca_result_linspace}.}
+    \label{fig:pyarray_range_code}
+
+\end{listing}
+
+\begin{table}[]
+    \centering
+    \footnotesize
+    \begin{tabularx}{{\textwidth}}{cccc>{\centering\arraybackslash}X>{\centering\arraybackslash}X>{\centering\arraybackslash}X}
+                \thickhline
+    \textbf{Mode}  & \textbf{start} & \textbf{stop} & \textbf{step} & \textbf{delta} & \textbf{tmp\_len} & \textbf{ceil(tmp\_len)}  \\
+    \hline
+    Exact & 0 & 600  & 1 & 600                             & 600                            & 600             \\
+    RR    & 0 & 600  & 1 & 600 $\pm$ 0.0                   & 600 $\pm$ 0.0                  & 600 $\pm$ 0.0   \\
+    MCA    & 0 & 600  & 1 & 599.9999999999999 $\pm$ 8e-14  & 600.0 $\pm$ 8e-14 &  600.01 $\pm$ 0.0995\\
+            \thickhline
+
+    \end{tabularx}
+    \caption{Results obtained through lines 3177-3190 in Listing~\ref{fig:pyarray_range_code}.
+Contrary to RR mode, Full MCA mode does not preserve exact operations which leads to an array length oscillating between 600 and 601.}
+    \label{tab:mca_result_linspace}
+\end{table}
+
+\subsubsection{Overall numerical quality}
 
 \subsection{SciPy}
+\label{sec:scipy_tests}
 
-We tested Pytracer on SciPy~\cite{virtanen2020scipy} examples provided in the Tutorial website section.
+We tested Pytracer on SciPy~\cite{virtanen2020scipy} examples provided in the tutorial website section.
 SciPy is organized in several libraries targeting specific computing domains.
@@
 \begin{itemize}
-    \item \texttt{fftpack}: Fast Fourier Transform routines
-    \item \texttt{interpolate}: Interpolation and smoothing splines
-    \item \texttt{optimize}: Optimization and root-finding routines
-    \item \texttt{integration}: Integration and ordinary differential equation solvers
+    \item \texttt{fftpack}: Fast Fourier Transform routines.
+    \item \texttt{interpolate}: Interpolation and smoothing splines.
+    \item \texttt{optimize}: Optimization and root-finding routines.
 \end{itemize}
 
-% \begin{table}[]
-%     \centering
-%     \begin{tabular}{|c|c|c|c|c||c|c|c|c|}
-%     \hline
-%     \multirow{3}{5em}{Application} & \multicolumn{4}{|c||}{RR} & \multicolumn{4}{|c|}{MCA} \\\cline{2-9}
-%                 & \multicolumn{2}{|c|}{numpy} &  \multicolumn{2}{|c||}{no numpy} & \multicolumn{2}{|c|}{numpy} & \multicolumn{2}{|c|}{no numpy} \\\cline{2-9}
-%                 & run & parse &  run & parse & run & parse & run & parse \\
-%     \hline
-%     %        &               RR                 &                 MCA               \\
-%     %        &  numpy         &   no numpy      &      numpy      &     no numpy    \\
-%     %        & run   & parse  &  run   &  parse &  run   & parse  & run    & parse  \\
-%     \multirow{4}{5em}{Interpolate}
-%     \multirow{12}{5em}{Optimize}
-%     \multirow{3}{5em}{FFT}
-%     Adaboost & \warn & \valid & \valid & \valid & \warn & \cross & \cross & \cross \\
-%     Bayesian Ridge Regression & \warn & \valid & \valid & \valid & \cross & \cross & \cross & \cross \\
-%     Online classifier comparison & \valid & \valid & \valid & \valid & \cross & \cross & \cross & \cross  \\
-%     Cluster Iris & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
-%     Covariance estimation & \valid & \cross & \valid & \cross & \cross & \cross & \valid & \cross \\
-%     Decision Tree Regression & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
-%     Digits Classification & \warn & \valid & \valid & \valid & \warn & \cross & \cross & \cross \\
-%     Face Recognition & \cross & \valid & \cross & \valid & \cross & \cross & \cross & \cross \\
-%     L1 Penalty & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \valid \\
-%     Lasso and elastic net & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \cross \\
-%     Separating hyperplan & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
-%     MNIST classification & \warn & \valid & \valid & \valid & \valid & \cross & \valid & \valid \\
-%     Multitask Lasso & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \valid \\
-%     Orthogonal matching & \warn & \valid & \valid & \valid & \cross & \valid & \cross & \valid \\
-%     PCA decomposition & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \cross \\
-%     Robust Linear Regression & \valid & \valid & \valid & \valid & \warn & \cross & \valid & \cross \\
-%     Segmentation toy & \warn & \valid & \valid & \cross & \warn & \cross & \cross & \cross \\
-%     SVM & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
-%     Tomography & \warn & \valid & \valid & \cross & \warn & \cross & \cross & \cross \\
-%     Weighted samples & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
-%     \hline
-%     \end{tabular}
-%     \caption{Pytracer executions summary}
-%     \label{tab:pytracer_sklearn_results_summary}
-% \end{table}
-
 \subsection{Scikit learn}
+\label{sec:sklearn_tests}
 
@@
 
-\begin{table}[]
-    \centering
-    \begin{tabular}{|c|c|c|c|c||c|c|c|c|}
-    \hline
-    \multirow{3}{5em}{Application} & \multicolumn{4}{|c||}{RR} & \multicolumn{4}{|c|}{MCA} \\\cline{2-9}
-                & \multicolumn{2}{|c|}{numpy} &  \multicolumn{2}{|c||}{no numpy} & \multicolumn{2}{|c|}{numpy} & \multicolumn{2}{|c|}{no numpy} \\\cline{2-9}
-                & run & parse &  run & parse & run & parse & run & parse \\
-    \hline
-    %        &               RR                 &                 MCA               \\
-    %        &  numpy         &   no numpy      &      numpy      &     no numpy    \\
-    %        & run   & parse  &  run   &  parse &  run   & parse  & run    & parse  \\
-    Adaboost & \warn & \valid & \valid & \valid & \warn & \cross & \cross & \cross \\
-    Bayesian Ridge Regression & \warn & \valid & \valid & \valid & \cross & \cross & \cross & \cross \\
-    Online classifier comparison & \valid & \valid & \valid & \valid & \cross & \cross & \cross & \cross  \\
-    Cluster Iris & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
-    Covariance estimation & \valid & \cross & \valid & \cross & \cross & \cross & \valid & \cross \\
-    Decision Tree Regression & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
-    Digits Classification & \warn & \valid & \valid & \valid & \warn & \cross & \cross & \cross \\
-    Face Recognition & \cross & \valid & \cross & \valid & \cross & \cross & \cross & \cross \\
-    L1 Penalty & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \valid \\
-    Lasso and elastic net & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \cross \\
-    Separating hyperplan & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
-    MNIST classification & \warn & \valid & \valid & \valid & \valid & \cross & \valid & \valid \\
-    Multitask Lasso & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \valid \\
-    Orthogonal matching & \warn & \valid & \valid & \valid & \cross & \valid & \cross & \valid \\
-    PCA decomposition & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \cross \\
-    Robust Linear Regression & \valid & \valid & \valid & \valid & \warn & \cross & \valid & \cross \\
-    Segmentation toy & \warn & \valid & \valid & \cross & \warn & \cross & \cross & \cross \\
-    SVM & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
-    Tomography & \warn & \valid & \valid & \cross & \warn & \cross & \cross & \cross \\
-    Weighted samples & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
-    \hline
-    \end{tabular}
-    \caption{Pytracer executions summary}
-    \label{tab:pytracer_sklearn_results_summary}
-\end{table}
-
 Table~\ref{tab:pytracer_sklearn_results_summary} summaries sklearn experiments with Pytracer.
 
-\subsubsection{Decision Tree Regression with AdaBoost}
+% \subsubsection{Decision Tree Regression with AdaBoost}
 
-A decision tree is boosted using the AdaBoost.R2~\cite{drucker1997improving} 
-algorithm on a 1D sinusoidal dataset with a small amount of Gaussian noise. 
-299 boosts (300 decision trees) is compared with a single decision tree regressor. 
-As the number of boosts is increased the regressor can fit more detail. 
-The execution with Pytracer reveals a numerical stability.
+% A decision tree is boosted using the AdaBoost.R2~\cite{drucker1997improving} 
+% algorithm on a 1D sinusoidal dataset with a small amount of Gaussian noise. 
+% 299 boosts (300 decision trees) is compared with a single decision tree regressor. 
+% As the number of boosts is increased the regressor can fit more detail. 
+% The execution with Pytracer reveals a numerical stability.
 
-\begin{figure}
-    \centering
-    \caption{Caption}
-    \includegraphics[width=\linewidth]{figure/adaboost/predict_adaboost_s.png}
-    \caption{Number of significant digits of predicted values array.}
-    \label{fig:adaboost_predict_s}
-\end{figure}
+% \begin{figure}
+%     \centering
+%     \caption{Caption}
+%     \includegraphics[width=\linewidth]{figure/adaboost/predict_adaboost_s.png}
+%     \caption{Number of significant digits of predicted values array.}
+%     \label{fig:adaboost_predict_s}
+% \end{figure}
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figure/adaboost/adaboost_boost_mean.png}
-    \caption{Mean values of boost function.}
-    \label{fig:adaboost_boost_mean}
-\end{figure}
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=\linewidth]{figure/adaboost/adaboost_boost_mean.png}
+%     \caption{Mean values of boost function.}
+%     \label{fig:adaboost_boost_mean}
+% \end{figure}
 
-\begin{figure}
-    \centering
-    \caption{Caption}
-    \includegraphics[width=\linewidth]{figure/adaboost/predict_adaboost_zoom_s.png}
-    \caption{Average number of significant digits of prediction over estimator}
-    \label{fig:adaboost_predict_zoom_s}
-\end{figure}
+% \begin{figure}
+%     \centering
+%     \caption{Caption}
+%     \includegraphics[width=\linewidth]{figure/adaboost/predict_adaboost_zoom_s.png}
+%     \caption{Average number of significant digits of prediction over estimator}
+%     \label{fig:adaboost_predict_zoom_s}
+% \end{figure}
 
-\begin{figure}
-\begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth]{figure/adaboost/to_predict_adaboost_mean.png}
-    \caption{Values to predict}
-    \label{fig:adaboost_to_predict_mean}
-\end{minipage}
-\begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth]{figure/adaboost/predict_adaboost_zoom_mean.png}
-    \caption{Predicted values}
-    \label{fig:adaboost_predicted_mean}
-\end{minipage}
-\caption{Comparison between original (fig.~\ref{fig:adaboost_to_predict_mean}) and predicted (fig.~\ref{fig:adaboost_predicted_mean}) values}
-\end{figure}
+% \begin{figure}
+% \begin{minipage}{0.4\linewidth}
+%     \includegraphics[width=\linewidth]{figure/adaboost/to_predict_adaboost_mean.png}
+%     \caption{Values to predict}
+%     \label{fig:adaboost_to_predict_mean}
+% \end{minipage}
+% \begin{minipage}{0.4\linewidth}
+%     \includegraphics[width=\linewidth]{figure/adaboost/predict_adaboost_zoom_mean.png}
+%     \caption{Predicted values}
+%     \label{fig:adaboost_predicted_mean}
+% \end{minipage}
+% \caption{Comparison between original (fig.~\ref{fig:adaboost_to_predict_mean}) and predicted (fig.~\ref{fig:adaboost_predicted_mean}) values}
+% \end{figure}
 
-\subsubsection{Bayesian Ridge Regression}
+% \subsubsection{Bayesian Ridge Regression}
 
-"\texttt{BayesianRidge} estimates a probabilistic model of the regression problem as described above. 
-The prior for the coefficient  is given by a spherical Gaussian:
-\[
-    p(w|\lambda)=\mathcal{N}(w|0,\lambda^{-1}\mathbf{I}_p)
-\]
-The priors over  and  are chosen to be gamma distributions, the conjugate prior for the precision of the Gaussian. 
-The resulting model is called Bayesian Ridge Regression, and is similar to the classical Ridge.
-The parameters, and are estimated jointly during the fit of the model, 
-the regularization parameters and being estimated by maximizing the log marginal likelihood. 
-The scikit-learn implementation is based on the algorithm~\cite{tipping2001sparse}."
+% "\texttt{BayesianRidge} estimates a probabilistic model of the regression problem as described above. 
+% The prior for the coefficient  is given by a spherical Gaussian:
+% \[
+%     p(w|\lambda)=\mathcal{N}(w|0,\lambda^{-1}\mathbf{I}_p)
+% \]
+% The priors over  and  are chosen to be gamma distributions, the conjugate prior for the precision of the Gaussian. 
+% The resulting model is called Bayesian Ridge Regression, and is similar to the classical Ridge.
+% The parameters, and are estimated jointly during the fit of the model, 
+% the regularization parameters and being estimated by maximizing the log marginal likelihood. 
+% The scikit-learn implementation is based on the algorithm~\cite{tipping2001sparse}."
 
-Both execution with RR and MCA modes failed but two different errors. 
-Execution in RR mode raises an error due to an invalid value encountered in the \texttt{sqrt} function
-while the MCA mode execution raises an error due to an issue with the Singular Value Decomposition (SVD) divergence.
+% Both execution with RR and MCA modes failed but two different errors. 
+% Execution in RR mode raises an error due to an invalid value encountered in the \texttt{sqrt} function
+% while the MCA mode execution raises an error due to an issue with the Singular Value Decomposition (SVD) divergence.
 
-RR executions fail with an invalid value in the \texttt{sqrt} function 
-used in the \texttt{\_update\_coef\_} method of the \texttt{BayesianRidge} class.
-This method updates the posterior mean and compute the corresponding Root-Mean-Square-Error (rmse).
+% RR executions fail with an invalid value in the \texttt{sqrt} function 
+% used in the \texttt{\_update\_coef\_} method of the \texttt{BayesianRidge} class.
+% This method updates the posterior mean and compute the corresponding Root-Mean-Square-Error (rmse).
 
-When we backtrack the error propagation, we see that
+% When we backtrack the error propagation, we see that
 
-MCA executions show the limit of Pytracer since the SVD decomposition in scipy is a wrapper around the 
-\texttt{gesdd} or \texttt{gesvd} LAPACK~\cite{anderson1999lapack} functions. 
-Numerical instabilities that are coming from this kernel are opaque for Pytracer since it works 
-at the Python level. Tools working on C/FORTAN codes 
-like Veritracer~\cite{chatelain2018veritracer} can be used to zoom in on these functions.
-Nevertheless, Pytracer provides have a visualization of the input used by the SVD and several
-metrics used in numerical analysis, like the condition number, that can help to understand.
+% MCA executions show the limit of Pytracer since the SVD decomposition in scipy is a wrapper around the 
+% \texttt{gesdd} or \texttt{gesvd} LAPACK~\cite{anderson1999lapack} functions. 
+% Numerical instabilities that are coming from this kernel are opaque for Pytracer since it works 
+% at the Python level. Tools working on C/FORTAN codes 
+% like Veritracer~\cite{chatelain2018veritracer} can be used to zoom in on these functions.
+% Nevertheless, Pytracer provides have a visualization of the input used by the SVD and several
+% metrics used in numerical analysis, like the condition number, that can help to understand.
 
-\subsection{Classifier comparisions}
+\subsubsection{Classifier comparisions}
 
@@
 Each solver is trained and predicts 20 times on 6 different training size ratio.
-
 Figure~\ref{fig:classifier_comparisons_general} shows the all functions
@@
     ("Perceptron", Perceptron()),
-        ("Passive-Aggressive I", PassiveAggressiveClassifier(loss='hinge',
-                                                             C=1.0, tol=1e-4)),
-        ("Passive-Aggressive II", PassiveAggressiveClassifier(loss='squared_hinge',
-                                                              C=1.0, tol=1e-4)),
-        ("SAG", LogisticRegression(
-            solver='sag', tol=1e-1, C=1.e4 / X.shape[0]))
+    ("Passive-Aggressive I", PassiveAggressiveClassifier(loss='hinge',C=1.0, tol=1e-4)),
+    ("Passive-Aggressive II", PassiveAggressiveClassifier(loss='squared_hinge',C=1.0, tol=1e-4)),
+    ("SAG", LogisticRegression(solver='sag', tol=1e-1, C=1.e4 / X.shape[0]))
 ]
@@
         for r in range(rounds):
-                X_train, X_test, y_train, y_test = \
-                    train_test_split(X, y, test_size=i, random_state=rng)
+            X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=i, random_state=rng)
             clf.fit(X_train, y_train)
@@
     \caption{Caption}
-    \includegraphics[width=\linewidth]{figure/classifier_comparisons/mean_predicition_s.png}
-    \caption{Number of significant digits (General view).}
+    \includegraphics[width=\linewidth]{figure/classifier_comparisons/mean_prediction_wo_legend.pdf}
+    \caption{Number of significant digits of the accuracy and predictions for the five classifiers. 
+    Yellow points represents the accuracy for each round and blue points the average accuracy 
+    over the 20 rounds. We can see that the Perceptron classifier has the highest stability.}
     \label{fig:classifier_comparisons_mean_predictions}
@@
 
-\begin{figure}
-    \centering
-    \caption{Caption}
-    \includegraphics[width=\linewidth]{figure/classifier_comparisons/SAG_predicition_s.png}
-    \caption{Number of significant digits (General view).}
-    \label{fig:classifier_comparisons_general}
-\end{figure}
+% \begin{figure}
+%     \centering
+%     \caption{Caption}
+%     \includegraphics[width=\linewidth]{figure/classifier_comparisons/SAG_predicition_s.png}
+%     \caption{Number of significant digits (General view).}
+%     \label{fig:classifier_comparisons_general}
+% \end{figure}
 
-\begin{figure}
-    \centering
-    \caption{Caption}
-    \includegraphics[width=\linewidth]{figure/classifier_comparisons/zoom_SAG_fit_coef_s.png}
-    \caption{Number of significant digits (General view).}
-    \label{fig:classifier_comparisons_general}
-\end{figure}
+% \begin{figure}
+%     \centering
+%     \caption{Caption}
+%     \includegraphics[width=\linewidth]{figure/classifier_comparisons/zoom_SAG_fit_coef_s.png}
+%     \caption{Number of significant digits (General view).}
+%     \label{fig:classifier_comparisons_general}
+% \end{figure}
 
-\subsection{Cluster IRIS}
+\subsubsection{Cluster IRIS}
 
@@
     \includegraphics[width=\linewidth]{figure/cluster_iris/general.png}
-    \caption{Number of significant digits (General view).}
+    \caption{Number of significant digits of the Cluster IRIS test.}
     \label{fig:cluster_iris_general}
@@
 
-Pytracer instrumentation overhead comes from the time spent to instrument module (initialization overhead)
+Pytracer instrumentation overhead comes from the time spent to instrument module (initial ?zation overhead)
 before executing the targeted application plus the cost for dumping the data during the execution (running overhead).
@@
     \end{tabular}
-    \caption{Caption}
+    \caption{Overheads of \pytracer on PyAFQ experiment with and without fuzzy.}
     \label{tab:pytracer_overhead}
@@
 
+Pytracer produces traces during the tracing phase that must be aggregated before visualizing.
+Each trace is read sequentially until the end of the file. 
+For the moment, Pytracer is not able to merge traces but we would like to extend it.
+We measure the postprocessing time depending on the regularity of the 
+trace and the batchsize.
+
 \section{Discussion}
 
-\begin{itemize}
-    \item Control flow divergence
-    \item MCA mode -> semantic bugs
-    \item Pytracer is flexible and works with any type of perturbations (uncertainty quantification, internal randomness, parallel sections).
+\pytracer is a tool for visualizing the numerical quality of function inputs/outputs over time.
+It generates numerical traces that are aggregated in postprocessing to measure numerical discrepancies between executions.
+\pytracer does not make any assumption about the noise model used to estimate uncertainties but has been tested with the MCA 
+through the fuzzy ecosystem on two broadly used scientific libraries for Python with a partial success.
 
-\end{itemize}
+As we shown in the section~\ref{sec:impact_mca_modes}, using the Full MCA mode leads to run-time errors
+that has a considerable impact on the proper functioning of the execution. This is unfortunate since these
+errors do not reflect real numerical errors but errors related to perturbations that should not occur.
+Fixing this misbehaviour would greatly help in the use of Full MCA mode since this mode allows simulating catastrophic
+cancellations which are common sources of numerical errors. By preserving exact operations, RR mode is far more conservative 
+and can be used more easily even though it does not simulate all perturbations that might be encountered.
+
+Also, by using a postprocess analysis to aggregate traces, \pytracer falls in the same pitfalls than veritracer
+and is limited to aggregate traces where execution flow path extremely diverge. A posteriori reconstruction
+is a challenging task as one must be able to identify precisely flow path taken and to find synchronization points
+to pursue the analysis. We retrieve for example this divergence behaviour in two general classes of numerical schemes:
+iterative methods and optimization processes. One solution to overcome this issue is to 
+integrate method used in code coverage analysis to keep track of flow paths taken in addition to the backtraces.
+But this would increase the complexity of the postprocess analysis as well as an extra slowdown factor.
+However, we believe that by coupling the gantt chart with a static analysis, \pytracer would be able to catch 
+some divergence patterns occurring within a function. Indeed, by instrumenting at the function level, \pytracer 
+has a view on function's callees (i.e. the functions that are called within a function) and thus should be able to
+partially detect flow divergences.
+
+By design principle, \pytracer is flexible on the noise model used although we only test it with the MCA model in our experiments.
+But we would like to compare different models against MCA in future works to see the resulting differences. 
+In particular, although \pytracer only works 
+on sequential application for the moment, it can be used to analyze parallel section internal to a function.
+The only restriction being that the section does not call other functions traced by \pytracer, 
+we would fall in the previous issue of divergence if it would not be the case.
+Since \pytracer only care about inputs and outputs of a function, the order of internal operations are transparent for it
+and thus should be able to handle those cases.
+
+Finally, elementary arithmetic operations are not instrumented by \pytracer and it can be a barrier to deeper analysis.
+However, we believe that an instrumentation at the function level present two advantages:
+it first limits the size of the traces since only inputs and outputs of a function are dumped instead 
+of a full report which, on one hand, decrease the overhead of the instrumentation and, on the other hand,
+help the user to quickly identify instabilities. One of the pitfalls can be to overwhelm the user with too much information, 
+which makes analysis more difficult. Nevertheless, the analysis at fine granularity can be interesting 
+at a final step of the understanding. Such an analysis would require a different instrumentation approach
+by for example working at the Abstract Syntax Tree (AST) level since it is trivial to get it in Python.
+An ideal way to do that would be to be able to extract and replay a function,
+in the same vein as the CERE~\cite{castro2015cere} tool does but for Python, and use an AST instrumentation to analyze step by step 
+the numerical quality of elementary operations within the fuzzy environment.
+Lastly, AST analysis can serve as a basis for finding relationship between variables which is another useful 
+piece of information for the user.
+
+\tristan{I moved this paragraph from results, it belongs here. It should be weaved in the discussion.}
+In addition to runtime errors that it raises, mismatching shapes is also a problem when aggregating
+traces as \pytracer will not be able to compute statistics for set of arrays having different shapes.
+Two solutions exist to overcome this issue: the first one is to not instrument the \texttt{PyArray\_Arange}
+function with MCA. The advantage is that it is easy to set up since it requires one extra line in the exclusion file.
+However, the same kind of problem may appear somewhere else
+because, as we have seen, the operations being evolved are elementary. The chances that developers reproduce
+the same pattern is very probable. The second solution is to ensure that Full MCA mode preserved the exact operations.
+This solution has the advantage of not having to worry about which functions should be instrumented or not with MCA,
+but it is hard to achieve it in practice. Indeed, we rely on the MCA implementation provided by Verificarlo that 
+uses an internal precision to add the random perturbation that is higher 
+than the working precision for applying the random noise. The result is then rounded to the working precision before returning it so
+any residual noise lower than the working precision is lost. 
+Keeping track of that noise would requires to record each intermediate computation in a shadow memory 
+or at least to keep a tag about their exactness.
+\Yohan{This idea has emerged by discussing with the Verificarlo's team. 
+I must find a way to express that, and to do not give the impression that we discovered or suggest it.}
+This option would require more extra works than the first one but would ensure more consistent results.
+
+\Yohan{Discuss issue to visualize complex values (fft2D)}
 
 \section{Conclusion}
+
+\tristan{I moved this from the opening of Section 4, as this reads more like a summary of \pytracer's features than an experiment description.
+It should be refactored in 1-2 paragraphs summarizing the main properties of \pytracer.}
+Our strategy is to demonstrate that \pytracer is:
+\begin{itemize}
+    \item Domain agnostic: \pytracer is intended to work on any scientific Python applications, 
+    without specific domain specific languages or needs to rely on specific libraries.
+    We target two of the most common libraries used in scientific computing within Python, SciPy and Scikit-learn, as
+    well as a domain specific application in neuroimaging. We show that \pytracer works
+    well on these libraries, capturing most of the functions' module targeted.
+    \item Automatic: \pytracer objective is to offer an automatic instrumentation for any Python applications,
+    from small prototype to state-of-the-art scientific libraries. 
+    \item Scalable: \pytracer goal is to trace real world application and use case.
+    In that perspective, we use \pytracer on PyAFQ, a domain specific application in neuroimaging to compute 
+    tractograms, generating \pytracer traces up to 1TB. We demonstrate that \pytracer is able to 
+    handle this volume of data and to offer an interactive and fluent visualization to the user.
+    We also show that \pytracer instrumentation gives a slowdown of $\times 6$.
+    \item Fuzzy compatible: \pytracer aims at evaluating numerical stability by using injection noise model.
+    Although the noise model used is orthogonal to \pytracer tracing mechanism, we emphasis in these experiments 
+    on the MCA model through the fuzzy environment, and discuss its compatibility with \pytracer tracing mechanism
+    to point out limitations of the trace-based approach and to propose research tracks to overcome them.
+    It should be noted that experiments conducted in this paper are the first largest application of the fuzzy ecosystem
+    by the wide range of applications covered. We therefore found interesting to give a feedback about pitfalls and benefits encountered
+    in order to shed light on the good and bad practices for first-time users and hence democratize the usage of MCA.
+    Moreover, these analyses will help the fuzzy developers to increase the overall stability of fuzzy.
+\end{itemize}
 

### 2021-09-22 paper.tex
Update after Tristan's review on sections 3 and 4.1

@@
 The scientific Python ecosystem is a central component of scientific
-analyses due to its rich offering of data manipulation, array programming,
+analyses due to its rich data manipulation, array programming,
 numerical analysis, and visualization tools. In particular, libraries such
 as NumPy~\cite{harris2020array}, SciPy~\cite{virtanen2020scipy}, scikit-learn~\cite{pedregosa2011scikit} or PyTorch~\cite{paszke2019pytorch} are used in hundreds of publications every year, providing a reference set of high-quality open-source core scientific libraries.
-Numerous domain-specific data analysis pipelines were built from this ecosystem by diverse research groups, leveraging Python's simplicity and expressivity.
+Diverse research groups built numerous domain-specific data analysis pipelines from this ecosystem, leveraging Python's simplicity and expressivity.
 
 Numerical stability is a crucial requirement of reliable scientific data
-processing. In unstable analyses, small numerical perturbations introduced
-by data noise, software and hardware updates, or parallelization lead to
-substantial deviations in final results and potentially different scientific conclusions, threatening the reliability of computational analyses.
-To address this issue, numerical stability analyses need to be conducted systematically.
+processing.
+In unstable analyses, small numerical perturbations introduced by data noise, software and hardware updates, or parallelization lead to substantial deviations in final results and potentially different scientific conclusions, threatening the reliability of computational analyses.
+Numerical stability analyses need to be conducted systematically to address this issue.
 However, no practical tool currently exists to conduct such analyses on Python programs.
@@
 PyTracer adopts a dynamic approach that evaluates numerical stability using program execution traces, enabling scaling to large programs without manual intervention.
-In contrast, theoretical approaches based on condition number or backward error analyses require detailed modelling of the program and its numerical implementation.
+In contrast, theoretical approaches based on condition number or backward error analyses require detailed modeling of the program and its numerical implementation.
 Similarly, static code analysis techniques such as Frama-C~\cite{cuoq2012frama}, Gappa~\cite{de2010certifying} or Flocq~\cite{boldo2011flocq} hardly scale to large codebases, particularly in dynamically-typed languages such as Python.
@@
 PyTracer estimates the significant digits of Python floating-point variables by combining program traces obtained with different numerical perturbations, which requires (1) tracing floating-point computations along program executions, (2) generating numerically-perturbed executions, and (3) visualizing stability evaluations.
-PyTracer addresses these requirements with (1) dynamic instrumentation of Python functions, modules and classes through meta-programming, (2) a ``fuzzy" Python interpreter instrumented with Monte-Carlo arithmetic, and (3) an interactive Plotly dashboard to visualize stability measures throughout program executions.
+PyTracer addresses these requirements with:
+Dynamic instrumentation of Python functions, modules, and classes through meta-programming
+A ``fuzzy" Python interpreter instrumented with Monte-Carlo arithmetic
+An interactive Plotly dashboard to visualize stability measures throughout program executions
 
@@
 SciPy, scikit-learn, and pyAFQ~\cite{kruper2021evaluating} --- an analysis toolbox for diffusion magnetic resonance imaging --- we demonstrate PyTracer as a practical solution to review the numerical stability of extensive code bases.
-The remainder of this manuscript describes related approaches, presents the design of PyTracer, and demonstrates its potential on various use cases.
-
-% \begin{itemize}
-%     \item Numerical instabilities are inherent to numerical computations \tristan{not only to HPC, also software updates, small perturbations in parameters or data}
-%     \item 
-%     \item Neuroimaging tools are facing reproducibility issues, one factor of which is numerical stability \tristan{neuroimaging should be an illustration, your intro should rather focus on Python in general, it's much more impactful}
-%     \item Detecting those instabilities is challenging: large data sets, large pipeline, long computation time, complex physics \tristan{Here you could illustrate the point with neuroimaging pipelines}
-%     \item Needs tools for automatically detecting these instabilities
-%     \item Needs tools to quickly identify unstable functions among large number of calls
-% \end{itemize}
+The remainder of this manuscript describes related approaches, presents the design of PyTracer, and demonstrates its potential in various use cases.
 
@@
 
-Several tools have been and continue to be developed to assess numerical quality. Those tools can be divided in two main categories depending whether they adopt a static or a dynamic approach.
-Static analysis produces theoretically-valid error bounds 
-while dynamic analysis is generally more scalable although it only provides experimental estimations.
-\pytracer adopts the dynamic approach, due to its scalability to large existing code bases.
+Several tools have been and continue to be developed to assess numerical quality. Those tools can be divided into two main categories depending on whether they adopt a static or a dynamic approach.
+The static analysis produces theoretically valid error bounds, while dynamic analysis is generally more scalable, although it only provides experimental estimations.
+\pytracer adopts the dynamic approach due to its scalability to large existing code bases.
 Dynamic approaches typically rely on the tracing of floating-point computations to detect instabilities and visualize them.
@@
 \subsection{Numerical tracing techniques}
-
-Many tools  are dedicated to the tracing of floating-point computations in C, C++ or FORTRAN programs due to the prevalence of these languages in High-Performance Computing (HPC). 
-The main tracing techniques are source-to-source and compiler based transformations.
-\tristan{Re-organize the following in two paragraphs, (1) source-to-source, (2) compiler-based.
-For each paragraph, define the technique in 1 sentence, then list the tools}
-CADNA~\cite{jezequel2008cadna} is a library for C, C++ and Fortran  implementing the
-CESTAC~\cite{vignes1993stochastic} stochastic arithmetic \tristan{is it source-to-source or compiler-based?}.
-Verificarlo~\cite{verificarlo} is a compiler that supports different types of arithmetic instrumentations, including
-Monte Carlo Arithmetic (MCA)~\cite{parker1997monte}.
+Tools to trace floating-point computations for C, C++, or FORTRAN programs are plethora due to the prevalence of these languages in High-Performance Computing (HPC). 
+The main tracing techniques are source-to-source, compiler-based transformations, and dynamic binary instrumentation.
+
+The Source-to-source technique requires a rewriting of the application to use modify floating-point types.
+CADNA~\cite{jezequel2008cadna} is a library for C, C++ and Fortran  implementing the CESTAC~\cite{vignes1993stochastic} stochastic arithmetic.
+pLiner uses source-to-source transformation at the Abstract Syntax Tree (AST)  level to rewrite parts of code with higher precision. 
+Shaman~\cite{demeure_phd} is a C++ library that uses a first-order error model to propagate numerical error. 
+MCAlib~\cite{frechtling2015mcalib} is a C library that implements the Monte Carlo Arithmetic (MCA)~\cite{parker1997monte} using the MPFR~\cite{fousse2007mpfr} library.
+The work in~\cite{tang2016software} proposed a source-to-source framework for executing targeted code in infinite and fixed precision with and without using stochastic arithmetic.
+
+The compiler-based approach uses a compiler to analyze or replace floating-point expressions with other models automatically. 
+Verificarlo~\cite{verificarlo} is a compiler that supports different types of arithmetic instrumentations, including MCA. 
 The work in ~\cite{bao2013fly} modified the GNU Compiler Collection (GCC) to track local floating-point errors across executions.
-pLiner~\cite{guo2020pliner} is a root cause analyzer based on the Clang compiler that detects floating-point operations
-responsible for result variability. 
-pLiner uses source-to-source transformation at the AST \tristan{expand acronym} level  to rewrite parts of code with higher precision.
+pLiner~\cite{guo2020pliner} is a root cause analyzer based on the Clang compiler that detects floating-point operations responsible for result variability.
 PFPSanitizer~\cite{chowdhary2020debugging,chowdhary2021parallel}, is a compiler that uses parallel shadow execution to detect numerical issues using higher precision.
-Shaman~\cite{demeure_phd} is a C++ library that uses a first-order error model to propagate numerical error. 
-FLiT~\cite{sawaya2017flit} is framework to detect variability induced by compilers and their optimizations.
-The work in~\cite{tang2016software} proposed a source-to-source framework for executing targeted code 
-in infinite and fixed precision with and without using stochastic arithmetic.
-The work in~\cite{wang2012development} proposes a numerical debugger based on GDB~\cite{stallman1988debugging} for 
-Discrete Stochastic Arithmetic (DSA) on FPGA as an Eclipse plugging. Similarly, Cadtrace~\cite{jezequel2008cadna}
-and Shaman propose a GDB based tool to respectively use the CADNA and Shaman libraries with GDB.
-
-Another technique, Dynamic Binary Instrumentation (DBI), evaluates numerical stability at the binary level,
-enabling the analysis of any binary regardless of the programming language. However, working at binary level makes it difficult to access high-level information needed
-for debugging and understanding the source code logic. In particular, analyzing Python code with DBI is feasible but provides very limited insights on the stability of specific Python code sections.
+FLiT~\cite{sawaya2017flit} is a framework to detect variability induced by compilers and their optimizations.
+The work in~\cite{wang2012development} proposes a numerical debugger based on GDB~\cite{stallman1988debugging} for Discrete Stochastic Arithmetic (DSA) on FPGA as an Eclipse plugging.
+Similarly, Cadtrace~\cite{jezequel2008cadna} and Shaman propose a GDB-based tool to use the CADNA and Shaman libraries with GDB, respectively.
+
+Dynamic Binary Instrumentation (DBI) operates on an executable directly, without the need for recompilation or manual changes, and is thus
+transparent to the programming language used. However, working at a binary level makes it difficult to access high-level information needed
+to debug and understand the source code logic. In particular, analyzing Python code with DBI is feasible but provides minimal insights on the stability of specific Python code sections.
 CraftHPC~\cite{lam2013dynamic} uses DBI to detect catastrophic cancellations at runtime.
 Verrou~\cite{fevotte2016verrou} is a Valgrind~\cite{nethercote2007valgrind} based tool that replaces on-the-fly
-floating-point operations by their stochastic arithmetic counterparts. FPDebug~\cite{benz2012dynamic} uses DBI to detect numerical 
-inaccuracies by using shadow computations with a higher precision.
+floating-point operations by their stochastic arithmetic counterparts. FPDebug~\cite{benz2012dynamic} uses DBI to detect numerical inaccuracies by using shadow computations with higher precision.
 Herbgring~\cite{sanchez2017finding} is a Valgrind-based tool to detect
-numerical instabilities. It uses a shadow memory to do detect precision losses by comparison with results obtained with the high-precision 
+numerical instabilities. It uses a shadow memory to detect precision losses by comparison with results obtained with the high-precision 
 MPFR library~\cite{fousse2007mpfr}. It is combined with symbolic computation to backtrack the root of the error.
-We can note that all methods based on a high-precision oracle suppose that computing with
-a large number of bits is sufficient to obtain an accurate result, which is not always true, see for example the famous Muller's sequence ~\cite{chatelain2018veritracer}.
-
-To the best of our knowledge, there is currently no tool dedicated to numerical analysis of Python code.
+We can note that all methods based on a high-precision oracle suppose that computing with a large number of bits is sufficient to obtain an accurate result, which is not always true, see, for example, the famous Muller's sequence ~\cite{chatelain2018veritracer}.
+
+Being agnostic to the programming language is a serious advantage of the DBI method compare to source-to-source and compiler-bases methods.
+However, working at a binary level makes it difficult to access high-level information needed to debug and understand the source code logic.
+On the other hand, Source-to-source presents the advantage of having a fine-grained control on code analyzed but lacks scalability, as rewriting large codes can be a tedious task if done by hand.
+Finally, the compiler-based approach takes advantage of the best of both by being automatic and having access to high-level information.
+However, like source-to-source, the compiler-based method is not suitable for analyzing closed-source proprietary libraries.
+
+To the best of our knowledge, there is currently no tool dedicated to the numerical analysis of Python code.
 Existing tools for tracing Python code are dedicated to performance profiling, for time (cProfile)
 or memory consumption (memprofile). 
-Anteater~\cite{faust2019anteater} is a Python tracer tool that aims at debugging Python application. 
-It operates source transformation at AST level but only deals with native numeric Python types.
-Moreover, the user needs to manually tag each variable to trace. Finally, according to the authors,
-Anteater do not scale to large traces.
-However, we can compare the methodology used by these tools \tristan{are you referring to Anteater here?
-if so, it should be "this" tool.
-Otherwise, list which tools you're referring to.} against the one used in Pytracer.
-These tools use an instrumentation based on decorators, a Python mechanism allowing 
-to instrument a function by adding a line over a function declaration.
-While this method is useful when targeting specific functions, it becomes time consuming 
-when applied to a large number of functions since one needs to tag functions manually,
-which is not feasible for large code bases where potentially unstable code sections are not known.
-
-% Moreover, the user has most of the time no clues
-% about where numerical instability comes from and must therefore all functions as potentially suspect. 
-% This issue enforces the need to use automatic approaches.
-%  Moreover, few tools embed a visualizer for 
-% analyzing numerical quality over time letting the postprocessing to the user.
-
-% \tristan{The content of this section is excellent but the structure is a bit messy.
-Would you like to restructure in 3 paragraphs as follows?
-(1) There's no numerical instrumentation tools in Python (your last paragraph + anteater), (2) DBI tools could be used but won't provide a detailed stack trace, (3) tools for other languages.}
+Anteater~\cite{faust2019anteater} is a Python tracer tool that aims at debugging Python applications. 
+It operates source transformation at the AST level but only deals with native numeric Python types.
+Moreover, the user needs to tag each variable to trace manually. Finally, according to the authors, Anteater does not scale to large traces.
+However, we can compare the methodology used by cProfile, memprofile, and Anteater against the one used in Pytracer.
+These tools use instrumentation based on decorators, a Python mechanism allowing to instrument a function by adding a line over a function declaration.
+While this method is proper when targeting specific functions, it becomes time-consuming when applied to many functions since one needs to tag functions manually, which is not feasible for large codebases where potentially unstable code sections are unknown.
 
@@
 Uncertainty analysis (UA) is a method to derive the output distribution response from an input distribution.
-The idea is to model uncertainty on data due to limited precision measurement for example by a probability distribution and 
-to estimate the impact on the result. 
+The idea is to model uncertainty on data due to limited precision measurement, for example, by a probability distribution, and to estimate the impact on the result. 
 Sensitivity analysis (SA) is quite close to uncertainty analysis but differs from the scale observed.
-While uncertainty analysis attempts to describe the whole output distribution, sensitivity analysis 
-measure the local response to a small perturbation~\cite{loucks2017water}. 
-Several approaches for UA and SA exist among them differential analysis, response surface methodology, Monte Carlo analysis
-and variance decomposition (see~\cite{helton2006survey}). In particular, Monte Carlo Analysis is a sampling-based technique
-that samples inputs space to estimate output response.
+While uncertainty analysis attempts to describe the whole output distribution, sensitivity analysis measures the local response to a small perturbation~\cite{loucks2017water}. 
+Several approaches for UA and SA exist, among them differential analysis, response surface methodology, Monte Carlo analysis, and variance decomposition (see~\cite{helton2006survey}).
+In particular, Monte Carlo Analysis is a sampling-based technique that samples inputs space to estimate output response.
 Monte Carlo analysis shares similarities with Monte Carlo Arithmetic.
@@
 
-The quality of a Random Number Generator is a key characteristic when dealing with stochastic model and differ from cryptography requirements.
-For numerical simulation a RNG of quality must have a good tradeoff between performance, period, correlation or uniformity~\cite{james2020review}.
-Poor quality RNGs may have a substantial impact on results~\cite{click2011quality}. As a first step, measuring variation induced by seed is 
-a good indicator about the program stability that can be compared against variability induced by floating-point arithmetic.
-\Yohan{This section lacks of strong arguments. Needs improvement}
+The quality of a Random Number Generator is a crucial characteristic when dealing with stochastic model and differ from cryptography requirements.
+For numerical simulation, an RNG of quality must have a good tradeoff between performance, period, correlation, or uniformity~\cite{james2020review}.
+Poor quality RNGs may have a substantial impact on results~\cite{click2011quality}.
+First, measuring variation induced by seed is a good indicator of program stability that we can compare against variability induced by floating-point arithmetic.
+\Yohan{This section lacks solid arguments. Needs improvement}
 
@@
 
-Visualization covers a wide range of specific domains in the numerical simulation area, from general purpose numerical visualization with tools
-like VTK~\cite{schroeder2000visualizing},
-to topological data analysis~\cite{tierny2018topological}, including matrix~\cite{wu2008matrix} or tensor~\cite{kindlmann2006diffusion} visualization.
+The visualization covers a wide range of specific domains in the numerical simulation area, from general-purpose numerical visualization with tools
+like VTK~\cite{schroeder2000visualizing}, to topological data analysis~\cite{tierny2018topological}, including matrix~\cite{wu2008matrix} or tensor~\cite{kindlmann2006diffusion} visualization.
 We review here tools dedicated to the analysis of the numerical variability induced by the floating-point model.
-We can first highlight the fact that despite the large number of existing tools dedicated to pinpoint 
-source code instructions, few of them allow the user to have a global view of the numerical accuracy of their computations
-or compare several executions of the same program under various perturbations.
-% Indeed, all methods based on an high-precision oracles cannot capture variability between several executions as they only refer 
-% to one oracle. In other words, the actual computation is compared against the same computation with higher-precision by 
-% using the same inputs data in a synchronous way.
-
-Veritracer~\cite{chatelain2018veritracer} was the first tool to propose an embedded visualizer to 
-visualize the numerical stability over time for C, C++ and Fortran codes.
-It is a trace-based tool built as an extension of Verificarlo~\cite{verificarlo} that offers contextual 
-information about variables traced to allow the user to quickly identify instabilities.
-However, it does not offer a dynamic interface neither takes into account information about 
-high-level structures like \texttt{struct} or \texttt{array}.
-FPAvizual~\cite{gu2014fpavisual} is a tool for visualizing effects of floating-point arithmetic but only for educational purposes.
-Anteater~\cite{faust2019anteater} proposes a visualizer for Python codes but as mentioned previously,
-it only deals with native Python types and the user needs to manually select variables to trace. 
-However, Anteater provides a real reflection around visual debugging beyond floating-point 
-analysis, which has inspired the design of \pytracer's visualization interface.
+We can first highlight that despite the large number of existing tools dedicated to pinpoint source code instructions, few of them allow the user to have a global view of the numerical accuracy of their computations or compare several executions of the same program under various perturbations.
+
+Veritracer~\cite{chatelain2018veritracer} was the first tool to propose an embedded visualizer to visualize the numerical stability over time for C, C++, and Fortran codes.
+It is a trace-based tool built as an extension of Verificarlo~\cite{verificarlo} that offers contextual information about variables traced to allow the user to identify instabilities quickly.
+However, it does not offer a dynamic interface neither takes into account information about high-level structures like \texttt{struct} or \texttt{array}.
+FPAvizual~\cite{gu2014fpavisual} is a tool for visualizing the effects of floating-point arithmetic but only for educational purposes.
+Anteater~\cite{faust2019anteater} proposes a visualizer for Python codes, but as mentioned previously, it only deals with native Python types, and the user needs to select variables to trace manually.
+However, Anteater provides an accurate reflection around visual debugging beyond floating-point analysis, which has inspired the design of \pytracer's visualization interface.
 
@@
 
-The PyTracer workflow follows a three step approach (Figure~\ref{fig:workflow}).
-When a Python application is loaded, \pytracer instruments it using ``monkey patching", a technique to modify Python programs without editing their source code.
+The PyTracer workflow follows a three-step approach (Figure~\ref{fig:workflow}).
+First, when a Python application is loaded, \pytracer instruments using ``monkey patching", a technique to modify Python programs without editing their source code.
 The instrumentation replaces all the functions with a wrapper that saves their arguments and outputs in a trace file using ``pickle", Python's object serialization mechanism.
@@
 The \texttt{finder} is responsible for finding the package (or 
-namespace\footnote{Python makes a distinction between \texttt{regular} and \texttt{namespace} packages.
+namespace\footnote{Python distinguishes between \texttt{regular} and \texttt{namespace} packages.
 A regular package is a directory that contains a \_\_init\_\_.py file and potentially subdirectories (sub-packages) 
-that contain themselves a \_\_init\_\_.py file and so on recursively. 
+that contain themselves a \texttt{\_\_init\_\_.py} file and so on recursively. 
 The package hierarchy follows those of the directory. 
@@
 
-Python implements default \tristanmod{\texttt{importers}}{\texttt{finder} and \texttt{loader}} classes as well as search paths for importing a module, but it also provides a way to create custom \texttt{finder} and \texttt{loader} classes.
+Python implements default \texttt{finder} and \texttt{loader} classes and search paths for importing a module, but it also provides a way to create custom \texttt{finder} and \texttt{loader} classes.
 To register a new \texttt{finder} class, one needs to add it to the \texttt{sys.meta\_path} list.
-When an \texttt{import} statement is encountered, Python first looks for a binding in the \texttt{sys.modules}
+When Python encounters an \texttt{import} statement, it first looks for a binding in the \texttt{sys.modules}
 and then iterates over \texttt{sys.meta\_path}.
-Python queries each \texttt{finder} class successively until it finds the module or it reaches the end of the list, raising a \texttt{ModuleNotFoundError}.
-\pytracer adds  a custom \texttt{finder} class at the head of the list that intercepts
+Python queries each \texttt{finder} class successively until it finds the module or reaches the end of the list, raising a \texttt{ModuleNotFoundError}.
+Then, \pytracer adds a custom \texttt{finder} class at the head of the list that intercepts
 the module import and creates the module with a custom \texttt{loader} class.
 
-\pytracer's \texttt{loader} class first loads the original module, then copies it as a new instance of the \texttt{ModuleType} class.
-It then calls the appropriate instrumentation function for each module attribute depending on its type (function, class or submodule). Once all the attributes are instrumented, 
-\pytracer replaces the original module by its instrumented counterpart
-in the \texttt{sys.modules} map \tristan{is the non-instrumented version ever added to sys.modules?
-If so, could this lead to race conditions?
-If not, replace with ``adds the instrumented module to the sys.modules map"}.
-Hence, the calling convention remains unchanged and the application will transparently call
-the instrumented module.
+\pytracer's \texttt{loader} class first loads the original module then copies it as a new instance of the \texttt{ModuleType} class.
+It then calls the appropriate instrumentation function for each module attribute depending on its type (function, class, or instances).
+Next, \pytracer replaces the original module with its instrumented counterpart in the \texttt{sys.modules} map once it has instrument all the attributes.
+Hence, the calling convention remains unchanged, and the application will transparently call the instrumented module.
+Finally, Pytracer updates all references to the original module that an object may hold.
+For example, functions have a \texttt{\_\_globals\_\_} attribute that contains references to internal objects that the function needs.
+Since those references point to non-instrumented objects, Pytracer must update them.
+\tristan{is the non-instrumented version ever added to sys.modules? If so, could this lead to race conditions? If not, replace with ``adds the instrumented module to the sys.modules map"}. 
+\Yohan{Yes, it replaces the original module.
+You can't have a race-condition since sys.modules is a dict with only one value for a given key.
+The trick is that the wrapped module keeps a reference to the original module, it's just that this reference is invisible for the others object since it's not in sys.modules and globals.
+By the way, Pytracer needs to update all possible references that original objects may hold, like functions in \_\_dict\_\_ attributes or locals references in \_\_globals\_\_ for example.}
 
@@
 
-Module functions are the simplest case to deal with.
-For each function, \pytracer's \texttt{loader} class
-creates a wrapper function, dynamically compiles it with the \texttt{compile}
-builtin function, and substitutes it for the original module function.
-However, this technique cannot be applied to
-callable class instances, i.e., class instances that have the \texttt{\_\_call\_\_} attribute but are not of the \texttt{FunctionType} type.
-Indeed, applying the wrapper technique would 1) modify the type of the class instance to \texttt{FunctionType},
-which could cause semantic bugs, and 2) mask class attributes, leading to \texttt{AttributeError} exceptions.
-To overcome this issue, \pytracer overrides the \texttt{\_\_call\_\_} attribute with the wrapper function when 
-possible. When the \texttt{\_\_call\_\_} attribute is not writable,  
-the class is not instrumented and a warning is returned.
-Listings~\ref{fig:wrapper_creation} and ~\ref{fig:generic_wrapper} show \pytracer's wrapper creation function \tristan{add docstrings to all Python code examples and clarify captions accordingly: you don't need to explain the meaning of each attribute in the caption if it's in the docstring.
-The caption can focus on the main functionality, reusing the text currently in 3.1.5.}.
+Module functions are the most straightforward case to treat.
+For each function, \pytracer's loader class creates a wrapper function, dynamically compiles it with the compile builtin function, and substitutes it for the original module function.
+However, we cannot apply this technique to callable class instances, i.e., class instances that have the \texttt{\_\_call\_\_} attribute but are not of the \texttt{FunctionType} type.
+Indeed, applying the wrapper technique would 1) modify the type of the class instance to \texttt{FunctionType}, which could cause syntactic and semantic bugs, and 2) mask class attributes, leading to \texttt{AttributeError} exceptions.
+To overcome this issue, \pytracer overrides the \texttt{\_\_call\_\_} attribute with the wrapper function when possible.
+When the \texttt{\_\_call\_\_} attribute is not writable,  Pytracer does not instrument the class and returns a warning.
+Listings~\ref{fig:wrapper_creation} and ~\ref{fig:generic_wrapper} show \pytracer's wrapper creation function.
+
+\tristan{add docstrings to all Python code examples and clarify captions accordingly: you don't need to explain the meaning of each attribute in the caption if it's in the docstring.
+The caption can focus on the main functionality, reusing the text currently in 3.1.5.}
+\Yohan{TODO}
+
+Listing~\ref{fig:wrapper_creation} shows how functions are instrumented.
+This function takes as inputs the information about the function to instrument (module name and full qualified name),
+the function itself, and the actual name of the function. It then creates a wrapper around the actual wrapper
+(\texttt{generic\_wrapper}) that will dump the values.
+Instead of passing the function, we pass the function's identifier, which is a unique 64-bits integer that references each Python object.
+This identifier is available
+with the \texttt{id} builtin function. it allows to get rid of aliases and to avoid instrumenting functions twice.
+
+Listing~\ref{fig:generic_wrapper} shows what the instrumented code does. 
+It first unpacks the function's information to get the function's identifier to retrieve the original function.
+Then arguments are bound by creating a mapping from positional and keyword arguments to parameters, avoiding conflicts and mispositioning.
+It also allows getting names of arguments for the visualization.
+Once bound, the \texttt{inputs} function dumps the arguments in the pickle file.
+Finally, Pytracer calls the function with the correct arguments, dumps the result, and returns it.
 
@@
 However, some classes, in particular base types, contain read-only attributes that cannot be instrumented. 
-By default, \pytracer returns a warning when it encounters such classes, but it treats NumPy's universal functions (\texttt{ufuncs}) specifically since they are ubiquitous in scientific computing.
+By default, \pytracer returns a warning when it encounters such classes, 
+but it treats NumPy's universal functions (\texttt{ufuncs}) specifically since they are ubiquitous in scientific computing. 
 NumPy's \texttt{ufuncs} are vectorized element-wise operators that apply to multidimensional arrays. 
 In particular, all the element-wise elementary mathematical functions are \texttt{ufuncs}.  
-To increase performance, \texttt{ufuncs} are implemented in C which prevents their instrumentation using the technique described previously.
-Instead, \pytracer uses
-NumPy's \texttt{frompyfunc} helper function to create an instrumented \texttt{ufunc} that wraps the original one.
-This approach works in many cases but it requires the instrumented function to return objects of type \texttt{PyObject}, which may create errors (Listing~\ref{fig:numpy_array_index_issue}). 
+To increase performance, \texttt{ufuncs} are implemented in C, which prevents their instrumentation using the technique described previously. 
+Instead, \pytracer uses NumPy's \texttt{frompyfunc} helper function to create an instrumented \texttt{ufunc} that wraps the original one.
+This approach works in many cases but it requires the instrumented function to return objects of type \texttt{PyObject}, 
+which may create errors (Listing~\ref{fig:numpy_array_index_issue}). 
 As a last resort, the user may disable \texttt{ufunc} tracing in Pytracer.
@@
 \subsubsection{Instrumenting iterators}
-
-In functional programming, iterators traverse containers lazily, meaning that the next element in the sequence is only computed when it is used by the application.
-This allows for the manipulation of virtually infinite sequences within finite memory.
-However, it implies that there is no full mapping of the container returned by an iterator in memory since each element is computed on the fly.
-Therefore, iterators are not serializable and \pytracer cannot save them to output traces.
-A workaround would be to convert iterators into explicit containers, and then return a new iterator on the explicit container.
-However, this would increase the memory footprint, possibly very importantly, and \pytracer therefore does not instrument iterators.
-
-\subsubsection{Instrumented code}
-\tristan{this text should be in 3.1.2. Given that it's quite specific to the code shown in the Listings, I think it could be part of the listing captions. }
-Listing~\ref{fig:wrapper_creation} shows how functions are instrumented.
-This function takes as inputs the information about the function to instrument (module name and full qualified name),
-the function itself and the actual name of the function. It then creates a wrapper around the actual wrapper
-(\texttt{generic\_wrapper}) that will dump the values. Instead of passing the function, we pass the identifier of 
-the function, which an unique 64-bits integer that references each Python object. This identifier is available
-with the \texttt{id} builtin function. it allows to get rid of aliases and to avoid instrumenting functions twice.
-
-Listing~\ref{fig:generic_wrapper} shows what the instrumented code does. 
-It first unpack function's information to get function's identifier to retrieve the original function.
-Then arguments are bound by creating a mapping from positional and keyword arguments to parameters, avoiding 
-conflicts and mispositioning. It also allows to get names of arguments for the visualization.
-Once arguments bound, they are dumped in the pickle file through the help of the \texttt{inputs} function.
-The function is then called with the right arguments and its returned valued dumped.
-Finally, the result of the original function is returned.
+In functional programming, iterators traverse containers lazily, meaning that the next element in the sequence is only computed when the application uses it.
+This technique allows for the manipulation of virtually infinite sequences within finite memory.
+However, it implies no complete mapping of the container returned by an iterator in memory since the application computes each element on the fly.
+Therefore, iterators are not serializable, and \pytracer cannot save them to output traces.
+A workaround would be to convert iterators into explicit containers and then return a new iterator on the explicit container.
+However, this would increase the memory footprint, possibly significantly, and \pytracer, therefore, does not instrument iterators.
 
@@
 \end{minipage}
-\caption{Illustration of the issue of using \texttt{frompyfunc} function to convert function to \texttt{ufunc}.
-Left: original code.
-Right: instrumented code.
-\tristan{This needs more explanation: where is the ufunc, what is the type returned by the original ufunc, and why does it crash in the instrumented version.}}
+\caption{Illustration of the issue of using \texttt{frompyfunc} function to convert function to \texttt{ufunc}. Left: original code. Right: instrumented code. 
+\tristan{This needs more explanation: where is the ufunc, what is the type returned by the original ufunc, and why does it crash in the instrumented version.} \Yohan{TODO}}
     \label{fig:numpy_array_index_issue}
@@
 \pytracer detects numerical instabilities by computing summary statistics across multiple application executions perturbed with numerical noise.
-While \pytracer's instrumentation, trace aggregation and visualization are applicable to various types of numerical noise, we experimented primarily with Monte-Carlo Arithmetic (MCA) as it is the most accurate model for floating-point errors.
+While \pytracer's instrumentation, trace aggregation, and visualization work with various types of numerical noise, we experimented primarily with Monte-Carlo Arithmetic (MCA) as it is the most accurate model for floating-point errors.
 
@@
 
-We enable MCA in Python programs via Verificarlo~\cite{verificarlo}, a clang-based compiler~\cite{lattner2008llvm}
-that replaces floating-point operations by a generic call to
-a configurable floating-point model. Several floating-point models, also called
-backends, are available~\cite{chatelain2019automatic,chatelain2019outils}.
+We enable MCA in Python programs via Verificarlo~\cite{verificarlo}, a clang-based compiler~\cite{lattner2008llvm} that replaces floating-point operations by a generic call to a configurable floating-point model.
+Several floating-point models, also called backends, are available~\cite{chatelain2019automatic,chatelain2019outils}.
 We leverage the fuzzy~\cite{kiar2020comparing} environment, a collection of software tools recompiled with Verificarlo.
-In particular, fuzzy provides MCA-instrumented versions of the Python interpreter as well as BLAS, LAPACK, NumPy, SciPy and scikit-learn,
-which allows for the injection of MCA perturbations to a wide range of existing scientific Python programs.
-Fuzzy is available in Verificarlo's GitHub organization at \href{https://github.com/verificarlo/fuzzy}{\url{github.com/verificarlo/fuzzy}}
-and provides Docker images for each MCA-enabled tools.
+In particular, fuzzy provides MCA-instrumented versions of the Python interpreter and BLAS, LAPACK, NumPy, SciPy, and scikit-learn, which allows for MCA injection perturbations to a wide range of existing scientific Python programs.
+Fuzzy is available in Verificarlo's GitHub organization at \href{https://github.com/verificarlo/fuzzy}{\url{github.com/verificarlo/fuzzy}} and provides Docker images for each MCA-enabled tool.
 
@@
 
-\pytracer stores traces in the pickle format, a compressed binary Python format to serialize Python objects.
-The main advantages of the pickle format compared to other serialization approaches such as marshal or JSON are its ability to serialize most Python objects, and its native compression.
+\pytracer stores the traces in the pickle format, a compressed binary Python format to serialize Python objects.
+The main advantages of the pickle format compared to other serialization approaches such as marshal or JSON are its ability to serialize most Python objects and its native compression.
 In addition, pickle writes Python objects sequentially according to their serialization order, which preserves the temporal ordering required by subsequent trace analyses.
@@
 
-Once traces are available, \pytracer sequentially parses them and computes the mean, standard deviation and
-number of significant digits (using Equation~\ref{eq:sig-digits}) of all saved values. These summary statistics are saved in an HDF5 file,
-a hierarchical format that facilitates browsing during the visualization.
+Once traces are available, \pytracer sequentially parses them and computes the mean, standard deviation, and the number of significant digits (using Equation~\ref{eq:sig-digits}) of all saved values.
+Pytracer saves these summary statistics in an HDF5 file, a hierarchical format that facilitates browsing during the visualization.
 This operation critically relies on the ordering of call input and output objects in the traces.
-It assumes that the application is deterministic, and in particular that it is single threaded and that the control flow does not depend on a random state.
+Furthermore, it assumes that the application is deterministic, and in particular, assumes it is single-threaded and that the control flow does not depend on a random state.
 Techniques to overcome this limitation are discussed in the discussion section.
@@
 that the call objects refer to the same function and stacktrace, and terminates the parsing otherwise.
-For each matching call object, \pytracer stores function arguments or returned values in a NumPy array from which statistics are computed. 
+For each matching call object, \pytracer stores function arguments or returned values in a NumPy array to compute statistics. 
 For compound objects such as tuples, dictionaries, or objects, it recursively parses the fields until finding
@@
 \subsection{Interactive visualization}
-
 The third main component of \pytracer is its interactive trace visualizer built with Plotly Dash~\cite{plotly}, a Python framework for web visualization.
 Plotly Dash abstracts the low-level details of web applications in a highly customizable development interface allowing to offload heavy computations to a server. 
-\subsubsection{General layout}
-Figure~\ref{fig:visu-layout} presents the general layout of the \pytracer visualizer, divided into 5 sub-components:
+Figure~\ref{fig:visu-layout} presents the general layout of the \pytracer visualizer, divided into five sub-components:
 \begin{enumerate}
- \item Timeline view: This view displays the values of each inputs and outputs for a given function at a given
-    invocation. By default, \pytracer shows the number of significant digits computed across the traces but the user 
-    can switch to the mean or the standard deviation. To differentiate inputs from outputs, the visualizer
-    uses an upper triangle for inputs and a down triangle for outputs. \pytracer represents internally all values 
-    as NumPy arrays.
-    In the case of non-scalar values or types that 
-    cannot be trivially cast into NumPy arrays, \pytracer splits the value in several variables. Hence, a class containing
-    $n$ floating point parameters will be transformed into $n$ variables. Each variable is prefixed with the original value
-    and postfixed with the name of the parameter. 
-    Finally, for non-scalar values (vectors or matrices), \pytracer shows the average of elements for non-scalar value (like vectors or matrices).
-Non-scalar values can be inspected with the Zoom view (see below).
- \item Gantt chart view: This view displays the call graph as a Gantt chart representing the instrumented functions. Each function call
-    is represented with a bar starting and ending at the function call and return.
+ \item Timeline view: This view displays the values of each input and output for a given function at a given invocation.
+By default, \pytracer shows the number of significant digits computed across the traces, but the user can switch to the mean or the standard deviation.
+The visualizer uses an upper triangle for inputs and a down triangle to differentiate inputs from outputs.
+\pytracer internally represents all values as NumPy arrays.
+In the case of non-scalar values or types that cannot be trivially cast into NumPy arrays, \pytracer splits the value into several variables.
+Hence, \pytracer will transform a class containing $n$ floating-point parameters into $n$ variables.
+Each variable is prefixed with the original value and postfixed with the name of the parameter.
+    Finally, for non-scalar values (vectors or matrices), \pytracer shows the average elements for non-scalar values (like vectors or matrices).
+non-scalar values can be inspected with the Zoom view (see below).
+ \item Gantt chart view: This view displays the call graph as a Gantt chart representing the instrumented functions.
+Each function call is represented with a bar starting and ending at the function call and return.
     The caller/callee relation is then determined by looking at the time overlaps.
     For example, in the figure, \texttt{function1} calls \texttt{function2} that itself calls \texttt{function4} and \texttt{function5}. 
-    This view provides insights on the calling context for each function since the same function can be called from different 
-    parents, which may influence numerical stability. 
+    This view provides insights on the calling context for each function since different parents functions can call the same function, which may influence numerical stability. 
  \item  Source code view: This view displays the source code file of the variable hovered in the timeline view. 
- \item  Zoom view: This view allows to closely examine non-scalar values, which is useful to see local differences that might
-    be masked by the averaging done in the timeline view. For example, a matrix can have instabilities around its diagonal but not in other regions.
+ \item Zoom view: This view allows closely examine non-scalar values, which is helpful to see local differences that might be masked by the averaging done in the timeline view.
+For example, a matrix can have instabilities around its diagonal but not in other regions.
     The visualizer also provides metrics about the value, such as the array shape, infinite norm, or condition number.
@@
 
-We evaluated \pytracer on widely-used Python libraries, namely SciPy, scikit-learn, and PyAFQ, demonstrating its its scalability and usability for real-world Python programs.
-For SciPy and Scikit-learn, we traced each application 5 times \tristanmod{by using the level 5 of the fuzzy ecosystem (cf.
-section~\ref{sec:fuzzy})}{ having activated MCA in the Python interpreter, BLAS, LAPACK, [CHECK THIS LIST]}.
-We repeated the experiment with two MCA modes, Random Rounding (RR) and Full MCA, and having enabled or disabled the instrumentation of NumPy's universal functions (\texttt{ufuncs}),
-resulting in 4 experiments for each application.
-We used the default virtual precision in Verificarlo, namely 24 bits for single-precision floating point values and 53 bits for double-precision values, which simulate machine error.
-For each library, we executed the software tests provided in the GitHub repositories \tristan{add a sentence for each library to summarize what they contain}.
+We evaluated \pytracer on widely-used Python libraries, namely SciPy, scikit-learn, and PyAFQ, demonstrating its scalability and usability for real-world Python programs. 
+SciPy is a Python-based ecosystem of open-source software for mathematics, science, and engineering, including NumPy.
+Scikit-learn is an open-source Python library for machine learning built upon SciPy.
+PyAFQ is a software package focused on automated delineation of the major fiber tracts in individual human brains, and quantification of the tissue properties within the tracts.
+For SciPy and scikit-learn, we traced each application five times, having activated MCA in the Python interpreter, BLAS, LAPACK, NumPy, SciPy, and scikit-learn.
+We repeated the experiment with two MCA modes, Random Rounding (RR) and Full MCA, and having enabled or disabled the instrumentation of NumPy's universal functions (\texttt{ufuncs}), resulting in 4 experiments for each application.
+We used the default virtual precision in Verificarlo, namely 24 bits for single-precision floating-point values and 53 bits for double-precision values, which simulates machine error.
+For each library, we executed the software tests provided in the GitHub repositories.
 
@@
 Tables~\ref{tab:pytracer_scipy_results_summary} and~\ref{tab:pytracer_sklearn_results_summary} summarize 
-the outcome of \pytracer experiments on SciPy and Scikit-learn.
+the outcome of \pytracer experiments on SciPy and scikit-learn.
 Each table reports on the tracing and trace aggregation steps with three possible outcomes: green for success, red for numerical error in the application, and orange for errors in the fuzzy noise injection or due to the instrumentation of NumPy \texttt{ufuncs}.
@@
 \label{sec:impact_mca_modes}
-
-Random Rounding perturbs only on the result of a floating-point operation while 
-Full MCA mode perturbs both the inputs and the result or the operation. 
+Random Rounding perturbs only the result of a floating-point operation, while Full MCA mode perturbs both the inputs and the operation's result. 
 Therefore, full MCA mode may trigger catastrophic cancellations while Random Rounding only introduces round-off errors which generally have a lesser impact.
-\Yohan{It is a strong assertion and I do not have literature to support it.
-Should be more precautionary.
-Even if, I believe, it's true.} \tristan{See how I reworded it.} Moreover, Random Rounding preserves exact operations,
-i.e., operations where the result can be exactly represented on the virtual precision, while Full MCA does not.
+Moreover, Random Rounding preserves exact operations, i.e., operations where the result can be exactly represented on the virtual precision, while Full MCA does not.
 
 \pytracer can only aggregate traces obtained from the same control flow path.
-In particular program branches triggered by an unstable floating-point comparison 
-lead to different control flows and result in parsing errors. 
+In particular, program branches triggered by an unstable floating-point comparison lead to different control flows and result in parsing errors.
 For example, comparing a residual error to a strict threshold in an iterative scheme or comparing the distance between two points generally results in unstable branches. 
-With Full MCA, even exact values such as integers represented with floating-point values are perturbed, which leads to a number of execution failures.
+With Full MCA, even exact values such as integers represented with floating-point values are perturbed, leading to many execution failures.
 For instance,  the \texttt{fft1} test from SciPy raised an \texttt{ValueError: operands could not be broadcast together with shapes (601,) (600,)} error due to an array shape mismatch.
-A closer inspection showed that one of the arrays involved in the error is created with the NumPy function \texttt{linspace} \tristan{I removed the linspace code, I think the most interesting part is what's going on in arange.
-Feel free to add it back if it's really necessary.} that itself calls function
-\texttt{arange} (Listing~\ref{fig:pyarray_range_code}).
+A closer inspection showed that one of the arrays involved in the error is created with the NumPy function \texttt{linspace} that itself calls function \texttt{arange} (Listing~\ref{fig:pyarray_range_code}).
 As can be seen in lines  3174-3178, the array size is stored in a floating-point value which will therefore be perturbed in Full MCA mode, as shown in Table~\ref{tab:mca_result_linspace}, resulting in array sizes that fluctuate
@@
 are due to this type of ``typing" errors.
-While they do not lead to any numerical issue, such typing errors should still be fixed to preserve code quality \tristan{Check this last sentence, we need to provide some sort of recommendations}.
-\tristan{how about opening a PR in numpy to fix this error?}
+While they do not lead to any numerical issue, such typing errors should still be fixed to preserve code quality.
+We provide solutions to help MCA better work with those cases in the discussion section.
+
+\tristan{Check this last sentence, we need to provide some sort of recommendations}. \tristan{how about opening a PR in numpy to fix this error?}
+\Yohan{For this case, they use the math.ceil to correctly round the number, I think the fix is more on the MCA side to
+correctly handle exact number than on the NumPy side.}
 

### 2021-10-28 paper.tex
First complete draft

@@
 \usepackage{minted} % Provides listing environment
+\usepackage[htt]{hyphenat}
+\usepackage{subcaption}
+% \usepackage{subfigure}
 
@@
 \begin{abstract}
-[abstract goes here]
+Numerical stability is a crucial requirement of reliable scientific computational codes.
+Despite the recent large numbers of tools dedicated to evaluating codes' numerical stability, analyzing a complete program remains a handy task for the user.
+To address this issue, we propose \pytracer, an automatic profiler for analyzing numerical instabilities of Python applications.
+\pytracer automatically instruments Python code to produce numerical traces that can be visualized through a Dash server, allowing an interactive visualization of numerical stability.
+\pytracer is designed to work with any random noise model that simulates numerical instabilities, and we demonstrate its usage with the Monte Carlo Arithmetic through the fuzzy ecosystem.
+Finally, we demonstrate that pytracer can handle intensively used Python scientific libraries such as NumPy, SciPy, and Scikit-learn on a representative set of tests, at low cost with an average slowdown $\times 3.5$.
 \end{abstract}
@@
 The scientific Python ecosystem is a central component of scientific
-analyses due to its rich data manipulation, array programming,
+analyses due to its rich offering of data manipulation, array programming,
 numerical analysis, and visualization tools. In particular, libraries such
@@
 PyTracer adopts a dynamic approach that evaluates numerical stability using program execution traces, enabling scaling to large programs without manual intervention.
-In contrast, theoretical approaches based on condition number or backward error analyses require detailed modeling of the program and its numerical implementation.
+In contrast, theoretical approaches based on condition numbers or backward error analysis require detailed modeling of the program and its numerical implementation.
 Similarly, static code analysis techniques such as Frama-C~\cite{cuoq2012frama}, Gappa~\cite{de2010certifying} or Flocq~\cite{boldo2011flocq} hardly scale to large codebases, particularly in dynamically-typed languages such as Python.
 
-PyTracer estimates the significant digits of Python floating-point variables by combining program traces obtained with different numerical perturbations, which requires (1) tracing floating-point computations along program executions, (2) generating numerically-perturbed executions, and (3) visualizing stability evaluations.
-PyTracer addresses these requirements with:
-Dynamic instrumentation of Python functions, modules, and classes through meta-programming
-A ``fuzzy" Python interpreter instrumented with Monte-Carlo arithmetic
-An interactive Plotly dashboard to visualize stability measures throughout program executions
+PyTracer estimates the number of significant digits of floating-point variables by combining program traces obtained with different numerical perturbations, which requires (1) tracing floating-point computations along program executions, (2) generating numerically-perturbed executions, and (3) visualizing stability evaluations.
+PyTracer addresses these requirements with (1) a dynamic instrumentation of Python functions, modules, and classes through meta-programming, (2) a ``fuzzy" Python interpreter instrumented with Monte-Carlo arithmetic, (3) an interactive Plotly dashboard to visualize stability measures throughout program executions.
 
 Through stability evaluations of 
-SciPy, scikit-learn, and pyAFQ~\cite{kruper2021evaluating} --- an analysis toolbox for diffusion magnetic resonance imaging --- we demonstrate PyTracer as a practical solution to review the numerical stability of extensive code bases.
+SciPy, scikit-learn, and PyAFQ~\cite{kruper2021evaluating} --- an analysis toolbox for diffusion magnetic resonance imaging --- we demonstrate PyTracer as a practical solution to review the numerical stability of extensive code bases.
 The remainder of this manuscript describes related approaches, presents the design of PyTracer, and demonstrates its potential in various use cases.
 
-\section{Related work}
+\section{Background and related work}
 
 Several tools have been and continue to be developed to assess numerical quality. Those tools can be divided into two main categories depending on whether they adopt a static or a dynamic approach.
-The static analysis produces theoretically valid error bounds, while dynamic analysis is generally more scalable, although it only provides experimental estimations.
+Static analysis produces theoretically valid error bounds, while dynamic analysis is generally more scalable, although it only provides experimental estimations.
 \pytracer adopts the dynamic approach due to its scalability to large existing code bases.
-Dynamic approaches typically rely on the tracing of floating-point computations to detect instabilities and visualize them.
-The remainder of this section reviews existing approaches for each of these three steps.
+Dynamic approaches typically trace floating-point computations, detect instabilities in traces, and visualize summary statistics about instabilities.
+The remainder of this section reviews existing approaches for each of these steps.
 
@@
 \subsection{Numerical tracing techniques}
-Tools to trace floating-point computations for C, C++, or FORTRAN programs are plethora due to the prevalence of these languages in High-Performance Computing (HPC). 
+Tools to trace floating-point computations for C, C++, or FORTRAN programs are numerous due to the prevalence of these languages in High-Performance Computing (HPC). 
 The main tracing techniques are source-to-source, compiler-based transformations, and dynamic binary instrumentation.
 
-The Source-to-source technique requires a rewriting of the application to use modify floating-point types.
+The source-to-source technique requires a rewriting of the application to modify floating-point types. Among frameworks that adopted this technique,
 CADNA~\cite{jezequel2008cadna} is a library for C, C++ and Fortran implementing the CESTAC~\cite{vignes1993stochastic} stochastic arithmetic.
-pLiner uses source-to-source transformation at the Abstract Syntax Tree (AST)  level to rewrite parts of code with higher precision. 
 Shaman~\cite{demeure_phd} is a C++ library that uses a first-order error model to propagate numerical error. 
 MCAlib~\cite{frechtling2015mcalib} is a C library that implements the Monte Carlo Arithmetic (MCA)~\cite{parker1997monte} using the MPFR~\cite{fousse2007mpfr} library.
-The work in~\cite{tang2016software} proposed a source-to-source framework for executing targeted code in infinite and fixed precision with and without using stochastic arithmetic.
+Finally, the work in~\cite{tang2016software} proposed a source-to-source framework for executing targeted code in infinite and fixed precision with and without  stochastic arithmetic.
 
@@
 Verificarlo~\cite{verificarlo} is a compiler that supports different types of arithmetic instrumentations, including MCA. 
-The work in ~\cite{bao2013fly} modified the GNU Compiler Collection (GCC) to track local floating-point errors across executions.
-pLiner~\cite{guo2020pliner} is a root cause analyzer based on the Clang compiler that detects floating-point operations responsible for result variability.
+The work in~\cite{bao2013fly} modified the GNU Compiler Collection (GCC) to track local floating-point errors across executions.
+pLiner~\cite{guo2020pliner} is a root cause analyzer based on the Clang compiler that detects floating-point operations responsible for result variability using a source-to-source transformation at the Abstract Syntax Tree (AST)  level to rewrite parts of code with higher precision.
 PFPSanitizer~\cite{chowdhary2020debugging,chowdhary2021parallel}, is a compiler that uses parallel shadow execution to detect numerical issues using higher precision.
@@
 Dynamic Binary Instrumentation (DBI) operates on an executable directly, without the need for recompilation or manual changes, and is thus
-transparent to the programming language used. However, working at a binary level makes it difficult to access high-level information needed
-to debug and understand the source code logic. In particular, analyzing Python code with DBI is feasible but provides minimal insights on the stability of specific Python code sections.
+transparent to the programming language used. 
 CraftHPC~\cite{lam2013dynamic} uses DBI to detect catastrophic cancellations at runtime.
@@
 
-Being agnostic to the programming language is a serious advantage of the DBI method compare to source-to-source and compiler-bases methods.
+Being agnostic to the programming language is a serious advantage of the DBI method compared to source-to-source and compiler-bases methods.
 However, working at a binary level makes it difficult to access high-level information needed to debug and understand the source code logic.
-On the other hand, Source-to-source presents the advantage of having a fine-grained control on code analyzed but lacks scalability, as rewriting large codes can be a tedious task if done by hand.
+Conversely, the source-to-source approach provides a fine-grained control on the code being analyzed, bu itt lacks scalability, as rewriting large codes can be a tedious task.
 Finally, the compiler-based approach takes advantage of the best of both by being automatic and having access to high-level information.
-However, like source-to-source, the compiler-based method is not suitable for analyzing closed-source proprietary libraries.
+However, like source-to-source, the compiler-based method is not suitable for analyzing closed-source libraries.
 
@@
 or memory consumption (memprofile). 
-Anteater~\cite{faust2019anteater} is a Python tracer tool that aims at debugging Python applications. 
-It operates source transformation at the AST level but only deals with native numeric Python types.
-Moreover, the user needs to tag each variable to trace manually. Finally, according to the authors, Anteater does not scale to large traces.
-However, we can compare the methodology used by cProfile, memprofile, and Anteater against the one used in Pytracer.
-These tools use instrumentation based on decorators, a Python mechanism allowing to instrument a function by adding a line over a function declaration.
-While this method is proper when targeting specific functions, it becomes time-consuming when applied to many functions since one needs to tag functions manually, which is not feasible for large codebases where potentially unstable code sections are unknown.
+Anteater~\cite{faust2019anteater} is a Python tracer tool to debug Python applications. 
+It performs source transformations at the AST level but only deals with native numeric Python types.
+Moreover, the user needs to manually tag each variable to trace. Finally, according to the authors, Anteater does not scale to large traces.
+cProfile, memprofile, and Anteater use Python decorators as the main instrumentation technique, a Python mechanism to instrument a function by adding a line over a function declaration.
+While this method is appropriate when targeting specific functions, it is not feasible for large code bases where the location of potentially unstable code sections is unknown.
 
@@
 
-Stochastic arithmetic is a theoretical model that exploits randomness to estimate the floating-point format's numerical instabilities.
-The idea is to treat round-off errors as a random variable for then using classical statistical tools to study them.
-
-The first published complete stochastic arithmetic framework is CESTAC~\cite{vignes1993stochastic}.
-Each floating-point computation is run multiple times in this method, switching the rounding mode to either round-up or round-down with
-an equal probability.
+Stochastic arithmetic leverages randomness to estimate numerical instabilities coming from the use of floating-point representations. The main idea is to treat round-off errors 
+% \tristan{only round-off errors or all numerical errors?} 
+as random variables and to characterize them statistically.
+
+The first published complete stochastic arithmetic framework was CESTAC~\cite{vignes1993stochastic}, where each floating-point computation is performed multiple times with different rounding modes: round-up or round-down.
 From these stochastic samples, one can then derive the number of significant digits in the computed result.
-In addition, the Discrete Stochastic Arithmetic (DSA~\cite{vignes2004discrete}) extends the CESTAC method to comparison operators implemented in the CADNA library.
-
-The Monte Carlo Arithmetic works on the same principle but introduces two differences:
-a virtual precision parameter allowing to simulate reduced working precision and different \texttt{modes} to introduce perturbations
-on the inputs or the output.
-MCA simulates round-off errors by introducing random perturbations in floating-point computations and replaces each floating-point number with its stochastic counterpart:
+Discrete Stochastic Arithmetic~\cite{vignes2004discrete} extends CESTAC to comparison operators implemented in the CADNA library.
+
+Monte Carlo Arithmetic (MCA)~\cite{parker1997monte} uses the same principle but introduces two differences:
+(i) a virtual precision parameter, allowing to simulate reduced working precision,  and (ii) different perturbation modes, to introduce perturbations
+on function inputs or output.
+MCA simulates round-off errors by introducing random perturbations in floating-point computations. It replaces each floating-point number with its stochastic counterpart:
 \[
@@
 \]
-where $\beta$ is the basis, $t$ the virtual precision and $\xi \in (-\frac{1}{2},\frac{1}{2})$ a random variable.
-Virtual precision is one strength of the MCA method since it allows simulating reduced working precision.
-MCA comes with three modes: Random Rounding (RR), Precision Bounding (PB), and FullMCA, which perturb either the output, the inputs, or both with the $inexact$ function.
-While the RR mode is equivalent to stochastic rounding, PB mode allows identifying catastrophic cancellations.
-
-MCA provides a formula \tristan{is this formula specific to MCA or can it also be applied to CESTAC?} \Yohan{Yes, CESTAC supposes that the random variable is normal and so use a different formulation} to compute the number of significant digits:
+where $\beta$ is the number base, $t$ the virtual precision and $\xi \in (-\frac{1}{2},\frac{1}{2})$ is a uniform variable.
+Virtual precision allows for the simulation of reduced working precision.
+MCA can be applied in three modes: Random Rounding (RR), Precision Bounding (PB), and full MCA, which respectively perturb either the output, the inputs, or both with the $inexact$ function.
+While the RR mode is equivalent to stochastic rounding, the PB mode allows identifying catastrophic cancellations.
+
+In stochastic arithmetic, numerical error is measured as the number of significant digits $s$ estimated among the sampled values.
+A common formula to determine this number from MCA samples is the one reported in~\cite{parker1997monte}:
 \begin{equation}
@@
 \end{equation}
-where $\sigma$ and $\mu$ are respectively the empirical standard deviation and expected value of a variable $x$ evaluating 
-several times with MCA. 
-Note that this formula gives an approximation of the real. Recently, Sohier et al. ~\cite{sohier2018confidence} introduced a 
-general theoretical framework that includes DSA and MCA formulae and allows to obtain associated rigorous confidence intervals on the number of significant digits estimated.
-
-\subsubsection{Uncertainty and sensitivity analysis}
-
-Uncertainty analysis (UA) is a method to derive the output distribution response from an input distribution.
-The idea is to model uncertainty on data due to limited precision measurement, for example, by a probability distribution, and to estimate the impact on the result. 
-Sensitivity analysis (SA) is quite close to uncertainty analysis but differs from the scale observed.
-While uncertainty analysis attempts to describe the whole output distribution, sensitivity analysis measures the local response to a small perturbation~\cite{loucks2017water}. 
-Several approaches for UA and SA exist, among them differential analysis, response surface methodology, Monte Carlo analysis, and variance decomposition (see~\cite{helton2006survey}).
-In particular, Monte Carlo Analysis is a sampling-based technique that samples inputs space to estimate output response.
+where $\mu$ and $\sigma$ are the sample mean and standard deviation of a variable sampled with MCA.
+Recent variations of this formula that also provide confidence intervals are discussed in~\cite{sohier2018confidence}.
+
+\subsubsection{Uncertainty, sensitivity, and random seed analysis}
+
+Uncertainty analysis (UA) is a method to estimate the output distribution given an input distribution.
+Sensitivity analysis (SA) is a variation of UA that measures the local response to a small perturbation~\cite{loucks2017water}. 
+Several approaches for UA and SA exist, among them differential analysis, response surface methodology, Monte Carlo analysis, and variance decomposition (see~\cite{helton2006survey} for a review).
+In particular, Monte Carlo analysis is a sampling-based technique that samples inputs space to estimate output response.
 Monte Carlo analysis shares similarities with Monte Carlo Arithmetic.
 For instance, the PRECISE framework~\cite{chaitin1996lectures} shares with MCA the idea of varying virtual precision to estimate output sensitivity.
-
-\subsubsection{Random seed sensitivity}
-
-The quality of a Random Number Generator is a crucial characteristic when dealing with stochastic model and differ from cryptography requirements.
-For numerical simulation, an RNG of quality must have a good tradeoff between performance, period, correlation, or uniformity~\cite{james2020review}.
-Poor quality RNGs may have a substantial impact on results~\cite{click2011quality}.
+Furthermore, the quality of a Random Number Generator is a crucial characteristic when dealing with stochastic model and differ from cryptography requirements.
+For numerical simulation, a good RNG provides a tradeoff between performance, period, correlation, or uniformity~\cite{james2020review}.
+On the other hand, poor quality RNGs may have a substantial impact on results~\cite{click2011quality}.
 First, measuring variation induced by seed is a good indicator of program stability that we can compare against variability induced by floating-point arithmetic.
-\Yohan{This section lacks solid arguments. Needs improvement}
 
@@
 
-The visualization covers a wide range of specific domains in the numerical simulation area, from general-purpose numerical visualization with tools
-like VTK~\cite{schroeder2000visualizing}, to topological data analysis~\cite{tierny2018topological}, including matrix~\cite{wu2008matrix} or tensor~\cite{kindlmann2006diffusion} visualization.
-We review here tools dedicated to the analysis of the numerical variability induced by the floating-point model.
-We can first highlight that despite the large number of existing tools dedicated to pinpoint source code instructions, few of them allow the user to have a global view of the numerical accuracy of their computations or compare several executions of the same program under various perturbations.
-
-Veritracer~\cite{chatelain2018veritracer} was the first tool to propose an embedded visualizer to visualize the numerical stability over time for C, C++, and Fortran codes.
-It is a trace-based tool built as an extension of Verificarlo~\cite{verificarlo} that offers contextual information about variables traced to allow the user to identify instabilities quickly.
-However, it does not offer a dynamic interface neither takes into account information about high-level structures like \texttt{struct} or \texttt{array}.
-FPAvizual~\cite{gu2014fpavisual} is a tool for visualizing the effects of floating-point arithmetic but only for educational purposes.
+Visualization covers a wide range of numerical simulation domains, from general-purpose numerical visualization with tools
+such as VTK~\cite{schroeder2000visualizing}, to topological data analysis~\cite{tierny2018topological}, including matrix~\cite{wu2008matrix} or tensor~\cite{kindlmann2006diffusion} visualization.
+We review here tools dedicated to the analysis of numerical variability induced by the floating-point model.
+Despite the large number of existing tools  to locate unstable source code sections, few of them allow the user to have a global view of the numerical accuracy of their computations or compare several executions of the same program under various perturbations.
+
+Veritracer~\cite{chatelain2018veritracer} was the first tool to propose an embedded visualizer of numerical stability over time for C, C++, and Fortran codes.
+It is an extension of Verificarlo~\cite{verificarlo} that offers contextual information about variables traced to allow the user to identify instabilities quickly.
+However, it does not offer a dynamic interface and does not include information about high-level structures such as \texttt{struct} or \texttt{array}.
+FPAvizual~\cite{gu2014fpavisual} visualizes the effects of floating-point arithmetic but only for educational purposes.
 Anteater~\cite{faust2019anteater} proposes a visualizer for Python codes, but as mentioned previously, it only deals with native Python types, and the user needs to select variables to trace manually.
-However, Anteater provides an accurate reflection around visual debugging beyond floating-point analysis, which has inspired the design of \pytracer's visualization interface.
+However, Anteater provides an insightful reflection
+% \tristan{It's a bit vague. Do you simply mean: ``Anteater's GUI inspired the design of \pytracer's interface"?} 
+around visual debugging beyond floating-point analysis, which has inspired the design of \pytracer's visualization interface.
 
@@
 The PyTracer workflow follows a three-step approach (Figure~\ref{fig:workflow}).
-First, when a Python application is loaded, \pytracer instruments using ``monkey patching", a technique to modify Python programs without editing their source code.
-The instrumentation replaces all the functions with a wrapper that saves their arguments and outputs in a trace file using ``pickle", Python's object serialization mechanism.
+First, \pytracer instruments applications using ``monkey patching", a technique to modify Python programs without editing their source code.
+The instrumentation replaces all the functions with a wrapper that saves their arguments and returned value in a trace file using ``pickle", Python's object serialization mechanism.
 \pytracer then aggregates trace files obtained from multiple perturbed executions, computing summary statistics about each traced variable.
@@
     \includegraphics[width=\linewidth]{figure/workflow.pdf}
-    \caption{Pytracer workflow \tristan{move the execution and noise injection to step 2}}
+    \caption{Pytracer workflow}
     \label{fig:workflow}
@@
 By default, \pytracer instruments all the attributes
-in a given module \tristan{not only the functions?} \Yohan{No, you can have class definitions or instances that need to be wrapped}, except the special ones of the form \texttt{\_\_*\_\_}.
-However, some attributes are not writable; in this case, \pytracer preservers the original attributes and warns the user. The user can also restrict the list of attributes to trace through
+in a given module except the special ones of the form \texttt{\_\_*\_\_}.
+However, some attributes are not writable; in this case, \pytracer preservers the original attributes and warns the user. The user can also restrict the list of traced attributes through
 an inclusion/exclusion mechanism.
-The main advantage of this instrumentation approach is the lack of required modification in the application source code, in contrast with decorator-based approaches, which enable instrumentation in read-only environments such as Singularity containers or HPC clusters.
+The main advantage of this instrumentation approach is the lack of required modification in the application source code, in contrast with decorator-based approaches, which is scalable and useful in read-only environments such as Singularity containers or HPC clusters.
 
@@
 
-Python implements default \texttt{finder} and \texttt{loader} classes and search paths for importing a module, but it also provides a way to create custom \texttt{finder} and \texttt{loader} classes.
-To register a new \texttt{finder} class, one needs to add it to the \texttt{sys.meta\_path} list.
+Python supports custom \texttt{finder} classes, registered in the \texttt{sys.meta\_path} list.
 When Python encounters an \texttt{import} statement, it first looks for a binding in the \texttt{sys.modules}
-and then iterates over \texttt{sys.meta\_path}.
-Python queries each \texttt{finder} class successively until it finds the module or reaches the end of the list, raising a \texttt{ModuleNotFoundError}.
-Then, \pytracer adds a custom \texttt{finder} class at the head of the list that intercepts
+and then iterates over the \texttt{finder} classes in \texttt{sys.meta\_path} until it finds the module to import. \pytracer adds a custom \texttt{finder} class at the head of the list that intercepts
 the module import and creates the module with a custom \texttt{loader} class.
 
-\pytracer's \texttt{loader} class first loads the original module then copies it as a new instance of the \texttt{ModuleType} class.
+\pytracer's \texttt{loader} class first loads the original module, then copies it as a new instance of the \texttt{ModuleType} class.
 It then calls the appropriate instrumentation function for each module attribute depending on its type (function, class, or instances).
-Next, \pytracer replaces the original module with its instrumented counterpart in the \texttt{sys.modules} map once it has instrument all the attributes.
+Then, \pytracer replaces the original module with its instrumented counterpart in the \texttt{sys.modules} map once it has instrument all the attributes.
 Hence, the calling convention remains unchanged, and the application will transparently call the instrumented module.
-Finally, Pytracer updates all references to the original module that an object may hold.
-For example, functions have a \texttt{\_\_globals\_\_} attribute that contains references to internal objects that the function needs.
-Since those references point to non-instrumented objects, Pytracer must update them.
-\tristan{is the non-instrumented version ever added to sys.modules? If so, could this lead to race conditions? If not, replace with ``adds the instrumented module to the sys.modules map"}. 
-\Yohan{Yes, it replaces the original module.
+Finally, Pytracer updates all existing references to the original module, such as the ones in \texttt{\_\_globals\_\_} function attributes that contain references to internal function objects.
+
+% \tristan{is the non-instrumented version ever added to sys.modules? If so, could this lead to race conditions? If not, replace with ``adds the instrumented module to the sys.modules map"}. 
+% \Yohan{Yes, it replaces the original module.
 You can't have a race-condition since sys.modules is a dict with only one value for a given key.
@@
 
-Module functions are the most straightforward case to treat.
-For each function, \pytracer's loader class creates a wrapper function, dynamically compiles it with the compile builtin function, and substitutes it for the original module function.
-However, we cannot apply this technique to callable class instances, i.e., class instances that have the \texttt{\_\_call\_\_} attribute but are not of the \texttt{FunctionType} type.
+For each function, \pytracer's \texttt{loader} class creates a wrapper function, dynamically compiles it with the compile builtin function, and substitutes it for the original module function.
+This simple technique
+cannot be applied to callable class instances, i.e., class instances that have the \texttt{\_\_call\_\_} attribute but are not of the \texttt{FunctionType} type.
 Indeed, applying the wrapper technique would 1) modify the type of the class instance to \texttt{FunctionType}, which could cause syntactic and semantic bugs, and 2) mask class attributes, leading to \texttt{AttributeError} exceptions.
@@
 When the \texttt{\_\_call\_\_} attribute is not writable,  Pytracer does not instrument the class and returns a warning.
-Listings~\ref{fig:wrapper_creation} and ~\ref{fig:generic_wrapper} show \pytracer's wrapper creation function.
-
-\tristan{add docstrings to all Python code examples and clarify captions accordingly: you don't need to explain the meaning of each attribute in the caption if it's in the docstring.
+Listings~\ref{fig:wrapper_creation} and~\ref{fig:generic_wrapper} show \pytracer's wrapper creation function.
+
+% \tristan{add docstrings to all Python code examples and clarify captions accordingly: you don't need to explain the meaning of each attribute in the caption if it's in the docstring.
 The caption can focus on the main functionality, reusing the text currently in 3.1.5.}
-\Yohan{TODO}
-
-Listing~\ref{fig:wrapper_creation} shows how functions are instrumented.
-This function takes as inputs the information about the function to instrument (module name and full qualified name),
-the function itself, and the actual name of the function. It then creates a wrapper around the actual wrapper
-(\texttt{generic\_wrapper}) that will dump the values.
+% \Yohan{TODO}
+
+% Listing~\ref{fig:wrapper_creation} shows how functions are instrumented.
+% This function takes as inputs the information about the function to instrument (module name and full qualified name),
+% the function itself, and the actual name of the function. It then creates a wrapper around the actual wrapper
+% (\texttt{generic\_wrapper}) that will save the values in trace files.
 Instead of passing the function, we pass the function's identifier, which is a unique 64-bits integer that references each Python object.
 This identifier is available
-with the \texttt{id} builtin function. it allows to get rid of aliases and to avoid instrumenting functions twice.
-
-Listing~\ref{fig:generic_wrapper} shows what the instrumented code does. 
-It first unpacks the function's information to get the function's identifier to retrieve the original function.
-Then arguments are bound by creating a mapping from positional and keyword arguments to parameters, avoiding conflicts and mispositioning.
+% with the \texttt{id} builtin function. it allows to get rid of aliases and to avoid instrumenting functions twice.  \tristan{Summarize this paragraph in the figure caption}
+
+% Listing~\ref{fig:generic_wrapper} shows what the instrumented code does. 
+% It first unpacks the function's information to get the function's identifier to retrieve the original function.
+% Then arguments are bound by creating a mapping from positional and keyword arguments to parameters, avoiding conflicts and mispositioning.
 It also allows getting names of arguments for the visualization.
-Once bound, the \texttt{inputs} function dumps the arguments in the pickle file.
-Finally, Pytracer calls the function with the correct arguments, dumps the result, and returns it.
+% Once bound, the \texttt{inputs} function dumps the arguments in the pickle file.
+% Finally, Pytracer calls the function with the correct arguments, dumps the result, and returns it. \tristan{Summarize this paragraph in the figure caption}
 
@@
 \begin{lstlisting}[language=Python,style=customPython]
-def get_wrapper_function(function_module, function_qualified_name, function, function_wrapper_name):
+def get_wrapper_function(module, qualname, name, function):
+    """Returns the instrumented function as a string.
+    This string will be compiled with the compile builtin function
+
+    Parameters:
+        module: Name of the function module
+        qualname: Qualified name of the function
+        name: Name of the function
+        function: Python object function
+
+    Returns:
+        wrapper_code: The code source of the wrapper
+    """
     function_id = id(function)
@@
     \caption{Function to create the instrumented version of a function.
-    This function returns the instrumented function as a string (\texttt{wrapper\_code}) that 
-    will be turned into a Python object with the \texttt{compile} built-in function.}
+    \pytracer uses the identifier of the function instead of the 
+    actual function to get rid of aliases and duplicated instrumentations.}
     \label{fig:wrapper_creation}
@@
 def generic_wrapper(self, info, *args, **kwargs):
+    """Generic wrapper dumping inputs and outputs of the wrapped function.
+    The id_dict dict keeps a mapping between the original function identifier
+    and itself. Arguments are binded to avoid mispositioning.
+    Returns the actual output of the wrapped function.
+
+    Parameters:
+        info: Tuple with the function's id, function's module and function's name
+        *args: Positional calling arguments
+        **kwargs: Keyword calling arguments
+
+    Returns:
+        outputs: Outputs of the wrapped function
+    """
     fid, fmodule, fname = info
@@
 \end{lstlisting}
-    \caption{\pytracer's wrapper function. 
-    The \texttt{original\_function\_cache} maintains a mapping between the original function and its identifier (available through 
-    \texttt{id} built-in function). Once the original function retrieved, the arguments are saved to the traces (through function 
-    \texttt{self.inputs}). The actual function is called and the result is saved (function \texttt{self.outputs}) then returned.
+    \caption{\pytracer's wrapper function that dumps
+    the inputs and outputs of the wrapped function.
+    \pytracer binds arguments to the function signature to avoid
+    mispositioning and to have actual names for the visualization.
+    The wrapper returns the actual output.
     }
@@
 This instrumentation preserves class types, avoiding type mismatches in the instrumented application.
-However, some classes, in particular base types, contain read-only attributes that cannot be instrumented. 
-By default, \pytracer returns a warning when it encounters such classes, 
-but it treats NumPy's universal functions (\texttt{ufuncs}) specifically since they are ubiquitous in scientific computing. 
-NumPy's \texttt{ufuncs} are vectorized element-wise operators that apply to multidimensional arrays. 
+However, some classes, in particular base types and NumPy's universal functions (\texttt{ufuncs}), contain read-only attributes that cannot be instrumented. 
+By default, \pytracer returns a warning when it encounters such classes.
+
+\subsubsection{Instrumenting instances}
+
+Pytracer automatically instruments the instances since it instruments the classes, but it cannot instruments or instantiates some classes like \texttt{ufunc}, although their instrumentation is desirable given their pervasiveness in scientific computing.
+Indeed, NumPy's \texttt{ufuncs} are vectorized element-wise operators that apply to multidimensional arrays, 
+including the set of elementary mathematical functions.
 In particular, all the element-wise elementary mathematical functions are \texttt{ufuncs}.  
-To increase performance, \texttt{ufuncs} are implemented in C, which prevents their instrumentation using the technique described previously. 
-Instead, \pytracer uses NumPy's \texttt{frompyfunc} helper function to create an instrumented \texttt{ufunc} that wraps the original one.
-This approach works in many cases but it requires the instrumented function to return objects of type \texttt{PyObject}, 
-which may create errors (Listing~\ref{fig:numpy_array_index_issue}). 
-As a last resort, the user may disable \texttt{ufunc} tracing in Pytracer.
+To increase performance, \texttt{ufuncs} are implemented in C, which prevents their instantiation.
+
+To overcome this issue, \pytracer wraps the instances into a transparent wrap class (\texttt{twc}) that overloads
+1) the \texttt{\_\_getattribute\_\_} that is called when one is accessing an instance's attribute.
+The \texttt{twc} returns the queried attribute of the instance instead of returning its attributes, allowing transparent access to the instance.
+2) the \texttt{\_\_call\_\_} functions that is called when one
+is calling the function (through the () operator). The \texttt{twc} calls the \texttt{generic\_wrapper} to saves 
+inputs and outputs as for classical functions. Finally, \pytracer overloads the \texttt{type} built-in function
+to preserve the type of the wrapped instance.
 
 \subsubsection{Instrumenting iterators}
+
 In functional programming, iterators traverse containers lazily, meaning that the next element in the sequence is only computed when the application uses it.
-This technique allows for the manipulation of virtually infinite sequences within finite memory.
-However, it implies no complete mapping of the container returned by an iterator in memory since the application computes each element on the fly.
-Therefore, iterators are not serializable, and \pytracer cannot save them to output traces.
+This technique allows for the manipulation of virtually infinite sequences with finite memory.
+However, it implies that no complete mapping of the container returned by an iterator exists in memory since the application computes each element on the fly.
+Therefore, iterators are not serializable and \pytracer cannot save them to output traces.
 A workaround would be to convert iterators into explicit containers and then return a new iterator on the explicit container.
-However, this would increase the memory footprint, possibly significantly, and \pytracer, therefore, does not instrument iterators.
-
-\begin{listing}
-\begin{minipage}[t]{0.4\linewidth}
-    \begin{lstlisting}[language=Python,style=customPython]
->>> import numpy as np
->>> x = np.array(range(10))
->>> index = np.array([1,-1],dtype=int)
->>> x[index]
->>> array([1, 9])
-    \end{lstlisting}
-\end{minipage}
-\begin{minipage}[t]{0.4\linewidth}
-    \begin{lstlisting}[language=Python,style=customPython]
->>> import numpy as np
->>> x = np.array(range(10))
->>> index = np.array([1,-1], dtype=object)
->>> x[index]
-Traceback (most recent call last):
-  File "<stdin>", line 1, in <module>
-IndexError: arrays used as indices must be of integer (or boolean) type
-    \end{lstlisting}
-\end{minipage}
-\caption{Illustration of the issue of using \texttt{frompyfunc} function to convert function to \texttt{ufunc}. Left: original code. Right: instrumented code. 
-\tristan{This needs more explanation: where is the ufunc, what is the type returned by the original ufunc, and why does it crash in the instrumented version.} \Yohan{TODO}}
-    \label{fig:numpy_array_index_issue}
-\end{listing}
+However, this would increase the memory footprint significantly.
+\pytracer therefore does not instrument iterators.
+
+% \begin{listing}
+% \begin{minipage}[t]{0.4\linewidth}
+%     \begin{lstlisting}[language=Python,style=customPython]
+% >>> import numpy as np
+% >>> x = np.array(range(10))
+% >>> index = np.array([1,-1],dtype=int)
+% >>> x[index]
+% >>> array([1, 9])
+%     \end{lstlisting}
+% \end{minipage}
+% \begin{minipage}[t]{0.4\linewidth}
+%     \begin{lstlisting}[language=Python,style=customPython]
+% >>> import numpy as np
+% >>> x = np.array(range(10))
+% >>> index = np.array([1,-1], dtype=object)
+% >>> x[index]
+% Traceback (most recent call last):
+%   File "<stdin>", line 1, in <module>
+% IndexError: arrays used as indices must be of integer (or boolean) type
+%     \end{lstlisting}
+% \end{minipage}
+% \caption{Illustration of the issue of using \texttt{frompyfunc} function to convert function to \texttt{ufunc}. Left: original code. Right: instrumented code. 
+% \tristan{This needs more explanation: where is the ufunc, what is the type returned by the original ufunc, and why does it crash in the instrumented version.} \Yohan{TODO}}
+%     \label{fig:numpy_array_index_issue}
+% \end{listing}
 
@@
 
-\pytracer detects numerical instabilities by computing summary statistics across multiple application executions perturbed with numerical noise.
-While \pytracer's instrumentation, trace aggregation, and visualization work with various types of numerical noise, we experimented primarily with Monte-Carlo Arithmetic (MCA) as it is the most accurate model for floating-point errors.
+\pytracer detects numerical instabilities by computing summary statistics across multiple executions perturbed with numerical noise.
+While \pytracer's instrumentation, trace aggregation, and visualization work with various types of numerical noise, we experimented primarily with Monte-Carlo Arithmetic (MCA) as it is an accurate model for floating-point errors.
 
@@
 Several floating-point models, also called backends, are available~\cite{chatelain2019automatic,chatelain2019outils}.
-We leverage the fuzzy~\cite{kiar2020comparing} environment, a collection of software tools recompiled with Verificarlo.
-In particular, fuzzy provides MCA-instrumented versions of the Python interpreter and BLAS, LAPACK, NumPy, SciPy, and scikit-learn, which allows for MCA injection perturbations to a wide range of existing scientific Python programs.
-Fuzzy is available in Verificarlo's GitHub organization at \href{https://github.com/verificarlo/fuzzy}{\url{github.com/verificarlo/fuzzy}} and provides Docker images for each MCA-enabled tool.
+We leverage the ``fuzzy"~\cite{kiar2020comparing} environment, a collection of software tools recompiled with Verificarlo.
+In particular, fuzzy provides MCA-instrumented versions of the Python interpreter as well as of the BLAS, LAPACK, NumPy, SciPy, and scikit-learn libraries, which enables MCA for a wide range of existing scientific Python programs.
+Fuzzy is available in Verificarlo's GitHub organization at \href{https://github.com/verificarlo/fuzzy}{\url{github.com/verificarlo/fuzzy}}.
 
@@
 
-\pytracer stores the traces in the pickle format, a compressed binary Python format to serialize Python objects.
+\pytracer stores traces in the pickle format, a compressed binary Python format to serialize Python objects.
 The main advantages of the pickle format compared to other serialization approaches such as marshal or JSON are its ability to serialize most Python objects and its native compression.
-In addition, pickle writes Python objects sequentially according to their serialization order, which preserves the temporal ordering required by subsequent trace analyses.
+In addition, pickle writes Python objects sequentially, which preserves the temporal ordering required by subsequent trace analyses.
 
@@
 
-Once traces are available, \pytracer sequentially parses them and computes the mean, standard deviation, and the number of significant digits (using Equation~\ref{eq:sig-digits}) of all saved values.
+Once traces are available, \pytracer sequentially parses them and computes the mean, standard deviation, and the number of significant digits (computed using Equation~\ref{eq:sig-digits}) of all saved values.
 Pytracer saves these summary statistics in an HDF5 file, a hierarchical format that facilitates browsing during the visualization.
@@
 Furthermore, it assumes that the application is deterministic, and in particular, assumes it is single-threaded and that the control flow does not depend on a random state.
-Techniques to overcome this limitation are discussed in the discussion section.
+% Techniques to overcome this limitation are discussed in the discussion section.
 
@@
 
-We evaluated \pytracer on widely-used Python libraries, namely SciPy, scikit-learn, and PyAFQ, demonstrating its scalability and usability for real-world Python programs. 
-SciPy is a Python-based ecosystem of open-source software for mathematics, science, and engineering, including NumPy.
-Scikit-learn is an open-source Python library for machine learning built upon SciPy.
-PyAFQ is a software package focused on automated delineation of the major fiber tracts in individual human brains, and quantification of the tissue properties within the tracts.
+We evaluated \pytracer on widely-used Python libraries, namely: SciPy, the main library for scientific computing in Python; scikit-learn, a reference machine-learning framework; PyAFQ, a neuroimaging analysis toolbox.
 For SciPy and scikit-learn, we traced each application five times, having activated MCA in the Python interpreter, BLAS, LAPACK, NumPy, SciPy, and scikit-learn.
-We repeated the experiment with two MCA modes, Random Rounding (RR) and Full MCA, and having enabled or disabled the instrumentation of NumPy's universal functions (\texttt{ufuncs}), resulting in 4 experiments for each application.
+We repeated the experiment with two MCA modes, Random Rounding (RR) and Full MCA, resulting in 2 experiments for each application.
 We used the default virtual precision in Verificarlo, namely 24 bits for single-precision floating-point values and 53 bits for double-precision values, which simulates machine error.
-For each library, we executed the software tests provided in the GitHub repositories.
+For each library, we executed the software tests provided in their GitHub repositories.
 
@@
 Tables~\ref{tab:pytracer_scipy_results_summary} and~\ref{tab:pytracer_sklearn_results_summary} summarize 
-the outcome of \pytracer experiments on SciPy and scikit-learn.
-Each table reports on the tracing and trace aggregation steps with three possible outcomes: green for success, red for numerical error in the application, and orange for errors in the fuzzy noise injection or due to the instrumentation of NumPy \texttt{ufuncs}.
-Overall, the tracing and parsing of SciPy and scikit-learn tests in Random Rounding mode and without \texttt{ufunc} instrumentation was entirely successful (tracing and parsing steps) for 31/40 tests.
+\pytracer's outcome on SciPy and scikit-learn tests.
+Each table reports on the tracing and trace aggregation steps with three possible outcomes: green for success, red for numerical error in the application, and orange for errors in the fuzzy noise injection.
+Overall, the tracing and parsing of SciPy and scikit-learn tests in Random Rounding mode was entirely successful (tracing and parsing steps) for 32/40 tests.
 The remaining tests failed due to numerical errors in the libraries, which we discuss hereafter.
-The instrumentation with Full MCA is more invasive and reduced the number of successful executions without \texttt{ufunc} instrumentation to 11/40.
-The instrumentation of \texttt{ufuncs} also reduced the success rate substantially, to 17/40 in Random Rounding mode and to 8/40 in Full MCA.
+The instrumentation with Full MCA is more invasive and reduced the number of successful executions to 13/40.
 
@@
     \centering
-    \begin{tabular}{|ll|c|c|c|c||c|c|c|c|}
-    \hline
-    \multicolumn{2}{|c}{ \multirow{3}{*}{Application} } & \multicolumn{4}{|c||}{Random Rounding (RR)} & \multicolumn{4}{c|}{Full MCA} \\\cline{3-10}
-         &   & \multicolumn{2}{c|}{\texttt{ufunc}} & \multicolumn{2}{c||}{no \texttt{ufunc}} & \multicolumn{2}{c|}{\texttt{ufunc}} & \multicolumn{2}{c|}{no \texttt{ufunc}} \\\cline{3-10}
-    & & trace & parse &  trace & parse & trace & parse & trace & parse \\
+    \begin{tabular}{|ll|c|c|c|c|}
+    \hline
+    \multicolumn{2}{|c}{ \multirow{2}{*}{Application} } & \multicolumn{2}{|c|}{RR} & \multicolumn{2}{c|}{Full MCA} \\
+    \cline{3-6}
+    & & trace & parse & trace & parse  \\
     \hline
@@
     \multicolumn{1}{|c|}{ \multirow{3}{2em}{ \rotatebox{90}{FFT} } }
-    & discrete\_cosine\_transform & \valid & \valid & \valid & \valid & \valid & \valid & \warn & \cross \\ 
-    \multicolumn{1}{|c|}{} & fft\_1D & \warn & \valid & \valid & \valid & \warn & \cross & \warn & \cross \\
-    \multicolumn{1}{|c|}{} & fft\_2D & \valid & \valid & \valid & \valid & \valid & \valid & \valid & \valid \\
+    & discrete\_cosine\_transform &  \valid & \valid & \warn & \cross \\ 
+    \multicolumn{1}{|c|}{} & fft\_1D & \valid & \valid& \warn & \cross \\
+    \multicolumn{1}{|c|}{} & fft\_2D & \valid & \valid & \valid & \valid \\
     \hline 
     \multicolumn{1}{|c|}{  \multirow{5}{2em}{ \rotatebox{90}{Interpolation} } }
-    & interpolation\_1D & \valid & \valid & \valid & \valid & \valid & \cross & \warn & \cross  \\
-    \multicolumn{1}{|c|}{} & multivariate\_data & \valid & \valid & \valid & \valid & \valid & \cross & \warn & \cross \\
-     \multicolumn{1}{|c|}{} & bspline & \valid & \valid & \valid & \valid & \valid & \valid & \valid & \valid \\
-     \multicolumn{1}{|c|}{} & spline\_1D & \warn & \valid & \valid & \cross & \warn & \cross & \warn & \cross \\
-     \multicolumn{1}{|c|}{} & spline\_2D & \warn & \valid & \valid & \valid & \warn & \cross & \warn & \cross \\
+    & interpolation\_1D & \valid & \valid & \warn & \cross  \\
+    \multicolumn{1}{|c|}{} & multivariate\_data & \valid & \valid & \warn & \cross \\
+     \multicolumn{1}{|c|}{} & bspline  & \valid & \valid & \valid & \valid \\
+     \multicolumn{1}{|c|}{} & spline\_1D & \valid & \cross & \warn & \cross \\
+     \multicolumn{1}{|c|}{} & spline\_2D & \valid & \valid & \warn & \cross \\
     \hline
      \multicolumn{1}{|c|}{ \multirow{12}{2em}{ \rotatebox{90}{Optimization} } }
-    & broyden\_fletcher\_goldfarb\_shanno & \valid & \valid & \valid & \valid & \valid & \valid & \valid & \valid \\
-     \multicolumn{1}{|c|}{} & global\_optimization & \warn & \valid & \warn & \valid & \warn & \cross & \cross & \cross \\
-    \multicolumn{1}{|c|}{}  & slsqp & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \cross \\
-     \multicolumn{1}{|c|}{} & least\_square\_minimization & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \valid \\
-     \multicolumn{1}{|c|}{} & nelder\_mead\_simplex & \valid & \valid & \valid & \valid & \valid & \valid & \valid & \valid \\
-     \multicolumn{1}{|c|}{} & newton\_conjugate\_gradient & \valid & \cross & \valid & \cross & \valid & \cross & \valid & \cross \\
-     \multicolumn{1}{|c|}{} & root\_finding\_large\_preconditionned & \valid & \cross & \valid & \cross & \warn & \cross & \valid & \cross \\
-    \multicolumn{1}{|c|}{}  & root\_finding\_large & \warn & \valid & \valid & \cross & \valid & \cross & \valid & \cross \\
-     \multicolumn{1}{|c|}{} & root\_findings & \warn & \valid & \valid & \valid & \warn & \valid & \warn & \cross \\
-    \multicolumn{1}{|c|}{}  & trust\_region\_exact & \valid & \valid & \valid & \valid & \valid & \valid & \valid & \valid \\
-     \multicolumn{1}{|c|}{} & trust\_region\_truncated\_generalized\_lanczos & \valid & \valid & \valid & \valid & \valid & \valid & \valid & \valid \\
-    \multicolumn{1}{|c|}{}  & trust\_region\_newton\_conjugate\_gradient & \valid & \valid & \valid & \valid & \valid & \valid & \valid & \valid \\
+    & broyden\_fletcher\_goldfarb\_shanno & \valid & \valid & \valid & \valid \\
+     \multicolumn{1}{|c|}{} & global\_optimization & \valid & \cross  & \warn & \cross \\
+    \multicolumn{1}{|c|}{}  & slsqp & \valid & \valid  & \valid & \valid \\
+     \multicolumn{1}{|c|}{} & least\_square\_minimization & \valid & \valid  & \warn & \cross \\
+     \multicolumn{1}{|c|}{} & nelder\_mead\_simplex  & \valid & \valid  & \valid & \valid \\
+     \multicolumn{1}{|c|}{} & newton\_conjugate\_gradient  & \valid & \valid  & \valid & \cross \\
+     \multicolumn{1}{|c|}{} & root\_findings  & \valid & \cross & \warn & \cross \\
+    \multicolumn{1}{|c|}{}  & root\_finding\_large & \valid & \cross  & \valid & \cross \\
+     \multicolumn{1}{|c|}{} & root\_finding\_large\_preconditionned & \valid & \cross & \valid & \cross \\
+    \multicolumn{1}{|c|}{}  & trust\_region\_exact& \valid & \valid  & \valid & \valid \\
+     \multicolumn{1}{|c|}{} & trust\_region\_truncated\_generalized\_lanczos & \valid & \valid & \valid & \valid \\
+    \multicolumn{1}{|c|}{}  & trust\_region\_newton\_conjugate\_gradient & \valid & \valid & \valid & \valid \\
     \hline
@@
     \caption{\pytracer execution summary on SciPy tests.\\RR: Random Rounding.
-\texttt{ufunc}: instrumentation of NumPy \texttt{ufuncs}.
 trace: outcome of \pytracer tracing, parse: outcome of \pytracer trace parsing and aggregation.
-\valid: successful run, \warn: error in fuzzy noise injection or due to the instrumentation of NumPy \texttt{ufuncs}, \cross: numerical error.}
+\valid: successful run, \warn: error in fuzzy noise injection, \cross: numerical error or divergent traces.}
     \label{tab:pytracer_scipy_results_summary}
@@
     \centering
-    \begin{tabular}{|c|c|c|c|c||c|c|c|c|}
-    \hline
-    \multirow{3}{5em}{Application} & \multicolumn{4}{|c||}{Random Rounding (RR)} & \multicolumn{4}{|c|}{Full MCA} \\\cline{2-9}
-                & \multicolumn{2}{|c|}{\texttt{ufunc}} &  \multicolumn{2}{|c||}{no \texttt{ufunc}} & \multicolumn{2}{|c|}{\texttt{ufunc}} & \multicolumn{2}{|c|}{no \texttt{ufunc}} \\\cline{2-9}
-                & trace & parse &  trace & parse & trace & parse & trace & parse \\
+    \begin{tabular}{|c|c|c|c|c|}
+    \hline
+    \multirow{2}{5em}{Application} & \multicolumn{2}{c|}{RR} & \multicolumn{2}{c|}{MCA} \\\cline{2-5}
+                                & trace & parse &  trace & parse \\
     \hline
@@
     %        & run   & parse  &  run   &  parse &  run   & parse  & run    & parse  \\
-    Adaboost & \warn & \valid & \valid & \valid & \warn & \cross & \cross & \cross \\
-    Bayesian Ridge Regression & \warn & \valid & \valid & \valid & \cross & \cross & \cross & \cross \\
-    Online classifier comparison & \valid & \valid & \valid & \valid & \cross & \cross & \cross & \cross  \\
-    Cluster Iris & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
-    Covariance estimation & \valid & \cross & \valid & \cross & \cross & \cross & \valid & \cross \\
-    Decision Tree Regression & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
-    Digits Classification & \warn & \valid & \valid & \valid & \warn & \cross & \cross & \cross \\
-    Face Recognition & \cross & \valid & \cross & \valid & \cross & \cross & \cross & \cross \\
-    L1 Penalty & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \valid \\
-    Lasso and elastic net & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \cross \\
-    Separating hyperplan & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
-    MNIST classification & \warn & \valid & \valid & \valid & \valid & \cross & \valid & \valid \\
-    Multitask Lasso & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \valid \\
-    Orthogonal matching & \warn & \valid & \valid & \valid & \cross & \valid & \cross & \valid \\
-    PCA decomposition & \warn & \valid & \valid & \valid & \warn & \cross & \valid & \cross \\
-    Robust Linear Regression & \valid & \valid & \valid & \valid & \warn & \cross & \valid & \cross \\
-    Segmentation toy & \warn & \valid & \valid & \cross & \warn & \cross & \cross & \cross \\
-    SVM & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
-    Tomography & \warn & \valid & \valid & \cross & \warn & \cross & \cross & \cross \\
-    Weighted samples & \valid & \valid & \valid & \valid & \valid & \cross & \valid & \cross \\
+    Adaboost & \valid & \valid  & \warn & \cross \\
+    Bayesian Ridge Regression  & \valid & \valid  & \cross & \cross \\
+    Online classifier comparison & \valid & \valid  & \warn & \cross  \\
+    K-Means Clustering  & \valid & \valid  & \valid & \cross \\
+    Covariance estimation  & \valid & \cross  & \warn & \cross \\
+    Decision Tree Regression & \valid & \valid  & \valid & \valid \\
+    Digits Classification  & \valid & \valid  & \warn & \cross \\
+    Face Recognition  & \cross & \valid  & \warn & \cross \\
+    L1 Penalty  & \valid & \valid  & \valid & \valid \\
+    Lasso and elastic net  & \valid & \valid  & \warn & \cross \\
+    Separating hyperplan  & \valid & \valid  & \valid & \cross \\
+    MNIST classification  & \valid & \valid  & \warn & \valid \\
+    Multitask Lasso  & \valid & \valid  & \warn & \valid \\
+    Orthogonal matching & \valid & \valid  & \valid & \valid \\
+    PCA decomposition  & \valid & \valid  & \valid & \valid \\
+    Robust Linear Regression  & \valid & \valid  & \warn & \cross \\
+    Segmentation toy  & \valid & \valid  & \warn & \cross \\
+    SVM  & \valid & \valid  & \valid & \cross \\
+    Tomography  & \valid & \cross  & \warn & \cross \\
+    Weighted samples  & \valid & \valid  & \valid & \cross \\
     \hline
@@
 \\RR: Random Rounding.
-\texttt{ufunc}: instrumentation of NumPy \texttt{ufuncs}.
 trace: outcome of \pytracer tracing, parse: outcome of \pytracer trace parsing and aggregation.
-\valid: successful run, \warn: error in fuzzy noise injection or due to the instrumentation of NumPy \texttt{ufuncs}, \cross: numerical error.}
+\valid: successful run, \warn: error in fuzzy noise injection, \cross: numerical error or divergent traces.}
     \label{tab:pytracer_sklearn_results_summary}
@@
 
+Table~\ref{tab:pytracer_test_precision_summary} summarizes the precision for main outputs of SciPy and scikit-learn tests. 
+We measure the precision in significant bits on the principal output computed by the test by taking the element-wise mean for non-scalar values and, if the test produces many outputs, we take the average value among results.
+A dash value means that the test produces an error.
+The numerical quality of obtained results and MCA modes combined vary from 0 to 52, with an average of 44 bits significant.
+For both modes, we note that only one test failed due to a numerical error (\texttt{face\_recognition} for RR and \textit{Bayesian Ridge Regression} for Full MCA) even though this number is underestimated since Full MCA mode is more intrusive than RR mode and most of the tests produce error caused by the fuzzy noise injection.
+
+\begin{table}
+\small
+\begin{subfigure}[t]{.5\linewidth}
+    \centering
+    \begin{tabular}{|l|c|c|}
+    \hline 
+    Application & RR & MCA \\
+    \hline
+    discrete\_cosine\_transform & 52 & 47 \\ 
+    fft\_1D & 41 & - \\
+    fft\_2D & 52 & 52  \\
+    \hline
+    interpolation\_1D & 51 & -   \\
+    multivariate\_data & 51 & - \\
+    bspline  & 10 & 10  \\
+    spline\_1D & 52 & 52 \\
+    spline\_2D & 10 & - \\
+    \hline
+    broyden\_fletcher\_goldfarb\_shanno & 48 & 46 \\
+    global\_optimization & 17 & - \\
+    | SHGO\footnote{Simplicial Homology Global Optimization} & 25 & - \\
+    | Dual Annealing & 4 & - \\
+    | Differential Evolution & 0 & - \\
+    | Basin Hopping & 40 & - \\
+    | SHGO Sobol & 45 & - \\
+    slsqp & 45 & 44 \\
+    least\_square\_minimization & 48 & -  \\
+    nelder\_mead\_simplex  & 44 & 42  \\
+    newton\_conjugate\_gradient  & 48 & 47 \\
+    root\_findings  & 52 & 50 \\
+    root\_finding\_large & 29 & 26   \\
+    root\_finding\_large\_preconditioned & 42 & 42 \\
+    trust\_region\_exact& 48 & 46  \\
+    trust\_region\_truncated\_generalized\_lanczos & 48 & 46  \\
+    trust\_region\_newton\_conjugate\_gradient & 52 & 47 \\
+    \hline
+    \end{tabular}
+\end{subfigure}
+\hspace{1cm}
+\begin{subfigure}[t]{.5\linewidth}
+    \begin{tabular}{|l|c|c|}
+    \hline 
+    Application & RR & MCA \\
+    \hline
+    Adaboost & 48 & - \\
+    Bayesian Ridge Regression  & 25 & -  \\
+    | $1^{st}$ dataset & nan & - \\
+    | $2^{nd}$ dataset & 20 & - \\
+    Online classifier comparison & 48 & -  \\
+    K-Means Clustering  & 52 & -   \\
+    Covariance estimation  & 48 & -   \\
+    Decision Tree Regression & 50 & 50  \\
+    Digits Classification  & 52 & 52 \\
+    Face Recognition  & - & - \\
+    L1 Penalty  & - & -   \\
+    Lasso and elastic net  & 48 & 47  \\
+    Separating hyperplan  & 3 & -  \\
+    MNIST classification  & 43 & - \\
+    Multitask Lasso  & 50 & 48   \\
+    Orthogonal matching & 52 & 52  \\
+    PCA decomposition  & 48 & 48   \\
+    Robust Linear Regression  & 50 & 48   \\
+    | Linear & 48 & 46 \\
+    | RANSAC & 50 & 48 \\
+    Segmentation toy  & 35 & - \\
+    SVM  & 43.5 &  -  \\
+    | Non-weighted & 44 & - \\
+    | Weighted & 43 & - \\
+    Tomography  & - & -  \\
+    Weighted samples  & 44 & -   \\
+    \hline
+    \end{tabular}
+\end{subfigure}
+    \caption{Summary of tests precision for main outputs of SciPy and scikit-learn tests. Precision is measured in significant bits on the principal output computed by the test.
+    For non-scalar values, the element-wise mean is taken. If the test produces many outputs, like when comparing methods, the average value among results is taken.  
+    A dash value means that the test produces an error. }
+    \label{tab:pytracer_test_precision_summary}
+\end{table}
+
 \subsection{SciPy}
@@
 SciPy is organized in several libraries targeting specific computing domains.
-We focused on the following packages:
+Therefore, we focused on the following packages:
 \begin{itemize}
@@
 
+\subsubsection{FFT}
+
+This package has three tests: \texttt{discrete\_cosine\_transform}, \texttt{fft\_1D}, and \texttt{fft\_2D}.
+The results for \texttt{discrete\_cosine\_transform},\texttt{fft\_1D} and  \texttt{fft\_2D} show
+correct numerical results with 48 significant bits in average. All computations are done with double precision.
+We observe that the FFT is stable with noisy inputs. The figures~\ref{fig:fft1D_mean} and~\ref{fig:fft1D_std}
+show the mean and standard deviation over the MCA samples respectively. 
+The top rows show the domain $z$ and the result fft$(z)$, in the logarithmic scale with the real part in blue and the imaginary part in orange.
+The three columns correspond to the FFT computations of: 
+\begin{enumerate}
+\item $z_1 = \sin(50 . 2\pi . x_i) + \dfrac{1}{2} \sin(80 . 2\pi . x_i),\; x_i = \frac{i}{600},\; i \in [0,600]$
+\item $ blackman(400)*z_1$
+\item $ z_2= e^{50 . i 2\pi . x_i} + \dfrac{1}{2} e^{-80 . i2\pi .x_i },\; x_i = \frac{i}{800},\; i \in [0,400] $
+\end{enumerate}
+
+Top row of figures~\ref{fig:fft1D_mean} and~\ref{fig:fft1D_std} 
+shows the mean value of the inputs while the bottom row shows the standard deviation.
+The points with low magnitude correspond to inputs near 0, when the input of $\sin$ or 
+$\exp$ is close to $k\pi$, $k \in \mathbf{Z}$.
+Indeed, since MCA introduces a small noise, the result is not exactly 0.
+We can see on the figure~\ref{fig:fft1D_std} that the maximal noise introduced by MCA on the
+inputs is of the order of magnitude of $10^{-14}$, two order of magnitude higher than the 
+$ulp \simeq 10^-16$ for double precision. 
+This small noise introduced can be interpreted as a white noise on the input signal. 
+We can see on bottom row of the figure~\ref{fig:fft1D_std} that the frequencies noise is in 
+the same order of of magnitude than the magnitude of the inputs noise, which is expected. 
+The two pics at 38 and 562 corresponds to the actual frequencies of the input.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{figure/FFT/fft_x.pdf}
+    \caption{Absolute value of the mean and standard deviation values for 
+    fft 1D inputs within RR mode (log scale).}
+    \label{fig:fft1D_mean}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{figure/FFT/fft_y.pdf}
+    \caption{Absolute value of the mean and standard deviation values 
+    for fft 1D outputs within RR mode (log scale).}
+    \label{fig:fft1D_std}
+\end{figure}
+
+% \begin{figure}
+% \begin{minipage}{.5\textwidth}
+%     \centering
+%     \includegraphics[width=\linewidth]{figure/FFT/fft_x_real_sig_36.png}
+%     \caption{$\Re(x)$}
+%     \label{fig:my_label}
+% \end{minipage}
+% \begin{minipage}{.5\textwidth}
+%     \centering
+%     \includegraphics[width=\linewidth]{figure/FFT/fft_x_imag_sig_36.png}
+%     \caption{$\Im(x)$}
+%     \label{fig:my_label}
+% \end{minipage}
+% \begin{minipage}{.5\textwidth}
+%     \centering
+%     \includegraphics[width=\linewidth]{figure/FFT/fft_ret_real_sig_36.png}
+%     \caption{$\Re$(fft$(x))$}
+%     \label{fig:my_label}
+% \end{minipage}
+% \begin{minipage}{.5\textwidth}
+%     \centering
+%     \includegraphics[width=\linewidth]{figure/FFT/fft_ret_imag_sig_36.png}
+%     \caption{$\Im$(fft$(x))$}
+%     \label{fig:my_label}
+% \end{minipage}
+% \end{figure}
+
+\subsection{Interpolation}
+
+This package has three tests: \texttt{interpolation\_1D}, \texttt{multivariate\_data}, \texttt{bspline}, \texttt{spline\_1D} and \texttt{spline\_2D}.
+
+The \texttt{interpolation\_1D} test interpolates the function $\cos(\frac{-x^2}{9})$ with 11 points $x\in[0,10]$.
+For the fives schemes tested (linear, cubic, nearest, previous, next), the solution found is precise, up to 51 bits out of the 53 available.
+
+The \texttt{multivariate\_data} test interpolates the grid $f(x,y)=x(1-x)\cos(4\pi.x)  \sin(4\pi.y^2)^2$ with $(x,y) \in [0,1] \times [0,1]$ sampling with 1000 points for each coordinate using three schemes: nearest, linear and cubic.
+Our results show a precision of 51 bits in average for the three schemes.
+
+The \texttt{bspline} test compares two edge filters: \texttt{bisplev} that evaluates a bivariate B-spline and its derivative and \texttt{convolved2d} that convolves two 2-dimensional arrays.
+Figure~\ref{fig:bspline_rr}
+shows the significant bits (figs.~\ref{fig:bspline_bisplev_sig},~\ref{fig:bspline_convol2d_sig}), 
+mean (figs.~\ref{fig:bspline_bisplev_mean},~\ref{fig:bspline_convol2d_mean}), and standard deviation (figs.~\ref{fig:bspline_bisplev_std},~\ref{fig:bspline_convol2d_std}) maps for the two methods as well as the input image (fig.~\ref{fig:bspline_input}) with the middle for the \texttt{bisplev} results and bottom row for the \texttt{convol2d}.
+We can see no visual differences between both methods with 11 significant bits in average.
+Standard deviations maps on figures~\ref{fig:bspline_bisplev_std} and~\ref{fig:bspline_convol2d_std} show that regions with low spatial frequencies correspond to regions with low standard deviation, similar to the FFT results.
+As it is mentioned in the SciPy tutorial, the \texttt{bisplev} function is faster than the \texttt{convol2d} while our experiments show that they have the same numerical precision which reinforces the use of \texttt{bisplev} over \texttt{convol2d} in this example.
+
+The \texttt{spline\_1D} test computes the 1D spline interpolation for the function $\sin(x)$ on points $x=\frac{2\pi k}{8}, k \in [0, 10]$.
+The spline interpolation uses two methods: \texttt{splrep} to build the spline representation and \texttt{splrev} to evaluate the spline at any point.
+It also computes the integral by using \texttt{splint} and the root finder \texttt{sproot}.
+Although the traces diverge, we can analyze the partial aggregation for the \texttt{splrep}, \texttt{splev} and \texttt{splint}.
+The three functions show results with an average precision of 51 bits with RR mode.
+
+The \texttt{spline\_2D} test computes the 2D spline interpolation for the function $z=(x+y)e^{-6(x^2+y^2)}$, with $(x,y) \in [-1,1]\times[-1,1]$ sampling with 21 points for each coordinate.
+\texttt{bisplrep} builds the spline representation with the $21 \times 21$ points of $z$ over a 71 grid sampling points for $(x,y)$.
+The figure~\ref{fig:spline2d_rr} shows the results of the spline evaluation with \texttt{bisplev}.
+
+% \begin{figure}
+% \begin{minipage}{.3\textwidth}
+%     \centering
+%     \includegraphics[width=\linewidth]{figure/multivariate_data/nearest_ret_mean_log.png}
+% \end{minipage}
+% \begin{minipage}{.3\textwidth}
+%     \centering
+%     \includegraphics[width=\linewidth]{figure/multivariate_data/linear_ret_mean_log.png}
+% \end{minipage}
+% \begin{minipage}{.3\textwidth}
+%     \centering
+%     \includegraphics[width=\linewidth]{figure/multivariate_data/cubic_ret_mean_log.png}
+% \end{minipage}
+
+% \begin{minipage}{.3\textwidth}
+%     \centering
+%     \includegraphics[width=\linewidth]{figure/multivariate_data/nearest_ret_std_log.png}
+% \end{minipage}
+% \begin{minipage}{.3\textwidth}
+%     \centering
+%     \includegraphics[width=\linewidth]{figure/multivariate_data/linear_ret_std_log.png}
+% \end{minipage}
+% \begin{minipage}{.3\textwidth}
+%     \centering
+%     \includegraphics[width=\linewidth]{figure/multivariate_data/cubic_ret_std_log.png}
+% \end{minipage}
+%     \label{fig:multivariate_data_RR}
+%     \caption{\texttt{multivariate\_data} results within RR mode. Each column represents an 
+%     interpolation scheme, with from left to right, the nearest, linear and cubic method.
+%     Top row shows the log of the absolute mean value value while bottom row shows the log of the
+%     standard deviation. We can see that precision drops between local extremum when the 
+%     mean value is close to 0.}
+% \end{figure}
+
+\begin{figure}
+\centering
+\begin{subfigure}{.3\linewidth}
+    \includegraphics[width=\linewidth]{}
+\end{subfigure}
+\begin{subfigure}{.3\linewidth}
+    \includegraphics[width=\linewidth]{figure/bspline/original_image.png}
+    \caption{}
+    \label{fig:bspline_input}
+\end{subfigure}
+\begin{subfigure}{.3\linewidth}
+    \includegraphics[width=\linewidth]{}
+\end{subfigure}
+\begin{subfigure}{0.3\linewidth}
+    \includegraphics[width=\linewidth]{figure/bspline/bisplev_ret_sig_portland_r.png}
+    \caption{}
+    \label{fig:bspline_input}
+    \label{fig:bspline_bisplev_sig}
+\end{subfigure}
+\begin{subfigure}{0.3\linewidth}
+    \includegraphics[width=\linewidth]{figure/bspline/bisplev_ret_mean_log_portland.png}
+    \caption{}
+    \label{fig:bspline_bisplev_mean}
+\end{subfigure}
+\begin{subfigure}{0.3\linewidth}
+    \includegraphics[width=\linewidth]{figure/bspline/bisplev_ret_std_log_portland.png}
+    \caption{}
+    \label{fig:bspline_bisplev_std}
+\end{subfigure}
+\begin{subfigure}{0.3\linewidth}
+    \includegraphics[width=\linewidth]{figure/bspline/convol2d_ret_sig_portland_r.png}
+    \caption{}
+    \label{fig:bspline_convol2d_sig}
+\end{subfigure}
+\begin{subfigure}{0.3\linewidth}
+    \includegraphics[width=\linewidth]{figure/bspline/convol2d_ret_mean_log_portland.png}
+    \caption{}
+    \label{fig:bspline_convol2d_mean}
+\end{subfigure}
+\begin{subfigure}{0.3\linewidth}
+    \includegraphics[width=\linewidth]{figure/bspline/convol2d_ret_std_log_portland.png}
+    \caption{}
+    \label{fig:bspline_convol2d_std}
+\end{subfigure}
+    \label{fig:bspline_rr}
+    \caption{\texttt{bspline} results within RR mode. Left column shows the \texttt{bisplev} function
+    while the right column shows the \texttt{convolve2d} function. }
+\end{figure}
+
+\begin{figure}
+\begin{subfigure}{.3\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure/spline_2d/bisplev_inputs_mean.png}
+    \caption{\texttt{bisplev} IEEE result}
+    \label{fig:bisplev_ieee}
+\end{subfigure}
+\begin{subfigure}{.3\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure/spline_2d/bisplev_inputs_mean_log.png}
+    \caption{Absolute mean value (log)}
+    \label{fig:bisplev_mean_log}
+\end{subfigure}
+\begin{subfigure}{.3\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure/spline_2d/bisplev_inputs_std_log.png}
+    \caption{Standard deviation (log)}
+    \label{fig:bisplev_std_log}
+\end{subfigure}
+    \caption{2D Spline interpolation results. Figure~\ref{fig:bisplev_ieee} shows the IEEE result
+    of the 2D-spline interpolation. Figures~\ref{fig:bisplev_mean_log} and~\ref{fig:bisplev_std_log}
+    show respectively in the logarithmic scale the absolute mean value and the standard deviation 
+    of the 5 samples run within RR mode.}
+    \label{fig:spline2d_rr}
+\end{figure}
+
+\subsubsection{Optimization}
+
+This package has ten tests: five for unconstrained minimization of multivariate scalar functions using different algorithms: \texttt{Nelder-Mead}~\cite{singer2009nelder} that iteratively transforms a simplex until its vertices are getting closer to local minima of the function.
+Fours Quasi-Newton-Raphson methods whose main goal is to determine $x$ that minimizes the function $f$ by using Newton's method step: $x_{k+1} = x_{k} - B^{-1}(x_k)\nabla f(x_k)$, where $\nabla$ and $B$ are the gradient and the approximation of the Hessian matrix of $f$.
+The \texttt{Broyden-Fletcher-Goldfarb-Shanno}~\cite{BFGS} (BFGS) and \texttt{Newton-Conjugate-Gradient}~\cite{nocedal2006numerical} (NCG) are line search methods that respectively approximates $H$ by adding two symmetric rank-one matrices and by using the Conjugate-Gradient method.
+The \texttt{Trust-Region Truncated Generalized Lanczos / Conjugate Gradient}~\cite{gould1999solving}, \texttt{Trust-Region Newton-Conjugate-Gradient} and \texttt{Trust-Region Nearly Exact}~\cite{nocedal2006numerical} are trust-region methods that approximates $H$ by solving the trust-region subproblem restricted to a truncated Krylov subspace and by solving nonlinear equations for each quadratic subproblem.
+Two tests for constrained minimization of multivariate scalar functions: \texttt{Sequential Least SQuares Programming} (SLSQP) and \texttt{Least-squares minimization}.
+And three for root finding with one for small problems \texttt{root\_finding} and two for large problems using a Krylov approximation for the inverse Jacobian with and without the help of a preconditioner: \texttt{root\_finding\_large\_preconditionned} and \texttt{root\_finding\_large}.
+
+The unconstrained minimization of multivariate scalar minimizes the Rosenbrock function of $N$ variables:
+\[f(x) = \sum_{i=1}^{N-1} 100(x_{i+1}-x^2_i)^2 + (1-x_i)^2\]
+The minimum value of this function is 0, which is achieved when $x_i=1$.
+Figure~\ref{fig:unconstrained_optimization} shows the number of significant bits of the solution for the different methods used.
+We can see that all methods have a good precision comprising between 43 and 53 bits significant.
+The Nelder-Mead method is the worst with $\simeq$ 43 bits on average, while the Trust-Region-Newton-CG has the best precision with $\simeq$ 53 bits significant, which is significant the maximum achievable within double precision.
+The remaining methods share a similar precision with less than 1 bit between them.
+
+The constrained minimization of multivariate scalar tests minimize the Rosenbrock function for SLSQP subject to
+\begin{eqnarray*}
+    x_0 + 2x_1 \leq 1 \\
+    x_0^2 + x_1 \leq 1 \\
+    x_0^2 - x_1 \leq 1 \\
+    2x_0 + x_1 = 1 \\
+    0 \leq x_0 \leq 1 \\
+    -0.5 \leq x_1 \leq 2 
+\end{eqnarray*}
+with the unique solution $[x_0, x_1] = [0.4149, 0.1701]$.
+Results within RR show a precision of 47 and 44 bits for the first and the second solution.
+The \texttt{least-square minimization} test solves a fitting problem from an enzymatic reaction~\cite{kowalik1968analysis} with 11 residuals defined as:
+\begin{eqnarray*}
+f_i(x) &=& \frac{x_0(u_i^2 + u_ix_1)}{u_i^2 + u_ix_2+x_3}-y_i,\; i=0,...,10 \\
+&0& \leq x_j \leq 100,\; j=0,..,3
+\end{eqnarray*}
+where where $y_i$ are measurement values, $u_i$ are values of the independent variable, and
+$x_i$ the unknown.
+Results within RR show a precision of [51,46,47,48] bits for the solution.
+
+Finally, the \texttt{root\_*} tests use three algorithms to 
+find root of non-linear equations. \texttt{root\_finding}
+uses the hybrid method of Powell to solve a single-variable transcendental equation and 
+the Levenberg-Marquardt for a set of non-linear equations. 
+\texttt{root\_finding\_large} and \texttt{root\_finding\_large\_preconditioned} tests use 
+Krylov method to solve an integrodifferential equation on a square
+ $(x,y) \in [0,1] \times [0,1]$, $P(x,1)=1$, and $P=0$ elsewhere on the boundary.
+The function $P$ is discretized with a Cartesian grid $P_{n,n}=P(nh,nh)$, with $n=75$ and its derivatives are approximated by $\partial_x^2P(x,y) \simeq (P(x+h,y) - 2P(x,y) + P(x-h,y))/h^2$.
+
+% the two following equations: $x + 2\cos(x) = 0$ and 
+% the set $x_0\cos(x_1)=4$; $x_0x_1-x_1 = 5$ while the 
+% \texttt{root\_finding\_large} and \texttt{root\_finding\_large\_preconditioned} tests 
+% solve the equation:
+% \[
+%     (\partial_x^2 + \partial_y^2)P + 5 \left(\int_0^1 \int_0^1 cosh(P)\, dx dy \right)^2 = 0
+% \]
+
+All tests diverge even within RR mode, which is not surprising since root-finding methods can easily take a few extra steps to find the root depending on the starting point.
+Nevertheless, for the \texttt{root\_finding\_large} test, 3 traces among the 5 samples can be merged for both RR and MCA modes.
+Figure~\ref{fig:root_finding_large} shows the mean and standard deviation of the result for these 3 samples.
+We can see that both RR and Full MCA found a similar solution, with a less precise one for Full MCA, although the spread between RR and MCA is small with a maximal standard deviation of $8.10^{-9}$ for MCA against $3.10^{-9}$ for RR mode.
+Finally, it is interesting to note the impact of the preconditioning on the result numerical quality, with a precision doubling between \texttt{root\_finding\_large} and \texttt{root\_finding\_large\_preconditioned} as table~\ref{tab:pytracer_test_precision_summary} shows.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{figure/unconstrained_optimization_comparison.png}
+    \caption{Comparison of results precision for different optimization solvers within RR mode.}
+    \label{fig:unconstrained_optimization}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \begin{subfigure}{0.45\linewidth}
+    \includegraphics[width=\linewidth]{figure/root_finding/solution_mean_RR.pdf}
+    \caption{}
+    \label{fig:my_label}
+    \end{subfigure}
+    \begin{subfigure}{0.45\linewidth}
+    \includegraphics[width=\linewidth]{figure/root_finding/solution_std_RR.pdf}
+    \caption{}
+    \label{fig:my_label}
+    \end{subfigure}
+
+    \begin{subfigure}{0.45\linewidth}
+    \includegraphics[width=\linewidth]{figure/root_finding/solution_mean_MCA.pdf}
+    \caption{}
+    \label{fig:my_label}
+    \end{subfigure}
+    \begin{subfigure}{0.45\linewidth}
+    \includegraphics[width=\linewidth]{figure/root_finding/solution_std_MCA.pdf}    \caption{}
+    \label{fig:my_label}
+    \end{subfigure}
+    \caption{Solution of \texttt{root\_finding\_large} test within RR (top row) and MCA (bottom row) with the mean value on the left and the standard deviation on the right.
+We can see that MCA has a less precision solution with a maximal standard deviation at $8.10^{-9}$ against $3.10^{-9}$ for RR mode.
+Moreover, we can see that a high standard deviation is localized around two extrema for both RR and Full MCA modes.
+Finally, the standard deviation stills lower than
+    the stopping criterion threshold fixed at $6.10^{-6}$.}
+    \label{fig:root_finding_large}
+\end{figure}
+
+% \begin{itemize}
+% \item broyden: RR 47 bits solution / MCA divergence 
+% \item global\_optimization: RR divergence / MCA issues
+% \item sqlsp: RR 46 bits solution / MCA 46 bits solution
+% \item least\_square\_minimization : RR 48 bits solution / MCA index issue
+% \item nelder\_mean\_simplex : RR 43 bits solution / MCA stable
+% \item newton\_conjugate\_gradient: RR 48 bits solution / MCA divergence
+% \item root\_finding\_large\_preconditionned : RR divergence / MCA divergence 3/5 converged
+% \item root\_finding\_large : RR divergence / MCA divergence (fgmres very low!) 3/5 converged
+% \item trust\_region\_exact : RR 47 bit solution / RR 45 bit solution
+% \item trust\_region\_truncated\_generalized\_lanczos : RR 48 bits solution / MCA 46 bits solution
+% \end{itemize}
+
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=\linewidth]{figure/nelder_mead/timeline_sig.png}
+%     \caption{Nelder-Mead: average of number of significant bits over time. 
+%     Solver ends when accuracy is reaching the tolerance.
+%     }
+%     \label{fig:my_label}
+% \end{figure}
+
 \subsection{Scikit learn}
@@
 
-We tested Pytracer on Scikit-learn~\cite{pedregosa2011scikit}, a "Python module integrating a wide range of state-of-the-art machine learning algorithms for medium-scale supervised and unsupervised problems".
+We tested Pytracer on the Scikit-learn~\cite{pedregosa2011scikit} library, a 
+Python library implementing a wide range of state-of-the-art machine learning algorithms.
 Scikit-learn offers a well supplied and documented list of examples that facilitates its using with Pytracer.
@@
 \href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_sgd_comparison.html#sphx-glr-auto-examples-linear-model-plot-sgd-comparison-py}{Comparing various online solvers}, 
-\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_sgd_comparison.html#sphx-glr-auto-examples-linear-model-plot-sgd-comparison-py}{K-means Clustering},
+\href{https://scikit-learn.org/stable/auto_examples/cluster/plot_cluster_iris.html#sphx-glr-auto-examples-cluster-plot-cluster-iris-py}{K-means Clustering},
+\href{https://scikit-learn.org/stable/auto_examples/covariance/plot_mahalanobis_distances.html#sphx-glr-auto-examples-covariance-plot-mahalanobis-distances-py}{Covariance Estimation},
+\href{https://scikit-learn.org/stable/auto_examples/tree/plot_tree_regression.html#sphx-glr-auto-examples-tree-plot-tree-regression-py}{Decision Tree Regression},
 \href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_sgd_comparison.html#sphx-glr-auto-examples-linear-model-plot-sgd-comparison-py}{Recognizing hand-written digits},
-\href{https://scikit-learn.org/stable/auto_examples/decomposition/plot_faces_decomposition.html#sphx-glr-auto-examples-decomposition-plot-faces-decomposition-py}{Faces dataset decompositions},
+\href{https://scikit-learn.org/stable/auto_examples/decomposition/plot_faces_decomposition.html#sphx-glr-auto-examples-decomposition-plot-faces-decomposition-py}{Faces dataset decomposition},
 \href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_logistic_l1_l2_sparsity.html#sphx-glr-auto-examples-linear-model-plot-logistic-l1-l2-sparsity-py}{L1 Penalty and Sparsity in Logistic Regression},
@@
 \href{https://scikit-learn.org/stable/auto_examples/decomposition/plot_pca_iris.html#sphx-glr-auto-examples-decomposition-plot-pca-iris-py}{PCA example with Iris Data-set},
-\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_poisson_regression_non_normal_loss.html#sphx-glr-auto-examples-linear-model-plot-poisson-regression-non-normal-loss-py}{Poisson regression and non-normal loss},
+% \href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_poisson_regression_non_normal_loss.html#sphx-glr-auto-examples-linear-model-plot-poisson-regression-non-normal-loss-py}{Poisson regression and non-normal loss},
 \href{https://scikit-learn.org/stable/auto_examples/cluster/plot_segmentation_toy.html#sphx-glr-auto-examples-cluster-plot-segmentation-toy-py}{Spectral clustering for image segmentation},
@@
 \href{https://scikit-learn.org/stable/auto_examples/applications/plot_tomography_l1_reconstruction.html#sphx-glr-auto-examples-applications-plot-tomography-l1-reconstruction-py}{Compressive sensing: tomography reconstruction with L1 prior (Lasso)},
-\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_tweedie_regression_insurance_claims.html#sphx-glr-auto-examples-linear-model-plot-tweedie-regression-insurance-claims-py}{Tweedie regression on insurance claims},
+% \href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_tweedie_regression_insurance_claims.html#sphx-glr-auto-examples-linear-model-plot-tweedie-regression-insurance-claims-py}{Tweedie regression on insurance claims},
 \href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_sgd_weighted_samples.html#sphx-glr-auto-examples-linear-model-plot-sgd-weighted-samples-py}{SGD: Weighted samples}.
 
-We used the fuzzy environment with numpy, scipy and scitkit-learn instrumented. 
-We tested two perturbations modes: Random Rounding (RR) and Full MCA (MCA).
-
-Table~\ref{tab:pytracer_sklearn_results_summary} summaries sklearn experiments with Pytracer.
-
-% \subsubsection{Decision Tree Regression with AdaBoost}
-
-% A decision tree is boosted using the AdaBoost.R2~\cite{drucker1997improving} 
-% algorithm on a 1D sinusoidal dataset with a small amount of Gaussian noise. 
-% 299 boosts (300 decision trees) is compared with a single decision tree regressor. 
-% As the number of boosts is increased the regressor can fit more detail. 
-% The execution with Pytracer reveals a numerical stability.
+% \subsubsection{Classifier comparisions}
+
+% This test compares the performance of 6 online solvers on the hand-written digits dataset.
+% These 6 solvers are:
+% \begin{itemize}
+%     \item Stochastic Gradient Descent 
+%     \item Averaged Stochastic Gradient Decent
+%     \item Perceptron
+%     \item Passive-Aggressive I \& II
+%     \item SAG: Minimizing Finite Sums with the Stochastic Average Gradient
+% \end{itemize}
+
+% Each solver is trained and predicts 20 times on 6 different training size ratio.
+% Figure~\ref{fig:classifier_comparisons_general} shows the all functions
+% traced by Pytracer over time. We can see the estimated number of significant digits varies a lot between 
+% values from 1 to 80 bits. Figure~\ref{fig:classifier_comparisons_mean_predictions} shows 
+% the average prediction score for each classifiers. The yellow points 
+% represent the average correct prediction score for one round and one classifier (line. 48) while blue points
+% tshows average predictions over the 20 rounds (line. 49).
+% We can see that precision is pretty low with an average solution below 10 significant bits, with 
+% an exception for values between the 24k and 32k invocation that correspond to the Perceptron
+% classifier. Indeed, this classifier is pretty stable with an average number of significant digits around 52 bits.
 
 % \begin{figure}
-%     \centering
-%     \caption{Caption}
-%     \includegraphics[width=\linewidth]{figure/adaboost/predict_adaboost_s.png}
-%     \caption{Number of significant digits of predicted values array.}
-%     \label{fig:adaboost_predict_s}
+%     \begin{lstlisting}[language=Python,style=customPython,numbers=left, firstnumber=19]
+% heldout = [0.95, 0.90, 0.75, 0.50, 0.01]
+% rounds = 20
+% X, y = datasets.load_digits(return_X_y=True)
+
+% classifiers = [
+%     ("SGD", SGDClassifier(max_iter=100)),
+%     ("ASGD", SGDClassifier(average=True)),
+%     ("Perceptron", Perceptron()),
+%     ("Passive-Aggressive I", PassiveAggressiveClassifier(loss='hinge',C=1.0, tol=1e-4)),
+%     ("Passive-Aggressive II", PassiveAggressiveClassifier(loss='squared_hinge',C=1.0, tol=1e-4)),
+%     ("SAG", LogisticRegression(solver='sag', tol=1e-1, C=1.e4 / X.shape[0]))
+% ]
+
+% xx = 1. - np.array(heldout)
+
+% for name, clf in classifiers:
+%     print("training %s" % name)
+%     rng = np.random.RandomState(42)
+%     yy = []
+%     for i in heldout:
+%         yy_ = []
+%         for r in range(rounds):
+%             X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=i, random_state=rng)
+%             clf.fit(X_train, y_train)
+%             y_pred = clf.predict(X_test)
+%             yy_.append(1 - np.mean(y_pred == y_test))
+%         yy.append(np.mean(yy_))
+%     plt.plot(xx, yy, label=name)
+%     \end{lstlisting}
+%     \label{fig:wrapper_code}
+% \caption{}
 % \end{figure}
-
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/adaboost/adaboost_boost_mean.png}
-%     \caption{Mean values of boost function.}
-%     \label{fig:adaboost_boost_mean}
-% \end{figure}
-
-% \begin{figure}
-%     \centering
-%     \caption{Caption}
-%     \includegraphics[width=\linewidth]{figure/adaboost/predict_adaboost_zoom_s.png}
-%     \caption{Average number of significant digits of prediction over estimator}
-%     \label{fig:adaboost_predict_zoom_s}
-% \end{figure}
-
-% \begin{figure}
-% \begin{minipage}{0.4\linewidth}
-%     \includegraphics[width=\linewidth]{figure/adaboost/to_predict_adaboost_mean.png}
-%     \caption{Values to predict}
-%     \label{fig:adaboost_to_predict_mean}
-% \end{minipage}
-% \begin{minipage}{0.4\linewidth}
-%     \includegraphics[width=\linewidth]{figure/adaboost/predict_adaboost_zoom_mean.png}
-%     \caption{Predicted values}
-%     \label{fig:adaboost_predicted_mean}
-% \end{minipage}
-% \caption{Comparison between original (fig.~\ref{fig:adaboost_to_predict_mean}) and predicted (fig.~\ref{fig:adaboost_predicted_mean}) values}
-% \end{figure}
-
-% \subsubsection{Bayesian Ridge Regression}
-
-% "\texttt{BayesianRidge} estimates a probabilistic model of the regression problem as described above. 
-% The prior for the coefficient  is given by a spherical Gaussian:
-% \[
-%     p(w|\lambda)=\mathcal{N}(w|0,\lambda^{-1}\mathbf{I}_p)
-% \]
-% The priors over  and  are chosen to be gamma distributions, the conjugate prior for the precision of the Gaussian. 
-% The resulting model is called Bayesian Ridge Regression, and is similar to the classical Ridge.
-% The parameters, and are estimated jointly during the fit of the model, 
-% the regularization parameters and being estimated by maximizing the log marginal likelihood. 
-% The scikit-learn implementation is based on the algorithm~\cite{tipping2001sparse}."
-
-% Both execution with RR and MCA modes failed but two different errors. 
-% Execution in RR mode raises an error due to an invalid value encountered in the \texttt{sqrt} function
-% while the MCA mode execution raises an error due to an issue with the Singular Value Decomposition (SVD) divergence.
-
-% RR executions fail with an invalid value in the \texttt{sqrt} function 
-% used in the \texttt{\_update\_coef\_} method of the \texttt{BayesianRidge} class.
-% This method updates the posterior mean and compute the corresponding Root-Mean-Square-Error (rmse).
-
-% When we backtrack the error propagation, we see that
-
-% MCA executions show the limit of Pytracer since the SVD decomposition in scipy is a wrapper around the 
-% \texttt{gesdd} or \texttt{gesvd} LAPACK~\cite{anderson1999lapack} functions. 
-% Numerical instabilities that are coming from this kernel are opaque for Pytracer since it works 
-% at the Python level. Tools working on C/FORTAN codes 
-% like Veritracer~\cite{chatelain2018veritracer} can be used to zoom in on these functions.
-% Nevertheless, Pytracer provides have a visualization of the input used by the SVD and several
-% metrics used in numerical analysis, like the condition number, that can help to understand.
-
-\subsubsection{Classifier comparisions}
-
-This test compares the performance of 6 online solvers on the hand-written digits dataset.
-These 6 solvers are:
-\begin{itemize}
-    \item Stochastic Gradient Descent 
-    \item Averaged Stochastic Gradient Decent
-    \item Perceptron
-    \item Passive-Aggressive I \& II
-    \item SAG: Minimizing Finite Sums with the Stochastic Average Gradient
-\end{itemize}
-
-Each solver is trained and predicts 20 times on 6 different training size ratio.
-Figure~\ref{fig:classifier_comparisons_general} shows the all functions
-traced by Pytracer over time. We can see the estimated number of significant digits varies a lot between 
-values from 1 to 80 bits. Figure~\ref{fig:classifier_comparisons_mean_predictions} shows 
-the average prediction score for each classifiers. The yellow points 
-represent the average correct prediction score for one round and one classifier (line. 48) while blue points
-tshows average predictions over the 20 rounds (line. 49).
-We can see that precision is pretty low with an average solution below 10 significant bits, with 
-an exception for values between the 24k and 32k invocation that correspond to the Perceptron
-classifier. Indeed, this classifier is pretty stable with an average number of significant digits around 52 bits.
-
-\begin{figure}
-    \begin{lstlisting}[language=Python,style=customPython,numbers=left, firstnumber=19]
-heldout = [0.95, 0.90, 0.75, 0.50, 0.01]
-rounds = 20
-X, y = datasets.load_digits(return_X_y=True)
-
-classifiers = [
-    ("SGD", SGDClassifier(max_iter=100)),
-    ("ASGD", SGDClassifier(average=True)),
-    ("Perceptron", Perceptron()),
-    ("Passive-Aggressive I", PassiveAggressiveClassifier(loss='hinge',C=1.0, tol=1e-4)),
-    ("Passive-Aggressive II", PassiveAggressiveClassifier(loss='squared_hinge',C=1.0, tol=1e-4)),
-    ("SAG", LogisticRegression(solver='sag', tol=1e-1, C=1.e4 / X.shape[0]))
-]
-
-xx = 1. - np.array(heldout)
-
-for name, clf in classifiers:
-    print("training %s" % name)
-    rng = np.random.RandomState(42)
-    yy = []
-    for i in heldout:
-        yy_ = []
-        for r in range(rounds):
-            X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=i, random_state=rng)
-            clf.fit(X_train, y_train)
-            y_pred = clf.predict(X_test)
-            yy_.append(1 - np.mean(y_pred == y_test))
-        yy.append(np.mean(yy_))
-    plt.plot(xx, yy, label=name)
-    \end{lstlisting}
-    \label{fig:wrapper_code}
-\caption{Illustration of the issue of using \texttt{frompyfunc} function to convert function to \texttt{ufunc}.}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \caption{Caption}
-    \includegraphics[width=\linewidth]{figure/classifier_comparisons/general.png}
-    \caption{Number of significant digits (General view).}
-    \label{fig:classifier_comparisons_general}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \caption{Caption}
-    \includegraphics[width=\linewidth]{figure/classifier_comparisons/mean_prediction_wo_legend.pdf}
-    \caption{Number of significant digits of the accuracy and predictions for the five classifiers. 
-    Yellow points represents the accuracy for each round and blue points the average accuracy 
-    over the 20 rounds. We can see that the Perceptron classifier has the highest stability.}
-    \label{fig:classifier_comparisons_mean_predictions}
-\end{figure}
 
@@
 
-\subsubsection{Cluster IRIS}
+% \subsubsection{Adaboost}
+\paragraph{Adaboost}
+This test compare a decision trees boosted with 300 estimators using the AdaBoost.R2~\cite{drucker1997improving} algorithm with
+a single decision tree regressor on a 1D sinusoidal dataset with a small amount of Gaussian noise. 
+The depth is fixed at 4. 
+% The example shows that as the number of boosts is increased the regressor can fit more detail.
+
+% RR Good 48 \\
+% MCA: arange issue /  bootstrap\_idx = random\_state.choice(a=np.arange(\_num\_samples(X)), size=\_num\_samples(X), replace=True, p=sample\_weight) / len(a) != len(p)
+
+\paragraph{Online classifier comparison}
+
+This example compares how the following online solvers perform on the hand-written digits dataset:
+Stochastic Gradient Descent (SGD) with maximum iterations fixed to 100, 
+Averaged Stochastic Gradient Descent (ASGD),
+Perceptron, Passive-Aggressive I with the hinge loss function, tolerance 
+and regularization fixed at $10^{-4}$ and $1$,
+Passive-Aggressive II with the squared hinge loss function, tolerance 
+and regularization fixed at $10^{-4}$ and $1$, and Stochastic Average Gradient (SAG)
+with the tolerance and regularization fixed at $10^{-4}$ and $5.10^{-8}$.
+
+% RR: stable 48 bits. \\
+% MCA: Index issue
+
+\paragraph{Bayesian Ridge Regression}
+
+This test compares a Bayesian Ridge Regression (BRR) to the Ordinary Least Squares (OLS) estimator on a synthetic dataset and for one-dimensional regression using polynomial feature expansion.
+Although the test does not raise a runtime error, the coefficients computed from the fitting for the synthetic dataset are \texttt{Not-A-Number} (NaN) values for both BRR and OLS.
+\pytracer traces reveal that the SVD solver used is the root cause.
+Figure~\ref{fig:brr_svd_sig} shows
+the number of significant bits for the singular values SVD decomposition 
+For BRR, the SVD is directly called to compute the coefficient, while for the OLS, it is called during the Least-Squares minimization.
+Scikit-learn uses SciPy that itself uses the LAPACK library to compute the SVD.
+The LAPACK library has two main methods for computing the SVD: 
+\texttt{gesdd} and \texttt{gesvd}.
+The first one uses a Divide \& Conquer approach, while the second uses a QR decomposition.
+While both methods expect to have the same accuracy~\cite{nakatsukasa2013stable}, it appears that results diverge in practice with inaccurate results for the Divide \& Conquer method, as the sill opened an issue on the official LAPACK GitHub repository \href{https://github.com/Reference-LAPACK/lapack/issues/316}{github.com/Reference-LAPACK/lapack/issues/316} shows.
+For the Least-Square problem, the LAPACK library has three solvers, including \texttt{dgelss} that internally uses \texttt{gesdd} and \texttt{dgelsd} that uses \texttt{gesvd}.
+By using the \texttt{gesvd} (dgelsd) method instead of the \texttt{gesdd} (dgelss) one, the SVD is converging within the RR and Full MCA modes, with a number of significant bits of 44 on average.
 
@@
     \centering
-    \caption{Caption}
-    \includegraphics[width=\linewidth]{figure/cluster_iris/general.png}
-    \caption{Number of significant digits of the Cluster IRIS test.}
-    \label{fig:cluster_iris_general}
+    \includegraphics[width=\linewidth]{figure/BRR/BRR_coefs_sig.pdf}
+    \caption{Bayesian Ridge Regression coefficients within RR mode.
+    The \texttt{BRR\_*} points show the \texttt{BayesianRidge} results
+    using the \texttt{gesdd} and \texttt{gesvd} methods. 
+    The \texttt{OLS\_*} points show the \texttt{LinearRegression} results
+    with the \texttt{dgelsd} and \texttt{dgelss} methods.
+    We can see that using the Divide \& Conquer method for the SVD
+    (\texttt{gesdd} and  \texttt{dgelsd})
+    gives very low precision
+    results for \textit{BRR} and even \texttt{NaN} values (star points) for \textit{OLS}. By switching to the \texttt{gesvd} method, 
+    results have a precision of 42 bits in average.
+    }
+    \label{fig:brr_svd_sig}
 \end{figure}
+
+% the coefficient weights are slightly shifted toward zeros, which stabilises them.
+% As the prior on the weights is a Gaussian prior, the histogram of the estimated weights is Gaussian.
+% The estimation of the model is done by iteratively maximizing the marginal log-likelihood of the observations.
+% We also plot predictions and uncertainties for Bayesian Ridge Regression for one dimensional regression using polynomial feature expansion.
+Note the uncertainty starts going up on the right side of the plot.
+This is because these test samples are outside of the range of the training samples.
+
+% RR: solution mean 15-24 / std 20-30 \\
+% MCA: SVD did not converge
+
+\paragraph{K-Means Clustering}
+
+This test uses the K-means to cluster the IRIS dataset.
+% The plots display firstly what a K-means algorithm would yield using three clusters.
+It is then shown what the effect of a bad initialization is on the classification process: By setting n\_{init} to only 1 (default is 10), the amount of times that the algorithm will be run with different centroid seeds is reduced.
+The next plot displays what using eight clusters would deliver and finally the ground truth.
+
+% RR Very stable (labels with highest precision) \\
+% MCA: Divergence
+
+\paragraph{Covariance estimation}
+
+This example shows covariance estimation with Mahalanobis distances on Gaussian distributed data.
+
+% For Gaussian distributed data, the distance of an observation xi to the mode of the distribution can be computed using its Mahalanobis distance:
+
+% d(μ,Σ)(xi)2=(xi−μ)TΣ−1(xi−μ)
+% where μ and Σ are the location and the covariance of the underlying Gaussian distributions.
+
+% In practice, μ and Σ are replaced by some estimates.
+The standard covariance maximum likelihood estimate (MLE) is very sensitive to the presence of outliers in the data set and therefore, the downstream Mahalanobis distances also are.
+It would be better to use a robust estimator of covariance to guarantee that the estimation is resistant to “erroneous” observations in the dataset and that the calculated Mahalanobis distances accurately reflect the true organization of the observations.
+
+% The Minimum Covariance Determinant estimator (MCD) is a robust, high-breakdown point (i.e. it can be used to estimate the covariance matrix of highly contaminated datasets, up to
+
+% nsamples−nfeatures−12 outliers) estimator of covariance. The idea behind the MCD is to find
+
+% nsamples+nfeatures+12 observations whose empirical covariance has the smallest determinant, yielding a “pure” subset of observations from which to compute standards estimates of location and covariance.
+The MCD was introduced by P.J.Rousseuw in 1.
+
+% This example illustrates how the Mahalanobis distances are affected by outlying data.
+Observations drawn from a contaminating distribution are not distinguishable from the observations coming from the real, Gaussian distribution when using standard covariance MLE based Mahalanobis distances.
+Using MCD-based Mahalanobis distances, the two populations become distinguishable.
+Associated applications include outlier detection, observation ranking and clustering.
+
+% RR: Traces diverge but precision seems stable (~48bits) \\
+% Main computation is in a loop that might be take extra steps to ends. \\
+% MCA: arange issue
+
+\paragraph{Decision Tree Regression}
+
+This test uses a decision tree to fit a sine curve with added noise.
+
+% A 1D regression with decision tree.
+% The decision trees is used to fit a sine curve with addition noisy observation. As a result, it learns local linear regressions approximating the sine curve.
+% We can see that if the maximum depth of the tree (controlled by the max\_depth parameter) is set too high, the decision trees learn too fine details of the training data and learn from the noise, i.e.
+they overfit.
+
+% RR Fit ok (50bits) , missing predict \\
+% MCA Fit ok (50bits) , missing predict
+
+\paragraph{Digits Classification}
+
+This test uses a Support Vector Classifier to recognize images of hand-written
+digits. The digits dataset consists of 8x8 pixel images of digits
+
+% RR Very stable (highest precision) \\
+% MCA: Very stable (highest precision)
+
+\paragraph{Face Recognition}
+
+The face recognition test uses eigenfaces (eigenvector) and Support Vector Machines (SVMs) to classify faces from the Labeled Faces in the Wild dataset~\cite{LFWTech}.
+This test uses a Principal Component Analysis (PCA) to extract the eigenfaces and then trains an SVM classifier to predict the name associated with a visage.
+This test is the only one to raise an error within RR mode due to a non-convergence of the Singular Value Decomposition (SVD) performed during the PCA.
+In this test, the PCA uses the Randomized SVD~\cite{halko2011finding} variant that first computes a low-rank approximation of the input matrix by using a stochastic algorithm and then uses this approximation as the input for the SVD.
+It is during the computation of this SVD that the test raised an error.
+
+Scikit-learn uses SciPy that itself uses the LAPACK library to compute the SVD. The LAPACK library has two main methods for computing the SVD: 
+\texttt{gesdd} and \texttt{gesvd}.
+The first one uses a Divide \& Conquer approach, while the second uses a QR decomposition.
+While both methods expect to have the same accuracy~\cite{nakatsukasa2013stable}, it appears that results diverge in practice with inaccurate results for the Divide \& Conquer method, as the sill opened an issue on the official LAPACK GitHub repository \href{https://github.com/Reference-LAPACK/lapack/issues/316}{github.com/Reference-LAPACK/lapack/issues/316} shows.
+The \texttt{randomized\_svd} scikit-learn function uses the Divide \& Conquer method for the SVD.
+
+By using the \texttt{gesvd} method instead of the \texttt{gesdd} one, the SVD is converging within the RR mode.
+Moreover, figure~\ref{fig:randomized_svd_S} shows the precision of the eigenvalues computed, varying between 15 and 20 bits out of the 24 available in single precision.
+Finally, the classifier metrics (precision, recall, F1-score, and support) are identical to the IEEE execution, meaning that the test is as precise as the original execution.
+
+In conclusion, the MCA model was helpful to detect the instability of the \texttt{gesdd} method that has been notified in several GitHub issues, including the LAPACK repository.
+It is worth mentioning that recently, a Pull Request has been submitted to let the user select the SVD method and avoid this kind of issue.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}{0.3\linewidth}
+    \includegraphics[width=\linewidth]{figure/face_recognition/randomized_svd_ret_U_sig_zoom.png}
+    \caption{Left matrix $U$ of the SVD decomposition}
+    \label{fig:randomized_svd_U}
+    \end{subfigure}
+    \begin{subfigure}{0.3\linewidth}
+    \includegraphics[width=\linewidth]{figure/face_recognition/randomized_svd_ret_S_sig.png}
+    \caption{Singular values $\Sigma$ of the SVD decomposition}
+    \label{fig:randomized_svd_S}
+    \end{subfigure}
+    \begin{subfigure}{0.3\linewidth}
+    \includegraphics[width=\linewidth]{figure/face_recognition/randomized_svd_ret_V_sig_zoom.png}
+    \caption{Right matrix $V$ of the SVD decomposition}
+    \label{fig:randomized_svd_V}
+    \end{subfigure}
+    \caption{Number of significant bits of the \texttt{randomized\_svd} function in the 
+    \texttt{face\_recognition} test using the \texttt{gesvd} SVD method within RR mode.
+    Figures~\ref{fig:randomized_svd_U},~\ref{fig:randomized_svd_S}, and~\ref{fig:randomized_svd_V}
+    show respectively the values $U$, $\Sigma$ and $V.$
+    Using this method makes the \texttt{randomized\_svd} converging contrary to the \texttt{gesdd} method that raised a runtime error. 
+    }
+    \label{fig:face_recognition_svd}
+\end{figure}
+
+% RR: Crash due to FP32 use. Does FP64 converge? No. Does sgsvd converge? Yes
+
+% MCA: arange issue
+
+% File "/usr/local/lib/python3.8/site-packages/sklearn/datasets/\_lfw.py", line 169, in \_load\_imgs
+%     faces[i, ...] = face
+% ValueError: could not broadcast input array from shape (49,37) into shape (50,37)
+
+\paragraph{L1 Penalty}
+
+This test compares the percentage of zero coefficients for logistic regression
+by varying the penalty (L1, L2 and Elastic-Net) and regularization (1, 0.1, 0.01) parameters. Large regularization value gives more freedom to the model
+while small value puts more constraints on the model.
+
+% of L1, L2 and Elastic-Net penalty.
+
+% Comparison of the sparsity (percentage of zero coefficients) of solutions when L1, L2 and Elastic-Net penalty are used for different values of C.
+We can see that large values of C give more freedom to the model.
+Conversely, smaller values of C constrain the model more.
+In the L1 penalty case, this leads to sparser solutions.
+As expected, the Elastic-Net penalty sparsity is between that of L1 and L2.
+% We classify 8x8 images of digits into two classes: 0-4 against 5-9. The visualization shows coefficients of the models for varying C.
+
+% RR: ok \\
+% MCA: stable for L1 and L2, not for Len but coef have less zeroes.
+
+\paragraph{Lasso and Elastic-Net}
+
+This test compares the Lasso and Elastic-Net regression models
+on a corrupted signal.
+
+% Estimates Lasso and Elastic-Net regression models on a manually generated sparse signal corrupted with an additive noise. Estimated coefficients are compared with the ground-truth.
+
+% RR: Good (48 bits on coefs) \\
+% MCA: Good like RR if we exclude one trace that fails due to arange issue
+
+\paragraph{Separating hyperplane}
+
+This test uses a linear Support Vector Machine (SVM) classifier trained using the Stochastic Gradient Descent (SGD) method to find the maximum separating hyperplane in 2D.
+The test trains the SVM with 50 random points separated in 2 clusters with hyperparameters $\alpha=0.01$ and using the hinge loss function.
+Once trained, the test generates a $[-1,5]\times[-1,5]$ Cartesian grid and predicts the class label for each point with integer coordinates.
+Figure~\ref{fig:separating_hyperplan} shows the ratio $\frac{mean}{std}$ with RR mode for each point of the grid (square) and the training dataset (circle), the two colors representing the two classes.
+We can see that white points close to the separating hyperplane are highly unstable with a number of significant bits below 0, meaning that
+the classifier hesitates about the class to predict.
+
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=\linewidth]{figure/separating_hyperplan/hyperplan.png}
+%     \caption{Ratio $mean/std$ of Separating hyperplane test result within RR mode.
+%     Circle and square points represent respectively the train and test dataset.
+%     The color represents the predicted class. We can see that 
+%     instability is high around the hyperplane which is coherent with 
+%     the fact the classifier has difficulty to decide in which side of the hyperplane the 
+%     point is.}
+%     \label{fig:separating_hyperplan}
+% \end{figure}
+
+\begin{figure}
+    \centering
+    \begin{subfigure}{.3\linewidth}
+    \includegraphics[width=\linewidth]{figure/separating_hyperplan/hyperplan.png}
+    \caption{}
+    \label{fig:hyperplan_sig}
+    \end{subfigure}
+    \begin{subfigure}{.3\linewidth}
+    \includegraphics[width=\linewidth]{figure/SVM/non_weighted.png}
+    \caption{}
+    \label{fig:SVM_nw_sig}
+    \end{subfigure}
+    \begin{subfigure}{.3\linewidth}
+    \includegraphics[width=\linewidth]{figure/Weighted/non_weighted.png}
+    \caption{}
+    \label{fig:weighted_nw_sig}
+    \end{subfigure}
+    \begin{subfigure}{.3\linewidth}
+    \includegraphics[width=\linewidth]{figure/separating_hyperplan/hyperplan_zoom.png}
+    \caption{}
+    \label{fig:hyperplan_sig_zoom}
+    \end{subfigure}
+    \begin{subfigure}{.3\linewidth}
+    \includegraphics[width=\linewidth]{figure/SVM/weighted.png}
+    \caption{}
+    \label{fig:SVM_w_sig}
+    \end{subfigure}
+    \begin{subfigure}{.3\linewidth}
+    \includegraphics[width=\linewidth]{figure/Weighted/weighted.png}
+    \caption{}
+    \label{fig:weighted_w_sig}
+    \end{subfigure}
+    \caption{Three examples of separating hyperplane tests.
+All figures show the number of significant bits of the results for the following tests: \textit{Separating Hyperplane} on figures.~\ref{fig:hyperplan_sig} for the original colormap and~\ref{fig:hyperplan_sig_zoom} with a rescaled colormap.
+We can see that this test exhibits a poor precision with less than 3 bits significant, although only the sign of the number matter to predict on which side of the hyperplane the point is classified.
+We can see in figure~\ref{fig:hyperplan_sig_zoom} by rescaling the colormap that the instabilities are concentrated around the hyperplane.
+    Figures~\ref{fig:SVM_nw_sig},~\ref{fig:SVM_w_sig},~\ref{fig:weighted_nw_sig}, and~\ref{fig:weighted_w_sig} show respectively the results of tests    \textit{SVM} and~\textit{Weighted samples}.
+Figures~\ref{fig:SVM_nw_sig} and~\ref{fig:weighted_nw_sig} show the unweighted classification while figures~\ref{fig:SVM_w_sig} and~\ref{fig:weighted_nw_sig} the classification taking into account the weights.
+We can see that taking into account the weight classes allows a better separating.}
+\label{fig:my_label}
+\end{figure}
+
+\paragraph{MNIST classification}
+
+This test fits a logistic regression with the SAGA solver with the L1 penalty  
+on a subset of the MNIST digits classification task.
+
+% Here we fit a multinomial logistic regression with L1 penalty on a subset of the MNIST digits classification task.
+We use the SAGA algorithm for this purpose: this a solver that is fast when the number of samples is significantly larger than the number of features and is able to finely optimize non-smooth objective functions which is the case with the l1-penalty.
+Test accuracy reaches > 0.8, while weight vectors remains sparse and therefore more easily interpretable.
+% Note that this accuracy of this l1-penalized linear model is significantly below what can be reached by an l2-penalized linear model or a non-linear multi-layer perceptron model on this dataset.
+
+% RR: Very stable \\
+% MCA: Parse by excluding a trace that failed due to an arange issue
+
+\paragraph{Multitask Lasso}
+
+This test compares the Lasso and MultiTaskLasso regression models
+on a corrupted signal.
+
+% The multi-task lasso allows to fit multiple regression problems jointly enforcing the selected features to be the same across tasks.
+This example simulates sequential measurements, each task is a time instant, and the relevant features vary in amplitude over time while being the same.
+The multi-task lasso imposes that features that are selected at one time point are select for all time point.
+This makes feature selection by the Lasso more stable.
+
+% RR: Stable (44~53 bits for coef) \\
+% MCA: Stable like RR if we exclude a trace that failed due index issue
+
+\paragraph{Orthogonal matching}
+
+This test uses the Orthogonal Matching Pursuit algorithm
+for recovering a sparse signal from a noisy measurement encoded with a dictionary.
+
+% RR: Very stable \\
+% MCA: Very stable
+
+\paragraph{PCA decomposition}
+
+This test makes a PCA decomposition on a synthetic dataset.
+% These figures aid in illustrating how a point cloud can be very flat in one direction–which is where PCA comes in to choose a direction that is not flat.
+
+% rr: stable (48 bits on components) \\
+% mca: stable (48 bits on components)
+
+\paragraph{Robust Linear Regression}
+
+This test compare the linear and  RANSAC regression methods on a noisy data.
+% In this example we see how to robustly fit a linear model to faulty data using the RANSAC algorithm.
+
+% RR: Very stable \\
+% MCA: Very stable if we exclude two traces that failed due to arange/index issues
+
+\paragraph{Segmentation Toy}
+
+This test uses a spectral clustering to separate connected circles in an image.
+
+% In this example, an image with connected circles is generated and spectral clustering is used to separate the circles.
+
+% In these settings, the Spectral clustering approach solves the problem know as ‘normalized graph cuts’: the image is seen as a graph of connected voxels, and the spectral clustering algorithm amounts to choosing graph cuts defining regions while minimizing the ratio of the gradient along the cut, and the volume of the region.
+
+% As the algorithm tries to balance the volume (ie balance the region sizes), if we take circles with different sizes, the segmentation fails.
+
+% In addition, as there is no useful information in the intensity of the image, or its gradient, we choose to perform the spectral clustering on a graph that is only weakly informed by the gradient.
+This is close to performing a Voronoi partition of the graph.
+
+% In addition, we use the mask of the objects to restrict the graph to the outline of the objects.
+In this example, we are interested in separating the objects one from the other, and not from the background.
+
+% RR Stable \\
+% MCA: Stable if we exclude three traces that failed due to index issue
+
+\paragraph{SVM}
+
+This test uses an plain and weighted classes SVC to find the best hyperplan separating an unbalanced dataset.
+
+% Find the optimal separating hyperplane using an SVC for classes that are unbalanced.
+
+% We first find the separating plane with a plain SVC and then plot (dashed) the separating hyperplane with automatically correction for unbalanced classes.
+
+% RR: stable (48 bits) \\
+% MCA: stable (48 bits)
+
+\paragraph{Tomography}
+
+This test compares the LASSO and Ridge regression models to 
+reconstruct an image from a set of projections for a dataset
+acquired from computed tomography.
+
+% This test shows the reconstruction of an image from a set of parallel projections, acquired along different angles. Such a dataset is acquired in computed tomography (CT).
+
+% Without any prior information on the sample, the number of projections required to reconstruct the image is of the order of the linear size l of the image (in pixels).
+For simplicity we consider here a sparse image, where only pixels on the boundary of objects have a non-zero value.
+Such data could correspond for example to a cellular material.
+Note however that most images are sparse in a different basis, such as the Haar wavelets.
+Only l/7 projections are acquired, therefore it is necessary to use prior information available on the sample (its sparsity): this is an example of compressive sensing.
+
+% The tomography projection operation is a linear transformation.
+In addition to the data-fidelity term corresponding to a linear regression, we penalize the L1 norm of the image to account for its sparsity.
+The resulting optimization problem is called the Lasso.
+We use the class Lasso, that uses the coordinate descent algorithm.
+Importantly, this implementation is more computationally efficient on a sparse matrix, than the projection operator used here.
+
+% The reconstruction with L1 penalization gives a result with zero error (all pixels are successfully labeled with 0 or 1), even if noise was added to the projections.
+In comparison, an L2 penalization (Ridge) produces a large number of labeling errors for the pixels.
+Important artifacts are observed on the reconstructed image, contrary to the L1 penalization.
+Note in particular the circular artifact separating the pixels in the corners, that have contributed to fewer projections than the central disk.
+
+% RR Divergence \\
+% MCA Index issue
+
+\paragraph{Weighted samples}
+
+This test uses a SGD to separate weighted points by 
+taking into account or the not the weights.
+
+% RR Stable (30~48 bits on coef) \\
+% MCA Unstable (0 bits on coef)
 
@@
 
-\subsection{Overhead}
-
-Pytracer instrumentation overhead comes from the time spent to instrument module (initial ?zation overhead)
+\subsection{Tracing}
+
+Pytracer instrumentation overhead comes from the time spent to instrument module (initialization overhead)
 before executing the targeted application plus the cost for dumping the data during the execution (running overhead).
-However, initialization overhead is amortized when traced applications are above ....
-Table~\ref{tab:pytracer_overhead} summaries the slowdown measure on pyAFQ test.
-We can see that Pytracer only a gives reasonable slowdown of $\times 6$.
-
-\begin{table}[]
-    \centering
-    \begin{tabular}{c|c|c|c|c}
-         Pytracer & Verificarlo Instrumentation & Backend & Time (hours:minutes:seconds) & Overhead \\
-         \hline 
-         No & No & - & 00:30:51 & 1 \\
-         No & Yes & IEEE & 01:32:56 & 3 \\
-         No & Yes & RR & 16:52:08 & 32 \\
-         Yes & No & - & 03:11:07 & 6  \\
-         Yes & Yes & IEEE & 11:14:33 & 22 \\
-         Yes & Yes & RR & 25:05:54 & 48 \\
+The initialization overhead is proportional the number of functions and classes traced. 
+However, initialization overhead is amortized when traced applications are above 8 seconds, which is proportional to 
+the number of functions and classes traced.
+Table~\ref{tab:pytracer_overhead} summaries the slowdown measure on SciPy
+and scikit-learn tests.
+We can see that Pytracer gives slowdown of $\times 17$ and
+$\times 3.5$ if we subtract the initialization step.
+By adding fuzzy, we have an average slowdown of $\times 37$ for RR mode and $\times 43$ for Full MCA.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{figure/performance.pdf}
+    \caption{
+    The figure presents the \pytracer tracing overheads: \textit{Slowdown} is the actual overhead, computed as the ratio between the execution time without and with \pytracer.
+This slowdown can be high for the tests running less than 8 seconds because \pytracer spends most of its time in the initialization step.
+Since this step is a constant factor of the number of functions instrumented, we also plot the slowdown of the instrumentation itself (\textit{Slowdown (Instrumentation)} calculated by subtracting the initialization time.
+    The \textit{Slowdown (RR)} and \textit{Slowdown (MCA)} colors show the slowdown of \pytracer 
+    using the fuzzy environment with RR and Full MCA modes.
+    The first four tests measure the initialization steps depending on the modules instrumented.
+    }
+    \label{fig:performances}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{figure/parsing_time.pdf}
+    \caption{\pytracer time to aggregate traces.}
+    \label{fig:performance_parsing_time}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{figure/parsing.pdf}
+    \caption{\pytracer trace and aggregation files size.
+    The figure presents the size measured for the trace and the aggregation size files.}
+    \label{fig:performance_parsing_size}
+\end{figure}
+
+\begin{table}
+\centering
+\begin{subfigure}[t]{.75\linewidth}
+    \centering
+    \begin{tabular}{|l|c|c|c|c|}
+    \hline 
+    Application & Original & Pytracer only & RR & MCA \\
+    \hline 
+    Loading & 0.456 & 8.152 & - & - \\
+    \hline
+    discrete\_cosine\_transform & 0.280 & 8.176 & 10.203 & - \\ 
+    fft\_1D & 0.650 & 9.075 & 11.345 & - \\
+    fft\_2D & 0.311 & 9.500 & 11.929  & 16.433   \\
+    \hline
+    interpolation\_1D & 0.377 & 8.803  & 11.954  & -   \\
+    multivariate\_data &0.626 & 8.648 &  12.711  & - \\
+    bspline & 0.109  & 9.050 & 13.396  & 16.830   \\
+    spline\_1D & 0.111 & 8.618 & 10.960   & - \\
+    spline\_2D & 0.655 & 8.649 & 19.424  & - \\
+    \hline
+    broyden\_fletcher\_goldfarb\_shanno &0.475 & 8.292 & 11.033 & 13.685 \\
+    global\_optimization &1.257 & 55.916  & 93.322  & - \\
+    slsqp & 0.469 & 8.192 & 10.795 & 12.439  \\
+    least\_square\_minimization & 0.505 & 10.151  & 13.888 & -  \\
+    nelder\_mead\_simplex & 0.471 & 8.418  & 11.382  & 12.792  \\
+    newton\_conjugate\_gradient & 0.487 & 8.548  & 11.956  & 14.281 \\
+    root\_findings & 0.462 & 8.198  & 10.787   & - \\
+    root\_finding\_large & 0.801 & 11.525 & 41.493   &  82.701  \\
+    root\_finding\_large\_preconditioned & 0.702 & 10.580 & 33.199   & 57.579  \\
+    trust\_region\_exact & 0.482 & 8.170 & 10.400  & 12.524 \\
+    trust\_region\_truncated\_generalized\_lanczos & 0.459 & 8.457 & 11.216 & 13.245  \\
+    trust\_region\_newton\_conjugate\_gradient & 0.479 & 8.538 & 11.179 & 13.488 \\
+    \hline
+    Adaboost &1.388 &14.553 &  20.999 & - \\
+    Bayesian Ridge Regression & 1.086 & 10.344 & 90.299 & -  \\
+    Online classifier comparison & 15.964 & 72.691 & 2104.114 & -  \\
+    K-Means Clustering & 1.621 & 17.614  & 34.005 & 52.902   \\
+    Covariance estimation & 1.357 & 11.755 & 23.964  & -   \\
+    Decision Tree Regression & 1.185 & 11.194 & 15.760 & 15.918  \\
+    Digits Classification & 1.672 & 12.725 & 40.634 & - \\
+    Face Recognition & 32.159  & 74.356 & - & - \\
+    L1 Penalty & 1.568 & 12.591 & 65.547 & 128.220 \\
+    Lasso and elastic net & 1.057 & 9.903 & 17.078 & -  \\
+    Separating hyperplan & 1.376 & 11.532  & 22.333 & 25.036 \\
+    MNIST classification & 19.650 & 37.838 & 402.389  & - \\
+    Multitask Lasso & 1.090 &10.196 & 15.025  & - \\
+    Orthogonal matching & 1.161 & 12.129 & 21.779   & 31.135 \\
+    PCA decomposition & 1.239 & 10.642 & 15.520 & 17.952    \\
+    Robust Linear Regression & 1.370 & 11.144  & 14.280  & - \\
+    Segmentation toy &1.679 & 22.385 & 87.811  & - \\
+    SVM & 1.403 & 11.737 & 23.203 & 24.126   \\
+    Tomography & 11.108 & 40.177  & 1376.134 & -  \\
+    Weighted samples & 1.358 & 11.768 & 21.255 & 20.541   \\
+    \hline
     \end{tabular}
-    \caption{Overheads of \pytracer on PyAFQ experiment with and without fuzzy.}
+\end{subfigure}
+    \caption{\pytracer tracing performances.}
     \label{tab:pytracer_overhead}
 \end{table}
+
+% \begin{table}[]
+%     \centering
+%     \begin{tabular}{c|c|c|c|c}
+%          Pytracer & Verificarlo Instrumentation & Backend & Time (hours:minutes:seconds) & Overhead \\
+%          \hline 
+%          No & No & - & 00:30:51 & 1 \\
+%          No & Yes & IEEE & 01:32:56 & 3 \\
+%          No & Yes & RR & 16:52:08 & 32 \\
+%          Yes & No & - & 03:11:07 & 6  \\
+%          Yes & Yes & IEEE & 11:14:33 & 22 \\
+%          Yes & Yes & RR & 25:05:54 & 48 \\
+%     \end{tabular}
+%     \caption{Overheads of \pytracer on PyAFQ experiment with and without fuzzy.}
+%     \label{tab:pytracer_overhead}
+% \end{table}
 
@@
 
-Pytracer produces traces during the tracing phase that must be aggregated before visualizing.
-Each trace is read sequentially until the end of the file. 
-For the moment, Pytracer is not able to merge traces but we would like to extend it.
-We measure the postprocessing time depending on the regularity of the 
-trace and the batchsize.
+The figures~\ref{fig:performance_parsing_time} and~\ref{fig:performance_parsing_size} show
+the postprocessing time and trace's sizes produced by \pytracer.
+We only report time for parsing and aggregation that have been successful.
+We measure a throughput of 7MB/s by taking the ratio size over time. 
+Finally, \pytracer has been tested on PyAFQ~\cite{kruper2021evaluating}, a neuroimaging Python tool
+to automated fiber quantification with generated traces of 
+1TB that \pytracer was able to handle and fluently visualize.
 
@@
 \pytracer does not make any assumption about the noise model used to estimate uncertainties but has been tested with the MCA 
-through the fuzzy ecosystem on two broadly used scientific libraries for Python with a partial success.
-
-As we shown in the section~\ref{sec:impact_mca_modes}, using the Full MCA mode leads to run-time errors
-that has a considerable impact on the proper functioning of the execution. This is unfortunate since these
-errors do not reflect real numerical errors but errors related to perturbations that should not occur.
-Fixing this misbehaviour would greatly help in the use of Full MCA mode since this mode allows simulating catastrophic
-cancellations which are common sources of numerical errors. By preserving exact operations, RR mode is far more conservative 
-and can be used more easily even though it does not simulate all perturbations that might be encountered.
-
-Also, by using a postprocess analysis to aggregate traces, \pytracer falls in the same pitfalls than veritracer
-and is limited to aggregate traces where execution flow path extremely diverge. A posteriori reconstruction
-is a challenging task as one must be able to identify precisely flow path taken and to find synchronization points
-to pursue the analysis. We retrieve for example this divergence behaviour in two general classes of numerical schemes:
-iterative methods and optimization processes. One solution to overcome this issue is to 
-integrate method used in code coverage analysis to keep track of flow paths taken in addition to the backtraces.
-But this would increase the complexity of the postprocess analysis as well as an extra slowdown factor.
-However, we believe that by coupling the gantt chart with a static analysis, \pytracer would be able to catch 
-some divergence patterns occurring within a function. Indeed, by instrumenting at the function level, \pytracer 
-has a view on function's callees (i.e. the functions that are called within a function) and thus should be able to
-partially detect flow divergences.
-
-By design principle, \pytracer is flexible on the noise model used although we only test it with the MCA model in our experiments.
-But we would like to compare different models against MCA in future works to see the resulting differences. 
-In particular, although \pytracer only works 
-on sequential application for the moment, it can be used to analyze parallel section internal to a function.
-The only restriction being that the section does not call other functions traced by \pytracer, 
-we would fall in the previous issue of divergence if it would not be the case.
-Since \pytracer only care about inputs and outputs of a function, the order of internal operations are transparent for it
-and thus should be able to handle those cases.
-
-Finally, elementary arithmetic operations are not instrumented by \pytracer and it can be a barrier to deeper analysis.
-However, we believe that an instrumentation at the function level present two advantages:
-it first limits the size of the traces since only inputs and outputs of a function are dumped instead 
-of a full report which, on one hand, decrease the overhead of the instrumentation and, on the other hand,
-help the user to quickly identify instabilities. One of the pitfalls can be to overwhelm the user with too much information, 
-which makes analysis more difficult. Nevertheless, the analysis at fine granularity can be interesting 
-at a final step of the understanding. Such an analysis would require a different instrumentation approach
-by for example working at the Abstract Syntax Tree (AST) level since it is trivial to get it in Python.
-An ideal way to do that would be to be able to extract and replay a function,
-in the same vein as the CERE~\cite{castro2015cere} tool does but for Python, and use an AST instrumentation to analyze step by step 
+through the fuzzy ecosystem on two broadly used scientific libraries for Python with partial success.
+
+As we showed in section~\ref{sec:impact_mca_modes}, using the Full MCA mode leads to runtime errors that have a considerable impact on the proper functioning of the execution, which is unfortunate since these
+errors do not reflect actual numerical errors but errors related to perturbations that should not occur.
+Fixing this misbehavior would greatly help use Full MCA mode since this mode allows simulating catastrophic cancellations, which are familiar sources of numerical errors.
+By preserving exact operations, RR mode is far more conservative and so easy to use even though it does not simulate all perturbations that might be encountered.
+
+Also, using a post-process analysis to aggregate traces, \pytracer falls in the same pitfalls as veritracer and is limited to aggregate traces where the execution flow path extremely diverges.
+Therefore, a posteriori reconstruction
+is a challenging task as one must precisely identify the flow path taken and find synchronization points to pursue the analysis.
+We retrieve, for example, this divergence behavior in two general classes of numerical schemes: iterative methods and optimization processes.
+One solution to overcome this issue is to integrate methods used in code coverage analysis to keep track of flow paths taken and the backtraces.
+However, this would increase the complexity of the postprocess analysis as well as an extra slowdown factor.
+However, we believe that by coupling the Gantt chart with static analysis, \pytracer would catch some divergence patterns occurring within a function.
+Indeed, by instrumenting at the function level, \pytracer has a view on function's callees (i.e., the functions called within a function) and thus should partially detect flow divergences.
+
+By design principle, \pytracer is flexible on the noise model used, although we only test it with the MCA model in our experiments.
+Nevertheless, we would like to compare different models against MCA in future works to see the resulting differences. 
+In particular, although \pytracer only works on a sequential application for the moment, it can be used to analyze parallel sections internal to a function.
+The only restriction is that the section does not call other functions traced by \pytracer; we would fall into the previous issue of divergence if it would not be the case.
+Since \pytracer only cares about inputs and outputs of a function, the order of internal operations is transparent for it and thus should be able to handle those cases.
+
+Finally, \pytracer does not instrument elementary arithmetic operations, and it can be a barrier to more profound analysis.
+However, we believe that instrumentation at the function level presents two advantages: it first limits the size of the traces since only inputs and outputs of a function are dumped instead of a full report which, on the one hand, decrease the overhead of the instrumentation and, on the other hand, help the user to identify instabilities quickly.
+One of the pitfalls can be overwhelming the user with too much information, which makes analysis more difficult.
+Nevertheless, the analysis at fine granularity can be interesting at the final step of the understanding.
+Such an analysis would require a different instrumentation approach by, for example, working at the Abstract Syntax Tree (AST) level since it is trivial to get it in Python.
+An ideal way to do that would be to be able to extract and replay a function, in the same vein as the CERE~\cite{castro2015cere} tool does but for Python, and use an AST instrumentation to analyze step by step
 the numerical quality of elementary operations within the fuzzy environment.
-Lastly, AST analysis can serve as a basis for finding relationship between variables which is another useful 
-piece of information for the user.
-
-\tristan{I moved this paragraph from results, it belongs here. It should be weaved in the discussion.}
-In addition to runtime errors that it raises, mismatching shapes is also a problem when aggregating
-traces as \pytracer will not be able to compute statistics for set of arrays having different shapes.
-Two solutions exist to overcome this issue: the first one is to not instrument the \texttt{PyArray\_Arange}
-function with MCA. The advantage is that it is easy to set up since it requires one extra line in the exclusion file.
+Lastly, AST analysis can serve as a basis for finding relationships between variables, which is valuable information for the user.
+
+In addition to runtime errors that it raises, mismatching shapes is also a problem when aggregating traces as \pytracer will not compute statistics for a set of arrays having different shapes.
+Two solutions exist to overcome this issue: the first one is to not instrument the \texttt{PyArray\_Arange} function with MCA.
+The advantage is that it is easy to set up since it requires one extra line in the exclusion file.
 However, the same kind of problem may appear somewhere else
-because, as we have seen, the operations being evolved are elementary. The chances that developers reproduce
-the same pattern is very probable. The second solution is to ensure that Full MCA mode preserved the exact operations.
-This solution has the advantage of not having to worry about which functions should be instrumented or not with MCA,
-but it is hard to achieve it in practice. Indeed, we rely on the MCA implementation provided by Verificarlo that 
-uses an internal precision to add the random perturbation that is higher 
-than the working precision for applying the random noise. The result is then rounded to the working precision before returning it so
-any residual noise lower than the working precision is lost. 
-Keeping track of that noise would requires to record each intermediate computation in a shadow memory 
-or at least to keep a tag about their exactness.
-\Yohan{This idea has emerged by discussing with the Verificarlo's team. 
-I must find a way to express that, and to do not give the impression that we discovered or suggest it.}
+because, as we have seen, the operations being evolved are elementary.
+The chances that developers reproduce the same pattern are very probable.
+The second solution is to ensure that the Full MCA mode preserves the exact operations.
+This solution has the advantage of not worrying about which functions should be instrumented or not with MCA, but it is hard to achieve it in practice.
+Indeed, we rely on the MCA implementation provided by Verificarlo that uses an internal precision to add the random perturbation that is higher than the working precision for applying the random noise.
+Verificarlo then rounds the result to the working precision before returning it, so any residual noise lower than the working precision is lost.
+Keeping track of that noise would require recording each intermediate computation in a shadow memory or keeping a tag about their exactness.
+\Yohan{This idea has emerged by discussing with Verificarlo's team. 
+I must find a way to express that and not give the impression that we discovered or suggest it.}
 This option would require more extra works than the first one but would ensure more consistent results.
 
-\Yohan{Discuss issue to visualize complex values (fft2D)}
-
 \section{Conclusion}
 
-\tristan{I moved this from the opening of Section 4, as this reads more like a summary of \pytracer's features than an experiment description.
+% \tristan{I moved this from the opening of Section 4, as this reads more like a summary of \pytracer's features than an experiment description.
 It should be refactored in 1-2 paragraphs summarizing the main properties of \pytracer.}
-Our strategy is to demonstrate that \pytracer is:
-\begin{itemize}
-    \item Domain agnostic: \pytracer is intended to work on any scientific Python applications, 
-    without specific domain specific languages or needs to rely on specific libraries.
-    We target two of the most common libraries used in scientific computing within Python, SciPy and Scikit-learn, as
-    well as a domain specific application in neuroimaging. We show that \pytracer works
-    well on these libraries, capturing most of the functions' module targeted.
-    \item Automatic: \pytracer objective is to offer an automatic instrumentation for any Python applications,
-    from small prototype to state-of-the-art scientific libraries. 
-    \item Scalable: \pytracer goal is to trace real world application and use case.
-    In that perspective, we use \pytracer on PyAFQ, a domain specific application in neuroimaging to compute 
-    tractograms, generating \pytracer traces up to 1TB. We demonstrate that \pytracer is able to 
-    handle this volume of data and to offer an interactive and fluent visualization to the user.
-    We also show that \pytracer instrumentation gives a slowdown of $\times 6$.
-    \item Fuzzy compatible: \pytracer aims at evaluating numerical stability by using injection noise model.
-    Although the noise model used is orthogonal to \pytracer tracing mechanism, we emphasis in these experiments 
-    on the MCA model through the fuzzy environment, and discuss its compatibility with \pytracer tracing mechanism
-    to point out limitations of the trace-based approach and to propose research tracks to overcome them.
-    It should be noted that experiments conducted in this paper are the first largest application of the fuzzy ecosystem
-    by the wide range of applications covered. We therefore found interesting to give a feedback about pitfalls and benefits encountered
-    in order to shed light on the good and bad practices for first-time users and hence democratize the usage of MCA.
-    Moreover, these analyses will help the fuzzy developers to increase the overall stability of fuzzy.
-\end{itemize}
+
+\pytracer is the first tool to propose a complete framework
+for analyzing and visualizing the numerical stability of Python codes.
+It works by automatically instrumenting Python libraries to produce numerical
+traces that can be interactively visualized through a Dash server.
+\pytracer does not require a manual intervention from the user neither rely on
+specific libraries and has been tested successfully tested on 
+intensively used on scientific libraries such as NumPy, SciPy and Scikit-learn.
+We demonstrated on a set of representative tests that \pytracer is scalable with an average instrumentation slowdown of $times 3.5$ and that is can handle traces up to 1TB while offering a fluent visualization to the user.
+Moreover,
+\pytracer is by construction agnostic to the noise model used 
+to evaluate the numerical stability. We demonstrated 
+that \pytracer can be used with the Monte Carlo Arithmetic 
+through the fuzzy environment. 
+The experiments conducted in this paper are the first largest application of the fuzzy ecosystem by the wide range of applications covered. It is also the occasion for us to
+provided  feedback 
+about pitfalls and benefits encountered
+in order to shed light on the good and bad practices for first-time users and democratize MCA's usage.
+\pytracer is available at \href{https://github.com/yohanchatelain/pytracer}{github://yohanchatelain/pytracer} under an open source licence.
+
+% \begin{itemize}
+
+%     \item Domain agnostic: \pytracer is intended to work on any scientific Python applications, without specific domain-specific languages or needs to rely on specific libraries.
+%     We target two of the most common libraries used in scientific computing within Python, SciPy and Scikit-learn, and a domain-specific application in neuroimaging.
+We show that \pytracer works well on these libraries, capturing most of the functions' module targeted.
+
+%     \item Automatic: \pytracer objective is to offer automatic instrumentation for Python applications,
+%     from small prototypes to state-of-the-art scientific libraries.
+
+%     \item Scalable: \pytracer goal is to trace real-world application and use case.
+%     In that perspective, we use \pytracer on PyAFQ, a domain-specific neuroimaging application to compute tractograms, generating \pytracer traces up to 1TB.
+We demonstrate that \pytracer can handle this volume of data and offer the user an interactive and fluent visualization.
+%     We also show that \pytracer instrumentation gives a slowdown of $\times 6$.
+
+%     \item Fuzzy compatible: \pytracer aims at evaluating numerical stability by using an injection noise model.
+%     Although the noise model used is orthogonal to \pytracer tracing mechanism, we emphasize in these experiments the MCA model through the fuzzy environment and discuss its compatibility with \pytracer tracing mechanism to point out limitations of the trace-based approach and to propose research tracks to overcome them.
+%     The experiments conducted in this paper are the first largest application of the fuzzy ecosystem by the wide range of applications covered.
+We, therefore, found it interesting to give feedback about pitfalls and benefits encountered
+%     in order to shed light on the good and bad practices for first-time users and democratize MCA's usage.
+%     Moreover, these analyses will help the fuzzy developers to increase the overall stability of fuzzy.
+
+% \end{itemize}
 

### 2021-11-04 paper.tex
Tristan review

@@
 \begin{abstract}
-Numerical stability is a crucial requirement of reliable scientific computational codes.
-Despite the recent large numbers of tools dedicated to evaluating codes' numerical stability, analyzing a complete program remains a handy task for the user.
-To address this issue, we propose \pytracer, an automatic profiler for analyzing numerical instabilities of Python applications.
-\pytracer automatically instruments Python code to produce numerical traces that can be visualized through a Dash server, allowing an interactive visualization of numerical stability.
-\pytracer is designed to work with any random noise model that simulates numerical instabilities, and we demonstrate its usage with the Monte Carlo Arithmetic through the fuzzy ecosystem.
-Finally, we demonstrate that pytracer can handle intensively used Python scientific libraries such as NumPy, SciPy, and Scikit-learn on a representative set of tests, at low cost with an average slowdown $\times 3.5$.
+Numerical stability is a crucial requirement of reliable scientific computing.
+However, despite the pervasiveness of Python in data science, analyzing large Python programs remains challenging due to the lack of scalable numerical analysis tools available for this language.
+To address this issue, we developed \pytracer, a profiler to quantify numerical instability in Python applications.
+\pytracer automatically instruments Python code to produce numerical traces and visualize them interactively in a Plotly dashboard.
+\pytracer is designed to work with any type of numerical noise model, including Monte-Carlo Arithmetic, random rounding or random data perturbations.
+We illustrate \pytracer's capabilities by testing the numerical stability of key functions in the SciPy and Scikit-learn Python libraries.
+\tristan{Add one sentence to summarize the findings} Finally, \pytracer slows down executions by only $3.5 \times$ on average.
 \end{abstract}
@@
 as NumPy~\cite{harris2020array}, SciPy~\cite{virtanen2020scipy}, scikit-learn~\cite{pedregosa2011scikit} or PyTorch~\cite{paszke2019pytorch} are used in hundreds of publications every year, providing a reference set of high-quality open-source core scientific libraries.
-Diverse research groups built numerous domain-specific data analysis pipelines from this ecosystem, leveraging Python's simplicity and expressivity.
+Researchers have built numerous domain-specific data analysis pipelines from this ecosystem, leveraging Python's simplicity and expressivity.
 
@@
 In unstable analyses, small numerical perturbations introduced by data noise, software and hardware updates, or parallelization lead to substantial deviations in final results and potentially different scientific conclusions, threatening the reliability of computational analyses.
-Numerical stability analyses need to be conducted systematically to address this issue.
-However, no practical tool currently exists to conduct such analyses on Python programs.
+To address this issue, numerical stability analyses need to be conducted systematically, however, no practical tool currently exists to conduct such analyses for Python programs.
 
 We present PyTracer, a numerical stability analyzer for Python programs.
-PyTracer adopts a dynamic approach that evaluates numerical stability using program execution traces, enabling scaling to large programs without manual intervention.
+PyTracer adopts a dynamic approach that evaluates numerical stability using program execution traces and is applicable to large programs without manual intervention.
 In contrast, theoretical approaches based on condition numbers or backward error analysis require detailed modeling of the program and its numerical implementation.
-Similarly, static code analysis techniques such as Frama-C~\cite{cuoq2012frama}, Gappa~\cite{de2010certifying} or Flocq~\cite{boldo2011flocq} hardly scale to large codebases, particularly in dynamically-typed languages such as Python.
-
-PyTracer estimates the number of significant digits of floating-point variables by combining program traces obtained with different numerical perturbations, which requires (1) tracing floating-point computations along program executions, (2) generating numerically-perturbed executions, and (3) visualizing stability evaluations.
-PyTracer addresses these requirements with (1) a dynamic instrumentation of Python functions, modules, and classes through meta-programming, (2) a ``fuzzy" Python interpreter instrumented with Monte-Carlo arithmetic, (3) an interactive Plotly dashboard to visualize stability measures throughout program executions.
-
-Through stability evaluations of 
-SciPy, scikit-learn, and PyAFQ~\cite{kruper2021evaluating} --- an analysis toolbox for diffusion magnetic resonance imaging --- we demonstrate PyTracer as a practical solution to review the numerical stability of extensive code bases.
-The remainder of this manuscript describes related approaches, presents the design of PyTracer, and demonstrates its potential in various use cases.
+Similarly, static code analysis techniques hardly scale to large codebases, particularly in dynamically-typed languages such as Python.
+
+PyTracer estimates the variability of floating-point variables by combining program traces obtained with different numerical perturbations, which requires (1) generating numerically-perturbed executions, (2) tracing floating-point computations along program executions, and (3) visualizing stability evaluations.
+PyTracer addresses these requirements with (1) a ``fuzzy" Python interpreter instrumented with Monte-Carlo arithmetic, (2) a dynamic instrumentation of Python functions, modules, and classes through meta-programming, (3) an interactive Plotly dashboard to visualize stability measures throughout program executions.
+
+Through stability evaluations of the
+SciPy and scikit-learn libraries, we demonstrate \pytracer as a practical solution to review the numerical stability of extensive code bases.
+The remainder of this manuscript describes related approaches, presents the design of \pytracer, and demonstrates its potential in various use cases.
 
@@
 
-Several tools have been and continue to be developed to assess numerical quality. Those tools can be divided into two main categories depending on whether they adopt a static or a dynamic approach.
-Static analysis produces theoretically valid error bounds, while dynamic analysis is generally more scalable, although it only provides experimental estimations.
+Several tools have been developed to assess numerical quality, divided into static and dynamic approaches.
+Static approaches typically analyze source code while dynamic approaches trace floating-point computations throughout executions.
+A detailed review of these approaches is presented in~\cite{cherubin2020tools}.
 \pytracer adopts the dynamic approach due to its scalability to large existing code bases.
@@
 
-The source-to-source technique requires a rewriting of the application to modify floating-point types. Among frameworks that adopted this technique,
-CADNA~\cite{jezequel2008cadna} is a library for C, C++ and Fortran implementing the CESTAC~\cite{vignes1993stochastic} stochastic arithmetic.
+The source-to-source technique requires a rewriting of the application to modify floating-point types. 
+CADNA~\cite{jezequel2008cadna} is a library for C, C++, and Fortran implementing the CESTAC~\cite{vignes1993stochastic} stochastic arithmetic.
 Shaman~\cite{demeure_phd} is a C++ library that uses a first-order error model to propagate numerical error.
@@
 
-The compiler-based approach uses a compiler to analyze or replace floating-point expressions with other models automatically. 
+The compiler-based approach instruments floating-point expressions at compile time. 
 Verificarlo~\cite{verificarlo} is a compiler that supports different types of arithmetic instrumentations, including MCA. 
 The work in~\cite{bao2013fly} modified the GNU Compiler Collection (GCC) to track local floating-point errors across executions.
-pLiner~\cite{guo2020pliner} is a root cause analyzer based on the Clang compiler that detects floating-point operations responsible for result variability using a source-to-source transformation at the Abstract Syntax Tree (AST)  level to rewrite parts of code with higher precision.
-PFPSanitizer~\cite{chowdhary2020debugging,chowdhary2021parallel}, is a compiler that uses parallel shadow execution to detect numerical issues using higher precision.
+pLiner~\cite{guo2020pliner} is a root-cause analyzer based on the Clang compiler that detects floating-point operations responsible for result variability using a source-to-source transformation at the Abstract Syntax Tree (AST) level to rewrite parts of code with higher precision.
+PFPSanitizer~\cite{chowdhary2020debugging,chowdhary2021parallel} is a compiler that uses parallel shadow execution to detect numerical issues using higher precision.
 FLiT~\cite{sawaya2017flit} is a framework to detect variability induced by compilers and their optimizations.
@@
 
-Dynamic Binary Instrumentation (DBI) operates on an executable directly, without the need for recompilation or manual changes, and is thus
-transparent to the programming language used. 
+Dynamic Binary Instrumentation (DBI) operates directly on executables, without the need for recompilation or manual changes. Therefore, it is applicable to any programming language.
 CraftHPC~\cite{lam2013dynamic} uses DBI to detect catastrophic cancellations at runtime.
-Verrou~\cite{fevotte2016verrou} is a Valgrind~\cite{nethercote2007valgrind} based tool that replaces on-the-fly
-floating-point operations by their stochastic arithmetic counterparts. FPDebug~\cite{benz2012dynamic} uses DBI to detect numerical inaccuracies by using shadow computations with higher precision.
+Verrou~\cite{fevotte2016verrou} is a Valgrind~\cite{nethercote2007valgrind} based tool that dynamically replaces
+floating-point operations with their stochastic arithmetic counterparts. FPDebug~\cite{benz2012dynamic} uses DBI to detect numerical inaccuracies by using shadow computations with higher precision.
 Herbgring~\cite{sanchez2017finding} is a Valgrind-based tool to detect
-numerical instabilities. It uses a shadow memory to detect precision losses by comparison with results obtained with the high-precision 
-MPFR library~\cite{fousse2007mpfr}. It is combined with symbolic computation to backtrack the root of the error.
-We can note that all methods based on a high-precision oracle suppose that computing with a large number of bits is sufficient to obtain an accurate result, which is not always true, see, for example, the famous Muller's sequence ~\cite{chatelain2018veritracer}.
+numerical instabilities.
+It uses a shadow memory to detect precision losses by comparison with results obtained at higher precision.
+It is combined with symbolic computation to backtrack the root of the error.
+We can note that all methods based on a high-precision oracle suppose that computing with a large number of bits is sufficient to obtain an accurate result, which is not always true (see for example, the famous Muller's sequence~\cite{chatelain2018veritracer} \tristan{it looks like your veritracer paper is the first time where the ``famous Muller's sequence" was described, is that so?}).
 
@@
 However, working at a binary level makes it difficult to access high-level information needed to debug and understand the source code logic.
-Conversely, the source-to-source approach provides a fine-grained control on the code being analyzed, bu itt lacks scalability, as rewriting large codes can be a tedious task.
+Conversely, the source-to-source approach provides a fine-grained control on the analyzed code, but it lacks scalability, as rewriting large codes can be a tedious task.
 Finally, the compiler-based approach takes advantage of the best of both by being automatic and having access to high-level information.
@@
 
-To the best of our knowledge, there is currently no tool dedicated to the numerical analysis of Python code.
-Existing tools for tracing Python code are dedicated to performance profiling, for time (cProfile)
+To the best of our knowledge, there is currently no tool dedicated to the numerical analysis of Python code. Existing tools for tracing Python code focus on  performance profiling for time (cProfile) 
 or memory consumption (memprofile). 
@@
 Moreover, the user needs to manually tag each variable to trace. Finally, according to the authors, Anteater does not scale to large traces.
-cProfile, memprofile, and Anteater use Python decorators as the main instrumentation technique, a Python mechanism to instrument a function by adding a line over a function declaration.
-While this method is appropriate when targeting specific functions, it is not feasible for large code bases where the location of potentially unstable code sections is unknown.
+cProfile, memprofile, and Anteater use Python decorators as the primary instrumentation technique, a Python mechanism to instrument a function by adding a line over a function declaration.
+While this method is appropriate when targeting specific functions, it is not feasible for large codebases where potentially unstable code sections are unknown.
 
 \label{sec:detecting-instabilities}
-\subsection{Detecting numerical instabilities}
-
-Three main approaches exist to detect numerical instabilities once floating-point computations are traced: stochastic arithmetic, uncertainty or sensitivity analysis, and random seed analysis.
-The main techniques for each approach are reviewed below.
+\subsection{Detecting numerical instabilities with stochastic arithmetic}
+\label{sec:mca}
 
@@
 
-\label{sec:mca}
-\subsubsection{Stochastic Arithmetic}
+% \subsubsection{Stochastic Arithmetic}
 
@@
 
+Three main approaches exist to detect numerical instabilities: stochastic arithmetic, uncertainty or sensitivity analysis, and random seed analysis.
+\tristan{add key references for uq/sa if any} \pytracer focuses on stochastic arithmetic \tristan{due to...}
 Stochastic arithmetic leverages randomness to estimate numerical instabilities coming from the use of floating-point representations. The main idea is to treat round-off errors 
 % \tristan{only round-off errors or all numerical errors?} 
-as random variables and to characterize them statistically.
+as random variables and characterize them statistically.
 
@@
 From these stochastic samples, one can then derive the number of significant digits in the computed result.
-Discrete Stochastic Arithmetic~\cite{vignes2004discrete} extends CESTAC to comparison operators implemented in the CADNA library.
+Discrete Stochastic Arithmetic~\cite{vignes2004discrete} extends CESTAC with comparison operators implemented in the CADNA library.
 
 Monte Carlo Arithmetic (MCA)~\cite{parker1997monte} uses the same principle but introduces two differences:
-(i) a virtual precision parameter, allowing to simulate reduced working precision,  and (ii) different perturbation modes, to introduce perturbations
+(i) a virtual precision parameter, allowing to simulate reduced working precision,  and (ii) different perturbation modes to introduce perturbations
 on function inputs or output.
-MCA simulates round-off errors by introducing random perturbations in floating-point computations. It replaces each floating-point number with its stochastic counterpart:
+MCA replaces each floating-point number with its stochastic counterpart:
 \[
@@
 \]
-where $\beta$ is the number base, $t$ the virtual precision and $\xi \in (-\frac{1}{2},\frac{1}{2})$ is a uniform variable.
+where $\beta$ is the number base, $t$ the virtual precision and $\xi \in (-\frac{1}{2},\frac{1}{2})$ is a random uniform variable.
 Virtual precision allows for the simulation of reduced working precision.
-MCA can be applied in three modes: Random Rounding (RR), Precision Bounding (PB), and full MCA, which respectively perturb either the output, the inputs, or both with the $inexact$ function.
+MCA can be applied in three modes: Random Rounding (RR), Precision Bounding (PB), and full MCA, which perturb either the output, the inputs, or both with the $inexact$ function.
 While the RR mode is equivalent to stochastic rounding, the PB mode allows identifying catastrophic cancellations.
 
-In stochastic arithmetic, numerical error is measured as the number of significant digits $s$ estimated among the sampled values.
+Stochastic arithmetic uses the number of significant digits $s$ estimated among the sampled values to quantify the numerical errors.
 A common formula to determine this number from MCA samples is the one reported in~\cite{parker1997monte}:
@@
 where $\mu$ and $\sigma$ are the sample mean and standard deviation of a variable sampled with MCA.  
-Recent variations of this formula that also provide confidence intervals are discussed in~\cite{sohier2018confidence}.
-
-\subsubsection{Uncertainty, sensitivity, and random seed analysis}
-
-Uncertainty analysis (UA) is a method to estimate the output distribution given an input distribution.
-Sensitivity analysis (SA) is a variation of UA that measures the local response to a small perturbation~\cite{loucks2017water}. 
-Several approaches for UA and SA exist, among them differential analysis, response surface methodology, Monte Carlo analysis, and variance decomposition (see~\cite{helton2006survey} for a review).
+Sohier et al.~\cite{sohier2018confidence} recently provided a rigorous generalization of this formula to include confidence intervals.
+
+% \subsubsection{Uncertainty, sensitivity, and random seed analysis}
+% \tristan{I'm wondering if we could remove this sub-section, as it doesn't seem to be critical to the understanding of the paper, wdyt?}
+% Uncertainty analysis (UA) is a method to estimate the output distribution given an input distribution.
+% Sensitivity analysis (SA) is a variation of UA that measures the local response to a small perturbation~\cite{loucks2017water}. 
+% Several approaches for UA and SA exist, among them differential analysis, response surface methodology, Monte Carlo analysis, and variance decomposition (see~\cite{helton2006survey} for a review).
 In particular, Monte Carlo analysis is a sampling-based technique that samples inputs space to estimate output response.
@@
 For instance, the PRECISE framework~\cite{chaitin1996lectures} shares with MCA the idea of varying virtual precision to estimate output sensitivity.
-Furthermore, the quality of a Random Number Generator is a crucial characteristic when dealing with stochastic model and differ from cryptography requirements.
-For numerical simulation, a good RNG provides a tradeoff between performance, period, correlation, or uniformity~\cite{james2020review}.
-On the other hand, poor quality RNGs may have a substantial impact on results~\cite{click2011quality}.
+
+% Furthermore, the quality of a Random Number Generator is a crucial characteristic when dealing with stochastic model and differ from cryptography requirements.
+A good RNG provides a tradeoff between performance, period, correlation, or uniformity~\cite{james2020review} for numerical simulation.
+% On the other hand, poor-quality RNGs may have a substantial impact on results~\cite{click2011quality}.
 First, measuring variation induced by seed is a good indicator of program stability that we can compare against variability induced by floating-point arithmetic.
@@
 Visualization covers a wide range of numerical simulation domains, from general-purpose numerical visualization with tools
-such as VTK~\cite{schroeder2000visualizing}, to topological data analysis~\cite{tierny2018topological}, including matrix~\cite{wu2008matrix} or tensor~\cite{kindlmann2006diffusion} visualization.
+such as VTK~\cite{schroeder2000visualizing} to topological data analysis~\cite{tierny2018topological}, including matrix~\cite{wu2008matrix} or tensor~\cite{kindlmann2006diffusion} visualization.
 We review here tools dedicated to the analysis of numerical variability induced by the floating-point model.
@@
 It is an extension of Verificarlo~\cite{verificarlo} that offers contextual information about variables traced to allow the user to identify instabilities quickly.
-However, it does not offer a dynamic interface and does not include information about high-level structures such as \texttt{struct} or \texttt{array}.
+However, it neither offers a dynamic interface nor includes information about high-level structures such as \texttt{struct} or \texttt{array}.
 FPAvizual~\cite{gu2014fpavisual} visualizes the effects of floating-point arithmetic but only for educational purposes.
@@
 % \subsection{Pytracer workflow}
-
-The PyTracer workflow follows a three-step approach (Figure~\ref{fig:workflow}).
-First, \pytracer instruments applications using ``monkey patching", a technique to modify Python programs without editing their source code.
-The instrumentation replaces all the functions with a wrapper that saves their arguments and returned value in a trace file using ``pickle", Python's object serialization mechanism.
-\pytracer then aggregates trace files obtained from multiple perturbed executions, computing summary statistics about each traced variable.
+\pytracer adopts the three-step workflow shown in Figure~\ref{fig:workflow}.
+First, it uses monkey patching to replace the functions called by the application with a wrapper that saves their arguments and returned values in a trace file.
+Second, it injects noise in the application, executes it multiple times, and aggregates the resulting trace files to compute summary statistics about each traced variable.
 Finally, a Plotly dashboard provides interactive visualizations highlighting unstable code sections.
@@
 without requiring source code modifications in the application.
-To do so, it creates a new, instrumented version of each module that preserves its original attributes so that the original application can transparently use it.
+To do so, it creates a new, instrumented version of each module that preserves its original attributes so that the application can transparently use it.
 By default, \pytracer instruments all the attributes
 in a given module except the special ones of the form \texttt{\_\_*\_\_}.
-However, some attributes are not writable; in this case, \pytracer preservers the original attributes and warns the user. The user can also restrict the list of traced attributes through
+However, some attributes are not writable. In this case, \pytracer preservers the original attributes and warns the user. The user can also restrict the list of traced attributes through
 an inclusion/exclusion mechanism.
-The main advantage of this instrumentation approach is the lack of required modification in the application source code, in contrast with decorator-based approaches, which is scalable and useful in read-only environments such as Singularity containers or HPC clusters.
+The main advantage of this instrumentation approach is the lack of required modification in the application source code, in contrast with decorator-based approaches.
+In addition, this technique is scalable and applicable in read-only environments such as Singularity containers or HPC clusters.
 
@@
 
-Python loads modules through an import mechanism triggered by the \texttt{import} keyword, using two objects: \texttt{finders} and \texttt{loaders}.
-The \texttt{finder} is responsible for finding the package (or 
-namespace\footnote{Python distinguishes between \texttt{regular} and \texttt{namespace} packages.
+Python loads modules through an import mechanism triggered by the \texttt{import} that involves two objects: \texttt{finders} and \texttt{loaders}. \texttt{Finders} search for packages (or 
+namespaces\footnote{Python distinguishes between \texttt{regular} and \texttt{namespace} packages.
 A regular package is a directory that contains a \_\_init\_\_.py file and potentially subdirectories (sub-packages) 
@@
 Hence, parts of the package can be located in zip files, on the network, or in separated directories.
-There are no functional differences between both types of packages.}) from its fully qualified name, whether it is located on the local storage, such as standard packages installed through the pip package manager, or on a distant server.
-\texttt{Finders} do not load the modules; they return a specification (\texttt{spec} object) encapsulating 
-information on where to find it and how to load it.
-The \texttt{loader} creates and initializes a module object, filling the import-related attributes 
+There are no functional differences between both types of packages.}) on the local storage --- such as standard packages installed through the pip package manager --- or on a distant server.
+\texttt{Finders} do not load modules. Instead, they return a specification (\texttt{spec} object) that includes 
+information on where to find and how to load modules.
+\texttt{Loaders} create module objects, initialize them, and fill import-related attributes 
 such as \texttt{\_\_spec\_\_}. 
-Then, the \texttt{loader} executes the module and populates its namespace. Finally, the module is bound to its import name in the \texttt{sys.modules} dictionary.
-
-Python supports custom \texttt{finder} classes, registered in the \texttt{sys.meta\_path} list.
-When Python encounters an \texttt{import} statement, it first looks for a binding in the \texttt{sys.modules}
-and then iterates over the \texttt{finder} classes in \texttt{sys.meta\_path} until it finds the module to import. \pytracer adds a custom \texttt{finder} class at the head of the list that intercepts
+\texttt{Loaders} then execute modules and populate their namespace. Finally, modules are bound to their import name in the \texttt{sys.modules} dictionary.
+
+Python supports custom \texttt{finder} classes registered in the \texttt{sys.meta\_path} list.
+When Python encounters an \texttt{import} statement, it first looks for an existing binding in \texttt{sys.modules} and then iterates over the \texttt{finder} classes in the \texttt{sys.meta\_path} list until it finds the module.
+\pytracer adds a custom \texttt{finder} class at the head of \texttt{sys.meta\_path} that intercepts
 the module import and creates the module with a custom \texttt{loader} class.
@@
 \pytracer's \texttt{loader} class first loads the original module, then copies it as a new instance of the \texttt{ModuleType} class.
-It then calls the appropriate instrumentation function for each module attribute depending on its type (function, class, or instances).
-Then, \pytracer replaces the original module with its instrumented counterpart in the \texttt{sys.modules} map once it has instrument all the attributes.
-Hence, the calling convention remains unchanged, and the application will transparently call the instrumented module.
-Finally, Pytracer updates all existing references to the original module, such as the ones in \texttt{\_\_globals\_\_} function attributes that contain references to internal function objects.
+It then calls the appropriate instrumentation function for each attribute depending on its type (function, class, or instances --- see below \tristan{iterators?}) and replaces the original module in the \texttt{sys.modules} map with the instrumented version.
+Finally, it updates all existing references to the original module, such as those in \texttt{\_\_globals\_\_} function attributes containing references to internal function objects \tristan{this sentence doesn't make sense, please update}.
+As a result, the application will transparently call the instrumented module.
 
@@
 
-For each function, \pytracer's \texttt{loader} class creates a wrapper function, dynamically compiles it with the compile builtin function, and substitutes it for the original module function.
-This simple technique
-cannot be applied to callable class instances, i.e., class instances that have the \texttt{\_\_call\_\_} attribute but are not of the \texttt{FunctionType} type.
-Indeed, applying the wrapper technique would 1) modify the type of the class instance to \texttt{FunctionType}, which could cause syntactic and semantic bugs, and 2) mask class attributes, leading to \texttt{AttributeError} exceptions.
-To overcome this issue, \pytracer overrides the \texttt{\_\_call\_\_} attribute with the wrapper function when possible.
+Listings~\ref{fig:wrapper_creation} and~\ref{fig:generic_wrapper} show \pytracer's function instrumentation mechanism.
+For each function to instrument, \pytracer's \texttt{loader} class creates a wrapper function, dynamically compiles it with the compile builtin function, and substitutes it for the original module function.
+However, this simple technique does not apply to callable class instances, i.e., class instances that have a \texttt{\_\_call\_\_} attribute and are not of type \texttt{FunctionType}.
+Indeed, applying the wrapper technique would 1) modify the type of the class instance to \texttt{FunctionType}, which could cause syntax and semantic errors, and 2) mask class attributes, leading to \texttt{AttributeError} exceptions.
+\pytracer overrides the \texttt{\_\_call\_\_} attribute with the wrapper function when possible to overcome this issue.
 When the \texttt{\_\_call\_\_} attribute is not writable,  Pytracer does not instrument the class and returns a warning.
-Listings~\ref{fig:wrapper_creation} and~\ref{fig:generic_wrapper} show \pytracer's wrapper creation function.
 
@@
     \pytracer uses the identifier of the function instead of the 
-    actual function to get rid of aliases and duplicated instrumentations.}
+    actual function to handle aliases and avoid duplicate instrumentation.}
     \label{fig:wrapper_creation}
@@
 \end{lstlisting}
-    \caption{\pytracer's wrapper function that dumps
+    \caption{\pytracer's generic wrapper function that dumps
     the inputs and outputs of the wrapped function.
     \pytracer binds arguments to the function signature to avoid
-    mispositioning and to have actual names for the visualization.
-    The wrapper returns the actual output.
+    mispositioning \tristan{what does mispositioning means here?} and to show readable names in the visualization.
     }
@@
 \pytracer instruments classes by wrapping their callable attributes as described previously. 
-This instrumentation preserves class types, avoiding type mismatches in the instrumented application.
-However, some classes, in particular base types and NumPy's universal functions (\texttt{ufuncs}), contain read-only attributes that cannot be instrumented. 
+This instrumentation preserves class types, which avoids type mismatches in the instrumented application.
+However, classes that describe particular base types and NumPy's universal functions (class \texttt{ufunc}) contain read-only attributes that cannot be instrumented.
 By default, \pytracer returns a warning when it encounters such classes.
 
-\subsubsection{Instrumenting instances}
-
-Pytracer automatically instruments the instances since it instruments the classes, but it cannot instruments or instantiates some classes like \texttt{ufunc}, although their instrumentation is desirable given their pervasiveness in scientific computing.
-Indeed, NumPy's \texttt{ufuncs} are vectorized element-wise operators that apply to multidimensional arrays, 
-including the set of elementary mathematical functions.
-In particular, all the element-wise elementary mathematical functions are \texttt{ufuncs}.  
-To increase performance, \texttt{ufuncs} are implemented in C, which prevents their instantiation.
-
-To overcome this issue, \pytracer wraps the instances into a transparent wrap class (\texttt{twc}) that overloads
-1) the \texttt{\_\_getattribute\_\_} that is called when one is accessing an instance's attribute.
+\subsubsection{Instrumenting class instances}
+
+\pytracer automatically instruments class instances since it instruments classes.
+However, it cannot instrument or instantiate classes that have read-only attributes --- in particular class \texttt{ufunc} ---, which is problematic given their pervasiveness in scientific computing.
+In particular, NumPy's universal functions include
+vectorized elementary mathematical functions and other prevalent ones. Universal functions are implemented in C, which prevents their modification.
+
+To overcome this issue, \pytracer wraps the class instance into a transparent wrap class (\texttt{twc}) that overloads
+1) function \texttt{\_\_getattribute\_\_}, called when an instance attribute is accessed --- instrumented to return the attributes from the original class, and 2) function \texttt{\_\_call\_\_}, called when the function is called through the () operator --- instrumented with function \texttt{generic\_wrapper} .
 The \texttt{twc} returns the queried attribute of the instance instead of returning its attributes, allowing transparent access to the instance.
-2) the \texttt{\_\_call\_\_} functions that is called when one
-is calling the function (through the () operator). The \texttt{twc} calls the \texttt{generic\_wrapper} to saves 
-inputs and outputs as for classical functions. Finally, \pytracer overloads the \texttt{type} built-in function
-to preserve the type of the wrapped instance.
+Finally, \pytracer overloads the builtin \texttt{type} function to preserve the type of the wrapped instance.
 
@@
 However, it implies that no complete mapping of the container returned by an iterator exists in memory since the application computes each element on the fly.
-Therefore, iterators are not serializable and \pytracer cannot save them to output traces.
-A workaround would be to convert iterators into explicit containers and then return a new iterator on the explicit container.
-However, this would increase the memory footprint significantly.
-\pytracer therefore does not instrument iterators.
+Therefore, builtin iterators are not serializable which implies that \pytracer cannot save them to output traces.
+A workaround would be to convert iterators into explicit containers, however, this would increase the memory footprint significantly. \pytracer, therefore, does not instrument iterators.
 
@@
 We enable MCA in Python programs via Verificarlo~\cite{verificarlo}, a clang-based compiler~\cite{lattner2008llvm} that replaces floating-point operations by a generic call to a configurable floating-point model.
-Several floating-point models, also called backends, are available~\cite{chatelain2019automatic,chatelain2019outils}.
-We leverage the ``fuzzy"~\cite{kiar2020comparing} environment, a collection of software tools recompiled with Verificarlo.
-In particular, fuzzy provides MCA-instrumented versions of the Python interpreter as well as of the BLAS, LAPACK, NumPy, SciPy, and scikit-learn libraries, which enables MCA for a wide range of existing scientific Python programs.
+Several floating-point models are available~\cite{chatelain2019automatic,chatelain2019outils}, also called backends.
+\pytracer leverages ``fuzzy"~\cite{kiar2020comparing}, a collection of software tools compiled with Verificarlo.
+In particular, fuzzy provides MCA-instrumented versions of the Python interpreter as well as the BLAS, LAPACK, NumPy, SciPy, and scikit-learn libraries, which enables MCA for a wide range of existing scientific Python programs.
 Fuzzy is available in Verificarlo's GitHub organization at \href{https://github.com/verificarlo/fuzzy}{\url{github.com/verificarlo/fuzzy}}.
@@
 
-\pytracer stores traces in the pickle format, a compressed binary Python format to serialize Python objects.
+\pytracer stores traces in the pickle format, a binary format to serialize Python objects.
 The main advantages of the pickle format compared to other serialization approaches such as marshal or JSON are its ability to serialize most Python objects and its native compression.
@@
 
-Traces record numerical values at the granularity of a function.
+Traces store numerical values at the granularity of function calls.
 When the application invokes a function, \pytracer saves a call input object containing contextual information (function's name, module's function, stacktrace) and the values of the function arguments.
@@
 
-Once traces are available, \pytracer sequentially parses them and computes the mean, standard deviation, and the number of significant digits (computed using Equation~\ref{eq:sig-digits}) of all saved values.
-Pytracer saves these summary statistics in an HDF5 file, a hierarchical format that facilitates browsing during the visualization.
+Once traces are available, \pytracer sequentially parses them and computes the mean, standard deviation, and number of significant digits (as in Equation~\ref{eq:sig-digits}) of all saved values.
+\pytracer saves these summary statistics in an HDF5 file, a hierarchical format that facilitates visual browsing.
 This operation critically relies on the ordering of call input and output objects in the traces.
-Furthermore, it assumes that the application is deterministic, and in particular, assumes it is single-threaded and that the control flow does not depend on a random state.
+Therefore, it assumes that the application is single-threaded and that the control flow does not depend on a random state.
 % Techniques to overcome this limitation are discussed in the discussion section.
@@
 that the call objects refer to the same function and stacktrace, and terminates the parsing otherwise.
-For each matching call object, \pytracer stores function arguments or returned values in a NumPy array to compute statistics. 
+PyTracer stores function arguments or returned values in a NumPy array for each matching call object to compute statistics.
 For compound objects such as tuples, dictionaries, or objects, it recursively parses the fields until finding
@@
  \item Timeline view: This view displays the values of each input and output for a given function at a given invocation.
-By default, \pytracer shows the number of significant digits computed across the traces, but the user can switch to the mean or the standard deviation.
-The visualizer uses an upper triangle for inputs and a down triangle to differentiate inputs from outputs.
+By default, \pytracer shows the number of significant digits computed across the traces.
+The user can switch to the mean or the standard deviation.
+The visualizer uses an upper triangle for inputs and a lower triangle for outputs.
 \pytracer internally represents all values as NumPy arrays.
@@
 Each variable is prefixed with the original value and postfixed with the name of the parameter.
-    Finally, for non-scalar values (vectors or matrices), \pytracer shows the average elements for non-scalar values (like vectors or matrices).
-non-scalar values can be inspected with the Zoom view (see below).
- \item Gantt chart view: This view displays the call graph as a Gantt chart representing the instrumented functions.
-Each function call is represented with a bar starting and ending at the function call and return.
-    The caller/callee relation is then determined by looking at the time overlaps.
+    Finally, non-scalar values (vectors or matrices) are represented by their average and can be inspected with the Zoom view (see below).
+ \item Gantt chart view: This view displays the call graph as a Gantt chart representing the instrumented functions. Each function call is represented with a bar.
+    The time overlaps reflect the caller/callee relation.
     For example, in the figure, \texttt{function1} calls \texttt{function2} that itself calls \texttt{function4} and \texttt{function5}. 
-    This view provides insights on the calling context for each function since different parents functions can call the same function, which may influence numerical stability. 
+    This view provides insights on the calling context for each function, which may influence numerical stability. 
  \item  Source code view: This view displays the source code file of the variable hovered in the timeline view. 
- \item Zoom view: This view allows closely examine non-scalar values, which is helpful to see local differences that might be masked by the averaging done in the timeline view.
-For example, a matrix can have instabilities around its diagonal but not in other regions.
-    The visualizer also provides metrics about the value, such as the array shape, infinite norm, or condition number.
-\item  Functions list view: This view allows the user to select the functions to plot in the timeline view.
+ \item Zoom view: This view provide details about non-scalar values. For example, a matrix may have instabilities around its diagonal but not in other regions.
+    The visualizer also provides additional metrics such as array shape, infinite norm, or condition number.
+\item  Functions list view: This view allows the user to select the functions plotted in the timeline view.
 \end{enumerate}
@@
 
-We evaluated \pytracer on widely-used Python libraries, namely: SciPy, the main library for scientific computing in Python; scikit-learn, a reference machine-learning framework; PyAFQ, a neuroimaging analysis toolbox.
-For SciPy and scikit-learn, we traced each application five times, having activated MCA in the Python interpreter, BLAS, LAPACK, NumPy, SciPy, and scikit-learn.
-We repeated the experiment with two MCA modes, Random Rounding (RR) and Full MCA, resulting in 2 experiments for each application.
+We evaluated \pytracer on two widely-used Python libraries: SciPy~\cite{virtanen2020scipy}, the main library for scientific computing in Python, and  scikit-learn~\cite{pedregosa2011scikit}, a reference machine-learning framework that
+ implements a wide range of state-of-the-art algorithms.
+For each library, we executed the software tests provided in their respective GitHub repositories.
+We traced each test five times, having activated MCA in the Python interpreter, BLAS, LAPACK, NumPy, SciPy, and scikit-learn.
+We repeated the experiment with two MCA modes, Random Rounding (RR) and Full MCA, resulting in 2 experiments for each test.
 We used the default virtual precision in Verificarlo, namely 24 bits for single-precision floating-point values and 53 bits for double-precision values, which simulates machine error.
-For each library, we executed the software tests provided in their GitHub repositories.
+\tristan{Report scipy and sklearn versions used.}
 
@@
 \pytracer's outcome on SciPy and scikit-learn tests.
-Each table reports on the tracing and trace aggregation steps with three possible outcomes: green for success, red for numerical error in the application, and orange for errors in the fuzzy noise injection.
-Overall, the tracing and parsing of SciPy and scikit-learn tests in Random Rounding mode was entirely successful (tracing and parsing steps) for 32/40 tests.
+Each table reports on the tracing and trace aggregation steps with three possible outcomes: green for success, red for numerical error in the application, and orange for errors in the fuzzy noise injection \tristan{Explain what this is, in a setence here or with a subsubsection if it requires more}.
+Overall, the tracing and parsing of SciPy and scikit-learn tests in Random Rounding mode was entirely successful for 32/40 tests.
 The remaining tests failed due to numerical errors in the libraries, which we discuss hereafter.
-The instrumentation with Full MCA is more invasive and reduced the number of successful executions to 13/40.
+The instrumentation with Full MCA is more invasive and reduced the number of successful executions to 12/40.
 
@@
 \label{sec:impact_mca_modes}
-Random Rounding perturbs only the result of a floating-point operation, while Full MCA mode perturbs both the inputs and the operation's result. 
-Therefore, full MCA mode may trigger catastrophic cancellations while Random Rounding only introduces round-off errors which generally have a lesser impact.
-Moreover, Random Rounding preserves exact operations, i.e., operations where the result can be exactly represented on the virtual precision, while Full MCA does not.
+Random Rounding perturbs only the result of a floating-point operation while Full MCA perturbs both the inputs and the result. 
+Therefore, Full MCA may trigger catastrophic cancellations while Random Rounding only introduces round-off errors which generally have a lesser impact.
+Moreover, Random Rounding preserves exact operations --- operations where the result can be exactly represented at the virtual precision --- while Full MCA does not.
 
@@
 In particular, program branches triggered by an unstable floating-point comparison lead to different control flows and result in parsing errors.
-For example, comparing a residual error to a strict threshold in an iterative scheme or comparing the distance between two points generally results in unstable branches. 
-With Full MCA, even exact values such as integers represented with floating-point values are perturbed, leading to many execution failures.
+For example, comparing a residual error or the distance between two points to a strict threshold in an iterative scheme generally results in unstable branches. 
+Full MCA even perturbs exact values such as integers represented with floating-point values, leading to many execution failures.
 For instance, the \texttt{fft1} test from SciPy raised an \texttt{ValueError: operands could not be broadcast together with shapes (601,) (600,)} error due to an array shape mismatch.
-A closer inspection showed that one of the arrays involved in the error is created with the NumPy function \texttt{linspace} that itself calls function \texttt{arange} (Listing~\ref{fig:pyarray_range_code}).
-As can be seen in lines  3174-3178, the array size is stored in a floating-point value which will therefore be perturbed in Full MCA mode, as shown in Table~\ref{tab:mca_result_linspace}, resulting in array sizes that fluctuate
-between N and N+1. 
+A closer inspection showed that one of the arrays involved in the error was created with the NumPy function \texttt{linspace} that itself calls function \texttt{arange} (Listing~\ref{fig:pyarray_range_code}).
+Lines 3174-3178 show that the function stores the array size in a floating-point value that will be perturbed by Full MCA, as shown in table~\ref{tab:mca_result_linspace}, resulting in array sizes that fluctuate between N and N+1.
 It is worth noting that 78\% of execution issues encountered in Full MCA mode without \texttt{ufunc} instrumentation
 are due to this type of ``typing" errors.
-While they do not lead to any numerical issue, such typing errors should still be fixed to preserve code quality.
+While they do not lead to any numerical issue, typing errors should still be fixed to preserve code quality \tristan{do we really mean that given your answer to my comment below?}.
 We provide solutions to help MCA better work with those cases in the discussion section.
@@
     \end{lstlisting}
-\caption{Source code of the \texttt{PyArray\_Range} Cython function called by NumPy function \texttt{linspace} to create an array of equally spaced elements.
+\caption{Source code of the \texttt{PyArray\_Range} Cython function called by NumPy function \texttt{linspace} to create an array of equally-spaced elements.
 The temporary array size assigned in line 3178 is stored as a floating-point value and is therefore perturbed in Full MCA mode, leading to differences amplified by the use of ceil rounding at line 3190 and resulting in different array sizes across MCA-perturbed executions.
@@
     \caption{Results obtained through lines 3177-3190 in Listing~\ref{fig:pyarray_range_code}.
-Contrary to RR mode, Full MCA mode does not preserve exact operations which leads to an array length oscillating between 600 and 601.}
+In contrast with RR, Full MCA does not preserve exact operations which leads to an array length oscillating between 600 and 601.}
     \label{tab:mca_result_linspace}
@@
 Table~\ref{tab:pytracer_test_precision_summary} summarizes the precision for main outputs of SciPy and scikit-learn tests. 
-We measure the precision in significant bits on the principal output computed by the test by taking the element-wise mean for non-scalar values and, if the test produces many outputs, we take the average value among results.
-A dash value means that the test produces an error.
-The numerical quality of obtained results and MCA modes combined vary from 0 to 52, with an average of 44 bits significant.
-For both modes, we note that only one test failed due to a numerical error (\texttt{face\_recognition} for RR and \textit{Bayesian Ridge Regression} for Full MCA) even though this number is underestimated since Full MCA mode is more intrusive than RR mode and most of the tests produce error caused by the fuzzy noise injection.
+We measured the precision in significant bits on the main test output by taking the element-wise mean for non-scalar values and, if the test produces many outputs, the average value among all of them.
+The numerical quality across all tests varies from 0 to 52, with an average of 44 significant bits.
+For both modes, we note that only one test failed due to a numerical error \tristan{can we see that in the table?
+if not, don't comment on it, it is puzzling.
+Could you show that in the table by using the same error symbols as in Table 2?} (\texttt{face\_recognition} for RR and \textit{Bayesian Ridge Regression} for Full MCA) even though we underestimate this number since Full MCA mode is more intrusive than RR mode and most of the tests produce error caused by the fuzzy noise injection.
 
@@
     \hline 
-    Application & RR & MCA \\
+    Test & RR & MCA \\
     \hline
@@
 \end{subfigure}
-    \caption{Summary of tests precision for main outputs of SciPy and scikit-learn tests. Precision is measured in significant bits on the principal output computed by the test.
-    For non-scalar values, the element-wise mean is taken. If the test produces many outputs, like when comparing methods, the average value among results is taken.  
-    A dash value means that the test produces an error. }
+    \caption{Summary of tests precision for main outputs of SciPy (left) and scikit-learn (right) tests. 
+    Dash values indicate runtime errors. \tristan{explain the meaning of nans here}}
     \label{tab:pytracer_test_precision_summary}
@@
 
-We tested Pytracer on SciPy~\cite{virtanen2020scipy} examples provided in the tutorial website section.
+We tested \pytracer on SciPy examples provided in the tutorial website section \tristan{Are these tests? If not we need to reword the begining of this section (I can do it, just let me know).}.
 SciPy is organized in several libraries targeting specific computing domains.
-Therefore, we focused on the following packages:
-\begin{itemize}
-    \item \texttt{fftpack}: Fast Fourier Transform routines.
-    \item \texttt{interpolate}: Interpolation and smoothing splines.
-    \item \texttt{optimize}: Optimization and root-finding routines.
-\end{itemize}
+We focused on \texttt{fftpack} (Fast Fourier Transform routines), \texttt{interpolate} (interpolation and smoothing splines), and \texttt{optimize} (Optimization and root-finding routines).
 
@@
 
-This package has three tests: \texttt{discrete\_cosine\_transform}, \texttt{fft\_1D}, and \texttt{fft\_2D}.
+This package has three tests \tristan{tests or examples?}: \texttt{discrete\_cosine\_transform}, \texttt{fft\_1D}, and \texttt{fft\_2D}. All computations are done in double precision.
 The results for \texttt{discrete\_cosine\_transform},\texttt{fft\_1D} and  \texttt{fft\_2D} show
-correct numerical results with 48 significant bits in average. All computations are done with double precision.
-We observe that the FFT is stable with noisy inputs. The figures~\ref{fig:fft1D_mean} and~\ref{fig:fft1D_std}
-show the mean and standard deviation over the MCA samples respectively. 
-The top rows show the domain $z$ and the result fft$(z)$, in the logarithmic scale with the real part in blue and the imaginary part in orange.
+precise numerical results with 48 significant bits in average. 
+We observe that the FFT computation is stable to noisy inputs. Figures~\ref{fig:fft1D_mean} (inputs) and~\ref{fig:fft1D_std} (outputs)
+show the mean and standard deviation of the MCA samples. 
 The three columns correspond to the FFT computations of: 
@@
 \item $z_1 = \sin(50 . 2\pi . x_i) + \dfrac{1}{2} \sin(80 . 2\pi . x_i),\; x_i = \frac{i}{600},\; i \in [0,600]$
-\item $ blackman(400)*z_1$
+\item $\mathrm{blackman}(400)*z_1 \tristan{is * the convolution operator?}$
 \item $ z_2= e^{50 . i 2\pi . x_i} + \dfrac{1}{2} e^{-80 . i2\pi .x_i },\; x_i = \frac{i}{800},\; i \in [0,400] $
@@
 
-Top row of figures~\ref{fig:fft1D_mean} and~\ref{fig:fft1D_std} 
-shows the mean value of the inputs while the bottom row shows the standard deviation.
-The points with low magnitude correspond to inputs near 0, when the input of $\sin$ or 
+Top row in Figures~\ref{fig:fft1D_mean} and~\ref{fig:fft1D_std} 
+show the input mean value while the bottom row shows the standard deviation.
+The points with low magnitude \tristan{in Figure~\ref{fig:fft1D_mean}?} correspond to inputs near 0 when the input of $\sin$ or 
 $\exp$ is close to $k\pi$, $k \in \mathbf{Z}$.
-Indeed, since MCA introduces a small noise, the result is not exactly 0.
-We can see on the figure~\ref{fig:fft1D_std} that the maximal noise introduced by MCA on the
-inputs is of the order of magnitude of $10^{-14}$, two order of magnitude higher than the 
+Indeed, since MCA introduces a slight noise, the result is not exactly 0.
+We can see in Figure~\ref{fig:fft1D_std} \tristan{isn't it in Figure 3?} that the maximal noise introduced by MCA on the
+inputs is in the order of $10^{-14}$, two orders of magnitude higher than the 
 $ulp \simeq 10^-16$ for double precision. 
-This small noise introduced can be interpreted as a white noise on the input signal. 
-We can see on bottom row of the figure~\ref{fig:fft1D_std} that the frequencies noise is in 
-the same order of of magnitude than the magnitude of the inputs noise, which is expected. 
-The two pics at 38 and 562 corresponds to the actual frequencies of the input.
+This slight noise introduced can be interpreted as white noise on the input signal. 
+We can see on the bottom row of Figure~\ref{fig:fft1D_std} that the frequency noise is of 
+the same order of of magnitude as the input noise, which is expected. 
+The two peaks at x=38 and x=562 corresponds to the actual frequencies of the input signal.
 
@@
     \caption{Absolute value of the mean and standard deviation values for 
-    fft 1D inputs within RR mode (log scale).}
+    fft 1D inputs within RR mode (log scale). The real part is shown in blue and the imaginary part in orange.\tristan{put stdev of middle column on the same scale as the other columns}}
     \label{fig:fft1D_mean}
@@
 
-The \texttt{interpolation\_1D} test interpolates the function $\cos(\frac{-x^2}{9})$ with 11 points $x\in[0,10]$.
-For the fives schemes tested (linear, cubic, nearest, previous, next), the solution found is precise, up to 51 bits out of the 53 available.
-
-The \texttt{multivariate\_data} test interpolates the grid $f(x,y)=x(1-x)\cos(4\pi.x)  \sin(4\pi.y^2)^2$ with $(x,y) \in [0,1] \times [0,1]$ sampling with 1000 points for each coordinate using three schemes: nearest, linear and cubic.
-Our results show a precision of 51 bits in average for the three schemes.
-
-The \texttt{bspline} test compares two edge filters: \texttt{bisplev} that evaluates a bivariate B-spline and its derivative and \texttt{convolved2d} that convolves two 2-dimensional arrays.
+\texttt{interpolation\_1D} interpolates function $f(x)=\cos(\frac{-x^2}{9})$ with 11 points $x\in[0,10]$.
+For the fives interpolation methods tested (linear, cubic, nearest, previous, next), the solution found is precise, up to 51 bits out of the 53 available.
+
+\texttt{multivariate\_data} interpolates the grid $f(x,y)=x(1-x)\cos(4\pi.x)  \sin(4\pi.y^2)^2$ with $(x,y) \in [0,1] \times [0,1]$.
+It samples 1,000 points for each coordinate and uses three interpolation methods: nearest, linear and cubic.
+Our results show a precision of 51 bits on average for the three methods.
+
+\texttt{bspline} compares two edge filters: \texttt{bisplev} evaluates a bivariate B-spline and its derivative whereas \texttt{convolved2d} convolves two 2-dimensional arrays.
 Figure~\ref{fig:bspline_rr}
 shows the significant bits (figs.~\ref{fig:bspline_bisplev_sig},~\ref{fig:bspline_convol2d_sig}), 
-mean (figs.~\ref{fig:bspline_bisplev_mean},~\ref{fig:bspline_convol2d_mean}), and standard deviation (figs.~\ref{fig:bspline_bisplev_std},~\ref{fig:bspline_convol2d_std}) maps for the two methods as well as the input image (fig.~\ref{fig:bspline_input}) with the middle for the \texttt{bisplev} results and bottom row for the \texttt{convol2d}.
-We can see no visual differences between both methods with 11 significant bits in average.
+mean (figs.~\ref{fig:bspline_bisplev_mean},~\ref{fig:bspline_convol2d_mean}), and standard deviation (figs.~\ref{fig:bspline_bisplev_std},~\ref{fig:bspline_convol2d_std}) \tristan{replace the figure references with labels in the figure, it would be much clearer} maps for the two methods as well as the input image (fig.~\ref{fig:bspline_input}) with the middle for the \texttt{bisplev} results and bottom row for the \texttt{convol2d}.
+Both methods exhibit similar precision, with 11 significant bits on average.
 Standard deviations maps on figures~\ref{fig:bspline_bisplev_std} and~\ref{fig:bspline_convol2d_std} show that regions with low spatial frequencies correspond to regions with low standard deviation, similar to the FFT results.
-As it is mentioned in the SciPy tutorial, the \texttt{bisplev} function is faster than the \texttt{convol2d} while our experiments show that they have the same numerical precision which reinforces the use of \texttt{bisplev} over \texttt{convol2d} in this example.
-
-The \texttt{spline\_1D} test computes the 1D spline interpolation for the function $\sin(x)$ on points $x=\frac{2\pi k}{8}, k \in [0, 10]$.
-The spline interpolation uses two methods: \texttt{splrep} to build the spline representation and \texttt{splrev} to evaluate the spline at any point.
+As it is mentioned in the SciPy tutorial, the \texttt{bisplev} function is faster than the \texttt{convol2d}.
+The comparable numerical precision observed in our experiments reinforce the use of \texttt{bisplev} over \texttt{convol2d} in this example.
+
+\texttt{spline\_1D} computes the 1D spline interpolation for $f(x)=\sin(x)$ on points $x=\frac{2\pi k}{8}, k \in [0, 10]$.
+The spline interpolation uses \texttt{splrep} to build the spline representation and \texttt{splrev} to evaluate the spline at any point.
 It also computes the integral by using \texttt{splint} and the root finder \texttt{sproot}.
@@
 
-The \texttt{spline\_2D} test computes the 2D spline interpolation for the function $z=(x+y)e^{-6(x^2+y^2)}$, with $(x,y) \in [-1,1]\times[-1,1]$ sampling with 21 points for each coordinate.
-\texttt{bisplrep} builds the spline representation with the $21 \times 21$ points of $z$ over a 71 grid sampling points for $(x,y)$.
-The figure~\ref{fig:spline2d_rr} shows the results of the spline evaluation with \texttt{bisplev}.
+\texttt{spline\_2D} computes the 2D spline interpolation for function $z=(x+y)e^{-6(x^2+y^2)}$, with $(x,y) \in [-1,1]\times[-1,1]$ and a sampling of 21 points for each coordinate.
+\texttt{bisplrep} builds the spline representation with the $21 \times 21$ points of $z$ over 71 grid sampling points for $(x,y)$.
+Figure~\ref{fig:spline2d_rr} shows the results of the spline evaluation with \texttt{bisplev}.
+\tristan{conclusion?}
 
@@
 \begin{subfigure}{.3\linewidth}
-    \includegraphics[width=\linewidth]{}
-\end{subfigure}
-\begin{subfigure}{.3\linewidth}
     \includegraphics[width=\linewidth]{figure/bspline/original_image.png}
@@
     \label{fig:bspline_input}
-\end{subfigure}
-\begin{subfigure}{.3\linewidth}
-    \includegraphics[width=\linewidth]{}
-\end{subfigure}
+\end{subfigure}\\
 \begin{subfigure}{0.3\linewidth}
@@
 \end{subfigure}
+    \caption{\texttt{bspline} results within RR mode. Left column shows the \texttt{bisplev} function
+    while the right column shows the \texttt{convolve2d} function. \tristan{isn't it top row vs bottom row? Replace these hard-to-read explanations with good labels in the figure}}
     \label{fig:bspline_rr}
-    \caption{\texttt{bspline} results within RR mode. Left column shows the \texttt{bisplev} function
-    while the right column shows the \texttt{convolve2d} function. }
 \end{figure}
@@
     show respectively in the logarithmic scale the absolute mean value and the standard deviation 
-    of the 5 samples run within RR mode.}
+    of the 5 samples run within RR mode. \tristan{any reason why you are showing the ieee result?}}
     \label{fig:spline2d_rr}
@@
 
-This package has ten tests: five for unconstrained minimization of multivariate scalar functions using different algorithms: \texttt{Nelder-Mead}~\cite{singer2009nelder} that iteratively transforms a simplex until its vertices are getting closer to local minima of the function.
-Fours Quasi-Newton-Raphson methods whose main goal is to determine $x$ that minimizes the function $f$ by using Newton's method step: $x_{k+1} = x_{k} - B^{-1}(x_k)\nabla f(x_k)$, where $\nabla$ and $B$ are the gradient and the approximation of the Hessian matrix of $f$.
-The \texttt{Broyden-Fletcher-Goldfarb-Shanno}~\cite{BFGS} (BFGS) and \texttt{Newton-Conjugate-Gradient}~\cite{nocedal2006numerical} (NCG) are line search methods that respectively approximates $H$ by adding two symmetric rank-one matrices and by using the Conjugate-Gradient method.
-The \texttt{Trust-Region Truncated Generalized Lanczos / Conjugate Gradient}~\cite{gould1999solving}, \texttt{Trust-Region Newton-Conjugate-Gradient} and \texttt{Trust-Region Nearly Exact}~\cite{nocedal2006numerical} are trust-region methods that approximates $H$ by solving the trust-region subproblem restricted to a truncated Krylov subspace and by solving nonlinear equations for each quadratic subproblem.
-Two tests for constrained minimization of multivariate scalar functions: \texttt{Sequential Least SQuares Programming} (SLSQP) and \texttt{Least-squares minimization}.
-And three for root finding with one for small problems \texttt{root\_finding} and two for large problems using a Krylov approximation for the inverse Jacobian with and without the help of a preconditioner: \texttt{root\_finding\_large\_preconditionned} and \texttt{root\_finding\_large}.
+This package has ten tests \tristan{that involve the same optimization problem solved with different methods?}: five for unconstrained minimization of multivariate scalar functions using different algorithms: \tristan{using twice : in the same sentence isn't recommended} \texttt{Nelder-Mead}~\cite{singer2009nelder} that iteratively transforms a simplex until its vertices are getting closer to local minima of the function.
+Fours \tristan{do you mean four?} Quasi-Newton-Raphson methods whose primary goal is to determine $x$ that minimizes the function $f$ by using Newton's method step: $x_{k+1} = x_{k} - B^{-1}(x_k)\nabla f(x_k)$, where $\nabla$ and $B$ are the gradient and the approximation of the Hessian matrix of $f$.
+The \texttt{Broyden-Fletcher-Goldfarb-Shanno}~\cite{BFGS} (BFGS) and \texttt{Newton-Conjugate-Gradient}~\cite{nocedal2006numerical} (NCG) are line search methods that approximate $H$ by adding two symmetric rank-one matrices and by using the Conjugate-Gradient method.
+The \texttt{Trust-Region Truncated Generalized Lanczos / Conjugate Gradient}~\cite{gould1999solving}, \texttt{Trust-Region Newton-Conjugate-Gradient}, and \texttt{Trust-Region Nearly Exact}~\cite{nocedal2006numerical} are trust-region methods approximating $H$ by solving the trust-region subproblem restricted to a truncated Krylov subspace and by solving nonlinear equations for each quadratic subproblem.
+\tristan{this sentence lacks a verb} Two tests for constrained minimization of multivariate scalar functions: \texttt{Sequential Least SQuares Programming} (SLSQP) and \texttt{Least-squares minimization}.
+Moreover, three for root finding with one for small problems \texttt{root\_finding} and two for large problems using a Krylov approximation for the inverse Jacobian with and without the help of a preconditioner: \texttt{root\_finding\_large\_preconditionned} and \texttt{root\_finding\_large}.
 
@@
 \[f(x) = \sum_{i=1}^{N-1} 100(x_{i+1}-x^2_i)^2 + (1-x_i)^2\]
-The minimum value of this function is 0, which is achieved when $x_i=1$.
+The minimum value of this function is 0, reached when $x_i=1$ \tristan{for all i's?}.
 Figure~\ref{fig:unconstrained_optimization} shows the number of significant bits of the solution for the different methods used.
-We can see that all methods have a good precision comprising between 43 and 53 bits significant.
-The Nelder-Mead method is the worst with $\simeq$ 43 bits on average, while the Trust-Region-Newton-CG has the best precision with $\simeq$ 53 bits significant, which is significant the maximum achievable within double precision.
-The remaining methods share a similar precision with less than 1 bit between them.
-
-The constrained minimization of multivariate scalar tests minimize the Rosenbrock function for SLSQP subject to
+All the methods have a good precision ranging from 43 to 53 significant bits.
+The Nelder-Mead method is the least precise one with $\simeq$ 43 significant bits on average, while the Trust-Region-Newton-CG is the most precise one with $\simeq$ 53 significant bits, this highest precision achievable in double precision.
+The remaining methods have a similar precision with less than 1 bit between them.
+\tristan{why is there only 9 methods in Fig 7 while you mentioned 10?}
+
+The constrained minimization of multivariate scalar tests minimize the Rosenbrock function for SLSQP subject to:
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-with the unique solution $[x_0, x_1] = [0.4149, 0.1701]$.
-Results within RR show a precision of 47 and 44 bits for the first and the second solution.
+The problem has a unique solution $[x_0, x_1] = [0.4149, 0.1701]$.
+Results within RR show a precision of 47 and 44 significant bits for the first and the second solution \tristan{which method is tested?}.
+
 The \texttt{least-square minimization} test solves a fitting problem from an enzymatic reaction~\cite{kowalik1968analysis} with 11 residuals defined as:
@@
 $x_i$ the unknown.
-Results within RR show a precision of [51,46,47,48] bits for the solution.
+Results within RR show a precision of 51, 46, 47, and 48 significant bits for each component of the solution respectively \tristan{which solver is used?}.
 
 Finally, the \texttt{root\_*} tests use three algorithms to 
-find root of non-linear equations. \texttt{root\_finding}
-uses the hybrid method of Powell to solve a single-variable transcendental equation and 
-the Levenberg-Marquardt for a set of non-linear equations. 
+find the root of non-linear equations. \texttt{root\_finding}
+uses the hybrid Powell method to solve a single-variable transcendental equation and 
+the Levenberg-Marquardt method for a set of non-linear equations. 
 \texttt{root\_finding\_large} and \texttt{root\_finding\_large\_preconditioned} tests use 
-Krylov method to solve an integrodifferential equation on a square
+the Krylov method to solve an integrodifferential equation on a square
  $(x,y) \in [0,1] \times [0,1]$, $P(x,1)=1$, and $P=0$ elsewhere on the boundary.
-The function $P$ is discretized with a Cartesian grid $P_{n,n}=P(nh,nh)$, with $n=75$ and its derivatives are approximated by $\partial_x^2P(x,y) \simeq (P(x+h,y) - 2P(x,y) + P(x-h,y))/h^2$.
+The function $P$ is discretized with a Cartesian grid $P_{n,n}=P(nh,nh)$, with $n=75$, and its derivatives are approximated by $\partial_x^2P(x,y) \simeq (P(x+h,y) - 2P(x,y) + P(x-h,y))/h^2$.
 
@@
 
-All tests diverge even within RR mode, which is not surprising since root-finding methods can easily take a few extra steps to find the root depending on the starting point.
+All the tests diverge even within RR, which is not surprising since root-finding methods can easily take a few extra steps to find the root depending on the starting point.
 Nevertheless, for the \texttt{root\_finding\_large} test, 3 traces among the 5 samples can be merged for both RR and MCA modes.
 Figure~\ref{fig:root_finding_large} shows the mean and standard deviation of the result for these 3 samples.
-We can see that both RR and Full MCA found a similar solution, with a less precise one for Full MCA, although the spread between RR and MCA is small with a maximal standard deviation of $8.10^{-9}$ for MCA against $3.10^{-9}$ for RR mode.
-Finally, it is interesting to note the impact of the preconditioning on the result numerical quality, with a precision doubling between \texttt{root\_finding\_large} and \texttt{root\_finding\_large\_preconditioned} as table~\ref{tab:pytracer_test_precision_summary} shows.
+We can see that both RR and Full MCA found a similar solution, although Full MCA leads to a lower precision than RR.
+\tristan{I don't get this: the spread between RR and MCA is small with a maximal standard deviation of $8.10^{-9}$ for MCA against $3.10^{-9}$ for RR mode.} Finally, it is interesting to note the impact of preconditioning on the result numerical quality: as Table~\ref{tab:pytracer_test_precision_summary} shows, the precision doubles between \texttt{root\_finding\_large} and \texttt{root\_finding\_large\_preconditioned}.
 
@@
     \end{subfigure}
-    \caption{Solution of \texttt{root\_finding\_large} test within RR (top row) and MCA (bottom row) with the mean value on the left and the standard deviation on the right.
+    \caption{Solution of \texttt{root\_finding\_large} test within RR (top row) and MCA (bottom row) \tristan{add sub-figure captions to avoid lengthy descriptions} with the mean value on the left and the standard deviation on the right.
 We can see that MCA has a less precision solution with a maximal standard deviation at $8.10^{-9}$ against $3.10^{-9}$ for RR mode.
@@
 Finally, the standard deviation stills lower than
-    the stopping criterion threshold fixed at $6.10^{-6}$.}
+    the stopping criterion threshold fixed at $6.10^{-6}$. }
     \label{fig:root_finding_large}
@@
 
-We tested Pytracer on the Scikit-learn~\cite{pedregosa2011scikit} library, a 
-Python library implementing a wide range of state-of-the-art machine learning algorithms.
-Scikit-learn offers a well supplied and documented list of examples that facilitates its using with Pytracer.
-Among the several available examples, we choose the following representative set:
+Scikit-learn offers a well-supplied and documented list of examples \tristan{examples ou tests?
+Si ce sont des tests, utilisons "test" partout a la place de "examples" ou "applications", pour sklearn comme pour scipy.} that facilitates its use with Pytracer.
+Among the several available examples, we choose the following representative set \tristan{Shall we just refer to Table 4 and remove this lengthy list?
+You could add the links in the table and mention in the table caption that the tests are linked to their source code}:
 \href{https://scikit-learn.org/stable/auto_examples/ensemble/plot_adaboost_regression.html#sphx-glr-auto-examples-ensemble-plot-adaboost-regression-py}{Decision Tree Regression with AdaBoost},
@@
 % \subsubsection{Adaboost}
+
+\tristan{For all the paragraphs below, add a sentence to describe the results as you did for scipy.
+If you have nothing more to say than what is reported in Table 4, then remove the paragraphs describing the algorithms and just refer to the sklearn doc linked from the table.
+If you have interesting things to discuss only for some tests, mention in the section intro that the text focuses on the most interesting stability patterns observed across all experiments.}
+
 \paragraph{Adaboost}
-This test compare a decision trees boosted with 300 estimators using the AdaBoost.R2~\cite{drucker1997improving} algorithm with
-a single decision tree regressor on a 1D sinusoidal dataset with a small amount of Gaussian noise. 
-The depth is fixed at 4. 
+This test compares a decision tree boosted with 300 estimators using the AdaBoost.R2~\cite{drucker1997improving} algorithm with
+a single decision tree regressor on a 1D sinusoidal dataset with a small amount of Gaussian noise and a depth fixed at 4. 
 % The example shows that as the number of boosts is increased the regressor can fit more detail.
@@
 Although the test does not raise a runtime error, the coefficients computed from the fitting for the synthetic dataset are \texttt{Not-A-Number} (NaN) values for both BRR and OLS.
-\pytracer traces reveal that the SVD solver used is the root cause.
+\pytracer traces reveal that the SVD solver used is the root cause for this error.
 Figure~\ref{fig:brr_svd_sig} shows
-the number of significant bits for the singular values SVD decomposition 
-For BRR, the SVD is directly called to compute the coefficient, while for the OLS, it is called during the Least-Squares minimization.
-Scikit-learn uses SciPy that itself uses the LAPACK library to compute the SVD.
+the number of significant bits for the singular values SVD decomposition. 
+For BRR, the SVD is directly called \tristan{from Lapack?} to compute the coefficients, while for the OLS, it is called during the Least-Squares minimization.
+Scikit-learn uses SciPy that itself uses the LAPACK library to compute the SVD \tristan{unclear what is the call path for each solver}.
 The LAPACK library has two main methods for computing the SVD: 
 \texttt{gesdd} and \texttt{gesvd}.
-The first one uses a Divide \& Conquer approach, while the second uses a QR decomposition.
-While both methods expect to have the same accuracy~\cite{nakatsukasa2013stable}, it appears that results diverge in practice with inaccurate results for the Divide \& Conquer method, as the sill opened an issue on the official LAPACK GitHub repository \href{https://github.com/Reference-LAPACK/lapack/issues/316}{github.com/Reference-LAPACK/lapack/issues/316} shows.
-For the Least-Square problem, the LAPACK library has three solvers, including \texttt{dgelss} that internally uses \texttt{gesdd} and \texttt{dgelsd} that uses \texttt{gesvd}.
-By using the \texttt{gesvd} (dgelsd) method instead of the \texttt{gesdd} (dgelss) one, the SVD is converging within the RR and Full MCA modes, with a number of significant bits of 44 on average.
+The former uses a Divide \& Conquer approach, while the latter uses a QR decomposition.
+While both methods are expected to have the same accuracy~\cite{nakatsukasa2013stable}, our results show that \texttt{gesdd} is totally imprecise, with an average number of significant digits of \tristan{0?}.
+This observation supports the on-going discussion among LAPACK developers on the instability of \texttt{gesdd} (see  \href{https://github.com/Reference-LAPACK/lapack/issues/316}{github.com/Reference-LAPACK/lapack/issues/316}).
+For the Least-Square problem, the LAPACK library has three solvers, including \texttt{dgelss} that internally uses \texttt{gesdd} and \texttt{dgelsd} that uses \texttt{gesvd} \tristan{t'es sur que c'est pas l'inverse?
+Sur la fig 9 on voit que dgelsd n'est pas precise du tout, ca suggere qu'elle utiliserait gesdd}.
+Using the \texttt{gesvd} (dgelsd) method instead of the \texttt{gesdd} (dgelss) one, the SVD is converging within the RR and Full MCA modes, with a number of significant bits of 44 on average.
+\tristan{Ce paragraph est difficile a lire (mais neanmoins super interessant !).
+Tu devrais le restructurer en expliquant (1) quelle methode utilise quel solver de quelle librairie, (2) la performance observee sur la fig 9 (tu pourais d'ailleurs ajouter le nom du solver (gesdd ou gesvd) entre parenthese dans la legende pour rendre l'explication plus claire, (3) le fait que ca confirme la discussion sur github et autres commentaires.}
 
@@
     (\texttt{gesdd} and  \texttt{dgelsd})
-    gives very low precision
+    gives low precision
     results for \textit{BRR} and even \texttt{NaN} values (star points) for \textit{OLS}. By switching to the \texttt{gesvd} method, 
-    results have a precision of 42 bits in average.
+    results have a precision of 42 bits on average.
     }
@@
 This test uses a Support Vector Classifier to recognize images of hand-written
-digits. The digits dataset consists of 8x8 pixel images of digits
+digits. The digits dataset consists of 8x8 pixel images of digits.
 
@@
 This test is the only one to raise an error within RR mode due to a non-convergence of the Singular Value Decomposition (SVD) performed during the PCA.
-In this test, the PCA uses the Randomized SVD~\cite{halko2011finding} variant that first computes a low-rank approximation of the input matrix by using a stochastic algorithm and then uses this approximation as the input for the SVD.
+In this test, the PCA uses the Randomized SVD~\cite{halko2011finding} variant that first computes a low-rank approximation of the input matrix using a stochastic algorithm and then uses this approximation as the input for the SVD.
 It is during the computation of this SVD that the test raised an error.
@@
 
-By using the \texttt{gesvd} method instead of the \texttt{gesdd} one, the SVD is converging within the RR mode.
+Using the  \texttt{gesvd} method instead of the \texttt{gesdd} one, the SVD converges within the RR mode.
 Moreover, figure~\ref{fig:randomized_svd_S} shows the precision of the eigenvalues computed, varying between 15 and 20 bits out of the 24 available in single precision.
@@
 In conclusion, the MCA model was helpful to detect the instability of the \texttt{gesdd} method that has been notified in several GitHub issues, including the LAPACK repository.
-It is worth mentioning that recently, a Pull Request has been submitted to let the user select the SVD method and avoid this kind of issue.
+It is worth mentioning that a Pull Request has recently been submitted to let the user select the SVD method and avoid this kind of issue.
 
@@
 This test compares the percentage of zero coefficients for logistic regression
-by varying the penalty (L1, L2 and Elastic-Net) and regularization (1, 0.1, 0.01) parameters. Large regularization value gives more freedom to the model
-while small value puts more constraints on the model.
+by varying the penalty (L1, L2 and Elastic-Net) and regularization (1, 0.1, 0.01) parameters. 
+A large regularization value gives the model more freedom than a small value, which puts more constraints on the model.
 
@@
 
-This test fits a logistic regression with the SAGA solver with the L1 penalty  
-on a subset of the MNIST digits classification task.
+This test fits a logistic regression with the SAGA solver with the L1 penalty on the MNIST digits classification task subset.
 
@@
 
-This test compare the linear and  RANSAC regression methods on a noisy data.
+This test compares the linear and  RANSAC regression methods on noisy data.
 % In this example we see how to robustly fit a linear model to faulty data using the RANSAC algorithm.
@@
 
-This test uses a spectral clustering to separate connected circles in an image.
+This test uses spectral clustering to separate connected circles in an image.
 
@@
 
-This test uses an plain and weighted classes SVC to find the best hyperplan separating an unbalanced dataset.
+This test uses a plain and weighted classes SVC to find the best hyperplane separating an unbalanced dataset.
 
@@
 This test compares the LASSO and Ridge regression models to 
-reconstruct an image from a set of projections for a dataset
+reconstruct an image from  projections for a dataset
 acquired from computed tomography.
@@
 
-This test uses a SGD to separate weighted points by 
-taking into account or the not the weights.
+This test uses an SGD to separate weighted points by 
+taking into account or not the weights.
 
@@
 
-\subsection{PyAFQ}
-
-PyAFQ is Python package for Automated Fiber Quantification.
-It aims at finding delineation of the major fiber tracts in individual human brains, and quantification of the tissue properties within the tracts.
+% \subsection{PyAFQ}
+
+% PyAFQ is a Python package for Automated Fiber Quantification.
+% It aims to find delineation of the major fiber tracts in individual human brains and quantify the tissue properties within the tracts.
+PyAFQ \pytracer tracing produces traces of 1TB with an average slowdown $\times 6$ compared to the actual execution.
+Moreover, \pytracer was able to visualize the aggregated traces, demonstrating its scalability fluently.
 
@@
 
-In this section, we review the performance overhead of the Pytracer's instrumentation cost
-and the time spent during the postprocessing analysis.
+This section reviews the performance overhead of the Pytracer's instrumentation cost and the time spent during the postprocessing analysis.
 
@@
 
-Pytracer instrumentation overhead comes from the time spent to instrument module (initialization overhead)
+Pytracer instrumentation overhead comes from the time spent on instrument module (initialization overhead)
 before executing the targeted application plus the cost for dumping the data during the execution (running overhead).
-The initialization overhead is proportional the number of functions and classes traced. 
-However, initialization overhead is amortized when traced applications are above 8 seconds, which is proportional to 
+The initialization overhead is proportional to the number of functions and classes traced. 
+However, initialization overhead is amortized when traced applications are above 8 seconds,  proportional to 
 the number of functions and classes traced.
@@
 and scikit-learn tests.
-We can see that Pytracer gives slowdown of $\times 17$ and
+We can see that Pytracer gives slowdowns of $\times 17$ and
 $\times 3.5$ if we subtract the initialization step.
-By adding fuzzy, we have an average slowdown of $\times 37$ for RR mode and $\times 43$ for Full MCA.
+Furthermore, we obtain an average slowdown of $\times 37$ for RR mode and $\times 43$ for Full MCA by adding fuzzy.
 
@@
     \caption{
-    The figure presents the \pytracer tracing overheads: \textit{Slowdown} is the actual overhead, computed as the ratio between the execution time without and with \pytracer.
+    \pytracer tracing overheads: \textit{Slowdown} is the actual overhead, computed as the ratio between the execution time without and with \pytracer.
 This slowdown can be high for the tests running less than 8 seconds because \pytracer spends most of its time in the initialization step.
@@
     using the fuzzy environment with RR and Full MCA modes.
-    The first four tests measure the initialization steps depending on the modules instrumented.
+    The first four tests measure the initialization steps depending on the modules instrumented. \tristan{you could make a horizontal chart to avoid rotating the labels (also in F  ig 13)}
     }
@@
 We measure a throughput of 7MB/s by taking the ratio size over time.
-Finally, \pytracer has been tested on PyAFQ~\cite{kruper2021evaluating}, a neuroimaging Python tool
-to automated fiber quantification with generated traces of 
-1TB that \pytracer was able to handle and fluently visualize.
 
@@
 It generates numerical traces that are aggregated in postprocessing to measure numerical discrepancies between executions.
-\pytracer does not make any assumption about the noise model used to estimate uncertainties but has been tested with the MCA 
+\pytracer does not assume the noise model used to estimate uncertainties but has been tested with the MCA 
 through the fuzzy ecosystem on two broadly used scientific libraries for Python with partial success.
@@
 Therefore, a posteriori reconstruction
-is a challenging task as one must precisely identify the flow path taken and find synchronization points to pursue the analysis.
+is challenging as one must precisely identify the flow path taken and find synchronization points to pursue the analysis.
 We retrieve, for example, this divergence behavior in two general classes of numerical schemes: iterative methods and optimization processes.
@@
 However, this would increase the complexity of the postprocess analysis as well as an extra slowdown factor.
-However, we believe that by coupling the Gantt chart with static analysis, \pytracer would catch some divergence patterns occurring within a function.
-Indeed, by instrumenting at the function level, \pytracer has a view on function's callees (i.e., the functions called within a function) and thus should partially detect flow divergences.
+However, by coupling the Gantt chart with static analysis, \pytracer would catch some divergence patterns occurring within a function.
+Indeed, by instrumenting at the function level, \pytracer views the function's callees (i.e., the functions called within a function) and thus should partially detect flow divergences.
 
@@
 However, we believe that instrumentation at the function level presents two advantages: it first limits the size of the traces since only inputs and outputs of a function are dumped instead of a full report which, on the one hand, decrease the overhead of the instrumentation and, on the other hand, help the user to identify instabilities quickly.
-One of the pitfalls can be overwhelming the user with too much information, which makes analysis more difficult.
+One of the pitfalls can be overwhelming the user with too much information, making analysis more difficult.
 Nevertheless, the analysis at fine granularity can be interesting at the final step of the understanding.
 Such an analysis would require a different instrumentation approach by, for example, working at the Abstract Syntax Tree (AST) level since it is trivial to get it in Python.
-An ideal way to do that would be to be able to extract and replay a function, in the same vein as the CERE~\cite{castro2015cere} tool does but for Python, and use an AST instrumentation to analyze step by step
-the numerical quality of elementary operations within the fuzzy environment.
-Lastly, AST analysis can serve as a basis for finding relationships between variables, which is valuable information for the user.
-
-In addition to runtime errors that it raises, mismatching shapes is also a problem when aggregating traces as \pytracer will not compute statistics for a set of arrays having different shapes.
-Two solutions exist to overcome this issue: the first one is to not instrument the \texttt{PyArray\_Arange} function with MCA.
+An ideal way to do that would be to extract and replay a function, in the same vein as the CERE~\cite{castro2015cere} tool does but for Python, and use an AST instrumentation to analyze the numerical quality of elementary operations step by step within the fuzzy environment.
+Lastly, AST analysis can serve as a basis for finding relationships between variables, valuable information for the user.
+
+In addition to the runtime errors it raises, mismatching shapes is also a problem when aggregating traces as PyTracer will not compute statistics for a set of arrays with different shapes.
+Two solutions exist to overcome this issue: the first is not to instrument the \texttt{PyArray\_Arange} function with MCA.
 The advantage is that it is easy to set up since it requires one extra line in the exclusion file.
@@
 because, as we have seen, the operations being evolved are elementary.
-The chances that developers reproduce the same pattern are very probable.
+Therefore, the chances that developers reproduce the same pattern are very probable.
 The second solution is to ensure that the Full MCA mode preserves the exact operations.
@@
 Keeping track of that noise would require recording each intermediate computation in a shadow memory or keeping a tag about their exactness.
-\Yohan{This idea has emerged by discussing with Verificarlo's team. 
+\Yohan{This idea emerged by discussing with Verificarlo's team. 
 I must find a way to express that and not give the impression that we discovered or suggest it.}
@@
 It works by automatically instrumenting Python libraries to produce numerical
-traces that can be interactively visualized through a Dash server.
-\pytracer does not require a manual intervention from the user neither rely on
-specific libraries and has been tested successfully tested on 
-intensively used on scientific libraries such as NumPy, SciPy and Scikit-learn.
-We demonstrated on a set of representative tests that \pytracer is scalable with an average instrumentation slowdown of $times 3.5$ and that is can handle traces up to 1TB while offering a fluent visualization to the user.
+traces interactively visualized through a Dash server.
+\pytracer does not require manual intervention from the user either rely on
+specific libraries and has been tested successfully on 
+intensively used on scientific libraries such as NumPy, SciPy, and Scikit-learn.
+We demonstrated on a set of representative tests that \pytracer is scalable with an average instrumentation slowdown of $times 3.5$, and that it can handle traces up to 1TB while offering a fluent visualization to the user.
 Moreover,
 \pytracer is by construction agnostic to the noise model used 
-to evaluate the numerical stability. We demonstrated 
+to evaluate the numerical stability. Finally, we have demonstrated 
 that \pytracer can be used with the Monte Carlo Arithmetic 
 through the fuzzy environment. 
-The experiments conducted in this paper are the first largest application of the fuzzy ecosystem by the wide range of applications covered. It is also the occasion for us to
-provided  feedback 
-about pitfalls and benefits encountered
-in order to shed light on the good and bad practices for first-time users and democratize MCA's usage.
-\pytracer is available at \href{https://github.com/yohanchatelain/pytracer}{github://yohanchatelain/pytracer} under an open source licence.
+The experiments conducted in this paper are the first largest application of the fuzzy ecosystem by the wide range of applications covered. 
+We also have to provide feedback about pitfalls and benefits encountered to shed light on first-time users' good and bad practices and democratize MCA's usage. 
+\pytracer is available at \href{https://github.com/yohanchatelain/pytracer}{github://yohanchatelain/pytracer} under an open source license.
 

### 2021-11-11 href.tex
Update comments

\newcommand{\discreteCosineRF}{ \href{https://docs.scipy.org/doc/scipy/tutorial/fft.html\#discrete-cosine-transforms}{discrete\_cosine\_transform} }
\newcommand{\fftOneDRf}{
\href{https://docs.scipy.org/doc/scipy/tutorial/fft.html\#d-discrete-fourier-transforms}{fft\_1D}
}

\newcommand{\fftTwoDRf}{
\href{https://docs.scipy.org/doc/scipy/tutorial/fft.html\#and-n-d-discrete-fourier-transforms}{fft\_2D}
}

\newcommand{\interOneDRf}{
\href{https://docs.scipy.org/doc/scipy/tutorial/interpolate.html\#d-interpolation-interp1d}{interpolation\_1D} 
}

\newcommand{\multiRf}{
\href{https://docs.scipy.org/doc/scipy/tutorial/interpolate.html\#multivariate-data-interpolation-griddata}{multivariate\_data} 
}

\newcommand{\bsplineRf}{
\href{https://docs.scipy.org/doc/scipy/tutorial/signal.html\#b-splines}{bspline}  
}

\newcommand{\splineOneDRf}{
    \href{https://docs.scipy.org/doc/scipy/tutorial/interpolate.html\#spline-interpolation-in-1-d-procedural-interpolate-splxxx}{
    spline\_1D} 
}

\newcommand{\splineTwoDRf}{
    \href{https://docs.scipy.org/doc/scipy/tutorial/interpolate.html\#d-spline-representation-procedural-bisplrep}{
    spline\_2D} 
}

\newcommand{\bfgsRf}{
    \href{https://docs.scipy.org/doc/scipy/tutorial/optimize.html\#broyden-fletcher-goldfarb-shanno-algorithm-method-bfgs}{broyden\_fletcher\_goldfarb\_shanno} 
}

\newcommand{\globalRf}{
    \href{https://docs.scipy.org/doc/scipy/tutorial/optimize.html\#global-optimization}{
    global\_optimization} 
}

\newcommand{\slsqpRf}{
    \href{https://docs.scipy.org/doc/scipy/tutorial/optimize.html\#sequential-least-squares-programming-slsqp-algorithm-method-slsqp}{
    slsqp} 
}

\newcommand{\lsmRf}{
    \href{https://docs.scipy.org/doc/scipy/tutorial/optimize.html\#least-squares-minimization-least-squares}{
    least\_square\_minimization} 
}

\newcommand{\nelderRf}{
    \href{https://docs.scipy.org/doc/scipy/tutorial/optimize.html\#nelder-mead-simplex-algorithm-method-nelder-mead}{nelder\_mead\_simplex}
}

\newcommand{\ncgRf}{
    \href{https://docs.scipy.org/doc/scipy/tutorial/optimize.html\#newton-conjugate-gradient-algorithm-method-newton-cg}{
    newton\_conjugate\_gradient}  
}

\newcommand{\rootRf}{
    \href{https://docs.scipy.org/doc/scipy/tutorial/optimize.html\#sets-of-equations}{
    root\_findings}  
}

\newcommand{\rootLargRf}{
    \href{https://docs.scipy.org/doc/scipy/tutorial/optimize.html\#root-finding-for-large-problems}{
    root\_finding\_large} 
}

\newcommand{\rootLargePredRf}{
    \href{https://docs.scipy.org/doc/scipy/tutorial/optimize.html\#still-too-slow-preconditioning}{
    root\_finding\_large\_preconditioned} 
}

\newcommand{\trustExactRf}{
    \href{https://docs.scipy.org/doc/scipy/tutorial/optimize.html\#trust-region-nearly-exact-algorithm-method-trust-exact}{
    trust\_region\_exact} 
}

\newcommand{\trustTruncRf}{
    \href{https://docs.scipy.org/doc/scipy/tutorial/optimize.html\#trust-region-truncated-generalized-lanczos-conjugate-gradient-algorithm-method-trust-krylov}{
    trust\_region\_truncated\_generalized\_lanczos} 
}

\newcommand{\trustNCGRf}{
    \href{https://docs.scipy.org/doc/scipy/tutorial/optimize.html\#trust-region-newton-conjugate-gradient-algorithm-method-trust-ncg}{
    trust\_region\_newton\_conjugate\_gradient} 
}

\newcommand{\AdaboostRf}{
    \href{https://scikit-learn.org/stable/auto_examples/ensemble/plot_adaboost_regression.html}{AdaBoost} 
}

\newcommand{\brrRf}{
    \href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_bayesian_ridge.html}{Bayesian Ridge Regression} 
}

\newcommand{\onlineClassifierComparisonRf}{
    \href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_sgd_comparison.html}{Online classifier comparison} 
}

\newcommand{\kmeansRf}{
    \href{https://scikit-learn.org/stable/auto_examples/cluster/plot_cluster_iris.html}{K-Means Clustering}  
}

\newcommand{\covarianceRf}{
    \href{https://scikit-learn.org/stable/auto_examples/covariance/plot_mahalanobis_distances.html}{Covariance estimation}  
}

\newcommand{\decisionRf}{
    \href{https://scikit-learn.org/stable/auto_examples/tree/plot_tree_regression.html}{Decision Tree Regression}
}

\newcommand{\digitsRf}{
    \href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_sgd_comparison.html}{Digits Classification} 
}

\newcommand{\faceRf}{
    \href{https://scikit-learn.org/stable/auto_examples/decomposition/plot_faces_decomposition.html}{Face Recognition} 
}

\newcommand{\penaltyRf}{
    \href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_logistic_l1_l2_sparsity.html}{L1 Penalty} 
}

\newcommand{\lassoRf}{
    \href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_lasso_and_elasticnet.html}{Lasso and Elastic Net} 
}

\newcommand{\hyperplaneRf}{
    \href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_sgd_separating_hyperplane.html}{Separating hyperplane} 
}

\newcommand{\mnistRf}{
    \href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_sparse_logistic_regression_mnist.html}{MNIST classification} 
}

\newcommand{\multitaskRf}{
    \href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_multi_task_lasso_support.html}{Multitask Lasso}  
}

\newcommand{\ompRf}{
    \href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_omp.html}{Orthogonal Matching} 
}

\newcommand{\pcaRf}{
    \href{https://scikit-learn.org/stable/auto_examples/decomposition/plot_pca_iris.html}{PCA decomposition}  
}

\newcommand{\robustRf}{
    \href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_ransac.html}{Robust Linear Regression} 
}

\newcommand{\toyRf}{
    \href{https://scikit-learn.org/stable/auto_examples/cluster/plot_segmentation_toy.html\#sphx-glr-auto-examples-cluster-plot-segmentation-toy-py}{Segmentation toy}  
}

\newcommand{\svmRf}{
    \href{https://scikit-learn.org/stable/auto_examples/svm/plot_separating_hyperplane_unbalanced.html\#sphx-glr-auto-examples-svm-plot-separating-hyperplane-unbalanced-py}{SVM}  
}

\newcommand{\tomographyRf}{
    \href{https://scikit-learn.org/stable/auto_examples/applications/plot_tomography_l1_reconstruction.html\#sphx-glr-auto-examples-applications-plot-tomography-l1-reconstruction-py}{
    Tomography} 
}

\newcommand{\weightedRf}{
    \href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_sgd_weighted_samples.html\#sphx-glr-auto-examples-linear-model-plot-sgd-weighted-samples-py}{SGD weighted samples} 
}

### 2021-11-11 paper.tex
Update comments

@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{xspace}
@@
 \newcommand{\warn}[0]{\cellcolor{orange!75}?}
+\newcommand{\scross}[0]{\ding{53}~}
+\newcommand{\svalid}[0]{\ding{51}~}
+\newcommand{\swarn}[0]{?~}
 \newcommand{\pytracer}[0]{PyTracer\xspace}
+
+\include{href}
 
@@
 However, despite the pervasiveness of Python in data science, analyzing large Python programs remains challenging due to the lack of scalable numerical analysis tools available for this language.
+We developed \pytracer, a profiler to quantify numerical instability in Python applications to address this issue.
+\pytracer automatically instruments Python code at a low cost ($\simeq3.5\times$) to produce numerical traces and visualize them interactively in a Plotly dashboard.
+We designed \pytracer to work with any numerical noise model, including Monte-Carlo Arithmetic, random rounding or, random data perturbations.
+We illustrate \pytracer's capabilities by testing the numerical stability of key functions in the SciPy and Scikit-learn Python libraries.
+\pytracer permitted pinpointing numerical instabilities caused by a LAPACK library function and fixing them.
+% Numerical stability is a crucial requirement of reliable scientific computing.
+However, despite the pervasiveness of Python in data science, analyzing large Python programs remains challenging due to the lack of scalable numerical analysis tools available for this language.
 To address this issue, we developed \pytracer, a profiler to quantify numerical instability in Python applications.
 \pytracer automatically instruments Python code to produce numerical traces and visualize them interactively in a Plotly dashboard.
-\pytracer is designed to work with any type of numerical noise model, including Monte-Carlo Arithmetic, random rounding or random data perturbations.
+% \pytracer is designed to work with any type of numerical noise model, including Monte-Carlo Arithmetic, random rounding or random data perturbations.
 We illustrate \pytracer's capabilities by testing the numerical stability of key functions in the SciPy and Scikit-learn Python libraries.
-\tristan{Add one sentence to summarize the findings} Finally, \pytracer slows down executions by only $3.5 \times$ on average.
+Finally, \pytracer slows down executions by only $3.5 \times$ on average.
+\tristan{Add one sentence to summarize the findings} 
 \end{abstract}
@@
 It is combined with symbolic computation to backtrack the root of the error.
-We can note that all methods based on a high-precision oracle suppose that computing with a large number of bits is sufficient to obtain an accurate result, which is not always true (see for example, the famous Muller's sequence~\cite{chatelain2018veritracer} \tristan{it looks like your veritracer paper is the first time where the ``famous Muller's sequence" was described, is that so?}).
+We can note that all methods based on a high-precision oracle suppose that computing with a large number of bits is sufficient to obtain an accurate result, which is not always true (see for example, the famous Muller's sequence~\cite{bajard1996introduction}.
+%\tristan{it looks like your veritracer paper is the first time where the ``famous Muller's sequence" was described, is that so?}).
 
@@
 
-Three main approaches exist to detect numerical instabilities: stochastic arithmetic, uncertainty or sensitivity analysis, and random seed analysis.
-\tristan{add key references for uq/sa if any} \pytracer focuses on stochastic arithmetic \tristan{due to...}
+Three main approaches exist to detect numerical instabilities: stochastic arithmetic, uncertainty or sensitivity analysis~\cite{helton2006survey}, and random seed analysis~\cite{click2011quality}.
+%\tristan{add key references for uq/sa if any}
+\pytracer focuses on stochastic arithmetic since it does not require assumptions about 
+the noise model contrary to the sensitivity analysis.
+Moreover, stochastic arithmetic allows evaluating the numerical quality of an implementation.
+%\tristan{due to...}
 Stochastic arithmetic leverages randomness to estimate numerical instabilities coming from the use of floating-point representations. The main idea is to treat round-off errors 
@@
 \pytracer's \texttt{loader} class first loads the original module, then copies it as a new instance of the \texttt{ModuleType} class.
-It then calls the appropriate instrumentation function for each attribute depending on its type (function, class, or instances --- see below \tristan{iterators?}) and replaces the original module in the \texttt{sys.modules} map with the instrumented version.
-Finally, it updates all existing references to the original module, such as those in \texttt{\_\_globals\_\_} function attributes containing references to internal function objects \tristan{this sentence doesn't make sense, please update}.
+It then calls the appropriate instrumentation function for each attribute depending on its type (function, class, or instances) and replaces the original module in the \texttt{sys.modules} map with the instrumented version.
+Finally, it updates all existing references to the original module contained in the global symbol table.
 As a result, the application will transparently call the instrumented module.
@@
     \caption{\pytracer's generic wrapper function that dumps
-    the inputs and outputs of the wrapped function.
-    \pytracer binds arguments to the function signature to avoid
-    mispositioning \tristan{what does mispositioning means here?} and to show readable names in the visualization.
-    }
+    the inputs and outputs of the wrapped function.}
     \label{fig:generic_wrapper}
@@
  implements a wide range of state-of-the-art algorithms.
-For each library, we executed the software tests provided in their respective GitHub repositories.
-We traced each test five times, having activated MCA in the Python interpreter, BLAS, LAPACK, NumPy, SciPy, and scikit-learn.
-We repeated the experiment with two MCA modes, Random Rounding (RR) and Full MCA, resulting in 2 experiments for each test.
+For each library, we executed the software examples provided in their respective GitHub repositories.
+We traced each example five times, having activated MCA in the Python interpreter, BLAS, LAPACK, NumPy, SciPy, and scikit-learn.
+We repeated the experiment with two MCA modes, Random Rounding (RR) and Full MCA, resulting in 2 experiments for each example.
 We used the default virtual precision in Verificarlo, namely 24 bits for single-precision floating-point values and 53 bits for double-precision values, which simulates machine error.
-\tristan{Report scipy and sklearn versions used.}
+We used Python-3.8.5, NummPy-1.19.1, SciPy-1.5.4, and scikit-learn-0.23.2.
+%  \tristan{Report scipy and sklearn versions used.}
 
@@
 
-Tables~\ref{tab:pytracer_scipy_results_summary} and~\ref{tab:pytracer_sklearn_results_summary} summarize 
-\pytracer's outcome on SciPy and scikit-learn tests.
-Each table reports on the tracing and trace aggregation steps with three possible outcomes: green for success, red for numerical error in the application, and orange for errors in the fuzzy noise injection \tristan{Explain what this is, in a setence here or with a subsubsection if it requires more}.
-Overall, the tracing and parsing of SciPy and scikit-learn tests in Random Rounding mode was entirely successful for 32/40 tests.
-The remaining tests failed due to numerical errors in the libraries, which we discuss hereafter.
+Table~\ref{tab:pytracer_results_summary} summarizes
+\pytracer's outcome on SciPy and scikit-learn examples.
+The columns \textit{trace} and \textit{parse} report on the tracing and trace aggregation steps with three possible outcomes: green for success, red for numerical error in the application, and orange for errors due to the fuzzy noise injection
+that are not considered as numerical errors, like for instance index errors due to an index shift.
+% \tristan{Explain what this is, in a setence here or with a subsubsection if it requires more}. 
+Overall, the tracing and parsing of SciPy and scikit-learn examples in Random Rounding mode was entirely successful for 32/40 examples.
+The remaining examples failed due to numerical errors in the libraries, which we discuss hereafter.
 The instrumentation with Full MCA is more invasive and reduced the number of successful executions to 12/40.
+
+The column \textit{result} summarizes the precision for main outputs of SciPy and scikit-learn examples. 
+We measured the precision in significant bits on the main example output by taking the element-wise mean for non-scalar values and, if the example produces many outputs, the average value among all of them.
+The numerical quality across all examples varies from 0 to 52, with an average of 44 significant bits.
+For both modes, we note that only one example failed due to a numerical error
+% \tristan{can we see that in the table? if not, don't comment on it, it is puzzling. Could you show that in the table by using the same error symbols as in Table 2?} 
+(\texttt{face\_recognition} for RR and \textit{Bayesian Ridge Regression} for Full MCA) even though we underestimate this number since Full MCA mode is more intrusive than RR mode and most of the examples produce error caused by the fuzzy noise injection.
 
@@
     \centering
-    \begin{tabular}{|ll|c|c|c|c|}
+    \small
+    \begin{subfigure}[t]{\linewidth}
+    \centering
+    \begin{tabular}{|ll|c|c|c|c|c|c|}
     \hline
-    \multicolumn{2}{|c}{ \multirow{2}{*}{Application} } & \multicolumn{2}{|c|}{RR} & \multicolumn{2}{c|}{Full MCA} \\
-    \cline{3-6}
-    & & trace & parse & trace & parse  \\
+    \multicolumn{2}{|c}{ \multirow{2}{*}{Application} } & \multicolumn{3}{|c|}{Random Rounding (RR)} & \multicolumn{3}{c|}{Full MCA} \\
+    \cline{3-8}
+    & & trace & parse & result & trace & parse & result \\
     \hline
@@
     \multicolumn{1}{|c|}{ \multirow{3}{2em}{ \rotatebox{90}{FFT} } }
-    & discrete\_cosine\_transform &  \valid & \valid & \warn & \cross \\ 
-    \multicolumn{1}{|c|}{} & fft\_1D & \valid & \valid& \warn & \cross \\
-    \multicolumn{1}{|c|}{} & fft\_2D & \valid & \valid & \valid & \valid \\
+    & \discreteCosineRF &  \valid & \valid & 52 & \warn & \cross & 47 \\ 
+    \multicolumn{1}{|c|}{} & \fftOneDRf & \valid & \valid & 41 & \warn  & \cross & - \\
+    \multicolumn{1}{|c|}{} & \fftTwoDRf & \valid & \valid & 52 & \valid & \valid & 52 \\
     \hline 
     \multicolumn{1}{|c|}{  \multirow{5}{2em}{ \rotatebox{90}{Interpolation} } }
-    & interpolation\_1D & \valid & \valid & \warn & \cross  \\
-    \multicolumn{1}{|c|}{} & multivariate\_data & \valid & \valid & \warn & \cross \\
-     \multicolumn{1}{|c|}{} & bspline  & \valid & \valid & \valid & \valid \\
-     \multicolumn{1}{|c|}{} & spline\_1D & \valid & \cross & \warn & \cross \\
-     \multicolumn{1}{|c|}{} & spline\_2D & \valid & \valid & \warn & \cross \\
+    & \interOneDRf & \valid & \valid & 51 & \warn & \cross &  - \\
+     \multicolumn{1}{|c|}{} & \multiRf      & \valid & \valid & 51 & \warn  & \cross & - \\
+     \multicolumn{1}{|c|}{} & \bsplineRf    & \valid & \valid &10 &  \valid & \valid & 10\\
+     \multicolumn{1}{|c|}{} & \splineOneDRf & \valid & \cross & 52 & \warn  & \cross & 52 \\
+     \multicolumn{1}{|c|}{} & \splineTwoDRf & \valid & \valid & 10 &  \warn  & \cross & - \\
     \hline
      \multicolumn{1}{|c|}{ \multirow{12}{2em}{ \rotatebox{90}{Optimization} } }
-    & broyden\_fletcher\_goldfarb\_shanno & \valid & \valid & \valid & \valid \\
-     \multicolumn{1}{|c|}{} & global\_optimization & \valid & \cross  & \warn & \cross \\
-    \multicolumn{1}{|c|}{}  & slsqp & \valid & \valid  & \valid & \valid \\
-     \multicolumn{1}{|c|}{} & least\_square\_minimization & \valid & \valid  & \warn & \cross \\
-     \multicolumn{1}{|c|}{} & nelder\_mead\_simplex  & \valid & \valid  & \valid & \valid \\
-     \multicolumn{1}{|c|}{} & newton\_conjugate\_gradient  & \valid & \valid  & \valid & \cross \\
-     \multicolumn{1}{|c|}{} & root\_findings  & \valid & \cross & \warn & \cross \\
-    \multicolumn{1}{|c|}{}  & root\_finding\_large & \valid & \cross  & \valid & \cross \\
-     \multicolumn{1}{|c|}{} & root\_finding\_large\_preconditionned & \valid & \cross & \valid & \cross \\
-    \multicolumn{1}{|c|}{}  & trust\_region\_exact& \valid & \valid  & \valid & \valid \\
-     \multicolumn{1}{|c|}{} & trust\_region\_truncated\_generalized\_lanczos & \valid & \valid & \valid & \valid \\
-    \multicolumn{1}{|c|}{}  & trust\_region\_newton\_conjugate\_gradient & \valid & \valid & \valid & \valid \\
+    & \bfgsRf & \valid & \valid & 48  & \valid & \valid & 46 \\
+     \multicolumn{1}{|c|}{} & \globalRf & \valid & \cross & 17 & \warn  & \cross & - \\
+     \multicolumn{1}{|c|}{} & | SHGO\footnote{Simplicial Homology Global Optimization} & \valid & \cross & 25 & \warn  & \cross & - \\
+     \multicolumn{1}{|c|}{} & | Dual Annealing & \valid & \cross & 4 & \warn  & \cross & - \\
+     \multicolumn{1}{|c|}{} & | Differential Evolution & \valid & \cross & 0 & \warn  & \cross & - \\
+     \multicolumn{1}{|c|}{} & | Basin Hopping & \valid & \cross & 40 & \warn  & \cross & - \\
+     \multicolumn{1}{|c|}{} & | SHGO Sobol    & \valid & \cross & 45 & \warn  & \cross & - \\
+     \multicolumn{1}{|c|}{} & \slsqpRf  & \valid & \valid & 45 & \valid & \valid & 44 \\
+     \multicolumn{1}{|c|}{} & \lsmRf    & \valid & \valid & 48 & \warn  & \cross & - \\
+     \multicolumn{1}{|c|}{} & \nelderRf & \valid & \valid & 44 & \valid & \valid & 42 \\
+     \multicolumn{1}{|c|}{} & \ncgRf    & \valid & \valid & 48 & \valid & \cross & 47 \\
+     \multicolumn{1}{|c|}{} & \rootRf   & \valid & \cross & 52 & \warn  & \cross & 50 \\
+    \multicolumn{1}{|c|}{}  & \rootLargRf      & \valid & \cross & 29 & \valid & \cross & 26 \\
+     \multicolumn{1}{|c|}{} & \rootLargePredRf & \valid & \cross & 42 & \valid & \cross & 42 \\
+    \multicolumn{1}{|c|}{}  & \trustExactRf & \valid & \valid & 48  & \valid & \valid & 46 \\
+     \multicolumn{1}{|c|}{} & \trustTruncRf & \valid & \valid & 48  & \valid & \valid & 46 \\
+    \multicolumn{1}{|c|}{}  & \trustNCGRf   & \valid & \valid & 52  & \valid & \valid & 47 \\
     \hline
-    \end{tabular}
-    \caption{\pytracer execution summary on SciPy tests.\\RR: Random Rounding.
-trace: outcome of \pytracer tracing, parse: outcome of \pytracer trace parsing and aggregation.
-\valid: successful run, \warn: error in fuzzy noise injection, \cross: numerical error or divergent traces.}
-    \label{tab:pytracer_scipy_results_summary}
-\end{table}
-
-\begin{table}[]
-    \centering
-    \begin{tabular}{|c|c|c|c|c|}
-    \hline
-    \multirow{2}{5em}{Application} & \multicolumn{2}{c|}{RR} & \multicolumn{2}{c|}{MCA} \\\cline{2-5}
-                                & trace & parse &  trace & parse \\
-    \hline
+%     \end{tabular}
+% \end{subfigure}
+%     \label{tab:pytracer_scipy_results_summary}
+% % \end{table}
+% % \begin{table}[]
+%     \centering
+% \begin{subfigure}[t]{.8\linewidth}
+%     \begin{tabular}{|c|c|c|c|c|c|c|}
+%     \hline
+%     \multirow{2}{5em}{Application} & \multicolumn{3}{c|}{RR} & \multicolumn{3}{c|}{MCA} \\\cline{2-7}
+%                                 & trace & parse & result &  trace & parse & result \\
+%     \hline
     %        &               RR                 &                 MCA               \\
@@
     %        & run   & parse  &  run   &  parse &  run   & parse  & run    & parse  \\
-    Adaboost & \valid & \valid  & \warn & \cross \\
-    Bayesian Ridge Regression  & \valid & \valid  & \cross & \cross \\
-    Online classifier comparison & \valid & \valid  & \warn & \cross  \\
-    K-Means Clustering  & \valid & \valid  & \valid & \cross \\
-    Covariance estimation  & \valid & \cross  & \warn & \cross \\
-    Decision Tree Regression & \valid & \valid  & \valid & \valid \\
-    Digits Classification  & \valid & \valid  & \warn & \cross \\
-    Face Recognition  & \cross & \valid  & \warn & \cross \\
-    L1 Penalty  & \valid & \valid  & \valid & \valid \\
-    Lasso and elastic net  & \valid & \valid  & \warn & \cross \\
-    Separating hyperplan  & \valid & \valid  & \valid & \cross \\
-    MNIST classification  & \valid & \valid  & \warn & \valid \\
-    Multitask Lasso  & \valid & \valid  & \warn & \valid \\
-    Orthogonal matching & \valid & \valid  & \valid & \valid \\
-    PCA decomposition  & \valid & \valid  & \valid & \valid \\
-    Robust Linear Regression  & \valid & \valid  & \warn & \cross \\
-    Segmentation toy  & \valid & \valid  & \warn & \cross \\
-    SVM  & \valid & \valid  & \valid & \cross \\
-    Tomography  & \valid & \cross  & \warn & \cross \\
-    Weighted samples  & \valid & \valid  & \valid & \cross \\
+
+    \multicolumn{1}{|c|}{ \multirow{20}{2em}{ \rotatebox{90}{Scikit-learn} } }
+    & \AdaboostRf   & \valid & \valid & 48 & \warn  & \cross & - \\
+    \multicolumn{1}{|c|}{} & \brrRf        & \valid & \valid & 25 & \cross & \cross & - \\
+    \multicolumn{1}{|c|}{} & | $1^{st}$ dataset & \valid & \valid & 25 & \cross & \cross & - \\
+    \multicolumn{1}{|c|}{} & | $2^{nd}$ dataset & \valid & \valid & nan & \cross & \cross & - \\
+    \multicolumn{1}{|c|}{} & \onlineClassifierComparisonRf & \valid & \valid & 20 & \warn & \cross & -  \\
+    \multicolumn{1}{|c|}{} & \kmeansRf     & \valid & \valid & 52 & \valid & \cross & - \\
+    \multicolumn{1}{|c|}{} & \covarianceRf & \valid & \cross & 48 & \warn  & \cross & - \\
+    \multicolumn{1}{|c|}{} & \decisionRf   & \valid & \valid & 50 & \valid & \valid & 50 \\
+    \multicolumn{1}{|c|}{} & \digitsRf     & \valid & \valid & 52 & \warn  & \cross & 52 \\
+    \multicolumn{1}{|c|}{} & \faceRf       & \cross & \valid & -  & \warn  & \cross & - \\
+    \multicolumn{1}{|c|}{} & \penaltyRf    & \valid & \valid & -  & \valid & \valid & - \\
+    \multicolumn{1}{|c|}{} & \lassoRf      & \valid & \valid & 48 & \warn  & \cross & 47 \\
+    \multicolumn{1}{|c|}{} & \hyperplaneRf & \valid & \valid & 3  & \valid & \cross & - \\
+    \multicolumn{1}{|c|}{} & \mnistRf      & \valid & \valid & 43 & \warn  & \valid & - \\
+    \multicolumn{1}{|c|}{} & \multitaskRf  & \valid & \valid & 50 & \warn  & \valid & 48 \\
+    \multicolumn{1}{|c|}{} & \ompRf        & \valid & \valid & 52 & \valid & \valid & 52 \\
+    \multicolumn{1}{|c|}{} & \pcaRf        & \valid & \valid & 48 & \valid & \valid & 48 \\
+    \multicolumn{1}{|c|}{} & \robustRf     & \valid & \valid & 50 & \warn  & \cross & 48 \\
+    \multicolumn{1}{|c|}{} & | Linear        & \valid & \valid & 48 & \warn  & \cross & 46 \\
+    \multicolumn{1}{|c|}{} & | RANSAC        & \valid & \valid & 50 & \warn  & \cross & 48 \\
+    \multicolumn{1}{|c|}{} & \toyRf        & \valid & \valid & 35 & \warn  & \cross & - \\
+    \multicolumn{1}{|c|}{} & \svmRf        & \valid & \valid & 43.5 & \valid & \cross & - \\
+    \multicolumn{1}{|c|}{} & | Non-weighted  & \valid & \valid & 43 & \valid & \cross & - \\
+    \multicolumn{1}{|c|}{} & | Weighted      & \valid & \valid & 44 & \valid & \cross & - \\
+    \multicolumn{1}{|c|}{} & \tomographyRf & \valid & \cross & - & \warn  & \cross & - \\
+    \multicolumn{1}{|c|}{} & \weightedRf   & \valid & \valid & 44 & \valid & \cross & - \\
     \hline
     \end{tabular}
-    \caption{\pytracer execution summary on Scikit-learn tests.
-\\RR: Random Rounding.
+    \end{subfigure}
+    \caption{\pytracer execution summary on SciPy and Scikit-learn examples.
+\\ \emph{trace}: outcome of \pytracer tracing, \emph{parse}: outcome of \pytracer trace parsing and aggregation, \emph{result}: precision for main outputs in significant bits.
+\valid: successful run, \warn: error from invalid noise injection, \cross: numerical error or divergent traces.
+\textit{nan} stands for (\texttt{Not-A-Number}).
+The names example are linked to their source code.}
+    \label{tab:pytracer_results_summary}
+\end{table}
+
+    % \caption{
+    % \pytracer execution summary on SciPy examples.\\RR: Random Rounding.
 trace: outcome of \pytracer tracing, parse: outcome of \pytracer trace parsing and aggregation.
-\valid: successful run, \warn: error in fuzzy noise injection, \cross: numerical error or divergent traces.}
-    \label{tab:pytracer_sklearn_results_summary}
-\end{table}
+\valid: successful run, \warn: error in fuzzy noise injection, \cross: numerical error or divergent traces.
+    % }
 
@@
 Full MCA even perturbs exact values such as integers represented with floating-point values, leading to many execution failures.
-For instance, the \texttt{fft1} test from SciPy raised an \texttt{ValueError: operands could not be broadcast together with shapes (601,) (600,)} error due to an array shape mismatch.
+For instance, the \texttt{fft1} example from SciPy raised an \texttt{ValueError: operands could not be broadcast together with shapes (601,) (600,)} error due to an array shape mismatch.
 A closer inspection showed that one of the arrays involved in the error was created with the NumPy function \texttt{linspace} that itself calls function \texttt{arange} (Listing~\ref{fig:pyarray_range_code}).
-Lines 3174-3178 show that the function stores the array size in a floating-point value that will be perturbed by Full MCA, as shown in table~\ref{tab:mca_result_linspace}, resulting in array sizes that fluctuate between N and N+1.
-It is worth noting that 78\% of execution issues encountered in Full MCA mode without \texttt{ufunc} instrumentation
+Lines 3174-3178 show that the function stores the array size in a floating-point value that will be perturbed by Full MCA, as shown in Table~\ref{tab:mca_result_linspace}, resulting in array sizes that fluctuate between N and N+1.
+It is worth noting that 78\% of execution issues encountered in Full MCA mode instrumentation
 are due to this type of ``typing" errors.  
-While they do not lead to any numerical issue, typing errors should still be fixed to preserve code quality \tristan{do we really mean that given your answer to my comment below?}.
+In conclusion, those regions of code should not be perturbed by MCA since the injected noise does not make sense.
+\tristan{conclusion: ces regions du code ne devraient pas etre bruitees car le bruit n'a pas de sens ici (exemple du spin dans -1/2,1/2. Ca correspond aux ?}
+% While they do not lead to any numerical issue, typing errors should still be fixed
+% by improving the Full MCA mode instrumentation in order to preserve code correctness.
+\tristan{do we really mean that given your answer to my comment below?}. 
+\Yohan{By reading again this sentence, I agree that it is confusing. 
+It suggests that we should fixed the code while my idea was to fix the MCA instrumentation.}
 We provide solutions to help MCA better work with those cases in the discussion section.
@@
 
-\subsubsection{Overall numerical quality}
-
-Table~\ref{tab:pytracer_test_precision_summary} summarizes the precision for main outputs of SciPy and scikit-learn tests. 
-We measured the precision in significant bits on the main test output by taking the element-wise mean for non-scalar values and, if the test produces many outputs, the average value among all of them.
-The numerical quality across all tests varies from 0 to 52, with an average of 44 significant bits.
-For both modes, we note that only one test failed due to a numerical error \tristan{can we see that in the table?
-if not, don't comment on it, it is puzzling.
-Could you show that in the table by using the same error symbols as in Table 2?} (\texttt{face\_recognition} for RR and \textit{Bayesian Ridge Regression} for Full MCA) even though we underestimate this number since Full MCA mode is more intrusive than RR mode and most of the tests produce error caused by the fuzzy noise injection.
-
-\begin{table}
-\small
-\begin{subfigure}[t]{.5\linewidth}
-    \centering
-    \begin{tabular}{|l|c|c|}
-    \hline 
-    Test & RR & MCA \\
-    \hline
-    discrete\_cosine\_transform & 52 & 47 \\ 
-    fft\_1D & 41 & - \\
-    fft\_2D & 52 & 52  \\
-    \hline
-    interpolation\_1D & 51 & -   \\
-    multivariate\_data & 51 & - \\
-    bspline  & 10 & 10  \\
-    spline\_1D & 52 & 52 \\
-    spline\_2D & 10 & - \\
-    \hline
-    broyden\_fletcher\_goldfarb\_shanno & 48 & 46 \\
-    global\_optimization & 17 & - \\
-    | SHGO\footnote{Simplicial Homology Global Optimization} & 25 & - \\
-    | Dual Annealing & 4 & - \\
-    | Differential Evolution & 0 & - \\
-    | Basin Hopping & 40 & - \\
-    | SHGO Sobol & 45 & - \\
-    slsqp & 45 & 44 \\
-    least\_square\_minimization & 48 & -  \\
-    nelder\_mead\_simplex  & 44 & 42  \\
-    newton\_conjugate\_gradient  & 48 & 47 \\
-    root\_findings  & 52 & 50 \\
-    root\_finding\_large & 29 & 26   \\
-    root\_finding\_large\_preconditioned & 42 & 42 \\
-    trust\_region\_exact& 48 & 46  \\
-    trust\_region\_truncated\_generalized\_lanczos & 48 & 46  \\
-    trust\_region\_newton\_conjugate\_gradient & 52 & 47 \\
-    \hline
-    \end{tabular}
-\end{subfigure}
-\hspace{1cm}
-\begin{subfigure}[t]{.5\linewidth}
-    \begin{tabular}{|l|c|c|}
-    \hline 
-    Test & RR & MCA \\
-    \hline
-    Adaboost & 48 & - \\
-    Bayesian Ridge Regression  & 25 & -  \\
-    | $1^{st}$ dataset & nan & - \\
-    | $2^{nd}$ dataset & 20 & - \\
-    Online classifier comparison & 48 & -  \\
-    K-Means Clustering  & 52 & -   \\
-    Covariance estimation  & 48 & -   \\
-    Decision Tree Regression & 50 & 50  \\
-    Digits Classification  & 52 & 52 \\
-    Face Recognition  & - & - \\
-    L1 Penalty  & - & -   \\
-    Lasso and elastic net  & 48 & 47  \\
-    Separating hyperplan  & 3 & -  \\
-    MNIST classification  & 43 & - \\
-    Multitask Lasso  & 50 & 48   \\
-    Orthogonal matching & 52 & 52  \\
-    PCA decomposition  & 48 & 48   \\
-    Robust Linear Regression  & 50 & 48   \\
-    | Linear & 48 & 46 \\
-    | RANSAC & 50 & 48 \\
-    Segmentation toy  & 35 & - \\
-    SVM  & 43.5 &  -  \\
-    | Non-weighted & 44 & - \\
-    | Weighted & 43 & - \\
-    Tomography  & - & -  \\
-    Weighted samples  & 44 & -   \\
-    \hline
-    \end{tabular}
-\end{subfigure}
-    \caption{Summary of tests precision for main outputs of SciPy (left) and scikit-learn (right) tests. 
-    Dash values indicate runtime errors. \tristan{explain the meaning of nans here}}
-    \label{tab:pytracer_test_precision_summary}
-\end{table}
+% \subsubsection{Overall numerical quality}
+
+% \begin{table}
+% \small
+% \begin{subfigure}[t]{.5\linewidth}
+%     \centering
+%     \begin{tabular}{|l|c|c|}
+%     \hline 
+%     Example & RR & MCA \\
+%     \hline
+%     \discreteCosineRF & 52 & 47 \\ 
+%     \fftOneDRf & 41 & \swarn \\
+%     \fftTwoDRf & 52 & 52  \\
+%     \hline
+%     \interOneDRf & 51 & \swarn   \\
+%     \multiRf & 51 & \swarn \\
+%     \bsplineRf & 10 & 10  \\
+%     \splineOneDRf & 52 & 52 \\
+%     \splineTwoDRf & 10 & \swarn \\
+%     \hline
+%     \bfgsRf & 48 & 46 \\
+%     \globalRf & 17 & \swarn \\
+%     | SHGO\footnote{Simplicial Homology Global Optimization} & 25 & \swarn \\
+%     | Dual Annealing & 4 & \swarn \\
+%     | Differential Evolution & 0 & \swarn \\
+%     | Basin Hopping & 40 & \swarn \\
+%     | SHGO Sobol & 45 & \swarn \\
+%     \slsqpRf & 45 & 44 \\
+%     \lsmRf & 48 & \swarn \\
+%     \nelderRf & 44 & 42  \\
+%     \ncgRf & 48 & 47 \\
+%     \rootRf & 52 & 50 \\
+%     \rootLargRf & 29 & 26   \\
+%     \rootLargePredRf & 42 & 42 \\
+%     \trustExactRf & 48 & 46  \\
+%     \trustTruncRf & 48 & 46  \\
+%     \trustNCGRf & 52 & 47 \\
+%     \hline
+%     \end{tabular}
+% \end{subfigure}
+% \hspace{1cm}
+% \begin{subfigure}[t]{.5\linewidth}
+%     \begin{tabular}{|l|c|c|}
+%     \hline 
+%     Example & RR & MCA \\
+%     \hline
+%     \AdaboostRf & 48 & \swarn \\
+%     \brrRf & 25 & \scross  \\
+%     | $1^{st}$ dataset & nan & \scross \\
+%     | $2^{nd}$ dataset & 20 & \scross \\
+%     \onlineClassifierComparisonRf & 48 & \swarn  \\
+%     \kmeansRf & 52 & \swarn   \\
+%     \covarianceRf & 48 & \swarn   \\
+%     \decisionRf & 50 & 50  \\
+%     \digitsRf & 52 & 52 \\
+%     \faceRf & \scross & \scross \\
+%     \penaltyRf & - & -   \\
+%     \lassoRf & 48 & 47  \\
+%     \hyperplaneRf & 3 & \swarn  \\
+%     \mnistRf & 43 & \swarn \\
+%     \multitaskRf & 50 & 48   \\
+%     \ompRf & 52 & 52  \\
+%     \pcaRf & 48 & 48   \\
+%     \robustRf & 50 & 48   \\
+%     | Linear & 48 & 46 \\
+%     | RANSAC & 50 & 48 \\
+%     \toyRf & 35 & \swarn \\
+%     \svmRf & 43.5 &  \swarn  \\
+%     | Non-weighted & 44 & \swarn \\
+%     | Weighted & 43 & \swarn \\
+%     \tomographyRf & \swarn & \swarn  \\
+%     \weightedRf & 44 & \swarn   \\
+%     \hline
+%     \end{tabular}
+% \end{subfigure}
+%     \caption{Summary of examples precision for main outputs of SciPy (left) and scikit-learn (right) examples. 
+%     \textit{\swarn} values indicate runtime errors or an impossible traces aggregation,
+%     \scross values indicate numerical errors, and \textit{nan} stands for (\texttt{Not-A-Number}).
+%     The names example are linked to their source code.
+%     % \tristan{explain the meaning of nans here}
+%     \tristan{let's discuss the possibility to merge Table 4 in Tables 1 and 2}
+%     }
+%     \label{tab:pytracer_test_precision_summary}
+% \end{table}
 
@@
 
-We tested \pytracer on SciPy examples provided in the tutorial website section \tristan{Are these tests? If not we need to reword the begining of this section (I can do it, just let me know).}.
+We tested \pytracer on SciPy examples provided in the tutorial website section 
+\tristan{Are these tests? If not we need to reword the begining of this section (I can do it, just let me know).}.
+\Yohan{No you right, these are examples, not tests, I used the two words interchangeably.}
 SciPy is organized in several libraries targeting specific computing domains.
@@
 
-This package has three tests \tristan{tests or examples?}: \texttt{discrete\_cosine\_transform}, \texttt{fft\_1D}, and \texttt{fft\_2D}. All computations are done in double precision.
+This package has three examples : \texttt{discrete\_cosine\_transform}, \texttt{fft\_1D}, and \texttt{fft\_2D}. All computations are done in double precision.
 The results for \texttt{discrete\_cosine\_transform},\texttt{fft\_1D} and  \texttt{fft\_2D} show
 precise numerical results with 48 significant bits in average. 
-We observe that the FFT computation is stable to noisy inputs. Figures~\ref{fig:fft1D_mean} (inputs) and~\ref{fig:fft1D_std} (outputs)
+We observe that the FFT computation is stable to noisy inputs. Figures~\ref{fig:fft1D_inputs} (inputs) and~\ref{fig:fft1D_outputs} (outputs)
 show the mean and standard deviation of the MCA samples. 
@@
 \item $z_1 = \sin(50 . 2\pi . x_i) + \dfrac{1}{2} \sin(80 . 2\pi . x_i),\; x_i = \frac{i}{600},\; i \in [0,600]$
-\item $\mathrm{blackman}(400)*z_1 \tristan{is * the convolution operator?}$
+\item $\mathrm{blackman}(400) \times z_1$
 \item $ z_2= e^{50 . i 2\pi . x_i} + \dfrac{1}{2} e^{-80 . i2\pi .x_i },\; x_i = \frac{i}{800},\; i \in [0,400] $
@@
 
-Top row in Figures~\ref{fig:fft1D_mean} and~\ref{fig:fft1D_std} 
+Top row in Figures~\ref{fig:fft1D_inputs} and~\ref{fig:fft1D_outputs} 
 show the input mean value while the bottom row shows the standard deviation.
-The points with low magnitude \tristan{in Figure~\ref{fig:fft1D_mean}?} correspond to inputs near 0 when the input of $\sin$ or 
-$\exp$ is close to $k\pi$, $k \in \mathbf{Z}$.
+The points with low magnitude in Figure~\ref{fig:fft1D_inputs} correspond 
+to inputs near 0 when the input of $\sin$ or 
+$\exp$ is close to $k\pi$, $k \in \mathbb{Z}$.
 Indeed, since MCA introduces a slight noise, the result is not exactly 0.
-We can see in Figure~\ref{fig:fft1D_std} \tristan{isn't it in Figure 3?} that the maximal noise introduced by MCA on the
+We can see in Figure~\ref{fig:fft1D_inputs} 
+% \tristan{isn't it in Figure 3?} 
+% \Yohan{No figure 4, I'm talking about the MCA noise, so we look at the std}
+that the maximal noise introduced by MCA on the
 inputs is in the order of $10^{-14}$, two orders of magnitude higher than the 
@@
 This slight noise introduced can be interpreted as white noise on the input signal. 
-We can see on the bottom row of Figure~\ref{fig:fft1D_std} that the frequency noise is of 
+We can see on the bottom row of Figure~\ref{fig:fft1D_outputs} that the frequency noise is of 
 the same order of of magnitude as the input noise, which is expected. 
@@
     fft 1D inputs within RR mode (log scale). The real part is shown in blue and the imaginary part in orange.\tristan{put stdev of middle column on the same scale as the other columns}}
-    \label{fig:fft1D_mean}
+    \label{fig:fft1D_inputs}
 \end{figure}
@@
     for fft 1D outputs within RR mode (log scale).}
-    \label{fig:fft1D_std}
+    \label{fig:fft1D_outputs}
 \end{figure}
@@
 Figure~\ref{fig:bspline_rr}
-shows the significant bits (figs.~\ref{fig:bspline_bisplev_sig},~\ref{fig:bspline_convol2d_sig}), 
-mean (figs.~\ref{fig:bspline_bisplev_mean},~\ref{fig:bspline_convol2d_mean}), and standard deviation (figs.~\ref{fig:bspline_bisplev_std},~\ref{fig:bspline_convol2d_std}) \tristan{replace the figure references with labels in the figure, it would be much clearer} maps for the two methods as well as the input image (fig.~\ref{fig:bspline_input}) with the middle for the \texttt{bisplev} results and bottom row for the \texttt{convol2d}.
+shows the significant bits, mean, and standard deviation 
+% \tristan{replace the figure references with labels in the figure, it would be much clearer} 
+maps for the two methods as well as the input image (fig.~\ref{fig:bspline_input}) with the middle for the \texttt{bisplev} results and bottom row for the \texttt{convol2d}.
 Both methods exhibit similar precision, with 11 significant bits on average.
-Standard deviations maps on figures~\ref{fig:bspline_bisplev_std} and~\ref{fig:bspline_convol2d_std} show that regions with low spatial frequencies correspond to regions with low standard deviation, similar to the FFT results.
+Standard deviations maps on Figures~\ref{fig:bspline_bisplev_std} and~\ref{fig:bspline_convol2d_std} show that regions with low spatial frequencies correspond to regions with low standard deviation, similar to the FFT results.
 As it is mentioned in the SciPy tutorial, the \texttt{bisplev} function is faster than the \texttt{convol2d}.
@@
 Figure~\ref{fig:spline2d_rr} shows the results of the spline evaluation with \texttt{bisplev}.
-\tristan{conclusion?}
+We can see that a significant loss of precision in places, following
+an interesting pattern that would be interesting to examine in detail.
+
+\tristan{conclusion? perte de significativite importante par endroits, qui suit un pattern interessant. IL serait interessant d'examiner plus en details pourquoi cela arrive.}
 
@@
 \begin{subfigure}{.3\linewidth}
-    \includegraphics[width=\linewidth]{figure/bspline/original_image.png}
-    \caption{}
-    \label{fig:bspline_input}
+    \includegraphics[width=\linewidth]{figure/bspline/original_image.pdf}
+    \caption{Original image.}
+    \label{fig:bspline_original_image}
 \end{subfigure}\\
 \begin{subfigure}{0.3\linewidth}
-    \includegraphics[width=\linewidth]{figure/bspline/bisplev_ret_sig_portland_r.png}
-    \caption{}
+    \includegraphics[width=\linewidth]{figure/bspline/bspline_sig.pdf}
+    \caption{\texttt{sepfir2d} significant bits.}
     \label{fig:bspline_input}
@@
 \begin{subfigure}{0.3\linewidth}
-    \includegraphics[width=\linewidth]{figure/bspline/bisplev_ret_mean_log_portland.png}
-    \caption{}
+    \includegraphics[width=\linewidth]{figure/bspline/bspline_mean_log.pdf}
+    \caption{\texttt{sepfir2d} mean.}
     \label{fig:bspline_bisplev_mean}
@@
 \begin{subfigure}{0.3\linewidth}
-    \includegraphics[width=\linewidth]{figure/bspline/bisplev_ret_std_log_portland.png}
-    \caption{}
+    \includegraphics[width=\linewidth]{figure/bspline/bspline_std_log.pdf}
+    \caption{\texttt{sepfir2d} standard deviation.}
     \label{fig:bspline_bisplev_std}
@@
 \begin{subfigure}{0.3\linewidth}
-    \includegraphics[width=\linewidth]{figure/bspline/convol2d_ret_sig_portland_r.png}
-    \caption{}
+    \includegraphics[width=\linewidth]{figure/bspline/convol2d_sig.pdf}
+    \caption{\texttt{convol2d} significant bits.}
     \label{fig:bspline_convol2d_sig}
@@
 \begin{subfigure}{0.3\linewidth}
-    \includegraphics[width=\linewidth]{figure/bspline/convol2d_ret_mean_log_portland.png}
-    \caption{}
+    \includegraphics[width=\linewidth]{figure/bspline/convol2d_mean_log.pdf}
+    \caption{\texttt{convol2d} mean.}
     \label{fig:bspline_convol2d_mean}
@@
 \begin{subfigure}{0.3\linewidth}
-    \includegraphics[width=\linewidth]{figure/bspline/convol2d_ret_std_log_portland.png}
-    \caption{}
+    \includegraphics[width=\linewidth]{figure/bspline/convol2d_std_log.pdf}
+    \caption{\texttt{convol2d} standard deviation.}
     \label{fig:bspline_convol2d_std}
 \end{subfigure}
-    \caption{\texttt{bspline} results within RR mode. Left column shows the \texttt{bisplev} function
-    while the right column shows the \texttt{convolve2d} function. \tristan{isn't it top row vs bottom row? Replace these hard-to-read explanations with good labels in the figure}}
+    \caption{\texttt{bspline} results within RR mode.
+    The SciPy tutorial mentions that \texttt{convol2d} is faster than \texttt{sepfir2d}.
+    In addition, our results show that \texttt{sepfir2d} offers a similar precision.
+    This gives an additional argument for using \texttt{sepfir2d} over \texttt{convol2d}.
+    % \tristan{can you use the same color maps as in figure 8?}
+    % Left column shows the \texttt{bisplev} function
+    % while the right column shows the \texttt{convolve2d} function. \tristan{isn't it top row vs bottom row? Replace these hard-to-read explanations with good labels in the figure}
+    }
     \label{fig:bspline_rr}
@@
     \centering
-    \includegraphics[width=\linewidth]{figure/spline_2d/bisplev_inputs_mean.png}
-    \caption{\texttt{bisplev} IEEE result}
-    \label{fig:bisplev_ieee}
+    \includegraphics[width=\linewidth]{figure/spline_2d/bisplev_mean.pdf}
+    \caption{Mean value}
+    \label{fig:bisplev_mean}
 \end{subfigure}
@@
     \centering
-    \includegraphics[width=\linewidth]{figure/spline_2d/bisplev_inputs_mean_log.png}
+    \includegraphics[width=\linewidth]{figure/spline_2d/bisplev_mean_log.pdf}
     \caption{Absolute mean value (log)}
@@
     \centering
-    \includegraphics[width=\linewidth]{figure/spline_2d/bisplev_inputs_std_log.png}
+    \includegraphics[width=\linewidth]{figure/spline_2d/bisplev_std_log.pdf}
     \caption{Standard deviation (log)}
@@
 \end{subfigure}
-    \caption{2D Spline interpolation results. Figure~\ref{fig:bisplev_ieee} shows the IEEE result
+    \caption{2D Spline interpolation results. Figure~\ref{fig:bisplev_mean} shows the mean result
     of the 2D-spline interpolation. Figures~\ref{fig:bisplev_mean_log} and~\ref{fig:bisplev_std_log}
     show respectively in the logarithmic scale the absolute mean value and the standard deviation 
-    of the 5 samples run within RR mode. \tristan{any reason why you are showing the ieee result?}}
+    of the 5 samples run within RR mode. 
+    % \tristan{any reason why you are showing the ieee result?} \tristan{can you use the same color maps as in figure 8?}
+    }
     \label{fig:spline2d_rr}
@@
 
-This package has ten tests \tristan{that involve the same optimization problem solved with different methods?}: five for unconstrained minimization of multivariate scalar functions using different algorithms: \tristan{using twice : in the same sentence isn't recommended} \texttt{Nelder-Mead}~\cite{singer2009nelder} that iteratively transforms a simplex until its vertices are getting closer to local minima of the function.
-Fours \tristan{do you mean four?} Quasi-Newton-Raphson methods whose primary goal is to determine $x$ that minimizes the function $f$ by using Newton's method step: $x_{k+1} = x_{k} - B^{-1}(x_k)\nabla f(x_k)$, where $\nabla$ and $B$ are the gradient and the approximation of the Hessian matrix of $f$.
+This package has eleven examples whose seven examples involve the same optimization problem 
+solved with and without constrained by using different methods.
+The last four solve solve a different problem each.
+
+\paragraph{Unconstrained minimization of multivariate scalar functions (six methods):}
+Four Quasi-Newton-Raphson methods aim to determine $x$ that minimizes the function $f$ by using Newton's method step: $x_{k+1} = x_{k} - B^{-1}(x_k)\nabla f(x_k)$, where $\nabla$ and $B$ are the gradient and the approximation of the Hessian matrix of $f$.
 The \texttt{Broyden-Fletcher-Goldfarb-Shanno}~\cite{BFGS} (BFGS) and \texttt{Newton-Conjugate-Gradient}~\cite{nocedal2006numerical} (NCG) are line search methods that approximate $H$ by adding two symmetric rank-one matrices and by using the Conjugate-Gradient method.
-The \texttt{Trust-Region Truncated Generalized Lanczos / Conjugate Gradient}~\cite{gould1999solving}, \texttt{Trust-Region Newton-Conjugate-Gradient}, and \texttt{Trust-Region Nearly Exact}~\cite{nocedal2006numerical} are trust-region methods approximating $H$ by solving the trust-region subproblem restricted to a truncated Krylov subspace and by solving nonlinear equations for each quadratic subproblem.
-\tristan{this sentence lacks a verb} Two tests for constrained minimization of multivariate scalar functions: \texttt{Sequential Least SQuares Programming} (SLSQP) and \texttt{Least-squares minimization}.
-Moreover, three for root finding with one for small problems \texttt{root\_finding} and two for large problems using a Krylov approximation for the inverse Jacobian with and without the help of a preconditioner: \texttt{root\_finding\_large\_preconditionned} and \texttt{root\_finding\_large}.
-
-The unconstrained minimization of multivariate scalar minimizes the Rosenbrock function of $N$ variables:
+The \texttt{Trust-Region Truncated Generalized Lanczos / Conjugate Gradient}~\cite{gould1999solving} (TR-Krylov), \texttt{Trust-Region Newton-Conjugate-Gradient} (TR-NCG), and \texttt{Trust-Region Nearly Exact}~\cite{nocedal2006numerical} (TR-Exact) are trust-region methods approximating $H$ by solving the trust-region subproblem restricted to a truncated Krylov subspace and by solving nonlinear equations for each quadratic subproblem.
+In addition, the \texttt{Nelder-Mead}~\cite{singer2009nelder} simplex-based method iteratively transforms a simplex until its vertices are getting closer to a local minima of the function.
+
+\paragraph{Constrained minimization of multivariate scalar functions (two methods):}
+\texttt{Sequential Least SQuares Programming} (SLSQP~\cite{kraft1988software})
+and \texttt{Least-squares minimization} that uses the Trust Region Reflective algorithm~\cite{li1993centering}.
+
+\paragraph{Root finding (three methods):}
+One for small problems using the hybrid Powell and Levenberg-Marquardt methods for small problems (\texttt{root\_finding}) and two for large problems using a Krylov approximation for the inverse Jacobian with and without the help of a preconditioner (\texttt{root\_finding\_large\_preconditionned} and \texttt{root\_finding\_large}).
+
+The unconstrained minimization methods minimize the Rosenbrock function of $N$ variables:
 \[f(x) = \sum_{i=1}^{N-1} 100(x_{i+1}-x^2_i)^2 + (1-x_i)^2\]
-The minimum value of this function is 0, reached when $x_i=1$ \tristan{for all i's?}.
+The minimum value of this function is 0, reached when $x_i=1,\; \forall i \leq N-1$. % \tristan{for all i's?}
 Figure~\ref{fig:unconstrained_optimization} shows the number of significant bits of the solution for the different methods used. 
+The $(p)$ notation for the NCG, Trust-Krylov, and Trust-NCG methods in the legend refers 
+to the variant where the Hessian matrix is replaced by 
+a function computing the matrix-vector product of the Hessian and an arbitrary vector
+that allows saving memory and time. 
 All the methods have a good precision ranging from 43 to 53 significant bits.
@@
 The remaining methods have a similar precision with less than 1 bit between them.
-\tristan{why is there only 9 methods in Fig 7 while you mentioned 10?}
-
-The constrained minimization of multivariate scalar tests minimize the Rosenbrock function for SLSQP subject to:
+% \tristan{why is there only 9 methods in Fig 7 while you mentioned 10?} \Yohan{There are 11 examples whose 6 for the unconstrained minimization (presented in Fig 7).
+For 3 methods, there is a variant using the Hessian product instead of the Hessian matrix.I realized that this variant is not explained in the text.
+I will update it.}
+
+The SLSQP also minimizes the Rosenbrock function with the following constraint:
 \begin{eqnarray*}
@@
 The problem has a unique solution $[x_0, x_1] = [0.4149, 0.1701]$.
-Results within RR show a precision of 47 and 44 significant bits for the first and the second solution \tristan{which method is tested?}.
-
-The \texttt{least-square minimization} test solves a fitting problem from an enzymatic reaction~\cite{kowalik1968analysis} with 11 residuals defined as:
+Results within RR show a precision of 47 and 44 significant bits for the first and the second solution. %\tristan{which method is tested?}.
+
+The \texttt{least-square minimization} example solves a fitting problem from an enzymatic reaction~\cite{kowalik1968analysis} with 11 residuals defined as:
 \begin{eqnarray*}
@@
 $x_i$ the unknown.
-Results within RR show a precision of 51, 46, 47, and 48 significant bits for each component of the solution respectively \tristan{which solver is used?}.
-
-Finally, the \texttt{root\_*} tests use three algorithms to 
+Results within RR show a precision of 51, 46, 47, and 48 significant bits for each component of the solution respectively.% \tristan{which solver is used?}.
+
+Finally, the \texttt{root\_*} examples use three algorithms to 
 find the root of non-linear equations. \texttt{root\_finding}
@@
 the Levenberg-Marquardt method for a set of non-linear equations. 
-\texttt{root\_finding\_large} and \texttt{root\_finding\_large\_preconditioned} tests use 
+\texttt{root\_finding\_large} and \texttt{root\_finding\_large\_preconditioned} examples use 
 the Krylov method to solve an integrodifferential equation on a square
@@
 
-All the tests diverge even within RR, which is not surprising since root-finding methods can easily take a few extra steps to find the root depending on the starting point.
-Nevertheless, for the \texttt{root\_finding\_large} test, 3 traces among the 5 samples can be merged for both RR and MCA modes.
+All the examples diverge even within RR, which is not surprising since root-finding methods can easily take a few extra steps to find the root depending on the starting point.
+Nevertheless, for the \texttt{root\_finding\_large} example, 3 traces among the 5 samples can be merged for both RR and MCA modes.
 Figure~\ref{fig:root_finding_large} shows the mean and standard deviation of the result for these 3 samples.
-We can see that both RR and Full MCA found a similar solution, although Full MCA leads to a lower precision than RR.
-\tristan{I don't get this: the spread between RR and MCA is small with a maximal standard deviation of $8.10^{-9}$ for MCA against $3.10^{-9}$ for RR mode.} Finally, it is interesting to note the impact of preconditioning on the result numerical quality: as Table~\ref{tab:pytracer_test_precision_summary} shows, the precision doubles between \texttt{root\_finding\_large} and \texttt{root\_finding\_large\_preconditioned}.
+We can see that both RR and Full MCA found a similar solution.
+Full MCA leads to a lower precision than RR although both standard deviation maps remain in the same order of magnitude.
+Finally, it is interesting to note the impact of preconditioning on the result numerical quality: as Table~\ref{tab:pytracer_results_summary} shows, the precision doubles between \texttt{root\_finding\_large} and \texttt{root\_finding\_large\_preconditioned}.
 
@@
     \centering
-    \includegraphics[width=\linewidth]{figure/unconstrained_optimization_comparison.png}
+    \includegraphics[width=\linewidth]{figure/unconstrained_optimization_comparison.pdf}
     \caption{Comparison of results precision for different optimization solvers within RR mode.}
@@
     \includegraphics[width=\linewidth]{figure/root_finding/solution_mean_RR.pdf}
-    \caption{}
-    \label{fig:my_label}
+    \caption{Mean solution (RR)}
+    \label{fig:mean_solution_rr}
     \end{subfigure}
@@
     \includegraphics[width=\linewidth]{figure/root_finding/solution_std_RR.pdf}
-    \caption{}
-    \label{fig:my_label}
+    \caption{Standard deviation solution (RR)}
+    \label{fig:stdev_rr}
     \end{subfigure}
@@
     \includegraphics[width=\linewidth]{figure/root_finding/solution_mean_MCA.pdf}
-    \caption{}
-    \label{fig:my_label}
+    \caption{Mean solution (Full MCA)}
+    \label{fig:mean_solution_mca}
     \end{subfigure}
     \begin{subfigure}{0.45\linewidth}
-    \includegraphics[width=\linewidth]{figure/root_finding/solution_std_MCA.pdf}    \caption{}
-    \label{fig:my_label}
+    \includegraphics[width=\linewidth]{figure/root_finding/solution_std_MCA.pdf}    
+    \caption{Standard deviation (Full MCA)}
+    \label{fig:stdev_mca}
     \end{subfigure}
-    \caption{Solution of \texttt{root\_finding\_large} test within RR (top row) and MCA (bottom row) \tristan{add sub-figure captions to avoid lengthy descriptions} with the mean value on the left and the standard deviation on the right.
+    \caption{Solution of \texttt{root\_finding\_large} example. 
     We can see that MCA has a less precision solution with a maximal standard deviation at $8.10^{-9}$ against $3.10^{-9}$ for RR mode.
@@
 
-Scikit-learn offers a well-supplied and documented list of examples \tristan{examples ou tests?
-Si ce sont des tests, utilisons "test" partout a la place de "examples" ou "applications", pour sklearn comme pour scipy.} that facilitates its use with Pytracer.
-Among the several available examples, we choose the following representative set \tristan{Shall we just refer to Table 4 and remove this lengthy list?
-You could add the links in the table and mention in the table caption that the tests are linked to their source code}:
-\href{https://scikit-learn.org/stable/auto_examples/ensemble/plot_adaboost_regression.html#sphx-glr-auto-examples-ensemble-plot-adaboost-regression-py}{Decision Tree Regression with AdaBoost},
-\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_bayesian_ridge.html#sphx-glr-auto-examples-linear-model-plot-bayesian-ridge-py}{Bayesian Ridge Regression}, 
-\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_sgd_comparison.html#sphx-glr-auto-examples-linear-model-plot-sgd-comparison-py}{Comparing various online solvers}, 
-\href{https://scikit-learn.org/stable/auto_examples/cluster/plot_cluster_iris.html#sphx-glr-auto-examples-cluster-plot-cluster-iris-py}{K-means Clustering},
-\href{https://scikit-learn.org/stable/auto_examples/covariance/plot_mahalanobis_distances.html#sphx-glr-auto-examples-covariance-plot-mahalanobis-distances-py}{Covariance Estimation},
-\href{https://scikit-learn.org/stable/auto_examples/tree/plot_tree_regression.html#sphx-glr-auto-examples-tree-plot-tree-regression-py}{Decision Tree Regression},
-\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_sgd_comparison.html#sphx-glr-auto-examples-linear-model-plot-sgd-comparison-py}{Recognizing hand-written digits},
-\href{https://scikit-learn.org/stable/auto_examples/decomposition/plot_faces_decomposition.html#sphx-glr-auto-examples-decomposition-plot-faces-decomposition-py}{Faces dataset decomposition},
-\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_logistic_l1_l2_sparsity.html#sphx-glr-auto-examples-linear-model-plot-logistic-l1-l2-sparsity-py}{L1 Penalty and Sparsity in Logistic Regression},
-\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_lasso_and_elasticnet.html#sphx-glr-auto-examples-linear-model-plot-lasso-and-elasticnet-py}{Lasso and Elastic Net for Sparse Signals},
-\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_sgd_separating_hyperplane.html#sphx-glr-auto-examples-linear-model-plot-sgd-separating-hyperplane-py}{SGD: Maximum margin separating hyperplane},
-\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_sparse_logistic_regression_mnist.html#sphx-glr-auto-examples-linear-model-plot-sparse-logistic-regression-mnist-py}{MNIST classification using multinomial logistic + L1},
-\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_sgd_iris.html#sphx-glr-auto-examples-linear-model-plot-sgd-iris-py}{Plot multi-class SGD on the iris dataset},
-\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_multi_task_lasso_support.html#sphx-glr-auto-examples-linear-model-plot-multi-task-lasso-support-py}{Joint feature selection with multi-task Lasso},
-\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_omp.html#sphx-glr-auto-examples-linear-model-plot-omp-py}{Orthogonal Matching Pursuit},
-\href{https://scikit-learn.org/stable/auto_examples/decomposition/plot_pca_iris.html#sphx-glr-auto-examples-decomposition-plot-pca-iris-py}{PCA example with Iris Data-set},
-% \href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_poisson_regression_non_normal_loss.html#sphx-glr-auto-examples-linear-model-plot-poisson-regression-non-normal-loss-py}{Poisson regression and non-normal loss},
-\href{https://scikit-learn.org/stable/auto_examples/cluster/plot_segmentation_toy.html#sphx-glr-auto-examples-cluster-plot-segmentation-toy-py}{Spectral clustering for image segmentation},
-\href{https://scikit-learn.org/stable/auto_examples/svm/plot_separating_hyperplane_unbalanced.html#sphx-glr-auto-examples-svm-plot-separating-hyperplane-unbalanced-py}{SVM: Separating hyperplane for unbalanced classes},
-\href{https://scikit-learn.org/stable/auto_examples/applications/plot_tomography_l1_reconstruction.html#sphx-glr-auto-examples-applications-plot-tomography-l1-reconstruction-py}{Compressive sensing: tomography reconstruction with L1 prior (Lasso)},
-% \href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_tweedie_regression_insurance_claims.html#sphx-glr-auto-examples-linear-model-plot-tweedie-regression-insurance-claims-py}{Tweedie regression on insurance claims},
-\href{https://scikit-learn.org/stable/auto_examples/linear_model/plot_sgd_weighted_samples.html#sphx-glr-auto-examples-linear-model-plot-sgd-weighted-samples-py}{SGD: Weighted samples}.
+Scikit-learn offers a well-supplied and documented list of examples 
+% \tristan{examples ou tests? Si ce sont des tests, utilisons "test" partout a la place de "examples" ou "applications", pour sklearn comme pour scipy.} 
+that facilitates its use with Pytracer.
+Among the several available examples, we choose the following representative set
+listed in~\ref{tab:pytracer_results_summary}. The following paragraphs 
+focus on the most interesting stability results observed across all experiments.
+% \tristan{Shall we just refer to Table 4 and remove this lengthy list? You could add the links in the table and mention in the table caption that the tests are linked to their source code}:
 
@@
 
-\tristan{For all the paragraphs below, add a sentence to describe the results as you did for scipy.
+% \tristan{For all the paragraphs below, add a sentence to describe the results as you did for scipy.
 If you have nothing more to say than what is reported in Table 4, then remove the paragraphs describing the algorithms and just refer to the sklearn doc linked from the table.
-If you have interesting things to discuss only for some tests, mention in the section intro that the text focuses on the most interesting stability patterns observed across all experiments.}
-
-\paragraph{Adaboost}
-This test compares a decision tree boosted with 300 estimators using the AdaBoost.R2~\cite{drucker1997improving} algorithm with
-a single decision tree regressor on a 1D sinusoidal dataset with a small amount of Gaussian noise and a depth fixed at 4. 
+If you have interesting things to discuss only for some examples, mention in the section intro that the text focuses on the most interesting stability patterns observed across all experiments.}
+
+% \paragraph{Adaboost}
+% This test compares a decision tree boosted with 300 estimators using the AdaBoost.R2~\cite{drucker1997improving} algorithm with
+% a single decision tree regressor on a 1D sinusoidal dataset with a small amount of Gaussian noise and a depth fixed at 4. 
 % The example shows that as the number of boosts is increased the regressor can fit more detail.
@@
 
-\paragraph{Online classifier comparison}
-
-This example compares how the following online solvers perform on the hand-written digits dataset:
-Stochastic Gradient Descent (SGD) with maximum iterations fixed to 100, 
-Averaged Stochastic Gradient Descent (ASGD),
-Perceptron, Passive-Aggressive I with the hinge loss function, tolerance 
-and regularization fixed at $10^{-4}$ and $1$,
-Passive-Aggressive II with the squared hinge loss function, tolerance 
-and regularization fixed at $10^{-4}$ and $1$, and Stochastic Average Gradient (SAG)
-with the tolerance and regularization fixed at $10^{-4}$ and $5.10^{-8}$.
+% \paragraph{Online classifier comparison}
+% This example compares how the following online solvers perform on the hand-written digits dataset:
+% Stochastic Gradient Descent (SGD) with maximum iterations fixed to 100, 
+% Averaged Stochastic Gradient Descent (ASGD),
+% Perceptron, Passive-Aggressive I with the hinge loss function, tolerance 
+% and regularization fixed at $10^{-4}$ and $1$,
+% Passive-Aggressive II with the squared hinge loss function, tolerance 
+% and regularization fixed at $10^{-4}$ and $1$, and Stochastic Average Gradient (SAG)
+% with the tolerance and regularization fixed at $10^{-4}$ and $5.10^{-8}$.
 
@@
 % MCA: Index issue
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\linewidth]{figure/BRR/call_path.pdf}
+    \caption{Call paths of the Bayesian Ridge Regression (BRR) and 
+    Ordinary Least Square (OLS) function. Each fill color represents the calling library
+    with orange for scikit-learn, blue for SciPy and yellow for LAPACK.
+    Dashed color represents the original path in red and the alternative one in green.
+    Figure~\ref{fig:brr_svd_sig} shows that using the original method to compute the \texttt{svd}
+    approach that leads to numerical instabilities and that the alternative one helps 
+    making the example to converge.
+    }
+    \label{fig:call_path_brr}
+\end{figure}
 
@@
 
-This test compares a Bayesian Ridge Regression (BRR) to the Ordinary Least Squares (OLS) estimator on a synthetic dataset and for one-dimensional regression using polynomial feature expansion.
-Although the test does not raise a runtime error, the coefficients computed from the fitting for the synthetic dataset are \texttt{Not-A-Number} (NaN) values for both BRR and OLS.
+This example compares a Bayesian Ridge Regression (BRR) to the Ordinary Least Squares (OLS) estimator on a synthetic dataset and for one-dimensional regression using polynomial feature expansion.
+Although the examples does not raise a runtime error, the coefficients computed from the fitting for the synthetic dataset are \texttt{Not-A-Number} (NaN) values for both BRR and OLS.
 \pytracer traces reveal that the SVD solver used is the root cause for this error.
-Figure~\ref{fig:brr_svd_sig} shows
-the number of significant bits for the singular values SVD decomposition. 
-For BRR, the SVD is directly called \tristan{from Lapack?} to compute the coefficients, while for the OLS, it is called during the Least-Squares minimization.
-Scikit-learn uses SciPy that itself uses the LAPACK library to compute the SVD \tristan{unclear what is the call path for each solver}.
-The LAPACK library has two main methods for computing the SVD: 
-\texttt{gesdd} and \texttt{gesvd}.
+Figure~\ref{fig:call_path_brr} shows the two call paths for BRR and OLS. 
+We can see that the LAPACK library has two main methods for computing the SVD: \texttt{gesdd} and \texttt{gesvd}.
 The former uses a Divide \& Conquer approach, while the latter uses a QR decomposition. 
-While both methods are expected to have the same accuracy~\cite{nakatsukasa2013stable}, our results show that \texttt{gesdd} is totally imprecise, with an average number of significant digits of \tristan{0?}.
+While both methods are expected to have the same accuracy~\cite{nakatsukasa2013stable}, Figure~\ref{fig:brr_svd_sig} show that \texttt{gesdd} is totally imprecise, with an average number of significant digits of 0 for BRR and even \texttt{NaN} values for OLS.
+On the same figure, we can see that 
+using the \texttt{gesvd} (dgelsd) method instead of the \texttt{gesdd} (dgelss) one, 
+the SVD is converging within the RR and Full MCA modes, with a number of significant bits of 44 on average. 
 This observation supports the on-going discussion among LAPACK developers on the instability of \texttt{gesdd} (see  \href{https://github.com/Reference-LAPACK/lapack/issues/316}{github.com/Reference-LAPACK/lapack/issues/316}).
-For the Least-Square problem, the LAPACK library has three solvers, including \texttt{dgelss} that internally uses \texttt{gesdd} and \texttt{dgelsd} that uses \texttt{gesvd} \tristan{t'es sur que c'est pas l'inverse?
-Sur la fig 9 on voit que dgelsd n'est pas precise du tout, ca suggere qu'elle utiliserait gesdd}.
-Using the \texttt{gesvd} (dgelsd) method instead of the \texttt{gesdd} (dgelss) one, the SVD is converging within the RR and Full MCA modes, with a number of significant bits of 44 on average.
-\tristan{Ce paragraph est difficile a lire (mais neanmoins super interessant !).
-Tu devrais le restructurer en expliquant (1) quelle methode utilise quel solver de quelle librairie, (2) la performance observee sur la fig 9 (tu pourais d'ailleurs ajouter le nom du solver (gesdd ou gesvd) entre parenthese dans la legende pour rendre l'explication plus claire, (3) le fait que ca confirme la discussion sur github et autres commentaires.}
+
+% \tristan{t'es sur que c'est pas l'inverse? Sur la fig 9 on voit que dgelsd n'est pas precise du tout, ca suggere qu'elle utiliserait gesdd}. 
+% \tristan{ce paragraph est difficile a lire (mais neanmoins super interessant !).
+tu devrais le restructurer en expliquant (1) quelle methode utilise quel solver de quelle librairie, (2) la performance observee sur la fig 9 (tu pourais d'ailleurs ajouter le nom du solver (gesdd ou gesvd) entre parenthese dans la legende pour rendre l'explication plus claire, (3) le fait que ca confirme la discussion sur github et autres commentaires.}
 
@@
 
-\paragraph{K-Means Clustering}
-
-This test uses the K-means to cluster the IRIS dataset.
+% \paragraph{K-Means Clustering}
+% This test uses the K-means to cluster the IRIS dataset.
 % The plots display firstly what a K-means algorithm would yield using three clusters.
@@
 
-\paragraph{Covariance estimation}
-
-This example shows covariance estimation with Mahalanobis distances on Gaussian distributed data.
+% \paragraph{Covariance estimation}
+% This example shows covariance estimation with Mahalanobis distances on Gaussian distributed data.
 
@@
 
-\paragraph{Decision Tree Regression}
-
-This test uses a decision tree to fit a sine curve with added noise.
+% \paragraph{Decision Tree Regression}
+% This test uses a decision tree to fit a sine curve with added noise.
 
@@
 
-\paragraph{Digits Classification}
-
-This test uses a Support Vector Classifier to recognize images of hand-written
-digits. The digits dataset consists of 8x8 pixel images of digits.
+% \paragraph{Digits Classification}
+% This test uses a Support Vector Classifier to recognize images of hand-written
+% digits. The digits dataset consists of 8x8 pixel images of digits.
 
@@
 
-The face recognition test uses eigenfaces (eigenvector) and Support Vector Machines (SVMs) to classify faces from the Labeled Faces in the Wild dataset~\cite{LFWTech}.
-This test uses a Principal Component Analysis (PCA) to extract the eigenfaces and then trains an SVM classifier to predict the name associated with a visage.
-This test is the only one to raise an error within RR mode due to a non-convergence of the Singular Value Decomposition (SVD) performed during the PCA.
-In this test, the PCA uses the Randomized SVD~\cite{halko2011finding} variant that first computes a low-rank approximation of the input matrix using a stochastic algorithm and then uses this approximation as the input for the SVD.
-It is during the computation of this SVD that the test raised an error.
-
-Scikit-learn uses SciPy that itself uses the LAPACK library to compute the SVD. The LAPACK library has two main methods for computing the SVD: 
-\texttt{gesdd} and \texttt{gesvd}.
-The first one uses a Divide \& Conquer approach, while the second uses a QR decomposition.
-While both methods expect to have the same accuracy~\cite{nakatsukasa2013stable}, it appears that results diverge in practice with inaccurate results for the Divide \& Conquer method, as the sill opened an issue on the official LAPACK GitHub repository \href{https://github.com/Reference-LAPACK/lapack/issues/316}{github.com/Reference-LAPACK/lapack/issues/316} shows.
-The \texttt{randomized\_svd} scikit-learn function uses the Divide \& Conquer method for the SVD.
-
-Using the  \texttt{gesvd} method instead of the \texttt{gesdd} one, the SVD converges within the RR mode.
-Moreover, figure~\ref{fig:randomized_svd_S} shows the precision of the eigenvalues computed, varying between 15 and 20 bits out of the 24 available in single precision.
-Finally, the classifier metrics (precision, recall, F1-score, and support) are identical to the IEEE execution, meaning that the test is as precise as the original execution.
-
-In conclusion, the MCA model was helpful to detect the instability of the \texttt{gesdd} method that has been notified in several GitHub issues, including the LAPACK repository.
-It is worth mentioning that a Pull Request has recently been submitted to let the user select the SVD method and avoid this kind of issue.
+The face recognition example uses eigenfaces (eigenvectors) and Support Vector Machines (SVMs) to classify faces from the Labeled Faces in the Wild dataset.
+This example uses a Principal Component Analysis (PCA) to extract the eigenfaces and then trains an SVM classifier to predict the name associated with a face.
+This example is the only one to raise an error with RR due to the non-convergence of the Singular Value Decomposition (SVD) performed in the PCA.
+
+In this example, the PCA uses the Randomized SVD~\cite{halko2011finding} method that first computes a low-rank approximation of the input matrix using a stochastic algorithm and then uses this approximation as input for the SVD.
+Unfortunately, the example raises an error during the computation of the SVD.
+The \texttt{randomized\_svd} scikit-learn function uses the Divide \& Conquer SVD method (\texttt{gesdd}, see previous comments). 
+Replacing \texttt{gesdd} for \texttt{gesvd} solves the SVD convergence issue.
+Figure~\ref{fig:randomized_svd_S} shows the precision of the eigenvalues computed with gesvd, which varies between 15 and 20 significant bits out of the 24 available in single precision.
+Finally, the classifier metrics (precision, recall, F1-score, and support) are identical to the IEEE execution for all MCA samples.
+
+In conclusion, Pytracer and the MCA model were helpful to detect the instability of the \texttt{gesdd} method mentioned in several GitHub issues, including the LAPACK repository.
+Furthermore, it is worth mentioning that a Pull Request has recently been submitted to let the user select the SVD method and avoid this kind of issue.
+Thus, we can see that Pytracer can detect instabilities that affect fundamental scientific computing components such as the LAPACK library.
+The Pytracer findings can therefore be extended to many application domains.
+\tristan{conclusion needs to be discussed. Note to self: generaliser un peu la conclusion: pytracer permet de se rendre compte de problemes de stabilite dont plusieurs librairies sont dependantes.}
 
@@
     \end{subfigure}
-    \caption{Number of significant bits of the \texttt{randomized\_svd} function in the 
-    \texttt{face\_recognition} test using the \texttt{gesvd} SVD method within RR mode.
+    \caption{Precision of the \texttt{randomized\_svd} function in the 
+    \texttt{face\_recognition} example using the \texttt{gesvd} SVD method and RR.
     Figures~\ref{fig:randomized_svd_U},~\ref{fig:randomized_svd_S}, and~\ref{fig:randomized_svd_V}
-    show respectively the values $U$, $\Sigma$ and $V.$
-    Using this method makes the \texttt{randomized\_svd} converging contrary to the \texttt{gesdd} method that raised a runtime error. 
+    show respectively the values $U$, $\Sigma$ and $V$.
+     Numerical precision is lower for smaller eigenvalues and this loss of precision translates to eigenvectors.
+It would be interesting to investigate the use of numerical precision for dimensionality reduction.
     }
@@
 
-\paragraph{L1 Penalty}
-
-This test compares the percentage of zero coefficients for logistic regression
-by varying the penalty (L1, L2 and Elastic-Net) and regularization (1, 0.1, 0.01) parameters. 
-A large regularization value gives the model more freedom than a small value, which puts more constraints on the model.
+% \paragraph{L1 Penalty}
+% This test compares the percentage of zero coefficients for logistic regression
+% by varying the penalty (L1, L2 and Elastic-Net) and regularization (1, 0.1, 0.01) parameters. 
+% A large regularization value gives the model more freedom than a small value, which puts more constraints on the model.
 
@@
 
-\paragraph{Lasso and Elastic-Net}
-
-This test compares the Lasso and Elastic-Net regression models
-on a corrupted signal.
+% \paragraph{Lasso and Elastic-Net}
+% This test compares the Lasso and Elastic-Net regression models
+% on a corrupted signal.
 
@@
 
-This test uses a linear Support Vector Machine (SVM) classifier trained using the Stochastic Gradient Descent (SGD) method to find the maximum separating hyperplane in 2D.
-The test trains the SVM with 50 random points separated in 2 clusters with hyperparameters $\alpha=0.01$ and using the hinge loss function.
-Once trained, the test generates a $[-1,5]\times[-1,5]$ Cartesian grid and predicts the class label for each point with integer coordinates.
-Figure~\ref{fig:separating_hyperplan} shows the ratio $\frac{mean}{std}$ with RR mode for each point of the grid (square) and the training dataset (circle), the two colors representing the two classes.
-We can see that white points close to the separating hyperplane are highly unstable with a number of significant bits below 0, meaning that
-the classifier hesitates about the class to predict.
+This example uses a linear Support Vector Machine (SVM) classifier trained using the Stochastic Gradient Descent (SGD) method to find the maximum separating hyperplane between sets of 2D points.
+The example trains the SVM with 50 random points separated in 2 clusters with hyperparameter $\alpha=0.01$ and using the hinge loss function.
+Once the model is trained, the example generates a $[-1,5]\times[-1,5]$ Cartesian grid
+discretized with 100 points and predicts the class label for each point with integer coordinates.
+Figure~\ref{fig:hyperplan_sig_zoom} shows the the number of significant bits %\tristan{isn't it significant bits?} \tristan{aren't the class predctions integers?}
+\Yohan{No its floating point values}1
+obtained with RR for each point of the grid %(squares \tristan{not sure where the squares are}) 
+and the training dataset (circles \tristan{why are some circles larger than other ones?}).
+We can see that yellow points %\tristan{I don't see any white point} 
+close to the separating hyperplane are highly unstable with a number of significant bits below 0, meaning that
+the classifier is unsure about the predicted class. 
+%\tristan{Describe and comment on the other 2 tests, why are they more stable? Is it because the training set has more points?}
 
@@
     \centering
+    % \begin{subfigure}{.3\linewidth}
+    % \includegraphics[width=\linewidth]{figure/separating_hyperplan/hyperplan.png}
+    % \caption{}
+    % \label{fig:hyperplan_sig}
+    % \end{subfigure}
     \begin{subfigure}{.3\linewidth}
-    \includegraphics[width=\linewidth]{figure/separating_hyperplan/hyperplan.png}
-    \caption{}
-    \label{fig:hyperplan_sig}
-    \end{subfigure}
+    \caption{Separating hyperplane}
+    \includegraphics[width=\linewidth]{figure/separating_hyperplan/hyperplane_zoom.pdf}
+    \label{fig:hyperplan_sig_zoom}
+    \end{subfigure} \\
     \begin{subfigure}{.3\linewidth}
-    \includegraphics[width=\linewidth]{figure/SVM/non_weighted.png}
-    \caption{}
+    \caption{SVM (non weighted)}
+    \includegraphics[width=\linewidth]{figure/SVM/non_weighted.pdf}
     \label{fig:SVM_nw_sig}
@@
     \begin{subfigure}{.3\linewidth}
-    \includegraphics[width=\linewidth]{figure/Weighted/non_weighted.png}
-    \caption{}
+    \caption{SVM (weighted)}
+    \includegraphics[width=\linewidth]{figure/SVM/weighted.pdf}
+    \label{fig:SVM_w_sig}
+    \end{subfigure} \\
+    \begin{subfigure}{.3\linewidth}
+    \caption{SGD weighted (non-weighted)}
+    \includegraphics[width=\linewidth]{figure/Weighted/non_weighted.pdf}
     \label{fig:weighted_nw_sig}
@@
     \begin{subfigure}{.3\linewidth}
-    \includegraphics[width=\linewidth]{figure/separating_hyperplan/hyperplan_zoom.png}
-    \caption{}
-    \label{fig:hyperplan_sig_zoom}
-    \end{subfigure}
-    \begin{subfigure}{.3\linewidth}
-    \includegraphics[width=\linewidth]{figure/SVM/weighted.png}
-    \caption{}
-    \label{fig:SVM_w_sig}
-    \end{subfigure}
-    \begin{subfigure}{.3\linewidth}
-    \includegraphics[width=\linewidth]{figure/Weighted/weighted.png}
-    \caption{}
+    \caption{SGD weighted (weighted)}
+    \includegraphics[width=\linewidth]{figure/Weighted/weighted.pdf}
     \label{fig:weighted_w_sig}
     \end{subfigure}
-    \caption{Three examples of separating hyperplane tests.
-All figures show the number of significant bits of the results for the following tests: \textit{Separating Hyperplane} on figures.~\ref{fig:hyperplan_sig} for the original colormap and~\ref{fig:hyperplan_sig_zoom} with a rescaled colormap.
-We can see that this test exhibits a poor precision with less than 3 bits significant, although only the sign of the number matter to predict on which side of the hyperplane the point is classified.
-We can see in figure~\ref{fig:hyperplan_sig_zoom} by rescaling the colormap that the instabilities are concentrated around the hyperplane.
-    Figures~\ref{fig:SVM_nw_sig},~\ref{fig:SVM_w_sig},~\ref{fig:weighted_nw_sig}, and~\ref{fig:weighted_w_sig} show respectively the results of tests    \textit{SVM} and~\textit{Weighted samples}.
-Figures~\ref{fig:SVM_nw_sig} and~\ref{fig:weighted_nw_sig} show the unweighted classification while figures~\ref{fig:SVM_w_sig} and~\ref{fig:weighted_nw_sig} the classification taking into account the weights.
-We can see that taking into account the weight classes allows a better separating.}
-\label{fig:my_label}
+    \caption{
+    These figures show three examples of separating hyperplane prediction.
+First, all figures show the number of significant bits of the prediction within RR mode.
+Second, we can see that the separating hyperplane is visible on each figure without plotting since it corresponds to a lower precision area.
+Indeed, the classifier has difficulty predicting which side the predicted point is on.
+Moreover, a large discretization step amplifies
+    this instability, as Figure~\ref{fig:separating_hyperplan} shows.
+Finally, Figures~\ref{fig:SVM_w_sig} and~\ref{fig:weighted_w_sig} show that taking into account the unbalancing or the weight of points allows for a better separating than ~\ref{fig:SVM_nw_sig} and ~\ref{fig:weighted_nw_sig}.
+% respectively the results of examples    \textit{SVM} and~\textit{Weighted samples}.
+Figures~\ref{fig:SVM_nw_sig} and~\ref{fig:weighted_nw_sig} show the unweighted classification while Figures~\ref{fig:SVM_w_sig} and~\ref{fig:weighted_nw_sig} the classification taking into account the weights.
+We can see that taking into account the weight classes allows a better separation.
+    % \tristan{add labels to subfigures} \tristan{don't use this yellow for class 1, take a color that isn't in the color map. Add a legend to show the class colors.}
+    }
+\label{fig:separating_hyperplan}
 \end{figure}
 
-\paragraph{MNIST classification}
-
-This test fits a logistic regression with the SAGA solver with the L1 penalty on the MNIST digits classification task subset.
+% \paragraph{MNIST classification}
+% This test fits a logistic regression with the SAGA solver with the L1 penalty on the MNIST digits classification task subset.
 
@@
 
-\paragraph{Multitask Lasso}
-
-This test compares the Lasso and MultiTaskLasso regression models
-on a corrupted signal.
+% \paragraph{Multitask Lasso}
+% This test compares the Lasso and MultiTaskLasso regression models
+% on a corrupted signal.
 
@@
 
-\paragraph{Orthogonal matching}
-
-This test uses the Orthogonal Matching Pursuit algorithm
-for recovering a sparse signal from a noisy measurement encoded with a dictionary.
+% \paragraph{Orthogonal matching}
+% This test uses the Orthogonal Matching Pursuit algorithm
+% for recovering a sparse signal from a noisy measurement encoded with a dictionary.
 
@@
 
-\paragraph{PCA decomposition}
-
-This test makes a PCA decomposition on a synthetic dataset.
+% \paragraph{PCA decomposition}
+% This test makes a PCA decomposition on a synthetic dataset.
 % These figures aid in illustrating how a point cloud can be very flat in one direction–which is where PCA comes in to choose a direction that is not flat.
@@
 
-\paragraph{Robust Linear Regression}
-
-This test compares the linear and  RANSAC regression methods on noisy data.
+% \paragraph{Robust Linear Regression}
+% This test compares the linear and  RANSAC regression methods on noisy data.
 % In this example we see how to robustly fit a linear model to faulty data using the RANSAC algorithm.
@@
 
-\paragraph{Segmentation Toy}
-
-This test uses spectral clustering to separate connected circles in an image.
+% \paragraph{Segmentation Toy}
+% This test uses spectral clustering to separate connected circles in an image.
 
@@
 \paragraph{SVM}
-
-This test uses a plain and weighted classes SVC to find the best hyperplane separating an unbalanced dataset.
-
+This example uses a plain Support Vector Classification~\cite{Platt99probabilisticoutputs} (SVC) 
+to find the best hyperplane separating an unbalanced dataset with two classes of 1000 and 100 points.
+This example tests two SVC configurations using a linear kernel with and without a class weight parameter.
+The SVC predicts the class label for each coordinate over a $[-5,5] \times [-5,5]$ grid discretized
+with 900 points.
+Figures~\ref{fig:SVM_nw_sig} and~\ref{fig:SVM_w_sig} show the result within RR of the classification with
+and without taking into account the unbalancing.
+We can see that the number of significant bits is lower on the separating line and
+that taking into account the unbalancing allows a better separation.
 % Find the optimal separating hyperplane using an SVC for classes that are unbalanced.
@@
 
-\paragraph{Tomography}
-
-This test compares the LASSO and Ridge regression models to 
-reconstruct an image from  projections for a dataset
-acquired from computed tomography.
+% \paragraph{Tomography}
+% This test compares the LASSO and Ridge regression models to 
+% reconstruct an image from  projections for a dataset
+% acquired from computed tomography.
 
@@
 
-\paragraph{Weighted samples}
-
-This test uses an SGD to separate weighted points by 
-taking into account or not the weights.
+\paragraph{SGD weighted samples}
+This example uses an SGD to separate weighted points by taking into account or not the weights.
+It divides the training set into two classes of 10 points with a bigger weight for the second class.
+The SGD is trained with hyperparameters $\alpha=0.01$ and a maximum number of iterations to 100.
+The prediction is made on a $[-4,5]\times[-4,5]$ grid discretized with 250000 points.
+Figures~\ref{fig:weighted_nw_sig} and~\ref{fig:weighted_w_sig} show the number of significant bits
+of prediction within RR along with dataset points in blue and violet.
+We can see that the separating plane is visible without plotting it since it corresponds to the yellow line of lower precision.
+As for the examples SVM and Separating hyperplane, the numerical instabilities are concentrated around the separation since the classifier cannot predict from which side points are placed.
+Finally, taking into account the points' weight allows for a better separating.
 
@@
 
-\section{Performance evaluation}
-
-This section reviews the performance overhead of the Pytracer's instrumentation cost and the time spent during the postprocessing analysis.
-
-\subsection{Tracing}
-
-Pytracer instrumentation overhead comes from the time spent on instrument module (initialization overhead)
-before executing the targeted application plus the cost for dumping the data during the execution (running overhead).
+\subsection{Overhead evaluation}
+\pytracer's tracing overhead consists of (1) module instrumentation time (initialization overhead) and (2) data write time during the execution (runtime overhead).
 The initialization overhead is proportional to the number of functions and classes traced.
-However, initialization overhead is amortized when traced applications are above 8 seconds,  proportional to 
-the number of functions and classes traced.
-Table~\ref{tab:pytracer_overhead} summaries the slowdown measure on SciPy
-and scikit-learn tests.
-We can see that Pytracer gives slowdowns of $\times 17$ and
-$\times 3.5$ if we subtract the initialization step.
-Furthermore, we obtain an average slowdown of $\times 37$ for RR mode and $\times 43$ for Full MCA by adding fuzzy.
+For example, by instrumenting NumPy, SciPy, and Scikit-learn, we measured an average initialization time of 8 seconds during our experiments.
+Hence, the initialization overhead is amortized when traced applications are above 8 seconds.
+Moreover, one can reduce this overhead by excluding intensively used functions such as \texttt{numpy.array}.
+Figure~\ref{fig:performance_tracing} summaries \pytracer's tracing overhead for SciPy and scikit-learn examples.
+We can see that \pytracer introduces a slowdown of $17\times$ reduced to $3.5\times$ if we subtract the initialization step.
+Finally, the fuzzy instrumentation increases the slowdown to  $37\times$ for RR and $43\times$ for Full MCA.
+
+% \pytracer's tracing overhead consists of (1) module instrumentation time (initialization overhead), and (2) data write time during the execution (runtime overhead).
+The initialization overhead is proportional to the number of functions and classes traced.
+However, the initialization overhead is amortized \tristan{what do you mean by amortized?
+I don't get this sentence} when traced applications are above 8 seconds,  proportional to
+% the number of functions and classes traced.
+Figure~\ref{fig:performance_tracing} summaries \pytracer's tracing overhead for SciPy and scikit-learn examples.
+We can see that \pytracer introduces a slowdown of reduced toif we subtract the initialization step
+% \tristan{not sure where to get these numbers from the table, to be clarified. Are these average values? Why are there two values?}. 
+% Fuzzy instrumentation increases the slowdown to for RR and   for Full MCA.
+% \tristan{Figure 13 is not referred in the text. Choose between the figure and the table, no need to put both.}
 
@@
     \pytracer tracing overheads: \textit{Slowdown} is the actual overhead, computed as the ratio between the execution time without and with \pytracer.
-This slowdown can be high for the tests running less than 8 seconds because \pytracer spends most of its time in the initialization step.
+This slowdown can be high for the examples running less than 8 seconds because \pytracer spends most of its time in the initialization step.
 Since this step is a constant factor of the number of functions instrumented, we also plot the slowdown of the instrumentation itself (\textit{Slowdown (Instrumentation)} calculated by subtracting the initialization time.
@@
     using the fuzzy environment with RR and Full MCA modes.
-    The first four tests measure the initialization steps depending on the modules instrumented. \tristan{you could make a horizontal chart to avoid rotating the labels (also in F  ig 13)}
+    The first four examples measure the initialization steps depending on the modules instrumented. \tristan{you could make a horizontal chart to avoid rotating the labels (also in Fig 13)}
     }
-    \label{fig:performances}
+    \label{fig:performance_tracing}
 \end{figure}
+
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=\linewidth]{figure/parsing_time.pdf}
+%     \caption{\pytracer time to aggregate traces.}
+%     \label{fig:performance_parsing_time}
+% \end{figure}
+
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=\linewidth]{figure/parsing.pdf}
+%     \caption{\pytracer trace and aggregation files size.
+%     The figure presents the size measured for the trace and the aggregation size files.}
+%     \label{fig:performance_parsing_size}
+% \end{figure}
 
@@
     \centering
-    \includegraphics[width=\linewidth]{figure/parsing_time.pdf}
-    \caption{\pytracer time to aggregate traces.}
-    \label{fig:performance_parsing_time}
+    \includegraphics[width=\linewidth]{performance_parsing.pdf}
+    \caption{\pytracer aggregation performance. The figure presents
+    the aggregation time (X-axis) versus the trace size (Y-axis).
+    We can see that the aggregation time is proportional to the trace size.}
+    \label{fig:performance_parsing}
 \end{figure}
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figure/parsing.pdf}
-    \caption{\pytracer trace and aggregation files size.
-    The figure presents the size measured for the trace and the aggregation size files.}
-    \label{fig:performance_parsing_size}
-\end{figure}
-
-\begin{table}
-\centering
-\begin{subfigure}[t]{.75\linewidth}
-    \centering
-    \begin{tabular}{|l|c|c|c|c|}
-    \hline 
-    Application & Original & Pytracer only & RR & MCA \\
-    \hline 
-    Loading & 0.456 & 8.152 & - & - \\
-    \hline
-    discrete\_cosine\_transform & 0.280 & 8.176 & 10.203 & - \\ 
-    fft\_1D & 0.650 & 9.075 & 11.345 & - \\
-    fft\_2D & 0.311 & 9.500 & 11.929  & 16.433   \\
-    \hline
-    interpolation\_1D & 0.377 & 8.803  & 11.954  & -   \\
-    multivariate\_data &0.626 & 8.648 &  12.711  & - \\
-    bspline & 0.109  & 9.050 & 13.396  & 16.830   \\
-    spline\_1D & 0.111 & 8.618 & 10.960   & - \\
-    spline\_2D & 0.655 & 8.649 & 19.424  & - \\
-    \hline
-    broyden\_fletcher\_goldfarb\_shanno &0.475 & 8.292 & 11.033 & 13.685 \\
-    global\_optimization &1.257 & 55.916  & 93.322  & - \\
-    slsqp & 0.469 & 8.192 & 10.795 & 12.439  \\
-    least\_square\_minimization & 0.505 & 10.151  & 13.888 & -  \\
-    nelder\_mead\_simplex & 0.471 & 8.418  & 11.382  & 12.792  \\
-    newton\_conjugate\_gradient & 0.487 & 8.548  & 11.956  & 14.281 \\
-    root\_findings & 0.462 & 8.198  & 10.787   & - \\
-    root\_finding\_large & 0.801 & 11.525 & 41.493   &  82.701  \\
-    root\_finding\_large\_preconditioned & 0.702 & 10.580 & 33.199   & 57.579  \\
-    trust\_region\_exact & 0.482 & 8.170 & 10.400  & 12.524 \\
-    trust\_region\_truncated\_generalized\_lanczos & 0.459 & 8.457 & 11.216 & 13.245  \\
-    trust\_region\_newton\_conjugate\_gradient & 0.479 & 8.538 & 11.179 & 13.488 \\
-    \hline
-    Adaboost &1.388 &14.553 &  20.999 & - \\
-    Bayesian Ridge Regression & 1.086 & 10.344 & 90.299 & -  \\
-    Online classifier comparison & 15.964 & 72.691 & 2104.114 & -  \\
-    K-Means Clustering & 1.621 & 17.614  & 34.005 & 52.902   \\
-    Covariance estimation & 1.357 & 11.755 & 23.964  & -   \\
-    Decision Tree Regression & 1.185 & 11.194 & 15.760 & 15.918  \\
-    Digits Classification & 1.672 & 12.725 & 40.634 & - \\
-    Face Recognition & 32.159  & 74.356 & - & - \\
-    L1 Penalty & 1.568 & 12.591 & 65.547 & 128.220 \\
-    Lasso and elastic net & 1.057 & 9.903 & 17.078 & -  \\
-    Separating hyperplan & 1.376 & 11.532  & 22.333 & 25.036 \\
-    MNIST classification & 19.650 & 37.838 & 402.389  & - \\
-    Multitask Lasso & 1.090 &10.196 & 15.025  & - \\
-    Orthogonal matching & 1.161 & 12.129 & 21.779   & 31.135 \\
-    PCA decomposition & 1.239 & 10.642 & 15.520 & 17.952    \\
-    Robust Linear Regression & 1.370 & 11.144  & 14.280  & - \\
-    Segmentation toy &1.679 & 22.385 & 87.811  & - \\
-    SVM & 1.403 & 11.737 & 23.203 & 24.126   \\
-    Tomography & 11.108 & 40.177  & 1376.134 & -  \\
-    Weighted samples & 1.358 & 11.768 & 21.255 & 20.541   \\
-    \hline
-    \end{tabular}
-\end{subfigure}
-    \caption{\pytracer tracing performances.}
-    \label{tab:pytracer_overhead}
-\end{table}
+% \begin{table}
+% \centering
+% \begin{subfigure}[t]{.75\linewidth}
+%     \centering
+%     \begin{tabular}{|l|c|c|c|c|}
+%     \hline 
+%     Application & Original & Pytracer only & RR & MCA \\
+%     \hline 
+%     Loading & 0.456 & 8.152 & - & - \\
+%     \hline
+%     discrete\_cosine\_transform & 0.280 & 8.176 & 10.203 & - \\ 
+%     fft\_1D & 0.650 & 9.075 & 11.345 & - \\
+%     fft\_2D & 0.311 & 9.500 & 11.929  & 16.433   \\
+%     \hline
+%     interpolation\_1D & 0.377 & 8.803  & 11.954  & -   \\
+%     multivariate\_data &0.626 & 8.648 &  12.711  & - \\
+%     bspline & 0.109  & 9.050 & 13.396  & 16.830   \\
+%     spline\_1D & 0.111 & 8.618 & 10.960   & - \\
+%     spline\_2D & 0.655 & 8.649 & 19.424  & - \\
+%     \hline
+%     broyden\_fletcher\_goldfarb\_shanno &0.475 & 8.292 & 11.033 & 13.685 \\
+%     global\_optimization &1.257 & 55.916  & 93.322  & - \\
+%     slsqp & 0.469 & 8.192 & 10.795 & 12.439  \\
+%     least\_square\_minimization & 0.505 & 10.151  & 13.888 & -  \\
+%     nelder\_mead\_simplex & 0.471 & 8.418  & 11.382  & 12.792  \\
+%     newton\_conjugate\_gradient & 0.487 & 8.548  & 11.956  & 14.281 \\
+%     root\_findings & 0.462 & 8.198  & 10.787   & - \\
+%     root\_finding\_large & 0.801 & 11.525 & 41.493   &  82.701  \\
+%     root\_finding\_large\_preconditioned & 0.702 & 10.580 & 33.199   & 57.579  \\
+%     trust\_region\_exact & 0.482 & 8.170 & 10.400  & 12.524 \\
+%     trust\_region\_truncated\_generalized\_lanczos & 0.459 & 8.457 & 11.216 & 13.245  \\
+%     trust\_region\_newton\_conjugate\_gradient & 0.479 & 8.538 & 11.179 & 13.488 \\
+%     \hline
+%     Adaboost &1.388 &14.553 &  20.999 & - \\
+%     Bayesian Ridge Regression & 1.086 & 10.344 & 90.299 & -  \\
+%     Online classifier comparison & 15.964 & 72.691 & 2104.114 & -  \\
+%     K-Means Clustering & 1.621 & 17.614  & 34.005 & 52.902   \\
+%     Covariance estimation & 1.357 & 11.755 & 23.964  & -   \\
+%     Decision Tree Regression & 1.185 & 11.194 & 15.760 & 15.918  \\
+%     Digits Classification & 1.672 & 12.725 & 40.634 & - \\
+%     Face Recognition & 32.159  & 74.356 & - & - \\
+%     L1 Penalty & 1.568 & 12.591 & 65.547 & 128.220 \\
+%     Lasso and elastic net & 1.057 & 9.903 & 17.078 & -  \\
+%     Separating hyperplan & 1.376 & 11.532  & 22.333 & 25.036 \\
+%     MNIST classification & 19.650 & 37.838 & 402.389  & - \\
+%     Multitask Lasso & 1.090 &10.196 & 15.025  & - \\
+%     Orthogonal matching & 1.161 & 12.129 & 21.779   & 31.135 \\
+%     PCA decomposition & 1.239 & 10.642 & 15.520 & 17.952    \\
+%     Robust Linear Regression & 1.370 & 11.144  & 14.280  & - \\
+%     Segmentation toy &1.679 & 22.385 & 87.811  & - \\
+%     SVM & 1.403 & 11.737 & 23.203 & 24.126   \\
+%     Tomography & 11.108 & 40.177  & 1376.134 & -  \\
+%     Weighted samples & 1.358 & 11.768 & 21.255 & 20.541   \\
+%     \hline
+%     \end{tabular}
+% \end{subfigure}
+%     \caption{\pytracer tracing overhead in seconds. \tristan{what is the unit in this table?}}
+%     \label{tab:pytracer_overhead}
+% \end{table}
 
@@
 
-\subsection{Postprocessing}
-
-The figures~\ref{fig:performance_parsing_time} and~\ref{fig:performance_parsing_size} show
-the postprocessing time and trace's sizes produced by \pytracer.
-We only report time for parsing and aggregation that have been successful.
-We measure a throughput of 7MB/s by taking the ratio size over time.
+Moreover, \pytracer's trace aggregation introduces to a post-processing overhead.
+Figure~\ref{fig:performance_parsing} shows
+the postprocessing time and trace sizes produced by \pytracer.
+In conclusion, the small overhead introduced by Pytracer allows one to analyze real-life applications.
+
+\tristan{A scatter plot with x=size and y=time might be easier to read.}
+\tristan{Add a conclusion comment about the overhead}
 
@@
 
-\pytracer is a tool for visualizing the numerical quality of function inputs/outputs over time.
+% Numpy   2509 (2403 not tests) (1848) functions, 1196 (1154) (817) classes (pure Python)
+% Scipy   4031 (2187) (506) functions, 1532 (472) (109) classes (pure Python)
+% Sklearn 4807 (1010) (81) functions, 546 (417) (41) classes (pure Python)
+
+\tristan{The next paragraphs read like nobody should use \pytracer ever because it's full of issues.
+Rewrite this section to explain why \pytracer is important, what it could be used for, what it brings to current context.
+We can discuss these points if you want.
+If you want to talk about limitations, formulate them as future work, not "pitfalls" or "problems".}
+
+Pytracer is a tool for visualizing the numerical quality of function inputs/outputs over time.
 It generates numerical traces that are aggregated in postprocessing to measure numerical discrepancies between executions.
-\pytracer does not assume the noise model used to estimate uncertainties but has been tested with the MCA 
+Pytracer does not assume the noise model used to estimate uncertainties, but we tested it with the MCA model
 through the fuzzy ecosystem on two broadly used scientific libraries for Python with partial success.
 
-As we showed in section~\ref{sec:impact_mca_modes}, using the Full MCA mode leads to runtime errors that have a considerable impact on the proper functioning of the execution, which is unfortunate since these
-errors do not reflect actual numerical errors but errors related to perturbations that should not occur.
+We demonstrated the \pytracer's capabilities to analyze intensively used Python libraries such as NumPy or Scikit-learn, such as 1) Scalability.
+The low instrumentation overhead of 3.5x enables analysis of real applications and permits having a global representation of the numerical quality of an application.
+2) Automaticity.
+\pytracer instrumentation is fully automatic and does not require manual intervention from the user, allowing the instrumentation of the NumPy, SciPy, and Scikit-learn libraries.
+3) Agnosticism. \pytracer works on any python libraries, with any data format supported by Pickle and any numerical noise model flavor.
+
+\pytracer is the first tool to bring the numerical analysis of Python codes available to everyone.
+Indeed, existing tools developed in the last years focused on traditional languages of the HPC community such as C, C++, and FORTRAN.
+However, the Python high-level abstraction allows for quickly developing applications while maintaining high performance with the help of specialized libraries like NumPy.
+Therefore, it is quite natural to see more fields systematically using Python, as in neuroimaging.
+Thus, \pytracer meets the numerical analysis needs of an ever-increasing number of applications writing in Python.
+Furthermore, \pytracer allows users to pinpoint numerical instabilities root causes precisely by working at the function level.
+Furthermore, the automaticity facilitates the usage and its integration in unit testing, for example.
+Hence, instead of tweaking hyperparameters to make solvers converge, the user has a practical way with \pytracer to quantify the numerical quality of its computations.
+Furthermore, the visualization permits a global view of the code and easily navigate through it.
+Moreover, it removes the need for ad-hoc scripts to visualize data.
+\pytracer currently supports n-dimensional NumPy arrays as well as native Python data.
+We want to extend \pytracer to support other formats such as 4D brain images in future works.
+
+As we showed in section~\ref{sec:impact_mca_modes}, using the Full MCA mode leads to runtime errors that have a considerable impact on the proper functioning of the execution, which is unfortunate since these errors do not reflect actual numerical errors but errors related to perturbations that should not occur.
 Fixing this misbehavior would greatly help use Full MCA mode since this mode allows simulating catastrophic cancellations, which are familiar sources of numerical errors.
-By preserving exact operations, RR mode is far more conservative and so easy to use even though it does not simulate all perturbations that might be encountered.
-
-Also, using a post-process analysis to aggregate traces, \pytracer falls in the same pitfalls as veritracer and is limited to aggregate traces where the execution flow path extremely diverges.
-Therefore, a posteriori reconstruction
-is challenging as one must precisely identify the flow path taken and find synchronization points to pursue the analysis.
-We retrieve, for example, this divergence behavior in two general classes of numerical schemes: iterative methods and optimization processes.
-One solution to overcome this issue is to integrate methods used in code coverage analysis to keep track of flow paths taken and the backtraces.
-However, this would increase the complexity of the postprocess analysis as well as an extra slowdown factor.
-However, by coupling the Gantt chart with static analysis, \pytracer would catch some divergence patterns occurring within a function.
-Indeed, by instrumenting at the function level, \pytracer views the function's callees (i.e., the functions called within a function) and thus should partially detect flow divergences.
-
-By design principle, \pytracer is flexible on the noise model used, although we only test it with the MCA model in our experiments.
-Nevertheless, we would like to compare different models against MCA in future works to see the resulting differences. 
-In particular, although \pytracer only works on a sequential application for the moment, it can be used to analyze parallel sections internal to a function.
-The only restriction is that the section does not call other functions traced by \pytracer; we would fall into the previous issue of divergence if it would not be the case.
-Since \pytracer only cares about inputs and outputs of a function, the order of internal operations is transparent for it and thus should be able to handle those cases.
-
-Finally, \pytracer does not instrument elementary arithmetic operations, and it can be a barrier to more profound analysis.
-However, we believe that instrumentation at the function level presents two advantages: it first limits the size of the traces since only inputs and outputs of a function are dumped instead of a full report which, on the one hand, decrease the overhead of the instrumentation and, on the other hand, help the user to identify instabilities quickly.
-One of the pitfalls can be overwhelming the user with too much information, making analysis more difficult.
-Nevertheless, the analysis at fine granularity can be interesting at the final step of the understanding.
-Such an analysis would require a different instrumentation approach by, for example, working at the Abstract Syntax Tree (AST) level since it is trivial to get it in Python.
-An ideal way to do that would be to extract and replay a function, in the same vein as the CERE~\cite{castro2015cere} tool does but for Python, and use an AST instrumentation to analyze the numerical quality of elementary operations step by step within the fuzzy environment.
-Lastly, AST analysis can serve as a basis for finding relationships between variables, valuable information for the user.
-
-In addition to the runtime errors it raises, mismatching shapes is also a problem when aggregating traces as PyTracer will not compute statistics for a set of arrays with different shapes.
+On the other hand, RR mode is far more conservative since it preserves exact operations and is easier to use even though it does not simulate all perturbations.
+In addition to the runtime errors it raises, mismatching shapes is also a problem when aggregating traces as \pytracer will not compute statistics for a set of arrays with different shapes.
 Two solutions exist to overcome this issue: the first is not to instrument the \texttt{PyArray\_Arange} function with MCA.
 The advantage is that it is easy to set up since it requires one extra line in the exclusion file.
-However, the same kind of problem may appear somewhere else
-because, as we have seen, the operations being evolved are elementary.
+However, the same kind of problem may appear somewhere else because, as we have seen, the evolved operations are elementary.
 Therefore, the chances that developers reproduce the same pattern are very probable.
-The second solution is to ensure that the Full MCA mode preserves the exact operations.
+Therefore, the second solution is to ensure that the Full MCA mode preserves the exact operations.
 This solution has the advantage of not worrying about which functions should be instrumented or not with MCA, but it is hard to achieve it in practice.
@@
 Keeping track of that noise would require recording each intermediate computation in a shadow memory or keeping a tag about their exactness.
-\Yohan{This idea emerged by discussing with Verificarlo's team. 
-I must find a way to express that and not give the impression that we discovered or suggest it.}
 This option would require more extra works than the first one but would ensure more consistent results.
+
+Also, we would like to extend the post-process analysis to aggregate traces where the execution flow path diverges.
+Therefore, a posteriori reconstruction is challenging as one must precisely identify the flow path taken and find synchronization points to pursue the analysis.
+We retrieve, for example, this divergence behavior in two general classes of numerical schemes: iterative methods and optimization processes.
+One solution is to integrate methods used in code coverage analysis to keep track of flow paths taken and the backtraces.
+However, this would increase the complexity of the postprocess analysis as well as an extra slowdown factor.
+However, by coupling the Gantt chart with static analysis, \pytracer would catch some divergence patterns occurring within a function.
+Indeed, by instrumenting at the function level, \pytracer views the function's callees (i.e., the functions called within a function) and thus should partially detect flow divergences.
+
+By design principle, \pytracer is flexible on the noise model used, although we only tested it with the MCA model in our experiments.
+Nevertheless, we would like to compare different models against MCA in future works to see the resulting differences.
+Furthermore, we would like to test \pytracer on parallel codes.
+
+Finally, we would extend \pytracer to instrument elementary arithmetic operations which can be helpful to more profound analyses.
+We nevertheless believe that instrumentation at the function level presents two advantages: it first limits the size of the traces since only inputs and outputs of a function are dumped instead of a full report which, on the one hand, decreases the overhead of the instrumentation and, on the other hand, help the user to identify instabilities quickly.
+Indeed, full reporting can overwhelm the user with too much information, making analysis more difficult at first.
+Second, the analysis at fine granularity is interesting at the final step of the understanding.
+Such an analysis would require a different instrumentation approach by, for example, working at the Abstract Syntax Tree (AST) level since it is trivial to get it in Python.
+Moreover, working at the AST level allows doing dependency analysis.
+Another extension would be to extract and replay a function, in the same vein as the CERE tool does but for Python, and to use an AST instrumentation to analyze the numerical quality of elementary operations step by step within the fuzzy environment.
+
+% \pytracer is a tool for visualizing the numerical quality of function inputs/outputs over time.
+% It generates numerical traces that are aggregated in postprocessing to measure numerical discrepancies between executions.
+% \pytracer does not assume the noise model used to estimate uncertainties but has been tested with the MCA 
+% through the fuzzy ecosystem on two broadly used scientific libraries for Python with partial success.
+
+% We demonstrated the Pytracer's capabilities to analyze intensively used Python libraries such as NumPy or Scikit-learn, such as 
+% 1) Scalability. The low instrumentation overhead of 3.5x enables analysis of real applications and permits having a global representation of the numerical quality of an application. 
+% 2) Automaticity. Pytracer instrumentation is fully automatic and does not require manual intervention from the user, allowing the instrumentation of 
+% the NumPy, SciPy and Scikit-learn libraries.
+% // that cumulate 5600 and 2043 pure Python functions and classes. 
+% 3) Agnosticity. Pytracer works on any python libraries, with any data format supported by pickle, and any numerical noise model flavor.
+
+% Pytracer is the first tool to bring numerical analysis of Python codes available to everyone.
+Indeed, existing tools developed in the last years focused on traditional HPC languages community such as C,C++, and FORTRAN.
+However, the Python high-level abstraction allows you to quickly develop applications while maintaining high performance with the help of specialized libraries like NumPy.
+Therefore, it is quite natural to see more fields systematically using Python, as is the case in neuroimaging.
+Thus, Pytracer meets the numerical analysis needs of an ever increasing number of applications writing in Python.
+
+% By working at function level, Pytracer allows users to precisely pinpoint numerical instabilities root causes.
+Furthermore, the automaticity facilitates the usage and its integration in unit testing.
+Hence, instead of tweaking hyperparameters to make solvers converging, the user has a practical way with Pytracer to quantify the numerical quality of its computations.
+
+% As we showed in section~\ref{sec:impact_mca_modes}, using the Full MCA mode leads to runtime errors that have a considerable impact on the proper functioning of the execution, which is unfortunate since these
+% errors do not reflect actual numerical errors but errors related to perturbations that should not occur.
+% Fixing this misbehavior would greatly help use Full MCA mode since this mode allows simulating catastrophic cancellations, which are familiar sources of numerical errors.
+By preserving exact operations, RR mode is far more conservative and so easy to use even though it does not simulate all perturbations that might be encountered.
+
+% Also, using a post-process analysis to aggregate traces, \pytracer falls in the same pitfalls as veritracer and is limited to aggregate traces where the execution flow path extremely diverges.
+Therefore, a posteriori reconstruction
+% is challenging as one must precisely identify the flow path taken and find synchronization points to pursue the analysis.
+We retrieve, for example, this divergence behavior in two general classes of numerical schemes: iterative methods and optimization processes.
+One solution to overcome this issue is to integrate methods used in code coverage analysis to keep track of flow paths taken and the backtraces.
+% However, this would increase the complexity of the postprocess analysis as well as an extra slowdown factor.
+% However, by coupling the Gantt chart with static analysis, \pytracer would catch some divergence patterns occurring within a function.
+Indeed, by instrumenting at the function level, \pytracer views the function's callees (i.e., the functions called within a function) and thus should partially detect flow divergences.
+
+% By design principle, \pytracer is flexible on the noise model used, although we only tested it with the MCA model in our experiments.
+% Nevertheless, we would like to compare different models against MCA in future works to see the resulting differences. 
+% In particular, although \pytracer only works on a sequential application for the moment, it can be used to analyze parallel sections internal to a function.
+% The only restriction is that the section does not call other functions traced by \pytracer; we would fall into the previous issue of divergence if it would not be the case.
+% Since \pytracer only cares about inputs and outputs of a function, the order of internal operations is transparent for it and thus should be able to handle those cases.
+
+% Finally, \pytracer does not instrument elementary arithmetic operations, and it can be a barrier to more profound analysis.
+% However, we believe that instrumentation at the function level presents two advantages: it first limits the size of the traces since only inputs and outputs of a function are dumped instead of a full report which, on the one hand, decrease the overhead of the instrumentation and, on the other hand, help the user to identify instabilities quickly.
+One of the pitfalls can be overwhelming the user with too much information, making analysis more difficult.
+Nevertheless, the analysis at fine granularity can be interesting at the final step of the understanding.
+Such an analysis would require a different instrumentation approach by, for example, working at the Abstract Syntax Tree (AST) level since it is trivial to get it in Python.
+% An ideal way to do that would be to extract and replay a function, in the same vein as the CERE~\cite{castro2015cere} tool does but for Python, and use an AST instrumentation to analyze the numerical quality of elementary operations step by step within the fuzzy environment.
+% Lastly, AST analysis can serve as a basis for finding relationships between variables, valuable information for the user.
+
+% In addition to the runtime errors it raises, mismatching shapes is also a problem when aggregating traces as PyTracer will not compute statistics for a set of arrays with different shapes.
+% Two solutions exist to overcome this issue: the first is not to instrument the \texttt{PyArray\_Arange} function with MCA.
+The advantage is that it is easy to set up since it requires one extra line in the exclusion file.
+% However, the same kind of problem may appear somewhere else
+% because, as we have seen, the operations being evolved are elementary.
+Therefore, the chances that developers reproduce the same pattern are very probable.
+The second solution is to ensure that the Full MCA mode preserves the exact operations.
+% This solution has the advantage of not worrying about which functions should be instrumented or not with MCA, but it is hard to achieve it in practice.
+Indeed, we rely on the MCA implementation provided by Verificarlo that uses an internal precision to add the random perturbation that is higher than the working precision for applying the random noise.
+Verificarlo then rounds the result to the working precision before returning it, so any residual noise lower than the working precision is lost.
+% Keeping track of that noise would require recording each intermediate computation in a shadow memory or keeping a tag about their exactness.
+% \Yohan{This idea emerged by discussing with Verificarlo's team. 
+% I must find a way to express that and not give the impression that we discovered or suggest it.}
+% This option would require more extra works than the first one but would ensure more consistent results.
 
@@
 
-\pytracer is the first tool to propose a complete framework
+\pytracer is the first tool to offer a complete framework
 for analyzing and visualizing the numerical stability of Python codes.
 It works by automatically instrumenting Python libraries to produce numerical
-traces interactively visualized through a Dash server.
-\pytracer does not require manual intervention from the user either rely on
-specific libraries and has been tested successfully on 
-intensively used on scientific libraries such as NumPy, SciPy, and Scikit-learn.
-We demonstrated on a set of representative tests that \pytracer is scalable with an average instrumentation slowdown of $times 3.5$, and that it can handle traces up to 1TB while offering a fluent visualization to the user.
+traces visualized through an interactive Plotly Dash server.
+\pytracer does not require manual code modification, and has been tested  with 
+major scientific libraries such as NumPy, SciPy, and Scikit-learn.
+Our results show that \pytracer is scalable, with an average instrumentation slowdown of $3.5\times$.
+\pytracer's visualization interface remains responsive even with traces of up to 1TB.
 Moreover,
 \pytracer is by construction agnostic to the noise model used 
-to evaluate the numerical stability. Finally, we have demonstrated 
+to evaluate the numerical stability. We have demonstrated 
 that \pytracer can be used with the Monte Carlo Arithmetic 
@@
 We also have to provide feedback about pitfalls and benefits encountered to shed light on first-time users' good and bad practices and democratize MCA's usage. 
-\pytracer is available at \href{https://github.com/yohanchatelain/pytracer}{github://yohanchatelain/pytracer} under an open source license.
+\pytracer is available at \href{https://github.com/big-data-lab-team/pytracer}{github://big-data-lab-team/pytracer} under MIT License.
 

### 2021-11-30 paper.tex
Update the discussion section

@@
 \usepackage{hyperref}
-\hypersetup{colorlinks=true,linkcolor=black,citecolor=blue,filecolor=black,urlcolor=blue}
+\hypersetup{colorlinks=true,linkcolor=blue!50!black,citecolor=blue!75!black,filecolor=black,urlcolor=blue!75!black}
 \usepackage{amsmath}
@@
 \usepackage{subcaption}
+\usepackage{graphicx,import}
+\usepackage{booktabs}
+
 % \usepackage{subfigure}
@@
 \newcommand{\warn}[0]{\cellcolor{orange!75}?}
+\newcommand{\na}[0]{\cellcolor{gray!25}}
+\newcommand{\s}[1]{\cellcolor{cyan!25}#1}
 \newcommand{\scross}[0]{\ding{53}~}
@@
 \newcommand{\pytracer}[0]{PyTracer\xspace}
+
+\setlength{\arrayrulewidth}{0.1pt}
 
@@
 However, despite the pervasiveness of Python in data science, analyzing large Python programs remains challenging due to the lack of scalable numerical analysis tools available for this language.
-We developed \pytracer, a profiler to quantify numerical instability in Python applications to address this issue.
-\pytracer automatically instruments Python code at a low cost ($\simeq3.5\times$) to produce numerical traces and visualize them interactively in a Plotly dashboard.
-We designed \pytracer to work with any numerical noise model, including Monte-Carlo Arithmetic, random rounding or, random data perturbations.
+We developed \pytracer, a profiler to quantify numerical instability in Python applications.
+\pytracer automatically instruments Python code to produce numerical traces and visualize them interactively in a Plotly dashboard.
+We designed \pytracer to work with any numerical noise model including Monte-Carlo Arithmetic, random rounding or random data perturbations.
 We illustrate \pytracer's capabilities by testing the numerical stability of key functions in the SciPy and Scikit-learn Python libraries.
-\pytracer permitted pinpointing numerical instabilities caused by a LAPACK library function and fixing them.
+Through these evaluations, we demonstrate \pytracer as a scalable, automatic, and generic framework for numerical evaluations in Python.
 % Numerical stability is a crucial requirement of reliable scientific computing.
@@
 Finally, \pytracer slows down executions by only $3.5 \times$ on average.
-\tristan{Add one sentence to summarize the findings} 
+% \tristan{Add one sentence to summarize the findings} 
 \end{abstract}
@@
 
-The scientific Python ecosystem is a central component of scientific
-analyses due to its rich offering of data manipulation, array programming,
+The scientific Python ecosystem is a central component of data
+analyses owing to its rich offering of data manipulation, array programming,
 numerical analysis, and visualization tools. In particular, libraries such
 as NumPy~\cite{harris2020array}, SciPy~\cite{virtanen2020scipy}, scikit-learn~\cite{pedregosa2011scikit} or PyTorch~\cite{paszke2019pytorch} are used in hundreds of publications every year, providing a reference set of high-quality open-source core scientific libraries.
-Researchers have built numerous domain-specific data analysis pipelines from this ecosystem, leveraging Python's simplicity and expressivity.
+Researchers have built numerous domain-specific software tools from this ecosystem, leveraging Python's simplicity and expressivity.
 
@@
 SciPy and scikit-learn libraries, we demonstrate \pytracer as a practical solution to review the numerical stability of extensive code bases.
-The remainder of this manuscript describes related approaches, presents the design of \pytracer, and demonstrates its potential in various use cases.
+This manuscript describes related approaches, presents the design of \pytracer, and demonstrates its potential in various use cases.
 
@@
 Dynamic approaches typically trace floating-point computations, detect instabilities in traces, and visualize summary statistics about instabilities.
-The remainder of this section reviews existing approaches for each of these steps.
+This section reviews existing approaches for each of these steps.
 
@@
 \subsection{Numerical tracing techniques}
-Tools to trace floating-point computations for C, C++, or FORTRAN programs are numerous due to the prevalence of these languages in High-Performance Computing (HPC). 
+Numerous tools exists to trace floating-point computations for C, C++, or FORTRAN programs due to the prevalence of these languages in High-Performance Computing (HPC). 
 The main tracing techniques are source-to-source, compiler-based transformations, and dynamic binary instrumentation.
@@
 It is combined with symbolic computation to backtrack the root of the error.
-We can note that all methods based on a high-precision oracle suppose that computing with a large number of bits is sufficient to obtain an accurate result, which is not always true (see for example, the famous Muller's sequence~\cite{bajard1996introduction}.
+We can note that all methods based on a high-precision oracle suppose that computing with a large number of bits is sufficient to obtain an accurate result, which is not always true (see for example, the famous Muller's sequence~\cite{bajard1996introduction}).
 %\tristan{it looks like your veritracer paper is the first time where the ``famous Muller's sequence" was described, is that so?}).
@@
 Being agnostic to the programming language is a serious advantage of the DBI method compared to source-to-source and compiler-bases methods.
-However, working at a binary level makes it difficult to access high-level information needed to debug and understand the source code logic.
+However, working at the binary level makes it difficult to access high-level information needed to debug and understand the source-code logic.
 Conversely, the source-to-source approach provides a fine-grained control on the analyzed code, but it lacks scalability, as rewriting large codes can be a tedious task.
@@
 %\tristan{add key references for uq/sa if any}
-\pytracer focuses on stochastic arithmetic since it does not require assumptions about 
-the noise model contrary to the sensitivity analysis.
-Moreover, stochastic arithmetic allows evaluating the numerical quality of an implementation.
+\pytracer focuses on stochastic arithmetic since it does not make any assumption about 
+the noise model, in contrast to sensitivity analysis.
 %\tristan{due to...}
@@
 
-The first published complete stochastic arithmetic framework was CESTAC~\cite{vignes1993stochastic}, where each floating-point computation is performed multiple times with different rounding modes: round-up or round-down.
+The first published complete stochastic arithmetic framework was CESTAC~\cite{vignes1993stochastic}.
+In CESTAC, each floating-point computation is performed multiple times with different rounding modes: round-up or round-down.
 From these stochastic samples, one can then derive the number of significant digits in the computed result.
@@
 on function inputs or output.
-MCA replaces each floating-point number with its stochastic counterpart:
+MCA replaces each floating-point number $x$ with a stochastic counterpart computed as:
 \[
@@
 \]
-where $\beta$ is the number base, $t$ the virtual precision and $\xi \in (-\frac{1}{2},\frac{1}{2})$ is a random uniform variable.
+where $\beta$ is the number base, $e_x$ is the magnitude of $x$, $t$ the virtual precision and $\xi \in (-\frac{1}{2},\frac{1}{2})$ is a random uniform variable.
 Virtual precision allows for the simulation of reduced working precision.
-MCA can be applied in three modes: Random Rounding (RR), Precision Bounding (PB), and full MCA, which perturb either the output, the inputs, or both with the $inexact$ function.
-While the RR mode is equivalent to stochastic rounding, the PB mode allows identifying catastrophic cancellations.
-
-Stochastic arithmetic uses the number of significant digits $s$ estimated among the sampled values to quantify the numerical errors.
+MCA can be applied in three modes: Random Rounding (RR), Precision Bounding (PB), and full MCA, which apply function $inexact$ to the output, the inputs, or both, respectively.
+While the RR mode is equivalent to stochastic rounding, the PB mode can also identify catastrophic cancellations.
+
+Stochastic arithmetic quantifies numerical error using the number of significant digits $s$ estimated among the sampled values.
 A common formula to determine this number from MCA samples is the one reported in~\cite{parker1997monte}:
@@
 where $\mu$ and $\sigma$ are the sample mean and standard deviation of a variable sampled with MCA.  
-Sohier et al.~\cite{sohier2018confidence} recently provided a rigorous generalization of this formula to include confidence intervals.
+Sohier et al.~\cite{sohier2018confidence} recently provided a generalization of this formula to include confidence intervals.
 
@@
 such as VTK~\cite{schroeder2000visualizing} to topological data analysis~\cite{tierny2018topological}, including matrix~\cite{wu2008matrix} or tensor~\cite{kindlmann2006diffusion} visualization.
-We review here tools dedicated to the analysis of numerical variability induced by the floating-point model.
-Despite the large number of existing tools  to locate unstable source code sections, few of them allow the user to have a global view of the numerical accuracy of their computations or compare several executions of the same program under various perturbations.
-
-Veritracer~\cite{chatelain2018veritracer} was the first tool to propose an embedded visualizer of numerical stability over time for C, C++, and Fortran codes.
-It is an extension of Verificarlo~\cite{verificarlo} that offers contextual information about variables traced to allow the user to identify instabilities quickly.
-However, it neither offers a dynamic interface nor includes information about high-level structures such as \texttt{struct} or \texttt{array}.
+Despite the large number of existing tools to identify numerically unstable sections of source code, few allow the user to have a global view of the numerical precision of their computations or to compare several executions of the same program under various perturbations.
+
+Veritracer~\cite{chatelain2018veritracer} was the first tool to propose an embedded visualizer of numerical stability over the execution of C, C++, and Fortran codes.
+Veritracer extends Verificarlo~\cite{verificarlo} with contextual information about traced variables, which allows the user to identify instabilities quickly.
+However, Veritracer neither offers a dynamic interface nor includes information about high-level structures such as \texttt{struct} or \texttt{array}.
 FPAvizual~\cite{gu2014fpavisual} visualizes the effects of floating-point arithmetic but only for educational purposes.
 Anteater~\cite{faust2019anteater} proposes a visualizer for Python codes, but as mentioned previously, it only deals with native Python types, and the user needs to select variables to trace manually.
-However, Anteater provides an insightful reflection
-% \tristan{It's a bit vague. Do you simply mean: ``Anteater's GUI inspired the design of \pytracer's interface"?} 
+Anteater provides an insightful reflection
 around visual debugging beyond floating-point analysis, which has inspired the design of \pytracer's visualization interface.
@@
 \pytracer adopts the three-step workflow shown in Figure~\ref{fig:workflow}.
-First, it uses monkey patching to replace the functions called by the application with a wrapper that saves their arguments and returned values in a trace file.
+First, \pytracer uses monkey patching to replace the functions called by the application with a wrapper that saves their arguments and returned values in a trace file.
 Second, it injects noise in the application, executes it multiple times, and aggregates the resulting trace files to compute summary statistics about each traced variable.
@@
 
-Python loads modules through an import mechanism triggered by the \texttt{import} that involves two objects: \texttt{finders} and \texttt{loaders}. \texttt{Finders} search for packages (or 
+Python loads modules through an import mechanism triggered by the \texttt{import} keyword that involves two objects: \texttt{finders} and \texttt{loaders}. \texttt{Finders} search for packages (or 
 namespaces\footnote{Python distinguishes between \texttt{regular} and \texttt{namespace} packages.
@@
 Listings~\ref{fig:wrapper_creation} and~\ref{fig:generic_wrapper} show \pytracer's function instrumentation mechanism.
-For each function to instrument, \pytracer's \texttt{loader} class creates a wrapper function, dynamically compiles it with the compile builtin function, and substitutes it for the original module function.
-However, this simple technique does not apply to callable class instances, i.e., class instances that have a \texttt{\_\_call\_\_} attribute and are not of type \texttt{FunctionType}.
+For each function to instrument, \pytracer's \texttt{loader} class creates a wrapper function, dynamically compiles it with the \texttt{compile} builtin function, and substitutes it for the original module function.
+Although simple, this technique does not apply to callable class instances, i.e., class instances that have a \texttt{\_\_call\_\_} attribute and are not of type \texttt{FunctionType}.
 Indeed, applying the wrapper technique would 1) modify the type of the class instance to \texttt{FunctionType}, which could cause syntax and semantic errors, and 2) mask class attributes, leading to \texttt{AttributeError} exceptions.
@@
 def generic_wrapper(self, info, *args, **kwargs):
-    """Generic wrapper dumping inputs and outputs of the wrapped function.
+    """Generic wrapper saving inputs and outputs of the wrapped function.
     The id_dict dict keeps a mapping between the original function identifier
@@
 \end{lstlisting}
-    \caption{\pytracer's generic wrapper function that dumps
+    \caption{\pytracer's generic wrapper function that saves
     the inputs and outputs of the wrapped function.}
@@
 However, it implies that no complete mapping of the container returned by an iterator exists in memory since the application computes each element on the fly.
-Therefore, builtin iterators are not serializable which implies that \pytracer cannot save them to output traces.
-A workaround would be to convert iterators into explicit containers, however, this would increase the memory footprint significantly. \pytracer, therefore, does not instrument iterators.
+Therefore, iterators are not serializable which implies that \pytracer cannot save them to output traces.
+A workaround would be to convert iterators into explicit containers, however, this would increase the memory footprint significantly. \pytracer, therefore, does not instrument non-builtin iterators.
 
@@
 
-Once traces are available, \pytracer sequentially parses them and computes the mean, standard deviation, and number of significant digits (as in Equation~\ref{eq:sig-digits}) of all saved values.
-\pytracer saves these summary statistics in an HDF5 file, a hierarchical format that facilitates visual browsing.
+Once traces are available, \pytracer sequentially parses them and computes the mean, standard deviation, and the number of significant digits (as in Equation~\ref{eq:sig-digits}) of all saved values.
+\pytracer saves these summary statistics in an HDF5 file, a hierarchical format that facilitates visual browsing since only
+required information are loaded when requested by the user.
 This operation critically relies on the ordering of call input and output objects in the traces.
@@
 \pytracer's outcome on SciPy and scikit-learn examples.
-The columns \textit{trace} and \textit{parse} report on the tracing and trace aggregation steps with three possible outcomes: green for success, red for numerical error in the application, and orange for errors due to the fuzzy noise injection
-that are not considered as numerical errors, like for instance index errors due to an index shift.
+Columns \textit{trace} and \textit{parse} report on the tracing and trace aggregation steps with three possible outcomes: green for success, red for numerical error in the application, and orange for errors due to the fuzzy noise injection
+that are not considered numerical errors.
+% , like for instance index errors due to an index shift.
 % \tristan{Explain what this is, in a setence here or with a subsubsection if it requires more}. 
@@
 
-The column \textit{result} summarizes the precision for main outputs of SciPy and scikit-learn examples. 
+Column \textit{sigbits} in Table~\ref{tab:pytracer_results_summary} summarizes the precision for the main outputs of SciPy and scikit-learn examples. 
 We measured the precision in significant bits on the main example output by taking the element-wise mean for non-scalar values and, if the example produces many outputs, the average value among all of them.
 The numerical quality across all examples varies from 0 to 52, with an average of 44 significant bits.
-For both modes, we note that only one example failed due to a numerical error
+For both modes, we note that only two examples failed due to a numerical error
 % \tristan{can we see that in the table? if not, don't comment on it, it is puzzling. Could you show that in the table by using the same error symbols as in Table 2?} 
@@
     \centering
-    \begin{tabular}{|ll|c|c|c|c|c|c|}
+    \begin{tabular}{|lll|c|c|c|c|c|c|}
     \hline
-    \multicolumn{2}{|c}{ \multirow{2}{*}{Application} } & \multicolumn{3}{|c|}{Random Rounding (RR)} & \multicolumn{3}{c|}{Full MCA} \\
-    \cline{3-8}
-    & & trace & parse & result & trace & parse & result \\
+    \multicolumn{3}{|c}{ \multirow{2}{*}{Application} } & \multicolumn{3}{|c|}{Random Rounding (RR)} & \multicolumn{3}{c|}{Full MCA} \\
+    \cline{4-9}
+    & & & trace & parse & result & trace & parse & sigbits \\
     \hline
@@
 
-    \multicolumn{1}{|c|}{ \multirow{3}{2em}{ \rotatebox{90}{FFT} } }
-    & \discreteCosineRF &  \valid & \valid & 52 & \warn & \cross & 47 \\ 
-    \multicolumn{1}{|c|}{} & \fftOneDRf & \valid & \valid & 41 & \warn  & \cross & - \\
-    \multicolumn{1}{|c|}{} & \fftTwoDRf & \valid & \valid & 52 & \valid & \valid & 52 \\
-    \hline 
-    \multicolumn{1}{|c|}{  \multirow{5}{2em}{ \rotatebox{90}{Interpolation} } }
+    \multicolumn{1}{|c|}{ \multirow{20}{2em}{ \rotatebox{90}{SciPy} } } &   
+    \multicolumn{1}{c|}{ \multirow{3}{2em}{ \rotatebox{90}{FFT} }}  & \discreteCosineRF &  \valid & \valid & \s{52} & \warn & \cross & \s{47} \\ 
+    \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \fftOneDRf & \valid & \valid & 41 & \warn  & \cross & - \\
+    \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \fftTwoDRf & \valid & \valid & \s{52} & \valid & \valid & \s{52} \\
+    \cline{2-9}
+    \multicolumn{1}{|c|}{} &  \multicolumn{1}{c|}{  \multirow{5}{*}{ \rotatebox{90}{Interpolation} } }
     & \interOneDRf & \valid & \valid & 51 & \warn & \cross &  - \\
-     \multicolumn{1}{|c|}{} & \multiRf      & \valid & \valid & 51 & \warn  & \cross & - \\
-     \multicolumn{1}{|c|}{} & \bsplineRf    & \valid & \valid &10 &  \valid & \valid & 10\\
-     \multicolumn{1}{|c|}{} & \splineOneDRf & \valid & \cross & 52 & \warn  & \cross & 52 \\
-     \multicolumn{1}{|c|}{} & \splineTwoDRf & \valid & \valid & 10 &  \warn  & \cross & - \\
-    \hline
-     \multicolumn{1}{|c|}{ \multirow{12}{2em}{ \rotatebox{90}{Optimization} } }
-    & \bfgsRf & \valid & \valid & 48  & \valid & \valid & 46 \\
-     \multicolumn{1}{|c|}{} & \globalRf & \valid & \cross & 17 & \warn  & \cross & - \\
-     \multicolumn{1}{|c|}{} & | SHGO\footnote{Simplicial Homology Global Optimization} & \valid & \cross & 25 & \warn  & \cross & - \\
-     \multicolumn{1}{|c|}{} & | Dual Annealing & \valid & \cross & 4 & \warn  & \cross & - \\
-     \multicolumn{1}{|c|}{} & | Differential Evolution & \valid & \cross & 0 & \warn  & \cross & - \\
-     \multicolumn{1}{|c|}{} & | Basin Hopping & \valid & \cross & 40 & \warn  & \cross & - \\
-     \multicolumn{1}{|c|}{} & | SHGO Sobol    & \valid & \cross & 45 & \warn  & \cross & - \\
-     \multicolumn{1}{|c|}{} & \slsqpRf  & \valid & \valid & 45 & \valid & \valid & 44 \\
-     \multicolumn{1}{|c|}{} & \lsmRf    & \valid & \valid & 48 & \warn  & \cross & - \\
-     \multicolumn{1}{|c|}{} & \nelderRf & \valid & \valid & 44 & \valid & \valid & 42 \\
-     \multicolumn{1}{|c|}{} & \ncgRf    & \valid & \valid & 48 & \valid & \cross & 47 \\
-     \multicolumn{1}{|c|}{} & \rootRf   & \valid & \cross & 52 & \warn  & \cross & 50 \\
-    \multicolumn{1}{|c|}{}  & \rootLargRf      & \valid & \cross & 29 & \valid & \cross & 26 \\
-     \multicolumn{1}{|c|}{} & \rootLargePredRf & \valid & \cross & 42 & \valid & \cross & 42 \\
-    \multicolumn{1}{|c|}{}  & \trustExactRf & \valid & \valid & 48  & \valid & \valid & 46 \\
-     \multicolumn{1}{|c|}{} & \trustTruncRf & \valid & \valid & 48  & \valid & \valid & 46 \\
-    \multicolumn{1}{|c|}{}  & \trustNCGRf   & \valid & \valid & 52  & \valid & \valid & 47 \\
+    \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \multiRf      & \valid & \valid & \s{51} & \warn  & \cross & \s{-} \\
+    \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{}  & \bsplineRf    & \valid & \valid &10 &  \valid & \valid & 10\\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} &     \splineOneDRf & \valid & \cross & \s{52} & \warn  & \cross & \s{52} \\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} &     \splineTwoDRf & \valid & \valid & 10 &  \warn  & \cross & - \\
+    \cline{2-9}
+    \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{ \multirow{12}{2em}{ \rotatebox{90}{Optimization} } }
+    & \bfgsRf & \valid & \valid & \s{48}  & \valid & \valid & \s{46} \\
+\cline{3-9}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \globalRf & \valid & \cross & 17 & \warn  & \cross & - \\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & | SHGO\footnote{Simplicial Homology Global Optimization} & \na & \na  & \s{25} & \na  & \na & \s{-} \\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & | Dual Annealing & \na & \na  & 4 & \na & \na  & - \\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & | Differential Evolution & \na & \na & \s{0} & \na & \na & \s{-} \\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & | Basin Hopping & \na  & \na & 40 & \na  & \na & - \\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & | SHGO Sobol    & \na  & \na  & \s{45} & \na  & \na & \s{-} \\
+\cline{3-9}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \slsqpRf  & \valid & \valid & 45 & \valid & \valid & 44 \\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \lsmRf    & \valid & \valid &\s{48} & \warn  & \cross & \s{-} \\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \nelderRf & \valid & \valid & 44 & \valid & \valid & 42 \\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \ncgRf    & \valid & \valid & \s{48} & \valid & \cross & \s{47} \\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \rootRf   & \valid & \cross & 52 & \warn  & \cross & 50 \\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \rootLargRf      & \valid & \cross & \s{29} & \valid & \cross & \s{26} \\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \rootLargePredRf & \valid & \cross & 42 & \valid & \cross & 42 \\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \trustExactRf & \valid & \valid & \s{48}  & \valid & \valid & \s{46} \\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \trustTruncRf & \valid & \valid & 48  & \valid & \valid & 46 \\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \trustNCGRf   & \valid & \valid & \s{52}  & \valid & \valid & \s{47} \\
     \hline
@@
 
-    \multicolumn{1}{|c|}{ \multirow{20}{2em}{ \rotatebox{90}{Scikit-learn} } }
+    \multicolumn{2}{|c|}{ \multirow{20}{2em}{ \rotatebox{90}{Scikit-learn} } }
     & \AdaboostRf   & \valid & \valid & 48 & \warn  & \cross & - \\
-    \multicolumn{1}{|c|}{} & \brrRf        & \valid & \valid & 25 & \cross & \cross & - \\
-    \multicolumn{1}{|c|}{} & | $1^{st}$ dataset & \valid & \valid & 25 & \cross & \cross & - \\
-    \multicolumn{1}{|c|}{} & | $2^{nd}$ dataset & \valid & \valid & nan & \cross & \cross & - \\
-    \multicolumn{1}{|c|}{} & \onlineClassifierComparisonRf & \valid & \valid & 20 & \warn & \cross & -  \\
-    \multicolumn{1}{|c|}{} & \kmeansRf     & \valid & \valid & 52 & \valid & \cross & - \\
-    \multicolumn{1}{|c|}{} & \covarianceRf & \valid & \cross & 48 & \warn  & \cross & - \\
-    \multicolumn{1}{|c|}{} & \decisionRf   & \valid & \valid & 50 & \valid & \valid & 50 \\
-    \multicolumn{1}{|c|}{} & \digitsRf     & \valid & \valid & 52 & \warn  & \cross & 52 \\
-    \multicolumn{1}{|c|}{} & \faceRf       & \cross & \valid & -  & \warn  & \cross & - \\
-    \multicolumn{1}{|c|}{} & \penaltyRf    & \valid & \valid & -  & \valid & \valid & - \\
-    \multicolumn{1}{|c|}{} & \lassoRf      & \valid & \valid & 48 & \warn  & \cross & 47 \\
-    \multicolumn{1}{|c|}{} & \hyperplaneRf & \valid & \valid & 3  & \valid & \cross & - \\
-    \multicolumn{1}{|c|}{} & \mnistRf      & \valid & \valid & 43 & \warn  & \valid & - \\
-    \multicolumn{1}{|c|}{} & \multitaskRf  & \valid & \valid & 50 & \warn  & \valid & 48 \\
-    \multicolumn{1}{|c|}{} & \ompRf        & \valid & \valid & 52 & \valid & \valid & 52 \\
-    \multicolumn{1}{|c|}{} & \pcaRf        & \valid & \valid & 48 & \valid & \valid & 48 \\
-    \multicolumn{1}{|c|}{} & \robustRf     & \valid & \valid & 50 & \warn  & \cross & 48 \\
-    \multicolumn{1}{|c|}{} & | Linear        & \valid & \valid & 48 & \warn  & \cross & 46 \\
-    \multicolumn{1}{|c|}{} & | RANSAC        & \valid & \valid & 50 & \warn  & \cross & 48 \\
-    \multicolumn{1}{|c|}{} & \toyRf        & \valid & \valid & 35 & \warn  & \cross & - \\
-    \multicolumn{1}{|c|}{} & \svmRf        & \valid & \valid & 43.5 & \valid & \cross & - \\
-    \multicolumn{1}{|c|}{} & | Non-weighted  & \valid & \valid & 43 & \valid & \cross & - \\
-    \multicolumn{1}{|c|}{} & | Weighted      & \valid & \valid & 44 & \valid & \cross & - \\
-    \multicolumn{1}{|c|}{} & \tomographyRf & \valid & \cross & - & \warn  & \cross & - \\
-    \multicolumn{1}{|c|}{} & \weightedRf   & \valid & \valid & 44 & \valid & \cross & - \\
+    \cline{3-9}
+    \multicolumn{2}{|c|}{} & \brrRf        & \valid & \valid & \s{25} & \cross & \cross & \s{-} \\
+    \multicolumn{2}{|c|}{} & | $1^{st}$ dataset & \na  & \na & 25 & \na  & \na  & - \\
+    \multicolumn{2}{|c|}{} & | $2^{nd}$ dataset & \na & \na  & \s{nan} & \na  & \na & \s{-} \\
+    \cline{3-9}
+    \multicolumn{2}{|c|}{} & \onlineClassifierComparisonRf & \valid & \valid & 20 & \warn & \cross & -  \\
+    \multicolumn{2}{|c|}{} & \kmeansRf     & \valid & \valid & \s{52} & \valid & \cross & \s{-} \\
+    \multicolumn{2}{|c|}{} & \covarianceRf & \valid & \cross & 48 & \warn  & \cross & - \\
+    \multicolumn{2}{|c|}{} & \decisionRf   & \valid & \valid & \s{50} & \valid & \valid & \s{50} \\
+    \multicolumn{2}{|c|}{} & \digitsRf     & \valid & \valid & 52 & \warn  & \cross & 52 \\
+    \multicolumn{2}{|c|}{} & \faceRf       & \cross & \valid & \s{-}  & \warn  & \cross & \s{-} \\
+    \multicolumn{2}{|c|}{} & \penaltyRf    & \valid & \valid & -  & \valid & \valid & - \\
+    \multicolumn{2}{|c|}{} & \lassoRf      & \valid & \valid & \s{48} & \warn  & \cross & \s{47} \\
+    \multicolumn{2}{|c|}{} & \hyperplaneRf & \valid & \valid & 3  & \valid & \cross & - \\
+    \multicolumn{2}{|c|}{} & \mnistRf      & \valid & \valid & \s{43} & \warn  & \valid & \s{-} \\
+    \multicolumn{2}{|c|}{} & \multitaskRf  & \valid & \valid & 50 & \warn  & \valid & 48 \\
+    \multicolumn{2}{|c|}{} & \ompRf        & \valid & \valid & \s{52} & \valid & \valid & \s{52} \\
+    \multicolumn{2}{|c|}{} & \pcaRf        & \valid & \valid & 48 & \valid & \valid & 48 \\
+\cline{3-9}
+    \multicolumn{2}{|c|}{} & \robustRf     & \valid & \valid & \s{50} & \warn  & \cross & \s{48} \\
+    \multicolumn{2}{|c|}{} & | Linear        & \na & \na & 48 & \na  & \na & 46 \\
+    \multicolumn{2}{|c|}{} & | RANSAC        & \na  & \na & \s{50} & \na  & \na  & \s{48} \\
+\cline{3-9}
+    \multicolumn{2}{|c|}{} & \toyRf        & \valid & \valid & 35 & \warn  & \cross & - \\
+\cline{3-9}
+    \multicolumn{2}{|c|}{} & \svmRf        & \valid & \valid & \s{43.5} & \valid & \cross & \s{-} \\
+    \multicolumn{2}{|c|}{} & | Non-weighted  & \na & \na & 43 & \na & \na  & - \\
+    \multicolumn{2}{|c|}{} & | Weighted      & \na  & \na & \s{44} & \na  & \na  & \s{-} \\
+\cline{3-9}
+    \multicolumn{2}{|c|}{} & \tomographyRf & \valid & \cross & - & \warn  & \cross & - \\
+    \multicolumn{2}{|c|}{} & \weightedRf   & \valid & \valid & \s{44} & \valid & \cross & \s{-} \\
     \hline
@@
     \caption{\pytracer execution summary on SciPy and Scikit-learn examples. 
-\\ \emph{trace}: outcome of \pytracer tracing, \emph{parse}: outcome of \pytracer trace parsing and aggregation, \emph{result}: precision for main outputs in significant bits.
+    % \tristan{Replace FFT with SciPy FFT, Interpolation with SciPy Interpolation and Optimization with SciPy Optimization, or add a SciPy header to these rows.} \tristan{Nitpick: you could add a color scheme to sigbits (for instance shades of blue), to make the column more easily readable.} \\
+    \emph{trace}: outcome of \pytracer tracing, \emph{parse}: outcome of \pytracer trace parsing and aggregation, \emph{result}: precision for main outputs in significant bits.
 \valid: successful run, \warn: error from invalid noise injection, \cross: numerical error or divergent traces.
 \textit{nan} stands for (\texttt{Not-A-Number}).
-The names example are linked to their source code.}
+Example names are linked to their source code.}
     \label{tab:pytracer_results_summary}
@@
 
-\subsubsection{Effect of MCA modes}
+\subsection{Effect of MCA modes}
 \label{sec:impact_mca_modes}
@@
 In conclusion, those regions of code should not be perturbed by MCA since the injected noise does not make sense.
-\tristan{conclusion: ces regions du code ne devraient pas etre bruitees car le bruit n'a pas de sens ici (exemple du spin dans -1/2,1/2. Ca correspond aux ?}
+% \tristan{conclusion: ces regions du code ne devraient pas etre bruitees car le bruit n'a pas de sens ici (exemple du spin dans -1/2,1/2. Ca correspond aux ?}
 % While they do not lead to any numerical issue, typing errors should still be fixed
 % by improving the Full MCA mode instrumentation in order to preserve code correctness.
-\tristan{do we really mean that given your answer to my comment below?}. 
-\Yohan{By reading again this sentence, I agree that it is confusing. 
-It suggests that we should fixed the code while my idea was to fix the MCA instrumentation.}
-We provide solutions to help MCA better work with those cases in the discussion section.
-
-\tristan{Check this last sentence, we need to provide some sort of recommendations}. \tristan{how about opening a PR in numpy to fix this error?}
-\Yohan{For this case, they use the math.ceil to correctly round the number, I think the fix is more on the MCA side to
-correctly handle exact number than on the NumPy side.}
+% \tristan{do we really mean that given your answer to my comment below?}. 
+% \Yohan{By reading again this sentence, I agree that it is confusing. 
+% It suggests that we should fixed the code while my idea was to fix the MCA instrumentation.}
+% We provide solutions to help MCA better work with those cases in the discussion section.
+
+% \tristan{Check this last sentence, we need to provide some sort of recommendations}. \tristan{how about opening a PR in numpy to fix this error?}
+% \Yohan{For this case, they use the math.ceil to correctly round the number, I think the fix is more on the MCA side to
+% correctly handle exact number than on the NumPy side.}
 
@@
 
-We tested \pytracer on SciPy examples provided in the tutorial website section 
-\tristan{Are these tests? If not we need to reword the begining of this section (I can do it, just let me know).}.
-\Yohan{No you right, these are examples, not tests, I used the two words interchangeably.}
+We tested \pytracer on SciPy examples provided in the tutorial website section. 
+% \tristan{Are these tests? If not we need to reword the begining of this section (I can do it, just let me know).}.
+% \Yohan{No you right, these are examples, not tests, I used the two words interchangeably.}
 SciPy is organized in several libraries targeting specific computing domains.
@@
     \caption{Absolute value of the mean and standard deviation values for 
-    fft 1D inputs within RR mode (log scale). The real part is shown in blue and the imaginary part in orange.\tristan{put stdev of middle column on the same scale as the other columns}}
+    fft 1D inputs within RR mode (log scale). The real part is shown in blue and the imaginary part in orange.}
     \label{fig:fft1D_inputs}
@@
 
-This package has three tests: \texttt{interpolation\_1D}, \texttt{multivariate\_data}, \texttt{bspline}, \texttt{spline\_1D} and \texttt{spline\_2D}.
+This package has five examples: \texttt{interpolation\_1D}, \texttt{multivariate\_data}, \texttt{bspline}, \texttt{spline\_1D} and \texttt{spline\_2D}.
 
 \texttt{interpolation\_1D} interpolates function $f(x)=\cos(\frac{-x^2}{9})$ with 11 points $x\in[0,10]$.
-For the fives interpolation methods tested (linear, cubic, nearest, previous, next), the solution found is precise, up to 51 bits out of the 53 available.
+For the five interpolation methods tested (linear, cubic, nearest, previous, next), the solution found is precise, up to 51 bits out of the 53 available.
 
@@
 % \tristan{replace the figure references with labels in the figure, it would be much clearer} 
-maps for the two methods as well as the input image (fig.~\ref{fig:bspline_input}) with the middle for the \texttt{bisplev} results and bottom row for the \texttt{convol2d}.
+maps for the two methods as well as the input image (Fig.~\ref{fig:bspline_original_image}).
+The middle row shows \texttt{sepfir2d} results and the bottom row shows \texttt{convol2d} results.
 Both methods exhibit similar precision, with 11 significant bits on average.
 Standard deviations maps on Figures~\ref{fig:bspline_bisplev_std} and~\ref{fig:bspline_convol2d_std} show that regions with low spatial frequencies correspond to regions with low standard deviation, similar to the FFT results.
-As it is mentioned in the SciPy tutorial, the \texttt{bisplev} function is faster than the \texttt{convol2d}.
+The SciPy tutorial mentions that \texttt{bisplev} is faster than \texttt{convol2d}.
 The comparable numerical precision observed in our experiments reinforce the use of \texttt{bisplev} over \texttt{convol2d} in this example.
@@
 Figure~\ref{fig:spline2d_rr} shows the results of the spline evaluation with \texttt{bisplev}.
-We can see that a significant loss of precision in places, following
-an interesting pattern that would be interesting to examine in detail.
-
-\tristan{conclusion? perte de significativite importante par endroits, qui suit un pattern interessant. IL serait interessant d'examiner plus en details pourquoi cela arrive.}
+We observe a significant loss of precision in places, which follows
+an interesting pattern that could be further investigated.
 
@@
     \includegraphics[width=\linewidth]{figure/bspline/bspline_sig.pdf}
-    \caption{\texttt{sepfir2d} significant bits.}
-    \label{fig:bspline_input}
+    \caption{\centering\texttt{sepfir2d} significant bits. \\ \textcolor{white}{.}}
     \label{fig:bspline_bisplev_sig}
@@
     \includegraphics[width=\linewidth]{figure/bspline/bspline_mean_log.pdf}
-    \caption{\texttt{sepfir2d} mean.}
+    \caption{\centering\texttt{sepfir2d} mean. \\(log)}
     \label{fig:bspline_bisplev_mean}
@@
     \includegraphics[width=\linewidth]{figure/bspline/bspline_std_log.pdf}
-    \caption{\texttt{sepfir2d} standard deviation.}
+    \caption{\centering\texttt{sepfir2d} standard deviation. (log)}
     \label{fig:bspline_bisplev_std}
@@
     \includegraphics[width=\linewidth]{figure/bspline/convol2d_sig.pdf}
-    \caption{\texttt{convol2d} significant bits.}
+    \caption{\centering\texttt{convol2d} significant bits. \\ \textcolor{white}{.}}
     \label{fig:bspline_convol2d_sig}
@@
     \includegraphics[width=\linewidth]{figure/bspline/convol2d_mean_log.pdf}
-    \caption{\texttt{convol2d} mean.}
+    \caption{\centering\texttt{convol2d} mean. \\ (log)}
     \label{fig:bspline_convol2d_mean}
@@
     \includegraphics[width=\linewidth]{figure/bspline/convol2d_std_log.pdf}
-    \caption{\texttt{convol2d} standard deviation.}
+    \caption{\centering\texttt{convol2d} standard deviation. (log)}
     \label{fig:bspline_convol2d_std}
 \end{subfigure}
-    \caption{\texttt{bspline} results within RR mode.
-    The SciPy tutorial mentions that \texttt{convol2d} is faster than \texttt{sepfir2d}.
-    In addition, our results show that \texttt{sepfir2d} offers a similar precision.
-    This gives an additional argument for using \texttt{sepfir2d} over \texttt{convol2d}.
+    \caption{\texttt{bspline} results within RR mode. \texttt{sepfir2d} and
+ \texttt{convol2d} have a similar precision.
     % \tristan{can you use the same color maps as in figure 8?}
@@
 
-This package has eleven examples whose seven examples involve the same optimization problem 
-solved with and without constrained by using different methods.
-The last four solve solve a different problem each.
-
-\paragraph{Unconstrained minimization of multivariate scalar functions (six methods):}
-Four Quasi-Newton-Raphson methods aim to determine $x$ that minimizes the function $f$ by using Newton's method step: $x_{k+1} = x_{k} - B^{-1}(x_k)\nabla f(x_k)$, where $\nabla$ and $B$ are the gradient and the approximation of the Hessian matrix of $f$.
+This package has eleven examples. Seven examples involve the same optimization problem 
+solved with and without constraints using different methods.
+One example optimizes a chemical problem under constraints.
+The last three examples solve a different problem each.
+
+\paragraph{Unconstrained minimization of multivariate scalar functions:}
+Four Quasi-Newton-Raphson methods minimize function $f$ by using Newton's step: $x_{k+1} = x_{k} - B^{-1}(x_k)\nabla f(x_k)$, where $\nabla$ and $B$ are the gradient and the approximation of the Hessian matrix of $f$.
 The \texttt{Broyden-Fletcher-Goldfarb-Shanno}~\cite{BFGS} (BFGS) and \texttt{Newton-Conjugate-Gradient}~\cite{nocedal2006numerical} (NCG) are line search methods that approximate $H$ by adding two symmetric rank-one matrices and by using the Conjugate-Gradient method.
@@
 In addition, the \texttt{Nelder-Mead}~\cite{singer2009nelder} simplex-based method iteratively transforms a simplex until its vertices are getting closer to a local minima of the function.
-
-\paragraph{Constrained minimization of multivariate scalar functions (two methods):}
-\texttt{Sequential Least SQuares Programming} (SLSQP~\cite{kraft1988software})
-and \texttt{Least-squares minimization} that uses the Trust Region Reflective algorithm~\cite{li1993centering}.
-
-\paragraph{Root finding (three methods):}
-One for small problems using the hybrid Powell and Levenberg-Marquardt methods for small problems (\texttt{root\_finding}) and two for large problems using a Krylov approximation for the inverse Jacobian with and without the help of a preconditioner (\texttt{root\_finding\_large\_preconditionned} and \texttt{root\_finding\_large}).
-
-The unconstrained minimization methods minimize the Rosenbrock function of $N$ variables:
+All methods are applied to the Rosenbrock function.
+
+\paragraph{Constrained minimization of multivariate scalar functions:}
+Two optimizers solve an optimization problem by taking into account constraints.
+The \texttt{Sequential Least SQuares Programming} uses the SLSQP~\cite{kraft1988software} method to optimize the Rosenbrock function.
+The \texttt{Least-squares minimization} uses the Trust Region Reflective algorithm~\cite{li1993centering}
+to solve a fitting problem from an enzymatic reaction.
+
+\paragraph{}
+The SLSQP and unconstrained minimization methods minimize the \textbf{Rosenbrock} function of $N$ variables
+that reaches its minimum (0) when $x_i=1,\; \forall i \leq N-1$:
 \[f(x) = \sum_{i=1}^{N-1} 100(x_{i+1}-x^2_i)^2 + (1-x_i)^2\]
-The minimum value of this function is 0, reached when $x_i=1,\; \forall i \leq N-1$. % \tristan{for all i's?}
+% The minimum value of this function is 0, reached when $x_i=1,\; \forall i \leq N-1$. % \tristan{for all i's?}
+
 Figure~\ref{fig:unconstrained_optimization} shows the number of significant bits of the solution for the different methods used. 
@@
 to the variant where the Hessian matrix is replaced by 
-a function computing the matrix-vector product of the Hessian and an arbitrary vector
-that allows saving memory and time. 
+a function computing the matrix-vector product of the Hessian and an arbitrary vector, to save memory and time.
 All the methods have a good precision ranging from 43 to 53 significant bits.
-The Nelder-Mead method is the least precise one with $\simeq$ 43 significant bits on average, while the Trust-Region-Newton-CG is the most precise one with $\simeq$ 53 significant bits, this highest precision achievable in double precision.
-The remaining methods have a similar precision with less than 1 bit between them.
+The Nelder-Mead method is the least precise one with $\simeq$ 43 significant bits on average, while the Trust-Region-Newton-CG is the most precise one with $\simeq$ 53 significant bits, the highest precision achievable in double precision.
+The remaining methods have a similar precision.
 % \tristan{why is there only 9 methods in Fig 7 while you mentioned 10?} \Yohan{There are 11 examples whose 6 for the unconstrained minimization (presented in Fig 7).
@@
 The problem has a unique solution $[x_0, x_1] = [0.4149, 0.1701]$.
-Results within RR show a precision of 47 and 44 significant bits for the first and the second solution. %\tristan{which method is tested?}.
+Results obtained with RR show a precision of 47 and 44 significant bits for the first and the second solution. %\tristan{which method is tested?}.
 
@@
 
-Finally, the \texttt{root\_*} examples use three algorithms to 
+\paragraph{Root finding:}
+% We tested three root finder algorithms with one for small problems using the hybrid Powell and Levenberg-Marquardt methods  (\texttt{root\_finding}) and two for large problems using a Krylov approximation for the inverse Jacobian with and without the help of a preconditioner (\texttt{root\_finding\_large\_preconditionned} and \texttt{root\_finding\_large}).
+
+The \texttt{root\_*} examples use three algorithms to 
 find the root of non-linear equations. \texttt{root\_finding}
@@
 \texttt{root\_finding\_large} and \texttt{root\_finding\_large\_preconditioned} examples use 
-the Krylov method to solve an integrodifferential equation on a square
+the Krylov method to approximate the inverse Jacbian with and without the help of a preconditioner. 
+They solve an integrodifferential equation on a square
  $(x,y) \in [0,1] \times [0,1]$, $P(x,1)=1$, and $P=0$ elsewhere on the boundary.
@@
 Figure~\ref{fig:root_finding_large} shows the mean and standard deviation of the result for these 3 samples.
-We can see that both RR and Full MCA found a similar solution.
+We can see that a similar solution was found for RR and Full MCA.
 Full MCA leads to a lower precision than RR although both standard deviation maps remain in the same order of magnitude.
@@
     \caption{Solution of \texttt{root\_finding\_large} example. 
-    We can see that MCA has a less precision solution with a maximal standard deviation at $8.10^{-9}$ against $3.10^{-9}$ for RR mode.
-Moreover, we can see that a high standard deviation is localized around two extrema for both RR and Full MCA modes.
-Finally, the standard deviation stills lower than
+    The standard deviation has two maximum for both RR and Full MCA modes. The standard deviation remains lower than
     the stopping criterion threshold fixed at $6.10^{-6}$. }
@@
 Among the several available examples, we choose the following representative set
-listed in~\ref{tab:pytracer_results_summary}. The following paragraphs 
+listed in Table~\ref{tab:pytracer_results_summary}. The following paragraphs 
 focus on the most interesting stability results observed across all experiments.
@@
     \caption{Call paths of the Bayesian Ridge Regression (BRR) and 
-    Ordinary Least Square (OLS) function. Each fill color represents the calling library
-    with orange for scikit-learn, blue for SciPy and yellow for LAPACK.
+    Ordinary Least Square (OLS) function. Color represents the calling library:
+    orange for scikit-learn, blue for SciPy and yellow for LAPACK.
     Dashed color represents the original path in red and the alternative one in green.
-    Figure~\ref{fig:brr_svd_sig} shows that using the original method to compute the \texttt{svd}
-    approach that leads to numerical instabilities and that the alternative one helps 
-    making the example to converge.
+    Figure~\ref{fig:brr_svd_sig} shows the original method  leads to numerical instabilities while the alternative one converges.
     }
@@
 This example compares a Bayesian Ridge Regression (BRR) to the Ordinary Least Squares (OLS) estimator on a synthetic dataset and for one-dimensional regression using polynomial feature expansion.
-Although the examples does not raise a runtime error, the coefficients computed from the fitting for the synthetic dataset are \texttt{Not-A-Number} (NaN) values for both BRR and OLS.
-\pytracer traces reveal that the SVD solver used is the root cause for this error.
+Although the example does not raise a runtime error, the regression coefficients computed from the fitting are
+non-significant. \pytracer traces reveal that the SVD solver used is the root cause for this error. 
 Figure~\ref{fig:call_path_brr} shows the two call paths for BRR and OLS. 
-We can see that the LAPACK library has two main methods for computing the SVD: \texttt{gesdd} and \texttt{gesvd}.
+The LAPACK library has two main methods for computing the SVD: \texttt{gesdd} and \texttt{gesvd}.
 The former uses a Divide \& Conquer approach, while the latter uses a QR decomposition. 
-While both methods are expected to have the same accuracy~\cite{nakatsukasa2013stable}, Figure~\ref{fig:brr_svd_sig} show that \texttt{gesdd} is totally imprecise, with an average number of significant digits of 0 for BRR and even \texttt{NaN} values for OLS.
+While both methods are expected to have the same accuracy~\cite{nakatsukasa2013stable}, Figure~\ref{fig:brr_svd_sig} shows that \texttt{gesdd} is totally imprecise, with an average number of significant digits of 0 for BRR and even \texttt{Not-a-Number} (\texttt{NaN}) values for OLS.
 On the same figure, we can see that 
 using the \texttt{gesvd} (dgelsd) method instead of the \texttt{gesdd} (dgelss) one, 
-the SVD is converging within the RR and Full MCA modes, with a number of significant bits of 44 on average. 
+the SVD converges for RR and Full MCA, with a number of significant bits of 44 on average. 
 This observation supports the on-going discussion among LAPACK developers on the instability of \texttt{gesdd} (see  \href{https://github.com/Reference-LAPACK/lapack/issues/316}{github.com/Reference-LAPACK/lapack/issues/316}).
@@
     \includegraphics[width=\linewidth]{figure/BRR/BRR_coefs_sig.pdf}
-    \caption{Bayesian Ridge Regression coefficients within RR mode.
-    The \texttt{BRR\_*} points show the \texttt{BayesianRidge} results
+    \caption{Precision of Bayesian Ridge Regression coefficients in RR mode.
+     \texttt{BRR\_*} show the \texttt{BayesianRidge} results
     using the \texttt{gesdd} and \texttt{gesvd} methods. 
-    The \texttt{OLS\_*} points show the \texttt{LinearRegression} results
+    \texttt{OLS\_*} show the \texttt{LinearRegression} results
     with the \texttt{dgelsd} and \texttt{dgelss} methods.
-    We can see that using the Divide \& Conquer method for the SVD
+   The Divide \& Conquer method 
     (\texttt{gesdd} and  \texttt{dgelsd})
-    gives low precision
-    results for \textit{BRR} and even \texttt{NaN} values (star points) for \textit{OLS}. By switching to the \texttt{gesvd} method, 
+    has low precision
+    for \textit{BRR} and results in \texttt{NaN} values (star points) for \textit{OLS}. By switching to the \texttt{gesvd} method, 
     results have a precision of 42 bits on average.
@@
 In this example, the PCA uses the Randomized SVD~\cite{halko2011finding} method that first computes a low-rank approximation of the input matrix using a stochastic algorithm and then uses this approximation as input for the SVD.
-Unfortunately, the example raises an error during the computation of the SVD.
-The \texttt{randomized\_svd} scikit-learn function uses the Divide \& Conquer SVD method (\texttt{gesdd}, see previous comments). 
+The example raises an error during the computation of the SVD.
+The \texttt{randomized\_svd} scikit-learn function uses the Divide \& Conquer SVD method \texttt{gesdd} mentioned previously.
 Replacing \texttt{gesdd} for \texttt{gesvd} solves the SVD convergence issue.
 Figure~\ref{fig:randomized_svd_S} shows the precision of the eigenvalues computed with gesvd, which varies between 15 and 20 significant bits out of the 24 available in single precision.
-Finally, the classifier metrics (precision, recall, F1-score, and support) are identical to the IEEE execution for all MCA samples.
+The classifier metrics (precision, recall, F1-score, and support) are identical to the IEEE execution for all MCA samples.
 
@@
 Thus, we can see that Pytracer can detect instabilities that affect fundamental scientific computing components such as the LAPACK library.
-The Pytracer findings can therefore be extended to many application domains.
-\tristan{conclusion needs to be discussed. Note to self: generaliser un peu la conclusion: pytracer permet de se rendre compte de problemes de stabilite dont plusieurs librairies sont dependantes.}
+% The Pytracer findings can therefore be extended to many application domains.
+% % \tristan{conclusion needs to be discussed.
+Note to self: generaliser un peu la conclusion: pytracer permet de se rendre compte de problemes de stabilite dont plusieurs librairies sont dependantes.}
 
@@
     show respectively the values $U$, $\Sigma$ and $V$.
-     Numerical precision is lower for smaller eigenvalues and this loss of precision translates to eigenvectors.
+     Numerical precision is lower for smaller singular values and this loss of precision translates to singular vectors.
 It would be interesting to investigate the use of numerical precision for dimensionality reduction.
@@
 discretized with 100 points and predicts the class label for each point with integer coordinates.
-Figure~\ref{fig:hyperplan_sig_zoom} shows the the number of significant bits %\tristan{isn't it significant bits?} \tristan{aren't the class predctions integers?}
-\Yohan{No its floating point values}1
-obtained with RR for each point of the grid %(squares \tristan{not sure where the squares are}) 
-and the training dataset (circles \tristan{why are some circles larger than other ones?}).
-We can see that yellow points %\tristan{I don't see any white point} 
+Figure~\ref{fig:hyperplan_sig_zoom} shows the number of significant bits %\tristan{isn't it significant bits?} \tristan{aren't the class predctions integers?}
+% \Yohan{No its floating point values}1
+obtained with RR for each point of the grid. %(squares \tristan{not sure where the squares are}) 
+We can see that yellow regions %\tristan{I don't see any white point} 
 close to the separating hyperplane are highly unstable with a number of significant bits below 0, meaning that
@@
     \caption{
-    These figures show three examples of separating hyperplane prediction.
-First, all figures show the number of significant bits of the prediction within RR mode.
-Second, we can see that the separating hyperplane is visible on each figure without plotting since it corresponds to a lower precision area.
-Indeed, the classifier has difficulty predicting which side the predicted point is on.
-Moreover, a large discretization step amplifies
-    this instability, as Figure~\ref{fig:separating_hyperplan} shows.
-Finally, Figures~\ref{fig:SVM_w_sig} and~\ref{fig:weighted_w_sig} show that taking into account the unbalancing or the weight of points allows for a better separating than ~\ref{fig:SVM_nw_sig} and ~\ref{fig:weighted_nw_sig}.
+    Three examples of separating hyperplane prediction.
+All the figures show the number of significant bits of the prediction in RR mode.
+The separating hyperplane corresponds to a lower-precsion region in each figure.
+Using a large discretization step amplifies
+    this instability.
 % respectively the results of examples    \textit{SVM} and~\textit{Weighted samples}.
@@
 We can see that the number of significant bits is lower on the separating line and
-that taking into account the unbalancing allows a better separation.
+that taking into account class imbalance allows for a better separation.
 % Find the optimal separating hyperplane using an SVC for classes that are unbalanced.
@@
 \paragraph{SGD weighted samples}
-This example uses an SGD to separate weighted points by taking into account or not the weights.
+This example uses an SGD to separate weighted points.
 It divides the training set into two classes of 10 points with a bigger weight for the second class.
 The SGD is trained with hyperparameters $\alpha=0.01$ and a maximum number of iterations to 100.
-The prediction is made on a $[-4,5]\times[-4,5]$ grid discretized with 250000 points.
+The prediction is made on a $[-4,5]\times[-4,5]$ grid discretized with 250 000 points.
 Figures~\ref{fig:weighted_nw_sig} and~\ref{fig:weighted_w_sig} show the number of significant bits
 of prediction within RR along with dataset points in blue and violet.
-We can see that the separating plane is visible without plotting it since it corresponds to the yellow line of lower precision.
-As for the examples SVM and Separating hyperplane, the numerical instabilities are concentrated around the separation since the classifier cannot predict from which side points are placed.
-Finally, taking into account the points' weight allows for a better separating.
+We can see that the separating plane corresponds to a region of lower precision, similar to the previous examples. 
+% Finally, taking into account the points' weight allows for a better separation \tristan{is this related to numerical stability? If not, you can ommit the comment.}.
 
@@
 The initialization overhead is proportional to the number of functions and classes traced.
-For example, by instrumenting NumPy, SciPy, and Scikit-learn, we measured an average initialization time of 8 seconds during our experiments.
-Hence, the initialization overhead is amortized when traced applications are above 8 seconds.
-Moreover, one can reduce this overhead by excluding intensively used functions such as \texttt{numpy.array}.
-Figure~\ref{fig:performance_tracing} summaries \pytracer's tracing overhead for SciPy and scikit-learn examples.
-We can see that \pytracer introduces a slowdown of $17\times$ reduced to $3.5\times$ if we subtract the initialization step.
-Finally, the fuzzy instrumentation increases the slowdown to  $37\times$ for RR and $43\times$ for Full MCA.
+For example, we measured an average initialization time of 8 seconds during our experiments with  NumPy, SciPy, and Scikit-learn.
+This overhead can be reduced by excluding intensively used functions such as \texttt{numpy.array} from the instrumentation.
+Figure~\ref{fig:performance_tracing} summarizes \pytracer's tracing overhead for SciPy and scikit-learn examples. 
+\textit{Slowdown} represents the slowdown of \pytracer without fuzzy measured as the ratio between the actual execution time (without \pytracer) and the execution time using \pytracer.
+The \textit{Slowdown RR} and \textit{Slowdown MCA} show the slowdown within the fuzzy environment. 
+Without fuzzy, \pytracer introduces an average slowdown of $17\times$ high for the examples running less than 8 seconds because \pytracer spends most of its time in the initialization step.
+Since this step is a constant factor of the number of functions instrumented, we also measured the instrumentation cost itself (\textit{Slowdown (Instrumentation)}) calculated by subtracting the initialization time to \textit{Slowdown}.
+We then obtain an average slowdown of $3.5\times$.
+Finally, the fuzzy instrumentation increases the average slowdown to $37\times$ for RR and $43\times$ for Full MCA.
 
@@
     \caption{
-    \pytracer tracing overheads: \textit{Slowdown} is the actual overhead, computed as the ratio between the execution time without and with \pytracer.
-This slowdown can be high for the examples running less than 8 seconds because \pytracer spends most of its time in the initialization step.
-Since this step is a constant factor of the number of functions instrumented, we also plot the slowdown of the instrumentation itself (\textit{Slowdown (Instrumentation)} calculated by subtracting the initialization time.
-    The \textit{Slowdown (RR)} and \textit{Slowdown (MCA)} colors show the slowdown of \pytracer 
+    \pytracer tracing overheads.
+\textit{Slowdown} represents the slowdown of \pytracer without fuzzy measured as the ratio between the actual execution time (without \pytracer) and the execution time using \pytracer.
+    \textit{Slowdown (Instrumentation)} show the actual instrumentation cost computed by subtracting the initialization step.
+    The \textit{Slowdown (RR)} and \textit{Slowdown (MCA)} are the slowdown of \pytracer 
     using the fuzzy environment with RR and Full MCA modes.
-    The first four examples measure the initialization steps depending on the modules instrumented. \tristan{you could make a horizontal chart to avoid rotating the labels (also in Fig 13)}
+    The first four examples measure the initialization steps depending on the modules instrumented. 
+    % \tristan{there's too much text in this caption, move some of it to the text, the caption should just explain the difference between the 4 slowdowns.
+From the text I'm not sure what is the difference between slowdown and slowdown(RR)/slowdown(MCA).}
     }
@@
     \centering
-    \includegraphics[width=\linewidth]{performance_parsing.pdf}
+    \includegraphics[width=\linewidth]{figure/parsing_time.pdf}
     \caption{\pytracer aggregation performance. The figure presents
-    the aggregation time (X-axis) versus the trace size (Y-axis).
+    the trace size (X-axis) versus the aggregation time (Y-axis).
     We can see that the aggregation time is proportional to the trace size.}
@@
 
-Moreover, \pytracer's trace aggregation introduces to a post-processing overhead.
 Figure~\ref{fig:performance_parsing} shows
 the postprocessing time and trace sizes produced by \pytracer. 
-In conclusion, the small overhead introduced by Pytracer allows one to analyze real-life applications.
-
-\tristan{A scatter plot with x=size and y=time might be easier to read.}
-\tristan{Add a conclusion comment about the overhead}
+The linear correlation between the log of the size and the log of the time shows a significant correlation 
+(p-value $\leq 10^{-8}$ for RR and p-value $\leq 10^{-3}$ for MCA).
+% \tristan{Mention linear correlation with p-value here.}
+
+In conclusion, while \pytracer's overhead is substantial, it remains tractable for real-life examples.
 
@@
 
-\tristan{The next paragraphs read like nobody should use \pytracer ever because it's full of issues.
-Rewrite this section to explain why \pytracer is important, what it could be used for, what it brings to current context.
-We can discuss these points if you want.
-If you want to talk about limitations, formulate them as future work, not "pitfalls" or "problems".}
-
-Pytracer is a tool for visualizing the numerical quality of function inputs/outputs over time.
-It generates numerical traces that are aggregated in postprocessing to measure numerical discrepancies between executions.
-Pytracer does not assume the noise model used to estimate uncertainties, but we tested it with the MCA model
-through the fuzzy ecosystem on two broadly used scientific libraries for Python with partial success.
-
-We demonstrated the \pytracer's capabilities to analyze intensively used Python libraries such as NumPy or Scikit-learn, such as 1) Scalability.
-The low instrumentation overhead of 3.5x enables analysis of real applications and permits having a global representation of the numerical quality of an application.
-2) Automaticity.
-\pytracer instrumentation is fully automatic and does not require manual intervention from the user, allowing the instrumentation of the NumPy, SciPy, and Scikit-learn libraries.
-3) Agnosticism. \pytracer works on any python libraries, with any data format supported by Pickle and any numerical noise model flavor.
-
-\pytracer is the first tool to bring the numerical analysis of Python codes available to everyone.
-Indeed, existing tools developed in the last years focused on traditional languages of the HPC community such as C, C++, and FORTRAN.
-However, the Python high-level abstraction allows for quickly developing applications while maintaining high performance with the help of specialized libraries like NumPy.
-Therefore, it is quite natural to see more fields systematically using Python, as in neuroimaging.
-Thus, \pytracer meets the numerical analysis needs of an ever-increasing number of applications writing in Python.
+% \pytracer is a tool for visualizing the numerical quality of function inputs and outputs along the execution of a Python program.
+It generates numerical traces and post-processes them to measure numerical discrepancies between executions.
+\pytracer does not require any particular noise model to estimate uncertainties.
+We tested it with MCA through the fuzzy ecosystem on two broadly used Python libraries.
+
+Through our analysis of SciPy and Scikit-learn, we demonstrated \pytracer's scalability, automaticity, and applicability to any Python program.
+The relatively low instrumentation overhead of 3.5 on average enables the analysis of real applications.
+\pytracer's instrumentation is fully automatic and does not require manual intervention from the user.
+Furthermore, \pytracer works on any Python libraries, with any data format supported by Pickle and any numerical noise model.
+
+\pytracer is the first tool to enable a systematic numerical analysis of Python codes.
+Existing tools focus on traditional languages of the HPC community, such as C, C++, and FORTRAN.
+However, Python's high-level abstraction allows for quickly developing applications while maintaining high-performance thanks to specialized libraries such as NumPy.
+Therefore, \pytracer meets the numerical analysis needs of an ever-increasing number of applications.
+
 Furthermore, \pytracer allows users to pinpoint numerical instabilities root causes precisely by working at the function level.
-Furthermore, the automaticity facilitates the usage and its integration in unit testing, for example.
-Hence, instead of tweaking hyperparameters to make solvers converge, the user has a practical way with \pytracer to quantify the numerical quality of its computations.
-Furthermore, the visualization permits a global view of the code and easily navigate through it.
-Moreover, it removes the need for ad-hoc scripts to visualize data.
-\pytracer currently supports n-dimensional NumPy arrays as well as native Python data.
-We want to extend \pytracer to support other formats such as 4D brain images in future works.
-
-As we showed in section~\ref{sec:impact_mca_modes}, using the Full MCA mode leads to runtime errors that have a considerable impact on the proper functioning of the execution, which is unfortunate since these errors do not reflect actual numerical errors but errors related to perturbations that should not occur.
-Fixing this misbehavior would greatly help use Full MCA mode since this mode allows simulating catastrophic cancellations, which are familiar sources of numerical errors.
-On the other hand, RR mode is far more conservative since it preserves exact operations and is easier to use even though it does not simulate all perturbations.
-In addition to the runtime errors it raises, mismatching shapes is also a problem when aggregating traces as \pytracer will not compute statistics for a set of arrays with different shapes.
+Indeed, evaluating the numerical stability is complex since calculations are strongly correlated between them.
+The instrumentation at the function level limits the size of the traces since only inputs and outputs of a function are dumped.
+It moreover decreases the overhead of the instrumentation and helps the user to identify instabilities quickly.
+Working at the function level is thus a suitable compromise between (1) analyzing at the floating-point operation level and (2) user debug prints.
+(1) Indeed, the fine-grained analysis is costly and hard to analyze due to many computations evolved in HPC codes.
+It overwhelms the user with too much information, making analysis more complicated but exciting at the final step of the understanding.
+(2) Looking at intermediate results through print statements
+is useful as a sanity check since it focuses on valuable information like residuals or norms.
+However, it is not sustainable in a systemic approach since the developer may unsuspected numerically unstable functions.
+Finally, the SciPy environment wraps many computation kernels written in C, like BLAS or LAPACK.
+By working at the function level, \pytracer allows the user to evaluate the numerical precision of such kernels and their impact on the code without getting deep into technical implementation aspects.
+
+Python is a popular language to prototype proof-of-concept. Integrating \pytracer at the early stages of the development cycle allows identifying numerical instabilities to write better quality code.
+\pytracer's automaticity facilitates the usage and enables its integration in unit testing.
+For example, it can be used in a non-regression test to ensure that updates do not degrade the numerical quality of a calculation.
+Moreover, the Plotly dashboard offers a quick visualization to analyze more finely the potential issues.
+
+\pytracer can also be useful for selecting the hyperparameters of a code, as is the case in machine learning.
+Indeed, we find many cases in the literature where users explore a range of hyperparameters to select the ones giving the best scores.
+With \pytracer, the user has a practical way to quantify the numerical quality and understand why hyperparameters lead to inconsistent results instead of tweaking hyperparameters to make solvers converge.
+
+The visualization permits a global view of the code and to understand interactions between computations.
+In addition, the Plotly dashboard helps to navigate through the code easily.
+It moreover removes the need for ad-hoc scripts to visualize data.
+Finally, the dashboard can be extended to support other data formats to visualize.
+At this stage, \pytracer currently supports n-dimensional NumPy arrays as well as native Python data.
+
+As we showed in Section~\ref{sec:impact_mca_modes}, using Full MCA mode leads to runtime errors that have a considerable impact on the proper functioning of the execution, that is unfortunate since these errors do not reflect actual numerical errors but are related to perturbations that should not occur.
+Conversely, RR mode is far more conservative since it preserves exact operations and is easier to use even though it does not simulate all perturbations.
+Therefore, from our experiments, we do not recommend the Full MCA mode for now, and more researches are needed to help fix the issues we encountered.
+
+% Through our analysis of SciPy and Scikit-learn, we demonstrated \pytracer's scalability, automaticity, and applicability to any Python program.
+The relatively low instrumentation overhead of $3.5\times$ on average enables the analysis of real applications.
+\pytracer's instrumentation is fully automatic and does not require manual intervention from the user.
+\pytracer works on any Python libraries, with any data format supported by Pickle and any numerical noise model.
+
+% \pytracer is the first tool to enable a systematic numerical analysis of Python codes.
+Existing tools focus on traditional languages of the HPC community such as C, C++, and FORTRAN.
+However, Python's high-level abstraction allows for quickly developing applications while maintaining high performance thanks to specialized libraries such as NumPy.
+Therefore, \pytracer meets the numerical analysis needs of an ever-increasing number of applications.
+
+% Furthermore, \pytracer allows users to pinpoint numerical instabilities root causes precisely by working at the function level.
+Indeed, evaluating the numerical stability is complex since calculations
+% are strongly correlated between them. 
+% The instrumentation at the function level limits the size of the traces since only inputs and outputs of a function are dumped.
+It moreover decreases the overhead of the instrumentation and helps the user to identify instabilities quickly.
+% Working at function level is thus a suitable compromise between (1) analyzing at the floating-point operation level and (2) user debug prints.
+% (1) Indeed, the fine-grained analysis is costly and hard to analyze due to the large amount of computations evolved in HPC codes.
+It overwhelms the user with too much information, making analysis more difficult but can be interesting at the final step of the understanding.
+% (2) Looking at intermediate results through print statements focuses on valuable information
+% (like residuals or norms) but may miss numerically unstable functions unsuspected by the developer.
+% Finally, the SciPy environment wraps a lot of computation kernels written in C, like BLAS or LAPACK.
+% By working at function level, \pytracer allows the user to evaluate the numerical precision of such kernels
+% and their impact on the code without getting deep into technical implementation aspects.
+
+% Python is a popular language to prototype proof-of-concept. Integrating \pytracer at early stages of the development cycle allows identifying numerical instabilities to write code of better quality.
+% \pytracer's automaticity facilitates the usage and enables its integration in unit testing.
+% It can be for example used in a non-regression test to ensure that the numerical quality of a calculation
+% is not degraded by updates. Moreover, the Plotly dashboard offers a quick visualization to 
+% analyze more finely the potential issues.
+
+% \pytracer can also be useful to select the hyperparameters of a code, as it is the case in machine learning.
+% Indeed, we find many cases in the literature where users explore a range of hyperparameters
+% to select the ones giving the best scores. With \pytracer, 
+% the user has a practical way to quantify the numerical quality and to understand why hyperparameters
+% lead to unstable outputs, instead of tweaking hyperparameters to make solvers converge,
+
+% The visualization permits a global view of the code and to understand interactions between 
+% computations. The Plotly dashboard help to easily navigate through the code.
+% It moreover removes the need for ad-hoc scripts to visualize data. 
+% Finally, the dashboard can be extended to support other data format to visualize.
+% \pytracer currently supports n-dimensional NumPy arrays as well as native Python data.
+
+% As we showed in Section~\ref{sec:impact_mca_modes}, using Full MCA mode leads to runtime errors that have a considerable impact on the proper functioning of the execution.
+This is unfortunate since these errors do not reflect actual numerical errors but errors related to perturbations that should not occur.
+% Conversely, RR mode is far more conservative since it preserves exact operations and is easier to use even though it does not simulate all perturbations.
+% From our experiments, we do not recommend the Full MCA mode for now and more researches are needed 
+% to help fixing issues we encountered.
+
+% Fixing this issue would enable the study of catastrophic cancellations, which are common sources of numerical errors. 
+% In addition to the runtime errors it raises, mismatching shapes is also a problem when aggregating traces as \pytracer will not compute statistics for a set of arrays with different shapes \tristan{So do you conclude that Full MCA is not usable while RR is?
+If so, you should recommend to use Pytracer with RR only.} \tristan{are you still talking about Full MCA here?
+if not, make another paragraph.
+If so, make it clearer.}.
 Two solutions exist to overcome this issue: the first is not to instrument the \texttt{PyArray\_Arange} function with MCA.
@@
 This option would require more extra works than the first one but would ensure more consistent results.
-
-Also, we would like to extend the post-process analysis to aggregate traces where the execution flow path diverges.
+\tristan{I find this paragraph too verbose, you should contract it to a few key sentences.}
+
+% \tristan{The following paragraphs are future work, not discussion. I'd remove them and flesh out the discussion from the ideas mentioned in the current 3rd paragraph}
+
+% Also, we would like to extend the post-process analysis to aggregate traces where the execution flow path diverges.
 Therefore, a posteriori reconstruction is challenging as one must precisely identify the flow path taken and find synchronization points to pursue the analysis.
@@
 
-By design principle, \pytracer is flexible on the noise model used, although we only tested it with the MCA model in our experiments.
+% By design principle, \pytracer is flexible on the noise model used, although we only tested it with the MCA model in our experiments.
 Nevertheless, we would like to compare different models against MCA in future works to see the resulting differences.
@@
 
-Finally, we would extend \pytracer to instrument elementary arithmetic operations which can be helpful to more profound analyses.
-We nevertheless believe that instrumentation at the function level presents two advantages: it first limits the size of the traces since only inputs and outputs of a function are dumped instead of a full report which, on the one hand, decreases the overhead of the instrumentation and, on the other hand, help the user to identify instabilities quickly.
+% Finally, we would extend \pytracer to instrument elementary arithmetic operations which can be helpful to more profound analyses.
+We nevertheless believe that instrumentation at the function level presents two advantages: it first limits the size of the traces since only inputs and outputs of a function are saved instead of a full report which, on the one hand, decreases the overhead of the instrumentation and, on the other hand, help the user to identify instabilities quickly.
 Indeed, full reporting can overwhelm the user with too much information, making analysis more difficult at first.
@@
 Such an analysis would require a different instrumentation approach by, for example, working at the Abstract Syntax Tree (AST) level since it is trivial to get it in Python.
-Moreover, working at the AST level allows doing dependency analysis.
+% Moreover, working at the AST level allows doing dependency analysis.
 Another extension would be to extract and replay a function, in the same vein as the CERE tool does but for Python, and to use an AST instrumentation to analyze the numerical quality of elementary operations step by step within the fuzzy environment.
@@
 % Finally, \pytracer does not instrument elementary arithmetic operations, and it can be a barrier to more profound analysis.
-% However, we believe that instrumentation at the function level presents two advantages: it first limits the size of the traces since only inputs and outputs of a function are dumped instead of a full report which, on the one hand, decrease the overhead of the instrumentation and, on the other hand, help the user to identify instabilities quickly.
-One of the pitfalls can be overwhelming the user with too much information, making analysis more difficult.
-Nevertheless, the analysis at fine granularity can be interesting at the final step of the understanding.
-Such an analysis would require a different instrumentation approach by, for example, working at the Abstract Syntax Tree (AST) level since it is trivial to get it in Python.
+%Such an analysis would require a different instrumentation approach by, for example, working at the Abstract Syntax Tree (AST) level since it is trivial to get it in Python.
 % An ideal way to do that would be to extract and replay a function, in the same vein as the CERE~\cite{castro2015cere} tool does but for Python, and use an AST instrumentation to analyze the numerical quality of elementary operations step by step within the fuzzy environment.
@@
 % \tristan{I moved this from the opening of Section 4, as this reads more like a summary of \pytracer's features than an experiment description.
-It should be refactored in 1-2 paragraphs summarizing the main properties of \pytracer.}
-
-\pytracer is the first tool to offer a complete framework
-for analyzing and visualizing the numerical stability of Python codes.
-It works by automatically instrumenting Python libraries to produce numerical
-traces visualized through an interactive Plotly Dash server.
-\pytracer does not require manual code modification, and has been tested  with 
-major scientific libraries such as NumPy, SciPy, and Scikit-learn.
+It should be refactored in 1-2 paragraphs summarizing the main properties of \\pytracer.}
+
+Evaluating the numerical stability of scientific Python codes is a tedious task and requires expertise to be conducted.
+Automatic tools to help the users understand what is going on in their codes is therefore crucial.
+In this perspective, \pytracer is the first tool to offer a complete framework for analyzing and visualizing the numerical stability of Python codes.
+It works by automatically instrumenting Python libraries to produce numerical traces visualized through an interactive Plotly Dash server.
+\pytracer does not require manual code modification, and we tested it with major scientific libraries such as NumPy, SciPy, and Scikit-learn.
 Our results show that \pytracer is scalable, with an average instrumentation slowdown of $3.5\times$.
@@
 Moreover,
-\pytracer is by construction agnostic to the noise model used 
-to evaluate the numerical stability. We have demonstrated 
-that \pytracer can be used with the Monte Carlo Arithmetic 
-through the fuzzy environment. 
+\pytracer is by construction agnostic to the noise model used to evaluate the numerical stability.
+Furthermore, we have demonstrated that \pytracer is usable with the Monte Carlo Arithmetic through the fuzzy environment.
 The experiments conducted in this paper are the first largest application of the fuzzy ecosystem by the wide range of applications covered.
-We also have to provide feedback about pitfalls and benefits encountered to shed light on first-time users' good and bad practices and democratize MCA's usage. 
+
+In future work, we would like to extend the post-process analysis to aggregate traces when the execution flow path diverges by leveraging techniques used in code coverage analysis.
+Moreover, we would like to extend \pytracer to instrument elementary arithmetic operations which can be helpful to more profound analyses.
+Finally, although \pytracer is flexible on the noise model used, we only tested it with the Monte Carlo Arithmetic.
+Therefore, we would like to compare different models against MCA.
 \pytracer is available at \href{https://github.com/big-data-lab-team/pytracer}{github://big-data-lab-team/pytracer} under MIT License.
+
+% Evaluating the numerical stability of scientific Python codes is a tedious task
+% and requires an expertise to be conducted. Automatic tools to help the users 
+% understanding what's going on in their codes is therefore crucial.
+% In this perspective, \pytracer is the first tool to offer a complete framework
+% for analyzing and visualizing the numerical stability of Python codes.
+% It works by automatically instrumenting Python libraries to produce numerical
+% traces visualized through an interactive Plotly Dash server.
+% \pytracer does not require manual code modification, and has been tested with 
+% major scientific libraries such as NumPy, SciPy, and Scikit-learn.
+Our results show that \pytracer is scalable, with an average instrumentation slowdown of $3.5\times$.
+\pytracer's visualization interface remains responsive even with traces of up to 1TB.
+Moreover,
+% \pytracer is by construction agnostic to the noise model used 
+% to evaluate the numerical stability. We have demonstrated 
+% that \pytracer can be used with the Monte Carlo Arithmetic 
+% through the fuzzy environment. 
+% The experiments conducted in this paper are the first largest application of the fuzzy ecosystem by the wide range of applications covered.
+
+% In future work, we would like to extend the post-process analysis to aggregate traces 
+% when the execution flow path diverges by leveraging techniques used in code coverage analysis.
+% Moreover, we would like to extend \pytracer to instrument elementary arithmetic operations 
+% which can be helpful to more profound analyses. Finally, although \pytracer is flexible on the noise
+% model used, we only tested it with the Monte Carlo Arithmetic. We would like to compare different 
+% models against MCA.
+
+% We also have to provide feedback about pitfalls and benefits encountered to shed light on first-time users' good and bad practices and democratize MCA's usage.
 

### 2021-12-10 paper.tex
Greg review

@@
 \newcommand{\tristanmod}[2]{\color{orange}\sout{#1} #2\color{black}\xspace}
+\newcommand{\gkmod}[2]{\color{purple}\sout{#1} #2\color{black}\xspace}
 
@@
 \title{PyTracer: Automatically profiling numerical instabilities in Python}
-\author{Yohan Chatelain$^1$, Gregory Kiar$^2$, Nigel Young$^1$, Tristan Glatard$^1$\\
+\author{Yohan Chatelain$^1$, Nigel Young$^1$,  Gregory Kiar$^2$,  Tristan Glatard$^1$\\
 $^1$Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada\\
@@
 Numerical stability is a crucial requirement of reliable scientific computing.
-However, despite the pervasiveness of Python in data science, analyzing large Python programs remains challenging due to the lack of scalable numerical analysis tools available for this language.
-We developed \pytracer, a profiler to quantify numerical instability in Python applications.
-\pytracer automatically instruments Python code to produce numerical traces and visualize them interactively in a Plotly dashboard.
-We designed \pytracer to work with any numerical noise model including Monte-Carlo Arithmetic, random rounding or random data perturbations.
-We illustrate \pytracer's capabilities by testing the numerical stability of key functions in the SciPy and Scikit-learn Python libraries.
-Through these evaluations, we demonstrate \pytracer as a scalable, automatic, and generic framework for numerical evaluations in Python.
+However, despite the pervasiveness of Python in data science, analyzing large Python programs remains challenging due to the lack of scalable numerical analysis tools available\gkmod{ for this language}{}.
+\gkmod{}{To fill this gap,}we developed \pytracer, a profiler to quantify numerical instability in Python applications.
+\pytracer \gkmod{automatically}{transparently?} instruments Python code to produce numerical traces and visualize them interactively in a Plotly dashboard.
+We designed \pytracer to \gkmod{work with any}{be agnostic to} numerical noise model \gkmod{including}{, allowing for tool evaluation through} Monte-Carlo Arithmetic, random rounding \gkmod{or}{,} random data perturbations\gkmod{}{, or structured noise for a particular application}.
+We illustrate \pytracer's capabilities by testing the numerical stability of key functions in \gkmod{the}{both} SciPy and Scikit-learn \gkmod{}{, two dominant} Python libraries \gkmod{}{for mathematical modeling}.
+Through these evaluations, we demonstrate \pytracer as a scalable, automatic, and generic framework for numerical \gkmod{evaluations}{profiling} in Python.
 % Numerical stability is a crucial requirement of reliable scientific computing.
@@
 
-The scientific Python ecosystem is a central component of data
-analyses owing to its rich offering of data manipulation, array programming,
+The scientific Python ecosystem \gkmod{is}{has become} a central component of data
+analyses \gkmod{}{in recent years,} owing to its rich offering of data manipulation, array programming,
 numerical analysis, and visualization tools. In particular, libraries such
-as NumPy~\cite{harris2020array}, SciPy~\cite{virtanen2020scipy}, scikit-learn~\cite{pedregosa2011scikit} or PyTorch~\cite{paszke2019pytorch} are used in hundreds of publications every year, providing a reference set of high-quality open-source core scientific libraries.
-Researchers have built numerous domain-specific software tools from this ecosystem, leveraging Python's simplicity and expressivity.
+as NumPy~\cite{harris2020array}, SciPy~\cite{virtanen2020scipy}, scikit-learn~\cite{pedregosa2011scikit} or PyTorch~\cite{paszke2019pytorch} are used in hundreds of publications \gkmod{every}{each} year, \gkmod{providing}{and serve as} a reference set of high-quality open-source core scientific libraries.
+Researchers have built numerous domain-specific software tools from this ecosystem, leveraging Python's simplicity and \gkmod{expressivity}{flexibility}.
 
@@
 processing.
-In unstable analyses, small numerical perturbations introduced by data noise, software and hardware updates, or parallelization lead to substantial deviations in final results and potentially different scientific conclusions, threatening the reliability of computational analyses.
-To address this issue, numerical stability analyses need to be conducted systematically, however, no practical tool currently exists to conduct such analyses for Python programs.
-
-We present PyTracer, a numerical stability analyzer for Python programs.
-PyTracer adopts a dynamic approach that evaluates numerical stability using program execution traces and is applicable to large programs without manual intervention.
-In contrast, theoretical approaches based on condition numbers or backward error analysis require detailed modeling of the program and its numerical implementation.
+In unstable analyses, small numerical perturbations introduced by data noise, software and hardware updates, or parallelization \gkmod{lead to}{have potential to introduce} substantial deviations in final results, \gkmod{and}{leading to} potentially different scientific conclusions, \gkmod{ultimately} threatening the reliability of computational analyses.
+To \gkmod{address}{prevent} this \gkmod{issue}{}, numerical stability analyses need to be conducted systematically, however, no practical tool currently exists to conduct such analyses for Python programs.
+
+We present PyTracer, a numerical stability \gkmod{analyzer}{profiling and visualization tool} for Python programs.
+\pytracer adopts a dynamic approach that evaluates numerical stability using program execution traces, and is applicable to large programs without manual intervention.
+\gkmod{}{The transparent nature of \pytracer is particularly valuable} in contrast \gkmod{}{to} theoretical approaches based on condition numbers or backward error analysis\gkmod{}{, which} require detailed modeling of the program and its numerical implementation.
 Similarly, static code analysis techniques hardly scale to large codebases, particularly in dynamically-typed languages such as Python.
 
-PyTracer estimates the variability of floating-point variables by combining program traces obtained with different numerical perturbations, which requires (1) generating numerically-perturbed executions, (2) tracing floating-point computations along program executions, and (3) visualizing stability evaluations.
-PyTracer addresses these requirements with (1) a ``fuzzy" Python interpreter instrumented with Monte-Carlo arithmetic, (2) a dynamic instrumentation of Python functions, modules, and classes through meta-programming, (3) an interactive Plotly dashboard to visualize stability measures throughout program executions.
+\pytracer estimates the variability of floating-point variables by combining program traces obtained with different numerical perturbations, which requires (1) generating numerically-perturbed executions, (2) tracing floating-point computations along program executions, and (3) visualizing stability evaluations.
+\pytracer addresses these requirements with (1) a ``fuzzy" Python interpreter instrumented with Monte-Carlo arithmetic, (2) a dynamic instrumentation of Python functions, modules, and classes through meta-programming, (3) an interactive Plotly dashboard to visualize stability measures throughout program executions.
 
@@
 
-Several tools have been developed to assess numerical quality, divided into static and dynamic approaches.
-Static approaches typically analyze source code while dynamic approaches trace floating-point computations throughout executions.
+Several tools have been developed to assess numerical quality, \gkmod{}{and can be} divided into static and dynamic approaches.
+Static approaches typically analyze source code, while dynamic approaches trace floating-point computations throughout executions.
 A detailed review of these approaches is presented in~\cite{cherubin2020tools}.
-\pytracer adopts the dynamic approach due to its scalability to large existing code bases.
+\pytracer adopts the dynamic approach due to its scalability to large \gkmod{existing}{} code bases.
 Dynamic approaches typically trace floating-point computations, detect instabilities in traces, and visualize summary statistics about instabilities.
@@
 Numerous tools exists to trace floating-point computations for C, C++, or FORTRAN programs due to the prevalence of these languages in High-Performance Computing (HPC). 
-The main tracing techniques are source-to-source, compiler-based transformations, and dynamic binary instrumentation.
-
+The main tracing techniques are \textit{source-to-source}, \textit{compiler-based transformations}, and \textit{dynamic binary instrumentation}.
+
+\gkmod{}{Note: this paragraph just reads like a list with no real interpretation/commentary.
+I think it would be better to state the strengths of this technique, cite examples, and then state limitations/why it isn't the only technique used.}
 The source-to-source technique requires a rewriting of the application to modify floating-point types. 
-CADNA~\cite{jezequel2008cadna} is a library for C, C++, and Fortran implementing the CESTAC~\cite{vignes1993stochastic} stochastic arithmetic.
+CADNA~\cite{jezequel2008cadna} is a library for C, C++, and Fortran implementing \gkmod{the}{} CESTAC~\cite{vignes1993stochastic} stochastic arithmetic.
 Shaman~\cite{demeure_phd} is a C++ library that uses a first-order error model to propagate numerical error.
@@
 
+\gkmod{}{Note: similar to the above, this is just a list rather than a highlight of how the compiler-based approach can be more scalable than source-to-source because it requires less manual intervention into a codebase (e.g.), then have your list, and finally say why it is still limited/not a global fix to this problem.}
 The compiler-based approach instruments floating-point expressions at compile time. 
@@
 
+\gkmod{}{Note: I like this comparison here, but do think that the comments above about providing some more info when each is mentioned would still help this section.}
 Being agnostic to the programming language is a serious advantage of the DBI method compared to source-to-source and compiler-bases methods.
@@
 the noise model, in contrast to sensitivity analysis.
+\gkmod{}{Q: isn't \pytracer agnostic to noise model/method for instability detection?
+Can't we just re-run the tool multiple times under whatever model for detecting instabilities that we choose and it will work all the same?
+If so, then I may reword this to say that pytracer works for all, and for our usecases here we use SA because X, Y, and Z...}
 %\tristan{due to...}
@@
 Stochastic arithmetic quantifies numerical error using the number of significant digits $s$ estimated among the sampled values.
-A common formula to determine this number from MCA samples is the one reported in~\cite{parker1997monte}:
+A common formula to determine this number from MCA samples is \gkmod{the one reported}{presented} in~\cite{parker1997monte}:
 \begin{equation}
@@
 
-Visualization covers a wide range of numerical simulation domains, from general-purpose numerical visualization with tools
+Visualization \gkmod{}{Note: You kind of jump right in to this section.
+Visualization of what in particular?
+Why do we want (need?) to visualize this sort of data?} covers a wide range of numerical simulation domains, from general-purpose numerical visualization with tools
 such as VTK~\cite{schroeder2000visualizing} to topological data analysis~\cite{tierny2018topological}, including matrix~\cite{wu2008matrix} or tensor~\cite{kindlmann2006diffusion} visualization.
@@
 
-Veritracer~\cite{chatelain2018veritracer} was the first tool to propose an embedded visualizer of numerical stability over the execution of C, C++, and Fortran codes.
+Veritracer~\cite{chatelain2018veritracer} was the first tool to propose an embedded visualizer of numerical stability over the execution of C, C++, and Fortran code.
 Veritracer extends Verificarlo~\cite{verificarlo} with contextual information about traced variables, which allows the user to identify instabilities quickly.
 However, Veritracer neither offers a dynamic interface nor includes information about high-level structures such as \texttt{struct} or \texttt{array}.
-FPAvizual~\cite{gu2014fpavisual} visualizes the effects of floating-point arithmetic but only for educational purposes.
-Anteater~\cite{faust2019anteater} proposes a visualizer for Python codes, but as mentioned previously, it only deals with native Python types, and the user needs to select variables to trace manually.
+FPAvizual~\cite{gu2014fpavisual} visualizes the effects of floating-point arithmetic but only for educational purposes \gkmod{}{Q: What does this mean?}.
+Anteater~\cite{faust2019anteater} proposes a visualizer for Python code, but as mentioned previously, it only deals with native Python types, and the user needs to select variables to trace manually.
 Anteater provides an insightful reflection
@@
 \pytracer adopts the three-step workflow shown in Figure~\ref{fig:workflow}.
-First, \pytracer uses monkey patching to replace the functions called by the application with a wrapper that saves their arguments and returned values in a trace file.
-Second, it injects noise in the application, executes it multiple times, and aggregates the resulting trace files to compute summary statistics about each traced variable.
+First, \pytracer uses \gkmod{monkey patching}{\textit{monkey patching}} to replace the functions called by the application with a wrapper that saves their arguments and returned values in a trace file \gkmod{}{Q: This is conceptually similar to a decorator, no?
+If so, perhaps it is worth mentioning}.
+Second, it injects noise in the application \gkmod{}{Q: \pytracer doesn't actually inject noise, does it?
+You can just run your tool however you want multiple times}, executes it multiple times, and aggregates the resulting trace files to compute summary statistics about each traced variable.
 Finally, a Plotly dashboard provides interactive visualizations highlighting unstable code sections.
@@
     \includegraphics[width=\linewidth]{figure/workflow.pdf}
-    \caption{Pytracer workflow}
+    \caption{Pytracer workflow \gkmod{}{Note: replace "Execution" with "Multiple Independent Executions", and maybe move it to be between the gears and the pkl files.}}
     \label{fig:workflow}
@@
 To do so, it creates a new, instrumented version of each module that preserves its original attributes so that the application can transparently use it.
+\gkmod{}{Note: this form of monkey patching is basically global and transparent decorating, right?}
 By default, \pytracer instruments all the attributes
-in a given module except the special ones of the form \texttt{\_\_*\_\_}.
+in a given module except the special ones of the form \texttt{\_\_*\_\_}\gkmod{}{, which is common for reserved Python methods}.
 However, some attributes are not writable. In this case, \pytracer preservers the original attributes and warns the user. The user can also restrict the list of traced attributes through
@@
 \pytracer automatically instruments class instances since it instruments classes.
-However, it cannot instrument or instantiate classes that have read-only attributes --- in particular class \texttt{ufunc} ---, which is problematic given their pervasiveness in scientific computing.
+However, it cannot instrument or instantiate classes that have read-only attributes --- in particular class \texttt{ufunc}, --- which is problematic given their pervasiveness in scientific computing.
 In particular, NumPy's universal functions include
-vectorized elementary mathematical functions and other prevalent ones. Universal functions are implemented in C, which prevents their modification.
+vectorized elementary mathematical functions and other prevalent \gkmod{ones}{Q: prevalent whats?}. Universal functions are implemented in C, which prevents their modification.
 
 To overcome this issue, \pytracer wraps the class instance into a transparent wrap class (\texttt{twc}) that overloads
-1) function \texttt{\_\_getattribute\_\_}, called when an instance attribute is accessed --- instrumented to return the attributes from the original class, and 2) function \texttt{\_\_call\_\_}, called when the function is called through the () operator --- instrumented with function \texttt{generic\_wrapper} .
-The \texttt{twc} returns the queried attribute of the instance instead of returning its attributes, allowing transparent access to the instance.
+1) function \texttt{\_\_getattribute\_\_}, called when an instance attribute is accessed --- instrumented to return the attributes from the original class, and 2) function \texttt{\_\_call\_\_}, called when the function is called through the () operator --- instrumented with function \texttt{generic\_wrapper}.
+\gkmod{}{Note: the previous sentence is a bit hard to follow; the word "called" is used a lot so I got a bit lost.} The \texttt{twc} returns the queried attribute of the instance instead of returning its attributes, allowing transparent access to the instance.
 Finally, \pytracer overloads the builtin \texttt{type} function to preserve the type of the wrapped instance.
@@
 \pytracer saves these summary statistics in an HDF5 file, a hierarchical format that facilitates visual browsing since only
-required information are loaded when requested by the user.
+required information are loaded when requested by the user. \gkmod{}{Q: Is there a reason we don't also use HDF for the raw traces? Lack of native compression?}
 This operation critically relies on the ordering of call input and output objects in the traces.
@@
 The third main component of \pytracer is its interactive trace visualizer built with Plotly Dash~\cite{plotly}, a Python framework for web visualization.
-Plotly Dash abstracts the low-level details of web applications in a highly customizable development interface allowing to offload heavy computations to a server. 
+Plotly Dash abstracts the low-level details of web applications in a highly customizable development interface allowing to offload heavy computations to a server \gkmod{}{Q: does it support using a remote server with forwarding, in the event that your local system isn't that beefy?}.
 Figure~\ref{fig:visu-layout} presents the general layout of the \pytracer visualizer, divided into five sub-components:
@@
 By default, \pytracer shows the number of significant digits computed across the traces.
-The user can switch to the mean or the standard deviation.
+The user can switch to the mean or the standard deviation \gkmod{}{Q: mean/stdev of what?
+the inputs/outputs?
+But what if they are on a totally different scale (e.g.
+log(0.0001)}.
 The visualizer uses an upper triangle for inputs and a lower triangle for outputs.
@@
 Each variable is prefixed with the original value and postfixed with the name of the parameter.
+\gkmod{}{Q: how is this managed for the sake of interpretability?
+E.g.
+if one of the components has very low significance and another few are fine, how can I easily identify where in my sequence we have the drop in precision?}
     Finally, non-scalar values (vectors or matrices) are represented by their average and can be inspected with the Zoom view (see below).
@@
     This view provides insights on the calling context for each function, which may influence numerical stability.
- \item  Source code view: This view displays the source code file of the variable hovered in the timeline view. 
+\gkmod{}{Note: this is a non-standard layout for gantt charts...
+normally the width/overlap is determined by time of start + duration.
+Is that information contained somewhere in here?
+If not, will a very fast function that calls sub-functions, say, 1000 times look longer than a very slow function that doesn't call any subfunctions?}
+ \item  Source code view: This view displays \gkmod{}{a local snapshot of} the source code file of the variable hovered in the timeline view. 
  \item Zoom view: This view provide details about non-scalar values. For example, a matrix may have instabilities around its diagonal but not in other regions.
@@
 \pytracer's outcome on SciPy and scikit-learn examples.
-Columns \textit{trace} and \textit{parse} report on the tracing and trace aggregation steps with three possible outcomes: green for success, red for numerical error in the application, and orange for errors due to the fuzzy noise injection
-that are not considered numerical errors.
+Columns \textit{trace} and \textit{parse} report on the tracing and aggregation steps with three possible outcomes: green for success, red for numerical error in the application, and orange for errors due to the fuzzy noise injection
+that are not considered numerical errors. \gkmod{}{Q: What does "success" or the other labels actually mean? What is the threshold for numerical errors, e.g.}
 % , like for instance index errors due to an index shift.
 % \tristan{Explain what this is, in a setence here or with a subsubsection if it requires more}. 
-Overall, the tracing and parsing of SciPy and scikit-learn examples in Random Rounding mode was entirely successful for 32/40 examples.
+Overall, the tracing and parsing of SciPy and scikit-learn examples in Random Rounding mode was entirely successful \gkmod{}{, indicating on average XX loss in numerical precision,} for 32/40 examples.
 The remaining examples failed due to numerical errors in the libraries, which we discuss hereafter.
-The instrumentation with Full MCA is more invasive and reduced the number of successful executions to 12/40.
+The instrumentation with Full MCA is more invasive and reduced the number of successful \gkmod{}{Q: Does this mean the 28 failed, or completed but poorly?
+In general, the way the states are being referred to so far in the results are rather ambiguous} executions to 12/40.
 
 Column \textit{sigbits} in Table~\ref{tab:pytracer_results_summary} summarizes the precision for the main outputs of SciPy and scikit-learn examples. 
-We measured the precision in significant bits on the main example output by taking the element-wise mean for non-scalar values and, if the example produces many outputs, the average value among all of them.
+We measured the precision in significant bits on the \gkmod{main}{final primary} example output by taking the element-wise mean for non-scalar values and, if the example produces many outputs, the average value among all of them.
 The numerical quality across all examples varies from 0 to 52, with an average of 44 significant bits.
@@
 % \tristan{can we see that in the table? if not, don't comment on it, it is puzzling. Could you show that in the table by using the same error symbols as in Table 2?} 
-(\texttt{face\_recognition} for RR and \textit{Bayesian Ridge Regression} for Full MCA) even though we underestimate this number since Full MCA mode is more intrusive than RR mode and most of the examples produce error caused by the fuzzy noise injection.
+(\texttt{face\_recognition} for RR and \texttt{Bayesian Ridge Regression} for Full MCA) even though this number is underestimated since Full MCA mode is more intrusive than RR mode and most of the examples produce error caused by the fuzzy noise injection.
+\gkmod{}{Note: I don't understand what is being said in the rest of the sentence following the parentheses}
 
@@
     \cline{4-9}
-    & & & trace & parse & result & trace & parse & sigbits \\
+    & & & trace & parse & sigbits & trace & parse & sigbits \\
     \hline
@@
 are due to this type of ``typing" errors.  
-In conclusion, those regions of code should not be perturbed by MCA since the injected noise does not make sense.
+Those code regions should not be perturbed by MCA since the injected noise does not make sense\gkmod{}{; however, given the typing errors in the source code, they are still susceptible to naturally occurring floating point errors}.
 % \tristan{conclusion: ces regions du code ne devraient pas etre bruitees car le bruit n'a pas de sens ici (exemple du spin dans -1/2,1/2. Ca correspond aux ?}
@@
 The results for \texttt{discrete\_cosine\_transform},\texttt{fft\_1D} and  \texttt{fft\_2D} show
-precise numerical results with 48 significant bits in average. 
+precise numerical results with 48 significant bits on average. 
 We observe that the FFT computation is stable to noisy inputs. Figures~\ref{fig:fft1D_inputs} (inputs) and~\ref{fig:fft1D_outputs} (outputs)
@@
 
-In conclusion, Pytracer and the MCA model were helpful to detect the instability of the \texttt{gesdd} method mentioned in several GitHub issues, including the LAPACK repository.
+In conclusion, \pytracer and the MCA model were helpful to detect the instability of the \texttt{gesdd} method mentioned in several GitHub issues, including the LAPACK repository.
 Furthermore, it is worth mentioning that a Pull Request has recently been submitted to let the user select the SVD method and avoid this kind of issue.
-Thus, we can see that Pytracer can detect instabilities that affect fundamental scientific computing components such as the LAPACK library.
+Thus, \pytracer can detect instabilities that affect fundamental scientific computing components such as the LAPACK library.
 % The Pytracer findings can therefore be extended to many application domains.
@@
     \centering
-    \includegraphics[width=\linewidth]{figure/parsing_time.pdf}
-    \caption{\pytracer aggregation performance. The figure presents
-    the trace size (X-axis) versus the aggregation time (Y-axis).
-    We can see that the aggregation time is proportional to the trace size.}
+    \includegraphics[width=\linewidth]{figure/performance_parsing.pdf}
+    \caption{\pytracer aggregation performance. 
+    % \tristan{change xlabel to "Trace size (bytes) and ylabel to "Aggregation time (seconds)}
+    }
     \label{fig:performance_parsing}
@@
 
-Through our analysis of SciPy and Scikit-learn, we demonstrated \pytracer's scalability, automaticity, and applicability to any Python program.
-The relatively low instrumentation overhead of 3.5 on average enables the analysis of real applications.
+Through our analysis of SciPy and scikit-learn, we demonstrated \pytracer's scalability, automaticity, and applicability to a wide range of Python program.
+The relatively low instrumentation overhead of 3.5$\times$ on average enables the analysis of real-scale applications.
 \pytracer's instrumentation is fully automatic and does not require manual intervention from the user.
-Furthermore, \pytracer works on any Python libraries, with any data format supported by Pickle and any numerical noise model.
+Furthermore, \pytracer works on any Python libraries, with any data format supported by pickle and any numerical noise model.
 
@@
 Existing tools focus on traditional languages of the HPC community, such as C, C++, and FORTRAN.
-However, Python's high-level abstraction allows for quickly developing applications while maintaining high-performance thanks to specialized libraries such as NumPy.
+However, Python's high-level abstraction allows for quick application implementations while maintaining high-performance thanks to specialized libraries such as NumPy.
 Therefore, \pytracer meets the numerical analysis needs of an ever-increasing number of applications.
 
-Furthermore, \pytracer allows users to pinpoint numerical instabilities root causes precisely by working at the function level.
-Indeed, evaluating the numerical stability is complex since calculations are strongly correlated between them.
-The instrumentation at the function level limits the size of the traces since only inputs and outputs of a function are dumped.
-It moreover decreases the overhead of the instrumentation and helps the user to identify instabilities quickly.
-Working at the function level is thus a suitable compromise between (1) analyzing at the floating-point operation level and (2) user debug prints.
-(1) Indeed, the fine-grained analysis is costly and hard to analyze due to many computations evolved in HPC codes.
-It overwhelms the user with too much information, making analysis more complicated but exciting at the final step of the understanding.
-(2) Looking at intermediate results through print statements
-is useful as a sanity check since it focuses on valuable information like residuals or norms.
-However, it is not sustainable in a systemic approach since the developer may unsuspected numerically unstable functions.
-Finally, the SciPy environment wraps many computation kernels written in C, like BLAS or LAPACK.
+\pytracer allows users to pinpoint the root causes of numerical instabilities by working at the function level.
+Numerical stability evaluations are complex since calculations are strongly interdependent.
+Function-level instrumentation limits the size of the traces since only inputs and outputs of a function are dumped.
+Moreover, it decreases instrumentation overhead and helps the user identify instabilities quickly.
+Working at the function level is thus a suitable compromise between analysis conducted at the floating-point operation level and user debug prints.
+Indeed,  fine-grained analyses are costly and hard to interpret as they overwhelm users with information.
+In contrast, looking at intermediate results through print statements
+is lightweight but not reliable since developers may not systematically instrument unstable functions.
+Finally, the SciPy environment wraps many computation kernels written in C, such as BLAS or LAPACK.
 By working at the function level, \pytracer allows the user to evaluate the numerical precision of such kernels and their impact on the code without getting deep into technical implementation aspects.
 
-Python is a popular language to prototype proof-of-concept. Integrating \pytracer at the early stages of the development cycle allows identifying numerical instabilities to write better quality code.
-\pytracer's automaticity facilitates the usage and enables its integration in unit testing.
-For example, it can be used in a non-regression test to ensure that updates do not degrade the numerical quality of a calculation.
-Moreover, the Plotly dashboard offers a quick visualization to analyze more finely the potential issues.
-
-\pytracer can also be useful for selecting the hyperparameters of a code, as is the case in machine learning.
-Indeed, we find many cases in the literature where users explore a range of hyperparameters to select the ones giving the best scores.
-With \pytracer, the user has a practical way to quantify the numerical quality and understand why hyperparameters lead to inconsistent results instead of tweaking hyperparameters to make solvers converge.
-
-The visualization permits a global view of the code and to understand interactions between computations.
-In addition, the Plotly dashboard helps to navigate through the code easily.
-It moreover removes the need for ad-hoc scripts to visualize data.
+Integrating \pytracer at the early stages of the development cycle would improve the overall numerical quality of the developed code.
+\pytracer's automaticity facilitates its usage and enables its integration in unit testing.
+For example, \pytracer could be used in regression tests to ensure that updates do not degrade the numerical quality of a calculation.
+
+\pytracer can also be useful for selecting hyperparameters, as is the case in machine learning.
+Indeed, it is common for data scientists to explore a range of hyperparameters and select the ones giving the best scores.
+With \pytracer, the user has a practical way to quantify numerical quality and understand why hyperparameters produce inconsistent results instead of tweaking hyperparameters to make solvers converge.
+For instance, the Face Recognition example  (Figure~\ref{fig:face_recognition_svd}) shows how numerical precision could inform the selection of the number of components in dimensionality reduction.
+
+The visualization provides a global view of the code and interactions between computations.
+In addition, the Plotly dashboard helps navigate through the code easily, without the need for ad-hoc scripts to visualize data.
 Finally, the dashboard can be extended to support other data formats to visualize.
@@
 
-As we showed in Section~\ref{sec:impact_mca_modes}, using Full MCA mode leads to runtime errors that have a considerable impact on the proper functioning of the execution, that is unfortunate since these errors do not reflect actual numerical errors but are related to perturbations that should not occur.
+As we showed in Section~\ref{sec:impact_mca_modes}, using Full MCA mode leads to runtime errors that have a considerable impact on the proper functioning of the execution, which is unfortunate since these errors do not reflect actual numerical errors but are related to perturbations that should not occur.
 Conversely, RR mode is far more conservative since it preserves exact operations and is easier to use even though it does not simulate all perturbations.
-Therefore, from our experiments, we do not recommend the Full MCA mode for now, and more researches are needed to help fix the issues we encountered.
+Therefore, from our experiments, we recommend the use of RR over Full MCA.
+More research is required to address the issues encountered with Full MCA.
+
+Finally, the wide range of results precision obtained from our experiments demonstrate that looking at the numerical variability is essential and that such analyses would benefit from being conducted systematically.
+We showed that well-known scientific libraries are prone to numerical error even though they have been well tested for decades.
+The omnipresence of these libraries in scientific codes should thus impel users to integrate numerical analysis in their development workflow in addition to testing their implementation.
 
@@
 
-Evaluating the numerical stability of scientific Python codes is a tedious task and requires expertise to be conducted.
-Automatic tools to help the users understand what is going on in their codes is therefore crucial.
+Evaluating the numerical stability of scientific Python programs is a tedious task that requires substantial expertise.
+Automatic tools to help users understand the behavior of their code are therefore crucial.
 In this perspective, \pytracer is the first tool to offer a complete framework for analyzing and visualizing the numerical stability of Python codes.
@@
 Our results show that \pytracer is scalable, with an average instrumentation slowdown of $3.5\times$.
-\pytracer's visualization interface remains responsive even with traces of up to 1TB.
-Moreover,
-\pytracer is by construction agnostic to the noise model used to evaluate the numerical stability.
-Furthermore, we have demonstrated that \pytracer is usable with the Monte Carlo Arithmetic through the fuzzy environment.
-The experiments conducted in this paper are the first largest application of the fuzzy ecosystem by the wide range of applications covered.
-
-In future work, we would like to extend the post-process analysis to aggregate traces when the execution flow path diverges by leveraging techniques used in code coverage analysis.
+Moreover, \pytracer's visualization interface remains responsive even with traces of up to 1TB.
+In our experiments, \pytracer enabled the systematic evaluation of 40 examples from the SciPy and scikit-learn libraries.
+
+In future work, we plan to extend the post-processing analysis to aggregate traces when the execution flow path diverges by leveraging techniques used in code coverage analysis.
 Moreover, we would like to extend \pytracer to instrument elementary arithmetic operations which can be helpful to more profound analyses.
-Finally, although \pytracer is flexible on the noise model used, we only tested it with the Monte Carlo Arithmetic.
+Finally, although \pytracer supports multiple noise models, we only tested it with Monte Carlo Arithmetic.
 Therefore, we would like to compare different models against MCA.

### 2021-12-21 paper.tex
Final version

@@
 Numerical stability is a crucial requirement of reliable scientific computing.
-However, despite the pervasiveness of Python in data science, analyzing large Python programs remains challenging due to the lack of scalable numerical analysis tools available\gkmod{ for this language}{}.
-\gkmod{}{To fill this gap,}we developed \pytracer, a profiler to quantify numerical instability in Python applications.
-\pytracer \gkmod{automatically}{transparently?} instruments Python code to produce numerical traces and visualize them interactively in a Plotly dashboard.
-We designed \pytracer to \gkmod{work with any}{be agnostic to} numerical noise model \gkmod{including}{, allowing for tool evaluation through} Monte-Carlo Arithmetic, random rounding \gkmod{or}{,} random data perturbations\gkmod{}{, or structured noise for a particular application}.
-We illustrate \pytracer's capabilities by testing the numerical stability of key functions in \gkmod{the}{both} SciPy and Scikit-learn \gkmod{}{, two dominant} Python libraries \gkmod{}{for mathematical modeling}.
-Through these evaluations, we demonstrate \pytracer as a scalable, automatic, and generic framework for numerical \gkmod{evaluations}{profiling} in Python.
+However, despite the pervasiveness of Python in data science, analyzing large Python programs remains challenging due to the lack of scalable numerical analysis tools available for this language.
+To fill this gap, we developed \pytracer, a profiler to quantify numerical instability in Python applications.
+\pytracer transparently instruments Python code to produce numerical traces and visualize them interactively in a Plotly dashboard.
+We designed \pytracer to be agnostic to numerical noise model , allowing for tool evaluation through Monte-Carlo Arithmetic, random rounding, random data perturbation, or structured noise for a particular application.
+We illustrate \pytracer's capabilities by testing the numerical stability of key functions in both SciPy and Scikit-learn, two dominant Python libraries for mathematical modeling.
+Through these evaluations, we demonstrate \pytracer as a scalable, automatic, and generic framework for numerical profiling in Python.
 % Numerical stability is a crucial requirement of reliable scientific computing.
@@
 
-The scientific Python ecosystem \gkmod{is}{has become} a central component of data
-analyses \gkmod{}{in recent years,} owing to its rich offering of data manipulation, array programming,
+The scientific Python ecosystem has become a central component of data
+analyses in recent years, owing to its rich offering of data manipulation, array programming,
 numerical analysis, and visualization tools. In particular, libraries such
-as NumPy~\cite{harris2020array}, SciPy~\cite{virtanen2020scipy}, scikit-learn~\cite{pedregosa2011scikit} or PyTorch~\cite{paszke2019pytorch} are used in hundreds of publications \gkmod{every}{each} year, \gkmod{providing}{and serve as} a reference set of high-quality open-source core scientific libraries.
-Researchers have built numerous domain-specific software tools from this ecosystem, leveraging Python's simplicity and \gkmod{expressivity}{flexibility}.
+as NumPy~\cite{harris2020array}, SciPy~\cite{virtanen2020scipy}, scikit-learn~\cite{pedregosa2011scikit} or PyTorch~\cite{paszke2019pytorch} are used in hundreds of publications each year, and serve as a reference set of high-quality open-source core scientific libraries.
+Researchers have built numerous domain-specific software tools from this ecosystem, leveraging Python's simplicity and flexibility.
 
@@
 processing.
-In unstable analyses, small numerical perturbations introduced by data noise, software and hardware updates, or parallelization \gkmod{lead to}{have potential to introduce} substantial deviations in final results, \gkmod{and}{leading to} potentially different scientific conclusions, \gkmod{ultimately} threatening the reliability of computational analyses.
-To \gkmod{address}{prevent} this \gkmod{issue}{}, numerical stability analyses need to be conducted systematically, however, no practical tool currently exists to conduct such analyses for Python programs.
-
-We present PyTracer, a numerical stability \gkmod{analyzer}{profiling and visualization tool} for Python programs.
+In unstable analyses, small numerical perturbations introduced by data noise, software and hardware updates, or parallelization have potential to introduce substantial deviations in final results, leading to potentially different scientific conclusions, ultimately threatening the reliability of computational analyses.
+To prevent this, numerical stability analyses need to be conducted systematically, however, no practical tool currently exists to conduct such analyses for Python programs.
+
+We present PyTracer, a numerical stability profiling and visualization tool for Python programs.
 \pytracer adopts a dynamic approach that evaluates numerical stability using program execution traces, and is applicable to large programs without manual intervention.
-\gkmod{}{The transparent nature of \pytracer is particularly valuable} in contrast \gkmod{}{to} theoretical approaches based on condition numbers or backward error analysis\gkmod{}{, which} require detailed modeling of the program and its numerical implementation.
-Similarly, static code analysis techniques hardly scale to large codebases, particularly in dynamically-typed languages such as Python.
+The transparent nature of \pytracer is particularly valuable in contrast to theoretical approaches based on condition numbers or backward error analysis, which require detailed modeling of the program and its numerical implementation.
+Similarly, static code analysis techniques hardly scale to large code bases, particularly in dynamically-typed languages such as Python.
 
@@
 
+This manuscript presents the design of \pytracer and demonstrates its potential in various use cases. 
 Through stability evaluations of the
 SciPy and scikit-learn libraries, we demonstrate \pytracer as a practical solution to review the numerical stability of extensive code bases. 
-This manuscript describes related approaches, presents the design of \pytracer, and demonstrates its potential in various use cases.
-
-\section{Background and related work}
-
-Several tools have been developed to assess numerical quality, \gkmod{}{and can be} divided into static and dynamic approaches.
-Static approaches typically analyze source code, while dynamic approaches trace floating-point computations throughout executions.
-A detailed review of these approaches is presented in~\cite{cherubin2020tools}.
-\pytracer adopts the dynamic approach due to its scalability to large \gkmod{existing}{} code bases.
-Dynamic approaches typically trace floating-point computations, detect instabilities in traces, and visualize summary statistics about instabilities.
-This section reviews existing approaches for each of these steps.
-
-% In this section, we review tools and theoretical frameworks related to \pytracer components.
-% We start by reviewing state-of-the-art dynamic tools for detecting numerical instabilities.
-% Then, we focus on existing theoretical approaches for perturbations-based techniques to detect numerical instabilities,
-% \pytracer being agnostic to perturbation technique used. Finally, we review visualization tools 
-% aiming at detecting numerical instabilities over execution time.
-
-\label{sec:soa}
-\subsection{Numerical tracing techniques}
-Numerous tools exists to trace floating-point computations for C, C++, or FORTRAN programs due to the prevalence of these languages in High-Performance Computing (HPC). 
-The main tracing techniques are \textit{source-to-source}, \textit{compiler-based transformations}, and \textit{dynamic binary instrumentation}.
-
-\gkmod{}{Note: this paragraph just reads like a list with no real interpretation/commentary.
-I think it would be better to state the strengths of this technique, cite examples, and then state limitations/why it isn't the only technique used.}
-The source-to-source technique requires a rewriting of the application to modify floating-point types. 
-CADNA~\cite{jezequel2008cadna} is a library for C, C++, and Fortran implementing \gkmod{the}{} CESTAC~\cite{vignes1993stochastic} stochastic arithmetic.
-Shaman~\cite{demeure_phd} is a C++ library that uses a first-order error model to propagate numerical error.
-MCAlib~\cite{frechtling2015mcalib} is a C library that implements the Monte Carlo Arithmetic (MCA)~\cite{parker1997monte} using the MPFR~\cite{fousse2007mpfr} library.
-Finally, the work in~\cite{tang2016software} proposed a source-to-source framework for executing targeted code in infinite and fixed precision with and without  stochastic arithmetic.
-
-\gkmod{}{Note: similar to the above, this is just a list rather than a highlight of how the compiler-based approach can be more scalable than source-to-source because it requires less manual intervention into a codebase (e.g.), then have your list, and finally say why it is still limited/not a global fix to this problem.}
-The compiler-based approach instruments floating-point expressions at compile time. 
-Verificarlo~\cite{verificarlo} is a compiler that supports different types of arithmetic instrumentations, including MCA. 
-The work in~\cite{bao2013fly} modified the GNU Compiler Collection (GCC) to track local floating-point errors across executions.
-pLiner~\cite{guo2020pliner} is a root-cause analyzer based on the Clang compiler that detects floating-point operations responsible for result variability using a source-to-source transformation at the Abstract Syntax Tree (AST) level to rewrite parts of code with higher precision.
-PFPSanitizer~\cite{chowdhary2020debugging,chowdhary2021parallel} is a compiler that uses parallel shadow execution to detect numerical issues using higher precision.
-FLiT~\cite{sawaya2017flit} is a framework to detect variability induced by compilers and their optimizations.
-The work in~\cite{wang2012development} proposes a numerical debugger based on GDB~\cite{stallman1988debugging} for Discrete Stochastic Arithmetic (DSA) on FPGA as an Eclipse plugging.
-Similarly, Cadtrace~\cite{jezequel2008cadna} and Shaman propose a GDB-based tool to use the CADNA and Shaman libraries with GDB, respectively.
-
-Dynamic Binary Instrumentation (DBI) operates directly on executables, without the need for recompilation or manual changes. Therefore, it is applicable to any programming language.
-CraftHPC~\cite{lam2013dynamic} uses DBI to detect catastrophic cancellations at runtime.
-Verrou~\cite{fevotte2016verrou} is a Valgrind~\cite{nethercote2007valgrind} based tool that dynamically replaces
-floating-point operations with their stochastic arithmetic counterparts. FPDebug~\cite{benz2012dynamic} uses DBI to detect numerical inaccuracies by using shadow computations with higher precision.
-Herbgring~\cite{sanchez2017finding} is a Valgrind-based tool to detect
-numerical instabilities.
-It uses a shadow memory to detect precision losses by comparison with results obtained at higher precision.
-It is combined with symbolic computation to backtrack the root of the error.
-We can note that all methods based on a high-precision oracle suppose that computing with a large number of bits is sufficient to obtain an accurate result, which is not always true (see for example, the famous Muller's sequence~\cite{bajard1996introduction}).
-%\tristan{it looks like your veritracer paper is the first time where the ``famous Muller's sequence" was described, is that so?}).
-
-\gkmod{}{Note: I like this comparison here, but do think that the comments above about providing some more info when each is mentioned would still help this section.}
-Being agnostic to the programming language is a serious advantage of the DBI method compared to source-to-source and compiler-bases methods.
-However, working at the binary level makes it difficult to access high-level information needed to debug and understand the source-code logic.
-Conversely, the source-to-source approach provides a fine-grained control on the analyzed code, but it lacks scalability, as rewriting large codes can be a tedious task.
-Finally, the compiler-based approach takes advantage of the best of both by being automatic and having access to high-level information.
-However, like source-to-source, the compiler-based method is not suitable for analyzing closed-source libraries.
-
-To the best of our knowledge, there is currently no tool dedicated to the numerical analysis of Python code. Existing tools for tracing Python code focus on performance profiling for time (cProfile) 
-or memory consumption (memprofile). 
-Anteater~\cite{faust2019anteater} is a Python tracer tool to debug Python applications. 
-It performs source transformations at the AST level but only deals with native numeric Python types.
-Moreover, the user needs to manually tag each variable to trace. Finally, according to the authors, Anteater does not scale to large traces.
-cProfile, memprofile, and Anteater use Python decorators as the primary instrumentation technique, a Python mechanism to instrument a function by adding a line over a function declaration.
-While this method is appropriate when targeting specific functions, it is not feasible for large codebases where potentially unstable code sections are unknown.
-
-\label{sec:detecting-instabilities}
-\subsection{Detecting numerical instabilities with stochastic arithmetic}
-\label{sec:mca}
-
-% We review here the existing theoretical framework that might be used to detect numerical instabilities.
-% Our experiments rely on the Monte Carlo Arithmetic (MCA), a stochastic arithmetic allowing 
-% to detect numerical errors by adding random perturbations in the floating-point computations.
-% However, Pytracer do not rely on any assumption about the perturbation model used and thus leaves the user free to use
-% an alternative model. As such, we describe two others options that we thought might be beneficial and complementary to MCA: 
-% input data uncertainty analysis and random seed sensitivity.
-
-% \subsubsection{Stochastic Arithmetic}
-
-% The Monte Carlo Arithmetic is a variant of so-called stochastic arithmetic, whose purpose is to model round-off errors by a random variable.
-
-Three main approaches exist to detect numerical instabilities: stochastic arithmetic, uncertainty or sensitivity analysis~\cite{helton2006survey}, and random seed analysis~\cite{click2011quality}.
-%\tristan{add key references for uq/sa if any}
-\pytracer focuses on stochastic arithmetic since it does not make any assumption about 
-the noise model, in contrast to sensitivity analysis.
-\gkmod{}{Q: isn't \pytracer agnostic to noise model/method for instability detection?
-Can't we just re-run the tool multiple times under whatever model for detecting instabilities that we choose and it will work all the same?
-If so, then I may reword this to say that pytracer works for all, and for our usecases here we use SA because X, Y, and Z...}
-%\tristan{due to...}
-Stochastic arithmetic leverages randomness to estimate numerical instabilities coming from the use of floating-point representations. The main idea is to treat round-off errors 
-% \tristan{only round-off errors or all numerical errors?} 
-as random variables and characterize them statistically.
-
-The first published complete stochastic arithmetic framework was CESTAC~\cite{vignes1993stochastic}.
-In CESTAC, each floating-point computation is performed multiple times with different rounding modes: round-up or round-down.
-From these stochastic samples, one can then derive the number of significant digits in the computed result.
-Discrete Stochastic Arithmetic~\cite{vignes2004discrete} extends CESTAC with comparison operators implemented in the CADNA library.
-
-Monte Carlo Arithmetic (MCA)~\cite{parker1997monte} uses the same principle but introduces two differences:
-(i) a virtual precision parameter, allowing to simulate reduced working precision, and (ii) different perturbation modes to introduce perturbations
-on function inputs or output.
-MCA replaces each floating-point number $x$ with a stochastic counterpart computed as:
-\[
-inexact(x) =  x + \beta^{e_x - t}\xi
-\]
-where $\beta$ is the number base, $e_x$ is the magnitude of $x$, $t$ the virtual precision and $\xi \in (-\frac{1}{2},\frac{1}{2})$ is a random uniform variable.
-Virtual precision allows for the simulation of reduced working precision.
-MCA can be applied in three modes: Random Rounding (RR), Precision Bounding (PB), and full MCA, which apply function $inexact$ to the output, the inputs, or both, respectively.
-While the RR mode is equivalent to stochastic rounding, the PB mode can also identify catastrophic cancellations.
-
-Stochastic arithmetic quantifies numerical error using the number of significant digits $s$ estimated among the sampled values.
-A common formula to determine this number from MCA samples is \gkmod{the one reported}{presented} in~\cite{parker1997monte}:
-\begin{equation}
-s = -\log_{\beta}{ \left| \dfrac{\sigma}{\mu} \right|} \label{eq:sig-digits}
-\end{equation}
-where $\mu$ and $\sigma$ are the sample mean and standard deviation of a variable sampled with MCA.  
-Sohier et al.~\cite{sohier2018confidence} recently provided a generalization of this formula to include confidence intervals.
-
-% \subsubsection{Uncertainty, sensitivity, and random seed analysis}
-% \tristan{I'm wondering if we could remove this sub-section, as it doesn't seem to be critical to the understanding of the paper, wdyt?}
-% Uncertainty analysis (UA) is a method to estimate the output distribution given an input distribution.
-% Sensitivity analysis (SA) is a variation of UA that measures the local response to a small perturbation~\cite{loucks2017water}. 
-% Several approaches for UA and SA exist, among them differential analysis, response surface methodology, Monte Carlo analysis, and variance decomposition (see~\cite{helton2006survey} for a review).
-In particular, Monte Carlo analysis is a sampling-based technique that samples inputs space to estimate output response.
-Monte Carlo analysis shares similarities with Monte Carlo Arithmetic.
-For instance, the PRECISE framework~\cite{chaitin1996lectures} shares with MCA the idea of varying virtual precision to estimate output sensitivity.
-
-% Furthermore, the quality of a Random Number Generator is a crucial characteristic when dealing with stochastic model and differ from cryptography requirements.
-A good RNG provides a tradeoff between performance, period, correlation, or uniformity~\cite{james2020review} for numerical simulation.
-% On the other hand, poor-quality RNGs may have a substantial impact on results~\cite{click2011quality}.
-First, measuring variation induced by seed is a good indicator of program stability that we can compare against variability induced by floating-point arithmetic.
-
-\subsection{Visualization}
-
-Visualization \gkmod{}{Note: You kind of jump right in to this section.
-Visualization of what in particular?
-Why do we want (need?) to visualize this sort of data?} covers a wide range of numerical simulation domains, from general-purpose numerical visualization with tools
-such as VTK~\cite{schroeder2000visualizing} to topological data analysis~\cite{tierny2018topological}, including matrix~\cite{wu2008matrix} or tensor~\cite{kindlmann2006diffusion} visualization.
-Despite the large number of existing tools to identify numerically unstable sections of source code, few allow the user to have a global view of the numerical precision of their computations or to compare several executions of the same program under various perturbations.
-
-Veritracer~\cite{chatelain2018veritracer} was the first tool to propose an embedded visualizer of numerical stability over the execution of C, C++, and Fortran code.
-Veritracer extends Verificarlo~\cite{verificarlo} with contextual information about traced variables, which allows the user to identify instabilities quickly.
-However, Veritracer neither offers a dynamic interface nor includes information about high-level structures such as \texttt{struct} or \texttt{array}.
-FPAvizual~\cite{gu2014fpavisual} visualizes the effects of floating-point arithmetic but only for educational purposes \gkmod{}{Q: What does this mean?}.
-Anteater~\cite{faust2019anteater} proposes a visualizer for Python code, but as mentioned previously, it only deals with native Python types, and the user needs to select variables to trace manually.
-Anteater provides an insightful reflection
-around visual debugging beyond floating-point analysis, which has inspired the design of \pytracer's visualization interface.
+%All information was obtained through \pytracer, visualized separately for improved customizability.
+%\tristan{this is a weird place to mention this ^^}
 
@@
 \pytracer adopts the three-step workflow shown in Figure~\ref{fig:workflow}.
-First, \pytracer uses \gkmod{monkey patching}{\textit{monkey patching}} to replace the functions called by the application with a wrapper that saves their arguments and returned values in a trace file \gkmod{}{Q: This is conceptually similar to a decorator, no?
-If so, perhaps it is worth mentioning}.
-Second, it injects noise in the application \gkmod{}{Q: \pytracer doesn't actually inject noise, does it?
-You can just run your tool however you want multiple times}, executes it multiple times, and aggregates the resulting trace files to compute summary statistics about each traced variable.
+First, \pytracer uses \textit{monkey patching} to replace the functions called by the application with a wrapper that saves their arguments and returned values in a trace file.
+% \gkmod{}{Q: This is conceptually similar to a decorator, no?
+If so, perhaps it is worth mentioning} \Yohan{Conceptually, monkey patching is the ability to dynamically change a class or a module.
+So it's more powerful than the decorators.
+But yes we use monkey-patching to automatically decorate the functions.}
+Second, it executes the application multiple times with noise injection, and aggregates the resulting trace files to compute summary statistics about each traced variable.
 Finally, a Plotly dashboard provides interactive visualizations highlighting unstable code sections.
@@
     \includegraphics[width=\linewidth]{figure/workflow.pdf}
-    \caption{Pytracer workflow \gkmod{}{Note: replace "Execution" with "Multiple Independent Executions", and maybe move it to be between the gears and the pkl files.}}
+    \caption{Pytracer workflow
+    % \gkmod{}{Note: replace "Execution" with "Multiple Independent Executions", and maybe move it to be between the gears and the pkl files.}
+    }
     \label{fig:workflow}
@@
 To do so, it creates a new, instrumented version of each module that preserves its original attributes so that the application can transparently use it.
-\gkmod{}{Note: this form of monkey patching is basically global and transparent decorating, right?}
+% \gkmod{}{Note: this form of monkey patching is basically global and transparent decorating, right?} \Yohan{Yes}
 By default, \pytracer instruments all the attributes
-in a given module except the special ones of the form \texttt{\_\_*\_\_}\gkmod{}{, which is common for reserved Python methods}.
+in a given module except the special ones of the form \texttt{\_\_*\_\_}, which is common for reserved Python methods.
 However, some attributes are not writable. In this case, \pytracer preservers the original attributes and warns the user. The user can also restrict the list of traced attributes through
@@
 In particular, NumPy's universal functions include
-vectorized elementary mathematical functions and other prevalent \gkmod{ones}{Q: prevalent whats?}. Universal functions are implemented in C, which prevents their modification.
+vectorized elementary mathematical and other prevalent functions. 
+%\gkmod{ones}{Q: prevalent whats?}.
+Universal functions are implemented in C, which prevents their modification.
 
 To overcome this issue, \pytracer wraps the class instance into a transparent wrap class (\texttt{twc}) that overloads
-1) function \texttt{\_\_getattribute\_\_}, called when an instance attribute is accessed --- instrumented to return the attributes from the original class, and 2) function \texttt{\_\_call\_\_}, called when the function is called through the () operator --- instrumented with function \texttt{generic\_wrapper}.
-\gkmod{}{Note: the previous sentence is a bit hard to follow; the word "called" is used a lot so I got a bit lost.} The \texttt{twc} returns the queried attribute of the instance instead of returning its attributes, allowing transparent access to the instance.
+1) function \texttt{\_\_getattribute\_\_}, called when an instance attribute is accessed --- instrumented to return the attributes from the original class, and 2) function \texttt{\_\_call\_\_}, used when an instance behaves like a function through the () operator --- instrumented with function \texttt{generic\_wrapper}.
+% \gkmod{}{Note: the previous sentence is a bit hard to follow; the word "called" is used a lot so I got a bit lost.}
+The \texttt{twc} returns the queried attribute of the instance instead of returning its attributes, allowing transparent access to the instance.
 Finally, \pytracer overloads the builtin \texttt{type} function to preserve the type of the wrapped instance.
@@
 
+Three  main  approaches  exist  to  detect  numerical  instabilities:  stochastic  arithmetic,  uncertainty  or  sensitivity analysis [23], and random seed analysis [11].
+PyTracer is agnostic to the noise model used and therefore works for all methods mentioned.
+For our use cases, we focus on stochastic arithmetic since it does not make any assumption about the noise model, in contrast to sensitivity analysis
+
+Stochastic arithmetic leverages randomness to estimate numerical instabilities coming from the use of floating-point representations.
+The main idea is to treat round-off errors as random variables and characterize them statistically.
+Monte Carlo Arithmetic (MCA)~\cite{parker1997monte} uses this principle by introducing two improvements:
+(i) a virtual precision parameter, allowing to simulate reduced working precision, and (ii) different perturbation modes to introduce perturbations
+on function inputs or output.
+MCA replaces each floating-point number $x$ with a stochastic counterpart computed as:
+\[
+inexact(x) =  x + \beta^{e_x - t}\xi
+\]
+where $\beta$ is the number base, $e_x$ is the magnitude of $x$, $t$ the virtual precision and $\xi \in (-\frac{1}{2},\frac{1}{2})$ is a random uniform variable.
+Virtual precision allows for the simulation of reduced working precision.
+MCA can be applied in three modes: Random Rounding (RR), Precision Bounding (PB), and full MCA, which apply function $inexact$ to the output, the inputs, or both, respectively.
+While the RR mode is equivalent to stochastic rounding, the PB mode can also identify catastrophic cancellations.
+
+Stochastic arithmetic quantifies numerical error using the number of significant digits $s$ estimated among the sampled values.
+A common formula to determine this number from MCA samples is presented in~\cite{parker1997monte}:
+\begin{equation}
+s = -\log_{\beta}{ \left| \dfrac{\sigma}{\mu} \right|} \label{eq:sig-digits}
+\end{equation}
+where $\mu$ and $\sigma$ are the sample mean and standard deviation of a variable sampled with MCA.  
+Sohier et al.~\cite{sohier2018confidence} recently provided a generalization of this formula to include confidence intervals.
+
 We enable MCA in Python programs via Verificarlo~\cite{verificarlo}, a clang-based compiler~\cite{lattner2008llvm} that replaces floating-point operations by a generic call to a configurable floating-point model.
@@
 \pytracer saves these summary statistics in an HDF5 file, a hierarchical format that facilitates visual browsing since only
-required information are loaded when requested by the user. \gkmod{}{Q: Is there a reason we don't also use HDF for the raw traces? Lack of native compression?}
+required information are loaded when requested by the user.
+% \gkmod{}{Q: Is there a reason we don't also use HDF for the raw traces? Lack of native compression?} \Yohan{Principaly because you can't save any Python objects in HDF5 while you can with Pickle}
 This operation critically relies on the ordering of call input and output objects in the traces.
@@
 The third main component of \pytracer is its interactive trace visualizer built with Plotly Dash~\cite{plotly}, a Python framework for web visualization.
-Plotly Dash abstracts the low-level details of web applications in a highly customizable development interface allowing to offload heavy computations to a server \gkmod{}{Q: does it support using a remote server with forwarding, in the event that your local system isn't that beefy?}.
+Plotly Dash abstracts the low-level details of web applications in a highly customizable development interface allowing to offload heavy computations to a server if necessary.
+% \gkmod{}{Q: does it support using a remote server with forwarding, in the event that your local system isn't that beefy?} \Yohan{Yes, that the meaning of the sentence. Should we reword it?}
 Figure~\ref{fig:visu-layout} presents the general layout of the \pytracer visualizer, divided into five sub-components:
@@
 By default, \pytracer shows the number of significant digits computed across the traces.
-The user can switch to the mean or the standard deviation \gkmod{}{Q: mean/stdev of what?
+The mean and standard deviation across perturbed samples are also available.
+%  \gkmod{}{Q: mean/stdev of what?
 the inputs/outputs?
@@
 log(0.0001)}.
+\Yohan{All values, a value mean one input or one output.
+For different scale, you can switch to the log scale.
+It is worth mentioning it?}
  The visualizer uses an upper triangle for inputs and a lower triangle for outputs.
@@
 Each variable is prefixed with the original value and postfixed with the name of the parameter.
-\gkmod{}{Q: how is this managed for the sake of interpretability?
+%  \gkmod{}{Q: how is this managed for the sake of interpretability?
 E.g.
-if one of the components has very low significance and another few are fine, how can I easily identify where in my sequence we have the drop in precision?}
+if one of the components has very low significance and another few are fine, how can I easily identify where in my sequence we have the drop in precision?} \Yohan{You can click on the value of interest in the legend and it will hide the others.
+}
     Finally, non-scalar values (vectors or matrices) are represented by their average and can be inspected with the Zoom view (see below).
@@
     This view provides insights on the calling context for each function, which may influence numerical stability.
-\gkmod{}{Note: this is a non-standard layout for gantt charts...
+    % \gkmod{}{Note: this is a non-standard layout for gantt charts...
 normally the width/overlap is determined by time of start + duration.
@@
 If not, will a very fast function that calls sub-functions, say, 1000 times look longer than a very slow function that doesn't call any subfunctions?}
- \item  Source code view: This view displays \gkmod{}{a local snapshot of} the source code file of the variable hovered in the timeline view. 
+    % \Yohan{I don't keep the duration because the different traces may have different time execution profiles and it will not make sense to average times.
+Moreover, since we focus on the numerical stability and not on performance, we only care about the call order.
+Yes it will look longer because the unit of the X-axis is the invocation, not the time.}
+ \item  Source code view: This view displays a local snapshot of the source code file of the variable hovered in the timeline view. 
  \item Zoom view: This view provide details about non-scalar values. For example, a matrix may have instabilities around its diagonal but not in other regions.
@@
 We used the default virtual precision in Verificarlo, namely 24 bits for single-precision floating-point values and 53 bits for double-precision values, which simulates machine error.
-We used Python-3.8.5, NummPy-1.19.1, SciPy-1.5.4, and scikit-learn-0.23.2.
+We used Python-3.8.5, NumPy-1.19.1, SciPy-1.5.4, and scikit-learn-0.23.2.
 %  \tristan{Report scipy and sklearn versions used.}
@@
 \pytracer's outcome on SciPy and scikit-learn examples.
-Columns \textit{trace} and \textit{parse} report on the tracing and aggregation steps with three possible outcomes: green for success, red for numerical error in the application, and orange for errors due to the fuzzy noise injection
-that are not considered numerical errors. \gkmod{}{Q: What does "success" or the other labels actually mean? What is the threshold for numerical errors, e.g.}
+Columns \textit{trace} and \textit{parse} report on the tracing and aggregation steps with three possible outcomes: 1) green for success, meaning that the execution ended well and no issues were raised by the application, 2) red for numerical error in the application, meaning that the execution raised a Python error before the end, and 3) orange for errors due to the fuzzy noise injection that are not considered numerical errors, meaning that the execution raised a Python error but due to a perturbation that should not have been introduced (i.e.
+a floating-point value representing an integer).
+% \gkmod{}{Q: What does "success" or the other labels actually mean? What is the threshold for numerical errors, e.g.}
 % , like for instance index errors due to an index shift.
 % \tristan{Explain what this is, in a setence here or with a subsubsection if it requires more}. 
-Overall, the tracing and parsing of SciPy and scikit-learn examples in Random Rounding mode was entirely successful \gkmod{}{, indicating on average XX loss in numerical precision,} for 32/40 examples.
+Overall, the tracing and parsing of SciPy and scikit-learn examples in Random Rounding mode was entirely successful for 32/40 examples and showed an average precision loss of 8 bits.
 The remaining examples failed due to numerical errors in the libraries, which we discuss hereafter.
-The instrumentation with Full MCA is more invasive and reduced the number of successful \gkmod{}{Q: Does this mean the 28 failed, or completed but poorly?
-In general, the way the states are being referred to so far in the results are rather ambiguous} executions to 12/40.
+The instrumentation with Full MCA is more invasive and reduced the number of successful executions to 12/40.
+Among the 28/40 failed executions, one failed due to an actual numerical error (\texttt{Bayesian Ridge Regression} example) and the other ones failed due to
+perturbations that should not have been introduced.
+% \tristan{finish this sentence}.
+% \gkmod{}{Q: Does this mean the 28 failed, or completed but poorly? In general, the way the states are being referred to so far in the results are rather ambiguous}
 
 Column \textit{sigbits} in Table~\ref{tab:pytracer_results_summary} summarizes the precision for the main outputs of SciPy and scikit-learn examples. 
-We measured the precision in significant bits on the \gkmod{main}{final primary} example output by taking the element-wise mean for non-scalar values and, if the example produces many outputs, the average value among all of them.
+We measured the precision in significant bits on the final primary example output by taking the element-wise mean for non-scalar values and, if the example produces many outputs, the average value among all of them.
 The numerical quality across all examples varies from 0 to 52, with an average of 44 significant bits.
@@
 % \tristan{can we see that in the table? if not, don't comment on it, it is puzzling. Could you show that in the table by using the same error symbols as in Table 2?} 
-(\texttt{face\_recognition} for RR and \texttt{Bayesian Ridge Regression} for Full MCA) even though this number is underestimated since Full MCA mode is more intrusive than RR mode and most of the examples produce error caused by the fuzzy noise injection.
-\gkmod{}{Note: I don't understand what is being said in the rest of the sentence following the parentheses}
+(\texttt{face\_recognition} for RR and \texttt{Bayesian Ridge Regression} for Full MCA).
+% even though this number is underestimated since Full MCA mode is more intrusive than RR mode.
+% Indeed, most of the examples produce an error caused by the fuzzy noise injection.
+\gkmod{}{Note: I don't understand what is being said in the rest of the sentence following the parentheses} \Yohan{Full MCA mode perturbs values that should not be perturbed and so
+% it triggers artificial bugs (as for numpy arange)}
 
@@
 are due to this type of ``typing" errors.  
-Those code regions should not be perturbed by MCA since the injected noise does not make sense\gkmod{}{; however, given the typing errors in the source code, they are still susceptible to naturally occurring floating point errors}.
+Those code regions should not be perturbed by MCA since the injected noise does not make sense.
+% \gkmod{}{; however, given the typing errors in the source code, they are still susceptible to naturally occurring floating point errors}.
+\Yohan{Not really since all rounding cases were carefully handled by the developers.
+We are facing here the same issue as for libmath:
+% people take into account the possible rounding outcomes and the code is written knowing that
+% the floating-point numbers behave like that. We break the assumptions by introducing noise here.}
 % \tristan{conclusion: ces regions du code ne devraient pas etre bruitees car le bruit n'a pas de sens ici (exemple du spin dans -1/2,1/2. Ca correspond aux ?}
@@
 
+\section{Related work}
+
+Several tools have been developed to assess numerical quality, and can be divided into static and dynamic approaches.
+Static approaches typically analyze source code, while dynamic approaches trace floating-point computations throughout executions.
+A detailed review of these approaches is presented in~\cite{cherubin2020tools}.
+% \pytracer adopts the dynamic approach due to its scalability to large code bases.
+Dynamic approaches typically trace floating-point computations, detect instabilities in traces, and visualize summary statistics about instabilities.
+This section reviews existing approaches for each of these steps.
+% \label{sec:soa}
+% \paragraph{Numerical tracing techniques}
+Numerous tools exists to trace floating-point computations for C, C++, or FORTRAN programs due to the prevalence of these languages in High-Performance Computing (HPC). 
+The main tracing techniques are \textit{source-to-source}, \textit{compiler-based transformations}, and \textit{dynamic binary instrumentation}.
+
+% \gkmod{}{Note: this paragraph just reads like a list with no real interpretation/commentary.
+I think it would be better to state the strengths of this technique, cite examples, and then state limitations/why it isn't the only technique used.}
+The source-to-source technique requires a rewriting of the application to modify floating-point types and provides a fine-grained control on the analyzed code.
+CADNA~\cite{jezequel2008cadna} is a library for C, C++, and Fortran implementing  
+CESTAC~\cite{vignes1993stochastic} stochastic arithmetic. Shaman~\cite{demeure_phd} is a C++ library that uses a first-order error model to propagate numerical error. 
+MCAlib~\cite{frechtling2015mcalib} is a C library that implements the Monte Carlo Arithmetic (MCA)~\cite{parker1997monte} using the MPFR~\cite{fousse2007mpfr} library.
+Finally, the work in~\cite{tang2016software} proposed a source-to-source framework for executing targeted code in infinite and fixed precision with and without stochastic arithmetic.
+The main drawback of the source-to-source approach is its lacks of scalability since rewriting large codes can be a tedious task.
+
+% \gkmod{}{Note: similar to the above, this is just a list rather than a highlight of how the compiler-based approach can be more scalable than source-to-source because it requires less manual intervention into a codebase (e.g.), then have your list, and finally say why it is still limited/not a global fix to this problem.}
+
+The compiler-based approach instruments floating-point expressions at compile time
+and so allows the user to automatically instrument large codebases.
+Verificarlo~\cite{verificarlo} is a compiler that supports different types of arithmetic instrumentations, including MCA. 
+The work in~\cite{bao2013fly} modified the GNU Compiler Collection (GCC) to track local floating-point errors across executions.
+pLiner~\cite{guo2020pliner} is a root-cause analyzer based on the Clang compiler that detects floating-point operations responsible for result variability using a source-to-source transformation at the Abstract Syntax Tree (AST) level to rewrite parts of code with higher precision.
+PFPSanitizer~\cite{chowdhary2020debugging,chowdhary2021parallel} is a compiler that uses parallel shadow execution to detect numerical issues using higher precision.
+FLiT~\cite{sawaya2017flit} is a framework to detect variability induced by compilers and their optimizations.
+The work in~\cite{wang2012development} proposes a numerical debugger based on GDB~\cite{stallman1988debugging} for Discrete Stochastic Arithmetic (DSA) on FPGA as an Eclipse plugging.
+Similarly, Cadtrace~\cite{jezequel2008cadna} and Shaman propose a GDB-based tool to use the CADNA and Shaman libraries with GDB, respectively.
+The main limitation of the compiler-based approach is that one must have access to the source code.
+
+Dynamic Binary Instrumentation (DBI) operates directly on executables, without the need for recompilation or manual changes. Therefore, it is applicable to any programming language.
+CraftHPC~\cite{lam2013dynamic} uses DBI to detect catastrophic cancellations at runtime.
+Verrou~\cite{fevotte2016verrou} is a Valgrind~\cite{nethercote2007valgrind} based tool that dynamically replaces
+floating-point operations with their stochastic arithmetic counterparts. FPDebug~\cite{benz2012dynamic} uses DBI to detect numerical inaccuracies by using shadow computations with higher precision.
+Herbgring~\cite{sanchez2017finding} is a Valgrind-based tool to detect
+numerical instabilities.
+It uses a shadow memory to detect precision losses by comparison with results obtained at higher precision.
+It is combined with symbolic computation to backtrack the root of the error.
+We can note that all methods based on a high-precision oracle suppose that computing with a large number of bits is sufficient to obtain an accurate result, which is not always true (see for example, the famous Muller's sequence~\cite{bajard1996introduction}).
+Although versatile, the DBI looses high-level information useful to understand the source-code logic.
+
+% \gkmod{}{Note: I like this comparison here, but do think that the comments above about providing some more info when each is mentioned would still help this section.}
+Being agnostic to the programming language is a serious advantage of the DBI method compared to source-to-source and compiler-bases methods.
+However, working at the binary level makes it difficult to access high-level information needed to debug and understand the source-code logic.
+Conversely, the source-to-source approach provides a fine-grained control on the analyzed code, but it lacks scalability, as rewriting large codes can be a tedious task.
+Finally, the compiler-based approach takes advantage of the best of both by being automatic and having access to high-level information.
+However, like source-to-source, the compiler-based method is not suitable for analyzing closed-source libraries.
+
+To the best of our knowledge, \pytracer is the first tool dedicated to the numerical analysis of Python code. Existing tools for tracing Python code focus on performance profiling for time (cProfile) 
+or memory consumption (memprofile). 
+Anteater~\cite{faust2019anteater} is a Python tracer tool to debug Python applications. 
+It performs source transformations at the AST level but only deals with native numeric Python types.
+Moreover, the user needs to manually tag each variable to trace. Finally, according to the authors, Anteater does not scale to large traces.
+cProfile, memprofile, and Anteater use Python decorators as the primary instrumentation technique, a Python mechanism to instrument a function by adding a line over a function declaration.
+While this method is appropriate when targeting specific functions, it is not feasible for large codebases where potentially unstable code sections are unknown.
+
+% \label{sec:detecting-instabilities}
+% \paragraph{Dynamically detecting numerical instabilities}
+% \label{sec:mca}
+% :
+%  \Yohan{Either detail this section with UA/SA or remove it since MCA is introduced in 'noise injection' subsection.
+} \tristan{I agree, let's just remove it, the core of the contribution is on the tracing, not in the detection of instabilities.}
+
+% % We review here the existing theoretical framework that might be used to detect numerical instabilities.
+% % Our experiments rely on the Monte Carlo Arithmetic (MCA), a stochastic arithmetic allowing 
+% % to detect numerical errors by adding random perturbations in the floating-point computations.
+% % However, Pytracer do not rely on any assumption about the perturbation model used and thus leaves the user free to use
+% % an alternative model. As such, we describe two others options that we thought might be beneficial and complementary to MCA: 
+% % input data uncertainty analysis and random seed sensitivity.
+
+% % \subsubsection{Stochastic Arithmetic}
+
+% % The Monte Carlo Arithmetic is a variant of so-called stochastic arithmetic, whose purpose is to model round-off errors by a random variable.
+
+% Three main approaches exist to detect numerical instabilities dynamically: stochastic arithmetic, uncertainty or sensitivity analysis~\cite{helton2006survey}, and random seed analysis~\cite{click2011quality}.
+% Stochastic arithmetic leverages randomness to estimate numerical instabilities coming from the use of floating-point representations.
+The main idea is to treat round-off errors as random variables and characterize them statistically.
+% The first published complete stochastic arithmetic framework was CESTAC~\cite{vignes1993stochastic}.
+In CESTAC, each floating-point computation is performed multiple times with different rounding modes: round-up or round-down.
+From these stochastic samples, one can then derive the number of significant digits in the computed result.
+Discrete Stochastic Arithmetic~\cite{vignes2004discrete} extends CESTAC with comparison operators implemented in the CADNA library.
+% Monte Carlo Arithmetic (MCA)~\cite{parker1997monte} uses the same principle but introduces two differences:
+% (i) a virtual precision parameter, allowing to simulate reduced working precision, and (ii) different perturbation modes to introduce perturbations
+% on function inputs or output.
+% Stochastic arithmetic quantifies numerical error using the number of significant digits $s$ estimated among the sampled values.
+A common formula to determine this number from MCA samples is presented in~\cite{parker1997monte}.
+% Sohier et al.~\cite{sohier2018confidence} recently provided a generalization of this formula to include confidence intervals.
+
+% % \subsubsection{Uncertainty, sensitivity, and random seed analysis}
+% % \tristan{I'm wondering if we could remove this sub-section, as it doesn't seem to be critical to the understanding of the paper, wdyt?}
+% % Uncertainty analysis (UA) is a method to estimate the output distribution given an input distribution.
+% % Sensitivity analysis (SA) is a variation of UA that measures the local response to a small perturbation~\cite{loucks2017water}. 
+% % Several approaches for UA and SA exist, among them differential analysis, response surface methodology, Monte Carlo analysis, and variance decomposition (see~\cite{helton2006survey} for a review).
+In particular, Monte Carlo analysis is a sampling-based technique that samples inputs space to estimate output response.
+Monte Carlo analysis shares similarities with Monte Carlo Arithmetic.
+For instance, the PRECISE framework~\cite{chaitin1996lectures} shares with MCA the idea of varying virtual precision to estimate output sensitivity.
+
+% % Furthermore, the quality of a Random Number Generator is a crucial characteristic when dealing with stochastic model and differ from cryptography requirements.
+A good RNG provides a tradeoff between performance, period, correlation, or uniformity~\cite{james2020review} for numerical simulation.
+% On the other hand, poor-quality RNGs may have a substantial impact on results~\cite{click2011quality}.
+First, measuring variation induced by seed is a good indicator of program stability that we can compare against variability induced by floating-point arithmetic.
+
+% \paragraph{Visualization of numerical data}
+% \tristan{now that it's here, I'm not sure if this section really adds to the paper. It could also go.}
+
+% Floating-point values approximate real number in the computer arithmetic but
+% data manipulated by scientific applications include a large variety of mathematical objects
+% beyond scalar values. 
+% Indeed, scientific visualization 
+% \gkmod{}{Note: You kind of jump right in to this section. Visualization of what in particular? Why do we want (need?) to visualize this sort of data?} 
+% covers a wide range of numerical simulation domains, from general-purpose numerical visualization with tools such as VTK~\cite{schroeder2000visualizing} to topological data analysis~\cite{tierny2018topological}, including matrix~\cite{wu2008matrix} or tensor~\cite{kindlmann2006diffusion} visualization.
+% To be able to visualize those objects is crucial for the practitioner 
+% as information about the structure of the object may be as important as the basic elements that constitute it (i.e. vectors or matrices). 
+% Despite the large number of existing tools to identify numerically unstable sections of source code, few allow the user to have a global view of the numerical precision of their computations or to compare several executions of the same program under various perturbations.
+
+% Veritracer~\cite{chatelain2018veritracer} was the first tool to propose an embedded visualizer of numerical stability over the execution of C, C++, and Fortran code.
+Veritracer extends Verificarlo~\cite{verificarlo} with contextual information about traced variables, which allows the user to identify instabilities quickly.
+% However, Veritracer neither offers a dynamic interface nor includes information about high-level structures such as \texttt{struct} or \texttt{array}.
+% FPAvizual~\cite{gu2014fpavisual} visualizes the effects of floating-point arithmetic but only for educational purposes and so does not target computational intensive applications\gkmod{}{Q: What does this mean?}.
+% Anteater~\cite{faust2019anteater} proposes a visualizer for Python code, but as mentioned previously, it only deals with native Python types, and the user needs to select variables to trace manually.
+Anteater provides an insightful reflection
+% around visual debugging beyond floating-point analysis, which has inspired the design of \pytracer's visualization interface.
+
 % Through our analysis of SciPy and Scikit-learn, we demonstrated \pytracer's scalability, automaticity, and applicability to any Python program.

### 2022-04-14 IEEEtran/paper-annotated.tex
Revision

--- 2021-12-21 paper.tex
@@
-\documentclass[11pt]{article}
-\usepackage[margin=0.5in]{geometry}
+%% bare_jrnl_compsoc.tex
+%% V1.4b
+%% 2015/08/26
+%% by Michael Shell
+%% See:
+%% http://www.michaelshell.org/
+%% for current contact information.
+%%
+%% This is a skeleton file demonstrating the use of IEEEtran.cls
+%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
+%% Computer Society journal paper.
+%%
+%% Support sites:
+%% http://www.michaelshell.org/tex/ieeetran/
+%% http://www.ctan.org/pkg/ieeetran
+%% and
+%% http://www.ieee.org/
+
+%%*************************************************************************
+%% Legal Notice:
+%% This code is offered as-is without any warranty either expressed or
+%% implied; without even the implied warranty of MERCHANTABILITY or
+%% FITNESS FOR A PARTICULAR PURPOSE! 
+%% User assumes all risk.
+%% In no event shall the IEEE or any contributor to this code be liable for
+%% any damages or losses, including, but not limited to, incidental,
+%% consequential, or any other damages, resulting from the use or misuse
+%% of any information contained here.
+%%
+%% All comments are the opinions of their respective authors and are not
+%% necessarily endorsed by the IEEE.
+%%
+%% This work is distributed under the LaTeX Project Public License (LPPL)
+%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
+%% distributed and modified. A copy of the LPPL, version 1.3, is included
+%% in the base LaTeX documentation of all distributions of LaTeX released
+%% 2003/12/01 or later.
+%% Retain all contribution notices and credits.
+%% ** Modified files should be clearly indicated as such, including  **
+%% ** renaming them and changing author support contact information. **
+%%*************************************************************************
+
+% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
+% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
+% *** with production work. The IEEE's font choices and paper sizes can   ***
+% *** trigger bugs that do not appear when using other class files.       ***                          ***
+% The testflow support page is at:
+% http://www.michaelshell.org/tex/testflow/
+
+\documentclass[10pt,journal,compsoc]{IEEEtran}
+
 \usepackage{todonotes}
-\usepackage{natbib}
 \usepackage{graphicx}
@@
 \usepackage{ulem} % provides sout
-\usepackage{minted} % Provides listing environment
+\usepackage[frozencache=true,cachedir=minted-cache]{minted} 
 \usepackage[htt]{hyphenat}      
@@
 \usepackage{booktabs}
-
-% \usepackage{subfigure}
-
-\newcommand{\tristan}[1]{\color{orange}\textbf{From Tristan:} #1\color{black}\xspace}
-\newcommand{\tristanmod}[2]{\color{orange}\sout{#1} #2\color{black}\xspace}
-\newcommand{\gkmod}[2]{\color{purple}\sout{#1} #2\color{black}\xspace}
-
-\newcommand{\Yohan}[1]{\color{green!75!black}\textbf{Yohan:} #1\color{black}\xspace}
+\usepackage{soul}
+
+%
+% If IEEEtran.cls has not been installed into the LaTeX system files,
+% manually specify the path to it like:
+% \documentclass[10pt,journal,compsoc]{../sty/IEEEtran}
+
+% Some very useful LaTeX packages include:
+% (uncomment the ones you want to load)
+
+% *** MISC UTILITY PACKAGES ***
+%
+%\usepackage{ifpdf}
+% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
+% compilation based on whether the output is pdf or dvi.
+% usage:
+% \ifpdf
+%   % pdf code
+% \else
+%   % dvi code
+% \fi
+% The latest version of ifpdf.sty can be obtained from:
+% http://www.ctan.org/pkg/ifpdf
+% Also, note that IEEEtran.cls V1.7 and later provides a builtin
+% \ifCLASSINFOpdf conditional that works the same way.
+% When switching from latex to pdflatex and vice-versa, the compiler may
+% have to be run twice to clear warning/error messages.
+
+% *** CITATION PACKAGES ***
+%
+\ifCLASSOPTIONcompsoc
+  % IEEE Computer Society needs nocompress option
+  % requires cite.sty v4.0 or later (November 2003)
+  \usepackage[nocompress]{cite}
+\else
+  % normal IEEE
+  \usepackage{cite}
+\fi
+% cite.sty was written by Donald Arseneau
+% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
+% \cite{} output to follow that of the IEEE. Loading the cite package will
+% result in citation numbers being automatically sorted and properly
+% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
+% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
+% \cite will automatically add leading space, if needed. Use cite.sty's
+% noadjust option (cite.sty V3.8 and later) if you want to turn this off
+% such as if a citation ever needs to be enclosed in parenthesis.
+% cite.sty is already installed on most LaTeX systems. Be sure and use
+% version 5.0 (2009-03-20) and later if using hyperref.sty.
+% The latest version can be obtained at:
+% http://www.ctan.org/pkg/cite
+% The documentation is contained in the cite.sty file itself.
+%
+% Note that some packages require special options to format as the Computer
+% Society requires. In particular, Computer Society  papers do not use
+% compressed citation ranges as is done in typical IEEE papers
+% (e.g., [1]-[4]). Instead, they list every citation separately in order
+% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
+% package with the nocompress option which is supported by cite.sty v4.0
+% and later. Note also the use of a CLASSOPTION conditional provided by
+% IEEEtran.cls V1.7 and later.
+
+% *** GRAPHICS RELATED PACKAGES ***
+%
+\ifCLASSINFOpdf
+  % \usepackage[pdftex]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../pdf/}{../jpeg/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+\else
+  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
+  % will default to the driver specified in the system graphics.cfg if no
+  % driver is specified.
+  % \usepackage[dvips]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../eps/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.eps}
+\fi
+% graphicx was written by David Carlisle and Sebastian Rahtz. It is
+% required if you want graphics, photos, etc. graphicx.sty is already
+% installed on most LaTeX systems. The latest version and documentation
+% can be obtained at: 
+% http://www.ctan.org/pkg/graphicx
+% Another good source of documentation is "Using Imported Graphics in
+% LaTeX2e" by Keith Reckdahl which can be found at:
+% http://www.ctan.org/pkg/epslatex
+%
+% latex, and pdflatex in dvi mode, support graphics in encapsulated
+% postscript (.eps) format. pdflatex in pdf mode supports graphics
+% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
+% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
+% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
+% which can result in "jaggedy"/blurry rendering of lines and letters as
+% well as large increases in file sizes.
+%
+% You can find documentation about the pdfTeX application at:
+% http://www.tug.org/applications/pdftex
+
+% *** MATH PACKAGES ***
+%
+%\usepackage{amsmath}
+% A popular package from the American Mathematical Society that provides
+% many useful and powerful commands for dealing with mathematics.
+%
+% Note that the amsmath package sets \interdisplaylinepenalty to 10000
+% thus preventing page breaks from occurring within multiline equations. Use:
+%\interdisplaylinepenalty=2500
+% after loading amsmath to restore such page breaks as IEEEtran.cls normally
+% does. amsmath.sty is already installed on most LaTeX systems. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/pkg/amsmath
+
+% *** SPECIALIZED LIST PACKAGES ***
+%
+%\usepackage{algorithmic}
+% algorithmic.sty was written by Peter Williams and Rogerio Brito.
+% This package provides an algorithmic environment fo describing algorithms.
+% You can use the algorithmic environment in-text or within a figure
+% environment to provide for a floating algorithm. Do NOT use the algorithm
+% floating environment provided by algorithm.sty (by the same authors) or
+% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
+% algorithm float types and packages that provide these will not provide
+% correct IEEE style captions. The latest version and documentation of
+% algorithmic.sty can be obtained at:
+% http://www.ctan.org/pkg/algorithms
+% Also of interest may be the (relatively newer and more customizable)
+% algorithmicx.sty package by Szasz Janos:
+% http://www.ctan.org/pkg/algorithmicx
+
+% *** ALIGNMENT PACKAGES ***
+%
+%\usepackage{array}
+% Frank Mittelbach's and David Carlisle's array.sty patches and improves
+% the standard LaTeX2e array and tabular environments to provide better
+% appearance and additional user controls. As the default LaTeX2e table
+% generation code is lacking to the point of almost being broken with
+% respect to the quality of the end results, all users are strongly
+% advised to use an enhanced (at the very least that provided by array.sty)
+% set of table tools. array.sty is already installed on most systems. The
+% latest version and documentation can be obtained at:
+% http://www.ctan.org/pkg/array
+
+% IEEEtran contains the IEEEeqnarray family of commands that can be used to
+% generate multiline equations as well as matrices, tables, etc., of high
+% quality.
+
+% *** SUBFIGURE PACKAGES ***
+%\ifCLASSOPTIONcompsoc
+%  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
+%\else
+%  \usepackage[caption=false,font=footnotesize]{subfig}
+%\fi
+% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
+% for subfigure.sty, the latter of which is no longer maintained and is
+% incompatible with some LaTeX packages including fixltx2e. However,
+% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
+% which will override IEEEtran.cls' handling of captions and this will result
+% in non-IEEE style figure/table captions. To prevent this problem, be sure
+% and invoke subfig.sty's "caption=false" package option (available since
+% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
+% handling of captions.
+% Note that the Computer Society format requires a sans serif font rather
+% than the serif font used in traditional IEEE formatting and thus the need
+% to invoke different subfig.sty package options depending on whether
+% compsoc mode has been enabled.
+%
+% The latest version and documentation of subfig.sty can be obtained at:
+% http://www.ctan.org/pkg/subfig
+
+% *** FLOAT PACKAGES ***
+%
+%\usepackage{fixltx2e}
+% fixltx2e, the successor to the earlier fix2col.sty, was written by
+% Frank Mittelbach and David Carlisle. This package corrects a few problems
+% in the LaTeX2e kernel, the most notable of which is that in current
+% LaTeX2e releases, the ordering of single and double column floats is not
+% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
+% single column figure to be placed prior to an earlier double column
+% figure.
+% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
+% corrections already built into the system in which case a warning will
+% be issued if an attempt is made to load fixltx2e.sty as it is no longer
+% needed.
+% The latest version and documentation can be found at:
+% http://www.ctan.org/pkg/fixltx2e
+
+%\usepackage{stfloats}
+% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
+% the ability to do double column floats at the bottom of the page as well
+% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
+% LaTeX2e). It also provides a command:
+%\fnbelowfloat
+% to enable the placement of footnotes below bottom floats (the standard
+% LaTeX2e kernel puts them above bottom floats). This is an invasive package
+% which rewrites many portions of the LaTeX2e float routines. It may not work
+% with other packages that modify the LaTeX2e float routines. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/pkg/stfloats
+% Do not use the stfloats baselinefloat ability as the IEEE does not allow
+% \baselineskip to stretch. Authors submitting work to the IEEE should note
+% that the IEEE rarely uses double column equations and that authors should try
+% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
+% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
+% such ways.
+% Do not attempt to use stfloats with fixltx2e as they are incompatible.
+% Instead, use Morten Hogholm'a dblfloatfix which combines the features
+% of both fixltx2e and stfloats:
+%
+% \usepackage{dblfloatfix}
+% The latest version can be found at:
+% http://www.ctan.org/pkg/dblfloatfix
+
+%\ifCLASSOPTIONcaptionsoff
+%  \usepackage[nomarkers]{endfloat}
+% \let\MYoriglatexcaption\caption
+% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
+%\fi
+% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
+% Axel Sommerfeldt. This package may be useful when used in conjunction with 
+% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
+% submissions have lists of figures/tables at the end of the paper and that
+% figures/tables without any captions are placed on a page by themselves at
+% the end of the document. If needed, the draftcls IEEEtran class option or
+% \CLASSINPUTbaselinestretch interface can be used to increase the line
+% spacing as well. Be sure and use the nomarkers option of endfloat to
+% prevent endfloat from "marking" where the figures would have been placed
+% in the text. The two hack lines of code above are a slight modification of
+% that suggested by in the endfloat docs (section 8.4.1) to ensure that
+% the full captions always appear in the list of figures/tables - even if
+% the user used the short optional argument of \caption[]{}.
+% IEEE papers do not typically make use of \caption[]'s optional argument,
+% so this should not be an issue. A similar trick can be used to disable
+% captions of packages such as subfig.sty that lack options to turn off
+% the subcaptions:
+% For subfig.sty:
+% \let\MYorigsubfloat\subfloat
+% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
+% However, the above trick will not work if both optional arguments of
+% the \subfloat command are used. Furthermore, there needs to be a
+% description of each subfigure *somewhere* and endfloat does not add
+% subfigure captions to its list of figures. Thus, the best approach is to
+% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
+% and instead reference/explain all the subfigures within the main caption.
+% The latest version of endfloat.sty and its documentation can obtained at:
+% http://www.ctan.org/pkg/endfloat
+%
+% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
+% later in the document, say, to conditionally put the References on a 
+% page by themselves.
+
+% *** PDF, URL AND HYPERLINK PACKAGES ***
+%
+%\usepackage{url}
+% url.sty was written by Donald Arseneau. It provides better support for
+% handling and breaking URLs. url.sty is already installed on most LaTeX
+% systems. The latest version and documentation can be obtained at:
+% http://www.ctan.org/pkg/url
+% Basically, \url{my_url_here}.
+
+% *** Do not adjust lengths that control margins, column widths, etc. ***
+% *** Do not use packages that alter fonts (such as pslatex).         ***
+% There should be no need to do such things with IEEEtran.cls V1.6 and later.
+% (Unless specifically asked to do so by the journal or conference you plan
+% to submit to, of course. )
+
+% correct bad hyphenation here
+\hyphenation{op-tical net-works semi-conduc-tor}
+
 \newcommand{\cross}[0]{\cellcolor{red!65}\ding{53}}
@@
 
+\definecolor{lightred}{rgb}{1.0,0.6,0.6}
+\definecolor{lightgreen}{rgb}{0.6,1.0,0.6}
+
+\DeclareRobustCommand{\add}[1]{{\sethlcolor{lightgreen}\hl{#1}}}
+\DeclareRobustCommand{\remove}[1]{{\sethlcolor{lightred}\hl{#1}}}
+
+\DeclareRobustCommand{\addCite}[1]{{\sethlcolor{lightgreen}\hl{\mbox{#1}}}}
+\DeclareRobustCommand{\removeCite}[1]{{\sethlcolor{lightred}\hl{\mbox{#1}}}}
+
 \setlength{\arrayrulewidth}{0.1pt}
@@
 
-\usepackage{tabularx} % provides tabularx to adjust table column sizes to page size
-% define thickline for use in tables
 \makeatletter
@@
 
-\title{PyTracer: Automatically profiling numerical instabilities in Python}
-\author{Yohan Chatelain$^1$, Nigel Young$^1$,  Gregory Kiar$^2$,  Tristan Glatard$^1$\\
+%
+% paper title
+% Titles are generally capitalized except for words such as a, an, and, as,
+% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
+% not capitalized unless they are the first or last word of the title.
+% Linebreaks \\ can be used within to get better formatting as desired.
+% Do not put math or special symbols in the title.
+\title{PyTracer: Automatically Profiling Numerical Instabilities in Python}
+%
+%
+% author names and IEEE memberships
+% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
+% a structure at a ~ so this keeps an author's name from being broken across
+% two lines.
+% use \thanks{} to gain access to the first footnote area
+% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
+% was not built to handle multiple paragraphs
+%
+%
+%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
+% lists the Computer Society journals use for "first footnote" author
+% affiliations. Use \IEEEcompsocthanksitem which works much like \item
+% for each affiliation group. When not in compsoc mode,
+% \IEEEcompsocitemizethanks becomes like \thanks and
+% \IEEEcompsocthanksitem becomes a line break with idention. This
+% facilitates dual compilation, although admittedly the differences in the
+% desired content of \author between the different types of papers makes a
+% one-size-fits-all approach a daunting prospect. For instance, compsoc 
+% journal papers have the author affiliations above the "Manuscript
+% received ..."  text while in non-compsoc journals this is reversed. Sigh.
+
+\author{Yohan Chatelain$^1$, Nigel Yong Sao Young$^1$,  Gregory Kiar$^2$,  Tristan Glatard$^1$\\
     $^1$Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada\\
     $^2$Center for the Developing Brain, Child Mind Institute, New York, NY, USA}
-    \date{}
+%% \author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
+%%         John~Doe,~\IEEEmembership{Fellow,~OSA,}
+%%         and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
+%% \IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M. Shell was with the Department
+%% of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
+%% GA, 30332.\protect\\
+%% % note need leading \protect in front of \\ to get a newline within \thanks as
+%% % \\ is fragile and will error, could use \hfil\break instead.
+%% E-mail: see http://www.michaelshell.org/contact.html
+%% \IEEEcompsocthanksitem J. Doe and J. Doe are with Anonymous University.}% <-this % stops an unwanted space
+%% \thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
+
+% note the % following the last \IEEEmembership and also \thanks - 
+% these prevent an unwanted space from occurring between the last author name
+% and the end of the author line. i.e., if you had this:
+% 
+% \author{....lastname \thanks{...} \thanks{...} }
+%                     ^------------^------------^----Do not want these spaces!
+%
+% a space would be appended to the last name and could cause every name on that
+% line to be shifted left slightly. This is one of those "LaTeX things". For
+% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
+% "AB" then you have to do: "\textbf{A}\textbf{B}"
+% \thanks is no different in this regard, so shield the last } of each \thanks
+% that ends a line with a % and do not let a space in before the next \thanks.
+% Spaces after \IEEEmembership other than the last one are OK (and needed) as
+% you are supposed to have spaces between the names. For what it is worth,
+% this is a minor point as most people would not even notice if the said evil
+% space somehow managed to creep in.
+
+% The paper headers
+\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
+{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
+% The only time the second header will appear is for the odd numbered pages
+% after the title page when using the twoside option.
+% 
+% *** Note that you probably will NOT want to include the author's ***
+% *** name in the headers of peer review papers.                   ***
+% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
+% you desire.
+
+% The publisher's ID mark at the bottom of the page is less important with
+% Computer Society journal papers as those publications place the marks
+% outside of the main text columns and, therefore, unlike regular IEEE
+% journals, the available text space is not reduced by their presence.
+% If you want to put a publisher's ID mark on the page you can do it like
+% this:
+%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
+% or like this to get the Computer Society new two part style.
+%\IEEEpubid{\makebox[\columnwidth]{\hfill 0000--0000/00/\$00.00~\copyright~2015 IEEE}%
+%\hspace{\columnsep}\makebox[\columnwidth]{Published by the IEEE Computer Society\hfill}}
+% Remember, if you use this you must call \IEEEpubidadjcol in the second
+% column for its text to clear the IEEEpubid mark (Computer Society jorunal
+% papers don't need this extra clearance.)
+
+% use for special paper notices
+%\IEEEspecialpapernotice{(Invited Paper)}
+
+% for Computer Society papers, we must declare the abstract and index terms
+% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
+% command as these need to go into the title area created by \maketitle.
+% As a general rule, do not put math, special symbols or citations
+% in the abstract or keywords.
+\IEEEtitleabstractindextext{%
+    \begin{abstract}
+        Numerical stability is a crucial requirement of reliable scientific
+        computing. However, despite the pervasiveness of Python in data science,
+        analyzing large Python programs remains challenging due to the lack of
+        scalable numerical analysis tools available for this language. To fill
+        this gap, we developed \pytracer, a profiler to quantify numerical
+        instability in Python applications. \pytracer transparently instruments
+        Python code to produce numerical traces and visualize them interactively
+        in a Plotly dashboard. We designed \pytracer to be agnostic to numerical
+        noise model , allowing for tool evaluation through Monte-Carlo
+        Arithmetic, random rounding, random data perturbation, or structured
+        noise for a particular application. We illustrate \pytracer's
+        capabilities by testing the numerical stability of key functions in both
+        SciPy and Scikit-learn, two dominant Python libraries for mathematical
+        modeling. Through these evaluations, we demonstrate \pytracer as a
+        scalable, automatic, and generic framework for numerical profiling in
+        Python.
+    \end{abstract}
+}
+% Note that keywords are not normally used for peerreview papers.
+%% \begin{IEEEkeywords}
+%% Computer Society, IEEE, IEEEtran, journal, \LaTeX, paper, template.
+%% \end{IEEEkeywords}}
+
+% make the title area
 \maketitle
 
-\begin{abstract}
-Numerical stability is a crucial requirement of reliable scientific computing.
-However, despite the pervasiveness of Python in data science, analyzing large Python programs remains challenging due to the lack of scalable numerical analysis tools available for this language.
-To fill this gap, we developed \pytracer, a profiler to quantify numerical instability in Python applications.
-\pytracer transparently instruments Python code to produce numerical traces and visualize them interactively in a Plotly dashboard.
-We designed \pytracer to be agnostic to numerical noise model , allowing for tool evaluation through Monte-Carlo Arithmetic, random rounding, random data perturbation, or structured noise for a particular application.
-We illustrate \pytracer's capabilities by testing the numerical stability of key functions in both SciPy and Scikit-learn, two dominant Python libraries for mathematical modeling.
-Through these evaluations, we demonstrate \pytracer as a scalable, automatic, and generic framework for numerical profiling in Python.
-% Numerical stability is a crucial requirement of reliable scientific computing.
-However, despite the pervasiveness of Python in data science, analyzing large Python programs remains challenging due to the lack of scalable numerical analysis tools available for this language.
-To address this issue, we developed \pytracer, a profiler to quantify numerical instability in Python applications.
-\pytracer automatically instruments Python code to produce numerical traces and visualize them interactively in a Plotly dashboard.
-% \pytracer is designed to work with any type of numerical noise model, including Monte-Carlo Arithmetic, random rounding or random data perturbations.
-We illustrate \pytracer's capabilities by testing the numerical stability of key functions in the SciPy and Scikit-learn Python libraries.
-Finally, \pytracer slows down executions by only $3.5 \times$ on average.
-% \tristan{Add one sentence to summarize the findings} 
-\end{abstract}
-
-\section{Introduction}
-
-The scientific Python ecosystem has become a central component of data
-analyses in recent years, owing to its rich offering of data manipulation, array programming,
-numerical analysis, and visualization tools. In particular, libraries such
-as NumPy~\cite{harris2020array}, SciPy~\cite{virtanen2020scipy}, scikit-learn~\cite{pedregosa2011scikit} or PyTorch~\cite{paszke2019pytorch} are used in hundreds of publications each year, and serve as a reference set of high-quality open-source core scientific libraries.
-Researchers have built numerous domain-specific software tools from this ecosystem, leveraging Python's simplicity and flexibility.
+% To allow for easy dual compilation without having to reenter the
+% abstract/keywords data, the \IEEEtitleabstractindextext text will
+% not be used in maketitle, but will appear (i.e., to be "transported")
+% here as \IEEEdisplaynontitleabstractindextext when the compsoc 
+% or transmag modes are not selected <OR> if conference mode is selected 
+% - because all conference papers position the abstract like regular
+% papers do.
+\IEEEdisplaynontitleabstractindextext
+% \IEEEdisplaynontitleabstractindextext has no effect when using
+% compsoc or transmag under a non-conference mode.
+
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+% \ifCLASSOPTIONpeerreview
+% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
+% \fi
+%
+% For peerreview papers, this IEEEtran command inserts a page break and
+% creates the second title. It will be ignored for other modes.
+\IEEEpeerreviewmaketitle
+
+\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
+% Computer Society journal (but not conference!) papers do something unusual
+% with the very first section heading (almost always called "Introduction").
+% They place it ABOVE the main text! IEEEtran.cls does not automatically do
+% this for you, but you can achieve this effect with the provided
+% \IEEEraisesectionheading{} command. Note the need to keep any \label that
+% is to refer to the section immediately after \section in the above as
+% \IEEEraisesectionheading puts \section within a raised box.
+
+\IEEEPARstart{T}{he} scientific Python ecosystem has become a central component
+of data analyses in recent years, owing to its rich offering of data
+manipulation, array programming, numerical analysis, and visualization tools. In
+particular, libraries such as NumPy~\cite{harris2020array},
+SciPy~\cite{virtanen2020scipy}, scikit-learn~\cite{pedregosa2011scikit} or
+PyTorch~\cite{paszke2019pytorch} are used in hundreds of publications each year,
+and serve as a reference set of high-quality open-source core scientific
+libraries. Researchers have built numerous domain-specific software tools from
+this ecosystem, leveraging Python's simplicity and flexibility.
 
 Numerical stability is a crucial requirement of reliable scientific data
-processing.
-In unstable analyses, small numerical perturbations introduced by data noise, software and hardware updates, or parallelization have potential to introduce substantial deviations in final results, leading to potentially different scientific conclusions, ultimately threatening the reliability of computational analyses.
-To prevent this, numerical stability analyses need to be conducted systematically, however, no practical tool currently exists to conduct such analyses for Python programs.
-
-We present PyTracer, a numerical stability profiling and visualization tool for Python programs.
-\pytracer adopts a dynamic approach that evaluates numerical stability using program execution traces, and is applicable to large programs without manual intervention.
-The transparent nature of \pytracer is particularly valuable in contrast to theoretical approaches based on condition numbers or backward error analysis, which require detailed modeling of the program and its numerical implementation.
-Similarly, static code analysis techniques hardly scale to large code bases, particularly in dynamically-typed languages such as Python.
-
-\pytracer estimates the variability of floating-point variables by combining program traces obtained with different numerical perturbations, which requires (1) generating numerically-perturbed executions, (2) tracing floating-point computations along program executions, and (3) visualizing stability evaluations.
-\pytracer addresses these requirements with (1) a ``fuzzy" Python interpreter instrumented with Monte-Carlo arithmetic, (2) a dynamic instrumentation of Python functions, modules, and classes through meta-programming, (3) an interactive Plotly dashboard to visualize stability measures throughout program executions.
-
-This manuscript presents the design of \pytracer and demonstrates its potential in various use cases. 
-Through stability evaluations of the
-SciPy and scikit-learn libraries, we demonstrate \pytracer as a practical solution to review the numerical stability of extensive code bases. 
-%All information was obtained through \pytracer, visualized separately for improved customizability.
-%\tristan{this is a weird place to mention this ^^}
+processing. In unstable analyses, small numerical perturbations introduced by
+data noise, software and hardware updates, or parallelization have potential to
+introduce substantial deviations in final results, leading to potentially
+different scientific conclusions, ultimately threatening the reliability of
+computational analyses. To prevent this, numerical stability analyses need to be
+conducted systematically, however, no practical tool currently exists to conduct
+such analyses for Python programs.
+
+We present PyTracer, a numerical stability profiling and visualization tool for
+Python programs. \pytracer adopts a dynamic approach that evaluates numerical
+stability using program execution traces, and is applicable to large programs
+without manual intervention. The transparent nature of \pytracer is particularly
+valuable in contrast to theoretical approaches based on condition numbers or
+backward error analysis~\addCite{\cite{higham2002accuracy}}, which require detailed modeling of the program and its
+numerical implementation. Similarly, static code analysis techniques~\addCite{\cite{goubault2006static}} hardly
+scale to large code bases, particularly in dynamically-typed languages such as
+Python.
+
+\pytracer estimates the variability of floating-point variables by combining
+program traces obtained with different numerical perturbations, which requires
+(\add{a}\remove{1}) generating numerically-perturbed executions, (\add{b}\remove{2}) tracing floating-point
+computations along program executions, and (\add{c}\remove{3}) visualizing stability
+evaluations. 
+\add{PyTracer uses the ``fuzzy" Python environment instrumented with Monte-Carlo
+arithmetic to address the requirement (a). \mbox{\pytracer} addresses the
+remaining requirements with (b) a dynamic instrumentation of Python functions,
+modules, and classes through meta-programming, (c) an interactive Plotly
+dashboard to visualize stability measures throughout program executions.
+\mbox{\pytracer} is available at
+\mbox{\href{https://github.com/big-data-lab-team/pytracer.git}{github.com/big-data-lab-team/pytracer.git}}
+under MIT License.}
+\remove{\mbox{\pytracer} addresses these requirements with (1) a ``fuzzy" Python
+    interpreter instrumented with Monte-Carlo arithmetic, (2) a dynamic
+    instrumentation of Python functions, modules, and classes through
+    meta-programming, (3) an interactive Plotly dashboard to visualize stability
+    measures throughout program executions. }
+
+This manuscript presents the design of \pytracer and demonstrates its potential
+in various use cases. Through stability evaluations of the SciPy and
+scikit-learn libraries, we demonstrate \pytracer as a practical solution to
+review the numerical stability of extensive code bases.
 
@@
 \pytracer adopts the three-step workflow shown in Figure~\ref{fig:workflow}.
-First, \pytracer uses \textit{monkey patching} to replace the functions called by the application with a wrapper that saves their arguments and returned values in a trace file.
-% \gkmod{}{Q: This is conceptually similar to a decorator, no?
-If so, perhaps it is worth mentioning} \Yohan{Conceptually, monkey patching is the ability to dynamically change a class or a module.
-So it's more powerful than the decorators.
-But yes we use monkey-patching to automatically decorate the functions.}
-Second, it executes the application multiple times with noise injection, and aggregates the resulting trace files to compute summary statistics about each traced variable.
-Finally, a Plotly dashboard provides interactive visualizations highlighting unstable code sections.
+First, \pytracer uses \textit{monkey patching} to replace the functions called
+by the application with a wrapper that saves their arguments and returned values
+in a trace file.
+Second, it executes the application multiple times with noise injection, and
+aggregates the resulting trace files to compute summary statistics about each
+traced variable. Finally, a Plotly dashboard provides interactive visualizations
+highlighting unstable code sections.
 
@@
 
-\pytracer dynamically instruments Python modules
-without requiring source code modifications in the application.
-To do so, it creates a new, instrumented version of each module that preserves its original attributes so that the application can transparently use it.
-% \gkmod{}{Note: this form of monkey patching is basically global and transparent decorating, right?} \Yohan{Yes}
-By default, \pytracer instruments all the attributes
-in a given module except the special ones of the form \texttt{\_\_*\_\_}, which is common for reserved Python methods.
-However, some attributes are not writable. In this case, \pytracer preservers the original attributes and warns the user. The user can also restrict the list of traced attributes through
-an inclusion/exclusion mechanism.
-The main advantage of this instrumentation approach is the lack of required modification in the application source code, in contrast with decorator-based approaches.
-In addition, this technique is scalable and applicable in read-only environments such as Singularity containers or HPC clusters.
+\pytracer dynamically instruments Python modules without requiring source code
+modifications in the application. To do so, it creates a new, instrumented
+version of each module that preserves its original attributes so that the
+application can transparently use it.
+% \gkmod{}{Note: this form of monkey patching is basically global and
+% transparent decorating, right?} \Yohan{Yes}
+By default, \pytracer instruments all the attributes in a given module except
+the special ones of the form \texttt{\_\_*\_\_}, which is common for reserved
+Python methods. However, some attributes are not writable. In this case,
+\pytracer \remove{preservers} \add{preserves} the original attributes and warns the user. The user can
+also restrict the list of traced attributes through an inclusion/exclusion
+mechanism. The main advantage of this instrumentation approach is the lack of
+required modification in the application source code, in contrast with
+\remove{decorator-based approaches} \add{a decorator-based approache~\mbox{\cite{hunt2019decorators}}}. 
+In addition, this technique is scalable and
+applicable in read-only environments such as Singularity containers or HPC
+clusters.
 
@@
 
-Python loads modules through an import mechanism triggered by the \texttt{import} keyword that involves two objects: \texttt{finders} and \texttt{loaders}. \texttt{Finders} search for packages (or 
-namespaces\footnote{Python distinguishes between \texttt{regular} and \texttt{namespace} packages.
-A regular package is a directory that contains a \_\_init\_\_.py file and potentially subdirectories (sub-packages) 
-that contain themselves a \texttt{\_\_init\_\_.py} file and so on recursively. 
-The package hierarchy follows those of the directory. 
-Namespace packages introduced in Python 3.3 (\href{https://www.python.org/dev/peps/pep-0420/}{PEP 420}) do not contain an
-\_\_init\_\_.py file and allow for flexible directory structures.
-Hence, parts of the package can be located in zip files, on the network, or in separated directories.
-There are no functional differences between both types of packages.}) on the local storage --- such as standard packages installed through the pip package manager --- or on a distant server.
-\texttt{Finders} do not load modules. Instead, they return a specification (\texttt{spec} object) that includes 
-information on where to find and how to load modules.
-\texttt{Loaders} create module objects, initialize them, and fill import-related attributes 
-such as \texttt{\_\_spec\_\_}. 
-\texttt{Loaders} then execute modules and populate their namespace. Finally, modules are bound to their import name in the \texttt{sys.modules} dictionary.
-
-Python supports custom \texttt{finder} classes registered in the \texttt{sys.meta\_path} list.
-When Python encounters an \texttt{import} statement, it first looks for an existing binding in \texttt{sys.modules} and then iterates over the \texttt{finder} classes in the \texttt{sys.meta\_path} list until it finds the module.
-\pytracer adds a custom \texttt{finder} class at the head of \texttt{sys.meta\_path} that intercepts
-the module import and creates the module with a custom \texttt{loader} class.
-
-\pytracer's \texttt{loader} class first loads the original module, then copies it as a new instance of the \texttt{ModuleType} class.
-It then calls the appropriate instrumentation function for each attribute depending on its type (function, class, or instances) and replaces the original module in the \texttt{sys.modules} map with the instrumented version.
-Finally, it updates all existing references to the original module contained in the global symbol table.
+Python loads modules through an import mechanism triggered by the
+\texttt{import} keyword that involves two objects: \texttt{finders} and
+\texttt{loaders}. \texttt{Finders} search for packages (or
+namespaces\footnote{Python distinguishes between \texttt{regular} and
+    \texttt{namespace} packages. A regular package is a directory that contains a
+    \_\_init\_\_.py file and potentially subdirectories (sub-packages) that contain
+    themselves a \texttt{\_\_init\_\_.py} file and so on recursively. The package
+    hierarchy follows those of the directory. Namespace packages introduced in
+    Python 3.3 (\href{https://www.python.org/dev/peps/pep-0420/}{PEP 420}) do not
+    contain an \_\_init\_\_.py file and allow for flexible directory structures.
+    Hence, parts of the package can be located in zip files, on the network, or in
+    separated directories. There are no functional differences between both types of
+    packages.}) on the local storage --- such as standard packages installed through
+the pip package manager --- or on a distant server. \texttt{Finders} do not load
+modules. Instead, they return a specification (\texttt{spec} object) that
+includes information on where to find and how to load modules. \texttt{Loaders}
+create module objects, initialize them, and fill import-related attributes such
+as \texttt{\_\_spec\_\_}. \texttt{Loaders} then execute modules and populate
+their namespace. Finally, modules are bound to their import name in the
+\texttt{sys.modules} dictionary.
+
+Python supports custom \texttt{finder} classes registered in the
+\texttt{sys.meta\_path} list. When Python encounters an \texttt{import}
+statement, it first looks for an existing binding in \texttt{sys.modules} and
+then iterates over the \texttt{finder} classes in the \texttt{sys.meta\_path}
+list until it finds the module. \pytracer adds a custom \texttt{finder} class at
+the head of \texttt{sys.meta\_path} that intercepts the module import and
+creates the module with a custom \texttt{loader} class.
+
+\pytracer's \texttt{loader} class first loads the original module, then copies
+it as a new instance of the \texttt{ModuleType} class. It then calls the
+appropriate instrumentation function for each attribute depending on its type
+(function, class, or instances) and replaces the original module in the
+\texttt{sys.modules} map with the instrumented version. Finally, it updates all
+existing references to the original module contained in the global symbol table.
 As a result, the application will transparently call the instrumented module.
 
-% \tristan{is the non-instrumented version ever added to sys.modules? If so, could this lead to race conditions? If not, replace with ``adds the instrumented module to the sys.modules map"}. 
-% \Yohan{Yes, it replaces the original module.
-You can't have a race-condition since sys.modules is a dict with only one value for a given key.
-The trick is that the wrapped module keeps a reference to the original module, it's just that this reference is invisible for the others object since it's not in sys.modules and globals.
-By the way, Pytracer needs to update all possible references that original objects may hold, like functions in \_\_dict\_\_ attributes or locals references in \_\_globals\_\_ for example.}
-
-% \pytracer intercepts the modules loaded with the \texttt{Finder} and \texttt{Loader} mechanisms \tristan{is it restrictive? Are there other mechanisms?}.
-% The Finder searches the loader of a module that is being imported while the 
-% Loader loads and initializes the module. \pytracer adds \tristan{overrides?} a new Finder and Loader on top of the default ones
-% to intercept imports and to instrument modules selected by the user. This mechanism allows returning 
-% the original module in the instrumentation code and returning the instrumented module in the targeted application
-% without modifying its actual code.
-
 \subsubsection{Instrumenting module functions}
 
-Listings~\ref{fig:wrapper_creation} and~\ref{fig:generic_wrapper} show \pytracer's function instrumentation mechanism.
-For each function to instrument, \pytracer's \texttt{loader} class creates a wrapper function, dynamically compiles it with the \texttt{compile} builtin function, and substitutes it for the original module function.
-Although simple, this technique does not apply to callable class instances, i.e., class instances that have a \texttt{\_\_call\_\_} attribute and are not of type \texttt{FunctionType}.
-Indeed, applying the wrapper technique would 1) modify the type of the class instance to \texttt{FunctionType}, which could cause syntax and semantic errors, and 2) mask class attributes, leading to \texttt{AttributeError} exceptions.
-\pytracer overrides the \texttt{\_\_call\_\_} attribute with the wrapper function when possible to overcome this issue.
-When the \texttt{\_\_call\_\_} attribute is not writable,  Pytracer does not instrument the class and returns a warning.
-
-% \tristan{add docstrings to all Python code examples and clarify captions accordingly: you don't need to explain the meaning of each attribute in the caption if it's in the docstring.
-The caption can focus on the main functionality, reusing the text currently in 3.1.5.}
-% \Yohan{TODO}
-
-% Listing~\ref{fig:wrapper_creation} shows how functions are instrumented.
-% This function takes as inputs the information about the function to instrument (module name and full qualified name),
-% the function itself, and the actual name of the function. It then creates a wrapper around the actual wrapper
-% (\texttt{generic\_wrapper}) that will save the values in trace files.
-Instead of passing the function, we pass the function's identifier, which is a unique 64-bits integer that references each Python object.
-This identifier is available
-% with the \texttt{id} builtin function. it allows to get rid of aliases and to avoid instrumenting functions twice.  \tristan{Summarize this paragraph in the figure caption}
-
-% Listing~\ref{fig:generic_wrapper} shows what the instrumented code does. 
-% It first unpacks the function's information to get the function's identifier to retrieve the original function.
-% Then arguments are bound by creating a mapping from positional and keyword arguments to parameters, avoiding conflicts and mispositioning.
-It also allows getting names of arguments for the visualization.
-% Once bound, the \texttt{inputs} function dumps the arguments in the pickle file.
-% Finally, Pytracer calls the function with the correct arguments, dumps the result, and returns it. \tristan{Summarize this paragraph in the figure caption}
-
-%
-% we can employ a case by case strategy depending on the class (i.e. numpy ufunc) or simply ignore
-% the instrumentation and let the original one.
-% \tristan{add a sentence to explain how callable instances are instrumented}
-
-\begin{listing}
-    \centering
-\begin{lstlisting}[language=Python,style=customPython]
-def get_wrapper_function(module, qualname, name, function):
-    """Returns the instrumented function as a string.
-    This string will be compiled with the compile builtin function
-
-    Parameters:
-        module: Name of the function module
-        qualname: Qualified name of the function
-        name: Name of the function
-        function: Python object function
-
-    Returns:
-        wrapper_code: The code source of the wrapper
-    """
-    function_id = id(function)
-    info = (function_id, function_module, function_qualified_name)
-    wrapper_code = f"""
-    def {function_wrapper_name}(*args, **kwargs):
-        return generic_wrapper({info},*args,**kwargs)"""
-    return wrapper_code
-\end{lstlisting}
-    \caption{Function to create the instrumented version of a function.
-    \pytracer uses the identifier of the function instead of the 
-    actual function to handle aliases and avoid duplicate instrumentation.}
-    \label{fig:wrapper_creation}
-\end{listing}
-
-\begin{listing}
-    \centering
-\begin{lstlisting}[language=Python,style=customPython,]
-def generic_wrapper(self, info, *args, **kwargs):
-    """Generic wrapper saving inputs and outputs of the wrapped function.
-    The id_dict dict keeps a mapping between the original function identifier
-    and itself. Arguments are binded to avoid mispositioning.
-    Returns the actual output of the wrapped function.
-
-    Parameters:
-        info: Tuple with the function's id, function's module and function's name
-        *args: Positional calling arguments
-        **kwargs: Keyword calling arguments
-
-    Returns:
-        outputs: Outputs of the wrapped function
-    """
-    fid, fmodule, fname = info
-    function = original_function_cache.id_dict[fid]
-    bind = Binding(function, *args, **kwargs)
-    stack = self.backtrace()
-    time = elements()
-    self.inputs(time=time,
-                module_name=fmodule,
-                function_name=fname,
-                function=function,
-                args=bind.arguments,
-                backtrace=stack)
-    outputs = function(*bind.args, **bind.kwargs)
-    self.outputs(time=time,
-                 module_name=fmodule,
-                 function_name=fname,
-                 function=function,
-                 args=outputs,
-                 backtrace=stack)
-    return outputs
-\end{lstlisting}
-    \caption{\pytracer's generic wrapper function that saves
-    the inputs and outputs of the wrapped function.}
-    \label{fig:generic_wrapper}
-\end{listing}
+\remove{Listings~\mbox{\ref{fig:wrapper_creation}} and~\mbox{\ref{fig:generic_wrapper}} show
+    \mbox{\pytracer}'s function instrumentation mechanism.}
+For each function to instrument, \pytracer's \texttt{loader} class creates a
+wrapper function, dynamically compiles it with the \texttt{compile} builtin
+function, and substitutes it for the original module function.  Although simple,
+this technique does not apply to callable class instances, i.e., class instances
+that have a \texttt{\_\_call\_\_} attribute and are not of type
+\texttt{FunctionType}. Indeed, applying the wrapper technique would 1) modify
+the type of the class instance to \texttt{FunctionType}, which could cause
+syntax and semantic errors, and 2) mask class attributes, leading to
+\texttt{AttributeError} exceptions. \pytracer overrides the
+\texttt{\_\_call\_\_} attribute with the wrapper function when possible to
+overcome this issue. When the \texttt{\_\_call\_\_} attribute is not writable,
+Pytracer does not instrument the class and returns a warning.
+
+% \begin{listing}
+%     \centering
+%     \begin{lstlisting}[language=Python,style=customPython]
+% def get_wrapper_function(module, qualname, name, function):
+%     """Returns the instrumented function as a string.
+%     This string will be compiled with the compile builtin function
+
+%     Parameters:
+%         module: Name of the function module
+%         qualname: Qualified name of the function
+%         name: Name of the function
+%         function: Python object function
+
+%     Returns:
+%         wrapper_code: The code source of the wrapper
+%     """
+%     info = (id(function), function_module, qualname)
+%     wrapper_code = f"""
+%     def {function_wrapper_name}(*args, **kwargs):
+%         return generic_wrapper({info},*args,**kwargs)"""
+%     return wrapper_code
+% \end{lstlisting}
+%     \caption{Function to create the instrumented version of a function.
+%         \pytracer uses the identifier of the function instead of the 
+%         actual function to handle aliases and avoid duplicate instrumentation.}
+%     \label{fig:wrapper_creation}
+% \end{listing}
+
+% \begin{listing}
+%     \centering
+%     \begin{lstlisting}[language=Python,style=customPython,]
+% def generic_wrapper(self, info, *args, **kwargs):
+%     """Generic wrapper saving inputs and outputs of the wrapped function.
+%     The id_dict dict keeps a mapping between the original function identifier
+%     and itself. Arguments are binded to avoid mispositioning.
+%     Returns the actual output of the wrapped function.
+
+%     Parameters:
+%         info: Tuple with the function's id, function's module and function's name
+%         *args: Positional calling arguments
+%         **kwargs: Keyword calling arguments
+
+%     Returns:
+%         outputs: Outputs of the wrapped function
+%     """
+%     fid, module_name, function_name = info
+%     function = original_function_cache.id_dict[fid]
+%     bind = Binding(function, *args, **kwargs)
+%     stack = self.backtrace()
+%     time = elements()
+%     self.inputs(time, module_name, function_name, function, bind.arguments, stack)
+%     outputs = function(*bind.args, **bind.kwargs)
+%     self.outputs(time, module_name, function_name, function, outputs, stack)
+%     return outputs
+% \end{lstlisting}
+%     \caption{\pytracer's generic wrapper function that saves
+%         the inputs and outputs of the wrapped function.}
+%     \label{fig:generic_wrapper}
+% \end{listing}
 
@@
 
-\pytracer instruments classes by wrapping their callable attributes as described previously. 
-This instrumentation preserves class types, which avoids type mismatches in the instrumented application.
-However, classes that describe particular base types and NumPy's universal functions (class \texttt{ufunc}) contain read-only attributes that cannot be instrumented.
-By default, \pytracer returns a warning when it encounters such classes.
+\pytracer instruments classes by wrapping their callable attributes as described
+previously. This instrumentation preserves class types, which avoids type
+mismatches in the instrumented application. However, classes that describe
+particular base types and NumPy's universal functions (class \texttt{ufunc})
+contain read-only attributes that cannot be instrumented. By default, \pytracer
+returns a warning when it encounters such classes.
 
@@
 
-\pytracer automatically instruments class instances since it instruments classes.
-However, it cannot instrument or instantiate classes that have read-only attributes --- in particular class \texttt{ufunc}, --- which is problematic given their pervasiveness in scientific computing.
-In particular, NumPy's universal functions include
-vectorized elementary mathematical and other prevalent functions. 
-%\gkmod{ones}{Q: prevalent whats?}.
-Universal functions are implemented in C, which prevents their modification.
-
-To overcome this issue, \pytracer wraps the class instance into a transparent wrap class (\texttt{twc}) that overloads
-1) function \texttt{\_\_getattribute\_\_}, called when an instance attribute is accessed --- instrumented to return the attributes from the original class, and 2) function \texttt{\_\_call\_\_}, used when an instance behaves like a function through the () operator --- instrumented with function \texttt{generic\_wrapper}.
-% \gkmod{}{Note: the previous sentence is a bit hard to follow; the word "called" is used a lot so I got a bit lost.}
-The \texttt{twc} returns the queried attribute of the instance instead of returning its attributes, allowing transparent access to the instance.
-Finally, \pytracer overloads the builtin \texttt{type} function to preserve the type of the wrapped instance.
+\pytracer automatically instruments class instances since it instruments
+classes. However, it cannot instrument or instantiate classes that have
+read-only attributes --- in particular class \texttt{ufunc}, --- which is
+problematic given their pervasiveness in scientific computing. In particular,
+NumPy's universal functions include vectorized elementary mathematical and other
+prevalent functions. Universal functions are implemented in C, which prevents
+their modification.
+
+To overcome this issue, \pytracer wraps the class instance into a transparent
+wrap class (\texttt{twc}) that overloads 1) function
+\texttt{\_\_getattribute\_\_}, called when an instance attribute is accessed ---
+instrumented to return the attributes from the original class, and 2) function
+\texttt{\_\_call\_\_}, used when an instance behaves like a function through the
+() operator --- instrumented with function \texttt{generic\_wrapper}. The
+\texttt{twc} returns the queried attribute of the instance instead of returning
+its attributes, allowing transparent access to the instance.  Finally, \pytracer
+overloads the builtin \texttt{type} function to preserve the type of the wrapped
+instance.
 
@@
 
-In functional programming, iterators traverse containers lazily, meaning that the next element in the sequence is only computed when the application uses it.
-This technique allows for the manipulation of virtually infinite sequences with finite memory.
-However, it implies that no complete mapping of the container returned by an iterator exists in memory since the application computes each element on the fly.
-Therefore, iterators are not serializable which implies that \pytracer cannot save them to output traces.
-A workaround would be to convert iterators into explicit containers, however, this would increase the memory footprint significantly. \pytracer, therefore, does not instrument non-builtin iterators.
-
-% \begin{listing}
-% \begin{minipage}[t]{0.4\linewidth}
-%     \begin{lstlisting}[language=Python,style=customPython]
-% >>> import numpy as np
-% >>> x = np.array(range(10))
-% >>> index = np.array([1,-1],dtype=int)
-% >>> x[index]
-% >>> array([1, 9])
-%     \end{lstlisting}
-% \end{minipage}
-% \begin{minipage}[t]{0.4\linewidth}
-%     \begin{lstlisting}[language=Python,style=customPython]
-% >>> import numpy as np
-% >>> x = np.array(range(10))
-% >>> index = np.array([1,-1], dtype=object)
-% >>> x[index]
-% Traceback (most recent call last):
-%   File "<stdin>", line 1, in <module>
-% IndexError: arrays used as indices must be of integer (or boolean) type
-%     \end{lstlisting}
-% \end{minipage}
-% \caption{Illustration of the issue of using \texttt{frompyfunc} function to convert function to \texttt{ufunc}. Left: original code. Right: instrumented code. 
-% \tristan{This needs more explanation: where is the ufunc, what is the type returned by the original ufunc, and why does it crash in the instrumented version.} \Yohan{TODO}}
-%     \label{fig:numpy_array_index_issue}
-% \end{listing}
+In functional programming, iterators traverse containers lazily, meaning that
+the next element in the sequence is only computed when the application uses it.
+This technique allows for the manipulation of virtually infinite sequences with
+finite memory. However, it implies that no complete mapping of the container
+returned by an iterator exists in memory since the application computes each
+element on the fly. Therefore, iterators are not serializable which implies that
+\pytracer cannot save them to output traces. A workaround would be to convert
+iterators into explicit containers, however, this would increase the memory
+footprint significantly. \pytracer, therefore, does not instrument non-builtin
+iterators.
 
@@
 
-\pytracer detects numerical instabilities by computing summary statistics across multiple executions perturbed with numerical noise.
-While \pytracer's instrumentation, trace aggregation, and visualization work with various types of numerical noise, we experimented primarily with Monte-Carlo Arithmetic (MCA) as it is an accurate model for floating-point errors.
+\pytracer detects numerical instabilities by computing summary statistics across
+multiple executions perturbed with numerical noise. While \pytracer's
+instrumentation, trace aggregation, and visualization work with various types of
+numerical noise, we experimented primarily with Monte-Carlo Arithmetic (MCA) as
+it is an accurate model for floating-point errors~\addCite{\cite{verificarlo}}.
 
@@
 
-Three  main  approaches  exist  to  detect  numerical  instabilities:  stochastic  arithmetic,  uncertainty  or  sensitivity analysis [23], and random seed analysis [11].
-PyTracer is agnostic to the noise model used and therefore works for all methods mentioned.
-For our use cases, we focus on stochastic arithmetic since it does not make any assumption about the noise model, in contrast to sensitivity analysis
-
-Stochastic arithmetic leverages randomness to estimate numerical instabilities coming from the use of floating-point representations.
-The main idea is to treat round-off errors as random variables and characterize them statistically.
-Monte Carlo Arithmetic (MCA)~\cite{parker1997monte} uses this principle by introducing two improvements:
-(i) a virtual precision parameter, allowing to simulate reduced working precision, and (ii) different perturbation modes to introduce perturbations
-on function inputs or output.
-MCA replaces each floating-point number $x$ with a stochastic counterpart computed as:
+Three  main  approaches  exist  to  detect  numerical  instabilities:
+stochastic  arithmetic,  uncertainty  or  sensitivity analysis [23], and random
+seed analysis [11].  \hl{PyTracer is agnostic to the noise model used and therefore
+    works for all methods mentioned}.  For our use cases, we focus on stochastic
+arithmetic since it does not make any assumption about the noise model, in
+contrast to sensitivity analysis\add{.}
+
+Stochastic arithmetic leverages randomness to estimate numerical instabilities
+coming from the use of floating-point representations. The main idea is to treat
+round-off errors as random variables and characterize them statistically. Monte
+Carlo Arithmetic (MCA)~\cite{parker1997monte} uses this principle by introducing
+two improvements: (i) a virtual precision parameter, allowing to simulate
+reduced working precision, and (ii) different perturbation modes to introduce
+perturbations on function inputs or output. MCA replaces each floating-point
+number $x$ with a stochastic counterpart computed as:
 \[
@@
 \]
-where $\beta$ is the number base, $e_x$ is the magnitude of $x$, $t$ the virtual precision and $\xi \in (-\frac{1}{2},\frac{1}{2})$ is a random uniform variable.
-Virtual precision allows for the simulation of reduced working precision.
-MCA can be applied in three modes: Random Rounding (RR), Precision Bounding (PB), and full MCA, which apply function $inexact$ to the output, the inputs, or both, respectively.
-While the RR mode is equivalent to stochastic rounding, the PB mode can also identify catastrophic cancellations.
-
-Stochastic arithmetic quantifies numerical error using the number of significant digits $s$ estimated among the sampled values.
-A common formula to determine this number from MCA samples is presented in~\cite{parker1997monte}:
+where $\beta$ is the number base, $e_x$ is the magnitude of $x$, $t$ the virtual
+precision and $\xi \in (-\frac{1}{2},\frac{1}{2})$ is a random uniform variable.
+Virtual precision allows for the simulation of reduced working precision. MCA
+can be applied in three modes: Random Rounding (RR), Precision Bounding (PB),
+and full MCA, which apply function $inexact$ to the output, the inputs, or both,
+respectively. While the RR mode is equivalent to stochastic rounding, the PB
+mode can also identify catastrophic cancellations.
+
+Stochastic arithmetic quantifies numerical error using the number of significant
+digits $s$ estimated among the sampled values. A common formula to determine
+this number from MCA samples is presented in~\cite{parker1997monte}:
 \begin{equation}
@@
 \end{equation}
-where $\mu$ and $\sigma$ are the sample mean and standard deviation of a variable sampled with MCA.  
-Sohier et al.~\cite{sohier2018confidence} recently provided a generalization of this formula to include confidence intervals.
-
-We enable MCA in Python programs via Verificarlo~\cite{verificarlo}, a clang-based compiler~\cite{lattner2008llvm} that replaces floating-point operations by a generic call to a configurable floating-point model.
-Several floating-point models are available~\cite{chatelain2019automatic,chatelain2019outils}, also called backends.
-\pytracer leverages ``fuzzy"~\cite{kiar2020comparing}, a collection of software tools compiled with Verificarlo.
-In particular, fuzzy provides MCA-instrumented versions of the Python interpreter as well as the BLAS, LAPACK, NumPy, SciPy, and scikit-learn libraries, which enables MCA for a wide range of existing scientific Python programs.
-Fuzzy is available in Verificarlo's GitHub organization at \href{https://github.com/verificarlo/fuzzy}{\url{github.com/verificarlo/fuzzy}}.
-
-% As the time of writing this article, fuzzy provides 5 levels of instrumentation (each level N including the lower levels):
-% \begin{enumerate}
-%     \item BLAS + LAPACK
-%     \item Python interpreter
-%     \item Numpy
-%     \item SciPy
-%     \item Scikit-learn
-% \end{enumerate}
+where $\mu$ and $\sigma$ are the sample mean and standard deviation of a
+variable sampled with MCA.  
+Sohier et al.~\cite{sohier2018confidence} recently provided a generalization of
+this formula to include confidence intervals.
+
+We enable MCA in Python programs via Verificarlo~\cite{verificarlo}, a
+clang-based compiler~\cite{lattner2008llvm} that replaces floating-point
+operations by a generic call to a configurable floating-point model. Several
+floating-point models are
+available~\cite{chatelain2019automatic,chatelain2019outils}, also called
+backends. \pytracer leverages ``fuzzy"~\cite{kiar2020comparing}, a collection of
+software tools compiled with Verificarlo. In particular, fuzzy provides
+MCA-instrumented versions of the Python interpreter as well as the BLAS, LAPACK,
+NumPy, SciPy, and scikit-learn libraries, which enables MCA for a wide range of
+existing scientific Python programs. Fuzzy is available in Verificarlo's GitHub
+organization at
+\href{https://github.com/verificarlo/fuzzy}{\url{github.com/verificarlo/fuzzy}}.
 
@@
 
-\pytracer stores traces in the pickle format, a binary format to serialize Python objects.
-The main advantages of the pickle format compared to other serialization approaches such as marshal or JSON are its ability to serialize most Python objects and its native compression.
-In addition, pickle writes Python objects sequentially, which preserves the temporal ordering required by subsequent trace analyses.
-
-Traces store numerical values at the granularity of function calls.
-When the application invokes a function, \pytracer saves a call input object containing contextual information (function's name, module's function, stacktrace) and the values of the function arguments.
-When the function returns, \pytracer saves a similar call output object containing the returned value.
+\pytracer stores traces in the pickle format, a binary format to serialize
+Python objects. The main advantages of the pickle format compared to other
+serialization approaches such as marshal or JSON are its ability to serialize
+most Python objects and its native compression.  In addition, pickle writes
+Python objects sequentially, which preserves the temporal ordering required by
+subsequent trace analyses.
+
+Traces store numerical values at the granularity of function calls. When the
+application invokes a function, \pytracer saves a call input object containing
+contextual information (function's name, module's function, stacktrace) and the
+values of the function arguments. When the function returns, \pytracer saves a
+similar call output object containing the returned value.
 
@@
 
-Once traces are available, \pytracer sequentially parses them and computes the mean, standard deviation, and the number of significant digits (as in Equation~\ref{eq:sig-digits}) of all saved values.
-\pytracer saves these summary statistics in an HDF5 file, a hierarchical format that facilitates visual browsing since only
-required information are loaded when requested by the user.
-% \gkmod{}{Q: Is there a reason we don't also use HDF for the raw traces? Lack of native compression?} \Yohan{Principaly because you can't save any Python objects in HDF5 while you can with Pickle}
-This operation critically relies on the ordering of call input and output objects in the traces.
-Therefore, it assumes that the application is single-threaded and that the control flow does not depend on a random state.
-% Techniques to overcome this limitation are discussed in the discussion section.
+Once traces are available, \pytracer sequentially parses them and computes the
+mean, standard deviation, and the number of significant digits (as in
+Equation~\ref{eq:sig-digits}) of all saved values. \pytracer saves these summary
+statistics in an HDF5 file, a hierarchical format that facilitates visual
+browsing since only required information are loaded when requested by the user.
+This operation critically relies on the ordering of call input and output
+objects in the traces. Therefore, it assumes that the application is
+single-threaded and that the control flow does not depend on a random state. 
+\add{Therefore, \mbox{\pytracer} cannot merge traces resulting from a different control flow path
+    and will stop the parsing when encountering one.}
 
@@
     \centering
-    \includegraphics[width=\textwidth]{figure/pytracer_layout.pdf}
+    \includegraphics[width=\columnwidth]{figure/pytracer_layout.pdf}
     \caption{Pytracer visualization layout.}
@@
 
-To aggregate traces, \pytracer successively unpickles call objects in each trace, checks
-that the call objects refer to the same function and stacktrace, and terminates the parsing otherwise.
-PyTracer stores function arguments or returned values in a NumPy array for each matching call object to compute statistics.
-For compound objects such as tuples, dictionaries, or objects, it recursively parses the fields until finding
-numeric types or NumPy arrays of numeric types.
+To aggregate traces, \pytracer successively unpickles call objects in each
+trace, checks that the call objects refer to the same function and stacktrace,
+and terminates the parsing otherwise. PyTracer stores function arguments or
+returned values in a NumPy array for each matching call object to compute
+statistics. For compound objects such as tuples, dictionaries, or objects, it
+recursively parses the fields until finding numeric types or NumPy arrays of
+numeric types.
 
 \subsection{Interactive visualization}
-The third main component of \pytracer is its interactive trace visualizer built with Plotly Dash~\cite{plotly}, a Python framework for web visualization.
-Plotly Dash abstracts the low-level details of web applications in a highly customizable development interface allowing to offload heavy computations to a server if necessary.
-% \gkmod{}{Q: does it support using a remote server with forwarding, in the event that your local system isn't that beefy?} \Yohan{Yes, that the meaning of the sentence. Should we reword it?}
-Figure~\ref{fig:visu-layout} presents the general layout of the \pytracer visualizer, divided into five sub-components:
+The third main component of \pytracer is its interactive trace visualizer built
+with Plotly Dash~\cite{plotly}, a Python framework for web visualization. Plotly
+Dash abstracts the low-level details of web applications in a highly
+customizable development interface allowing to offload heavy computations to a
+server if necessary. Figure~\ref{fig:visu-layout} presents the general layout of
+the \pytracer visualizer, divided into five sub-components:
 \begin{enumerate}
- \item Timeline view: This view displays the values of each input and output for a given function at a given invocation.
-By default, \pytracer shows the number of significant digits computed across the traces.
-The mean and standard deviation across perturbed samples are also available.
-%  \gkmod{}{Q: mean/stdev of what?
-the inputs/outputs?
-But what if they are on a totally different scale (e.g.
-log(0.0001)}.
-\Yohan{All values, a value mean one input or one output.
-For different scale, you can switch to the log scale.
-It is worth mentioning it?}
- The visualizer uses an upper triangle for inputs and a lower triangle for outputs.
-\pytracer internally represents all values as NumPy arrays.
-In the case of non-scalar values or types that cannot be trivially cast into NumPy arrays, \pytracer splits the value into several variables.
-Hence, \pytracer will transform a class containing $n$ floating-point parameters into $n$ variables.
-Each variable is prefixed with the original value and postfixed with the name of the parameter.
-%  \gkmod{}{Q: how is this managed for the sake of interpretability?
-E.g.
-if one of the components has very low significance and another few are fine, how can I easily identify where in my sequence we have the drop in precision?} \Yohan{You can click on the value of interest in the legend and it will hide the others.
-}
-    Finally, non-scalar values (vectors or matrices) are represented by their average and can be inspected with the Zoom view (see below).
- \item Gantt chart view: This view displays the call graph as a Gantt chart representing the instrumented functions. Each function call is represented with a bar.
-    The time overlaps reflect the caller/callee relation.
-    For example, in the figure, \texttt{function1} calls \texttt{function2} that itself calls \texttt{function4} and \texttt{function5}. 
-    This view provides insights on the calling context for each function, which may influence numerical stability.
-    % \gkmod{}{Note: this is a non-standard layout for gantt charts...
-normally the width/overlap is determined by time of start + duration.
-Is that information contained somewhere in here?
-If not, will a very fast function that calls sub-functions, say, 1000 times look longer than a very slow function that doesn't call any subfunctions?}
-    % \Yohan{I don't keep the duration because the different traces may have different time execution profiles and it will not make sense to average times.
-Moreover, since we focus on the numerical stability and not on performance, we only care about the call order.
-Yes it will look longer because the unit of the X-axis is the invocation, not the time.}
- \item  Source code view: This view displays a local snapshot of the source code file of the variable hovered in the timeline view. 
- \item Zoom view: This view provide details about non-scalar values. For example, a matrix may have instabilities around its diagonal but not in other regions.
-    The visualizer also provides additional metrics such as array shape, infinite norm, or condition number.
-\item  Functions list view: This view allows the user to select the functions plotted in the timeline view.
+    \item Timeline view: This view displays the values of each input and output
+          for a given function at a given invocation. By default, \pytracer
+          shows the number of significant digits computed across the traces. The
+          mean and standard deviation across perturbed samples are also
+          available. The visualizer uses an upper triangle for inputs and a
+          lower triangle for outputs. \pytracer internally represents all values
+          as NumPy arrays. In the case of non-scalar values or types that cannot
+          be trivially cast into NumPy arrays, \pytracer splits the value into
+          several variables. Hence, \pytracer will transform a class containing
+          $n$ floating-point parameters into $n$ variables. Each variable is
+          prefixed with the original value and postfixed with the name of the
+          parameter. Finally, non-scalar values (vectors or matrices) are
+          represented by their average and can be inspected with the Zoom view
+          (see below).
+    \item Gantt chart view: This view displays the call graph as a Gantt chart
+          representing the instrumented functions. Each function call is
+          represented with a bar. The time overlaps reflect the caller/callee
+          relation. For example, in the figure, \texttt{function1} calls
+          \texttt{function2} that itself calls \texttt{function4} and
+          \texttt{function5}. This view provides insights on the calling context
+          for each function, which may influence numerical stability.
+    \item  Source code view: This view displays a local snapshot of the source
+          code file of the variable hovered in the timeline view.
+    \item Zoom view: This view provide details about non-scalar values. For
+          example, a matrix may have instabilities around its diagonal but not
+          in other regions. The visualizer also provides additional metrics such
+          as array shape, infinite norm, or condition number.
+    \item  Functions list view: This view allows the user to select the
+          functions plotted in the timeline view.
 \end{enumerate}
@@
 
-We evaluated \pytracer on two widely-used Python libraries: SciPy~\cite{virtanen2020scipy}, the main library for scientific computing in Python, and  scikit-learn~\cite{pedregosa2011scikit}, a reference machine-learning framework that
- implements a wide range of state-of-the-art algorithms.
-For each library, we executed the software examples provided in their respective GitHub repositories.
-We traced each example five times, having activated MCA in the Python interpreter, BLAS, LAPACK, NumPy, SciPy, and scikit-learn.
-We repeated the experiment with two MCA modes, Random Rounding (RR) and Full MCA, resulting in 2 experiments for each example.
-We used the default virtual precision in Verificarlo, namely 24 bits for single-precision floating-point values and 53 bits for double-precision values, which simulates machine error.
-We used Python-3.8.5, NumPy-1.19.1, SciPy-1.5.4, and scikit-learn-0.23.2.
-%  \tristan{Report scipy and sklearn versions used.}
+We evaluated \pytracer on two widely-used Python libraries:
+SciPy~\cite{virtanen2020scipy}, the main library for scientific computing in
+Python, and  scikit-learn~\cite{pedregosa2011scikit}, a reference
+machine-learning framework that implements a wide range of state-of-the-art
+algorithms. For each library, we executed the software examples provided in
+their respective GitHub repositories. We traced each example five times, having
+activated MCA in the Python interpreter \add{as well as} BLAS, LAPACK, NumPy, SciPy, and
+scikit-learn. \add{Only instrumented the Python interpreter would lead to
+    only perturbe pure Python floating-point operations and thus to miss
+    operations in compiled codes (i.e. Cython and shared libraries).}
+\hl{We repeated the experiment with two MCA modes, Random Rounding
+    (RR) and Full MCA, resulting in 2 experiments for each example}. We used the
+default virtual precision in Verificarlo, namely 24 bits for single-precision
+floating-point values and 53 bits for double-precision values, which simulates
+machine error. We used Python-3.8.5, NumPy-1.19.1, SciPy-1.5.4, and
+scikit-learn-0.23.2.
 
@@
 
-Table~\ref{tab:pytracer_results_summary} summarizes
-\pytracer's outcome on SciPy and scikit-learn examples.
-Columns \textit{trace} and \textit{parse} report on the tracing and aggregation steps with three possible outcomes: 1) green for success, meaning that the execution ended well and no issues were raised by the application, 2) red for numerical error in the application, meaning that the execution raised a Python error before the end, and 3) orange for errors due to the fuzzy noise injection that are not considered numerical errors, meaning that the execution raised a Python error but due to a perturbation that should not have been introduced (i.e.
-a floating-point value representing an integer).
-% \gkmod{}{Q: What does "success" or the other labels actually mean? What is the threshold for numerical errors, e.g.}
-% , like for instance index errors due to an index shift.
-% \tristan{Explain what this is, in a setence here or with a subsubsection if it requires more}. 
-Overall, the tracing and parsing of SciPy and scikit-learn examples in Random Rounding mode was entirely successful for 32/40 examples and showed an average precision loss of 8 bits.
-The remaining examples failed due to numerical errors in the libraries, which we discuss hereafter.
-The instrumentation with Full MCA is more invasive and reduced the number of successful executions to 12/40.
-Among the 28/40 failed executions, one failed due to an actual numerical error (\texttt{Bayesian Ridge Regression} example) and the other ones failed due to
+Table~\ref{tab:pytracer_results_summary} summarizes \pytracer's outcome on SciPy
+and scikit-learn examples. Columns \textit{trace} and \textit{parse} report on
+the tracing and aggregation steps with three possible outcomes: 1) green for
+success, meaning that the execution ended well and no issues were raised by the
+application, 2) red for numerical error in the application, meaning that the
+execution raised a Python error before the end, and 3) orange for errors due to
+the fuzzy noise injection that are not considered numerical errors, meaning that
+the execution raised a Python error but due to a perturbation that should not
+have been introduced (i.e. a floating-point value representing an integer).
+Overall, the tracing and parsing of SciPy and scikit-learn examples in Random
+Rounding mode was entirely successful for 32/40 examples and showed an average
+precision loss of 8 bits. The remaining examples failed due to numerical errors
+in the libraries, which we discuss hereafter. The instrumentation with Full MCA
+is more invasive and reduced the number of successful executions to 12/40. Among
+the 28/40 failed executions, one failed due to an actual numerical error
+(\texttt{Bayesian Ridge Regression} example) and the other ones failed due to
 perturbations that should not have been introduced.
-% \tristan{finish this sentence}.
-% \gkmod{}{Q: Does this mean the 28 failed, or completed but poorly? In general, the way the states are being referred to so far in the results are rather ambiguous}
-
-Column \textit{sigbits} in Table~\ref{tab:pytracer_results_summary} summarizes the precision for the main outputs of SciPy and scikit-learn examples. 
-We measured the precision in significant bits on the final primary example output by taking the element-wise mean for non-scalar values and, if the example produces many outputs, the average value among all of them.
-The numerical quality across all examples varies from 0 to 52, with an average of 44 significant bits.
-For both modes, we note that only two examples failed due to a numerical error
-% \tristan{can we see that in the table? if not, don't comment on it, it is puzzling. Could you show that in the table by using the same error symbols as in Table 2?} 
-(\texttt{face\_recognition} for RR and \texttt{Bayesian Ridge Regression} for Full MCA).
-% even though this number is underestimated since Full MCA mode is more intrusive than RR mode.
-% Indeed, most of the examples produce an error caused by the fuzzy noise injection.
-\gkmod{}{Note: I don't understand what is being said in the rest of the sentence following the parentheses} \Yohan{Full MCA mode perturbs values that should not be perturbed and so
-% it triggers artificial bugs (as for numpy arange)}
-
-\begin{table}[]
+
+Column \textit{sigbits} in Table~\ref{tab:pytracer_results_summary} summarizes
+the precision for the main outputs of SciPy and scikit-learn examples. We
+measured the precision in significant bits on the final primary example output
+by taking the element-wise mean for non-scalar values and, if the example
+produces many outputs, the average value among all of them. The numerical
+quality across all examples varies from 0 to 52, with an average of 44
+significant bits. For both modes, we note that only two examples failed due to a
+numerical error (\texttt{face\_recognition} for RR and \texttt{Bayesian Ridge
+    Regression} for Full MCA).
+
+\begin{table*}[]
     \centering
@@
             \hline
-    %        &               RR                 &                 MCA               \\
-    %        &  numpy         &   no numpy      &      numpy      &     no numpy    \\
-    %        & run   & parse  &  run   &  parse &  run   & parse  & run    & parse  \\
-
             \multicolumn{1}{|c|}{ \multirow{20}{2em}{ \rotatebox{90}{SciPy} } } & 
@@
             \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \multiRf                                                 & \valid & \valid   & \s{51}  & \warn  & \cross & \s{-}   \\
-    \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{}  & \bsplineRf    & \valid & \valid &10 &  \valid & \valid & 10\\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \bsplineRf                                               & \valid & \valid   & 10      & \valid & \valid & 10      \\
             \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \splineOneDRf                                            & \valid & \cross   & \s{52}  & \warn  & \cross & \s{52}  \\
@@
             \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \slsqpRf                                                 & \valid & \valid   & 45      & \valid & \valid & 44      \\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \lsmRf    & \valid & \valid &\s{48} & \warn  & \cross & \s{-} \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \lsmRf                                                   & \valid & \valid   & \s{48}  & \warn  & \cross & \s{-}   \\
             \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \nelderRf                                                & \valid & \valid   & 44      & \valid & \valid & 42      \\
@@
             \hline
-%     \end{tabular}
-% \end{subfigure}
-%     \label{tab:pytracer_scipy_results_summary}
-% % \end{table}
-% % \begin{table}[]
-%     \centering
-% \begin{subfigure}[t]{.8\linewidth}
-%     \begin{tabular}{|c|c|c|c|c|c|c|}
-%     \hline
-%     \multirow{2}{5em}{Application} & \multicolumn{3}{c|}{RR} & \multicolumn{3}{c|}{MCA} \\\cline{2-7}
-%                                 & trace & parse & result &  trace & parse & result \\
-%     \hline
-    %        &               RR                 &                 MCA               \\
-    %        &  numpy         &   no numpy      &      numpy      &     no numpy    \\
-    %        & run   & parse  &  run   &  parse &  run   & parse  & run    & parse  \\
-
             \multicolumn{2}{|c|}{ \multirow{20}{2em}{ \rotatebox{90}{Scikit-learn} } }
@@
     \label{tab:pytracer_results_summary}
-\end{table}
-
-    % \caption{
-    % \pytracer execution summary on SciPy examples.\\RR: Random Rounding.
-trace: outcome of \pytracer tracing, parse: outcome of \pytracer trace parsing and aggregation.
-\valid: successful run, \warn: error in fuzzy noise injection, \cross: numerical error or divergent traces.
-    % }
+\end{table*}
 
@@
 \label{sec:impact_mca_modes}
-Random Rounding perturbs only the result of a floating-point operation while Full MCA perturbs both the inputs and the result. 
-Therefore, Full MCA may trigger catastrophic cancellations while Random Rounding only introduces round-off errors which generally have a lesser impact.
-Moreover, Random Rounding preserves exact operations --- operations where the result can be exactly represented at the virtual precision --- while Full MCA does not.
-
-\pytracer can only aggregate traces obtained from the same control flow path.
-In particular, program branches triggered by an unstable floating-point comparison lead to different control flows and result in parsing errors.
-For example, comparing a residual error or the distance between two points to a strict threshold in an iterative scheme generally results in unstable branches. 
-Full MCA even perturbs exact values such as integers represented with floating-point values, leading to many execution failures.
-For instance, the \texttt{fft1} example from SciPy raised an \texttt{ValueError: operands could not be broadcast together with shapes (601,) (600,)} error due to an array shape mismatch.
-A closer inspection showed that one of the arrays involved in the error was created with the NumPy function \texttt{linspace} that itself calls function \texttt{arange} (Listing~\ref{fig:pyarray_range_code}).
-Lines 3174-3178 show that the function stores the array size in a floating-point value that will be perturbed by Full MCA, as shown in Table~\ref{tab:mca_result_linspace}, resulting in array sizes that fluctuate between N and N+1.
-It is worth noting that 78\% of execution issues encountered in Full MCA mode instrumentation
-are due to this type of ``typing" errors.  
-Those code regions should not be perturbed by MCA since the injected noise does not make sense.
-% \gkmod{}{; however, given the typing errors in the source code, they are still susceptible to naturally occurring floating point errors}.
-\Yohan{Not really since all rounding cases were carefully handled by the developers.
-We are facing here the same issue as for libmath:
-% people take into account the possible rounding outcomes and the code is written knowing that
-% the floating-point numbers behave like that. We break the assumptions by introducing noise here.}
-% \tristan{conclusion: ces regions du code ne devraient pas etre bruitees car le bruit n'a pas de sens ici (exemple du spin dans -1/2,1/2. Ca correspond aux ?}
-% While they do not lead to any numerical issue, typing errors should still be fixed
-% by improving the Full MCA mode instrumentation in order to preserve code correctness.
-% \tristan{do we really mean that given your answer to my comment below?}. 
-% \Yohan{By reading again this sentence, I agree that it is confusing. 
-% It suggests that we should fixed the code while my idea was to fix the MCA instrumentation.}
-% We provide solutions to help MCA better work with those cases in the discussion section.
-
-% \tristan{Check this last sentence, we need to provide some sort of recommendations}. \tristan{how about opening a PR in numpy to fix this error?}
-% \Yohan{For this case, they use the math.ceil to correctly round the number, I think the fix is more on the MCA side to
-% correctly handle exact number than on the NumPy side.}
-
-% \begin{figure}
-%     \begin{lstlisting}[language=Python,style=customPython,numbers=left, firstnumber=11]
-% # Number of sample points
-% N = 600
-% # sample spacing
-% T = 1.0 / 800.0
-% x = np.linspace(0.0, N*T, N, endpoint=False)
-% y = np.sin(50.0 * 2.0*np.pi*x) + 0.5*np.sin(80.0 * 2.0*np.pi*x)
-% yf = fft(y)
-% w = blackman(N)
-% ywf = fft(y*w)
-%     \end{lstlisting}
-%     \label{fig:fft1_code}
-% \caption{Code snippet from \texttt{fft\_1D} illustrating issue arising when using Full MCA mode.
-% Line 19 raises \texttt{ValueError: operands could not be broadcast together with shapes (601,) (600,)} since
-% arrays \texttt{y} and \texttt{w} do not have the same shape. This is due to random errors introduces by 
-% Full MCA mode in the \texttt{linspace} function.
-% }
-% \end{figure}
-
-% \begin{figure}
-%     \begin{lstlisting}[language=Python,style=customPython,numbers=left, firstnumber=1, mathescape=true]
-% def linspace(start, stop, num=50, endpoint=True, retstep=False, dtype=None,
-%              axis=0):
-%     num = operator.index(num) // 3 $\lstsetnumber{\ldots}$
-%     ...$\lstresetnumber\setcounter{lstnumber}{5}$
-%     div = (num - 1) if endpoint else num // 6  $\lstsetnumber{\ldots}$
-%     ...$\lstresetnumber\setcounter{lstnumber}{13}$
-%     delta = stop - start // 14
-%     y = _nx.arange(0, num, dtype=dt).reshape((-1,) + (1,) * ndim(delta)) // 15
-%     \end{lstlisting}
-%     \label{fig:linspace_code}
-% \caption{Code snippet from \texttt{linspace} function from numpy package. 
-%     It uses the \textit{arange} function implemented as a Cython function (fig.~\ref{fig:pyarray_range_code}) to create the array. 
-% }
-% \end{figure}
+Random Rounding perturbs only the result of a floating-point operation while
+Full MCA perturbs both the inputs and the result. Therefore, Full MCA may
+trigger catastrophic cancellations while Random Rounding only introduces
+round-off errors which generally have a lesser impact. Moreover, Random Rounding
+preserves exact operations --- operations where the result can be exactly
+represented at the virtual precision --- while Full MCA does not.
+
+\pytracer can only aggregate traces obtained from the same control flow path. In
+particular, program branches triggered by an unstable floating-point comparison
+lead to different control flows and result in parsing errors. For example,
+comparing a residual error or the distance between two points to a strict
+threshold in an iterative scheme generally results in unstable branches. Full
+MCA even perturbs exact values such as integers represented with floating-point
+values, leading to many execution failures. For instance, the \texttt{fft1}
+example from SciPy raised an \texttt{ValueError: operands could not be broadcast
+    together with shapes (601,) (600,)} error due to an array shape mismatch. A
+closer inspection showed that one of the arrays involved in the error was
+created with the NumPy function \texttt{linspace} that itself calls function
+\texttt{arange} (Listing~\ref{fig:pyarray_range_code}). Lines 3174-3178 show
+that the function stores the array size in a floating-point value that will be
+perturbed by Full MCA, as shown in Table~\ref{tab:mca_result_linspace},
+resulting in array sizes that fluctuate between N and N+1. It is worth noting
+that 78\% of execution issues encountered in Full MCA mode instrumentation are
+due to this type of ``typing" errors.  
+Those code regions should not be perturbed by MCA since the injected noise does
+not make sense.
 
@@
     \begin{lstlisting}[language=C,style=customC,numbers=left, firstnumber=3163, mathescape=true]
-/*NUMPY_API
-  Arange,
-*/
+/* NUMPY_API Arange, */
 NPY_NO_EXPORT PyObject *
-PyArray_Arange(double start, double stop, double step /* default 1 */, int type_num) 
-{
+PyArray_Arange(double start, double stop, double step, int type_num) {
     npy_intp length; 
@@
     ...$\lstresetnumber\setcounter{lstnumber}{3201}$
-    range = (PyArrayObject *)PyArray_New(&PyArray_Type, 1, &length, type_num, $\lstsetnumber{}$
-                        NULL, NULL, 0, 0, NULL);
+    range = (PyArrayObject *)PyArray_New(&PyArray_Type, 1, &length, type_num, NULL, NULL, 0, 0, NULL);
     \end{lstlisting}
@@
 
-\begin{table}[]
+\begin{table}[t]
     \centering
-    \footnotesize
-    \begin{tabularx}{{\textwidth}}{cccc>{\centering\arraybackslash}X>{\centering\arraybackslash}X>{\centering\arraybackslash}X}
+    % \begin{tabular}{ccccccc}
+    %     \thickhline
+    %     \textbf{Mode} & \textbf{start} & \textbf{stop} & \textbf{step} & \textbf{delta}                & \textbf{tmp\_len} & \textbf{ceil(tmp\_len)} \\
+    %     \hline
+    %     Exact         & 0              & 600           & 1             & 600                           & 600               & 600                     \\
+    %     RR            & 0              & 600           & 1             & 600 $\pm$ 0.0                 & 600 $\pm$ 0.0     & 600 $\pm$ 0.0           \\
+    %     MCA           & 0              & 600           & 1             & 599.9999999999999 $\pm$ 8e-14 & 600.0 $\pm$ 8e-14 & 600.01 $\pm$ 0.0995     \\
+    %     \thickhline        
+    % \end{tabular}
+    \begin{tabular}{l|ccc}
+        \hline                                                   
+        \textbf{Mode}           & Exact & RR            & MCA                   \\
+        \hline
+        \texttt{start}          & 0     & 0             & 0                     \\
+        \texttt{stop}           & 600   & 600           & 600                   \\
+        \texttt{step}           & 1     & 1             & 1                     \\ 
+        \texttt{delta}          & 600   & 600 $\pm$ 0.0 & 599.9...9 $\pm$ 8e-14 \\
+        \texttt{tmp\_len}       & 600   & 600 $\pm$ 0.0 & 600.0 $\pm$ 8e-14     \\
+        \texttt{ceil(tmp\_len)} & 600   & 600 $\pm$ 0.0 & 600.01 $\pm$ 0.0995   \\
         \thickhline        
-    \textbf{Mode}  & \textbf{start} & \textbf{stop} & \textbf{step} & \textbf{delta} & \textbf{tmp\_len} & \textbf{ceil(tmp\_len)}  \\
-    \hline
-    Exact & 0 & 600  & 1 & 600                             & 600                            & 600             \\
-    RR    & 0 & 600  & 1 & 600 $\pm$ 0.0                   & 600 $\pm$ 0.0                  & 600 $\pm$ 0.0   \\
-    MCA    & 0 & 600  & 1 & 599.9999999999999 $\pm$ 8e-14  & 600.0 $\pm$ 8e-14 &  600.01 $\pm$ 0.0995\\
-            \thickhline
-
-    \end{tabularx}
+    \end{tabular}
     \caption{Results obtained through lines 3177-3190 in Listing~\ref{fig:pyarray_range_code}.
@@
 
-% \subsubsection{Overall numerical quality}
-
-% \begin{table}
-% \small
-% \begin{subfigure}[t]{.5\linewidth}
-%     \centering
-%     \begin{tabular}{|l|c|c|}
-%     \hline 
-%     Example & RR & MCA \\
-%     \hline
-%     \discreteCosineRF & 52 & 47 \\ 
-%     \fftOneDRf & 41 & \swarn \\
-%     \fftTwoDRf & 52 & 52  \\
-%     \hline
-%     \interOneDRf & 51 & \swarn   \\
-%     \multiRf & 51 & \swarn \\
-%     \bsplineRf & 10 & 10  \\
-%     \splineOneDRf & 52 & 52 \\
-%     \splineTwoDRf & 10 & \swarn \\
-%     \hline
-%     \bfgsRf & 48 & 46 \\
-%     \globalRf & 17 & \swarn \\
-%     | SHGO\footnote{Simplicial Homology Global Optimization} & 25 & \swarn \\
-%     | Dual Annealing & 4 & \swarn \\
-%     | Differential Evolution & 0 & \swarn \\
-%     | Basin Hopping & 40 & \swarn \\
-%     | SHGO Sobol & 45 & \swarn \\
-%     \slsqpRf & 45 & 44 \\
-%     \lsmRf & 48 & \swarn \\
-%     \nelderRf & 44 & 42  \\
-%     \ncgRf & 48 & 47 \\
-%     \rootRf & 52 & 50 \\
-%     \rootLargRf & 29 & 26   \\
-%     \rootLargePredRf & 42 & 42 \\
-%     \trustExactRf & 48 & 46  \\
-%     \trustTruncRf & 48 & 46  \\
-%     \trustNCGRf & 52 & 47 \\
-%     \hline
-%     \end{tabular}
-% \end{subfigure}
-% \hspace{1cm}
-% \begin{subfigure}[t]{.5\linewidth}
-%     \begin{tabular}{|l|c|c|}
-%     \hline 
-%     Example & RR & MCA \\
-%     \hline
-%     \AdaboostRf & 48 & \swarn \\
-%     \brrRf & 25 & \scross  \\
-%     | $1^{st}$ dataset & nan & \scross \\
-%     | $2^{nd}$ dataset & 20 & \scross \\
-%     \onlineClassifierComparisonRf & 48 & \swarn  \\
-%     \kmeansRf & 52 & \swarn   \\
-%     \covarianceRf & 48 & \swarn   \\
-%     \decisionRf & 50 & 50  \\
-%     \digitsRf & 52 & 52 \\
-%     \faceRf & \scross & \scross \\
-%     \penaltyRf & - & -   \\
-%     \lassoRf & 48 & 47  \\
-%     \hyperplaneRf & 3 & \swarn  \\
-%     \mnistRf & 43 & \swarn \\
-%     \multitaskRf & 50 & 48   \\
-%     \ompRf & 52 & 52  \\
-%     \pcaRf & 48 & 48   \\
-%     \robustRf & 50 & 48   \\
-%     | Linear & 48 & 46 \\
-%     | RANSAC & 50 & 48 \\
-%     \toyRf & 35 & \swarn \\
-%     \svmRf & 43.5 &  \swarn  \\
-%     | Non-weighted & 44 & \swarn \\
-%     | Weighted & 43 & \swarn \\
-%     \tomographyRf & \swarn & \swarn  \\
-%     \weightedRf & 44 & \swarn   \\
-%     \hline
-%     \end{tabular}
-% \end{subfigure}
-%     \caption{Summary of examples precision for main outputs of SciPy (left) and scikit-learn (right) examples. 
-%     \textit{\swarn} values indicate runtime errors or an impossible traces aggregation,
-%     \scross values indicate numerical errors, and \textit{nan} stands for (\texttt{Not-A-Number}).
-%     The names example are linked to their source code.
-%     % \tristan{explain the meaning of nans here}
-%     \tristan{let's discuss the possibility to merge Table 4 in Tables 1 and 2}
-%     }
-%     \label{tab:pytracer_test_precision_summary}
-% \end{table}
-
 \subsection{SciPy}
@@
 We tested \pytracer on SciPy examples provided in the tutorial website section.
-% \tristan{Are these tests? If not we need to reword the begining of this section (I can do it, just let me know).}.
-% \Yohan{No you right, these are examples, not tests, I used the two words interchangeably.}
-SciPy is organized in several libraries targeting specific computing domains.
-We focused on \texttt{fftpack} (Fast Fourier Transform routines), \texttt{interpolate} (interpolation and smoothing splines), and \texttt{optimize} (Optimization and root-finding routines).
+SciPy is organized in several libraries targeting specific computing domains. We
+focused on \texttt{fftpack} (Fast Fourier Transform routines),
+\texttt{interpolate} (interpolation and smoothing splines), and
+\texttt{optimize} (Optimization and root-finding routines).
 
@@
 
-This package has three examples : \texttt{discrete\_cosine\_transform}, \texttt{fft\_1D}, and \texttt{fft\_2D}. All computations are done in double precision.
-The results for \texttt{discrete\_cosine\_transform},\texttt{fft\_1D} and  \texttt{fft\_2D} show
-precise numerical results with 48 significant bits on average. 
-We observe that the FFT computation is stable to noisy inputs. Figures~\ref{fig:fft1D_inputs} (inputs) and~\ref{fig:fft1D_outputs} (outputs)
-show the mean and standard deviation of the MCA samples. 
-The three columns correspond to the FFT computations of: 
+This package has three examples : \texttt{discrete\_cosine\_transform},
+\texttt{fft\_1D}, and \texttt{fft\_2D}. All computations are done in double
+precision. The results for \texttt{discrete\_cosine\_transform},\texttt{fft\_1D}
+and  \texttt{fft\_2D} show precise numerical results with 48 significant bits on
+average. We observe that the FFT computation is stable to noisy inputs.
+Figures~\ref{fig:fft1D_inputs} (inputs) and~\ref{fig:fft1D_outputs} (outputs)
+show the mean and standard deviation of the MCA samples. The three columns
+correspond to the FFT computations of: 
 \begin{enumerate}
@@
 
-Top row in Figures~\ref{fig:fft1D_inputs} and~\ref{fig:fft1D_outputs} 
-show the input mean value while the bottom row shows the standard deviation.
-The points with low magnitude in Figure~\ref{fig:fft1D_inputs} correspond 
-to inputs near 0 when the input of $\sin$ or 
-$\exp$ is close to $k\pi$, $k \in \mathbb{Z}$.
-Indeed, since MCA introduces a slight noise, the result is not exactly 0.
-We can see in Figure~\ref{fig:fft1D_inputs} 
-% \tristan{isn't it in Figure 3?} 
-% \Yohan{No figure 4, I'm talking about the MCA noise, so we look at the std}
-that the maximal noise introduced by MCA on the
-inputs is in the order of $10^{-14}$, two orders of magnitude higher than the 
-$ulp \simeq 10^-16$ for double precision. 
-This slight noise introduced can be interpreted as white noise on the input signal. 
-We can see on the bottom row of Figure~\ref{fig:fft1D_outputs} that the frequency noise is of 
-the same order of of magnitude as the input noise, which is expected. 
-The two peaks at x=38 and x=562 corresponds to the actual frequencies of the input signal.
+\add{The} top row in Figures~\ref{fig:fft1D_inputs} and~\ref{fig:fft1D_outputs} show the
+input mean value while the bottom row shows the standard deviation. The points
+with low magnitude in Figure~\ref{fig:fft1D_inputs} correspond to inputs near 0
+when the input of $\sin$ or $\exp$ is close to $k\pi$, $k \in \mathbb{Z}$.
+Indeed, since MCA introduces a slight noise, the result is not exactly 0. We can
+see in Figure~\ref{fig:fft1D_inputs} that the maximal noise introduced by MCA on
+the inputs is in the order of $10^{-14}$, two orders of magnitude higher than
+the $ulp \simeq 10^-16$ for double precision. This slight noise introduced can
+be interpreted as white noise on the input signal. We can see on the bottom row
+of Figure~\ref{fig:fft1D_outputs} that the frequency noise is of the same order
+of of magnitude as the input noise, which is expected. The two peaks at x=38 and
+x=562 corresponds to the actual frequencies of the input signal.
 
@@
 
-% \begin{figure}
-% \begin{minipage}{.5\textwidth}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/FFT/fft_x_real_sig_36.png}
-%     \caption{$\Re(x)$}
-%     \label{fig:my_label}
-% \end{minipage}
-% \begin{minipage}{.5\textwidth}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/FFT/fft_x_imag_sig_36.png}
-%     \caption{$\Im(x)$}
-%     \label{fig:my_label}
-% \end{minipage}
-% \begin{minipage}{.5\textwidth}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/FFT/fft_ret_real_sig_36.png}
-%     \caption{$\Re$(fft$(x))$}
-%     \label{fig:my_label}
-% \end{minipage}
-% \begin{minipage}{.5\textwidth}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/FFT/fft_ret_imag_sig_36.png}
-%     \caption{$\Im$(fft$(x))$}
-%     \label{fig:my_label}
-% \end{minipage}
-% \end{figure}
-
 \subsection{Interpolation}
 
-This package has five examples: \texttt{interpolation\_1D}, \texttt{multivariate\_data}, \texttt{bspline}, \texttt{spline\_1D} and \texttt{spline\_2D}.
-
-\texttt{interpolation\_1D} interpolates function $f(x)=\cos(\frac{-x^2}{9})$ with 11 points $x\in[0,10]$.
-For the five interpolation methods tested (linear, cubic, nearest, previous, next), the solution found is precise, up to 51 bits out of the 53 available.
-
-\texttt{multivariate\_data} interpolates the grid $f(x,y)=x(1-x)\cos(4\pi.x)  \sin(4\pi.y^2)^2$ with $(x,y) \in [0,1] \times [0,1]$.
-It samples 1,000 points for each coordinate and uses three interpolation methods: nearest, linear and cubic.
-Our results show a precision of 51 bits on average for the three methods.
-
-\texttt{bspline} compares two edge filters: \texttt{bisplev} evaluates a bivariate B-spline and its derivative whereas \texttt{convolved2d} convolves two 2-dimensional arrays.
-Figure~\ref{fig:bspline_rr}
-shows the significant bits, mean, and standard deviation 
-% \tristan{replace the figure references with labels in the figure, it would be much clearer} 
-maps for the two methods as well as the input image (Fig.~\ref{fig:bspline_original_image}).
-The middle row shows \texttt{sepfir2d} results and the bottom row shows \texttt{convol2d} results.
-Both methods exhibit similar precision, with 11 significant bits on average.
-Standard deviations maps on Figures~\ref{fig:bspline_bisplev_std} and~\ref{fig:bspline_convol2d_std} show that regions with low spatial frequencies correspond to regions with low standard deviation, similar to the FFT results.
-The SciPy tutorial mentions that \texttt{bisplev} is faster than \texttt{convol2d}.
-The comparable numerical precision observed in our experiments reinforce the use of \texttt{bisplev} over \texttt{convol2d} in this example.
-
-\texttt{spline\_1D} computes the 1D spline interpolation for $f(x)=\sin(x)$ on points $x=\frac{2\pi k}{8}, k \in [0, 10]$.
-The spline interpolation uses \texttt{splrep} to build the spline representation and \texttt{splrev} to evaluate the spline at any point.
-It also computes the integral by using \texttt{splint} and the root finder \texttt{sproot}.
-Although the traces diverge, we can analyze the partial aggregation for the \texttt{splrep}, \texttt{splev} and \texttt{splint}.
-The three functions show results with an average precision of 51 bits with RR mode.
-
-\texttt{spline\_2D} computes the 2D spline interpolation for function $z=(x+y)e^{-6(x^2+y^2)}$, with $(x,y) \in [-1,1]\times[-1,1]$ and a sampling of 21 points for each coordinate.
-\texttt{bisplrep} builds the spline representation with the $21 \times 21$ points of $z$ over 71 grid sampling points for $(x,y)$.
-Figure~\ref{fig:spline2d_rr} shows the results of the spline evaluation with \texttt{bisplev}.
-We observe a significant loss of precision in places, which follows
-an interesting pattern that could be further investigated.
-
-% \begin{figure}
-% \begin{minipage}{.3\textwidth}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/multivariate_data/nearest_ret_mean_log.png}
-% \end{minipage}
-% \begin{minipage}{.3\textwidth}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/multivariate_data/linear_ret_mean_log.png}
-% \end{minipage}
-% \begin{minipage}{.3\textwidth}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/multivariate_data/cubic_ret_mean_log.png}
-% \end{minipage}
-
-% \begin{minipage}{.3\textwidth}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/multivariate_data/nearest_ret_std_log.png}
-% \end{minipage}
-% \begin{minipage}{.3\textwidth}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/multivariate_data/linear_ret_std_log.png}
-% \end{minipage}
-% \begin{minipage}{.3\textwidth}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/multivariate_data/cubic_ret_std_log.png}
-% \end{minipage}
-%     \label{fig:multivariate_data_RR}
-%     \caption{\texttt{multivariate\_data} results within RR mode. Each column represents an 
-%     interpolation scheme, with from left to right, the nearest, linear and cubic method.
-%     Top row shows the log of the absolute mean value value while bottom row shows the log of the
-%     standard deviation. We can see that precision drops between local extremum when the 
-%     mean value is close to 0.}
-% \end{figure}
+This package has five examples: \texttt{interpolation\_1D},
+\texttt{multivariate\_data}, \texttt{bspline}, \texttt{spline\_1D} and
+\texttt{spline\_2D}.
+
+\texttt{interpolation\_1D} interpolates function $f(x)=\cos(\frac{-x^2}{9})$
+with 11 points $x\in[0,10]$. For the five interpolation methods tested (linear,
+cubic, nearest, previous, next), the solution found is precise, up to 51 bits
+out of the 53 available.
+
+\texttt{multivariate\_data} interpolates the grid $f(x,y)=x(1-x)\cos(4\pi.x)
+    \sin(4\pi.y^2)^2$ with $(x,y) \in [0,1] \times [0,1]$. It samples 1,000 points
+for each coordinate and uses three interpolation methods: nearest, linear and
+cubic. Our results show a precision of 51 bits on average for the three methods.
+
+\texttt{bspline} compares two edge filters: \texttt{bisplev} evaluates a
+bivariate B-spline and its derivative whereas \texttt{convolved2d} convolves two
+2-dimensional arrays. Figure~\ref{fig:bspline_rr} shows the significant bits,
+mean, and standard deviation maps for the two methods as well as the input image
+(Fig.~\ref{fig:bspline_original_image}). The middle row shows \texttt{sepfir2d}
+results and the bottom row shows \texttt{convol2d} results. Both methods exhibit
+similar precision, with 11 significant bits on average. Standard deviations maps
+on Figures~\ref{fig:bspline_bisplev_std} and~\ref{fig:bspline_convol2d_std} show
+that regions with low spatial frequencies correspond to regions with low
+standard deviation, similar to the FFT results. The SciPy tutorial mentions that
+\texttt{bisplev} is faster than \texttt{convol2d}. The comparable numerical
+precision observed in our experiments reinforce the use of \texttt{bisplev} over
+\texttt{convol2d} in this example.
+
+\texttt{spline\_1D} computes the 1D spline interpolation for $f(x)=\sin(x)$ on
+points $x=\frac{2\pi k}{8}, k \in [0, 10]$. The spline interpolation uses
+\texttt{splrep} to build the spline representation and \texttt{splrev} to
+evaluate the spline at any point. It also computes the integral by using
+\texttt{splint} and the root finder \texttt{sproot}. Although the traces
+diverge, we can analyze the partial aggregation for the \texttt{splrep},
+\texttt{splev} and \texttt{splint}. The three functions show results with an
+average precision of 51 bits with RR mode.
+
+\texttt{spline\_2D} computes the 2D spline interpolation for function
+$z=(x+y)e^{-6(x^2+y^2)}$, with $(x,y) \in [-1,1]\times[-1,1]$ and a sampling of
+21 points for each coordinate. \texttt{bisplrep} builds the spline
+representation with the $21 \times 21$ points of $z$ over 71 grid sampling
+points for $(x,y)$. Figure~\ref{fig:spline2d_rr} shows the results of the spline
+evaluation with \texttt{bisplev}.  We observe a significant loss of precision in
+places, which follows an interesting pattern that could be further investigated.
 
@@
         \includegraphics[width=\linewidth]{figure/bspline/bspline_sig.pdf}
-    \caption{\centering\texttt{sepfir2d} significant bits. \\ \textcolor{white}{.}}
+        \caption{\centering\texttt{sepfir2d} significant bits}
         \label{fig:bspline_bisplev_sig}
@@
         \includegraphics[width=\linewidth]{figure/bspline/bspline_mean_log.pdf}
-    \caption{\centering\texttt{sepfir2d} mean. \\(log)}
+        \caption{\centering\texttt{sepfir2d} mean (log)}
         \label{fig:bspline_bisplev_mean}
@@
         \includegraphics[width=\linewidth]{figure/bspline/bspline_std_log.pdf}
-    \caption{\centering\texttt{sepfir2d} standard deviation. (log)}
+        \caption{\centering\texttt{sepfir2d} standard deviation (log)}
         \label{fig:bspline_bisplev_std}
@@
         \includegraphics[width=\linewidth]{figure/bspline/convol2d_sig.pdf}
-    \caption{\centering\texttt{convol2d} significant bits. \\ \textcolor{white}{.}}
+        \caption{\centering\texttt{convol2d} significant bits}
         \label{fig:bspline_convol2d_sig}
@@
         \includegraphics[width=\linewidth]{figure/bspline/convol2d_mean_log.pdf}
-    \caption{\centering\texttt{convol2d} mean. \\ (log)}
+        \caption{\centering\texttt{convol2d} mean (log)}
         \label{fig:bspline_convol2d_mean}
@@
         \includegraphics[width=\linewidth]{figure/bspline/convol2d_std_log.pdf}
-    \caption{\centering\texttt{convol2d} standard deviation. (log)}
+        \caption{\centering\texttt{convol2d} standard deviation (log)}
         \label{fig:bspline_convol2d_std}
@@
         \texttt{convol2d} have a similar precision.
-    % \tristan{can you use the same color maps as in figure 8?}
-    % Left column shows the \texttt{bisplev} function
-    % while the right column shows the \texttt{convolve2d} function. \tristan{isn't it top row vs bottom row? Replace these hard-to-read explanations with good labels in the figure}
     }
@@
 \begin{figure}
+    \centering
     \begin{subfigure}{.3\textwidth}
@@
 
-This package has eleven examples. Seven examples involve the same optimization problem 
-solved with and without constraints using different methods.
-One example optimizes a chemical problem under constraints.
-The last three examples solve a different problem each.
-
-\paragraph{Unconstrained minimization of multivariate scalar functions:}
-Four Quasi-Newton-Raphson methods minimize function $f$ by using Newton's step: $x_{k+1} = x_{k} - B^{-1}(x_k)\nabla f(x_k)$, where $\nabla$ and $B$ are the gradient and the approximation of the Hessian matrix of $f$.
-The \texttt{Broyden-Fletcher-Goldfarb-Shanno}~\cite{BFGS} (BFGS) and \texttt{Newton-Conjugate-Gradient}~\cite{nocedal2006numerical} (NCG) are line search methods that approximate $H$ by adding two symmetric rank-one matrices and by using the Conjugate-Gradient method.
-The \texttt{Trust-Region Truncated Generalized Lanczos / Conjugate Gradient}~\cite{gould1999solving} (TR-Krylov), \texttt{Trust-Region Newton-Conjugate-Gradient} (TR-NCG), and \texttt{Trust-Region Nearly Exact}~\cite{nocedal2006numerical} (TR-Exact) are trust-region methods approximating $H$ by solving the trust-region subproblem restricted to a truncated Krylov subspace and by solving nonlinear equations for each quadratic subproblem.
-In addition, the \texttt{Nelder-Mead}~\cite{singer2009nelder} simplex-based method iteratively transforms a simplex until its vertices are getting closer to a local minima of the function.
-All methods are applied to the Rosenbrock function.
-
-\paragraph{Constrained minimization of multivariate scalar functions:}
+This package has eleven examples. Seven examples involve the same optimization
+problem solved with and without constraints using different methods. One example
+optimizes a chemical problem under constraints. The last three examples solve a
+different problem each.
+
+\paragraph{Unconstrained minimization of multivariate scalar functions}
+Four Quasi-Newton-Raphson methods minimize function $f$ by using Newton's step:
+$x_{k+1} = x_{k} - B^{-1}(x_k)\nabla f(x_k)$, where $\nabla$ and $B$ are the
+gradient and the approximation of the Hessian matrix of $f$. The
+\texttt{Broyden-Fletcher-Goldfarb-Shanno}~\cite{BFGS} (BFGS) and
+\texttt{Newton-Conjugate-Gradient}~\cite{nocedal2006numerical} (NCG) are line
+search methods that approximate $H$ by adding two symmetric rank-one matrices
+and by using the Conjugate-Gradient method. The \texttt{Trust-Region Truncated
+    Generalized Lanczos / Conjugate Gradient}~\cite{gould1999solving} (TR-Krylov),
+\texttt{Trust-Region Newton-Conjugate-Gradient} (TR-NCG), and
+\texttt{Trust-Region Nearly Exact}~\cite{nocedal2006numerical} (TR-Exact) are
+trust-region methods approximating $H$ by solving the trust-region subproblem
+restricted to a truncated Krylov subspace and by solving nonlinear equations for
+each quadratic subproblem. In addition, the
+\texttt{Nelder-Mead}~\cite{singer2009nelder} simplex-based method iteratively
+transforms a simplex until its vertices are getting closer to a local minima of
+the function. All methods are applied to the Rosenbrock function.
+
+\paragraph{Constrained minimization of multivariate scalar functions}
 Two optimizers solve an optimization problem by taking into account constraints.
-The \texttt{Sequential Least SQuares Programming} uses the SLSQP~\cite{kraft1988software} method to optimize the Rosenbrock function.
-The \texttt{Least-squares minimization} uses the Trust Region Reflective algorithm~\cite{li1993centering}
-to solve a fitting problem from an enzymatic reaction.
-
-\paragraph{}
-The SLSQP and unconstrained minimization methods minimize the \textbf{Rosenbrock} function of $N$ variables
-that reaches its minimum (0) when $x_i=1,\; \forall i \leq N-1$:
-\[f(x) = \sum_{i=1}^{N-1} 100(x_{i+1}-x^2_i)^2 + (1-x_i)^2\]
-% The minimum value of this function is 0, reached when $x_i=1,\; \forall i \leq N-1$. % \tristan{for all i's?}
-
-Figure~\ref{fig:unconstrained_optimization} shows the number of significant bits of the solution for the different methods used. 
-The $(p)$ notation for the NCG, Trust-Krylov, and Trust-NCG methods in the legend refers 
-to the variant where the Hessian matrix is replaced by 
-a function computing the matrix-vector product of the Hessian and an arbitrary vector, to save memory and time.
-All the methods have a good precision ranging from 43 to 53 significant bits.
-The Nelder-Mead method is the least precise one with $\simeq$ 43 significant bits on average, while the Trust-Region-Newton-CG is the most precise one with $\simeq$ 53 significant bits, the highest precision achievable in double precision.
-The remaining methods have a similar precision.
-% \tristan{why is there only 9 methods in Fig 7 while you mentioned 10?} \Yohan{There are 11 examples whose 6 for the unconstrained minimization (presented in Fig 7).
-For 3 methods, there is a variant using the Hessian product instead of the Hessian matrix.I realized that this variant is not explained in the text.
-I will update it.}
+The \texttt{Sequential Least SQuares Programming} uses the
+SLSQP~\cite{kraft1988software} method to optimize the Rosenbrock function. The
+\texttt{Least-squares minimization} uses the Trust Region Reflective
+algorithm~\cite{li1993centering} to solve a fitting problem from an enzymatic
+reaction.
+
+The SLSQP and unconstrained minimization methods minimize the
+\textbf{Rosenbrock} function of $N$ variables that reaches its minimum (0) when
+$x_i=1,\; \forall i \leq N-1$:
+$f(x) = \sum_{i=1}^{N-1} 100(x_{i+1}-x^2_i)^2 + (1-x_i)^2$.
+Figure~\ref{fig:unconstrained_optimization} shows the number of significant bits
+of the solution for the different methods used. The $(p)$ notation for the NCG,
+Trust-Krylov, and Trust-NCG methods in the legend refers to the variant where
+the Hessian matrix is replaced by a function computing the matrix-vector product
+of the Hessian and an arbitrary vector, to save memory and time. All the methods
+have a good precision ranging from 43 to 53 significant bits. The Nelder-Mead
+method is the least precise one with $\simeq$ 43 significant bits on average,
+while the Trust-Region-Newton-CG is the most precise one with $\simeq$ 53
+significant bits, the highest precision achievable in double precision. The
+remaining methods have a similar precision.
 
 The SLSQP also minimizes the Rosenbrock function with the following constraint:
-\begin{eqnarray*}
-    x_0 + 2x_1 \leq 1 \\
-    x_0^2 + x_1 \leq 1 \\
-    x_0^2 - x_1 \leq 1 \\
-    2x_0 + x_1 = 1 \\
-    0 \leq x_0 \leq 1 \\
-    -0.5 \leq x_1 \leq 2 
-\end{eqnarray*}
-The problem has a unique solution $[x_0, x_1] = [0.4149, 0.1701]$.
-Results obtained with RR show a precision of 47 and 44 significant bits for the first and the second solution. %\tristan{which method is tested?}.
+$x_0$ + $2x_1$ $\leq$ 1 
+$x_0^2$ + $x_1$ $\leq$ 1 
+$x_0^2$ - $x_1$ $\leq$ 1 
+$2x_0$ + $x_1$ = 1 
+0 $\leq$ $x_0$ $\leq$ 1 
+-0.5 $\leq$ $x_1$ $\leq$ 2. 
+% \begin{eqnarray*}
+%     x_0 + 2x_1 \leq 1 \\
+%     x_0^2 + x_1 \leq 1 \\
+%     x_0^2 - x_1 \leq 1 \\
+%     2x_0 + x_1 = 1 \\
+%     0 \leq x_0 \leq 1 \\
+%     -0.5 \leq x_1 \leq 2 
+% \end{eqnarray*}
+The problem has a unique solution $[x_0, x_1] = [0.4149, 0.1701]$. Results
+obtained with RR show a precision of 47 and 44 significant bits for the first
+and the second solution. %\tristan{which method is tested?}.
 
@@
 \end{eqnarray*}
-where where $y_i$ are measurement values, $u_i$ are values of the independent variable, and
-$x_i$ the unknown.
-Results within RR show a precision of 51, 46, 47, and 48 significant bits for each component of the solution respectively.% \tristan{which solver is used?}.
-
-\paragraph{Root finding:}
+where where $y_i$ are measurement values, $u_i$ are values of the independent
+variable, and $x_i$ the unknown. Results within RR show a precision of 51, 46,
+47, and 48 significant bits for each component of the solution
+respectively.% \tristan{which solver is used?}.
+
+\paragraph{Root finding}
 % We tested three root finder algorithms with one for small problems using the hybrid Powell and Levenberg-Marquardt methods  (\texttt{root\_finding}) and two for large problems using a Krylov approximation for the inverse Jacobian with and without the help of a preconditioner (\texttt{root\_finding\_large\_preconditionned} and \texttt{root\_finding\_large}).
 
-The \texttt{root\_*} examples use three algorithms to 
-find the root of non-linear equations. \texttt{root\_finding}
-uses the hybrid Powell method to solve a single-variable transcendental equation and 
-the Levenberg-Marquardt method for a set of non-linear equations. 
-\texttt{root\_finding\_large} and \texttt{root\_finding\_large\_preconditioned} examples use 
-the Krylov method to approximate the inverse Jacbian with and without the help of a preconditioner. 
-They solve an integrodifferential equation on a square
- $(x,y) \in [0,1] \times [0,1]$, $P(x,1)=1$, and $P=0$ elsewhere on the boundary.
-The function $P$ is discretized with a Cartesian grid $P_{n,n}=P(nh,nh)$, with $n=75$, and its derivatives are approximated by $\partial_x^2P(x,y) \simeq (P(x+h,y) - 2P(x,y) + P(x-h,y))/h^2$.
+The \texttt{root\_*} examples use three algorithms to find the root of
+non-linear equations. \texttt{root\_finding} uses the hybrid Powell method to
+solve a single-variable transcendental equation and the Levenberg-Marquardt
+method for a set of non-linear equations. \texttt{root\_finding\_large} and
+\texttt{root\_finding\_large\_preconditioned} examples use the Krylov method to
+approximate the inverse Jac\add{o}bian with and without the help of a preconditioner.
+They solve an integrodifferential equation on a square $(x,y) \in [0,1] \times
+    [0,1]$, $P(x,1)=1$, and $P=0$ elsewhere on the boundary. The function $P$ is
+discretized with a Cartesian grid $P_{n,n}=P(nh,nh)$, with $n=75$, and its
+derivatives are approximated by $\partial_x^2P(x,y) \simeq (P(x+h,y) - 2P(x,y) +
+    P(x-h,y))/h^2$.
 
@@
 
-All the examples diverge even within RR, which is not surprising since root-finding methods can easily take a few extra steps to find the root depending on the starting point.
-Nevertheless, for the \texttt{root\_finding\_large} example, 3 traces among the 5 samples can be merged for both RR and MCA modes.
-Figure~\ref{fig:root_finding_large} shows the mean and standard deviation of the result for these 3 samples.
-We can see that a similar solution was found for RR and Full MCA.
-Full MCA leads to a lower precision than RR although both standard deviation maps remain in the same order of magnitude.
-Finally, it is interesting to note the impact of preconditioning on the result numerical quality: as Table~\ref{tab:pytracer_results_summary} shows, the precision doubles between \texttt{root\_finding\_large} and \texttt{root\_finding\_large\_preconditioned}.
+All the examples diverge even within RR, which is not surprising since
+root-finding methods can easily take a few extra steps to find the root
+depending on the starting point. Nevertheless, for the
+\texttt{root\_finding\_large} example, 3 traces among the 5 samples can be
+merged for both RR and MCA modes. Figure~\ref{fig:root_finding_large} shows the
+mean and standard deviation of the result for these 3 samples. We can see that a
+similar solution was found for RR and Full MCA. Full MCA leads to a lower
+precision than RR although both standard deviation maps remain in the same order
+of magnitude. Finally, it is interesting to note the impact of preconditioning
+on the result numerical quality: as Table~\ref{tab:pytracer_results_summary}
+shows, the precision doubles between \texttt{root\_finding\_large} and
+\texttt{root\_finding\_large\_preconditioned}.
 
@@
 
-Scikit-learn offers a well-supplied and documented list of examples 
-% \tristan{examples ou tests? Si ce sont des tests, utilisons "test" partout a la place de "examples" ou "applications", pour sklearn comme pour scipy.} 
-that facilitates its use with Pytracer.
-Among the several available examples, we choose the following representative set
-listed in Table~\ref{tab:pytracer_results_summary}. The following paragraphs 
-focus on the most interesting stability results observed across all experiments.
+Scikit-learn offers a well-supplied and documented list of examples that
+facilitates its use with Pytracer. Among the several available examples, we
+choose the following representative set listed in
+Table~\ref{tab:pytracer_results_summary}. The following paragraphs focus on the
+most interesting stability results observed across all experiments.
 % \tristan{Shall we just refer to Table 4 and remove this lengthy list? You could add the links in the table and mention in the table caption that the tests are linked to their source code}:
@@
 
-This example compares a Bayesian Ridge Regression (BRR) to the Ordinary Least Squares (OLS) estimator on a synthetic dataset and for one-dimensional regression using polynomial feature expansion.
-Although the example does not raise a runtime error, the regression coefficients computed from the fitting are
-non-significant. \pytracer traces reveal that the SVD solver used is the root cause for this error. 
-Figure~\ref{fig:call_path_brr} shows the two call paths for BRR and OLS. 
-The LAPACK library has two main methods for computing the SVD: \texttt{gesdd} and \texttt{gesvd}.
-The former uses a Divide \& Conquer approach, while the latter uses a QR decomposition. 
-While both methods are expected to have the same accuracy~\cite{nakatsukasa2013stable}, Figure~\ref{fig:brr_svd_sig} shows that \texttt{gesdd} is totally imprecise, with an average number of significant digits of 0 for BRR and even \texttt{Not-a-Number} (\texttt{NaN}) values for OLS.
-On the same figure, we can see that 
-using the \texttt{gesvd} (dgelsd) method instead of the \texttt{gesdd} (dgelss) one, 
-the SVD converges for RR and Full MCA, with a number of significant bits of 44 on average. 
-This observation supports the on-going discussion among LAPACK developers on the instability of \texttt{gesdd} (see  \href{https://github.com/Reference-LAPACK/lapack/issues/316}{github.com/Reference-LAPACK/lapack/issues/316}).
+This example compares a Bayesian Ridge Regression (BRR) to the Ordinary Least
+Squares (OLS) estimator on a synthetic dataset and for one-dimensional
+regression using polynomial feature expansion. Although the example does not
+raise a runtime error, the regression coefficients computed from the fitting are
+non-significant. \pytracer traces reveal that the SVD solver used is the root
+cause for this error. Figure~\ref{fig:call_path_brr} shows the two call paths
+for BRR and OLS. The LAPACK library has two main methods for computing the SVD:
+\texttt{gesdd} and \texttt{gesvd}. The former uses a Divide \& Conquer approach,
+while the latter uses a QR decomposition. While both methods are expected to
+have the same accuracy~\cite{nakatsukasa2013stable},
+Figure~\ref{fig:brr_svd_sig} shows that \texttt{gesdd} is totally imprecise,
+with an average number of significant digits of 0 for BRR and even
+\texttt{Not-a-Number} (\texttt{NaN}) values for OLS. On the same figure, we can
+see that using the \texttt{gesvd} (\remove{dgelsd} \add{dgelss}) method instead of the \texttt{gesdd}
+(\remove{dgelss} \add{dgelsd}) one, the SVD converges for RR and Full MCA, with a number of
+significant bits of 44 on average. This observation supports the on-going
+discussion among LAPACK developers on the instability of \texttt{gesdd} (see
+\href{https://github.com/Reference-LAPACK/lapack/issues/316}{github.com/Reference-LAPACK/lapack/issues/316}).
 
@@
 
-The face recognition example uses eigenfaces (eigenvectors) and Support Vector Machines (SVMs) to classify faces from the Labeled Faces in the Wild dataset.
-This example uses a Principal Component Analysis (PCA) to extract the eigenfaces and then trains an SVM classifier to predict the name associated with a face.
-This example is the only one to raise an error with RR due to the non-convergence of the Singular Value Decomposition (SVD) performed in the PCA.
-
-In this example, the PCA uses the Randomized SVD~\cite{halko2011finding} method that first computes a low-rank approximation of the input matrix using a stochastic algorithm and then uses this approximation as input for the SVD.
-The example raises an error during the computation of the SVD.
-The \texttt{randomized\_svd} scikit-learn function uses the Divide \& Conquer SVD method \texttt{gesdd} mentioned previously.
-Replacing \texttt{gesdd} for \texttt{gesvd} solves the SVD convergence issue.
-Figure~\ref{fig:randomized_svd_S} shows the precision of the eigenvalues computed with gesvd, which varies between 15 and 20 significant bits out of the 24 available in single precision.
-The classifier metrics (precision, recall, F1-score, and support) are identical to the IEEE execution for all MCA samples.
-
-In conclusion, \pytracer and the MCA model were helpful to detect the instability of the \texttt{gesdd} method mentioned in several GitHub issues, including the LAPACK repository.
-Furthermore, it is worth mentioning that a Pull Request has recently been submitted to let the user select the SVD method and avoid this kind of issue.
-Thus, \pytracer can detect instabilities that affect fundamental scientific computing components such as the LAPACK library.
+The face recognition example uses eigenfaces (eigenvectors) and Support Vector
+Machines (SVMs) to classify faces from the Labeled Faces in the Wild dataset.
+This example uses a Principal Component Analysis (PCA) to extract the eigenfaces
+and then trains an SVM classifier to predict the name associated with a face.
+This example is the only one to raise an error with RR due to the
+non-convergence of the Singular Value Decomposition (SVD) performed in the PCA.
+
+In this example, the PCA uses the Randomized SVD~\cite{halko2011finding} method
+that first computes a low-rank approximation of the input matrix using a
+stochastic algorithm and then uses this approximation as input for the SVD. The
+example raises an error during the computation of the SVD. The
+\texttt{randomized\_svd} scikit-learn function uses the Divide \& Conquer SVD
+method \texttt{gesdd} mentioned previously. Replacing \texttt{gesdd} for
+\texttt{gesvd} solves the SVD convergence issue.
+Figure~\ref{fig:randomized_svd_S} shows the precision of the eigenvalues
+computed with gesvd \add{in single precision}, which varies between 15 and 20 significant bits out of the
+24 available in single precision. The classifier metrics (precision, recall,
+F1-score, and support) are identical to the IEEE execution for all MCA samples.
+
+In conclusion, \pytracer and the MCA model were helpful to detect the
+instability of the \texttt{gesdd} method mentioned in several GitHub issues,
+including the LAPACK repository. Furthermore, it is worth mentioning that a Pull
+Request has recently been submitted to let the user select the SVD method and
+avoid this kind of issue. Thus, \pytracer can detect instabilities that affect
+fundamental scientific computing components such as the LAPACK library.
 % The Pytracer findings can therefore be extended to many application domains.
@@
     \begin{subfigure}{0.3\linewidth}
-    \includegraphics[width=\linewidth]{figure/face_recognition/randomized_svd_ret_U_sig_zoom.png}
+        \includegraphics[width=\linewidth]{figure/face_recognition/randomized_svd_ret_U_sig.pdf}
         \caption{Left matrix $U$ of the SVD decomposition}
@@
     \begin{subfigure}{0.3\linewidth}
-    \includegraphics[width=\linewidth]{figure/face_recognition/randomized_svd_ret_S_sig.png}
+        \includegraphics[width=\linewidth]{figure/face_recognition/svd_ret_S_sig.pdf}
         \caption{Singular values $\Sigma$ of the SVD decomposition}
@@
     \begin{subfigure}{0.3\linewidth}
-    \includegraphics[width=\linewidth]{figure/face_recognition/randomized_svd_ret_V_sig_zoom.png}
+        \includegraphics[width=\linewidth]{figure/face_recognition/randomized_svd_ret_V_sig.pdf}
         \caption{Right matrix $V$ of the SVD decomposition}
@@
 
-This example uses a linear Support Vector Machine (SVM) classifier trained using the Stochastic Gradient Descent (SGD) method to find the maximum separating hyperplane between sets of 2D points.
-The example trains the SVM with 50 random points separated in 2 clusters with hyperparameter $\alpha=0.01$ and using the hinge loss function.
-Once the model is trained, the example generates a $[-1,5]\times[-1,5]$ Cartesian grid
-discretized with 100 points and predicts the class label for each point with integer coordinates.
-Figure~\ref{fig:hyperplan_sig_zoom} shows the number of significant bits %\tristan{isn't it significant bits?} \tristan{aren't the class predctions integers?}
-% \Yohan{No its floating point values}1
-obtained with RR for each point of the grid. %(squares \tristan{not sure where the squares are}) 
-We can see that yellow regions %\tristan{I don't see any white point} 
-close to the separating hyperplane are highly unstable with a number of significant bits below 0, meaning that
-the classifier is unsure about the predicted class. 
+This example uses a linear Support Vector Machine (SVM) classifier trained using
+the Stochastic Gradient Descent (SGD) method to find the maximum separating
+hyperplane between sets of 2D points. The example trains the SVM with 50 random
+points separated in 2 clusters with hyperparameter $\alpha=0.01$ and using the
+hinge loss function. Once the model is trained, the example generates a
+$[-1,5]\times[-1,5]$ Cartesian grid discretized with 100 points and predicts the
+class label for each point with integer coordinates.
+Figure~\ref{fig:hyperplan_sig_zoom} shows the number of significant bits
+obtained with RR for each point of the grid. 
+We can see that yellow regions 
+close to the separating hyperplane are highly unstable with a number of
+significant bits below 0, meaning that the classifier is unsure about the
+predicted class. 
 %\tristan{Describe and comment on the other 2 tests, why are they more stable? Is it because the training set has more points?}
@@
     % \end{subfigure}
-    \begin{subfigure}{.3\linewidth}
+    \begin{subfigure}{.45\linewidth}
+        \includegraphics[width=\linewidth]{figure/separating_hyperplan/hyperplane_zoom.pdf}
         \caption{Separating hyperplane}
-    \includegraphics[width=\linewidth]{figure/separating_hyperplan/hyperplane_zoom.pdf}
         \label{fig:hyperplan_sig_zoom}
     \end{subfigure} \\
-    \begin{subfigure}{.3\linewidth}
+    \begin{subfigure}{.45\linewidth}
+        \includegraphics[width=\linewidth]{figure/SVM/non_weighted.pdf}
         \caption{SVM (non weighted)}
-    \includegraphics[width=\linewidth]{figure/SVM/non_weighted.pdf}
         \label{fig:SVM_nw_sig}
     \end{subfigure}
-    \begin{subfigure}{.3\linewidth}
+    \begin{subfigure}{.45\linewidth}
+        \includegraphics[width=\linewidth]{figure/SVM/weighted.pdf}
         \caption{SVM (weighted)}
-    \includegraphics[width=\linewidth]{figure/SVM/weighted.pdf}
         \label{fig:SVM_w_sig}
     \end{subfigure} \\
-    \begin{subfigure}{.3\linewidth}
+    \begin{subfigure}{.45\linewidth}
+        \includegraphics[width=\linewidth]{figure/Weighted/non_weighted.pdf}
         \caption{SGD weighted (non-weighted)}
-    \includegraphics[width=\linewidth]{figure/Weighted/non_weighted.pdf}
         \label{fig:weighted_nw_sig}
     \end{subfigure}
-    \begin{subfigure}{.3\linewidth}
+    \begin{subfigure}{.45\linewidth}
+        \includegraphics[width=\linewidth]{figure/Weighted/weighted.pdf}
         \caption{SGD weighted (weighted)}
-    \includegraphics[width=\linewidth]{figure/Weighted/weighted.pdf}
         \label{fig:weighted_w_sig}
@@
 \paragraph{SVM}
-This example uses a plain Support Vector Classification~\cite{Platt99probabilisticoutputs} (SVC) 
-to find the best hyperplane separating an unbalanced dataset with two classes of 1000 and 100 points.
-This example tests two SVC configurations using a linear kernel with and without a class weight parameter.
-The SVC predicts the class label for each coordinate over a $[-5,5] \times [-5,5]$ grid discretized
-with 900 points.
-Figures~\ref{fig:SVM_nw_sig} and~\ref{fig:SVM_w_sig} show the result within RR of the classification with
-and without taking into account the unbalancing.
-We can see that the number of significant bits is lower on the separating line and
+This example uses a plain Support Vector
+Classification~\cite{Platt99probabilisticoutputs} (SVC) to find the best
+hyperplane separating an unbalanced dataset with two classes of 1000 and 100
+points. This example tests two SVC configurations using a linear kernel with and
+without a class weight parameter. The SVC predicts the class label for each
+coordinate over a $[-5,5] \times [-5,5]$ grid discretized with 900 points.
+Figures~\ref{fig:SVM_nw_sig} and~\ref{fig:SVM_w_sig} show the result within RR
+of the classification with and without taking into account the unbalancing. We
+can see that the number of significant bits is lower on the separating line and
 that taking into account class imbalance allows for a better separation.
@@
 \paragraph{SGD weighted samples}
-This example uses an SGD to separate weighted points.
-It divides the training set into two classes of 10 points with a bigger weight for the second class.
-The SGD is trained with hyperparameters $\alpha=0.01$ and a maximum number of iterations to 100.
-The prediction is made on a $[-4,5]\times[-4,5]$ grid discretized with 250 000 points.
-Figures~\ref{fig:weighted_nw_sig} and~\ref{fig:weighted_w_sig} show the number of significant bits
-of prediction within RR along with dataset points in blue and violet.
-We can see that the separating plane corresponds to a region of lower precision, similar to the previous examples. 
+This example uses an SGD to separate weighted points. It divides the training
+set into two classes of 10 points with a bigger weight for the second class. The
+SGD is trained with hyperparameters $\alpha=0.01$ and a maximum number of
+iterations to 100. The prediction is made on a $[-4,5]\times[-4,5]$ grid
+discretized with 250\add{,}000 points. Figures~\ref{fig:weighted_nw_sig}
+and~\ref{fig:weighted_w_sig} show the number of significant bits of prediction
+within RR along with dataset points in blue and \remove{violet} \add{purple}. We can see that the
+separating plane corresponds to a region of lower precision, similar to the
+previous examples. 
 % Finally, taking into account the points' weight allows for a better separation \tristan{is this related to numerical stability? If not, you can ommit the comment.}.
@@
 \subsection{Overhead evaluation}
-\pytracer's tracing overhead consists of (1) module instrumentation time (initialization overhead) and (2) data write time during the execution (runtime overhead).
-The initialization overhead is proportional to the number of functions and classes traced.
-For example, we measured an average initialization time of 8 seconds during our experiments with  NumPy, SciPy, and Scikit-learn.
-This overhead can be reduced by excluding intensively used functions such as \texttt{numpy.array} from the instrumentation.
-Figure~\ref{fig:performance_tracing} summarizes \pytracer's tracing overhead for SciPy and scikit-learn examples. 
-\textit{Slowdown} represents the slowdown of \pytracer without fuzzy measured as the ratio between the actual execution time (without \pytracer) and the execution time using \pytracer.
-The \textit{Slowdown RR} and \textit{Slowdown MCA} show the slowdown within the fuzzy environment. 
-Without fuzzy, \pytracer introduces an average slowdown of $17\times$ high for the examples running less than 8 seconds because \pytracer spends most of its time in the initialization step.
-Since this step is a constant factor of the number of functions instrumented, we also measured the instrumentation cost itself (\textit{Slowdown (Instrumentation)}) calculated by subtracting the initialization time to \textit{Slowdown}.
-We then obtain an average slowdown of $3.5\times$.
-Finally, the fuzzy instrumentation increases the average slowdown to $37\times$ for RR and $43\times$ for Full MCA.
+
+\pytracer's tracing overhead consists of (1) module instrumentation time
+(initialization overhead) and (2) data write time during the execution (runtime
+overhead). The initialization overhead is proportional to the number of
+functions and classes traced. For example, we measured an average initialization
+time of 8 seconds during our experiments with  NumPy, SciPy, and Scikit-learn.
+This overhead can be reduced by excluding intensively used functions such as
+\texttt{numpy.array} from the instrumentation.
+Figure~\ref{fig:performance_tracing} summarizes \pytracer's tracing overhead for
+SciPy and scikit-learn examples. \textit{Slowdown} represents the slowdown of
+\pytracer without fuzzy measured as the ratio between the actual execution time
+(without \pytracer) and the execution time using \pytracer. The \textit{Slowdown
+    RR} and \textit{Slowdown MCA} show the slowdown within the fuzzy environment.
+Without fuzzy, \pytracer introduces an average slowdown of $17\times$ high for
+the examples running less than 8 seconds because \pytracer spends most of its
+time in the initialization step. Since this step is a constant factor of the
+number of functions instrumented, we also measured the instrumentation cost
+itself (\textit{Slowdown (Instrumentation)}) calculated by subtracting the
+initialization time to \textit{Slowdown}. We then obtain an average slowdown of
+$3.5\times$. Finally, the \remove{fuzzy instrumentation} \add{using MCA operations (throuhg fuzzy) instead of the native ones} increases the average slowdown
+to $37\times$ for RR and $43\times$ for Full MCA.
 
@@
         using the fuzzy environment with RR and Full MCA modes.
-    The first four examples measure the initialization steps depending on the modules instrumented. 
+        The first \remove{first} \add{last} four examples measure the initialization steps depending on the modules instrumented. 
         % \tristan{there's too much text in this caption, move some of it to the text, the caption should just explain the difference between the 4 slowdowns.
@@
 
-Figure~\ref{fig:performance_parsing} shows
-the postprocessing time and trace sizes produced by \pytracer. 
-The linear correlation between the log of the size and the log of the time shows a significant correlation 
-(p-value $\leq 10^{-8}$ for RR and p-value $\leq 10^{-3}$ for MCA).
+Figure~\ref{fig:performance_parsing} shows the postprocessing time and trace
+sizes produced by \pytracer. The linear correlation between the log of the size
+and the log of the time shows a significant correlation (p-value $\leq 10^{-8}$
+for RR and p-value $\leq 10^{-3}$ for MCA).
 % \tristan{Mention linear correlation with p-value here.}
 
-In conclusion, while \pytracer's overhead is substantial, it remains tractable for real-life examples.
+In conclusion, while \pytracer's overhead is substantial, it remains tractable
+for real-life examples.
 
@@
 
-Through our analysis of SciPy and scikit-learn, we demonstrated \pytracer's scalability, automaticity, and applicability to a wide range of Python program.
-The relatively low instrumentation overhead of 3.5$\times$ on average enables the analysis of real-scale applications.
-\pytracer's instrumentation is fully automatic and does not require manual intervention from the user.
-Furthermore, \pytracer works on any Python libraries, with any data format supported by pickle and any numerical noise model.
-
-\pytracer is the first tool to enable a systematic numerical analysis of Python codes.
-Existing tools focus on traditional languages of the HPC community, such as C, C++, and FORTRAN.
-However, Python's high-level abstraction allows for quick application implementations while maintaining high-performance thanks to specialized libraries such as NumPy.
-Therefore, \pytracer meets the numerical analysis needs of an ever-increasing number of applications.
-
-\pytracer allows users to pinpoint the root causes of numerical instabilities by working at the function level.
-Numerical stability evaluations are complex since calculations are strongly interdependent.
-Function-level instrumentation limits the size of the traces since only inputs and outputs of a function are dumped.
-Moreover, it decreases instrumentation overhead and helps the user identify instabilities quickly.
-Working at the function level is thus a suitable compromise between analysis conducted at the floating-point operation level and user debug prints.
-Indeed,  fine-grained analyses are costly and hard to interpret as they overwhelm users with information.
-In contrast, looking at intermediate results through print statements
-is lightweight but not reliable since developers may not systematically instrument unstable functions.
-Finally, the SciPy environment wraps many computation kernels written in C, such as BLAS or LAPACK.
-By working at the function level, \pytracer allows the user to evaluate the numerical precision of such kernels and their impact on the code without getting deep into technical implementation aspects.
-
-Integrating \pytracer at the early stages of the development cycle would improve the overall numerical quality of the developed code.
-\pytracer's automaticity facilitates its usage and enables its integration in unit testing.
-For example, \pytracer could be used in regression tests to ensure that updates do not degrade the numerical quality of a calculation.
-
-\pytracer can also be useful for selecting hyperparameters, as is the case in machine learning.
-Indeed, it is common for data scientists to explore a range of hyperparameters and select the ones giving the best scores.
-With \pytracer, the user has a practical way to quantify numerical quality and understand why hyperparameters produce inconsistent results instead of tweaking hyperparameters to make solvers converge.
-For instance, the Face Recognition example  (Figure~\ref{fig:face_recognition_svd}) shows how numerical precision could inform the selection of the number of components in dimensionality reduction.
-
-The visualization provides a global view of the code and interactions between computations.
-In addition, the Plotly dashboard helps navigate through the code easily, without the need for ad-hoc scripts to visualize data.
-Finally, the dashboard can be extended to support other data formats to visualize.
-At this stage, \pytracer currently supports n-dimensional NumPy arrays as well as native Python data.
-
-As we showed in Section~\ref{sec:impact_mca_modes}, using Full MCA mode leads to runtime errors that have a considerable impact on the proper functioning of the execution, which is unfortunate since these errors do not reflect actual numerical errors but are related to perturbations that should not occur.
-Conversely, RR mode is far more conservative since it preserves exact operations and is easier to use even though it does not simulate all perturbations.
-Therefore, from our experiments, we recommend the use of RR over Full MCA.
-More research is required to address the issues encountered with Full MCA.
-
-Finally, the wide range of results precision obtained from our experiments demonstrate that looking at the numerical variability is essential and that such analyses would benefit from being conducted systematically.
-We showed that well-known scientific libraries are prone to numerical error even though they have been well tested for decades.
-The omnipresence of these libraries in scientific codes should thus impel users to integrate numerical analysis in their development workflow in addition to testing their implementation.
+Through our analysis of SciPy and scikit-learn, we demonstrated \pytracer's
+scalability, automaticity, and applicability to a wide range of Python program.
+The relatively low instrumentation overhead of 3.5$\times$ on average enables
+the analysis of real-scale applications. \pytracer's instrumentation is fully
+automatic and does not require manual intervention from the user. Furthermore,
+\pytracer works on any Python libraries, with any data format supported by
+pickle and any numerical noise model.
+
+\pytracer is the first tool to enable a systematic numerical analysis of Python
+codes. Existing tools focus on traditional languages of the HPC community, such
+as C, C++, and FORTRAN. However, Python's high-level abstraction allows for
+quick application implementations while maintaining high-performance thanks to
+specialized libraries such as NumPy. Therefore, \pytracer meets the numerical
+analysis needs of an ever-increasing number of applications.
+
+\pytracer allows users to pinpoint the root causes of numerical instabilities by
+working at the function level. Numerical stability evaluations are complex since
+calculations are strongly interdependent. Function-level instrumentation limits
+the size of the traces since only inputs and outputs of a function are dumped.
+Moreover, it decreases instrumentation overhead and helps the user identify
+instabilities quickly. Working at the function level is thus a suitable
+compromise between analysis conducted at the floating-point operation level and
+user debug prints. Indeed,  fine-grained analyses are costly and hard to
+interpret as they overwhelm users with information. In contrast, looking at
+intermediate results through print statements is lightweight but not reliable
+since developers may not systematically instrument unstable functions. Finally,
+the SciPy environment wraps many computation kernels written in C, such as BLAS
+or LAPACK. By working at the function level, \pytracer allows the user to
+evaluate the numerical precision of such kernels and their impact on the code
+without getting deep into technical implementation aspects.
+
+Integrating \pytracer at the early stages of the development cycle would improve
+the overall numerical quality of the developed code. \pytracer's automaticity
+facilitates its usage and enables its integration in unit testing. For example,
+\pytracer could be used in regression tests to ensure that updates do not
+degrade the numerical quality of a calculation.
+
+\pytracer can also be useful for selecting hyperparameters, as is the case in
+machine learning. Indeed, it is common for data scientists to explore a range of
+hyperparameters and select the ones giving the best scores. With \pytracer, the
+user has a practical way to quantify numerical quality and understand why
+hyperparameters produce inconsistent results instead of tweaking hyperparameters
+to make solvers converge. For instance, the Face Recognition example
+(Figure~\ref{fig:face_recognition_svd}) shows how numerical precision could
+inform the selection of the number of components in dimensionality reduction.
+
+The visualization provides a global view of the code and interactions between
+computations. In addition, the Plotly dashboard helps navigate through the code
+easily, without the need for ad-hoc scripts to visualize data. Finally, the
+dashboard can be extended to support other data formats to visualize. At this
+stage, \pytracer currently supports n-dimensional NumPy arrays as well as native
+Python data.
+
+As we showed in Section~\ref{sec:impact_mca_modes}, using Full MCA mode leads to
+runtime errors that have a considerable impact on the proper functioning of the
+execution, which is unfortunate since these errors do not reflect actual
+numerical errors but are related to perturbations that should not occur.
+Conversely, RR mode is far more conservative since it preserves exact operations
+and is easier to use even though it does not simulate all perturbations.
+Therefore, from our experiments, we recommend the use of RR over Full MCA. More
+research is required to address the issues encountered with Full MCA.
+
+Finally, the wide range of results precision obtained from our experiments
+demonstrate that looking at the numerical variability is essential and that such
+analyses would benefit from being conducted systematically. We showed that
+well-known scientific libraries are prone to numerical error even though they
+have been well tested for decades. The omnipresence of these libraries in
+scientific codes should thus impel users to integrate numerical analysis in
+their development workflow in addition to testing their implementation.
 
@@
 
-Several tools have been developed to assess numerical quality, and can be divided into static and dynamic approaches.
-Static approaches typically analyze source code, while dynamic approaches trace floating-point computations throughout executions.
-A detailed review of these approaches is presented in~\cite{cherubin2020tools}.
-% \pytracer adopts the dynamic approach due to its scalability to large code bases.
-Dynamic approaches typically trace floating-point computations, detect instabilities in traces, and visualize summary statistics about instabilities.
-This section reviews existing approaches for each of these steps.
-% \label{sec:soa}
-% \paragraph{Numerical tracing techniques}
-Numerous tools exists to trace floating-point computations for C, C++, or FORTRAN programs due to the prevalence of these languages in High-Performance Computing (HPC). 
-The main tracing techniques are \textit{source-to-source}, \textit{compiler-based transformations}, and \textit{dynamic binary instrumentation}.
-
-% \gkmod{}{Note: this paragraph just reads like a list with no real interpretation/commentary.
-I think it would be better to state the strengths of this technique, cite examples, and then state limitations/why it isn't the only technique used.}
-The source-to-source technique requires a rewriting of the application to modify floating-point types and provides a fine-grained control on the analyzed code.
+Several tools have been developed to assess numerical quality, and can be
+divided into static and dynamic approaches. Static approaches typically analyze
+source code, while dynamic approaches trace floating-point computations
+throughout executions. A detailed review of these approaches is presented
+in~\cite{cherubin2020tools}. 
+% \pytracer adopts the dynamic approach due to its scalability to large code
+% bases. Dynamic approaches typically trace floating-point computations, detect
+% instabilities in traces, and visualize summary statistics about instabilities.
+% This section reviews existing approaches for each of these steps.
+% \label{sec:soa} \paragraph{Numerical tracing techniques}
+Numerous tools exists to trace floating-point computations for C, C++, or
+FORTRAN programs due to the prevalence of these languages in High-Performance
+Computing (HPC). The main tracing techniques are \textit{source-to-source},
+\textit{compiler-based transformations}, and \textit{dynamic binary
+    instrumentation}.
+
+% \gkmod{}{Note: this paragraph just reads like a list with no real
+% interpretation/commentary. I think it would be better to state the strengths
+% of this technique, cite examples, and then state limitations/why it isn't the
+% only technique used.}
+The source-to-source technique requires a rewriting of the application to modify
+floating-point types and provides a fine-grained control on the analyzed code.
 CADNA~\cite{jezequel2008cadna} is a library for C, C++, and Fortran implementing
-CESTAC~\cite{vignes1993stochastic} stochastic arithmetic. Shaman~\cite{demeure_phd} is a C++ library that uses a first-order error model to propagate numerical error. 
-MCAlib~\cite{frechtling2015mcalib} is a C library that implements the Monte Carlo Arithmetic (MCA)~\cite{parker1997monte} using the MPFR~\cite{fousse2007mpfr} library.
-Finally, the work in~\cite{tang2016software} proposed a source-to-source framework for executing targeted code in infinite and fixed precision with and without stochastic arithmetic.
-The main drawback of the source-to-source approach is its lacks of scalability since rewriting large codes can be a tedious task.
-
-% \gkmod{}{Note: similar to the above, this is just a list rather than a highlight of how the compiler-based approach can be more scalable than source-to-source because it requires less manual intervention into a codebase (e.g.), then have your list, and finally say why it is still limited/not a global fix to this problem.}
-
-The compiler-based approach instruments floating-point expressions at compile time
-and so allows the user to automatically instrument large codebases.
-Verificarlo~\cite{verificarlo} is a compiler that supports different types of arithmetic instrumentations, including MCA. 
-The work in~\cite{bao2013fly} modified the GNU Compiler Collection (GCC) to track local floating-point errors across executions.
-pLiner~\cite{guo2020pliner} is a root-cause analyzer based on the Clang compiler that detects floating-point operations responsible for result variability using a source-to-source transformation at the Abstract Syntax Tree (AST) level to rewrite parts of code with higher precision.
-PFPSanitizer~\cite{chowdhary2020debugging,chowdhary2021parallel} is a compiler that uses parallel shadow execution to detect numerical issues using higher precision.
-FLiT~\cite{sawaya2017flit} is a framework to detect variability induced by compilers and their optimizations.
-The work in~\cite{wang2012development} proposes a numerical debugger based on GDB~\cite{stallman1988debugging} for Discrete Stochastic Arithmetic (DSA) on FPGA as an Eclipse plugging.
-Similarly, Cadtrace~\cite{jezequel2008cadna} and Shaman propose a GDB-based tool to use the CADNA and Shaman libraries with GDB, respectively.
-The main limitation of the compiler-based approach is that one must have access to the source code.
-
-Dynamic Binary Instrumentation (DBI) operates directly on executables, without the need for recompilation or manual changes. Therefore, it is applicable to any programming language.
-CraftHPC~\cite{lam2013dynamic} uses DBI to detect catastrophic cancellations at runtime.
-Verrou~\cite{fevotte2016verrou} is a Valgrind~\cite{nethercote2007valgrind} based tool that dynamically replaces
-floating-point operations with their stochastic arithmetic counterparts. FPDebug~\cite{benz2012dynamic} uses DBI to detect numerical inaccuracies by using shadow computations with higher precision.
-Herbgring~\cite{sanchez2017finding} is a Valgrind-based tool to detect
-numerical instabilities.
-It uses a shadow memory to detect precision losses by comparison with results obtained at higher precision.
-It is combined with symbolic computation to backtrack the root of the error.
-We can note that all methods based on a high-precision oracle suppose that computing with a large number of bits is sufficient to obtain an accurate result, which is not always true (see for example, the famous Muller's sequence~\cite{bajard1996introduction}).
-Although versatile, the DBI looses high-level information useful to understand the source-code logic.
-
-% \gkmod{}{Note: I like this comparison here, but do think that the comments above about providing some more info when each is mentioned would still help this section.}
-Being agnostic to the programming language is a serious advantage of the DBI method compared to source-to-source and compiler-bases methods.
-However, working at the binary level makes it difficult to access high-level information needed to debug and understand the source-code logic.
-Conversely, the source-to-source approach provides a fine-grained control on the analyzed code, but it lacks scalability, as rewriting large codes can be a tedious task.
-Finally, the compiler-based approach takes advantage of the best of both by being automatic and having access to high-level information.
-However, like source-to-source, the compiler-based method is not suitable for analyzing closed-source libraries.
-
-To the best of our knowledge, \pytracer is the first tool dedicated to the numerical analysis of Python code. Existing tools for tracing Python code focus on performance profiling for time (cProfile) 
-or memory consumption (memprofile). 
-Anteater~\cite{faust2019anteater} is a Python tracer tool to debug Python applications. 
-It performs source transformations at the AST level but only deals with native numeric Python types.
-Moreover, the user needs to manually tag each variable to trace. Finally, according to the authors, Anteater does not scale to large traces.
-cProfile, memprofile, and Anteater use Python decorators as the primary instrumentation technique, a Python mechanism to instrument a function by adding a line over a function declaration.
-While this method is appropriate when targeting specific functions, it is not feasible for large codebases where potentially unstable code sections are unknown.
+CESTAC~\cite{vignes1993stochastic} stochastic arithmetic.
+Shaman~\cite{demeure_phd} is a C++ library that uses a first-order error model
+to propagate numerical error. MCAlib~\cite{frechtling2015mcalib} is a C library
+that implements the Monte Carlo Arithmetic (MCA)~\cite{parker1997monte} using
+the MPFR~\cite{fousse2007mpfr} library. \add{ADAPT \mbox{~\cite{menon2018adapt}} uses
+    Automatic Differentiation to compute a sensitivity profile for each variable of
+    given program}. Finally, the work in~\cite{tang2016software} proposed a
+source-to-source framework for executing targeted code in infinite and fixed
+precision with and without stochastic arithmetic. The main drawback of the
+source-to-source approach is its lacks of scalability since rewriting large
+codes can be a tedious task.
+
+% \gkmod{}{Note: similar to the above, this is just a list rather than a
+% highlight of how the compiler-based approach can be more scalable than
+% source-to-source because it requires less manual intervention into a codebase
+% (e.g.), then have your list, and finally say why it is still limited/not a
+% global fix to this problem.}
+
+The compiler-based approach instruments floating-point expressions at compile
+time and so allows the user to automatically instrument large codebases.
+Verificarlo~\cite{verificarlo} is a compiler that supports different types of
+arithmetic instrumentations, including MCA. The work in~\cite{bao2013fly}
+modified the GNU Compiler Collection (GCC) to track local floating-point errors
+across executions. pLiner~\cite{guo2020pliner} is a root-cause analyzer based on
+the Clang compiler that detects floating-point operations responsible for result
+variability using a source-to-source transformation at the Abstract Syntax Tree
+(AST) level to rewrite parts of code with higher precision.
+PFPSanitizer~\cite{chowdhary2020debugging,chowdhary2021parallel} \add{and
+    NSan~\mbox{\cite{courbet2021nsan}} are compiler based approaches}
+that use shadow execution to detect numerical issues using higher
+precision.
+FLiT~\cite{sawaya2017flit} is a framework to detect variability
+induced by compilers and their optimizations. The work
+in~\cite{wang2012development} proposes a numerical debugger based on
+GDB~\cite{stallman1988debugging} for Discrete Stochastic Arithmetic (DSA) on
+FPGA as an Eclipse plugging. Similarly, Cadtrace~\cite{jezequel2008cadna} and
+Shaman propose a GDB-based tool to use the CADNA and Shaman libraries with GDB,
+respectively. The main limitation of the compiler-based approach is that one
+must have access to the source code.
+
+Dynamic Binary Instrumentation (DBI) operates directly on executables, without
+the need for recompilation or manual changes. Therefore, it is applicable to any
+programming language. CraftHPC~\cite{lam2013dynamic} uses DBI to detect
+catastrophic cancellations at runtime. Verrou~\cite{fevotte2016verrou} is a
+Valgrind~\cite{nethercote2007valgrind} based tool that dynamically replaces
+floating-point operations with their stochastic arithmetic counterparts.
+FPDebug~\cite{benz2012dynamic} uses DBI to detect numerical inaccuracies by
+using shadow computations with higher precision.
+Herbgrin\remove{g}\add{d}~\cite{sanchez2017finding} is a Valgrind-based tool to detect numerical
+instabilities. It uses a shadow memory to detect precision losses by comparison
+with results obtained \remove{at} \add{in} higher precision. It is combined with symbolic
+computation to backtrack the root of the error. We can note that all methods
+based on a high-precision oracle suppose that computing with a large number of
+bits is sufficient to obtain an accurate result, which is not always true (see
+for example, the famous Muller's sequence~\cite{bajard1996introduction}).
+Although versatile, the DBI looses high-level information useful to understand
+the source-code logic.
+
+% \gkmod{}{Note: I like this comparison here, but do think that the comments
+% above about providing some more info when each is mentioned would still help
+% this section.}
+Being agnostic to the programming language is a serious advantage of the DBI
+method compared to source-to-source and compiler-bases methods. However, working
+at the binary level makes it difficult to access high-level information needed
+to debug and understand the source-code logic. Conversely, the source-to-source
+approach provides a fine-grained control on the analyzed code, but it lacks
+scalability, as rewriting large codes can be a tedious task. Finally, the
+compiler-based approach takes advantage of the best of both by being automatic
+and having access to high-level information. However, like source-to-source, the
+compiler-based method is not suitable for analyzing closed-source libraries.
+
+To the best of our knowledge, \pytracer is the first tool dedicated to the
+numerical analysis of Python code. Existing tools for tracing Python code focus
+on performance profiling for time (cProfile) or memory consumption (memprofile).
+Anteater~\cite{faust2019anteater} is a Python tracer tool to debug Python
+applications. It performs source transformations at the AST level but only deals
+with native numeric Python types. Moreover, the user needs to manually tag each
+variable to trace. Finally, according to the authors, Anteater does not scale to
+large traces. cProfile, memprofile, and Anteater use Python decorators as the
+primary instrumentation technique, a Python mechanism to instrument a function
+by adding a line over a function declaration. While this method is appropriate
+when targeting specific functions, it is not feasible for large codebases where
+potentially unstable code sections are unknown.
 
@@
 
-% Evaluating the numerical stability of scientific Python codes is a tedious task
-% and requires an expertise to be conducted. Automatic tools to help the users 
-% understanding what's going on in their codes is therefore crucial.
-% In this perspective, \pytracer is the first tool to offer a complete framework
-% for analyzing and visualizing the numerical stability of Python codes.
-% It works by automatically instrumenting Python libraries to produce numerical
-% traces visualized through an interactive Plotly Dash server.
-% \pytracer does not require manual code modification, and has been tested with 
-% major scientific libraries such as NumPy, SciPy, and Scikit-learn.
-Our results show that \pytracer is scalable, with an average instrumentation slowdown of $3.5\times$.
-\pytracer's visualization interface remains responsive even with traces of up to 1TB.
-Moreover,
-% \pytracer is by construction agnostic to the noise model used 
-% to evaluate the numerical stability. We have demonstrated 
-% that \pytracer can be used with the Monte Carlo Arithmetic 
-% through the fuzzy environment. 
-% The experiments conducted in this paper are the first largest application of the fuzzy ecosystem by the wide range of applications covered.
-
-% In future work, we would like to extend the post-process analysis to aggregate traces 
-% when the execution flow path diverges by leveraging techniques used in code coverage analysis.
-% Moreover, we would like to extend \pytracer to instrument elementary arithmetic operations 
-% which can be helpful to more profound analyses. Finally, although \pytracer is flexible on the noise
-% model used, we only tested it with the Monte Carlo Arithmetic. We would like to compare different 
-% models against MCA.
-
-% We also have to provide feedback about pitfalls and benefits encountered to shed light on first-time users' good and bad practices and democratize MCA's usage.
-
-% \begin{itemize}
-
-%     \item Domain agnostic: \pytracer is intended to work on any scientific Python applications, without specific domain-specific languages or needs to rely on specific libraries.
-%     We target two of the most common libraries used in scientific computing within Python, SciPy and Scikit-learn, and a domain-specific application in neuroimaging.
-We show that \pytracer works well on these libraries, capturing most of the functions' module targeted.
-
-%     \item Automatic: \pytracer objective is to offer automatic instrumentation for Python applications,
-%     from small prototypes to state-of-the-art scientific libraries.
-
-%     \item Scalable: \pytracer goal is to trace real-world application and use case.
-%     In that perspective, we use \pytracer on PyAFQ, a domain-specific neuroimaging application to compute tractograms, generating \pytracer traces up to 1TB.
-We demonstrate that \pytracer can handle this volume of data and offer the user an interactive and fluent visualization.
-%     We also show that \pytracer instrumentation gives a slowdown of $\times 6$.
-
-%     \item Fuzzy compatible: \pytracer aims at evaluating numerical stability by using an injection noise model.
-%     Although the noise model used is orthogonal to \pytracer tracing mechanism, we emphasize in these experiments the MCA model through the fuzzy environment and discuss its compatibility with \pytracer tracing mechanism to point out limitations of the trace-based approach and to propose research tracks to overcome them.
-%     The experiments conducted in this paper are the first largest application of the fuzzy ecosystem by the wide range of applications covered.
-We, therefore, found it interesting to give feedback about pitfalls and benefits encountered
-%     in order to shed light on the good and bad practices for first-time users and democratize MCA's usage.
-%     Moreover, these analyses will help the fuzzy developers to increase the overall stability of fuzzy.
-
-% \end{itemize}
-
-\bibliographystyle{abbrv}
-\bibliography{biblio}
-
-%%
-%% If your work has an appendix, this is the place to put it.
-\appendix
-
+% % use section* for acknowledgment
+% \ifCLASSOPTIONcompsoc
+%     % The Computer Society usually uses the plural form
+%     \section*{Acknowledgments}
+% \else
+%     % regular IEEE prefers the singular form
+%     \section*{Acknowledgment}
+% \fi
+
+% The authors would like to thank...
+
+% Can use something like this to put references on a page
+% by themselves when using endfloat and the captionsoff option.
+\ifCLASSOPTIONcaptionsoff
+    \newpage
+\fi
+
+\bibliographystyle{IEEEtran}
+\bibliography{paper-annotated}
+
+% trigger a \newpage just before the given reference
+% number - used to balance the columns on the last page
+% adjust value as needed - may need to be readjusted if
+% the document is modified later
+%\IEEEtriggeratref{8}
+% The "triggered" command can be changed if desired:
+%\IEEEtriggercmd{\enlargethispage{-5in}}
+
+% references section
+
+% can use a bibliography generated by BibTeX as a .bbl file
+% BibTeX documentation can be easily obtained at:
+% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
+% The IEEEtran BibTeX style support page is at:
+% http://www.michaelshell.org/tex/ieeetran/bibtex/
+%\bibliographystyle{IEEEtran}
+% argument is your BibTeX string definitions and bibliography database(s)
+%\bibliography{IEEEabrv,../bib/paper}
+%
+% <OR> manually copy in the resultant .bbl file
+% set second argument of \begin to the number of references
+% (used to reserve space for the reference number labels box)
+%% \begin{thebibliography}{1}
+
+%% \bibitem{IEEEhowto:kopka}
+%% H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
+%%   0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+
+%% \end{thebibliography}
+
+% biography section
+% 
+% If you have an EPS/PDF photo (graphicx package needed) extra braces are
+% needed around the contents of the optional argument to biography to prevent
+% the LaTeX parser from getting confused when it sees the complicated
+% \includegraphics command within an optional argument. (You could create
+% your own custom macro containing the \includegraphics command to make things
+% simpler here.)
+%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
+% or if you just want to reserve a space for a photo:
+
+\vskip -2\baselineskip plus -1fil
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/yohan.jpg}}]{Yohan Chatelain}
+    received his Ph.D. degree from the University of Paris-Saclay
+    (UVSQ), Versailles, France in 2019.
+    He is a postdoctoral researcher in the Big Data Infrastructures for
+    Neuroinformatics lab at the University of Concordia, Montreal, Canada. His
+    research topics include computer arithmetic, high-performance computing, and
+    reproducibility. Yohan aims at democratizing the use of
+    the analysis of stability for scientific computing codes through automatic tools to
+    improve numerical quality. 
+\end{IEEEbiography}
+
+\vskip -2\baselineskip plus -1fil
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/NigelPhoto.png}}]{Nigel Yong Sao Young}
+    was born in Mauritius Island. He is a recent Computer
+    Science graduate at Concordia University. He is currently working on his
+    software startup, based in the city of Montreal.
+\end{IEEEbiography}
+
+%% % if you will not have a photo at all:
+\vskip -2\baselineskip plus -1fil
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/greg_kiar.png}}]{Gregory Kiar}
+    is a research scientist at the Child Mind Institute. Throughout his degrees
+    in Biomedical Engineering, Greg has developed techniques to study biosignal
+    data, a turn-key tool that allows researchers to generate maps of brain
+    connectivity from diffusion MRI data, and techniques to assess and improve
+    the stability of research in neuroscience. 
+    Greg’s research bridges the
+    fields of numerical analysis and brain imaging to evaluate and improve the
+    trustworthiness of techniques used to study the brain. 
+\end{IEEEbiography}
+
+\vskip -2\baselineskip plus -1fil
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/glatard_tristan.jpg}}]{Tristan Glatard}
+    is Associate Professor in the Department of Computer Science and Software
+    Engineering at Concordia University in Montreal, and Canada Research Chair
+    (Tier II) on Big Data Infrastructures for Neuroinformatics. Before that, he
+    was research scientist at the French National Centre for Scientific Research
+    and Visiting Scholar at McGill University. 
+\end{IEEEbiography}
+
+%% % insert where needed to balance the two columns on the last page with
+%% % biographies
+%% %\newpage
+
+%% \begin{IEEEbiographynophoto}{Jane Doe}
+%% Biography text here.
+%% \end{IEEEbiographynophoto}
+
+% You can push biographies down or up by placing
+% a \vfill before or after them. The appropriate
+% use of \vfill depends on what kind of text is
+% on the last page and whether or not the columns
+% are being equalized.
+
+%\vfill
+
+% Can be used to pull up biographies so that the bottom of the last one
+% is flush with the other column.
+%\enlargethispage{-5in}
+
+% that's all folks
 \end{document}
-\endinput
-%%
-%% End of file `sample-authordraft.tex'.

### 2022-04-14 IEEEtran/paper.tex
Revision

--- 2022-04-14 IEEEtran/paper-annotated.tex
@@
 \usepackage{soul}
-
 %
@@
 
-\definecolor{lightred}{rgb}{1.0,0.6,0.6}
-\definecolor{lightgreen}{rgb}{0.6,1.0,0.6}
-
-\DeclareRobustCommand{\add}[1]{{\sethlcolor{lightgreen}\hl{#1}}}
-\DeclareRobustCommand{\remove}[1]{{\sethlcolor{lightred}\hl{#1}}}
-
-\DeclareRobustCommand{\addCite}[1]{{\sethlcolor{lightgreen}\hl{\mbox{#1}}}}
-\DeclareRobustCommand{\removeCite}[1]{{\sethlcolor{lightred}\hl{\mbox{#1}}}}
+\newcommand{\add}[1]{\colorbox{green!25!white}{#1}}
+\newcommand{\remove}[1]{\colorbox{red!25!white}{\st{#1}}}
 
@@
     \begin{abstract}
-        Numerical stability is a crucial requirement of reliable scientific
+        \add{Numerical stability is} a \remove{crucial requirement} of reliable scientific
         computing. However, despite the pervasiveness of Python in data science,
@@
 valuable in contrast to theoretical approaches based on condition numbers or
-backward error analysis~\addCite{\cite{higham2002accuracy}}, which require detailed modeling of the program and its
-numerical implementation. Similarly, static code analysis techniques~\addCite{\cite{goubault2006static}} hardly
+backward error analysis, which require detailed modeling of the program and its
+numerical implementation. Similarly, static code analysis techniques hardly
 scale to large code bases, particularly in dynamically-typed languages such as
@@
 program traces obtained with different numerical perturbations, which requires
-(\add{a}\remove{1}) generating numerically-perturbed executions, (\add{b}\remove{2}) tracing floating-point
-computations along program executions, and (\add{c}\remove{3}) visualizing stability
-evaluations. 
-\add{PyTracer uses the ``fuzzy" Python environment instrumented with Monte-Carlo
-arithmetic to address the requirement (a). \mbox{\pytracer} addresses the
-remaining requirements with (b) a dynamic instrumentation of Python functions,
-modules, and classes through meta-programming, (c) an interactive Plotly
-dashboard to visualize stability measures throughout program executions.
-\mbox{\pytracer} is available at
-\mbox{\href{https://github.com/big-data-lab-team/pytracer.git}{github.com/big-data-lab-team/pytracer.git}}
-under MIT License.}
-\remove{\mbox{\pytracer} addresses these requirements with (1) a ``fuzzy" Python
+(1) generating numerically-perturbed executions, (2) tracing floating-point
+computations along program executions, and (3) visualizing stability
+evaluations. \pytracer addresses these requirements with (1) a ``fuzzy" Python
 interpreter instrumented with Monte-Carlo arithmetic, (2) a dynamic
@@
 meta-programming, (3) an interactive Plotly dashboard to visualize stability
-    measures throughout program executions. }
+measures throughout program executions.
 
@@
 Python methods. However, some attributes are not writable. In this case,
-\pytracer \remove{preservers} \add{preserves} the original attributes and warns the user. The user can
+\pytracer preservers the original attributes and warns the user. The user can
 also restrict the list of traced attributes through an inclusion/exclusion
@@
 required modification in the application source code, in contrast with
-\remove{decorator-based approaches} \add{a decorator-based approache~\mbox{\cite{hunt2019decorators}}}. 
-In addition, this technique is scalable and
+decorator-based approaches. In addition, this technique is scalable and
 applicable in read-only environments such as Singularity containers or HPC
@@
 
-\remove{Listings~\mbox{\ref{fig:wrapper_creation}} and~\mbox{\ref{fig:generic_wrapper}} show
-    \mbox{\pytracer}'s function instrumentation mechanism.}
-For each function to instrument, \pytracer's \texttt{loader} class creates a
-wrapper function, dynamically compiles it with the \texttt{compile} builtin
-function, and substitutes it for the original module function.  Although simple,
-this technique does not apply to callable class instances, i.e., class instances
-that have a \texttt{\_\_call\_\_} attribute and are not of type
-\texttt{FunctionType}. Indeed, applying the wrapper technique would 1) modify
-the type of the class instance to \texttt{FunctionType}, which could cause
-syntax and semantic errors, and 2) mask class attributes, leading to
-\texttt{AttributeError} exceptions. \pytracer overrides the
-\texttt{\_\_call\_\_} attribute with the wrapper function when possible to
-overcome this issue. When the \texttt{\_\_call\_\_} attribute is not writable,
-Pytracer does not instrument the class and returns a warning.
-
-% \begin{listing}
-%     \centering
-%     \begin{lstlisting}[language=Python,style=customPython]
-% def get_wrapper_function(module, qualname, name, function):
-%     """Returns the instrumented function as a string.
-%     This string will be compiled with the compile builtin function
-
-%     Parameters:
-%         module: Name of the function module
-%         qualname: Qualified name of the function
-%         name: Name of the function
-%         function: Python object function
-
-%     Returns:
-%         wrapper_code: The code source of the wrapper
-%     """
-%     info = (id(function), function_module, qualname)
-%     wrapper_code = f"""
-%     def {function_wrapper_name}(*args, **kwargs):
-%         return generic_wrapper({info},*args,**kwargs)"""
-%     return wrapper_code
-% \end{lstlisting}
-%     \caption{Function to create the instrumented version of a function.
-%         \pytracer uses the identifier of the function instead of the 
-%         actual function to handle aliases and avoid duplicate instrumentation.}
-%     \label{fig:wrapper_creation}
-% \end{listing}
-
-% \begin{listing}
-%     \centering
-%     \begin{lstlisting}[language=Python,style=customPython,]
-% def generic_wrapper(self, info, *args, **kwargs):
-%     """Generic wrapper saving inputs and outputs of the wrapped function.
-%     The id_dict dict keeps a mapping between the original function identifier
-%     and itself. Arguments are binded to avoid mispositioning.
-%     Returns the actual output of the wrapped function.
-
-%     Parameters:
-%         info: Tuple with the function's id, function's module and function's name
-%         *args: Positional calling arguments
-%         **kwargs: Keyword calling arguments
-
-%     Returns:
-%         outputs: Outputs of the wrapped function
-%     """
-%     fid, module_name, function_name = info
-%     function = original_function_cache.id_dict[fid]
-%     bind = Binding(function, *args, **kwargs)
-%     stack = self.backtrace()
-%     time = elements()
-%     self.inputs(time, module_name, function_name, function, bind.arguments, stack)
-%     outputs = function(*bind.args, **bind.kwargs)
-%     self.outputs(time, module_name, function_name, function, outputs, stack)
-%     return outputs
-% \end{lstlisting}
-%     \caption{\pytracer's generic wrapper function that saves
-%         the inputs and outputs of the wrapped function.}
-%     \label{fig:generic_wrapper}
-% \end{listing}
+Listings~\ref{fig:wrapper_creation} and~\ref{fig:generic_wrapper} show
+\pytracer's function instrumentation mechanism. For each function to instrument,
+\pytracer's \texttt{loader} class creates a wrapper function, dynamically
+compiles it with the \texttt{compile} builtin function, and substitutes it for
+the original module function.  Although simple, this technique does not apply to
+callable class instances, i.e., class instances that have a
+\texttt{\_\_call\_\_} attribute and are not of type \texttt{FunctionType}.
+Indeed, applying the wrapper technique would 1) modify the type of the class
+instance to \texttt{FunctionType}, which could cause syntax and semantic errors,
+and 2) mask class attributes, leading to \texttt{AttributeError} exceptions.
+\pytracer overrides the \texttt{\_\_call\_\_} attribute with the wrapper
+function when possible to overcome this issue. When the \texttt{\_\_call\_\_}
+attribute is not writable,  Pytracer does not instrument the class and returns a
+warning.
+
+\begin{listing}
+    \centering
+    \begin{lstlisting}[language=Python,style=customPython]
+def get_wrapper_function(module, qualname, name, function):
+    """Returns the instrumented function as a string.
+    This string will be compiled with the compile builtin function
+
+    Parameters:
+        module: Name of the function module
+        qualname: Qualified name of the function
+        name: Name of the function
+        function: Python object function
+
+    Returns:
+        wrapper_code: The code source of the wrapper
+    """
+    info = (id(function), function_module, qualname)
+    wrapper_code = f"""
+    def {function_wrapper_name}(*args, **kwargs):
+        return generic_wrapper({info},*args,**kwargs)"""
+    return wrapper_code
+\end{lstlisting}
+    \caption{Function to create the instrumented version of a function.
+        \pytracer uses the identifier of the function instead of the 
+        actual function to handle aliases and avoid duplicate instrumentation.}
+    \label{fig:wrapper_creation}
+\end{listing}
+
+\begin{listing}
+    \centering
+    \begin{lstlisting}[language=Python,style=customPython,]
+def generic_wrapper(self, info, *args, **kwargs):
+    """Generic wrapper saving inputs and outputs of the wrapped function.
+    The id_dict dict keeps a mapping between the original function identifier
+    and itself. Arguments are binded to avoid mispositioning.
+    Returns the actual output of the wrapped function.
+
+    Parameters:
+        info: Tuple with the function's id, function's module and function's name
+        *args: Positional calling arguments
+        **kwargs: Keyword calling arguments
+
+    Returns:
+        outputs: Outputs of the wrapped function
+    """
+    fid, module_name, function_name = info
+    function = original_function_cache.id_dict[fid]
+    bind = Binding(function, *args, **kwargs)
+    stack = self.backtrace()
+    time = elements()
+    self.inputs(time, module_name, function_name, function, bind.arguments, stack)
+    outputs = function(*bind.args, **bind.kwargs)
+    self.outputs(time, module_name, function_name, function, outputs, stack)
+    return outputs
+\end{lstlisting}
+    \caption{\pytracer's generic wrapper function that saves
+        the inputs and outputs of the wrapped function.}
+    \label{fig:generic_wrapper}
+\end{listing}
 
@@
 numerical noise, we experimented primarily with Monte-Carlo Arithmetic (MCA) as
-it is an accurate model for floating-point errors~\addCite{\cite{verificarlo}}.
+it is an accurate model for floating-point errors.
 
@@
 stochastic  arithmetic,  uncertainty  or  sensitivity analysis [23], and random
-seed analysis [11].  \hl{PyTracer is agnostic to the noise model used and therefore
-    works for all methods mentioned}.  For our use cases, we focus on stochastic
+seed analysis [11].  PyTracer is agnostic to the noise model used and therefore
+works for all methods mentioned.  For our use cases, we focus on stochastic
 arithmetic since it does not make any assumption about the noise model, in
-contrast to sensitivity analysis\add{.}
+contrast to sensitivity analysis
 
@@
 single-threaded and that the control flow does not depend on a random state.
-\add{Therefore, \mbox{\pytracer} cannot merge traces resulting from a different control flow path
-    and will stop the parsing when encountering one.}
 
@@
 their respective GitHub repositories. We traced each example five times, having
-activated MCA in the Python interpreter \add{as well as} BLAS, LAPACK, NumPy, SciPy, and
-scikit-learn. \add{Only instrumented the Python interpreter would lead to
-    only perturbe pure Python floating-point operations and thus to miss
-    operations in compiled codes (i.e. Cython and shared libraries).}
-\hl{We repeated the experiment with two MCA modes, Random Rounding
-    (RR) and Full MCA, resulting in 2 experiments for each example}. We used the
+activated MCA in the Python interpreter, BLAS, LAPACK, NumPy, SciPy, and
+scikit-learn. We repeated the experiment with two MCA modes, Random Rounding
+(RR) and Full MCA, resulting in 2 experiments for each example. We used the
 default virtual precision in Verificarlo, namely 24 bits for single-precision
@@
 \begin{listing}
-    \begin{lstlisting}[language=C,style=customC,numbers=left, firstnumber=3163, mathescape=true]
+    \begin{lstlisting}[language=C,style=customC,numbers=right, firstnumber=3163, mathescape=true]
 /* NUMPY_API Arange, */
@@
 
-\add{The} top row in Figures~\ref{fig:fft1D_inputs} and~\ref{fig:fft1D_outputs} show the
+Top row in Figures~\ref{fig:fft1D_inputs} and~\ref{fig:fft1D_outputs} show the
 input mean value while the bottom row shows the standard deviation. The points
@@
 
-\paragraph{Unconstrained minimization of multivariate scalar functions}
+\paragraph{Unconstrained minimization of multivariate scalar functions:}
 Four Quasi-Newton-Raphson methods minimize function $f$ by using Newton's step:
@@
 
-\paragraph{Constrained minimization of multivariate scalar functions}
+\paragraph{Constrained minimization of multivariate scalar functions:}
 Two optimizers solve an optimization problem by taking into account constraints.
@@
 
+\paragraph{}
 The SLSQP and unconstrained minimization methods minimize the
@@
 
-\paragraph{Root finding}
+\paragraph{Root finding:}
 % We tested three root finder algorithms with one for small problems using the hybrid Powell and Levenberg-Marquardt methods  (\texttt{root\_finding}) and two for large problems using a Krylov approximation for the inverse Jacobian with and without the help of a preconditioner (\texttt{root\_finding\_large\_preconditionned} and \texttt{root\_finding\_large}).
@@
 \texttt{root\_finding\_large\_preconditioned} examples use the Krylov method to
-approximate the inverse Jac\add{o}bian with and without the help of a preconditioner.
+approximate the inverse Jacbian with and without the help of a preconditioner.
 They solve an integrodifferential equation on a square $(x,y) \in [0,1] \times
@@
 \texttt{Not-a-Number} (\texttt{NaN}) values for OLS. On the same figure, we can
-see that using the \texttt{gesvd} (\remove{dgelsd} \add{dgelss}) method instead of the \texttt{gesdd}
-(\remove{dgelss} \add{dgelsd}) one, the SVD converges for RR and Full MCA, with a number of
+see that using the \texttt{gesvd} (dgelsd) method instead of the \texttt{gesdd}
+(dgelss) one, the SVD converges for RR and Full MCA, with a number of
 significant bits of 44 on average. This observation supports the on-going
@@
 
-The face recognition example uses eigenfaces (eigenvectors) and Support Vector
-Machines (SVMs) to classify faces from the Labeled Faces in the Wild dataset.
-This example uses a Principal Component Analysis (PCA) to extract the eigenfaces
-and then trains an SVM classifier to predict the name associated with a face.
-This example is the only one to raise an error with RR due to the
-non-convergence of the Singular Value Decomposition (SVD) performed in the PCA.
-
-In this example, the PCA uses the Randomized SVD~\cite{halko2011finding} method
-that first computes a low-rank approximation of the input matrix using a
-stochastic algorithm and then uses this approximation as input for the SVD. The
-example raises an error during the computation of the SVD. The
-\texttt{randomized\_svd} scikit-learn function uses the Divide \& Conquer SVD
-method \texttt{gesdd} mentioned previously. Replacing \texttt{gesdd} for
-\texttt{gesvd} solves the SVD convergence issue.
-Figure~\ref{fig:randomized_svd_S} shows the precision of the eigenvalues
-computed with gesvd \add{in single precision}, which varies between 15 and 20 significant bits out of the
-24 available in single precision. The classifier metrics (precision, recall,
-F1-score, and support) are identical to the IEEE execution for all MCA samples.
-
-In conclusion, \pytracer and the MCA model were helpful to detect the
-instability of the \texttt{gesdd} method mentioned in several GitHub issues,
-including the LAPACK repository. Furthermore, it is worth mentioning that a Pull
-Request has recently been submitted to let the user select the SVD method and
-avoid this kind of issue. Thus, \pytracer can detect instabilities that affect
-fundamental scientific computing components such as the LAPACK library.
+The face recognition example uses eigenfaces (eigenvectors) and Support Vector Machines (SVMs) to classify faces from the Labeled Faces in the Wild dataset.
+This example uses a Principal Component Analysis (PCA) to extract the eigenfaces and then trains an SVM classifier to predict the name associated with a face.
+This example is the only one to raise an error with RR due to the non-convergence of the Singular Value Decomposition (SVD) performed in the PCA.
+
+In this example, the PCA uses the Randomized SVD~\cite{halko2011finding} method that first computes a low-rank approximation of the input matrix using a stochastic algorithm and then uses this approximation as input for the SVD.
+The example raises an error during the computation of the SVD.
+The \texttt{randomized\_svd} scikit-learn function uses the Divide \& Conquer SVD method \texttt{gesdd} mentioned previously.
+Replacing \texttt{gesdd} for \texttt{gesvd} solves the SVD convergence issue.
+Figure~\ref{fig:randomized_svd_S} shows the precision of the eigenvalues computed with gesvd, which varies between 15 and 20 significant bits out of the 24 available in single precision.
+The classifier metrics (precision, recall, F1-score, and support) are identical to the IEEE execution for all MCA samples.
+
+In conclusion, \pytracer and the MCA model were helpful to detect the instability of the \texttt{gesdd} method mentioned in several GitHub issues, including the LAPACK repository.
+Furthermore, it is worth mentioning that a Pull Request has recently been submitted to let the user select the SVD method and avoid this kind of issue.
+Thus, \pytracer can detect instabilities that affect fundamental scientific computing components such as the LAPACK library.
 % The Pytracer findings can therefore be extended to many application domains.
@@
 iterations to 100. The prediction is made on a $[-4,5]\times[-4,5]$ grid
-discretized with 250\add{,}000 points. Figures~\ref{fig:weighted_nw_sig}
+discretized with 250 000 points. Figures~\ref{fig:weighted_nw_sig}
 and~\ref{fig:weighted_w_sig} show the number of significant bits of prediction
-within RR along with dataset points in blue and \remove{violet} \add{purple}. We can see that the
+within RR along with dataset points in blue and violet. We can see that the
 separating plane corresponds to a region of lower precision, similar to the
@@
 initialization time to \textit{Slowdown}. We then obtain an average slowdown of
-$3.5\times$. Finally, the \remove{fuzzy instrumentation} \add{using MCA operations (throuhg fuzzy) instead of the native ones} increases the average slowdown
+$3.5\times$. Finally, the fuzzy instrumentation increases the average slowdown
 to $37\times$ for RR and $43\times$ for Full MCA.
@@
         using the fuzzy environment with RR and Full MCA modes.
-        The first \remove{first} \add{last} four examples measure the initialization steps depending on the modules instrumented. 
+        The first four examples measure the initialization steps depending on the modules instrumented. 
         % \tristan{there's too much text in this caption, move some of it to the text, the caption should just explain the difference between the 4 slowdowns.
@@
 CADNA~\cite{jezequel2008cadna} is a library for C, C++, and Fortran implementing
+
 CESTAC~\cite{vignes1993stochastic} stochastic arithmetic.
@@
 that implements the Monte Carlo Arithmetic (MCA)~\cite{parker1997monte} using
-the MPFR~\cite{fousse2007mpfr} library. \add{ADAPT \mbox{~\cite{menon2018adapt}} uses
-    Automatic Differentiation to compute a sensitivity profile for each variable of
-    given program}. Finally, the work in~\cite{tang2016software} proposed a
-source-to-source framework for executing targeted code in infinite and fixed
-precision with and without stochastic arithmetic. The main drawback of the
-source-to-source approach is its lacks of scalability since rewriting large
-codes can be a tedious task.
+the MPFR~\cite{fousse2007mpfr} library. Finally, the work
+in~\cite{tang2016software} proposed a source-to-source framework for executing
+targeted code in infinite and fixed precision with and without stochastic
+arithmetic. The main drawback of the source-to-source approach is its lacks of
+scalability since rewriting large codes can be a tedious task.
 
@@
 (AST) level to rewrite parts of code with higher precision.
-PFPSanitizer~\cite{chowdhary2020debugging,chowdhary2021parallel} \add{and
-    NSan~\mbox{\cite{courbet2021nsan}} are compiler based approaches}
-that use shadow execution to detect numerical issues using higher
-precision.
-FLiT~\cite{sawaya2017flit} is a framework to detect variability
+PFPSanitizer~\cite{chowdhary2020debugging,chowdhary2021parallel} is a compiler
+that uses parallel shadow execution to detect numerical issues using higher
+precision. FLiT~\cite{sawaya2017flit} is a framework to detect variability
 induced by compilers and their optimizations. The work
@@
 using shadow computations with higher precision.
-Herbgrin\remove{g}\add{d}~\cite{sanchez2017finding} is a Valgrind-based tool to detect numerical
+Herbgring~\cite{sanchez2017finding} is a Valgrind-based tool to detect numerical
 instabilities. It uses a shadow memory to detect precision losses by comparison
-with results obtained \remove{at} \add{in} higher precision. It is combined with symbolic
+with results obtained at higher precision. It is combined with symbolic
 computation to backtrack the root of the error. We can note that all methods
@@
 \bibliographystyle{IEEEtran}
-\bibliography{paper-annotated}
+\bibliography{paper}
 

### 2022-04-14 preprint/paper.tex
Revision

--- 2021-12-21 paper.tex
@@
 \usepackage{todonotes}
-\usepackage{natbib}
 \usepackage{graphicx}
@@
 \title{PyTracer: Automatically profiling numerical instabilities in Python}
-\author{Yohan Chatelain$^1$, Nigel Young$^1$,  Gregory Kiar$^2$,  Tristan Glatard$^1$\\
+\author{Yohan Chatelain$^1$, Nigel Yong$^1$,  Gregory Kiar$^2$,  Tristan Glatard$^1$\\
 $^1$Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada\\
 $^2$Center for the Developing Brain, Child Mind Institute, New York, NY, USA}
-    \date{}
+\date{\textit{This work has been submitted to the IEEE for possible publication. 
+Copyright may be transferred without notice, after which this version may no 
+longer be accessible.}}
 \maketitle
@@
     \includegraphics[width=\linewidth]{figure/bspline/bspline_sig.pdf}
-    \caption{\centering\texttt{sepfir2d} significant bits. \\ \textcolor{white}{.}}
+    \caption{\centering\texttt{sepfir2d} significant bits. \newline \textcolor{white}{.}}
     \label{fig:bspline_bisplev_sig}
@@
     \includegraphics[width=\linewidth]{figure/bspline/bspline_mean_log.pdf}
-    \caption{\centering\texttt{sepfir2d} mean. \\(log)}
+    \caption{\centering\texttt{sepfir2d} mean. \newline (log)}
     \label{fig:bspline_bisplev_mean}
@@
     \includegraphics[width=\linewidth]{figure/bspline/convol2d_sig.pdf}
-    \caption{\centering\texttt{convol2d} significant bits. \\ \textcolor{white}{.}}
+    \caption{\centering\texttt{convol2d} significant bits. \newline \textcolor{white}{.}}
     \label{fig:bspline_convol2d_sig}
@@
     \includegraphics[width=\linewidth]{figure/bspline/convol2d_mean_log.pdf}
-    \caption{\centering\texttt{convol2d} mean. \\ (log)}
+    \caption{\centering\texttt{convol2d} mean. \newline (log)}
     \label{fig:bspline_convol2d_mean}
@@
 \bibliographystyle{abbrv}
-\bibliography{biblio}
+\bibliography{paper}
 

### 2022-05-10 IEEEtran/paper-annotated.tex
Update for major revision

@@
 \usepackage{soul}
-
+%\usepackage{cancel}
 %
@@
 
-\definecolor{lightred}{rgb}{1.0,0.6,0.6}
-\definecolor{lightgreen}{rgb}{0.6,1.0,0.6}
-
-\DeclareRobustCommand{\add}[1]{{\sethlcolor{lightgreen}\hl{#1}}}
-\DeclareRobustCommand{\remove}[1]{{\sethlcolor{lightred}\hl{#1}}}
-
-\DeclareRobustCommand{\addCite}[1]{{\sethlcolor{lightgreen}\hl{\mbox{#1}}}}
-\DeclareRobustCommand{\removeCite}[1]{{\sethlcolor{lightred}\hl{\mbox{#1}}}}
+\definecolor{lightred}{rgb}{0.6,0.0,0.0}
+\definecolor{lightgreen}{rgb}{0.8,1.0,0.8}
+
+\DeclareRobustCommand{\add}[1]{\sethlcolor{lightgreen}\hl{#1}}
+\DeclareRobustCommand{\remove}[1]{\textcolor{lightred}{\sout{#1}}}
+
+\DeclareRobustCommand{\addCite}[1]{\textcolor{lightgreen}{\mbox{#1}}}
 
@@
     \end{abstract}
+
+    % Note that keywords are not normally used for peerreview papers.
+    \begin{IEEEkeywords}
+        Computer arithmetic, Quality analysis and evaluation, Visualization
+        techniques and methodologies, Tracing,  Stochastic analysis
+    \end{IEEEkeywords}
 }
-% Note that keywords are not normally used for peerreview papers.
-%% \begin{IEEEkeywords}
-%% Computer Society, IEEE, IEEEtran, journal, \LaTeX, paper, template.
-%% \end{IEEEkeywords}}
 
@@
 valuable in contrast to theoretical approaches based on condition numbers or
-backward error analysis~\addCite{\cite{higham2002accuracy}}, which require detailed modeling of the program and its
-numerical implementation. Similarly, static code analysis techniques~\addCite{\cite{goubault2006static}} hardly
-scale to large code bases, particularly in dynamically-typed languages such as
-Python.
+backward error analysis~\addCite{\cite{higham2002accuracy}}, which require
+detailed modeling of the program and its numerical implementation. Similarly,
+static code analysis techniques~\addCite{\cite{goubault2006static}} hardly scale
+to large code bases, particularly in dynamically-typed languages such as Python.
 
@@
 program traces obtained with different numerical perturbations, which requires
-(\add{a}\remove{1}) generating numerically-perturbed executions, (\add{b}\remove{2}) tracing floating-point
-computations along program executions, and (\add{c}\remove{3}) visualizing stability
-evaluations. 
+(\add{a}\remove{1}) generating numerically-perturbed executions,
+(\add{b}\remove{2}) tracing floating-point computations along program
+executions, and (\add{c}\remove{3}) visualizing stability evaluations.
 \add{PyTracer uses the ``fuzzy" Python environment instrumented with Monte-Carlo
@@
     \mbox{\href{https://github.com/big-data-lab-team/pytracer.git}{github.com/big-data-lab-team/pytracer.git}}
-under MIT License.}
-\remove{\mbox{\pytracer} addresses these requirements with (1) a ``fuzzy" Python
-    interpreter instrumented with Monte-Carlo arithmetic, (2) a dynamic
-    instrumentation of Python functions, modules, and classes through
+    under MIT License.} \remove{\mbox{\pytracer} addresses these requirements with
+    (1) a ``fuzzy" Python interpreter instrumented with Monte-Carlo arithmetic, (2)
+    a dynamic instrumentation of Python functions, modules, and classes through
     meta-programming, (3) an interactive Plotly dashboard to visualize stability
@@
 review the numerical stability of extensive code bases.
+
+\section{Philosophy of \pytracer}
+
+\add{PyTracer follows a three steps approach:}
+\begin{enumerate}
+    \item \add{Automatic instrumentation of Python programs to save the value of inputs and outputs of function in a file.}
+    \item \add{Aggregation of the traces generated to produce a statistics summary.}
+    \item \add{Interactive visualization to navigate through the code execution.}
+\end{enumerate}
+
+\add{
+    The main goal of PyTracer is to help the developper visualizing the numerical
+    stability of Python applications. PyTracer saves time for the user by
+    instrumenting and aggregating values. In the same way that GDB makes the user
+    save time when debugging an application by providing all information in one
+    layout, PyTracer allows the user to visualize the overall numerical quality to
+    quickly detect instabilities. The PyTracer visualization layout improves result
+    analysis in any case since 1) the user does not have to manually instrument its
+    code to dump raw data and creates specific post-processing scripts to visualize
+    it 2) PyTracer allows the user to export the raw data traced to extend the
+    analysis. 
+}
+
+\add{
+    The main challenge addresses by PyTracer is the transparent instrumentation of Python 
+    applications. Indeed, since Python is interpreted language, one has no complete 
+    view of the function that will be executed by a given program. 
+    Moreover, since we target Python application used in HPC environments, one has
+    most of the time no access to source codes or with limited write access.
+    Therefore, PyTracer tackles this issue by instrumenting the function dynamically 
+    thanks to the Python introspection.
+}
+
+\add{
+    The based-trace approach used by PyTracer permits to limit the 
+    overhead at runtime since the statistics computation is reported to the postprocess analysis.
+    However, it limits the aggregation to deterministic executions,
+    although control-flow analysis can help to merge divergent execution paths.
+}
 
@@
 
-\begin{figure}
+\begin{figure*}
     \centering
-    \includegraphics[width=\linewidth]{figure/workflow.pdf}
+    \includegraphics[width=0.75\linewidth]{figure/workflow.pdf}
     \caption{Pytracer workflow
-        % \gkmod{}{Note: replace "Execution" with "Multiple Independent Executions", and maybe move it to be between the gears and the pkl files.}
+        % \gkmod{}{Note: replace "Execution" with "Multiple Independent
+        % Executions", and maybe move it to be between the gears and the pkl
+        % files.}
     }
     \label{fig:workflow}
-\end{figure}
+\end{figure*}
 
@@
 Python methods. However, some attributes are not writable. In this case,
-\pytracer \remove{preservers} \add{preserves} the original attributes and warns the user. The user can
-also restrict the list of traced attributes through an inclusion/exclusion
-mechanism. The main advantage of this instrumentation approach is the lack of
-required modification in the application source code, in contrast with
-\remove{decorator-based approaches} \add{a decorator-based approache~\mbox{\cite{hunt2019decorators}}}. 
-In addition, this technique is scalable and
-applicable in read-only environments such as Singularity containers or HPC
-clusters.
+\pytracer \remove{preservers} \add{preserves} the original attributes and warns
+the user. The user can also restrict the list of traced attributes through an
+inclusion/exclusion mechanism. The main advantage of this instrumentation
+approach is the lack of required modification in the application source code, in
+contrast with \remove{decorator-based approaches} \add{a decorator-based
+    approache~\mbox{\cite{hunt2019decorators}}}. In addition, this technique is
+scalable and applicable in read-only environments such as Singularity containers
+or HPC clusters.
 
@@
 stochastic  arithmetic,  uncertainty  or  sensitivity analysis [23], and random
-seed analysis [11].  \hl{PyTracer is agnostic to the noise model used and therefore
+seed analysis [11].  \add{PyTracer is agnostic to the noise model used and therefore
     works for all methods mentioned}.  For our use cases, we focus on stochastic
@@
 Virtual precision allows for the simulation of reduced working precision. MCA
-can be applied in three modes: Random Rounding (RR), Precision Bounding (PB),
-and full MCA, which apply function $inexact$ to the output, the inputs, or both,
-respectively. While the RR mode is equivalent to stochastic rounding, the PB
-mode can also identify catastrophic cancellations.
+can be applied in three modes \add{but we only used the} Random Rounding (RR) \add{in our
+    experiments} \remove{, Precision Bounding (PB), and full MCA,} which apply
+function $inexact$ to the output. \remove{, the inputs, or both, respectively.
+    While the RR mode is equivalent to stochastic rounding, the PB mode can also
+    identify catastrophic cancellations.} \add{Random Rounding simulates roundoff errors.}
 
@@
 where $\mu$ and $\sigma$ are the sample mean and standard deviation of a
-variable sampled with MCA.  
-Sohier et al.~\cite{sohier2018confidence} recently provided a generalization of
+variable sampled with MCA. \add{This can be seen as the ratio signal over noise.}
+Sohier et al.~\cite{sohier2021confidence} recently provided a generalization of
 this formula to include confidence intervals.
@@
 single-threaded and that the control flow does not depend on a random state.
-\add{Therefore, \mbox{\pytracer} cannot merge traces resulting from a different control flow path
-    and will stop the parsing when encountering one.}
-
-\begin{figure}
+\add{Therefore, \mbox{\pytracer} cannot merge traces resulting from a different
+    control flow path and will stop the parsing when encountering one.}
+
+\begin{figure*}
     \centering
-    \includegraphics[width=\columnwidth]{figure/pytracer_layout.pdf}
+    \includegraphics[width=0.75\linewidth]{figure/pytracer_layout.pdf}
     \caption{Pytracer visualization layout.}
     \label{fig:visu-layout}
-\end{figure}
+\end{figure*}
 
@@
 
-\section{Numerical evaluations}
+\section{Results}
 
@@
 their respective GitHub repositories. We traced each example five times, having
-activated MCA in the Python interpreter \add{as well as} BLAS, LAPACK, NumPy, SciPy, and
-scikit-learn. \add{Only instrumented the Python interpreter would lead to
-    only perturbe pure Python floating-point operations and thus to miss
-    operations in compiled codes (i.e. Cython and shared libraries).}
-\hl{We repeated the experiment with two MCA modes, Random Rounding
-    (RR) and Full MCA, resulting in 2 experiments for each example}. We used the
-default virtual precision in Verificarlo, namely 24 bits for single-precision
-floating-point values and 53 bits for double-precision values, which simulates
-machine error. We used Python-3.8.5, NumPy-1.19.1, SciPy-1.5.4, and
-scikit-learn-0.23.2.
-
-\subsection{Results overview}
+activated MCA in the Python interpreter \add{as well as} BLAS, LAPACK, NumPy,
+SciPy, and scikit-learn. \add{Only instrumented the Python interpreter would
+    lead to only perturbe pure Python floating-point operations and thus to miss
+    operations in compiled codes (i.e. Cython and shared libraries).} \add{We
+    repeated the experiment with two MCA modes, Random Rounding (RR) and Full MCA,
+    resulting in 2 experiments for each example}. We used the default virtual
+precision in Verificarlo, namely 24 bits for single-precision floating-point
+values and 53 bits for double-precision values, which simulates machine error.
+We used Python-3.8.5, NumPy-1.19.1, SciPy-1.5.4, and scikit-learn-0.23.2.
+
+\add{Monte Carlo Arithmetic samples the floating-point variability of a given
+    program, and hence the more MCA repetitions we have, the more accurate will be
+    the sampling distribution. In theory, an infinite number of MCA repetitions
+    should give the exact distribution. While in practice low sample size (3$\simeq$30)
+    can give a good estimate, the issue is to capture "rare events" that could make the
+    computation strongly diverge from the mean. For now, determining the number of
+    MCA samples to use is still an open research question. 
+    Recent theoretical works}~\cite{sohier2021confidence}
+\add{on the significant digits computation allow computing an associated
+    confidence interval depending on the sample size and the underlying distribution of the outputs.}
+
+% \subsection{Results overview}
+
+% Table~\ref{tab:pytracer_results_summary} summarizes \pytracer's outcome on SciPy
+% and scikit-learn examples. Columns \textit{trace} and \textit{parse} report on
+% the tracing and aggregation steps with three possible outcomes: 1) green for
+% success, meaning that the execution ended well and no issues were raised by the
+% application, 2) red for numerical error in the application, meaning that the
+% execution raised a Python error before the end, and 3) orange for errors due to
+% the fuzzy noise injection that are not considered numerical errors, meaning that
+% the execution raised a Python error but due to a perturbation that should not
+% have been introduced (i.e. a floating-point value representing an integer).
+% Overall, the tracing and parsing of SciPy and scikit-learn examples in Random
+% Rounding mode was entirely successful for 32/40 examples and showed an average
+% precision loss of 8 bits. The remaining examples failed due to numerical errors
+% in the libraries, which we discuss hereafter. The instrumentation with Full MCA
+% is more invasive and reduced the number of successful executions to 12/40. Among
+% the 28/40 failed executions, one failed due to an actual numerical error
+% (\texttt{Bayesian Ridge Regression} example) and the other ones failed due to
+% perturbations that should not have been introduced.
+
+% Column \textit{sigbits} in Table~\ref{tab:pytracer_results_summary} summarizes
+% the precision for the main outputs of SciPy and scikit-learn examples. We
+% measured the precision in significant bits on the final primary example output
+% by taking the element-wise mean for non-scalar values and, if the example
+% produces many outputs, the average value among all of them. The numerical
+% quality across all examples varies from 0 to 52, with an average of 44
+% significant bits. For both modes, we note that only two examples failed due to a
+% numerical error (\texttt{face\_recognition} for RR and \texttt{Bayesian Ridge
+%     Regression} for Full MCA).
+
+\begin{table*}[]
+    \centering
+    \normalsize
+    \begin{subfigure}[t]{\linewidth}
+        \centering
+        \begin{tabular}{|lll|c|c|c|}
+            \hline
+            \multicolumn{3}{|c}{ \multirow{2}{*}{Application} }                 & \multicolumn{3}{|c|}{Random Rounding (RR)}                                                                                                                         \\
+            \cline{4-6}
+                                                                                &                                                                           &                                                          & trace  & parse    & sigbits \\
+            \hline
+            \multicolumn{1}{|c|}{ \multirow{20}{2em}{ \rotatebox{90}{SciPy} } } & 
+            \multicolumn{1}{c|}{ \multirow{3}{2em}{ \rotatebox{90}{FFT} }}      & \discreteCosineRF                                                         & \valid                                                   & \valid & \s{52}             \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \fftOneDRf                                               & \valid & \valid   & 41      \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \fftTwoDRf                                               & \valid & \valid   & \s{52}  \\
+            \cline{2-6}
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{  \multirow{5}{*}{ \rotatebox{90}{Interpolation} } }
+                                                                                & \interOneDRf                                                              & \valid                                                   & \valid & 51                 \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \multiRf                                                 & \valid & \valid   & \s{51}  \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \bsplineRf                                               & \valid & \valid   & 10      \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \splineOneDRf                                            & \valid & \cross   & \s{52}  \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \splineTwoDRf                                            & \valid & \valid   & 10      \\
+            \cline{2-6}
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{ \multirow{12}{2em}{ \rotatebox{90}{Optimization} } }
+                                                                                & \bfgsRf                                                                   & \valid                                                   & \valid & \s{48}             \\
+            \cline{3-6}
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \globalRf                                                & \valid & \cross   & 17      \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & | SHGO\footnote{Simplicial Homology Global Optimization} & \na    & \na      & \s{25}  \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & | Dual Annealing                                         & \na    & \na      & 4       \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & | Differential Evolution                                 & \na    & \na      & \s{0}   \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & | Basin Hopping                                          & \na    & \na      & 40      \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & | SHGO Sobol                                             & \na    & \na      & \s{45}  \\
+            \cline{3-6}
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \slsqpRf                                                 & \valid & \valid   & 45      \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \lsmRf                                                   & \valid & \valid   & \s{48}  \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \nelderRf                                                & \valid & \valid   & 44      \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \ncgRf                                                   & \valid & \valid   & \s{48}  \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \rootRf                                                  & \valid & \cross   & 52      \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \rootLargRf                                              & \valid & \cross   & \s{29}  \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \rootLargePredRf                                         & \valid & \cross   & 42      \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \trustExactRf                                            & \valid & \valid   & \s{48}  \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \trustTruncRf                                            & \valid & \valid   & 48      \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \trustNCGRf                                              & \valid & \valid   & \s{52}  \\
+            \hline
+            \multicolumn{2}{|c|}{ \multirow{20}{2em}{ \rotatebox{90}{Scikit-learn} } }
+                                                                                & \AdaboostRf                                                               & \valid                                                   & \valid & 48                 \\
+            \cline{3-6}
+            \multicolumn{2}{|c|}{}                                              & \brrRf                                                                    & \valid                                                   & \valid & \s{25}             \\
+            \multicolumn{2}{|c|}{}                                              & | $1^{st}$ dataset                                                        & \na                                                      & \na    & 25                 \\
+            \multicolumn{2}{|c|}{}                                              & | $2^{nd}$ dataset                                                        & \na                                                      & \na    & \s{nan}            \\
+            \cline{3-6}
+            \multicolumn{2}{|c|}{}                                              & \onlineClassifierComparisonRf                                             & \valid                                                   & \valid & 20                 \\
+            \multicolumn{2}{|c|}{}                                              & \kmeansRf                                                                 & \valid                                                   & \valid & \s{52}             \\
+            \multicolumn{2}{|c|}{}                                              & \covarianceRf                                                             & \valid                                                   & \cross & 48                 \\
+            \multicolumn{2}{|c|}{}                                              & \decisionRf                                                               & \valid                                                   & \valid & \s{50}             \\
+            \multicolumn{2}{|c|}{}                                              & \digitsRf                                                                 & \valid                                                   & \valid & 52                 \\
+            \multicolumn{2}{|c|}{}                                              & \faceRf                                                                   & \cross                                                   & \valid & \s{-}              \\
+            \multicolumn{2}{|c|}{}                                              & \penaltyRf                                                                & \valid                                                   & \valid & -                  \\
+            \multicolumn{2}{|c|}{}                                              & \lassoRf                                                                  & \valid                                                   & \valid & \s{48}             \\
+            \multicolumn{2}{|c|}{}                                              & \hyperplaneRf                                                             & \valid                                                   & \valid & 3                  \\
+            \multicolumn{2}{|c|}{}                                              & \mnistRf                                                                  & \valid                                                   & \valid & \s{43}             \\
+            \multicolumn{2}{|c|}{}                                              & \multitaskRf                                                              & \valid                                                   & \valid & 50                 \\
+            \multicolumn{2}{|c|}{}                                              & \ompRf                                                                    & \valid                                                   & \valid & \s{52}             \\
+            \multicolumn{2}{|c|}{}                                              & \pcaRf                                                                    & \valid                                                   & \valid & 48                 \\
+            \cline{3-6}
+            \multicolumn{2}{|c|}{}                                              & \robustRf                                                                 & \valid                                                   & \valid & \s{50}             \\
+            \multicolumn{2}{|c|}{}                                              & | Linear                                                                  & \na                                                      & \na    & 48                 \\
+            \multicolumn{2}{|c|}{}                                              & | RANSAC                                                                  & \na                                                      & \na    & \s{50}             \\
+            \cline{3-6}
+            \multicolumn{2}{|c|}{}                                              & \toyRf                                                                    & \valid                                                   & \valid & 35                 \\
+            \cline{3-6}
+            \multicolumn{2}{|c|}{}                                              & \svmRf                                                                    & \valid                                                   & \valid & \s{43.5}           \\
+            \multicolumn{2}{|c|}{}                                              & | Non-weighted                                                            & \na                                                      & \na    & 43                 \\
+            \multicolumn{2}{|c|}{}                                              & | Weighted                                                                & \na                                                      & \na    & \s{44}             \\
+            \cline{3-6}
+            \multicolumn{2}{|c|}{}                                              & \tomographyRf                                                             & \valid                                                   & \cross & -                  \\
+            \multicolumn{2}{|c|}{}                                              & \weightedRf                                                               & \valid                                                   & \valid & \s{44}             \\
+            \hline
+        \end{tabular}
+    \end{subfigure}
+    \caption{\pytracer execution summary on SciPy and Scikit-learn examples.
+        % \tristan{Replace FFT with SciPy FFT, Interpolation with SciPy
+        % Interpolation and Optimization with SciPy Optimization, or add a SciPy
+        % header to these rows.} \tristan{Nitpick: you could add a color scheme
+        % to sigbits (for instance shades of blue), to make the column more
+        % easily readable.} \\
+        \emph{trace}: outcome of \pytracer tracing, \emph{parse}: outcome of
+        \pytracer trace parsing and aggregation, \emph{result}: precision for
+        main outputs in significant bits. \valid: successful run, \remove{\warn: error
+            from invalid noise injection,} \cross: numerical error or divergent
+        traces. \textit{nan} stands for (\texttt{Not-A-Number}). Example names
+        are linked to their source code.}
+    \label{tab:pytracer_results_summary}
+\end{table*}
+
+\subsection{Pytracer is applicable to scientific computation libraries of reference}
 
@@
 and scikit-learn examples. Columns \textit{trace} and \textit{parse} report on
-the tracing and aggregation steps with three possible outcomes: 1) green for
+the tracing and aggregation steps with two possible outcomes: 1) green for
 success, meaning that the execution ended well and no issues were raised by the
-application, 2) red for numerical error in the application, meaning that the
-execution raised a Python error before the end, and 3) orange for errors due to
-the fuzzy noise injection that are not considered numerical errors, meaning that
-the execution raised a Python error but due to a perturbation that should not
-have been introduced (i.e. a floating-point value representing an integer).
+application, and 2) red for numerical error in the application, meaning that the
+execution raised a Python error before the end. \remove{, and 3)
+    orange for errors due to the fuzzy noise injection that are
+    not considered numerical errors, meaning that the execu-
+    tion raised a Python error but due to a perturbation that
+    should not have been introduced (i.e. a floating-point value
+    representing an integer).}
 Overall, the tracing and parsing of SciPy and scikit-learn examples in Random
@@
 precision loss of 8 bits. The remaining examples failed due to numerical errors
-in the libraries, which we discuss hereafter. The instrumentation with Full MCA
-is more invasive and reduced the number of successful executions to 12/40. Among
-the 28/40 failed executions, one failed due to an actual numerical error
-(\texttt{Bayesian Ridge Regression} example) and the other ones failed due to
-perturbations that should not have been introduced.
+in the libraries, which we discuss hereafter. 
+\remove{The instrumentation with Full MCA is
+    more invasive and reduced the number of successful exe-
+    cutions to 12/40. Among the 28/40 failed executions, one
+    failed due to an actual numerical error (Bayesian Ridge
+    Regression example) and the other ones failed due to
+    perturbations that should not have been introduced.}
 
@@
 quality across all examples varies from 0 to 52, with an average of 44
-significant bits. For both modes, we note that only two examples failed due to a
-numerical error (\texttt{face\_recognition} for RR and \texttt{Bayesian Ridge
-    Regression} for Full MCA).
-
-\begin{table*}[]
-    \centering
-    \small
-    \begin{subfigure}[t]{\linewidth}
-        \centering
-        \begin{tabular}{|lll|c|c|c|c|c|c|}
-            \hline
-            \multicolumn{3}{|c}{ \multirow{2}{*}{Application} }                 & \multicolumn{3}{|c|}{Random Rounding (RR)}                                & \multicolumn{3}{c|}{Full MCA}                                                                                      \\
-            \cline{4-9}
-                                                                                &                                                                           &                                                          & trace  & parse    & sigbits & trace  & parse  & sigbits \\
-            \hline
-            \multicolumn{1}{|c|}{ \multirow{20}{2em}{ \rotatebox{90}{SciPy} } } & 
-            \multicolumn{1}{c|}{ \multirow{3}{2em}{ \rotatebox{90}{FFT} }}      & \discreteCosineRF                                                         & \valid                                                   & \valid & \s{52}   & \warn   & \cross & \s{47}           \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \fftOneDRf                                               & \valid & \valid   & 41      & \warn  & \cross & -       \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \fftTwoDRf                                               & \valid & \valid   & \s{52}  & \valid & \valid & \s{52}  \\
-            \cline{2-9}
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{  \multirow{5}{*}{ \rotatebox{90}{Interpolation} } }
-                                                                                & \interOneDRf                                                              & \valid                                                   & \valid & 51       & \warn   & \cross & -                \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \multiRf                                                 & \valid & \valid   & \s{51}  & \warn  & \cross & \s{-}   \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \bsplineRf                                               & \valid & \valid   & 10      & \valid & \valid & 10      \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \splineOneDRf                                            & \valid & \cross   & \s{52}  & \warn  & \cross & \s{52}  \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \splineTwoDRf                                            & \valid & \valid   & 10      & \warn  & \cross & -       \\
-            \cline{2-9}
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{ \multirow{12}{2em}{ \rotatebox{90}{Optimization} } }
-                                                                                & \bfgsRf                                                                   & \valid                                                   & \valid & \s{48}   & \valid  & \valid & \s{46}           \\
-            \cline{3-9}
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \globalRf                                                & \valid & \cross   & 17      & \warn  & \cross & -       \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & | SHGO\footnote{Simplicial Homology Global Optimization} & \na    & \na      & \s{25}  & \na    & \na    & \s{-}   \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & | Dual Annealing                                         & \na    & \na      & 4       & \na    & \na    & -       \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & | Differential Evolution                                 & \na    & \na      & \s{0}   & \na    & \na    & \s{-}   \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & | Basin Hopping                                          & \na    & \na      & 40      & \na    & \na    & -       \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & | SHGO Sobol                                             & \na    & \na      & \s{45}  & \na    & \na    & \s{-}   \\
-            \cline{3-9}
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \slsqpRf                                                 & \valid & \valid   & 45      & \valid & \valid & 44      \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \lsmRf                                                   & \valid & \valid   & \s{48}  & \warn  & \cross & \s{-}   \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \nelderRf                                                & \valid & \valid   & 44      & \valid & \valid & 42      \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \ncgRf                                                   & \valid & \valid   & \s{48}  & \valid & \cross & \s{47}  \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \rootRf                                                  & \valid & \cross   & 52      & \warn  & \cross & 50      \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \rootLargRf                                              & \valid & \cross   & \s{29}  & \valid & \cross & \s{26}  \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \rootLargePredRf                                         & \valid & \cross   & 42      & \valid & \cross & 42      \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \trustExactRf                                            & \valid & \valid   & \s{48}  & \valid & \valid & \s{46}  \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \trustTruncRf                                            & \valid & \valid   & 48      & \valid & \valid & 46      \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \trustNCGRf                                              & \valid & \valid   & \s{52}  & \valid & \valid & \s{47}  \\
-            \hline
-            \multicolumn{2}{|c|}{ \multirow{20}{2em}{ \rotatebox{90}{Scikit-learn} } }
-                                                                                & \AdaboostRf                                                               & \valid                                                   & \valid & 48       & \warn   & \cross & -                \\
-            \cline{3-9}
-            \multicolumn{2}{|c|}{}                                              & \brrRf                                                                    & \valid                                                   & \valid & \s{25}   & \cross  & \cross & \s{-}            \\
-            \multicolumn{2}{|c|}{}                                              & | $1^{st}$ dataset                                                        & \na                                                      & \na    & 25       & \na     & \na    & -                \\
-            \multicolumn{2}{|c|}{}                                              & | $2^{nd}$ dataset                                                        & \na                                                      & \na    & \s{nan}  & \na     & \na    & \s{-}            \\
-            \cline{3-9}
-            \multicolumn{2}{|c|}{}                                              & \onlineClassifierComparisonRf                                             & \valid                                                   & \valid & 20       & \warn   & \cross & -                \\
-            \multicolumn{2}{|c|}{}                                              & \kmeansRf                                                                 & \valid                                                   & \valid & \s{52}   & \valid  & \cross & \s{-}            \\
-            \multicolumn{2}{|c|}{}                                              & \covarianceRf                                                             & \valid                                                   & \cross & 48       & \warn   & \cross & -                \\
-            \multicolumn{2}{|c|}{}                                              & \decisionRf                                                               & \valid                                                   & \valid & \s{50}   & \valid  & \valid & \s{50}           \\
-            \multicolumn{2}{|c|}{}                                              & \digitsRf                                                                 & \valid                                                   & \valid & 52       & \warn   & \cross & 52               \\
-            \multicolumn{2}{|c|}{}                                              & \faceRf                                                                   & \cross                                                   & \valid & \s{-}    & \warn   & \cross & \s{-}            \\
-            \multicolumn{2}{|c|}{}                                              & \penaltyRf                                                                & \valid                                                   & \valid & -        & \valid  & \valid & -                \\
-            \multicolumn{2}{|c|}{}                                              & \lassoRf                                                                  & \valid                                                   & \valid & \s{48}   & \warn   & \cross & \s{47}           \\
-            \multicolumn{2}{|c|}{}                                              & \hyperplaneRf                                                             & \valid                                                   & \valid & 3        & \valid  & \cross & -                \\
-            \multicolumn{2}{|c|}{}                                              & \mnistRf                                                                  & \valid                                                   & \valid & \s{43}   & \warn   & \valid & \s{-}            \\
-            \multicolumn{2}{|c|}{}                                              & \multitaskRf                                                              & \valid                                                   & \valid & 50       & \warn   & \valid & 48               \\
-            \multicolumn{2}{|c|}{}                                              & \ompRf                                                                    & \valid                                                   & \valid & \s{52}   & \valid  & \valid & \s{52}           \\
-            \multicolumn{2}{|c|}{}                                              & \pcaRf                                                                    & \valid                                                   & \valid & 48       & \valid  & \valid & 48               \\
-            \cline{3-9}
-            \multicolumn{2}{|c|}{}                                              & \robustRf                                                                 & \valid                                                   & \valid & \s{50}   & \warn   & \cross & \s{48}           \\
-            \multicolumn{2}{|c|}{}                                              & | Linear                                                                  & \na                                                      & \na    & 48       & \na     & \na    & 46               \\
-            \multicolumn{2}{|c|}{}                                              & | RANSAC                                                                  & \na                                                      & \na    & \s{50}   & \na     & \na    & \s{48}           \\
-            \cline{3-9}
-            \multicolumn{2}{|c|}{}                                              & \toyRf                                                                    & \valid                                                   & \valid & 35       & \warn   & \cross & -                \\
-            \cline{3-9}
-            \multicolumn{2}{|c|}{}                                              & \svmRf                                                                    & \valid                                                   & \valid & \s{43.5} & \valid  & \cross & \s{-}            \\
-            \multicolumn{2}{|c|}{}                                              & | Non-weighted                                                            & \na                                                      & \na    & 43       & \na     & \na    & -                \\
-            \multicolumn{2}{|c|}{}                                              & | Weighted                                                                & \na                                                      & \na    & \s{44}   & \na     & \na    & \s{-}            \\
-            \cline{3-9}
-            \multicolumn{2}{|c|}{}                                              & \tomographyRf                                                             & \valid                                                   & \cross & -        & \warn   & \cross & -                \\
-            \multicolumn{2}{|c|}{}                                              & \weightedRf                                                               & \valid                                                   & \valid & \s{44}   & \valid  & \cross & \s{-}            \\
-            \hline
-        \end{tabular}
-    \end{subfigure}
-    \caption{\pytracer execution summary on SciPy and Scikit-learn examples.
-        % \tristan{Replace FFT with SciPy FFT, Interpolation with SciPy Interpolation and Optimization with SciPy Optimization, or add a SciPy header to these rows.} \tristan{Nitpick: you could add a color scheme to sigbits (for instance shades of blue), to make the column more easily readable.} \\
-        \emph{trace}: outcome of \pytracer tracing, \emph{parse}: outcome of \pytracer trace parsing and aggregation, \emph{result}: precision for main outputs in significant bits.
-\valid: successful run, \warn: error from invalid noise injection, \cross: numerical error or divergent traces.
-\textit{nan} stands for (\texttt{Not-A-Number}).
-Example names are linked to their source code.}
-    \label{tab:pytracer_results_summary}
-\end{table*}
-
-\subsection{Effect of MCA modes}
-\label{sec:impact_mca_modes}
+significant bits. We note that only one example failed due to a
+numerical error (\texttt{face\_recognition}
+\remove{for RR and \texttt{Bayesian Ridge Regression} for full MCA}).
+
+\noindent \remove{\textbf{3.2 Effect of MCA modes}}
+
+\remove{
     Random Rounding perturbs only the result of a floating-point operation while
@@
     preserves exact operations --- operations where the result can be exactly
-represented at the virtual precision --- while Full MCA does not.
-
-\pytracer can only aggregate traces obtained from the same control flow path. In
+    represented at the virtual precision --- while Full MCA does not.}
+
+\remove{\pytracer can only aggregate traces obtained from the same control flow path. In
     particular, program branches triggered by an unstable floating-point comparison
@@
     Those code regions should not be perturbed by MCA since the injected noise does
-not make sense.
-
-\begin{listing}
-    \begin{lstlisting}[language=C,style=customC,numbers=left, firstnumber=3163, mathescape=true]
-/* NUMPY_API Arange, */
-NPY_NO_EXPORT PyObject *
-PyArray_Arange(double start, double stop, double step, int type_num) {
-    npy_intp length; 
-    PyArrayObject *range; $\lstsetnumber{\ldots}$
-    ...$\lstresetnumber\setcounter{lstnumber}{3173}$
-    double delta, tmp_len; $\lstsetnumber{\ldots}$
-    ...$\lstresetnumber\setcounter{lstnumber}{3176}$
-    delta = stop - start; 
-    tmp_len = delta/step; $\lstsetnumber{\ldots}$
-    ...$\lstresetnumber\setcounter{lstnumber}{3189}$
-        length = _arange_safe_ceil_to_intp(tmp_len); $\lstsetnumber{\ldots}$
-    ...$\lstresetnumber\setcounter{lstnumber}{3201}$
-    range = (PyArrayObject *)PyArray_New(&PyArray_Type, 1, &length, type_num, NULL, NULL, 0, 0, NULL);
-    \end{lstlisting}
-    \caption{Source code of the \texttt{PyArray\_Range} Cython function called by NumPy function \texttt{linspace} to create an array of equally-spaced elements.
-The temporary array size assigned in line 3178 is stored as a floating-point value and is therefore perturbed in Full MCA mode, leading to differences amplified by the use of ceil rounding at line 3190 and resulting in different array sizes across MCA-perturbed executions.
-See also Table~\ref{tab:mca_result_linspace}.}
-    \label{fig:pyarray_range_code}
-
-\end{listing}
-
-\begin{table}[t]
-    \centering
-    % \begin{tabular}{ccccccc}
-    %     \thickhline
-    %     \textbf{Mode} & \textbf{start} & \textbf{stop} & \textbf{step} & \textbf{delta}                & \textbf{tmp\_len} & \textbf{ceil(tmp\_len)} \\
-    %     \hline
-    %     Exact         & 0              & 600           & 1             & 600                           & 600               & 600                     \\
-    %     RR            & 0              & 600           & 1             & 600 $\pm$ 0.0                 & 600 $\pm$ 0.0     & 600 $\pm$ 0.0           \\
-    %     MCA           & 0              & 600           & 1             & 599.9999999999999 $\pm$ 8e-14 & 600.0 $\pm$ 8e-14 & 600.01 $\pm$ 0.0995     \\
-    %     \thickhline        
-    % \end{tabular}
-    \begin{tabular}{l|ccc}
-        \hline                                                   
-        \textbf{Mode}           & Exact & RR            & MCA                   \\
-        \hline
-        \texttt{start}          & 0     & 0             & 0                     \\
-        \texttt{stop}           & 600   & 600           & 600                   \\
-        \texttt{step}           & 1     & 1             & 1                     \\ 
-        \texttt{delta}          & 600   & 600 $\pm$ 0.0 & 599.9...9 $\pm$ 8e-14 \\
-        \texttt{tmp\_len}       & 600   & 600 $\pm$ 0.0 & 600.0 $\pm$ 8e-14     \\
-        \texttt{ceil(tmp\_len)} & 600   & 600 $\pm$ 0.0 & 600.01 $\pm$ 0.0995   \\
-        \thickhline        
-    \end{tabular}
-    \caption{Results obtained through lines 3177-3190 in Listing~\ref{fig:pyarray_range_code}.
-In contrast with RR, Full MCA does not preserve exact operations which leads to an array length oscillating between 600 and 601.}
-    \label{tab:mca_result_linspace}
-\end{table}
-
-\subsection{SciPy}
-\label{sec:scipy_tests}
-
-We tested \pytracer on SciPy examples provided in the tutorial website section.
-SciPy is organized in several libraries targeting specific computing domains. We
-focused on \texttt{fftpack} (Fast Fourier Transform routines),
-\texttt{interpolate} (interpolation and smoothing splines), and
-\texttt{optimize} (Optimization and root-finding routines).
-
-\subsubsection{FFT}
-
-This package has three examples : \texttt{discrete\_cosine\_transform},
-\texttt{fft\_1D}, and \texttt{fft\_2D}. All computations are done in double
-precision. The results for \texttt{discrete\_cosine\_transform},\texttt{fft\_1D}
-and  \texttt{fft\_2D} show precise numerical results with 48 significant bits on
-average. We observe that the FFT computation is stable to noisy inputs.
-Figures~\ref{fig:fft1D_inputs} (inputs) and~\ref{fig:fft1D_outputs} (outputs)
-show the mean and standard deviation of the MCA samples. The three columns
-correspond to the FFT computations of: 
-\begin{enumerate}
-    \item $z_1 = \sin(50 . 2\pi . x_i) + \dfrac{1}{2} \sin(80 . 2\pi . x_i),\; x_i = \frac{i}{600},\; i \in [0,600]$
-    \item $\mathrm{blackman}(400) \times z_1$
-    \item $ z_2= e^{50 . i 2\pi . x_i} + \dfrac{1}{2} e^{-80 . i2\pi .x_i },\; x_i = \frac{i}{800},\; i \in [0,400] $
-\end{enumerate}
-
-\add{The} top row in Figures~\ref{fig:fft1D_inputs} and~\ref{fig:fft1D_outputs} show the
-input mean value while the bottom row shows the standard deviation. The points
-with low magnitude in Figure~\ref{fig:fft1D_inputs} correspond to inputs near 0
-when the input of $\sin$ or $\exp$ is close to $k\pi$, $k \in \mathbb{Z}$.
-Indeed, since MCA introduces a slight noise, the result is not exactly 0. We can
-see in Figure~\ref{fig:fft1D_inputs} that the maximal noise introduced by MCA on
-the inputs is in the order of $10^{-14}$, two orders of magnitude higher than
-the $ulp \simeq 10^-16$ for double precision. This slight noise introduced can
-be interpreted as white noise on the input signal. We can see on the bottom row
-of Figure~\ref{fig:fft1D_outputs} that the frequency noise is of the same order
-of of magnitude as the input noise, which is expected. The two peaks at x=38 and
-x=562 corresponds to the actual frequencies of the input signal.
+    not make sense.}
+
+\subsection{\pytracer supports the visualization of compound data type}
+
+\add{PyTracer supports native floating point formats as well as compound data type,
+    such as complex floating point values, N-dimensional arrays and arbitrary Python
+    classes. For the Python classes, PyTracer recursively parses the class attributes to
+    extract scalar and N-dimensional arrays floating-points values.}
+
+Figures~\ref{fig:fft1D_inputs} and~\ref{fig:fft1D_outputs} \add{show the
+    visualization of the \texttt{fft\_1D} inputs and outputs values. Results are
+    complex value encoded on double precision. PyTracer allows visualizing the
+    numerical precision of real (blue points) and imaginary (orange points) parts.}
+\add{The} top row in Figures~\ref{fig:fft1D_inputs} and~\ref{fig:fft1D_outputs}
+show the input mean value while the bottom row shows the standard deviation. The
+points with low magnitude in Figure~\ref{fig:fft1D_inputs} correspond to inputs
+near 0 when the input of $\sin$ or $\exp$ is close to $k\pi$, $k \in
+    \mathbb{Z}$. Indeed, since MCA introduces a slight noise, the result is not
+exactly 0. We can see in Figure~\ref{fig:fft1D_inputs} that the maximal noise
+introduced by MCA on the inputs is in the order of $10^{-14}$, two orders of
+magnitude higher than the $ulp \simeq 10^-16$ for double precision. This slight
+noise introduced can be interpreted as white noise on the input signal. We can
+see on the bottom row of Figure~\ref{fig:fft1D_outputs} that the frequency noise
+is of the same order of of magnitude as the input noise, which is expected. The
+two peaks at x=38 and x=562 corresponds to the actual frequencies of the input
+signal.
+
+Figure~\ref{fig:spline2d_rr} \add{shows the results of the spline evaluation with
+    \texttt{bisplev} from the \texttt{spline\_2D} example. It computes the 2D spline
+    interpolation for function $z=(x+y)e^{-6(x^2+y^2)}$, with $(x,y) \in
+        [-1,1]\times[-1,1]$. The result is a 2D-array that is natively supported by
+    PyTracer. We observe a significant loss of precision in places, which follows
+    an interesting pattern that could be further investigated.}
 
@@
     \includegraphics[width=\linewidth]{figure/FFT/fft_x.pdf}
-    \caption{Absolute value of the mean and standard deviation values for
-        fft 1D inputs within RR mode (log scale). The real part is shown in blue and the imaginary part in orange.}
+    \caption{Absolute value of the mean and standard deviation values for fft 1D
+        inputs within RR mode (log scale). The real part is shown in blue and
+        the imaginary part in orange.}
     \label{fig:fft1D_inputs}
@@
 
-\subsection{Interpolation}
-
-This package has five examples: \texttt{interpolation\_1D},
-\texttt{multivariate\_data}, \texttt{bspline}, \texttt{spline\_1D} and
-\texttt{spline\_2D}.
-
-\texttt{interpolation\_1D} interpolates function $f(x)=\cos(\frac{-x^2}{9})$
-with 11 points $x\in[0,10]$. For the five interpolation methods tested (linear,
-cubic, nearest, previous, next), the solution found is precise, up to 51 bits
-out of the 53 available.
-
-\texttt{multivariate\_data} interpolates the grid $f(x,y)=x(1-x)\cos(4\pi.x)
-    \sin(4\pi.y^2)^2$ with $(x,y) \in [0,1] \times [0,1]$. It samples 1,000 points
-for each coordinate and uses three interpolation methods: nearest, linear and
-cubic. Our results show a precision of 51 bits on average for the three methods.
-
-\texttt{bspline} compares two edge filters: \texttt{bisplev} evaluates a
-bivariate B-spline and its derivative whereas \texttt{convolved2d} convolves two
-2-dimensional arrays. Figure~\ref{fig:bspline_rr} shows the significant bits,
-mean, and standard deviation maps for the two methods as well as the input image
-(Fig.~\ref{fig:bspline_original_image}). The middle row shows \texttt{sepfir2d}
-results and the bottom row shows \texttt{convol2d} results. Both methods exhibit
-similar precision, with 11 significant bits on average. Standard deviations maps
-on Figures~\ref{fig:bspline_bisplev_std} and~\ref{fig:bspline_convol2d_std} show
-that regions with low spatial frequencies correspond to regions with low
-standard deviation, similar to the FFT results. The SciPy tutorial mentions that
-\texttt{bisplev} is faster than \texttt{convol2d}. The comparable numerical
-precision observed in our experiments reinforce the use of \texttt{bisplev} over
-\texttt{convol2d} in this example.
-
-\texttt{spline\_1D} computes the 1D spline interpolation for $f(x)=\sin(x)$ on
-points $x=\frac{2\pi k}{8}, k \in [0, 10]$. The spline interpolation uses
-\texttt{splrep} to build the spline representation and \texttt{splrev} to
-evaluate the spline at any point. It also computes the integral by using
-\texttt{splint} and the root finder \texttt{sproot}. Although the traces
-diverge, we can analyze the partial aggregation for the \texttt{splrep},
-\texttt{splev} and \texttt{splint}. The three functions show results with an
-average precision of 51 bits with RR mode.
-
-\texttt{spline\_2D} computes the 2D spline interpolation for function
-$z=(x+y)e^{-6(x^2+y^2)}$, with $(x,y) \in [-1,1]\times[-1,1]$ and a sampling of
-21 points for each coordinate. \texttt{bisplrep} builds the spline
-representation with the $21 \times 21$ points of $z$ over 71 grid sampling
-points for $(x,y)$. Figure~\ref{fig:spline2d_rr} shows the results of the spline
-evaluation with \texttt{bisplev}.  We observe a significant loss of precision in
-places, which follows an interesting pattern that could be further investigated.
-
-\begin{figure}
+\begin{figure*}
     \centering
     \begin{subfigure}{.3\linewidth}
-        \includegraphics[width=\linewidth]{figure/bspline/original_image.pdf}
-        \caption{Original image.}
-        \label{fig:bspline_original_image}
-    \end{subfigure}\\
-    \begin{subfigure}{0.3\linewidth}
-        \includegraphics[width=\linewidth]{figure/bspline/bspline_sig.pdf}
-        \caption{\centering\texttt{sepfir2d} significant bits}
-        \label{fig:bspline_bisplev_sig}
-    \end{subfigure}
-    \begin{subfigure}{0.3\linewidth}
-        \includegraphics[width=\linewidth]{figure/bspline/bspline_mean_log.pdf}
-        \caption{\centering\texttt{sepfir2d} mean (log)}
-        \label{fig:bspline_bisplev_mean}
-    \end{subfigure}
-    \begin{subfigure}{0.3\linewidth}
-        \includegraphics[width=\linewidth]{figure/bspline/bspline_std_log.pdf}
-        \caption{\centering\texttt{sepfir2d} standard deviation (log)}
-        \label{fig:bspline_bisplev_std}
-    \end{subfigure}
-    \begin{subfigure}{0.3\linewidth}
-        \includegraphics[width=\linewidth]{figure/bspline/convol2d_sig.pdf}
-        \caption{\centering\texttt{convol2d} significant bits}
-        \label{fig:bspline_convol2d_sig}
-    \end{subfigure}
-    \begin{subfigure}{0.3\linewidth}
-        \includegraphics[width=\linewidth]{figure/bspline/convol2d_mean_log.pdf}
-        \caption{\centering\texttt{convol2d} mean (log)}
-        \label{fig:bspline_convol2d_mean}
-    \end{subfigure}
-    \begin{subfigure}{0.3\linewidth}
-        \includegraphics[width=\linewidth]{figure/bspline/convol2d_std_log.pdf}
-        \caption{\centering\texttt{convol2d} standard deviation (log)}
-        \label{fig:bspline_convol2d_std}
-    \end{subfigure}
-    \caption{\texttt{bspline} results within RR mode. \texttt{sepfir2d} and
-        \texttt{convol2d} have a similar precision.
-    }
-    \label{fig:bspline_rr}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \begin{subfigure}{.3\textwidth}
         \centering
@@
     \end{subfigure}
-    \begin{subfigure}{.3\textwidth}
+    \begin{subfigure}{.3\linewidth}
         \centering
@@
     \end{subfigure}
-    \caption{2D Spline interpolation results. Figure~\ref{fig:bisplev_mean} shows the mean result
-        of the 2D-spline interpolation. Figures~\ref{fig:bisplev_mean_log} and~\ref{fig:bisplev_std_log}
-        show respectively in the logarithmic scale the absolute mean value and the standard deviation 
-        of the 5 samples run within RR mode. 
-        % \tristan{any reason why you are showing the ieee result?} \tristan{can you use the same color maps as in figure 8?}
+    \caption{2D Spline interpolation results. Figure~\ref{fig:bisplev_mean}
+        shows the mean result of the 2D-spline interpolation.
+        Figures~\ref{fig:bisplev_mean_log} and~\ref{fig:bisplev_std_log} show
+        respectively in the logarithmic scale the absolute mean value and the
+        standard deviation of the 5 samples run within RR mode. 
     }
     \label{fig:spline2d_rr}
-\end{figure}
-
-\subsubsection{Optimization}
-
-This package has eleven examples. Seven examples involve the same optimization
-problem solved with and without constraints using different methods. One example
-optimizes a chemical problem under constraints. The last three examples solve a
-different problem each.
-
-\paragraph{Unconstrained minimization of multivariate scalar functions}
-Four Quasi-Newton-Raphson methods minimize function $f$ by using Newton's step:
-$x_{k+1} = x_{k} - B^{-1}(x_k)\nabla f(x_k)$, where $\nabla$ and $B$ are the
-gradient and the approximation of the Hessian matrix of $f$. The
-\texttt{Broyden-Fletcher-Goldfarb-Shanno}~\cite{BFGS} (BFGS) and
-\texttt{Newton-Conjugate-Gradient}~\cite{nocedal2006numerical} (NCG) are line
-search methods that approximate $H$ by adding two symmetric rank-one matrices
-and by using the Conjugate-Gradient method. The \texttt{Trust-Region Truncated
-    Generalized Lanczos / Conjugate Gradient}~\cite{gould1999solving} (TR-Krylov),
-\texttt{Trust-Region Newton-Conjugate-Gradient} (TR-NCG), and
-\texttt{Trust-Region Nearly Exact}~\cite{nocedal2006numerical} (TR-Exact) are
-trust-region methods approximating $H$ by solving the trust-region subproblem
-restricted to a truncated Krylov subspace and by solving nonlinear equations for
-each quadratic subproblem. In addition, the
-\texttt{Nelder-Mead}~\cite{singer2009nelder} simplex-based method iteratively
-transforms a simplex until its vertices are getting closer to a local minima of
-the function. All methods are applied to the Rosenbrock function.
-
-\paragraph{Constrained minimization of multivariate scalar functions}
-Two optimizers solve an optimization problem by taking into account constraints.
-The \texttt{Sequential Least SQuares Programming} uses the
-SLSQP~\cite{kraft1988software} method to optimize the Rosenbrock function. The
-\texttt{Least-squares minimization} uses the Trust Region Reflective
-algorithm~\cite{li1993centering} to solve a fitting problem from an enzymatic
-reaction.
-
-The SLSQP and unconstrained minimization methods minimize the
-\textbf{Rosenbrock} function of $N$ variables that reaches its minimum (0) when
-$x_i=1,\; \forall i \leq N-1$:
-$f(x) = \sum_{i=1}^{N-1} 100(x_{i+1}-x^2_i)^2 + (1-x_i)^2$.
-Figure~\ref{fig:unconstrained_optimization} shows the number of significant bits
-of the solution for the different methods used. The $(p)$ notation for the NCG,
-Trust-Krylov, and Trust-NCG methods in the legend refers to the variant where
-the Hessian matrix is replaced by a function computing the matrix-vector product
-of the Hessian and an arbitrary vector, to save memory and time. All the methods
-have a good precision ranging from 43 to 53 significant bits. The Nelder-Mead
-method is the least precise one with $\simeq$ 43 significant bits on average,
-while the Trust-Region-Newton-CG is the most precise one with $\simeq$ 53
-significant bits, the highest precision achievable in double precision. The
-remaining methods have a similar precision.
-
-The SLSQP also minimizes the Rosenbrock function with the following constraint:
-$x_0$ + $2x_1$ $\leq$ 1 
-$x_0^2$ + $x_1$ $\leq$ 1 
-$x_0^2$ - $x_1$ $\leq$ 1 
-$2x_0$ + $x_1$ = 1 
-0 $\leq$ $x_0$ $\leq$ 1 
--0.5 $\leq$ $x_1$ $\leq$ 2. 
-% \begin{eqnarray*}
-%     x_0 + 2x_1 \leq 1 \\
-%     x_0^2 + x_1 \leq 1 \\
-%     x_0^2 - x_1 \leq 1 \\
-%     2x_0 + x_1 = 1 \\
-%     0 \leq x_0 \leq 1 \\
-%     -0.5 \leq x_1 \leq 2 
-% \end{eqnarray*}
-The problem has a unique solution $[x_0, x_1] = [0.4149, 0.1701]$. Results
-obtained with RR show a precision of 47 and 44 significant bits for the first
-and the second solution. %\tristan{which method is tested?}.
-
-The \texttt{least-square minimization} example solves a fitting problem from an enzymatic reaction~\cite{kowalik1968analysis} with 11 residuals defined as:
-\begin{eqnarray*}
-    f_i(x) &=& \frac{x_0(u_i^2 + u_ix_1)}{u_i^2 + u_ix_2+x_3}-y_i,\; i=0,...,10 \\
-    &0& \leq x_j \leq 100,\; j=0,..,3
-\end{eqnarray*}
-where where $y_i$ are measurement values, $u_i$ are values of the independent
-variable, and $x_i$ the unknown. Results within RR show a precision of 51, 46,
-47, and 48 significant bits for each component of the solution
-respectively.% \tristan{which solver is used?}.
-
-\paragraph{Root finding}
-% We tested three root finder algorithms with one for small problems using the hybrid Powell and Levenberg-Marquardt methods  (\texttt{root\_finding}) and two for large problems using a Krylov approximation for the inverse Jacobian with and without the help of a preconditioner (\texttt{root\_finding\_large\_preconditionned} and \texttt{root\_finding\_large}).
-
-The \texttt{root\_*} examples use three algorithms to find the root of
-non-linear equations. \texttt{root\_finding} uses the hybrid Powell method to
-solve a single-variable transcendental equation and the Levenberg-Marquardt
-method for a set of non-linear equations. \texttt{root\_finding\_large} and
-\texttt{root\_finding\_large\_preconditioned} examples use the Krylov method to
-approximate the inverse Jac\add{o}bian with and without the help of a preconditioner.
-They solve an integrodifferential equation on a square $(x,y) \in [0,1] \times
-    [0,1]$, $P(x,1)=1$, and $P=0$ elsewhere on the boundary. The function $P$ is
-discretized with a Cartesian grid $P_{n,n}=P(nh,nh)$, with $n=75$, and its
-derivatives are approximated by $\partial_x^2P(x,y) \simeq (P(x+h,y) - 2P(x,y) +
-    P(x-h,y))/h^2$.
-
-% the two following equations: $x + 2\cos(x) = 0$ and 
-% the set $x_0\cos(x_1)=4$; $x_0x_1-x_1 = 5$ while the 
-% \texttt{root\_finding\_large} and \texttt{root\_finding\_large\_preconditioned} tests 
-% solve the equation:
-% \[
-%     (\partial_x^2 + \partial_y^2)P + 5 \left(\int_0^1 \int_0^1 cosh(P)\, dx dy \right)^2 = 0
-% \]
-
-All the examples diverge even within RR, which is not surprising since
-root-finding methods can easily take a few extra steps to find the root
-depending on the starting point. Nevertheless, for the
-\texttt{root\_finding\_large} example, 3 traces among the 5 samples can be
-merged for both RR and MCA modes. Figure~\ref{fig:root_finding_large} shows the
-mean and standard deviation of the result for these 3 samples. We can see that a
-similar solution was found for RR and Full MCA. Full MCA leads to a lower
-precision than RR although both standard deviation maps remain in the same order
-of magnitude. Finally, it is interesting to note the impact of preconditioning
-on the result numerical quality: as Table~\ref{tab:pytracer_results_summary}
-shows, the precision doubles between \texttt{root\_finding\_large} and
-\texttt{root\_finding\_large\_preconditioned}.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figure/unconstrained_optimization_comparison.pdf}
-    \caption{Comparison of results precision for different optimization solvers within RR mode.}
-    \label{fig:unconstrained_optimization}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \begin{subfigure}{0.45\linewidth}
-        \includegraphics[width=\linewidth]{figure/root_finding/solution_mean_RR.pdf}
-        \caption{Mean solution (RR)}
-        \label{fig:mean_solution_rr}
-    \end{subfigure}
-    \begin{subfigure}{0.45\linewidth}
-        \includegraphics[width=\linewidth]{figure/root_finding/solution_std_RR.pdf}
-        \caption{Standard deviation solution (RR)}
-        \label{fig:stdev_rr}
-    \end{subfigure}
-
-    \begin{subfigure}{0.45\linewidth}
-        \includegraphics[width=\linewidth]{figure/root_finding/solution_mean_MCA.pdf}
-        \caption{Mean solution (Full MCA)}
-        \label{fig:mean_solution_mca}
-    \end{subfigure}
-    \begin{subfigure}{0.45\linewidth}
-        \includegraphics[width=\linewidth]{figure/root_finding/solution_std_MCA.pdf}
-        \caption{Standard deviation (Full MCA)}
-        \label{fig:stdev_mca}
-    \end{subfigure}
-    \caption{Solution of \texttt{root\_finding\_large} example.
-        The standard deviation has two maximum for both RR and Full MCA modes. The standard deviation remains lower than
-        the stopping criterion threshold fixed at $6.10^{-6}$. }
-    \label{fig:root_finding_large}
-\end{figure}
-
-% \begin{itemize}
-% \item broyden: RR 47 bits solution / MCA divergence 
-% \item global\_optimization: RR divergence / MCA issues
-% \item sqlsp: RR 46 bits solution / MCA 46 bits solution
-% \item least\_square\_minimization : RR 48 bits solution / MCA index issue
-% \item nelder\_mean\_simplex : RR 43 bits solution / MCA stable
-% \item newton\_conjugate\_gradient: RR 48 bits solution / MCA divergence
-% \item root\_finding\_large\_preconditionned : RR divergence / MCA divergence 3/5 converged
-% \item root\_finding\_large : RR divergence / MCA divergence (fgmres very low!) 3/5 converged
-% \item trust\_region\_exact : RR 47 bit solution / RR 45 bit solution
-% \item trust\_region\_truncated\_generalized\_lanczos : RR 48 bits solution / MCA 46 bits solution
-% \end{itemize}
-
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/nelder_mead/timeline_sig.png}
-%     \caption{Nelder-Mead: average of number of significant bits over time. 
-%     Solver ends when accuracy is reaching the tolerance.
-%     }
-%     \label{fig:my_label}
-% \end{figure}
-
-\subsection{Scikit learn}
-\label{sec:sklearn_tests}
-
-Scikit-learn offers a well-supplied and documented list of examples that
-facilitates its use with Pytracer. Among the several available examples, we
-choose the following representative set listed in
-Table~\ref{tab:pytracer_results_summary}. The following paragraphs focus on the
-most interesting stability results observed across all experiments.
-% \tristan{Shall we just refer to Table 4 and remove this lengthy list? You could add the links in the table and mention in the table caption that the tests are linked to their source code}:
-
-% \subsubsection{Classifier comparisions}
-
-% This test compares the performance of 6 online solvers on the hand-written digits dataset.
-% These 6 solvers are:
-% \begin{itemize}
-%     \item Stochastic Gradient Descent 
-%     \item Averaged Stochastic Gradient Decent
-%     \item Perceptron
-%     \item Passive-Aggressive I \& II
-%     \item SAG: Minimizing Finite Sums with the Stochastic Average Gradient
-% \end{itemize}
-
-% Each solver is trained and predicts 20 times on 6 different training size ratio.
-% Figure~\ref{fig:classifier_comparisons_general} shows the all functions
-% traced by Pytracer over time. We can see the estimated number of significant digits varies a lot between 
-% values from 1 to 80 bits. Figure~\ref{fig:classifier_comparisons_mean_predictions} shows 
-% the average prediction score for each classifiers. The yellow points 
-% represent the average correct prediction score for one round and one classifier (line. 48) while blue points
-% tshows average predictions over the 20 rounds (line. 49).
-% We can see that precision is pretty low with an average solution below 10 significant bits, with 
-% an exception for values between the 24k and 32k invocation that correspond to the Perceptron
-% classifier. Indeed, this classifier is pretty stable with an average number of significant digits around 52 bits.
-
-% \begin{figure}
-%     \begin{lstlisting}[language=Python,style=customPython,numbers=left, firstnumber=19]
-% heldout = [0.95, 0.90, 0.75, 0.50, 0.01]
-% rounds = 20
-% X, y = datasets.load_digits(return_X_y=True)
-
-% classifiers = [
-%     ("SGD", SGDClassifier(max_iter=100)),
-%     ("ASGD", SGDClassifier(average=True)),
-%     ("Perceptron", Perceptron()),
-%     ("Passive-Aggressive I", PassiveAggressiveClassifier(loss='hinge',C=1.0, tol=1e-4)),
-%     ("Passive-Aggressive II", PassiveAggressiveClassifier(loss='squared_hinge',C=1.0, tol=1e-4)),
-%     ("SAG", LogisticRegression(solver='sag', tol=1e-1, C=1.e4 / X.shape[0]))
-% ]
-
-% xx = 1. - np.array(heldout)
-
-% for name, clf in classifiers:
-%     print("training %s" % name)
-%     rng = np.random.RandomState(42)
-%     yy = []
-%     for i in heldout:
-%         yy_ = []
-%         for r in range(rounds):
-%             X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=i, random_state=rng)
-%             clf.fit(X_train, y_train)
-%             y_pred = clf.predict(X_test)
-%             yy_.append(1 - np.mean(y_pred == y_test))
-%         yy.append(np.mean(yy_))
-%     plt.plot(xx, yy, label=name)
-%     \end{lstlisting}
-%     \label{fig:wrapper_code}
-% \caption{}
-% \end{figure}
-
-% \begin{figure}
-%     \centering
-%     \caption{Caption}
-%     \includegraphics[width=\linewidth]{figure/classifier_comparisons/SAG_predicition_s.png}
-%     \caption{Number of significant digits (General view).}
-%     \label{fig:classifier_comparisons_general}
-% \end{figure}
-
-% \begin{figure}
-%     \centering
-%     \caption{Caption}
-%     \includegraphics[width=\linewidth]{figure/classifier_comparisons/zoom_SAG_fit_coef_s.png}
-%     \caption{Number of significant digits (General view).}
-%     \label{fig:classifier_comparisons_general}
-% \end{figure}
-
-% \subsubsection{Adaboost}
-
-% \tristan{For all the paragraphs below, add a sentence to describe the results as you did for scipy.
-If you have nothing more to say than what is reported in Table 4, then remove the paragraphs describing the algorithms and just refer to the sklearn doc linked from the table.
-If you have interesting things to discuss only for some examples, mention in the section intro that the text focuses on the most interesting stability patterns observed across all experiments.}
-
-% \paragraph{Adaboost}
-% This test compares a decision tree boosted with 300 estimators using the AdaBoost.R2~\cite{drucker1997improving} algorithm with
-% a single decision tree regressor on a 1D sinusoidal dataset with a small amount of Gaussian noise and a depth fixed at 4. 
-% The example shows that as the number of boosts is increased the regressor can fit more detail.
-
-% RR Good 48 \\
-% MCA: arange issue /  bootstrap\_idx = random\_state.choice(a=np.arange(\_num\_samples(X)), size=\_num\_samples(X), replace=True, p=sample\_weight) / len(a) != len(p)
-
-% \paragraph{Online classifier comparison}
-% This example compares how the following online solvers perform on the hand-written digits dataset:
-% Stochastic Gradient Descent (SGD) with maximum iterations fixed to 100, 
-% Averaged Stochastic Gradient Descent (ASGD),
-% Perceptron, Passive-Aggressive I with the hinge loss function, tolerance 
-% and regularization fixed at $10^{-4}$ and $1$,
-% Passive-Aggressive II with the squared hinge loss function, tolerance 
-% and regularization fixed at $10^{-4}$ and $1$, and Stochastic Average Gradient (SAG)
-% with the tolerance and regularization fixed at $10^{-4}$ and $5.10^{-8}$.
-
-% RR: stable 48 bits. \\
-% MCA: Index issue
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\linewidth]{figure/BRR/call_path.pdf}
-    \caption{Call paths of the Bayesian Ridge Regression (BRR) and
-        Ordinary Least Square (OLS) function. Color represents the calling library:
-        orange for scikit-learn, blue for SciPy and yellow for LAPACK.
-        Dashed color represents the original path in red and the alternative one in green.
-        Figure~\ref{fig:brr_svd_sig} shows the original method  leads to numerical instabilities while the alternative one converges.
-    }
-    \label{fig:call_path_brr}
-\end{figure}
-
-\paragraph{Bayesian Ridge Regression}
-
-This example compares a Bayesian Ridge Regression (BRR) to the Ordinary Least
-Squares (OLS) estimator on a synthetic dataset and for one-dimensional
-regression using polynomial feature expansion. Although the example does not
-raise a runtime error, the regression coefficients computed from the fitting are
-non-significant. \pytracer traces reveal that the SVD solver used is the root
-cause for this error. Figure~\ref{fig:call_path_brr} shows the two call paths
-for BRR and OLS. The LAPACK library has two main methods for computing the SVD:
-\texttt{gesdd} and \texttt{gesvd}. The former uses a Divide \& Conquer approach,
-while the latter uses a QR decomposition. While both methods are expected to
-have the same accuracy~\cite{nakatsukasa2013stable},
-Figure~\ref{fig:brr_svd_sig} shows that \texttt{gesdd} is totally imprecise,
-with an average number of significant digits of 0 for BRR and even
-\texttt{Not-a-Number} (\texttt{NaN}) values for OLS. On the same figure, we can
-see that using the \texttt{gesvd} (\remove{dgelsd} \add{dgelss}) method instead of the \texttt{gesdd}
-(\remove{dgelss} \add{dgelsd}) one, the SVD converges for RR and Full MCA, with a number of
-significant bits of 44 on average. This observation supports the on-going
-discussion among LAPACK developers on the instability of \texttt{gesdd} (see
-\href{https://github.com/Reference-LAPACK/lapack/issues/316}{github.com/Reference-LAPACK/lapack/issues/316}).
-
-% \tristan{t'es sur que c'est pas l'inverse? Sur la fig 9 on voit que dgelsd n'est pas precise du tout, ca suggere qu'elle utiliserait gesdd}. 
-% \tristan{ce paragraph est difficile a lire (mais neanmoins super interessant !).
-tu devrais le restructurer en expliquant (1) quelle methode utilise quel solver de quelle librairie, (2) la performance observee sur la fig 9 (tu pourais d'ailleurs ajouter le nom du solver (gesdd ou gesvd) entre parenthese dans la legende pour rendre l'explication plus claire, (3) le fait que ca confirme la discussion sur github et autres commentaires.}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figure/BRR/BRR_coefs_sig.pdf}
-    \caption{Precision of Bayesian Ridge Regression coefficients in RR mode.
-        \texttt{BRR\_*} show the \texttt{BayesianRidge} results
-        using the \texttt{gesdd} and \texttt{gesvd} methods. 
-        \texttt{OLS\_*} show the \texttt{LinearRegression} results
-        with the \texttt{dgelsd} and \texttt{dgelss} methods.
-        The Divide \& Conquer method 
-        (\texttt{gesdd} and  \texttt{dgelsd})
-        has low precision
-        for \textit{BRR} and results in \texttt{NaN} values (star points) for \textit{OLS}. By switching to the \texttt{gesvd} method, 
-        results have a precision of 42 bits on average.
-    }
-    \label{fig:brr_svd_sig}
-\end{figure}
-
-% the coefficient weights are slightly shifted toward zeros, which stabilises them.
-% As the prior on the weights is a Gaussian prior, the histogram of the estimated weights is Gaussian.
-% The estimation of the model is done by iteratively maximizing the marginal log-likelihood of the observations.
-% We also plot predictions and uncertainties for Bayesian Ridge Regression for one dimensional regression using polynomial feature expansion.
-Note the uncertainty starts going up on the right side of the plot.
-This is because these test samples are outside of the range of the training samples.
-
-% RR: solution mean 15-24 / std 20-30 \\
-% MCA: SVD did not converge
-
-% \paragraph{K-Means Clustering}
-% This test uses the K-means to cluster the IRIS dataset.
-% The plots display firstly what a K-means algorithm would yield using three clusters.
-It is then shown what the effect of a bad initialization is on the classification process: By setting n\_{init} to only 1 (default is 10), the amount of times that the algorithm will be run with different centroid seeds is reduced.
-The next plot displays what using eight clusters would deliver and finally the ground truth.
-
-% RR Very stable (labels with highest precision) \\
-% MCA: Divergence
-
-% \paragraph{Covariance estimation}
-% This example shows covariance estimation with Mahalanobis distances on Gaussian distributed data.
-
-% For Gaussian distributed data, the distance of an observation xi to the mode of the distribution can be computed using its Mahalanobis distance:
-
-% d(μ,Σ)(xi)2=(xi−μ)TΣ−1(xi−μ)
-% where μ and Σ are the location and the covariance of the underlying Gaussian distributions.
-
-% In practice, μ and Σ are replaced by some estimates.
-The standard covariance maximum likelihood estimate (MLE) is very sensitive to the presence of outliers in the data set and therefore, the downstream Mahalanobis distances also are.
-It would be better to use a robust estimator of covariance to guarantee that the estimation is resistant to “erroneous” observations in the dataset and that the calculated Mahalanobis distances accurately reflect the true organization of the observations.
-
-% The Minimum Covariance Determinant estimator (MCD) is a robust, high-breakdown point (i.e. it can be used to estimate the covariance matrix of highly contaminated datasets, up to
-
-% nsamples−nfeatures−12 outliers) estimator of covariance. The idea behind the MCD is to find
-
-% nsamples+nfeatures+12 observations whose empirical covariance has the smallest determinant, yielding a “pure” subset of observations from which to compute standards estimates of location and covariance.
-The MCD was introduced by P.J.Rousseuw in 1.
-
-% This example illustrates how the Mahalanobis distances are affected by outlying data.
-Observations drawn from a contaminating distribution are not distinguishable from the observations coming from the real, Gaussian distribution when using standard covariance MLE based Mahalanobis distances.
-Using MCD-based Mahalanobis distances, the two populations become distinguishable.
-Associated applications include outlier detection, observation ranking and clustering.
-
-% RR: Traces diverge but precision seems stable (~48bits) \\
-% Main computation is in a loop that might be take extra steps to ends. \\
-% MCA: arange issue
-
-% \paragraph{Decision Tree Regression}
-% This test uses a decision tree to fit a sine curve with added noise.
-
-% A 1D regression with decision tree.
-% The decision trees is used to fit a sine curve with addition noisy observation. As a result, it learns local linear regressions approximating the sine curve.
-% We can see that if the maximum depth of the tree (controlled by the max\_depth parameter) is set too high, the decision trees learn too fine details of the training data and learn from the noise, i.e.
-they overfit.
-
-% RR Fit ok (50bits) , missing predict \\
-% MCA Fit ok (50bits) , missing predict
-
-% \paragraph{Digits Classification}
-% This test uses a Support Vector Classifier to recognize images of hand-written
-% digits. The digits dataset consists of 8x8 pixel images of digits.
-
-% RR Very stable (highest precision) \\
-% MCA: Very stable (highest precision)
-
-\paragraph{Face Recognition}
-
+\end{figure*}
+
+\subsection{\pytracer allows visualizing numerical stability at a fine grained level}
+
+\add{We illustrate on two examples how PyTracer is effective for analyzing
+    the numerical stability at a fine grained level: Face recognition and Bayesian Ridge Regression.}
 The face recognition example uses eigenfaces (eigenvectors) and Support Vector
@@
 and then trains an SVM classifier to predict the name associated with a face.
-This example is the only one to raise an error with RR due to the
+\add{When executing within fuzzy environment, this example crashed with the following
+    Python error raised: \texttt{"SVD did not converge"}.}
+This example is the only one to raise an error due to the
 non-convergence of the Singular Value Decomposition (SVD) performed in the PCA.
-
-In this example, the PCA uses the Randomized SVD~\cite{halko2011finding} method
+The PCA uses the Randomized SVD~\cite{halko2011finding} method
 that first computes a low-rank approximation of the input matrix using a
-stochastic algorithm and then uses this approximation as input for the SVD. The
-example raises an error during the computation of the SVD. The
-\texttt{randomized\_svd} scikit-learn function uses the Divide \& Conquer SVD
-method \texttt{gesdd} mentioned previously. Replacing \texttt{gesdd} for
-\texttt{gesvd} solves the SVD convergence issue.
+stochastic algorithm and then uses this approximation as input for the SVD. 
+\add{When walking through the code with PyTracer, we see that}
+the \texttt{randomized\_svd} scikit-learn function uses the Divide \& Conquer SVD
+method \texttt{gesdd}. The LAPACK library has two main methods for computing the SVD:
+\texttt{gesdd} and \texttt{gesvd}. The former uses a Divide \& Conquer approach,
+while the latter uses a QR decomposition. While both methods are expected to
+have the same accuracy~\cite{nakatsukasa2013stable}, the Divide \& Conquer
+makes the SVD to not converge with MCA.
+
+Replacing \texttt{gesdd} for \texttt{gesvd} solves the SVD convergence issue.
+\pytracer allows to quickly visualize the new precision of the result.
 Figure~\ref{fig:randomized_svd_S} shows the precision of the eigenvalues
-computed with gesvd \add{in single precision}, which varies between 15 and 20 significant bits out of the
-24 available in single precision. The classifier metrics (precision, recall,
-F1-score, and support) are identical to the IEEE execution for all MCA samples.
+computed displayed in decreasing order with \texttt{gesvd} \add{in single precision}, 
+which varies between 15 and 20
+significant bits out of the 24 available in single precision. The classifier
+metrics (precision, recall, F1-score, and support) are identical to the IEEE
+execution for all MCA samples. \add{We can note that even with using the \texttt{gesvd},
+    the precision of the singular values (vectors) is not uniform. 
+    Indeed, we can see that the precision of the lowest singular values (vectors) decreases 
+    until reaching 0 significant bits.}
+
+The second example, compares a Bayesian Ridge Regression (BRR) to the Ordinary
+Least Squares (OLS) estimator on a synthetic dataset and for one-dimensional
+regression using polynomial feature expansion. Although the example does not
+raise a runtime error, the regression coefficients computed from the fitting are
+non-significant. \pytracer traces reveal that the SVD solver used is the root
+cause for this error. \add{Indeed, the BayesianRidge model first computes an SVD
+    before iteratively updating the coefficients until reaching the convergence
+    criterion. However, PyTracer reveals an issue in the singular values computed.}
+\add{We can see on Figure}~\ref{fig:BRR_svd} \add{that the last singular values is
+    \texttt{NaN} due to numerical error during the SVD although the remaining
+    singular values exhibit high numerical precision (between 44 and 50 bits).
+    Surprinsingly, this \texttt{NaN} value does not raise issue and is silently
+    propagated. Indeed, the stopping criterion compares that the sum of the absolute
+    differences between coefficients of two successive iterations but coefficients
+    contain \texttt{NaN} since they are computed from singular values. Hence, the
+    following condition is never met \texttt{if iter\_ != 0 and
+        np.sum(np.abs(coef\_old\_ - coef\_)) < self.tol:} since the comparison with a
+    \texttt{NaN} is always false.}
+
+\add{The OLS uses the Least Square to fit the model. PyTracer shows that the
+    coefficients fitted are \texttt{NaN} values. By looking at the callgraph, we can
+    see that the scipy calls the \texttt{lstsq} method from the
+    \texttt{scipy.linalg} package which uses the \texttt{gelsd} LAPACK function.
+    Figure}~\ref{fig:OLS_svd} \add{shows the singular values returned by the
+    \texttt{lstsq} method shows that one singular value has a \texttt{NaN} value
+    that corrupted the calculation of the coefficients. By using the \texttt{gelss},
+    PyTracer shows that the \texttt{NaN} value disapeared from the singular values
+    (fig.}~\ref{fig:OLS_svd_fixed}\add{) and thus does not contaminated the computation of
+    the coefficients that exhibit a precision of 42 bits in average. We can see that
+    the full access to all values computed by the application with PyTracer allows
+    the user to quickly identify the issue.}
 
@@
 avoid this kind of issue. Thus, \pytracer can detect instabilities that affect
-fundamental scientific computing components such as the LAPACK library.
-% The Pytracer findings can therefore be extended to many application domains.
-% % \tristan{conclusion needs to be discussed.
-Note to self: generaliser un peu la conclusion: pytracer permet de se rendre compte de problemes de stabilite dont plusieurs librairies sont dependantes.}
-
-\begin{figure}
+fundamental scientific computing components such as the LAPACK library. \add{The
+    unify view of all traces allows the user to quickly navigate through the
+    different numerical precision of variables which saves time for the developer
+    compare to the print statement debugging.}
+% The Pytracer findings can therefore be extended to many application domains. %
+% \tristan{conclusion needs to be discussed. Note to self: generaliser un peu la
+% conclusion: pytracer permet de se rendre compte de problemes de stabilite dont
+% plusieurs librairies sont dependantes.}
+
+\begin{figure*}
     \centering
@@
     \caption{Precision of the \texttt{randomized\_svd} function in the
-        \texttt{face\_recognition} example using the \texttt{gesvd} SVD method and RR.
-        Figures~\ref{fig:randomized_svd_U},~\ref{fig:randomized_svd_S}, and~\ref{fig:randomized_svd_V}
-        show respectively the values $U$, $\Sigma$ and $V$.
-        Numerical precision is lower for smaller singular values and this loss of precision translates to singular vectors.
-It would be interesting to investigate the use of numerical precision for dimensionality reduction.
-    }
+        \texttt{face\_recognition} example using the \texttt{gesvd} SVD method
+        and RR. Figures~\ref{fig:randomized_svd_U},~\ref{fig:randomized_svd_S},
+        and~\ref{fig:randomized_svd_V} show respectively the values $U$,
+        $\Sigma$ and $V$. Numerical precision is lower for smaller singular
+        values and this loss of precision translates to singular vectors. It
+        would be interesting to investigate the use of numerical precision for
+        dimensionality reduction. }
     \label{fig:face_recognition_svd}
+\end{figure*}
+
+\begin{figure}
+    \centering
+    \begin{subfigure}{0.49\linewidth}
+        \includegraphics[width=\linewidth]{figure/BRR_singular_values.png}
+        \caption{BRR}
+        \label{fig:BRR_svd}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+        \includegraphics[width=\linewidth]{figure/OLS_singular_values.png}
+        \caption{OLS}
+        \label{fig:OLS_svd}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+        \includegraphics[width=\linewidth]{figure/BRR_singular_values_fixed.png}
+        \caption{BRR (fixed)}
+        \label{fig:BRR_svd_fixed}
+    \end{subfigure}
+    \begin{subfigure}{0.49\linewidth}
+        \includegraphics[width=\linewidth]{figure/OLS_singular_values_fixed.png}
+        \caption{OLS (fixed)}
+        \label{fig:OLS_svd_fixed}
+    \end{subfigure}
+    \caption{\add{Numerical precision of the singular values of the SVD from the
+            Bayesian Ridge model fitting (left) and from the Ordinary Least Square model
+            fitting (right) in the Bayesian Ridge Regression example. Red star
+            represents \texttt{NaN} value. Both SVD give \texttt{NaN} coefficients.
+            Switching from Divide \& Conquer to QR factorization improve numerical precision.
+            PyTracer helps to quickly visualize improvements.}}
 \end{figure}
@@
 
-% File "/usr/local/lib/python3.8/site-packages/sklearn/datasets/\_lfw.py", line 169, in \_load\_imgs
-%     faces[i, ...] = face
-% ValueError: could not broadcast input array from shape (49,37) into shape (50,37)
-
-% \paragraph{L1 Penalty}
-% This test compares the percentage of zero coefficients for logistic regression
-% by varying the penalty (L1, L2 and Elastic-Net) and regularization (1, 0.1, 0.01) parameters. 
-% A large regularization value gives the model more freedom than a small value, which puts more constraints on the model.
+% File "/usr/local/lib/python3.8/site-packages/sklearn/datasets/\_lfw.py", line
+%     169, in \_load\_imgs faces[i, ...] = face ValueError: could not broadcast
+%     input array from shape (49,37) into shape (50,37)
+
+% \paragraph{L1 Penalty} This test compares the percentage of zero coefficients
+% for logistic regression by varying the penalty (L1, L2 and Elastic-Net) and
+% regularization (1, 0.1, 0.01) parameters. A large regularization value gives
+% the model more freedom than a small value, which puts more constraints on the
+% model.
 
@@
 
-% Comparison of the sparsity (percentage of zero coefficients) of solutions when L1, L2 and Elastic-Net penalty are used for different values of C.
-We can see that large values of C give more freedom to the model.
-Conversely, smaller values of C constrain the model more.
-In the L1 penalty case, this leads to sparser solutions.
-As expected, the Elastic-Net penalty sparsity is between that of L1 and L2.
-% We classify 8x8 images of digits into two classes: 0-4 against 5-9. The visualization shows coefficients of the models for varying C.
+% Comparison of the sparsity (percentage of zero coefficients) of solutions when
+% L1, L2 and Elastic-Net penalty are used for different values of C. We can see
+% that large values of C give more freedom to the model. Conversely, smaller
+% values of C constrain the model more. In the L1 penalty case, this leads to
+% sparser solutions. As expected, the Elastic-Net penalty sparsity is between
+% that of L1 and L2. We classify 8x8 images of digits into two classes: 0-4
+% against 5-9. The visualization shows coefficients of the models for varying C.
 
@@
 
-% \paragraph{Lasso and Elastic-Net}
-% This test compares the Lasso and Elastic-Net regression models
-% on a corrupted signal.
-
-% Estimates Lasso and Elastic-Net regression models on a manually generated sparse signal corrupted with an additive noise. Estimated coefficients are compared with the ground-truth.
+% \paragraph{Lasso and Elastic-Net} This test compares the Lasso and Elastic-Net
+% regression models on a corrupted signal.
+
+% Estimates Lasso and Elastic-Net regression models on a manually generated
+% sparse signal corrupted with an additive noise. Estimated coefficients are
+% compared with the ground-truth.
 
@@
 
-\paragraph{Separating hyperplane}
-
-This example uses a linear Support Vector Machine (SVM) classifier trained using
-the Stochastic Gradient Descent (SGD) method to find the maximum separating
-hyperplane between sets of 2D points. The example trains the SVM with 50 random
-points separated in 2 clusters with hyperparameter $\alpha=0.01$ and using the
-hinge loss function. Once the model is trained, the example generates a
-$[-1,5]\times[-1,5]$ Cartesian grid discretized with 100 points and predicts the
-class label for each point with integer coordinates.
-Figure~\ref{fig:hyperplan_sig_zoom} shows the number of significant bits
-obtained with RR for each point of the grid. 
-We can see that yellow regions 
-close to the separating hyperplane are highly unstable with a number of
-significant bits below 0, meaning that the classifier is unsure about the
-predicted class. 
-%\tristan{Describe and comment on the other 2 tests, why are they more stable? Is it because the training set has more points?}
-
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/separating_hyperplan/hyperplan.png}
-%     \caption{Ratio $mean/std$ of Separating hyperplane test result within RR mode.
-%     Circle and square points represent respectively the train and test dataset.
-%     The color represents the predicted class. We can see that 
-%     instability is high around the hyperplane which is coherent with 
-%     the fact the classifier has difficulty to decide in which side of the hyperplane the 
-%     point is.}
-%     \label{fig:separating_hyperplan}
-% \end{figure}
-
-\begin{figure}
-    \centering
-    % \begin{subfigure}{.3\linewidth}
-    % \includegraphics[width=\linewidth]{figure/separating_hyperplan/hyperplan.png}
-    % \caption{}
-    % \label{fig:hyperplan_sig}
-    % \end{subfigure}
-    \begin{subfigure}{.45\linewidth}
-        \includegraphics[width=\linewidth]{figure/separating_hyperplan/hyperplane_zoom.pdf}
-        \caption{Separating hyperplane}
-        \label{fig:hyperplan_sig_zoom}
-    \end{subfigure} \\
-    \begin{subfigure}{.45\linewidth}
-        \includegraphics[width=\linewidth]{figure/SVM/non_weighted.pdf}
-        \caption{SVM (non weighted)}
-        \label{fig:SVM_nw_sig}
-    \end{subfigure}
-    \begin{subfigure}{.45\linewidth}
-        \includegraphics[width=\linewidth]{figure/SVM/weighted.pdf}
-        \caption{SVM (weighted)}
-        \label{fig:SVM_w_sig}
-    \end{subfigure} \\
-    \begin{subfigure}{.45\linewidth}
-        \includegraphics[width=\linewidth]{figure/Weighted/non_weighted.pdf}
-        \caption{SGD weighted (non-weighted)}
-        \label{fig:weighted_nw_sig}
-    \end{subfigure}
-    \begin{subfigure}{.45\linewidth}
-        \includegraphics[width=\linewidth]{figure/Weighted/weighted.pdf}
-        \caption{SGD weighted (weighted)}
-        \label{fig:weighted_w_sig}
-    \end{subfigure}
-    \caption{
-        Three examples of separating hyperplane prediction.
-All the figures show the number of significant bits of the prediction in RR mode.
-The separating hyperplane corresponds to a lower-precsion region in each figure.
-Using a large discretization step amplifies
-        this instability.
-        % respectively the results of examples    \textit{SVM} and~\textit{Weighted samples}.
-Figures~\ref{fig:SVM_nw_sig} and~\ref{fig:weighted_nw_sig} show the unweighted classification while Figures~\ref{fig:SVM_w_sig} and~\ref{fig:weighted_nw_sig} the classification taking into account the weights.
-We can see that taking into account the weight classes allows a better separation.
-        % \tristan{add labels to subfigures} \tristan{don't use this yellow for class 1, take a color that isn't in the color map. Add a legend to show the class colors.}
-    }
-    \label{fig:separating_hyperplan}
-\end{figure}
-
-% \paragraph{MNIST classification}
-% This test fits a logistic regression with the SAGA solver with the L1 penalty on the MNIST digits classification task subset.
-
-% Here we fit a multinomial logistic regression with L1 penalty on a subset of the MNIST digits classification task.
-We use the SAGA algorithm for this purpose: this a solver that is fast when the number of samples is significantly larger than the number of features and is able to finely optimize non-smooth objective functions which is the case with the l1-penalty.
-Test accuracy reaches > 0.8, while weight vectors remains sparse and therefore more easily interpretable.
-% Note that this accuracy of this l1-penalized linear model is significantly below what can be reached by an l2-penalized linear model or a non-linear multi-layer perceptron model on this dataset.
+% \paragraph{MNIST classification} This test fits a logistic regression with the
+% SAGA solver with the L1 penalty on the MNIST digits classification task
+% subset.
+
+% Here we fit a multinomial logistic regression with L1 penalty on a subset of
+% the MNIST digits classification task. We use the SAGA algorithm for this
+% purpose: this a solver that is fast when the number of samples is
+% significantly larger than the number of features and is able to finely
+% optimize non-smooth objective functions which is the case with the l1-penalty.
+% Test accuracy reaches > 0.8, while weight vectors remains sparse and therefore
+% more easily interpretable. Note that this accuracy of this l1-penalized linear
+% model is significantly below what can be reached by an l2-penalized linear
+% model or a non-linear multi-layer perceptron model on this dataset.
 
@@
 
-% \paragraph{Multitask Lasso}
-% This test compares the Lasso and MultiTaskLasso regression models
-% on a corrupted signal.
-
-% The multi-task lasso allows to fit multiple regression problems jointly enforcing the selected features to be the same across tasks.
-This example simulates sequential measurements, each task is a time instant, and the relevant features vary in amplitude over time while being the same.
-The multi-task lasso imposes that features that are selected at one time point are select for all time point.
-This makes feature selection by the Lasso more stable.
+% \paragraph{Multitask Lasso} This test compares the Lasso and MultiTaskLasso
+% regression models on a corrupted signal.
+
+% The multi-task lasso allows to fit multiple regression problems jointly
+% enforcing the selected features to be the same across tasks. This example
+% simulates sequential measurements, each task is a time instant, and the
+% relevant features vary in amplitude over time while being the same. The
+% multi-task lasso imposes that features that are selected at one time point are
+% select for all time point. This makes feature selection by the Lasso more
+% stable.
 
@@
 
-% \paragraph{Orthogonal matching}
-% This test uses the Orthogonal Matching Pursuit algorithm
-% for recovering a sparse signal from a noisy measurement encoded with a dictionary.
+% \paragraph{Orthogonal matching} This test uses the Orthogonal Matching Pursuit
+% algorithm for recovering a sparse signal from a noisy measurement encoded with
+% a dictionary.
 
@@
 
-% \paragraph{PCA decomposition}
-% This test makes a PCA decomposition on a synthetic dataset.
-% These figures aid in illustrating how a point cloud can be very flat in one direction–which is where PCA comes in to choose a direction that is not flat.
+% \paragraph{PCA decomposition} This test makes a PCA decomposition on a
+% synthetic dataset. These figures aid in illustrating how a point cloud can be
+% very flat in one direction–which is where PCA comes in to choose a direction
+% that is not flat.
 
@@
 
-% \paragraph{Robust Linear Regression}
-% This test compares the linear and  RANSAC regression methods on noisy data.
-% In this example we see how to robustly fit a linear model to faulty data using the RANSAC algorithm.
+% \paragraph{Robust Linear Regression} This test compares the linear and  RANSAC
+% regression methods on noisy data. In this example we see how to robustly fit a
+% linear model to faulty data using the RANSAC algorithm.
 
 % RR: Very stable \\
-% MCA: Very stable if we exclude two traces that failed due to arange/index issues
-
-% \paragraph{Segmentation Toy}
-% This test uses spectral clustering to separate connected circles in an image.
-
-% In this example, an image with connected circles is generated and spectral clustering is used to separate the circles.
-
-% In these settings, the Spectral clustering approach solves the problem know as ‘normalized graph cuts’: the image is seen as a graph of connected voxels, and the spectral clustering algorithm amounts to choosing graph cuts defining regions while minimizing the ratio of the gradient along the cut, and the volume of the region.
-
-% As the algorithm tries to balance the volume (ie balance the region sizes), if we take circles with different sizes, the segmentation fails.
-
-% In addition, as there is no useful information in the intensity of the image, or its gradient, we choose to perform the spectral clustering on a graph that is only weakly informed by the gradient.
-This is close to performing a Voronoi partition of the graph.
-
-% In addition, we use the mask of the objects to restrict the graph to the outline of the objects.
-In this example, we are interested in separating the objects one from the other, and not from the background.
+% MCA: Very stable if we exclude two traces that failed due to arange/index
+% issues
+
+% \paragraph{Segmentation Toy} This test uses spectral clustering to separate
+% connected circles in an image.
+
+% In this example, an image with connected circles is generated and spectral
+% clustering is used to separate the circles.
+
+% In these settings, the Spectral clustering approach solves the problem know as
+% ‘normalized graph cuts’: the image is seen as a graph of connected voxels, and
+% the spectral clustering algorithm amounts to choosing graph cuts defining
+% regions while minimizing the ratio of the gradient along the cut, and the
+% volume of the region.
+
+% As the algorithm tries to balance the volume (ie balance the region sizes), if
+% we take circles with different sizes, the segmentation fails.
+
+% In addition, as there is no useful information in the intensity of the image,
+% or its gradient, we choose to perform the spectral clustering on a graph that
+% is only weakly informed by the gradient. This is close to performing a Voronoi
+% partition of the graph.
+
+% In addition, we use the mask of the objects to restrict the graph to the
+% outline of the objects. In this example, we are interested in separating the
+% objects one from the other, and not from the background.
 
@@
 
-\paragraph{SVM}
-This example uses a plain Support Vector
-Classification~\cite{Platt99probabilisticoutputs} (SVC) to find the best
-hyperplane separating an unbalanced dataset with two classes of 1000 and 100
-points. This example tests two SVC configurations using a linear kernel with and
-without a class weight parameter. The SVC predicts the class label for each
-coordinate over a $[-5,5] \times [-5,5]$ grid discretized with 900 points.
-Figures~\ref{fig:SVM_nw_sig} and~\ref{fig:SVM_w_sig} show the result within RR
-of the classification with and without taking into account the unbalancing. We
-can see that the number of significant bits is lower on the separating line and
-that taking into account class imbalance allows for a better separation.
-% Find the optimal separating hyperplane using an SVC for classes that are unbalanced.
-
-% We first find the separating plane with a plain SVC and then plot (dashed) the separating hyperplane with automatically correction for unbalanced classes.
+% Find the optimal separating hyperplane using an SVC for classes that are
+% unbalanced.
+
+% We first find the separating plane with a plain SVC and then plot (dashed) the
+% separating hyperplane with automatically correction for unbalanced classes.
 
@@
 
-% \paragraph{Tomography}
-% This test compares the LASSO and Ridge regression models to 
-% reconstruct an image from  projections for a dataset
-% acquired from computed tomography.
-
-% This test shows the reconstruction of an image from a set of parallel projections, acquired along different angles. Such a dataset is acquired in computed tomography (CT).
-
-% Without any prior information on the sample, the number of projections required to reconstruct the image is of the order of the linear size l of the image (in pixels).
-For simplicity we consider here a sparse image, where only pixels on the boundary of objects have a non-zero value.
-Such data could correspond for example to a cellular material.
-Note however that most images are sparse in a different basis, such as the Haar wavelets.
-Only l/7 projections are acquired, therefore it is necessary to use prior information available on the sample (its sparsity): this is an example of compressive sensing.
-
-% The tomography projection operation is a linear transformation.
-In addition to the data-fidelity term corresponding to a linear regression, we penalize the L1 norm of the image to account for its sparsity.
-The resulting optimization problem is called the Lasso.
-We use the class Lasso, that uses the coordinate descent algorithm.
-Importantly, this implementation is more computationally efficient on a sparse matrix, than the projection operator used here.
-
-% The reconstruction with L1 penalization gives a result with zero error (all pixels are successfully labeled with 0 or 1), even if noise was added to the projections.
-In comparison, an L2 penalization (Ridge) produces a large number of labeling errors for the pixels.
-Important artifacts are observed on the reconstructed image, contrary to the L1 penalization.
-Note in particular the circular artifact separating the pixels in the corners, that have contributed to fewer projections than the central disk.
+% \paragraph{Tomography} This test compares the LASSO and Ridge regression
+% models to reconstruct an image from  projections for a dataset acquired from
+% computed tomography.
+
+% This test shows the reconstruction of an image from a set of parallel
+% projections, acquired along different angles. Such a dataset is acquired in
+% computed tomography (CT).
+
+% Without any prior information on the sample, the number of projections
+% required to reconstruct the image is of the order of the linear size l of the
+% image (in pixels). For simplicity we consider here a sparse image, where only
+% pixels on the boundary of objects have a non-zero value. Such data could
+% correspond for example to a cellular material. Note however that most images
+% are sparse in a different basis, such as the Haar wavelets. Only l/7
+% projections are acquired, therefore it is necessary to use prior information
+% available on the sample (its sparsity): this is an example of compressive
+% sensing.
+
+% The tomography projection operation is a linear transformation. In addition to
+% the data-fidelity term corresponding to a linear regression, we penalize the
+% L1 norm of the image to account for its sparsity. The resulting optimization
+% problem is called the Lasso. We use the class Lasso, that uses the coordinate
+% descent algorithm. Importantly, this implementation is more computationally
+% efficient on a sparse matrix, than the projection operator used here.
+
+% The reconstruction with L1 penalization gives a result with zero error (all
+% pixels are successfully labeled with 0 or 1), even if noise was added to the
+% projections. In comparison, an L2 penalization (Ridge) produces a large number
+% of labeling errors for the pixels. Important artifacts are observed on the
+% reconstructed image, contrary to the L1 penalization. Note in particular the
+% circular artifact separating the pixels in the corners, that have contributed
+% to fewer projections than the central disk.
 
@@
 
-\paragraph{SGD weighted samples}
-This example uses an SGD to separate weighted points. It divides the training
-set into two classes of 10 points with a bigger weight for the second class. The
-SGD is trained with hyperparameters $\alpha=0.01$ and a maximum number of
-iterations to 100. The prediction is made on a $[-4,5]\times[-4,5]$ grid
-discretized with 250\add{,}000 points. Figures~\ref{fig:weighted_nw_sig}
-and~\ref{fig:weighted_w_sig} show the number of significant bits of prediction
-within RR along with dataset points in blue and \remove{violet} \add{purple}. We can see that the
-separating plane corresponds to a region of lower precision, similar to the
-previous examples. 
-% Finally, taking into account the points' weight allows for a better separation \tristan{is this related to numerical stability? If not, you can ommit the comment.}.
+% Finally, taking into account the points' weight allows for a better separation
+% \tristan{is this related to numerical stability? If not, you can ommit the
+% comment.}.
 
@@
 
-% PyAFQ is a Python package for Automated Fiber Quantification.
-% It aims to find delineation of the major fiber tracts in individual human brains and quantify the tissue properties within the tracts.
-PyAFQ \pytracer tracing produces traces of 1TB with an average slowdown $\times 6$ compared to the actual execution.
-Moreover, \pytracer was able to visualize the aggregated traces, demonstrating its scalability fluently.
-
-\subsection{Overhead evaluation}
+% PyAFQ is a Python package for Automated Fiber Quantification. It aims to find
+% delineation of the major fiber tracts in individual human brains and quantify
+% the tissue properties within the tracts. PyAFQ \pytracer tracing produces
+% traces of 1TB with an average slowdown $\times 6$ compared to the actual
+% execution. Moreover, \pytracer was able to visualize the aggregated traces,
+% demonstrating its scalability fluently.
+
+\subsection{Overhead remains tractable and evolves linearly with the trace size}
 
@@
 (without \pytracer) and the execution time using \pytracer. The \textit{Slowdown
-    RR} and \textit{Slowdown MCA} show the slowdown within the fuzzy environment.
+    RR} \remove{and \textit{Slowdown MCA}} shows the slowdown within the fuzzy environment.
 Without fuzzy, \pytracer introduces an average slowdown of $17\times$ high for
@@
 initialization time to \textit{Slowdown}. We then obtain an average slowdown of
-$3.5\times$. Finally, the \remove{fuzzy instrumentation} \add{using MCA operations (throuhg fuzzy) instead of the native ones} increases the average slowdown
-to $37\times$ for RR and $43\times$ for Full MCA.
-
-% \pytracer's tracing overhead consists of (1) module instrumentation time (initialization overhead), and (2) data write time during the execution (runtime overhead).
-The initialization overhead is proportional to the number of functions and classes traced.
-However, the initialization overhead is amortized \tristan{what do you mean by amortized?
-I don't get this sentence} when traced applications are above 8 seconds,  proportional to
-% the number of functions and classes traced.
-Figure~\ref{fig:performance_tracing} summaries \pytracer's tracing overhead for SciPy and scikit-learn examples.
-We can see that \pytracer introduces a slowdown of reduced toif we subtract the initialization step
-% \tristan{not sure where to get these numbers from the table, to be clarified. Are these average values? Why are there two values?}. 
+$3.5\times$. Finally, the \remove{fuzzy instrumentation} \add{using MCA
+    operations (throuhg fuzzy) instead of the native ones} increases the average
+slowdown to $37\times$ for RR\remove{and $43\times$ for Full MCA}.
+
+% \pytracer's tracing overhead consists of (1) module instrumentation time
+% (initialization overhead), and (2) data write time during the execution
+% (runtime overhead). The initialization overhead is proportional to the number
+% of functions and classes traced. However, the initialization overhead is
+% amortized \tristan{what do you mean by amortized? I don't get this sentence}
+% when traced applications are above 8 seconds,  proportional to the number of
+% functions and classes traced. Figure~\ref{fig:performance_tracing} summaries
+% \pytracer's tracing overhead for SciPy and scikit-learn examples. We can see
+% that \pytracer introduces a slowdown of reduced toif we subtract the
+% initialization step \tristan{not sure where to get these numbers from the
+% table, to be clarified. Are these average values? Why are there two values?}.
 % Fuzzy instrumentation increases the slowdown to for RR and   for Full MCA.
-% \tristan{Figure 13 is not referred in the text. Choose between the figure and the table, no need to put both.}
+% \tristan{Figure 13 is not referred in the text. Choose between the figure and
+% the table, no need to put both.}
 
@@
     \caption{
-        \pytracer tracing overheads.
-\textit{Slowdown} represents the slowdown of \pytracer without fuzzy measured as the ratio between the actual execution time (without \pytracer) and the execution time using \pytracer.
-        \textit{Slowdown (Instrumentation)} show the actual instrumentation cost computed by subtracting the initialization step.
-        The \textit{Slowdown (RR)} and \textit{Slowdown (MCA)} are the slowdown of \pytracer 
-        using the fuzzy environment with RR and Full MCA modes.
-        The first \remove{first} \add{last} four examples measure the initialization steps depending on the modules instrumented. 
+        \pytracer tracing overheads. \textit{Slowdown} represents the slowdown
+        of \pytracer without fuzzy measured as the ratio between the actual
+        execution time (without \pytracer) and the execution time using
+        \pytracer. \textit{Slowdown (Instrumentation)} show the actual
+        instrumentation cost computed by subtracting the initialization step.
+        The \textit{Slowdown (RR)} \remove{and \textit{Slowdown (MCA)} are} \add{is} the slowdown
+        of \pytracer using the fuzzy environment with \add{the} RR \remove{and Full MCA} mode\remove{s}. The
+        first \remove{first} \add{last} four examples measure the initialization
+        steps depending on the modules instrumented. 
         % \tristan{there's too much text in this caption, move some of it to the text, the caption should just explain the difference between the 4 slowdowns.
@@
 and the log of the time shows a significant correlation (p-value $\leq 10^{-8}$
-for RR and p-value $\leq 10^{-3}$ for MCA).
+\remove{for RR and p-value $\leq 10^{-3}$ for MCA}).
 % \tristan{Mention linear correlation with p-value here.}
@@
 
-% \pytracer is a tool for visualizing the numerical quality of function inputs and outputs along the execution of a Python program.
-It generates numerical traces and post-processes them to measure numerical discrepancies between executions.
-\pytracer does not require any particular noise model to estimate uncertainties.
-We tested it with MCA through the fuzzy ecosystem on two broadly used Python libraries.
+% \pytracer is a tool for visualizing the numerical quality of function inputs
+% and outputs along the execution of a Python program. It generates numerical
+% traces and post-processes them to measure numerical discrepancies between
+% executions. \pytracer does not require any particular noise model to estimate
+% uncertainties. We tested it with MCA through the fuzzy ecosystem on two
+% broadly used Python libraries.
 
@@
 
+\remove{
     As we showed in Section~\ref{sec:impact_mca_modes}, using Full MCA mode leads to
@@
     research is required to address the issues encountered with Full MCA. 
+}
 
@@
 using shadow computations with higher precision.
-Herbgrin\remove{g}\add{d}~\cite{sanchez2017finding} is a Valgrind-based tool to detect numerical
-instabilities. It uses a shadow memory to detect precision losses by comparison
-with results obtained \remove{at} \add{in} higher precision. It is combined with symbolic
-computation to backtrack the root of the error. We can note that all methods
-based on a high-precision oracle suppose that computing with a large number of
-bits is sufficient to obtain an accurate result, which is not always true (see
-for example, the famous Muller's sequence~\cite{bajard1996introduction}).
-Although versatile, the DBI looses high-level information useful to understand
-the source-code logic.
+Herbgrin\remove{g}\add{d}~\cite{sanchez2017finding} is a Valgrind-based tool to
+detect numerical instabilities. It uses a shadow memory to detect precision
+losses by comparison with results obtained \remove{at} \add{in} higher
+precision. It is combined with symbolic computation to backtrack the root of the
+error. We can note that all methods based on a high-precision oracle suppose
+that computing with a large number of bits is sufficient to obtain an accurate
+result, which is not always true (see for example, the famous Muller's
+sequence~\cite{bajard1996introduction}). Although versatile, the DBI looses
+high-level information useful to understand the source-code logic.
 
@@
 
-% \label{sec:detecting-instabilities}
-% \paragraph{Dynamically detecting numerical instabilities}
-% \label{sec:mca}
+% \label{sec:detecting-instabilities} \paragraph{Dynamically detecting numerical
+% instabilities} \label{sec:mca}
 % :
-%  \Yohan{Either detail this section with UA/SA or remove it since MCA is introduced in 'noise injection' subsection.
-} \tristan{I agree, let's just remove it, the core of the contribution is on the tracing, not in the detection of instabilities.}
-
-% % We review here the existing theoretical framework that might be used to detect numerical instabilities.
-% % Our experiments rely on the Monte Carlo Arithmetic (MCA), a stochastic arithmetic allowing 
-% % to detect numerical errors by adding random perturbations in the floating-point computations.
-% % However, Pytracer do not rely on any assumption about the perturbation model used and thus leaves the user free to use
-% % an alternative model. As such, we describe two others options that we thought might be beneficial and complementary to MCA: 
-% % input data uncertainty analysis and random seed sensitivity.
+%  \Yohan{Either detail this section with UA/SA or remove it since MCA is
+%  introduced in 'noise injection' subsection. } \tristan{I agree, let's just
+%  remove it, the core of the contribution is on the tracing, not in the
+%  detection of instabilities.}
+
+% % We review here the existing theoretical framework that might be used to
+% detect numerical instabilities. % Our experiments rely on the Monte Carlo
+% Arithmetic (MCA), a stochastic arithmetic allowing % to detect numerical
+% errors by adding random perturbations in the floating-point computations. %
+% However, Pytracer do not rely on any assumption about the perturbation model
+% used and thus leaves the user free to use % an alternative model. As such, we
+% describe two others options that we thought might be beneficial and
+% complementary to MCA: % input data uncertainty analysis and random seed
+% sensitivity.
 
@@
 
-% % The Monte Carlo Arithmetic is a variant of so-called stochastic arithmetic, whose purpose is to model round-off errors by a random variable.
-
-% Three main approaches exist to detect numerical instabilities dynamically: stochastic arithmetic, uncertainty or sensitivity analysis~\cite{helton2006survey}, and random seed analysis~\cite{click2011quality}.
-% Stochastic arithmetic leverages randomness to estimate numerical instabilities coming from the use of floating-point representations.
-The main idea is to treat round-off errors as random variables and characterize them statistically.
-% The first published complete stochastic arithmetic framework was CESTAC~\cite{vignes1993stochastic}.
-In CESTAC, each floating-point computation is performed multiple times with different rounding modes: round-up or round-down.
-From these stochastic samples, one can then derive the number of significant digits in the computed result.
-Discrete Stochastic Arithmetic~\cite{vignes2004discrete} extends CESTAC with comparison operators implemented in the CADNA library.
-% Monte Carlo Arithmetic (MCA)~\cite{parker1997monte} uses the same principle but introduces two differences:
-% (i) a virtual precision parameter, allowing to simulate reduced working precision, and (ii) different perturbation modes to introduce perturbations
-% on function inputs or output.
-% Stochastic arithmetic quantifies numerical error using the number of significant digits $s$ estimated among the sampled values.
-A common formula to determine this number from MCA samples is presented in~\cite{parker1997monte}.
-% Sohier et al.~\cite{sohier2018confidence} recently provided a generalization of this formula to include confidence intervals.
-
-% % \subsubsection{Uncertainty, sensitivity, and random seed analysis}
-% % \tristan{I'm wondering if we could remove this sub-section, as it doesn't seem to be critical to the understanding of the paper, wdyt?}
-% % Uncertainty analysis (UA) is a method to estimate the output distribution given an input distribution.
-% % Sensitivity analysis (SA) is a variation of UA that measures the local response to a small perturbation~\cite{loucks2017water}. 
-% % Several approaches for UA and SA exist, among them differential analysis, response surface methodology, Monte Carlo analysis, and variance decomposition (see~\cite{helton2006survey} for a review).
-In particular, Monte Carlo analysis is a sampling-based technique that samples inputs space to estimate output response.
-Monte Carlo analysis shares similarities with Monte Carlo Arithmetic.
-For instance, the PRECISE framework~\cite{chaitin1996lectures} shares with MCA the idea of varying virtual precision to estimate output sensitivity.
-
-% % Furthermore, the quality of a Random Number Generator is a crucial characteristic when dealing with stochastic model and differ from cryptography requirements.
-A good RNG provides a tradeoff between performance, period, correlation, or uniformity~\cite{james2020review} for numerical simulation.
-% On the other hand, poor-quality RNGs may have a substantial impact on results~\cite{click2011quality}.
-First, measuring variation induced by seed is a good indicator of program stability that we can compare against variability induced by floating-point arithmetic.
-
-% \paragraph{Visualization of numerical data}
-% \tristan{now that it's here, I'm not sure if this section really adds to the paper. It could also go.}
+% % The Monte Carlo Arithmetic is a variant of so-called stochastic arithmetic,
+% whose purpose is to model round-off errors by a random variable.
+
+% Three main approaches exist to detect numerical instabilities dynamically:
+% stochastic arithmetic, uncertainty or sensitivity
+% analysis~\cite{helton2006survey}, and random seed
+% analysis~\cite{click2011quality}. Stochastic arithmetic leverages randomness
+% to estimate numerical instabilities coming from the use of floating-point
+% representations. The main idea is to treat round-off errors as random
+% variables and characterize them statistically. The first published complete
+% stochastic arithmetic framework was CESTAC~\cite{vignes1993stochastic}. In
+% CESTAC, each floating-point computation is performed multiple times with
+% different rounding modes: round-up or round-down. From these stochastic
+% samples, one can then derive the number of significant digits in the computed
+% result. Discrete Stochastic Arithmetic~\cite{vignes2004discrete} extends
+% CESTAC with comparison operators implemented in the CADNA library. Monte Carlo
+% Arithmetic (MCA)~\cite{parker1997monte} uses the same principle but introduces
+% two differences: (i) a virtual precision parameter, allowing to simulate
+% reduced working precision, and (ii) different perturbation modes to introduce
+% perturbations on function inputs or output. Stochastic arithmetic quantifies
+% numerical error using the number of significant digits $s$ estimated among the
+% sampled values. A common formula to determine this number from MCA samples is
+% presented in~\cite{parker1997monte}. Sohier et al.~\cite{sohier2018confidence}
+% recently provided a generalization of this formula to include confidence
+% intervals.
+
+% % \subsubsection{Uncertainty, sensitivity, and random seed analysis} %
+% \tristan{I'm wondering if we could remove this sub-section, as it doesn't seem
+% to be critical to the understanding of the paper, wdyt?} % Uncertainty
+% analysis (UA) is a method to estimate the output distribution given an input
+% distribution. % Sensitivity analysis (SA) is a variation of UA that measures
+% the local response to a small perturbation~\cite{loucks2017water}. % Several
+% approaches for UA and SA exist, among them differential analysis, response
+% surface methodology, Monte Carlo analysis, and variance decomposition
+% (see~\cite{helton2006survey} for a review). In particular, Monte Carlo
+% analysis is a sampling-based technique that samples inputs space to estimate
+% output response. Monte Carlo analysis shares similarities with Monte Carlo
+% Arithmetic. For instance, the PRECISE framework~\cite{chaitin1996lectures}
+% shares with MCA the idea of varying virtual precision to estimate output
+% sensitivity.
+
+% % Furthermore, the quality of a Random Number Generator is a crucial
+% characteristic when dealing with stochastic model and differ from cryptography
+% requirements. A good RNG provides a tradeoff between performance, period,
+% correlation, or uniformity~\cite{james2020review} for numerical simulation.  
+% On the other hand, poor-quality RNGs may have a substantial impact on
+% results~\cite{click2011quality}. First, measuring variation induced by seed is
+% a good indicator of program stability that we can compare against variability
+% induced by floating-point arithmetic.
+
+% \paragraph{Visualization of numerical data} \tristan{now that it's here, I'm
+% not sure if this section really adds to the paper. It could also go.}
 
 % Floating-point values approximate real number in the computer arithmetic but
-% data manipulated by scientific applications include a large variety of mathematical objects
-% beyond scalar values. 
-% Indeed, scientific visualization 
-% \gkmod{}{Note: You kind of jump right in to this section. Visualization of what in particular? Why do we want (need?) to visualize this sort of data?} 
-% covers a wide range of numerical simulation domains, from general-purpose numerical visualization with tools such as VTK~\cite{schroeder2000visualizing} to topological data analysis~\cite{tierny2018topological}, including matrix~\cite{wu2008matrix} or tensor~\cite{kindlmann2006diffusion} visualization.
-% To be able to visualize those objects is crucial for the practitioner 
-% as information about the structure of the object may be as important as the basic elements that constitute it (i.e. vectors or matrices). 
-% Despite the large number of existing tools to identify numerically unstable sections of source code, few allow the user to have a global view of the numerical precision of their computations or to compare several executions of the same program under various perturbations.
-
-% Veritracer~\cite{chatelain2018veritracer} was the first tool to propose an embedded visualizer of numerical stability over the execution of C, C++, and Fortran code.
-Veritracer extends Verificarlo~\cite{verificarlo} with contextual information about traced variables, which allows the user to identify instabilities quickly.
-% However, Veritracer neither offers a dynamic interface nor includes information about high-level structures such as \texttt{struct} or \texttt{array}.
-% FPAvizual~\cite{gu2014fpavisual} visualizes the effects of floating-point arithmetic but only for educational purposes and so does not target computational intensive applications\gkmod{}{Q: What does this mean?}.
-% Anteater~\cite{faust2019anteater} proposes a visualizer for Python code, but as mentioned previously, it only deals with native Python types, and the user needs to select variables to trace manually.
-Anteater provides an insightful reflection
-% around visual debugging beyond floating-point analysis, which has inspired the design of \pytracer's visualization interface.
-
-% Through our analysis of SciPy and Scikit-learn, we demonstrated \pytracer's scalability, automaticity, and applicability to any Python program.
-The relatively low instrumentation overhead of $3.5\times$ on average enables the analysis of real applications.
-\pytracer's instrumentation is fully automatic and does not require manual intervention from the user.
-\pytracer works on any Python libraries, with any data format supported by Pickle and any numerical noise model.
-
-% \pytracer is the first tool to enable a systematic numerical analysis of Python codes.
-Existing tools focus on traditional languages of the HPC community such as C, C++, and FORTRAN.
-However, Python's high-level abstraction allows for quickly developing applications while maintaining high performance thanks to specialized libraries such as NumPy.
-Therefore, \pytracer meets the numerical analysis needs of an ever-increasing number of applications.
-
-% Furthermore, \pytracer allows users to pinpoint numerical instabilities root causes precisely by working at the function level.
-Indeed, evaluating the numerical stability is complex since calculations
-% are strongly correlated between them. 
-% The instrumentation at the function level limits the size of the traces since only inputs and outputs of a function are dumped.
-It moreover decreases the overhead of the instrumentation and helps the user to identify instabilities quickly.
-% Working at function level is thus a suitable compromise between (1) analyzing at the floating-point operation level and (2) user debug prints.
-% (1) Indeed, the fine-grained analysis is costly and hard to analyze due to the large amount of computations evolved in HPC codes.
-It overwhelms the user with too much information, making analysis more difficult but can be interesting at the final step of the understanding.
-% (2) Looking at intermediate results through print statements focuses on valuable information
-% (like residuals or norms) but may miss numerically unstable functions unsuspected by the developer.
-% Finally, the SciPy environment wraps a lot of computation kernels written in C, like BLAS or LAPACK.
-% By working at function level, \pytracer allows the user to evaluate the numerical precision of such kernels
-% and their impact on the code without getting deep into technical implementation aspects.
-
-% Python is a popular language to prototype proof-of-concept. Integrating \pytracer at early stages of the development cycle allows identifying numerical instabilities to write code of better quality.
-% \pytracer's automaticity facilitates the usage and enables its integration in unit testing.
-% It can be for example used in a non-regression test to ensure that the numerical quality of a calculation
-% is not degraded by updates. Moreover, the Plotly dashboard offers a quick visualization to 
-% analyze more finely the potential issues.
-
-% \pytracer can also be useful to select the hyperparameters of a code, as it is the case in machine learning.
-% Indeed, we find many cases in the literature where users explore a range of hyperparameters
-% to select the ones giving the best scores. With \pytracer, 
-% the user has a practical way to quantify the numerical quality and to understand why hyperparameters
-% lead to unstable outputs, instead of tweaking hyperparameters to make solvers converge,
-
-% The visualization permits a global view of the code and to understand interactions between 
-% computations. The Plotly dashboard help to easily navigate through the code.
-% It moreover removes the need for ad-hoc scripts to visualize data. 
-% Finally, the dashboard can be extended to support other data format to visualize.
-% \pytracer currently supports n-dimensional NumPy arrays as well as native Python data.
-
-% As we showed in Section~\ref{sec:impact_mca_modes}, using Full MCA mode leads to runtime errors that have a considerable impact on the proper functioning of the execution.
-This is unfortunate since these errors do not reflect actual numerical errors but errors related to perturbations that should not occur.
-% Conversely, RR mode is far more conservative since it preserves exact operations and is easier to use even though it does not simulate all perturbations.
-% From our experiments, we do not recommend the Full MCA mode for now and more researches are needed 
-% to help fixing issues we encountered.
-
-% Fixing this issue would enable the study of catastrophic cancellations, which are common sources of numerical errors. 
-% In addition to the runtime errors it raises, mismatching shapes is also a problem when aggregating traces as \pytracer will not compute statistics for a set of arrays with different shapes \tristan{So do you conclude that Full MCA is not usable while RR is?
-If so, you should recommend to use Pytracer with RR only.} \tristan{are you still talking about Full MCA here?
-if not, make another paragraph.
-If so, make it clearer.}.
-Two solutions exist to overcome this issue: the first is not to instrument the \texttt{PyArray\_Arange} function with MCA.
-The advantage is that it is easy to set up since it requires one extra line in the exclusion file.
-However, the same kind of problem may appear somewhere else because, as we have seen, the evolved operations are elementary.
-Therefore, the chances that developers reproduce the same pattern are very probable.
-Therefore, the second solution is to ensure that the Full MCA mode preserves the exact operations.
-This solution has the advantage of not worrying about which functions should be instrumented or not with MCA, but it is hard to achieve it in practice.
-Indeed, we rely on the MCA implementation provided by Verificarlo that uses an internal precision to add the random perturbation that is higher than the working precision for applying the random noise.
-Verificarlo then rounds the result to the working precision before returning it, so any residual noise lower than the working precision is lost.
-Keeping track of that noise would require recording each intermediate computation in a shadow memory or keeping a tag about their exactness.
-This option would require more extra works than the first one but would ensure more consistent results.
-\tristan{I find this paragraph too verbose, you should contract it to a few key sentences.}
-
-% \tristan{The following paragraphs are future work, not discussion. I'd remove them and flesh out the discussion from the ideas mentioned in the current 3rd paragraph}
-
-% Also, we would like to extend the post-process analysis to aggregate traces where the execution flow path diverges.
-Therefore, a posteriori reconstruction is challenging as one must precisely identify the flow path taken and find synchronization points to pursue the analysis.
-We retrieve, for example, this divergence behavior in two general classes of numerical schemes: iterative methods and optimization processes.
-One solution is to integrate methods used in code coverage analysis to keep track of flow paths taken and the backtraces.
-However, this would increase the complexity of the postprocess analysis as well as an extra slowdown factor.
-However, by coupling the Gantt chart with static analysis, \pytracer would catch some divergence patterns occurring within a function.
-Indeed, by instrumenting at the function level, \pytracer views the function's callees (i.e., the functions called within a function) and thus should partially detect flow divergences.
-
-% By design principle, \pytracer is flexible on the noise model used, although we only tested it with the MCA model in our experiments.
-Nevertheless, we would like to compare different models against MCA in future works to see the resulting differences.
-Furthermore, we would like to test \pytracer on parallel codes.
-
-% Finally, we would extend \pytracer to instrument elementary arithmetic operations which can be helpful to more profound analyses.
-We nevertheless believe that instrumentation at the function level presents two advantages: it first limits the size of the traces since only inputs and outputs of a function are saved instead of a full report which, on the one hand, decreases the overhead of the instrumentation and, on the other hand, help the user to identify instabilities quickly.
-Indeed, full reporting can overwhelm the user with too much information, making analysis more difficult at first.
-Second, the analysis at fine granularity is interesting at the final step of the understanding.
-Such an analysis would require a different instrumentation approach by, for example, working at the Abstract Syntax Tree (AST) level since it is trivial to get it in Python.
-% Moreover, working at the AST level allows doing dependency analysis.
-Another extension would be to extract and replay a function, in the same vein as the CERE tool does but for Python, and to use an AST instrumentation to analyze the numerical quality of elementary operations step by step within the fuzzy environment.
-
-% \pytracer is a tool for visualizing the numerical quality of function inputs/outputs over time.
-% It generates numerical traces that are aggregated in postprocessing to measure numerical discrepancies between executions.
-% \pytracer does not assume the noise model used to estimate uncertainties but has been tested with the MCA 
-% through the fuzzy ecosystem on two broadly used scientific libraries for Python with partial success.
-
-% We demonstrated the Pytracer's capabilities to analyze intensively used Python libraries such as NumPy or Scikit-learn, such as 
-% 1) Scalability. The low instrumentation overhead of 3.5x enables analysis of real applications and permits having a global representation of the numerical quality of an application. 
-% 2) Automaticity. Pytracer instrumentation is fully automatic and does not require manual intervention from the user, allowing the instrumentation of 
-% the NumPy, SciPy and Scikit-learn libraries.
-% // that cumulate 5600 and 2043 pure Python functions and classes. 
-% 3) Agnosticity. Pytracer works on any python libraries, with any data format supported by pickle, and any numerical noise model flavor.
-
-% Pytracer is the first tool to bring numerical analysis of Python codes available to everyone.
-Indeed, existing tools developed in the last years focused on traditional HPC languages community such as C,C++, and FORTRAN.
-However, the Python high-level abstraction allows you to quickly develop applications while maintaining high performance with the help of specialized libraries like NumPy.
-Therefore, it is quite natural to see more fields systematically using Python, as is the case in neuroimaging.
-Thus, Pytracer meets the numerical analysis needs of an ever increasing number of applications writing in Python.
-
-% By working at function level, Pytracer allows users to precisely pinpoint numerical instabilities root causes.
-Furthermore, the automaticity facilitates the usage and its integration in unit testing.
-Hence, instead of tweaking hyperparameters to make solvers converging, the user has a practical way with Pytracer to quantify the numerical quality of its computations.
-
-% As we showed in section~\ref{sec:impact_mca_modes}, using the Full MCA mode leads to runtime errors that have a considerable impact on the proper functioning of the execution, which is unfortunate since these
-% errors do not reflect actual numerical errors but errors related to perturbations that should not occur.
-% Fixing this misbehavior would greatly help use Full MCA mode since this mode allows simulating catastrophic cancellations, which are familiar sources of numerical errors.
-By preserving exact operations, RR mode is far more conservative and so easy to use even though it does not simulate all perturbations that might be encountered.
-
-% Also, using a post-process analysis to aggregate traces, \pytracer falls in the same pitfalls as veritracer and is limited to aggregate traces where the execution flow path extremely diverges.
-Therefore, a posteriori reconstruction
-% is challenging as one must precisely identify the flow path taken and find synchronization points to pursue the analysis.
-We retrieve, for example, this divergence behavior in two general classes of numerical schemes: iterative methods and optimization processes.
-One solution to overcome this issue is to integrate methods used in code coverage analysis to keep track of flow paths taken and the backtraces.
-% However, this would increase the complexity of the postprocess analysis as well as an extra slowdown factor.
-% However, by coupling the Gantt chart with static analysis, \pytracer would catch some divergence patterns occurring within a function.
-Indeed, by instrumenting at the function level, \pytracer views the function's callees (i.e., the functions called within a function) and thus should partially detect flow divergences.
-
-% By design principle, \pytracer is flexible on the noise model used, although we only tested it with the MCA model in our experiments.
-% Nevertheless, we would like to compare different models against MCA in future works to see the resulting differences. 
-% In particular, although \pytracer only works on a sequential application for the moment, it can be used to analyze parallel sections internal to a function.
-% The only restriction is that the section does not call other functions traced by \pytracer; we would fall into the previous issue of divergence if it would not be the case.
-% Since \pytracer only cares about inputs and outputs of a function, the order of internal operations is transparent for it and thus should be able to handle those cases.
-
-% Finally, \pytracer does not instrument elementary arithmetic operations, and it can be a barrier to more profound analysis.
-%Such an analysis would require a different instrumentation approach by, for example, working at the Abstract Syntax Tree (AST) level since it is trivial to get it in Python.
-% An ideal way to do that would be to extract and replay a function, in the same vein as the CERE~\cite{castro2015cere} tool does but for Python, and use an AST instrumentation to analyze the numerical quality of elementary operations step by step within the fuzzy environment.
-% Lastly, AST analysis can serve as a basis for finding relationships between variables, valuable information for the user.
-
-% In addition to the runtime errors it raises, mismatching shapes is also a problem when aggregating traces as PyTracer will not compute statistics for a set of arrays with different shapes.
-% Two solutions exist to overcome this issue: the first is not to instrument the \texttt{PyArray\_Arange} function with MCA.
-The advantage is that it is easy to set up since it requires one extra line in the exclusion file.
-% However, the same kind of problem may appear somewhere else
-% because, as we have seen, the operations being evolved are elementary.
-Therefore, the chances that developers reproduce the same pattern are very probable.
-The second solution is to ensure that the Full MCA mode preserves the exact operations.
-% This solution has the advantage of not worrying about which functions should be instrumented or not with MCA, but it is hard to achieve it in practice.
-Indeed, we rely on the MCA implementation provided by Verificarlo that uses an internal precision to add the random perturbation that is higher than the working precision for applying the random noise.
-Verificarlo then rounds the result to the working precision before returning it, so any residual noise lower than the working precision is lost.
-% Keeping track of that noise would require recording each intermediate computation in a shadow memory or keeping a tag about their exactness.
-% \Yohan{This idea emerged by discussing with Verificarlo's team. 
-% I must find a way to express that and not give the impression that we discovered or suggest it.}
-% This option would require more extra works than the first one but would ensure more consistent results.
+% data manipulated by scientific applications include a large variety of
+% mathematical objects beyond scalar values. Indeed, scientific visualization
+% \gkmod{}{Note: You kind of jump right in to this section. Visualization of
+% what in particular? Why do we want (need?) to visualize this sort of data?}
+% covers a wide range of numerical simulation domains, from general-purpose
+% numerical visualization with tools such as VTK~\cite{schroeder2000visualizing}
+% to topological data analysis~\cite{tierny2018topological}, including
+% matrix~\cite{wu2008matrix} or tensor~\cite{kindlmann2006diffusion}
+% visualization. To be able to visualize those objects is crucial for the
+% practitioner as information about the structure of the object may be as
+% important as the basic elements that constitute it (i.e. vectors or matrices).
+% Despite the large number of existing tools to identify numerically unstable
+% sections of source code, few allow the user to have a global view of the
+% numerical precision of their computations or to compare several executions of
+% the same program under various perturbations.
+
+% Veritracer~\cite{chatelain2018veritracer} was the first tool to propose an
+% embedded visualizer of numerical stability over the execution of C, C++, and
+% Fortran code. Veritracer extends Verificarlo~\cite{verificarlo} with
+% contextual information about traced variables, which allows the user to
+% identify instabilities quickly. However, Veritracer neither offers a dynamic
+% interface nor includes information about high-level structures such as
+% \texttt{struct} or \texttt{array}. FPAvizual~\cite{gu2014fpavisual} visualizes
+% the effects of floating-point arithmetic but only for educational purposes and
+% so does not target computational intensive applications\gkmod{}{Q: What does
+% this mean?}. Anteater~\cite{faust2019anteater} proposes a visualizer for
+% Python code, but as mentioned previously, it only deals with native Python
+% types, and the user needs to select variables to trace manually. Anteater
+% provides an insightful reflection around visual debugging beyond
+% floating-point analysis, which has inspired the design of \pytracer's
+% visualization interface.
+
+% Through our analysis of SciPy and Scikit-learn, we demonstrated \pytracer's
+% scalability, automaticity, and applicability to any Python program. The
+% relatively low instrumentation overhead of $3.5\times$ on average enables the
+% analysis of real applications. \pytracer's instrumentation is fully automatic
+% and does not require manual intervention from the user. \pytracer works on any
+% Python libraries, with any data format supported by Pickle and any numerical
+% noise model.
+
+% \pytracer is the first tool to enable a systematic numerical analysis of
+% Python codes. Existing tools focus on traditional languages of the HPC
+% community such as C, C++, and FORTRAN. However, Python's high-level
+% abstraction allows for quickly developing applications while maintaining high
+% performance thanks to specialized libraries such as NumPy. Therefore,
+% \pytracer meets the numerical analysis needs of an ever-increasing number of
+% applications.
+
+% Furthermore, \pytracer allows users to pinpoint numerical instabilities root
+% causes precisely by working at the function level. Indeed, evaluating the
+% numerical stability is complex since calculations are strongly correlated
+% between them. The instrumentation at the function level limits the size of the
+% traces since only inputs and outputs of a function are dumped. It moreover
+% decreases the overhead of the instrumentation and helps the user to identify
+% instabilities quickly. Working at function level is thus a suitable compromise
+% between (1) analyzing at the floating-point operation level and (2) user debug
+% prints. (1) Indeed, the fine-grained analysis is costly and hard to analyze
+% due to the large amount of computations evolved in HPC codes. It overwhelms
+% the user with too much information, making analysis more difficult but can be
+% interesting at the final step of the understanding. (2) Looking at
+% intermediate results through print statements focuses on valuable information
+% (like residuals or norms) but may miss numerically unstable functions
+% unsuspected by the developer. Finally, the SciPy environment wraps a lot of
+% computation kernels written in C, like BLAS or LAPACK. By working at function
+% level, \pytracer allows the user to evaluate the numerical precision of such
+% kernels and their impact on the code without getting deep into technical
+% implementation aspects.
+
+% Python is a popular language to prototype proof-of-concept. Integrating
+% \pytracer at early stages of the development cycle allows identifying
+% numerical instabilities to write code of better quality. \pytracer's
+% automaticity facilitates the usage and enables its integration in unit
+% testing. It can be for example used in a non-regression test to ensure that
+% the numerical quality of a calculation is not degraded by updates. Moreover,
+% the Plotly dashboard offers a quick visualization to analyze more finely the
+% potential issues.
+
+% \pytracer can also be useful to select the hyperparameters of a code, as it is
+% the case in machine learning. Indeed, we find many cases in the literature
+% where users explore a range of hyperparameters to select the ones giving the
+% best scores. With \pytracer, the user has a practical way to quantify the
+% numerical quality and to understand why hyperparameters lead to unstable
+% outputs, instead of tweaking hyperparameters to make solvers converge,
+
+% The visualization permits a global view of the code and to understand
+% interactions between computations. The Plotly dashboard help to easily
+% navigate through the code. It moreover removes the need for ad-hoc scripts to
+% visualize data. Finally, the dashboard can be extended to support other data
+% format to visualize. \pytracer currently supports n-dimensional NumPy arrays
+% as well as native Python data.
+
+% As we showed in Section~\ref{sec:impact_mca_modes}, using Full MCA mode leads
+% to runtime errors that have a considerable impact on the proper functioning of
+% the execution. This is unfortunate since these errors do not reflect actual
+% numerical errors but errors related to perturbations that should not occur.
+% Conversely, RR mode is far more conservative since it preserves exact
+% operations and is easier to use even though it does not simulate all
+% perturbations. From our experiments, we do not recommend the Full MCA mode for
+% now and more researches are needed to help fixing issues we encountered.
+
+% Fixing this issue would enable the study of catastrophic cancellations, which
+% are common sources of numerical errors. In addition to the runtime errors it
+% raises, mismatching shapes is also a problem when aggregating traces as
+% \pytracer will not compute statistics for a set of arrays with different
+% shapes \tristan{So do you conclude that Full MCA is not usable while RR is? If
+% so, you should recommend to use Pytracer with RR only.} \tristan{are you still
+% talking about Full MCA here? if not, make another paragraph. If so, make it
+% clearer.}. Two solutions exist to overcome this issue: the first is not to
+% instrument the \texttt{PyArray\_Arange} function with MCA. The advantage is
+% that it is easy to set up since it requires one extra line in the exclusion
+% file. However, the same kind of problem may appear somewhere else because, as
+% we have seen, the evolved operations are elementary. Therefore, the chances
+% that developers reproduce the same pattern are very probable. Therefore, the
+% second solution is to ensure that the Full MCA mode preserves the exact
+% operations. This solution has the advantage of not worrying about which
+% functions should be instrumented or not with MCA, but it is hard to achieve it
+% in practice. Indeed, we rely on the MCA implementation provided by Verificarlo
+% that uses an internal precision to add the random perturbation that is higher
+% than the working precision for applying the random noise. Verificarlo then
+% rounds the result to the working precision before returning it, so any
+% residual noise lower than the working precision is lost. Keeping track of that
+% noise would require recording each intermediate computation in a shadow memory
+% or keeping a tag about their exactness. This option would require more extra
+% works than the first one but would ensure more consistent results. \tristan{I
+% find this paragraph too verbose, you should contract it to a few key
+% sentences.}
+
+% \tristan{The following paragraphs are future work, not discussion. I'd remove
+% them and flesh out the discussion from the ideas mentioned in the current 3rd
+% paragraph}
+
+% Also, we would like to extend the post-process analysis to aggregate traces
+% where the execution flow path diverges. Therefore, a posteriori reconstruction
+% is challenging as one must precisely identify the flow path taken and find
+% synchronization points to pursue the analysis. We retrieve, for example, this
+% divergence behavior in two general classes of numerical schemes: iterative
+% methods and optimization processes. One solution is to integrate methods used
+% in code coverage analysis to keep track of flow paths taken and the
+% backtraces. However, this would increase the complexity of the postprocess
+% analysis as well as an extra slowdown factor. However, by coupling the Gantt
+% chart with static analysis, \pytracer would catch some divergence patterns
+% occurring within a function. Indeed, by instrumenting at the function level,
+% \pytracer views the function's callees (i.e., the functions called within a
+% function) and thus should partially detect flow divergences.
+
+% By design principle, \pytracer is flexible on the noise model used, although
+% we only tested it with the MCA model in our experiments. Nevertheless, we
+% would like to compare different models against MCA in future works to see the
+% resulting differences. Furthermore, we would like to test \pytracer on
+% parallel codes.
+
+% Finally, we would extend \pytracer to instrument elementary arithmetic
+% operations which can be helpful to more profound analyses. We nevertheless
+% believe that instrumentation at the function level presents two advantages: it
+% first limits the size of the traces since only inputs and outputs of a
+% function are saved instead of a full report which, on the one hand, decreases
+% the overhead of the instrumentation and, on the other hand, help the user to
+% identify instabilities quickly. Indeed, full reporting can overwhelm the user
+% with too much information, making analysis more difficult at first. Second,
+% the analysis at fine granularity is interesting at the final step of the
+% understanding. Such an analysis would require a different instrumentation
+% approach by, for example, working at the Abstract Syntax Tree (AST) level
+% since it is trivial to get it in Python. Moreover, working at the AST level
+% allows doing dependency analysis. Another extension would be to extract and
+% replay a function, in the same vein as the CERE tool does but for Python, and
+% to use an AST instrumentation to analyze the numerical quality of elementary
+% operations step by step within the fuzzy environment.
+
+% \pytracer is a tool for visualizing the numerical quality of function
+% inputs/outputs over time. It generates numerical traces that are aggregated in
+% postprocessing to measure numerical discrepancies between executions.
+% \pytracer does not assume the noise model used to estimate uncertainties but
+% has been tested with the MCA through the fuzzy ecosystem on two broadly used
+% scientific libraries for Python with partial success.
+
+% We demonstrated the Pytracer's capabilities to analyze intensively used Python
+% libraries such as NumPy or Scikit-learn, such as 
+% 1) Scalability. The low instrumentation overhead of 3.5x enables analysis of
+%    real applications and permits having a global representation of the
+%    numerical quality of an application. 
+% 2) Automaticity. Pytracer instrumentation is fully automatic and does not
+%    require manual intervention from the user, allowing the instrumentation of
+%    the NumPy, SciPy and Scikit-learn libraries. // that cumulate 5600 and 2043
+%    pure Python functions and classes. 
+% 3) Agnosticity. Pytracer works on any python libraries, with any data format
+%    supported by pickle, and any numerical noise model flavor.
+
+% Pytracer is the first tool to bring numerical analysis of Python codes
+% available to everyone. Indeed, existing tools developed in the last years
+% focused on traditional HPC languages community such as C,C++, and FORTRAN.
+% However, the Python high-level abstraction allows you to quickly develop
+% applications while maintaining high performance with the help of specialized
+% libraries like NumPy. Therefore, it is quite natural to see more fields
+% systematically using Python, as is the case in neuroimaging. Thus, Pytracer
+% meets the numerical analysis needs of an ever increasing number of
+% applications writing in Python.
+
+% By working at function level, Pytracer allows users to precisely pinpoint
+% numerical instabilities root causes. Furthermore, the automaticity facilitates
+% the usage and its integration in unit testing. Hence, instead of tweaking
+% hyperparameters to make solvers converging, the user has a practical way with
+% Pytracer to quantify the numerical quality of its computations.
+
+% As we showed in section~\ref{sec:impact_mca_modes}, using the Full MCA mode
+% leads to runtime errors that have a considerable impact on the proper
+% functioning of the execution, which is unfortunate since these errors do not
+% reflect actual numerical errors but errors related to perturbations that
+% should not occur. Fixing this misbehavior would greatly help use Full MCA mode
+% since this mode allows simulating catastrophic cancellations, which are
+% familiar sources of numerical errors. By preserving exact operations, RR mode
+% is far more conservative and so easy to use even though it does not simulate
+% all perturbations that might be encountered.
+
+% Also, using a post-process analysis to aggregate traces, \pytracer falls in
+% the same pitfalls as veritracer and is limited to aggregate traces where the
+% execution flow path extremely diverges. Therefore, a posteriori reconstruction
+% is challenging as one must precisely identify the flow path taken and find
+% synchronization points to pursue the analysis. We retrieve, for example, this
+% divergence behavior in two general classes of numerical schemes: iterative
+% methods and optimization processes. One solution to overcome this issue is to
+% integrate methods used in code coverage analysis to keep track of flow paths
+% taken and the backtraces. However, this would increase the complexity of the
+% postprocess analysis as well as an extra slowdown factor. However, by coupling
+% the Gantt chart with static analysis, \pytracer would catch some divergence
+% patterns occurring within a function. Indeed, by instrumenting at the function
+% level, \pytracer views the function's callees (i.e., the functions called
+% within a function) and thus should partially detect flow divergences.
+
+% By design principle, \pytracer is flexible on the noise model used, although
+% we only tested it with the MCA model in our experiments. Nevertheless, we
+% would like to compare different models against MCA in future works to see the
+% resulting differences. In particular, although \pytracer only works on a
+% sequential application for the moment, it can be used to analyze parallel
+% sections internal to a function. The only restriction is that the section does
+% not call other functions traced by \pytracer; we would fall into the previous
+% issue of divergence if it would not be the case. Since \pytracer only cares
+% about inputs and outputs of a function, the order of internal operations is
+% transparent for it and thus should be able to handle those cases.
+
+% Finally, \pytracer does not instrument elementary arithmetic operations, and
+%it can be a barrier to more profound analysis. Such an analysis would require a
+%different instrumentation approach by, for example, working at the Abstract
+%Syntax Tree (AST) level since it is trivial to get it in Python. An ideal way
+%to do that would be to extract and replay a function, in the same vein as the
+%CERE~\cite{castro2015cere} tool does but for Python, and use an AST
+%instrumentation to analyze the numerical quality of elementary operations step
+%by step within the fuzzy environment. Lastly, AST analysis can serve as a basis
+%for finding relationships between variables, valuable information for the user.
+
+% In addition to the runtime errors it raises, mismatching shapes is also a
+% problem when aggregating traces as PyTracer will not compute statistics for a
+% set of arrays with different shapes. Two solutions exist to overcome this
+% issue: the first is not to instrument the \texttt{PyArray\_Arange} function
+% with MCA. The advantage is that it is easy to set up since it requires one
+% extra line in the exclusion file. However, the same kind of problem may appear
+% somewhere else because, as we have seen, the operations being evolved are
+% elementary. Therefore, the chances that developers reproduce the same pattern
+% are very probable. The second solution is to ensure that the Full MCA mode
+% preserves the exact operations. This solution has the advantage of not
+% worrying about which functions should be instrumented or not with MCA, but it
+% is hard to achieve it in practice. Indeed, we rely on the MCA implementation
+% provided by Verificarlo that uses an internal precision to add the random
+% perturbation that is higher than the working precision for applying the random
+% noise. Verificarlo then rounds the result to the working precision before
+% returning it, so any residual noise lower than the working precision is lost.
+% Keeping track of that noise would require recording each intermediate
+% computation in a shadow memory or keeping a tag about their exactness.
+% \Yohan{This idea emerged by discussing with Verificarlo's team. I must find a
+% way to express that and not give the impression that we discovered or suggest
+% it.} This option would require more extra works than the first one but would
+% ensure more consistent results.
 
@@
 
-% \tristan{I moved this from the opening of Section 4, as this reads more like a summary of \pytracer's features than an experiment description.
-It should be refactored in 1-2 paragraphs summarizing the main properties of \\pytracer.}
-
-Evaluating the numerical stability of scientific Python programs is a tedious task that requires substantial expertise.
-Automatic tools to help users understand the behavior of their code are therefore crucial.
-In this perspective, \pytracer is the first tool to offer a complete framework for analyzing and visualizing the numerical stability of Python codes.
-It works by automatically instrumenting Python libraries to produce numerical traces visualized through an interactive Plotly Dash server.
-\pytracer does not require manual code modification, and we tested it with major scientific libraries such as NumPy, SciPy, and Scikit-learn.
-Our results show that \pytracer is scalable, with an average instrumentation slowdown of $3.5\times$.
-Moreover, \pytracer's visualization interface remains responsive even with traces of up to 1TB.
-In our experiments, \pytracer enabled the systematic evaluation of 40 examples from the SciPy and scikit-learn libraries.
-
-In future work, we plan to extend the post-processing analysis to aggregate traces when the execution flow path diverges by leveraging techniques used in code coverage analysis.
-Moreover, we would like to extend \pytracer to instrument elementary arithmetic operations which can be helpful to more profound analyses.
-Finally, although \pytracer supports multiple noise models, we only tested it with Monte Carlo Arithmetic.
-Therefore, we would like to compare different models against MCA.
-\pytracer is available at \href{https://github.com/big-data-lab-team/pytracer}{github://big-data-lab-team/pytracer} under MIT License.
+% \tristan{I moved this from the opening of Section 4, as this reads more like a
+% summary of \pytracer's features than an experiment description. It should be
+% refactored in 1-2 paragraphs summarizing the main properties of \\pytracer.}
+
+Evaluating the numerical stability of scientific Python programs is a tedious
+task that requires substantial expertise. Automatic tools to help users
+understand the behavior of their code are therefore crucial. In this
+perspective, \pytracer is the first tool to offer a complete framework for
+analyzing and visualizing the numerical stability of Python codes. It works by
+automatically instrumenting Python libraries to produce numerical traces
+visualized through an interactive Plotly Dash server. \pytracer does not require
+manual code modification, and we tested it with major scientific libraries such
+as NumPy, SciPy, and Scikit-learn. Our results show that \pytracer is scalable,
+with an average instrumentation slowdown of $3.5\times$. Moreover, \pytracer's
+visualization interface remains responsive even with traces of up to 1TB. In our
+experiments, \pytracer enabled the systematic evaluation of 40 examples from the
+SciPy and scikit-learn libraries.
+
+In future work, we plan to extend the post-processing analysis to aggregate
+traces when the execution flow path diverges by leveraging techniques used in
+code coverage analysis. Moreover, we would like to extend \pytracer to
+instrument elementary arithmetic operations which can be helpful to more
+profound analyses. Finally, although \pytracer supports multiple noise models,
+we only tested it with Monte Carlo Arithmetic. Therefore, we would like to
+compare different models against MCA. \pytracer is available at
+\href{https://github.com/big-data-lab-team/pytracer}{github://big-data-lab-team/pytracer}
+under MIT License.
 
@@
 \vskip -2\baselineskip plus -1fil
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/yohan.jpg}}]{Yohan Chatelain}
-    received his Ph.D. degree from the University of Paris-Saclay
-    (UVSQ), Versailles, France in 2019.
-    He is a postdoctoral researcher in the Big Data Infrastructures for
-    Neuroinformatics lab at the University of Concordia, Montreal, Canada. His
-    research topics include computer arithmetic, high-performance computing, and
-    reproducibility. Yohan aims at democratizing the use of
-    the analysis of stability for scientific computing codes through automatic tools to
-    improve numerical quality. 
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/yohan.jpg}}]{Yohan
+        Chatelain} received his Ph.D. degree from the University of Paris-Saclay
+    (UVSQ), Versailles, France in 2019. He is a postdoctoral researcher in the
+    Big Data Infrastructures for Neuroinformatics lab at the University of
+    Concordia, Montreal, Canada. His research topics include computer
+    arithmetic, high-performance computing, and reproducibility. Yohan aims at
+    democratizing the use of the analysis of stability for scientific computing
+    codes through automatic tools to improve numerical quality. 
 \end{IEEEbiography}
@@
 \vskip -2\baselineskip plus -1fil
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/NigelPhoto.png}}]{Nigel Yong Sao Young}
-    was born in Mauritius Island. He is a recent Computer
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/NigelPhoto.png}}]{Nigel
+        Yong Sao Young} was born in Mauritius Island. He is a recent Computer
     Science graduate at Concordia University. He is currently working on his
@@
 \vskip -2\baselineskip plus -1fil
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/greg_kiar.png}}]{Gregory Kiar}
-    is a research scientist at the Child Mind Institute. Throughout his degrees
-    in Biomedical Engineering, Greg has developed techniques to study biosignal
-    data, a turn-key tool that allows researchers to generate maps of brain
-    connectivity from diffusion MRI data, and techniques to assess and improve
-    the stability of research in neuroscience. 
-    Greg’s research bridges the
-    fields of numerical analysis and brain imaging to evaluate and improve the
-    trustworthiness of techniques used to study the brain. 
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/greg_kiar.png}}]{Gregory
+        Kiar} is a research scientist at the Child Mind Institute. Throughout his
+    degrees in Biomedical Engineering, Greg has developed techniques to study
+    biosignal data, a turn-key tool that allows researchers to generate maps of
+    brain connectivity from diffusion MRI data, and techniques to assess and
+    improve the stability of research in neuroscience. Greg’s research bridges
+    the fields of numerical analysis and brain imaging to evaluate and improve
+    the trustworthiness of techniques used to study the brain. 
 \end{IEEEbiography}
@@
 \vskip -2\baselineskip plus -1fil
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/glatard_tristan.jpg}}]{Tristan Glatard}
-    is Associate Professor in the Department of Computer Science and Software
-    Engineering at Concordia University in Montreal, and Canada Research Chair
-    (Tier II) on Big Data Infrastructures for Neuroinformatics. Before that, he
-    was research scientist at the French National Centre for Scientific Research
-    and Visiting Scholar at McGill University. 
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/glatard_tristan.jpg}}]{Tristan
+        Glatard} is Associate Professor in the Department of Computer Science and
+    Software Engineering at Concordia University in Montreal, and Canada
+    Research Chair (Tier II) on Big Data Infrastructures for Neuroinformatics.
+    Before that, he was research scientist at the French National Centre for
+    Scientific Research and Visiting Scholar at McGill University. 
 \end{IEEEbiography}
@@
 
+\appendix
+
+\include{annex}
+
 % that's all folks

### 2022-05-10 IEEEtran/paper.tex
Update for major revision

--- 2022-04-14 IEEEtran/paper-annotated.tex
@@
 
-\definecolor{lightred}{rgb}{1.0,0.6,0.6}
-\definecolor{lightgreen}{rgb}{0.6,1.0,0.6}
-
-\DeclareRobustCommand{\add}[1]{{\sethlcolor{lightgreen}\hl{#1}}}
-\DeclareRobustCommand{\remove}[1]{{\sethlcolor{lightred}\hl{#1}}}
-
-\DeclareRobustCommand{\addCite}[1]{{\sethlcolor{lightgreen}\hl{\mbox{#1}}}}
-\DeclareRobustCommand{\removeCite}[1]{{\sethlcolor{lightred}\hl{\mbox{#1}}}}
+\definecolor{lightred}{rgb}{0.6,0.0,0.0}
+\definecolor{lightgreen}{rgb}{0.8,1.0,0.8}
+
+\DeclareRobustCommand{\add}[1]{#1}
+\DeclareRobustCommand{\remove}[1]{}
+
+\DeclareRobustCommand{\addCite}[1]{\textcolor{lightgreen}{\mbox{#1}}}
 
@@
 valuable in contrast to theoretical approaches based on condition numbers or
-backward error analysis~\addCite{\cite{higham2002accuracy}}, which require detailed modeling of the program and its
-numerical implementation. Similarly, static code analysis techniques~\addCite{\cite{goubault2006static}} hardly
-scale to large code bases, particularly in dynamically-typed languages such as
-Python.
+backward error analysis~\cite{higham2002accuracy}, which require
+detailed modeling of the program and its numerical implementation. Similarly,
+static code analysis techniques~\cite{goubault2006static} hardly scale
+to large code bases, particularly in dynamically-typed languages such as Python.
 
@@
 numerical noise, we experimented primarily with Monte-Carlo Arithmetic (MCA) as
-it is an accurate model for floating-point errors~\addCite{\cite{verificarlo}}.
+it is an accurate model for floating-point errors~\cite{verificarlo}.
 
@@
 variable sampled with MCA.
-Sohier et al.~\cite{sohier2018confidence} recently provided a generalization of
+Sohier et al.~\cite{sohier2021confidence} recently provided a generalization of
 this formula to include confidence intervals.
@@
 \pytracer stores traces in the pickle format, a binary format to serialize
-Python objects. The main advantages of the pickle format compared to other
-serialization approaches such as marshal or JSON are its ability to serialize
-most Python objects and its native compression.  In addition, pickle writes
+Python objects. The main advantage of the pickle format compared to other
+serialization approaches such as marshal or JSON is the ability to serialize
+most Python objects with a native compression. In addition, pickle writes
 Python objects sequentially, which preserves the temporal ordering required by
@@
 single-threaded and that the control flow does not depend on a random state.
-\add{Therefore, \mbox{\pytracer} cannot merge traces resulting from a different control flow path
-    and will stop the parsing when encountering one.}
-
-\begin{figure}
+\add{Therefore, \mbox{\pytracer} cannot merge traces resulting from a different
+    control flow path and stops the parsing when encountering one.}
+
+\begin{figure*}
     \centering
-    \includegraphics[width=\columnwidth]{figure/pytracer_layout.pdf}
+    \includegraphics[width=0.75\linewidth]{figure/pytracer_layout.pdf}
     \caption{Pytracer visualization layout.}
     \label{fig:visu-layout}
-\end{figure}
+\end{figure*}
 
@@
 their respective GitHub repositories. We traced each example five times, having
-activated MCA in the Python interpreter \add{as well as} BLAS, LAPACK, NumPy, SciPy, and
-scikit-learn. \add{Only instrumented the Python interpreter would lead to
-    only perturbe pure Python floating-point operations and thus to miss
-    operations in compiled codes (i.e. Cython and shared libraries).}
-\hl{We repeated the experiment with two MCA modes, Random Rounding
-    (RR) and Full MCA, resulting in 2 experiments for each example}. We used the
-default virtual precision in Verificarlo, namely 24 bits for single-precision
-floating-point values and 53 bits for double-precision values, which simulates
-machine error. We used Python-3.8.5, NumPy-1.19.1, SciPy-1.5.4, and
-scikit-learn-0.23.2.
-
-\subsection{Results overview}
+activated MCA in the Python interpreter \add{as well as} BLAS, LAPACK, NumPy,
+SciPy, and scikit-learn. \add{Only instrumented the Python interpreter would
+    lead to only perturbe pure Python floating-point operations and thus to miss
+    operations in compiled codes (i.e. Cython and shared libraries).} We used the default virtual
+precision in Verificarlo, namely 24 bits for single-precision floating-point
+values and 53 bits for double-precision values, which simulates machine error.
+We used Python-3.8.5, NumPy-1.19.1, SciPy-1.5.4, and scikit-learn-0.23.2.
+
+\add{Monte Carlo Arithmetic samples the floating-point variability of a given
+    program, and hence the more MCA repetitions we have, the more accurate will be
+    the sampling distribution. In theory, an infinite number of MCA repetitions
+    should give the exact distribution. While in practice low sample size (3$\simeq$30)
+    can give a good estimate, the issue is to capture "rare events" that could make the
+    computation strongly diverge from the mean. For now, determining the number of
+    MCA samples to use is still an open research question. 
+    Recent theoretical works}~\cite{sohier2021confidence}
+\add{on the significant digits computation allow computing an associated
+    confidence interval depending on the sample size and the underlying distribution of the outputs.}
+
+% \subsection{Results overview}
+
+% Table~\ref{tab:pytracer_results_summary} summarizes \pytracer's outcome on SciPy
+% and scikit-learn examples. Columns \textit{trace} and \textit{parse} report on
+% the tracing and aggregation steps with three possible outcomes: 1) green for
+% success, meaning that the execution ended well and no issues were raised by the
+% application, 2) red for numerical error in the application, meaning that the
+% execution raised a Python error before the end, and 3) orange for errors due to
+% the fuzzy noise injection that are not considered numerical errors, meaning that
+% the execution raised a Python error but due to a perturbation that should not
+% have been introduced (i.e. a floating-point value representing an integer).
+% Overall, the tracing and parsing of SciPy and scikit-learn examples in Random
+% Rounding mode was entirely successful for 32/40 examples and showed an average
+% precision loss of 8 bits. The remaining examples failed due to numerical errors
+% in the libraries, which we discuss hereafter. The instrumentation with Full MCA
+% is more invasive and reduced the number of successful executions to 12/40. Among
+% the 28/40 failed executions, one failed due to an actual numerical error
+% (\texttt{Bayesian Ridge Regression} example) and the other ones failed due to
+% perturbations that should not have been introduced.
+
+% Column \textit{sigbits} in Table~\ref{tab:pytracer_results_summary} summarizes
+% the precision for the main outputs of SciPy and scikit-learn examples. We
+% measured the precision in significant bits on the final primary example output
+% by taking the element-wise mean for non-scalar values and, if the example
+% produces many outputs, the average value among all of them. The numerical
+% quality across all examples varies from 0 to 52, with an average of 44
+% significant bits. For both modes, we note that only two examples failed due to a
+% numerical error (\texttt{face\_recognition} for RR and \texttt{Bayesian Ridge
+%     Regression} for Full MCA).
+
+\begin{table*}[]
+    \centering
+    \normalsize
+    \begin{subfigure}[t]{\linewidth}
+        \centering
+        \begin{tabular}{|lll|c|c|c|}
+            \hline
+            \multicolumn{3}{|c}{ \multirow{2}{*}{Application} }                 & \multicolumn{3}{|c|}{Random Rounding (RR)}                                                                                                                         \\
+            \cline{4-6}
+                                                                                &                                                                           &                                                          & trace  & parse    & sigbits \\
+            \hline
+            \multicolumn{1}{|c|}{ \multirow{20}{2em}{ \rotatebox{90}{SciPy} } } & 
+            \multicolumn{1}{c|}{ \multirow{3}{2em}{ \rotatebox{90}{FFT} }}      & \discreteCosineRF                                                         & \valid                                                   & \valid & \s{52}             \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \fftOneDRf                                               & \valid & \valid   & 41      \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \fftTwoDRf                                               & \valid & \valid   & \s{52}  \\
+            \cline{2-6}
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{  \multirow{5}{*}{ \rotatebox{90}{Interpolation} } }
+                                                                                & \interOneDRf                                                              & \valid                                                   & \valid & 51                 \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \multiRf                                                 & \valid & \valid   & \s{51}  \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \bsplineRf                                               & \valid & \valid   & 10      \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \splineOneDRf                                            & \valid & \cross   & \s{52}  \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \splineTwoDRf                                            & \valid & \valid   & 10      \\
+            \cline{2-6}
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{ \multirow{12}{2em}{ \rotatebox{90}{Optimization} } }
+                                                                                & \bfgsRf                                                                   & \valid                                                   & \valid & \s{48}             \\
+            \cline{3-6}
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \globalRf                                                & \valid & \cross   & 17      \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & | SHGO\footnote{Simplicial Homology Global Optimization} & \na    & \na      & \s{25}  \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & | Dual Annealing                                         & \na    & \na      & 4       \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & | Differential Evolution                                 & \na    & \na      & \s{0}   \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & | Basin Hopping                                          & \na    & \na      & 40      \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & | SHGO Sobol                                             & \na    & \na      & \s{45}  \\
+            \cline{3-6}
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \slsqpRf                                                 & \valid & \valid   & 45      \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \lsmRf                                                   & \valid & \valid   & \s{48}  \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \nelderRf                                                & \valid & \valid   & 44      \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \ncgRf                                                   & \valid & \valid   & \s{48}  \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \rootRf                                                  & \valid & \cross   & 52      \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \rootLargRf                                              & \valid & \cross   & \s{29}  \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \rootLargePredRf                                         & \valid & \cross   & 42      \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \trustExactRf                                            & \valid & \valid   & \s{48}  \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \trustTruncRf                                            & \valid & \valid   & 48      \\
+            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \trustNCGRf                                              & \valid & \valid   & \s{52}  \\
+            \hline
+            \multicolumn{2}{|c|}{ \multirow{20}{2em}{ \rotatebox{90}{Scikit-learn} } }
+                                                                                & \AdaboostRf                                                               & \valid                                                   & \valid & 48                 \\
+            \cline{3-6}
+            \multicolumn{2}{|c|}{}                                              & \brrRf                                                                    & \valid                                                   & \valid & \s{25}             \\
+            \multicolumn{2}{|c|}{}                                              & | $1^{st}$ dataset                                                        & \na                                                      & \na    & 25                 \\
+            \multicolumn{2}{|c|}{}                                              & | $2^{nd}$ dataset                                                        & \na                                                      & \na    & \s{nan}            \\
+            \cline{3-6}
+            \multicolumn{2}{|c|}{}                                              & \onlineClassifierComparisonRf                                             & \valid                                                   & \valid & 20                 \\
+            \multicolumn{2}{|c|}{}                                              & \kmeansRf                                                                 & \valid                                                   & \valid & \s{52}             \\
+            \multicolumn{2}{|c|}{}                                              & \covarianceRf                                                             & \valid                                                   & \cross & 48                 \\
+            \multicolumn{2}{|c|}{}                                              & \decisionRf                                                               & \valid                                                   & \valid & \s{50}             \\
+            \multicolumn{2}{|c|}{}                                              & \digitsRf                                                                 & \valid                                                   & \valid & 52                 \\
+            \multicolumn{2}{|c|}{}                                              & \faceRf                                                                   & \cross                                                   & \valid & \s{-}              \\
+            \multicolumn{2}{|c|}{}                                              & \penaltyRf                                                                & \valid                                                   & \valid & -                  \\
+            \multicolumn{2}{|c|}{}                                              & \lassoRf                                                                  & \valid                                                   & \valid & \s{48}             \\
+            \multicolumn{2}{|c|}{}                                              & \hyperplaneRf                                                             & \valid                                                   & \valid & 3                  \\
+            \multicolumn{2}{|c|}{}                                              & \mnistRf                                                                  & \valid                                                   & \valid & \s{43}             \\
+            \multicolumn{2}{|c|}{}                                              & \multitaskRf                                                              & \valid                                                   & \valid & 50                 \\
+            \multicolumn{2}{|c|}{}                                              & \ompRf                                                                    & \valid                                                   & \valid & \s{52}             \\
+            \multicolumn{2}{|c|}{}                                              & \pcaRf                                                                    & \valid                                                   & \valid & 48                 \\
+            \cline{3-6}
+            \multicolumn{2}{|c|}{}                                              & \robustRf                                                                 & \valid                                                   & \valid & \s{50}             \\
+            \multicolumn{2}{|c|}{}                                              & | Linear                                                                  & \na                                                      & \na    & 48                 \\
+            \multicolumn{2}{|c|}{}                                              & | RANSAC                                                                  & \na                                                      & \na    & \s{50}             \\
+            \cline{3-6}
+            \multicolumn{2}{|c|}{}                                              & \toyRf                                                                    & \valid                                                   & \valid & 35                 \\
+            \cline{3-6}
+            \multicolumn{2}{|c|}{}                                              & \svmRf                                                                    & \valid                                                   & \valid & \s{43.5}           \\
+            \multicolumn{2}{|c|}{}                                              & | Non-weighted                                                            & \na                                                      & \na    & 43                 \\
+            \multicolumn{2}{|c|}{}                                              & | Weighted                                                                & \na                                                      & \na    & \s{44}             \\
+            \cline{3-6}
+            \multicolumn{2}{|c|}{}                                              & \tomographyRf                                                             & \valid                                                   & \cross & -                  \\
+            \multicolumn{2}{|c|}{}                                              & \weightedRf                                                               & \valid                                                   & \valid & \s{44}             \\
+            \hline
+        \end{tabular}
+    \end{subfigure}
+    \caption{\pytracer execution summary on SciPy and Scikit-learn examples.
+        % \tristan{Replace FFT with SciPy FFT, Interpolation with SciPy
+        % Interpolation and Optimization with SciPy Optimization, or add a SciPy
+        % header to these rows.} \tristan{Nitpick: you could add a color scheme
+        % to sigbits (for instance shades of blue), to make the column more
+        % easily readable.} \\
+        \emph{trace}: outcome of \pytracer tracing, \emph{parse}: outcome of
+        \pytracer trace parsing and aggregation, \emph{result}: precision for
+        main outputs in significant bits. \valid: successful run, \remove{\warn: error
+            from invalid noise injection,} \cross: numerical error or divergent
+        traces. \textit{nan} stands for (\texttt{Not-A-Number}). Example names
+        are linked to their source code.}
+    \label{tab:pytracer_results_summary}
+\end{table*}
+
+\subsection{Pytracer is applicable to scientific computation libraries of reference}
 
@@
 and then trains an SVM classifier to predict the name associated with a face.
-This example is the only one to raise an error with RR due to the
+\add{When executing within fuzzy environment, this example crashed with the following
+    Python error raised: \texttt{"SVD did not converge"}.}
+This example is the only one to raise an error due to the
 non-convergence of the Singular Value Decomposition (SVD) performed in the PCA.
-
-In this example, the PCA uses the Randomized SVD~\cite{halko2011finding} method
+The PCA uses the Randomized SVD~\cite{halko2011finding} method
 that first computes a low-rank approximation of the input matrix using a
-stochastic algorithm and then uses this approximation as input for the SVD. The
-example raises an error during the computation of the SVD. The
-\texttt{randomized\_svd} scikit-learn function uses the Divide \& Conquer SVD
-method \texttt{gesdd} mentioned previously. Replacing \texttt{gesdd} for
-\texttt{gesvd} solves the SVD convergence issue.
+stochastic algorithm and then uses this approximation as input for the SVD. 
+\add{When walking through the code with PyTracer, we see that}
+the \texttt{randomized\_svd} scikit-learn function uses the Divide \& Conquer SVD
+method \texttt{gesdd}. The LAPACK library has two main methods for computing the SVD:
+\texttt{gesdd} and \texttt{gesvd}. The former uses a Divide \& Conquer approach,
+while the latter uses a QR decomposition. While both methods are expected to
+have the same accuracy~\cite{nakatsukasa2013stable}, the Divide \& Conquer
+makes the SVD to not converge with MCA.
+
+Replacing \texttt{gesdd} for \texttt{gesvd} solves the SVD convergence issue.
+\pytracer allows to quickly visualize the new precision of the result.
 Figure~\ref{fig:randomized_svd_S} shows the precision of the eigenvalues
-computed with gesvd \add{in single precision}, which varies between 15 and 20 significant bits out of the
-24 available in single precision. The classifier metrics (precision, recall,
-F1-score, and support) are identical to the IEEE execution for all MCA samples.
+computed displayed in decreasing order with \texttt{gesvd} \add{in single precision}, 
+which varies between 15 and 20
+significant bits out of the 24 available in single precision. The classifier
+metrics (precision, recall, F1-score, and support) are identical to the IEEE
+execution for all MCA samples. \add{We can note that even with using the \texttt{gesvd},
+    the precision of the singular values (vectors) is not uniform. 
+    Indeed, we can see that the precision of the lowest singular values (vectors) decreases 
+    until reaching 0 significant bits.}
+
+The second example, compares a Bayesian Ridge Regression (BRR) to the Ordinary
+Least Squares (OLS) estimator on a synthetic dataset and for one-dimensional
+regression using polynomial feature expansion. Although the example does not
+raise a runtime error, the regression coefficients computed from the fitting are
+non-significant. \pytracer traces reveal that the SVD solver used is the root
+cause for this error. \add{Indeed, the BayesianRidge model first computes an SVD
+    before iteratively updating the coefficients until reaching the convergence
+    criterion. However, PyTracer reveals an issue in the singular values computed.}
+\add{We can see on Figure}~\ref{fig:BRR_svd} \add{that the last singular values is
+    \texttt{NaN} due to numerical error during the SVD although the remaining
+    singular values exhibit high numerical precision (between 44 and 50 bits).
+    Surprinsingly, this \texttt{NaN} value does not raise issue and is silently
+    propagated. Indeed, the stopping criterion compares that the sum of the absolute
+    differences between coefficients of two successive iterations but coefficients
+    contain \texttt{NaN} since they are computed from singular values. Hence, the
+    following right condition is never met \texttt{if iter\_!=0 and np.sum(np.abs(coef\_old\_-coef\_))<self.tol:} since the comparison with a
+    \texttt{NaN} is always false.}
+
+\add{The OLS uses the Least Square to fit the model. PyTracer shows that the
+    coefficients fitted are \texttt{NaN} values. By looking at the callgraph, we can
+    see that the scipy calls the \texttt{lstsq} method from the
+    \texttt{scipy.linalg} package which uses the \texttt{gelsd} LAPACK function.
+    Figure}~\ref{fig:OLS_svd} \add{shows the singular values returned by the
+    \texttt{lstsq} method shows that one singular value has a \texttt{NaN} value
+    that corrupted the calculation of the coefficients. By using the \texttt{gelss},
+    PyTracer shows that the \texttt{NaN} value disapeared from the singular values
+    (fig.}~\ref{fig:OLS_svd_fixed}\add{) and thus does not contaminated the computation of
+    the coefficients that exhibit a precision of 42 bits in average. We can see that
+    the full access to all values computed by the application with PyTracer allows
+    the user to quickly identify the issue.}
 
@@
 
+\clearpage
+\appendix
+
+\include{annex}
+
 % that's all folks

### 2022-05-12 IEEEtran/annex.tex
Add annex

--- 2021-12-10 paper.tex
@@
-\documentclass[11pt]{article}
-\usepackage[margin=0.5in]{geometry}
-\usepackage{todonotes}
-\usepackage{natbib}
-\usepackage{graphicx}
-\usepackage{listings}
-\usepackage{color}
-\usepackage{hyperref}
-\usepackage{multirow}
-\usepackage{pifont}
-\usepackage{xcolor,colortbl}
-\usepackage{hyperref}
-\hypersetup{colorlinks=true,linkcolor=blue!50!black,citecolor=blue!75!black,filecolor=black,urlcolor=blue!75!black}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{xspace}
-\usepackage{makecell}
-\usepackage{ulem} % provides sout
-\usepackage{minted} % Provides listing environment
-\usepackage[htt]{hyphenat}
-\usepackage{subcaption}
-\usepackage{graphicx,import}
-\usepackage{booktabs}
-
-% \usepackage{subfigure}
-
-\newcommand{\tristan}[1]{\color{orange}\textbf{From Tristan:} #1\color{black}\xspace}
-\newcommand{\tristanmod}[2]{\color{orange}\sout{#1} #2\color{black}\xspace}
-\newcommand{\gkmod}[2]{\color{purple}\sout{#1} #2\color{black}\xspace}
-
-\newcommand{\Yohan}[1]{\color{green!75!black}\textbf{Yohan:} #1\color{black}\xspace}
-\newcommand{\cross}[0]{\cellcolor{red!65}\ding{53}}
-\newcommand{\valid}[0]{\cellcolor{green!75!black}\ding{51}}
-\newcommand{\warn}[0]{\cellcolor{orange!75}?}
-\newcommand{\na}[0]{\cellcolor{gray!25}}
-\newcommand{\s}[1]{\cellcolor{cyan!25}#1}
-\newcommand{\scross}[0]{\ding{53}~}
-\newcommand{\svalid}[0]{\ding{51}~}
-\newcommand{\swarn}[0]{?~}
-\newcommand{\pytracer}[0]{PyTracer\xspace}
-
-\setlength{\arrayrulewidth}{0.1pt}
-
-\include{href}
-
-\usepackage{tabularx} % provides tabularx to adjust table column sizes to page size
-% define thickline for use in tables
-\makeatletter
-\newcommand{\thickhline}{%
-    \noalign {\ifnum 0=`}\fi \hrule height 1pt
-    \futurelet \reserved@a \@xhline
-}
-\newcolumntype{"}{@{\hskip\tabcolsep\vrule width 1pt\hskip\tabcolsep}}
-\makeatother
-
-\lstdefinestyle{customPython}{
-  belowcaptionskip=1\baselineskip,
-  breaklines=true,
-  xleftmargin=\parindent,
-  language=Python,
-  showstringspaces=false,
-  basicstyle=\scriptsize\ttfamily,
-  keywordstyle=\bfseries\color[rgb]{0.580, 0.000, 0.827},
-  %{purple!40!lightgray},
-  commentstyle=\itshape\color{green!40!black},
-  identifierstyle=\bfseries\color{cyan!75!black},
-  stringstyle=\color{orange},
-  deletekeywords={double,float},
-  classoffset=1, % starting new class
-  otherkeywords={double,float},
-  morekeywords={double,float},
-  keywordstyle=\bfseries\color{green!55!black},
-  classoffset=0
-}
-
-\lstdefinestyle{customC}{
-  belowcaptionskip=1\baselineskip,
-  breaklines=true,
-  xleftmargin=\parindent,
-  language=C,
-  showstringspaces=false,
-  basicstyle=\scriptsize\ttfamily,
-  keywordstyle=\bfseries\color[rgb]{0.580, 0.000, 0.827},
-  %{purple!40!lightgray},
-  commentstyle=\itshape\color{green!40!black},
-  identifierstyle=\bfseries\color{cyan!75!black},
-  stringstyle=\color{orange},
-  deletekeywords={double,float},
-  classoffset=1, % starting new class
-  otherkeywords={double,float},
-  morekeywords={double,float},
-  keywordstyle=\bfseries\color{green!55!black},
-  classoffset=0
-}
-
-\begin{document}
-
-\makeatletter
-\let\orig@lstnumber=\thelstnumber
-\newcommand\lstsetnumber[1]{\gdef\thelstnumber{#1}}
-\newcommand\lstresetnumber{\global\let\thelstnumber=\orig@lstnumber}
-\makeatother
-
-\title{PyTracer: Automatically profiling numerical instabilities in Python}
-\author{Yohan Chatelain$^1$, Nigel Young$^1$,  Gregory Kiar$^2$,  Tristan Glatard$^1$\\
-$^1$Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada\\
-$^2$Center for the Developing Brain, Child Mind Institute, New York, NY, USA}
-    \date{}
-\maketitle
-
-\begin{abstract}
-Numerical stability is a crucial requirement of reliable scientific computing.
-However, despite the pervasiveness of Python in data science, analyzing large Python programs remains challenging due to the lack of scalable numerical analysis tools available\gkmod{ for this language}{}.
-\gkmod{}{To fill this gap,}we developed \pytracer, a profiler to quantify numerical instability in Python applications.
-\pytracer \gkmod{automatically}{transparently?} instruments Python code to produce numerical traces and visualize them interactively in a Plotly dashboard.
-We designed \pytracer to \gkmod{work with any}{be agnostic to} numerical noise model \gkmod{including}{, allowing for tool evaluation through} Monte-Carlo Arithmetic, random rounding \gkmod{or}{,} random data perturbations\gkmod{}{, or structured noise for a particular application}.
-We illustrate \pytracer's capabilities by testing the numerical stability of key functions in \gkmod{the}{both} SciPy and Scikit-learn \gkmod{}{, two dominant} Python libraries \gkmod{}{for mathematical modeling}.
-Through these evaluations, we demonstrate \pytracer as a scalable, automatic, and generic framework for numerical \gkmod{evaluations}{profiling} in Python.
-% Numerical stability is a crucial requirement of reliable scientific computing.
-However, despite the pervasiveness of Python in data science, analyzing large Python programs remains challenging due to the lack of scalable numerical analysis tools available for this language.
-To address this issue, we developed \pytracer, a profiler to quantify numerical instability in Python applications.
-\pytracer automatically instruments Python code to produce numerical traces and visualize them interactively in a Plotly dashboard.
-% \pytracer is designed to work with any type of numerical noise model, including Monte-Carlo Arithmetic, random rounding or random data perturbations.
-We illustrate \pytracer's capabilities by testing the numerical stability of key functions in the SciPy and Scikit-learn Python libraries.
-Finally, \pytracer slows down executions by only $3.5 \times$ on average.
-% \tristan{Add one sentence to summarize the findings} 
-\end{abstract}
-
-\section{Introduction}
-
-The scientific Python ecosystem \gkmod{is}{has become} a central component of data
-analyses \gkmod{}{in recent years,} owing to its rich offering of data manipulation, array programming,
-numerical analysis, and visualization tools. In particular, libraries such
-as NumPy~\cite{harris2020array}, SciPy~\cite{virtanen2020scipy}, scikit-learn~\cite{pedregosa2011scikit} or PyTorch~\cite{paszke2019pytorch} are used in hundreds of publications \gkmod{every}{each} year, \gkmod{providing}{and serve as} a reference set of high-quality open-source core scientific libraries.
-Researchers have built numerous domain-specific software tools from this ecosystem, leveraging Python's simplicity and \gkmod{expressivity}{flexibility}.
-
-Numerical stability is a crucial requirement of reliable scientific data
-processing.
-In unstable analyses, small numerical perturbations introduced by data noise, software and hardware updates, or parallelization \gkmod{lead to}{have potential to introduce} substantial deviations in final results, \gkmod{and}{leading to} potentially different scientific conclusions, \gkmod{ultimately} threatening the reliability of computational analyses.
-To \gkmod{address}{prevent} this \gkmod{issue}{}, numerical stability analyses need to be conducted systematically, however, no practical tool currently exists to conduct such analyses for Python programs.
-
-We present PyTracer, a numerical stability \gkmod{analyzer}{profiling and visualization tool} for Python programs.
-\pytracer adopts a dynamic approach that evaluates numerical stability using program execution traces, and is applicable to large programs without manual intervention.
-\gkmod{}{The transparent nature of \pytracer is particularly valuable} in contrast \gkmod{}{to} theoretical approaches based on condition numbers or backward error analysis\gkmod{}{, which} require detailed modeling of the program and its numerical implementation.
-Similarly, static code analysis techniques hardly scale to large codebases, particularly in dynamically-typed languages such as Python.
-
-\pytracer estimates the variability of floating-point variables by combining program traces obtained with different numerical perturbations, which requires (1) generating numerically-perturbed executions, (2) tracing floating-point computations along program executions, and (3) visualizing stability evaluations.
-\pytracer addresses these requirements with (1) a ``fuzzy" Python interpreter instrumented with Monte-Carlo arithmetic, (2) a dynamic instrumentation of Python functions, modules, and classes through meta-programming, (3) an interactive Plotly dashboard to visualize stability measures throughout program executions.
-
-Through stability evaluations of the
-SciPy and scikit-learn libraries, we demonstrate \pytracer as a practical solution to review the numerical stability of extensive code bases.
-This manuscript describes related approaches, presents the design of \pytracer, and demonstrates its potential in various use cases.
-
-\section{Background and related work}
-
-Several tools have been developed to assess numerical quality, \gkmod{}{and can be} divided into static and dynamic approaches.
-Static approaches typically analyze source code, while dynamic approaches trace floating-point computations throughout executions.
-A detailed review of these approaches is presented in~\cite{cherubin2020tools}.
-\pytracer adopts the dynamic approach due to its scalability to large \gkmod{existing}{} code bases.
-Dynamic approaches typically trace floating-point computations, detect instabilities in traces, and visualize summary statistics about instabilities.
-This section reviews existing approaches for each of these steps.
-
-% In this section, we review tools and theoretical frameworks related to \pytracer components.
-% We start by reviewing state-of-the-art dynamic tools for detecting numerical instabilities.
-% Then, we focus on existing theoretical approaches for perturbations-based techniques to detect numerical instabilities,
-% \pytracer being agnostic to perturbation technique used. Finally, we review visualization tools 
-% aiming at detecting numerical instabilities over execution time.
-
-\label{sec:soa}
-\subsection{Numerical tracing techniques}
-Numerous tools exists to trace floating-point computations for C, C++, or FORTRAN programs due to the prevalence of these languages in High-Performance Computing (HPC). 
-The main tracing techniques are \textit{source-to-source}, \textit{compiler-based transformations}, and \textit{dynamic binary instrumentation}.
-
-\gkmod{}{Note: this paragraph just reads like a list with no real interpretation/commentary.
-I think it would be better to state the strengths of this technique, cite examples, and then state limitations/why it isn't the only technique used.}
-The source-to-source technique requires a rewriting of the application to modify floating-point types. 
-CADNA~\cite{jezequel2008cadna} is a library for C, C++, and Fortran implementing \gkmod{the}{} CESTAC~\cite{vignes1993stochastic} stochastic arithmetic.
-Shaman~\cite{demeure_phd} is a C++ library that uses a first-order error model to propagate numerical error.
-MCAlib~\cite{frechtling2015mcalib} is a C library that implements the Monte Carlo Arithmetic (MCA)~\cite{parker1997monte} using the MPFR~\cite{fousse2007mpfr} library.
-Finally, the work in~\cite{tang2016software} proposed a source-to-source framework for executing targeted code in infinite and fixed precision with and without  stochastic arithmetic.
-
-\gkmod{}{Note: similar to the above, this is just a list rather than a highlight of how the compiler-based approach can be more scalable than source-to-source because it requires less manual intervention into a codebase (e.g.), then have your list, and finally say why it is still limited/not a global fix to this problem.}
-The compiler-based approach instruments floating-point expressions at compile time. 
-Verificarlo~\cite{verificarlo} is a compiler that supports different types of arithmetic instrumentations, including MCA. 
-The work in~\cite{bao2013fly} modified the GNU Compiler Collection (GCC) to track local floating-point errors across executions.
-pLiner~\cite{guo2020pliner} is a root-cause analyzer based on the Clang compiler that detects floating-point operations responsible for result variability using a source-to-source transformation at the Abstract Syntax Tree (AST) level to rewrite parts of code with higher precision.
-PFPSanitizer~\cite{chowdhary2020debugging,chowdhary2021parallel} is a compiler that uses parallel shadow execution to detect numerical issues using higher precision.
-FLiT~\cite{sawaya2017flit} is a framework to detect variability induced by compilers and their optimizations.
-The work in~\cite{wang2012development} proposes a numerical debugger based on GDB~\cite{stallman1988debugging} for Discrete Stochastic Arithmetic (DSA) on FPGA as an Eclipse plugging.
-Similarly, Cadtrace~\cite{jezequel2008cadna} and Shaman propose a GDB-based tool to use the CADNA and Shaman libraries with GDB, respectively.
-
-Dynamic Binary Instrumentation (DBI) operates directly on executables, without the need for recompilation or manual changes. Therefore, it is applicable to any programming language.
-CraftHPC~\cite{lam2013dynamic} uses DBI to detect catastrophic cancellations at runtime.
-Verrou~\cite{fevotte2016verrou} is a Valgrind~\cite{nethercote2007valgrind} based tool that dynamically replaces
-floating-point operations with their stochastic arithmetic counterparts. FPDebug~\cite{benz2012dynamic} uses DBI to detect numerical inaccuracies by using shadow computations with higher precision.
-Herbgring~\cite{sanchez2017finding} is a Valgrind-based tool to detect
-numerical instabilities.
-It uses a shadow memory to detect precision losses by comparison with results obtained at higher precision.
-It is combined with symbolic computation to backtrack the root of the error.
-We can note that all methods based on a high-precision oracle suppose that computing with a large number of bits is sufficient to obtain an accurate result, which is not always true (see for example, the famous Muller's sequence~\cite{bajard1996introduction}).
-%\tristan{it looks like your veritracer paper is the first time where the ``famous Muller's sequence" was described, is that so?}).
-
-\gkmod{}{Note: I like this comparison here, but do think that the comments above about providing some more info when each is mentioned would still help this section.}
-Being agnostic to the programming language is a serious advantage of the DBI method compared to source-to-source and compiler-bases methods.
-However, working at the binary level makes it difficult to access high-level information needed to debug and understand the source-code logic.
-Conversely, the source-to-source approach provides a fine-grained control on the analyzed code, but it lacks scalability, as rewriting large codes can be a tedious task.
-Finally, the compiler-based approach takes advantage of the best of both by being automatic and having access to high-level information.
-However, like source-to-source, the compiler-based method is not suitable for analyzing closed-source libraries.
-
-To the best of our knowledge, there is currently no tool dedicated to the numerical analysis of Python code. Existing tools for tracing Python code focus on performance profiling for time (cProfile) 
-or memory consumption (memprofile). 
-Anteater~\cite{faust2019anteater} is a Python tracer tool to debug Python applications. 
-It performs source transformations at the AST level but only deals with native numeric Python types.
-Moreover, the user needs to manually tag each variable to trace. Finally, according to the authors, Anteater does not scale to large traces.
-cProfile, memprofile, and Anteater use Python decorators as the primary instrumentation technique, a Python mechanism to instrument a function by adding a line over a function declaration.
-While this method is appropriate when targeting specific functions, it is not feasible for large codebases where potentially unstable code sections are unknown.
-
-\label{sec:detecting-instabilities}
-\subsection{Detecting numerical instabilities with stochastic arithmetic}
-\label{sec:mca}
-
-% We review here the existing theoretical framework that might be used to detect numerical instabilities.
-% Our experiments rely on the Monte Carlo Arithmetic (MCA), a stochastic arithmetic allowing 
-% to detect numerical errors by adding random perturbations in the floating-point computations.
-% However, Pytracer do not rely on any assumption about the perturbation model used and thus leaves the user free to use
-% an alternative model. As such, we describe two others options that we thought might be beneficial and complementary to MCA: 
-% input data uncertainty analysis and random seed sensitivity.
-
-% \subsubsection{Stochastic Arithmetic}
-
-% The Monte Carlo Arithmetic is a variant of so-called stochastic arithmetic, whose purpose is to model round-off errors by a random variable.
-
-Three main approaches exist to detect numerical instabilities: stochastic arithmetic, uncertainty or sensitivity analysis~\cite{helton2006survey}, and random seed analysis~\cite{click2011quality}.
-%\tristan{add key references for uq/sa if any}
-\pytracer focuses on stochastic arithmetic since it does not make any assumption about 
-the noise model, in contrast to sensitivity analysis.
-\gkmod{}{Q: isn't \pytracer agnostic to noise model/method for instability detection?
-Can't we just re-run the tool multiple times under whatever model for detecting instabilities that we choose and it will work all the same?
-If so, then I may reword this to say that pytracer works for all, and for our usecases here we use SA because X, Y, and Z...}
-%\tristan{due to...}
-Stochastic arithmetic leverages randomness to estimate numerical instabilities coming from the use of floating-point representations. The main idea is to treat round-off errors 
-% \tristan{only round-off errors or all numerical errors?} 
-as random variables and characterize them statistically.
-
-The first published complete stochastic arithmetic framework was CESTAC~\cite{vignes1993stochastic}.
-In CESTAC, each floating-point computation is performed multiple times with different rounding modes: round-up or round-down.
-From these stochastic samples, one can then derive the number of significant digits in the computed result.
-Discrete Stochastic Arithmetic~\cite{vignes2004discrete} extends CESTAC with comparison operators implemented in the CADNA library.
-
-Monte Carlo Arithmetic (MCA)~\cite{parker1997monte} uses the same principle but introduces two differences:
-(i) a virtual precision parameter, allowing to simulate reduced working precision, and (ii) different perturbation modes to introduce perturbations
-on function inputs or output.
-MCA replaces each floating-point number $x$ with a stochastic counterpart computed as:
-\[
-inexact(x) =  x + \beta^{e_x - t}\xi
-\]
-where $\beta$ is the number base, $e_x$ is the magnitude of $x$, $t$ the virtual precision and $\xi \in (-\frac{1}{2},\frac{1}{2})$ is a random uniform variable.
-Virtual precision allows for the simulation of reduced working precision.
-MCA can be applied in three modes: Random Rounding (RR), Precision Bounding (PB), and full MCA, which apply function $inexact$ to the output, the inputs, or both, respectively.
-While the RR mode is equivalent to stochastic rounding, the PB mode can also identify catastrophic cancellations.
-
-Stochastic arithmetic quantifies numerical error using the number of significant digits $s$ estimated among the sampled values.
-A common formula to determine this number from MCA samples is \gkmod{the one reported}{presented} in~\cite{parker1997monte}:
-\begin{equation}
-s = -\log_{\beta}{ \left| \dfrac{\sigma}{\mu} \right|} \label{eq:sig-digits}
-\end{equation}
-where $\mu$ and $\sigma$ are the sample mean and standard deviation of a variable sampled with MCA.  
-Sohier et al.~\cite{sohier2018confidence} recently provided a generalization of this formula to include confidence intervals.
-
-% \subsubsection{Uncertainty, sensitivity, and random seed analysis}
-% \tristan{I'm wondering if we could remove this sub-section, as it doesn't seem to be critical to the understanding of the paper, wdyt?}
-% Uncertainty analysis (UA) is a method to estimate the output distribution given an input distribution.
-% Sensitivity analysis (SA) is a variation of UA that measures the local response to a small perturbation~\cite{loucks2017water}. 
-% Several approaches for UA and SA exist, among them differential analysis, response surface methodology, Monte Carlo analysis, and variance decomposition (see~\cite{helton2006survey} for a review).
-In particular, Monte Carlo analysis is a sampling-based technique that samples inputs space to estimate output response.
-Monte Carlo analysis shares similarities with Monte Carlo Arithmetic.
-For instance, the PRECISE framework~\cite{chaitin1996lectures} shares with MCA the idea of varying virtual precision to estimate output sensitivity.
-
-% Furthermore, the quality of a Random Number Generator is a crucial characteristic when dealing with stochastic model and differ from cryptography requirements.
-A good RNG provides a tradeoff between performance, period, correlation, or uniformity~\cite{james2020review} for numerical simulation.
-% On the other hand, poor-quality RNGs may have a substantial impact on results~\cite{click2011quality}.
-First, measuring variation induced by seed is a good indicator of program stability that we can compare against variability induced by floating-point arithmetic.
-
-\subsection{Visualization}
-
-Visualization \gkmod{}{Note: You kind of jump right in to this section.
-Visualization of what in particular?
-Why do we want (need?) to visualize this sort of data?} covers a wide range of numerical simulation domains, from general-purpose numerical visualization with tools
-such as VTK~\cite{schroeder2000visualizing} to topological data analysis~\cite{tierny2018topological}, including matrix~\cite{wu2008matrix} or tensor~\cite{kindlmann2006diffusion} visualization.
-Despite the large number of existing tools to identify numerically unstable sections of source code, few allow the user to have a global view of the numerical precision of their computations or to compare several executions of the same program under various perturbations.
-
-Veritracer~\cite{chatelain2018veritracer} was the first tool to propose an embedded visualizer of numerical stability over the execution of C, C++, and Fortran code.
-Veritracer extends Verificarlo~\cite{verificarlo} with contextual information about traced variables, which allows the user to identify instabilities quickly.
-However, Veritracer neither offers a dynamic interface nor includes information about high-level structures such as \texttt{struct} or \texttt{array}.
-FPAvizual~\cite{gu2014fpavisual} visualizes the effects of floating-point arithmetic but only for educational purposes \gkmod{}{Q: What does this mean?}.
-Anteater~\cite{faust2019anteater} proposes a visualizer for Python code, but as mentioned previously, it only deals with native Python types, and the user needs to select variables to trace manually.
-Anteater provides an insightful reflection
-around visual debugging beyond floating-point analysis, which has inspired the design of \pytracer's visualization interface.
-
-\section{\pytracer design}
-
-% \subsection{Pytracer workflow}
-\pytracer adopts the three-step workflow shown in Figure~\ref{fig:workflow}.
-First, \pytracer uses \gkmod{monkey patching}{\textit{monkey patching}} to replace the functions called by the application with a wrapper that saves their arguments and returned values in a trace file \gkmod{}{Q: This is conceptually similar to a decorator, no?
-If so, perhaps it is worth mentioning}.
-Second, it injects noise in the application \gkmod{}{Q: \pytracer doesn't actually inject noise, does it?
-You can just run your tool however you want multiple times}, executes it multiple times, and aggregates the resulting trace files to compute summary statistics about each traced variable.
-Finally, a Plotly dashboard provides interactive visualizations highlighting unstable code sections.
-
-% \tristan{mention monkey patching}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figure/workflow.pdf}
-    \caption{Pytracer workflow \gkmod{}{Note: replace "Execution" with "Multiple Independent Executions", and maybe move it to be between the gears and the pkl files.}}
-    \label{fig:workflow}
-\end{figure}
-
-\subsection{Python code instrumentation}
-
-%\tristan{``Instrumentation" should appear in Figure 1}
-
-\pytracer dynamically instruments Python modules
-without requiring source code modifications in the application.
-To do so, it creates a new, instrumented version of each module that preserves its original attributes so that the application can transparently use it.
-\gkmod{}{Note: this form of monkey patching is basically global and transparent decorating, right?}
-By default, \pytracer instruments all the attributes
-in a given module except the special ones of the form \texttt{\_\_*\_\_}\gkmod{}{, which is common for reserved Python methods}.
-However, some attributes are not writable. In this case, \pytracer preservers the original attributes and warns the user. The user can also restrict the list of traced attributes through
-an inclusion/exclusion mechanism.
-The main advantage of this instrumentation approach is the lack of required modification in the application source code, in contrast with decorator-based approaches.
-In addition, this technique is scalable and applicable in read-only environments such as Singularity containers or HPC clusters.
-
-\subsubsection{Intercepting module import}
-
-Python loads modules through an import mechanism triggered by the \texttt{import} keyword that involves two objects: \texttt{finders} and \texttt{loaders}. \texttt{Finders} search for packages (or 
-namespaces\footnote{Python distinguishes between \texttt{regular} and \texttt{namespace} packages.
-A regular package is a directory that contains a \_\_init\_\_.py file and potentially subdirectories (sub-packages) 
-that contain themselves a \texttt{\_\_init\_\_.py} file and so on recursively. 
-The package hierarchy follows those of the directory. 
-Namespace packages introduced in Python 3.3 (\href{https://www.python.org/dev/peps/pep-0420/}{PEP 420}) do not contain an
-\_\_init\_\_.py file and allow for flexible directory structures.
-Hence, parts of the package can be located in zip files, on the network, or in separated directories.
-There are no functional differences between both types of packages.}) on the local storage --- such as standard packages installed through the pip package manager --- or on a distant server.
-\texttt{Finders} do not load modules. Instead, they return a specification (\texttt{spec} object) that includes 
-information on where to find and how to load modules.
-\texttt{Loaders} create module objects, initialize them, and fill import-related attributes 
-such as \texttt{\_\_spec\_\_}. 
-\texttt{Loaders} then execute modules and populate their namespace. Finally, modules are bound to their import name in the \texttt{sys.modules} dictionary.
-
-Python supports custom \texttt{finder} classes registered in the \texttt{sys.meta\_path} list.
-When Python encounters an \texttt{import} statement, it first looks for an existing binding in \texttt{sys.modules} and then iterates over the \texttt{finder} classes in the \texttt{sys.meta\_path} list until it finds the module.
-\pytracer adds a custom \texttt{finder} class at the head of \texttt{sys.meta\_path} that intercepts
-the module import and creates the module with a custom \texttt{loader} class.
-
-\pytracer's \texttt{loader} class first loads the original module, then copies it as a new instance of the \texttt{ModuleType} class.
-It then calls the appropriate instrumentation function for each attribute depending on its type (function, class, or instances) and replaces the original module in the \texttt{sys.modules} map with the instrumented version.
-Finally, it updates all existing references to the original module contained in the global symbol table.
-As a result, the application will transparently call the instrumented module.
-
-% \tristan{is the non-instrumented version ever added to sys.modules? If so, could this lead to race conditions? If not, replace with ``adds the instrumented module to the sys.modules map"}. 
-% \Yohan{Yes, it replaces the original module.
-You can't have a race-condition since sys.modules is a dict with only one value for a given key.
-The trick is that the wrapped module keeps a reference to the original module, it's just that this reference is invisible for the others object since it's not in sys.modules and globals.
-By the way, Pytracer needs to update all possible references that original objects may hold, like functions in \_\_dict\_\_ attributes or locals references in \_\_globals\_\_ for example.}
-
-% \pytracer intercepts the modules loaded with the \texttt{Finder} and \texttt{Loader} mechanisms \tristan{is it restrictive? Are there other mechanisms?}.
-% The Finder searches the loader of a module that is being imported while the 
-% Loader loads and initializes the module. \pytracer adds \tristan{overrides?} a new Finder and Loader on top of the default ones
-% to intercept imports and to instrument modules selected by the user. This mechanism allows returning 
-% the original module in the instrumentation code and returning the instrumented module in the targeted application
-% without modifying its actual code.
-
-\subsubsection{Instrumenting module functions}
-
-Listings~\ref{fig:wrapper_creation} and~\ref{fig:generic_wrapper} show \pytracer's function instrumentation mechanism.
-For each function to instrument, \pytracer's \texttt{loader} class creates a wrapper function, dynamically compiles it with the \texttt{compile} builtin function, and substitutes it for the original module function.
-Although simple, this technique does not apply to callable class instances, i.e., class instances that have a \texttt{\_\_call\_\_} attribute and are not of type \texttt{FunctionType}.
-Indeed, applying the wrapper technique would 1) modify the type of the class instance to \texttt{FunctionType}, which could cause syntax and semantic errors, and 2) mask class attributes, leading to \texttt{AttributeError} exceptions.
-\pytracer overrides the \texttt{\_\_call\_\_} attribute with the wrapper function when possible to overcome this issue.
-When the \texttt{\_\_call\_\_} attribute is not writable,  Pytracer does not instrument the class and returns a warning.
-
-% \tristan{add docstrings to all Python code examples and clarify captions accordingly: you don't need to explain the meaning of each attribute in the caption if it's in the docstring.
-The caption can focus on the main functionality, reusing the text currently in 3.1.5.}
-% \Yohan{TODO}
-
-% Listing~\ref{fig:wrapper_creation} shows how functions are instrumented.
-% This function takes as inputs the information about the function to instrument (module name and full qualified name),
-% the function itself, and the actual name of the function. It then creates a wrapper around the actual wrapper
-% (\texttt{generic\_wrapper}) that will save the values in trace files.
-Instead of passing the function, we pass the function's identifier, which is a unique 64-bits integer that references each Python object.
-This identifier is available
-% with the \texttt{id} builtin function. it allows to get rid of aliases and to avoid instrumenting functions twice.  \tristan{Summarize this paragraph in the figure caption}
-
-% Listing~\ref{fig:generic_wrapper} shows what the instrumented code does. 
-% It first unpacks the function's information to get the function's identifier to retrieve the original function.
-% Then arguments are bound by creating a mapping from positional and keyword arguments to parameters, avoiding conflicts and mispositioning.
-It also allows getting names of arguments for the visualization.
-% Once bound, the \texttt{inputs} function dumps the arguments in the pickle file.
-% Finally, Pytracer calls the function with the correct arguments, dumps the result, and returns it. \tristan{Summarize this paragraph in the figure caption}
-
-%
-% we can employ a case by case strategy depending on the class (i.e. numpy ufunc) or simply ignore
-% the instrumentation and let the original one.
-% \tristan{add a sentence to explain how callable instances are instrumented}
-
-\begin{listing}
-    \centering
-\begin{lstlisting}[language=Python,style=customPython]
-def get_wrapper_function(module, qualname, name, function):
-    """Returns the instrumented function as a string.
-    This string will be compiled with the compile builtin function
-
-    Parameters:
-        module: Name of the function module
-        qualname: Qualified name of the function
-        name: Name of the function
-        function: Python object function
-
-    Returns:
-        wrapper_code: The code source of the wrapper
-    """
-    function_id = id(function)
-    info = (function_id, function_module, function_qualified_name)
-    wrapper_code = f"""
-    def {function_wrapper_name}(*args, **kwargs):
-        return generic_wrapper({info},*args,**kwargs)"""
-    return wrapper_code
-\end{lstlisting}
-    \caption{Function to create the instrumented version of a function.
-    \pytracer uses the identifier of the function instead of the 
-    actual function to handle aliases and avoid duplicate instrumentation.}
-    \label{fig:wrapper_creation}
-\end{listing}
-
-\begin{listing}
-    \centering
-\begin{lstlisting}[language=Python,style=customPython,]
-def generic_wrapper(self, info, *args, **kwargs):
-    """Generic wrapper saving inputs and outputs of the wrapped function.
-    The id_dict dict keeps a mapping between the original function identifier
-    and itself. Arguments are binded to avoid mispositioning.
-    Returns the actual output of the wrapped function.
-
-    Parameters:
-        info: Tuple with the function's id, function's module and function's name
-        *args: Positional calling arguments
-        **kwargs: Keyword calling arguments
-
-    Returns:
-        outputs: Outputs of the wrapped function
-    """
-    fid, fmodule, fname = info
-    function = original_function_cache.id_dict[fid]
-    bind = Binding(function, *args, **kwargs)
-    stack = self.backtrace()
-    time = elements()
-    self.inputs(time=time,
-                module_name=fmodule,
-                function_name=fname,
-                function=function,
-                args=bind.arguments,
-                backtrace=stack)
-    outputs = function(*bind.args, **bind.kwargs)
-    self.outputs(time=time,
-                 module_name=fmodule,
-                 function_name=fname,
-                 function=function,
-                 args=outputs,
-                 backtrace=stack)
-    return outputs
-\end{lstlisting}
-    \caption{\pytracer's generic wrapper function that saves
-    the inputs and outputs of the wrapped function.}
-    \label{fig:generic_wrapper}
-\end{listing}
-
-\subsubsection{Instrumenting classes}
-
-\pytracer instruments classes by wrapping their callable attributes as described previously. 
-This instrumentation preserves class types, which avoids type mismatches in the instrumented application.
-However, classes that describe particular base types and NumPy's universal functions (class \texttt{ufunc}) contain read-only attributes that cannot be instrumented.
-By default, \pytracer returns a warning when it encounters such classes.
-
-\subsubsection{Instrumenting class instances}
-
-\pytracer automatically instruments class instances since it instruments classes.
-However, it cannot instrument or instantiate classes that have read-only attributes --- in particular class \texttt{ufunc}, --- which is problematic given their pervasiveness in scientific computing.
-In particular, NumPy's universal functions include
-vectorized elementary mathematical functions and other prevalent \gkmod{ones}{Q: prevalent whats?}. Universal functions are implemented in C, which prevents their modification.
-
-To overcome this issue, \pytracer wraps the class instance into a transparent wrap class (\texttt{twc}) that overloads
-1) function \texttt{\_\_getattribute\_\_}, called when an instance attribute is accessed --- instrumented to return the attributes from the original class, and 2) function \texttt{\_\_call\_\_}, called when the function is called through the () operator --- instrumented with function \texttt{generic\_wrapper}.
-\gkmod{}{Note: the previous sentence is a bit hard to follow; the word "called" is used a lot so I got a bit lost.} The \texttt{twc} returns the queried attribute of the instance instead of returning its attributes, allowing transparent access to the instance.
-Finally, \pytracer overloads the builtin \texttt{type} function to preserve the type of the wrapped instance.
-
-\subsubsection{Instrumenting iterators}
-
-In functional programming, iterators traverse containers lazily, meaning that the next element in the sequence is only computed when the application uses it.
-This technique allows for the manipulation of virtually infinite sequences with finite memory.
-However, it implies that no complete mapping of the container returned by an iterator exists in memory since the application computes each element on the fly.
-Therefore, iterators are not serializable which implies that \pytracer cannot save them to output traces.
-A workaround would be to convert iterators into explicit containers, however, this would increase the memory footprint significantly. \pytracer, therefore, does not instrument non-builtin iterators.
-
-% \begin{listing}
-% \begin{minipage}[t]{0.4\linewidth}
-%     \begin{lstlisting}[language=Python,style=customPython]
-% >>> import numpy as np
-% >>> x = np.array(range(10))
-% >>> index = np.array([1,-1],dtype=int)
-% >>> x[index]
-% >>> array([1, 9])
-%     \end{lstlisting}
-% \end{minipage}
-% \begin{minipage}[t]{0.4\linewidth}
-%     \begin{lstlisting}[language=Python,style=customPython]
-% >>> import numpy as np
-% >>> x = np.array(range(10))
-% >>> index = np.array([1,-1], dtype=object)
-% >>> x[index]
-% Traceback (most recent call last):
-%   File "<stdin>", line 1, in <module>
-% IndexError: arrays used as indices must be of integer (or boolean) type
-%     \end{lstlisting}
-% \end{minipage}
-% \caption{Illustration of the issue of using \texttt{frompyfunc} function to convert function to \texttt{ufunc}. Left: original code. Right: instrumented code. 
-% \tristan{This needs more explanation: where is the ufunc, what is the type returned by the original ufunc, and why does it crash in the instrumented version.} \Yohan{TODO}}
-%     \label{fig:numpy_array_index_issue}
-% \end{listing}
-
-\subsection{Detecting numerical instabilities}
-
-\pytracer detects numerical instabilities by computing summary statistics across multiple executions perturbed with numerical noise.
-While \pytracer's instrumentation, trace aggregation, and visualization work with various types of numerical noise, we experimented primarily with Monte-Carlo Arithmetic (MCA) as it is an accurate model for floating-point errors.
-
-\subsubsection{Noise injection}
-\label{sec:fuzzy}
-
-We enable MCA in Python programs via Verificarlo~\cite{verificarlo}, a clang-based compiler~\cite{lattner2008llvm} that replaces floating-point operations by a generic call to a configurable floating-point model.
-Several floating-point models are available~\cite{chatelain2019automatic,chatelain2019outils}, also called backends.
-\pytracer leverages ``fuzzy"~\cite{kiar2020comparing}, a collection of software tools compiled with Verificarlo.
-In particular, fuzzy provides MCA-instrumented versions of the Python interpreter as well as the BLAS, LAPACK, NumPy, SciPy, and scikit-learn libraries, which enables MCA for a wide range of existing scientific Python programs.
-Fuzzy is available in Verificarlo's GitHub organization at \href{https://github.com/verificarlo/fuzzy}{\url{github.com/verificarlo/fuzzy}}.
-
-% As the time of writing this article, fuzzy provides 5 levels of instrumentation (each level N including the lower levels):
-% \begin{enumerate}
-%     \item BLAS + LAPACK
-%     \item Python interpreter
-%     \item Numpy
-%     \item SciPy
-%     \item Scikit-learn
-% \end{enumerate}
-
-\subsubsection{Trace format}
-
-\pytracer stores traces in the pickle format, a binary format to serialize Python objects.
-The main advantages of the pickle format compared to other serialization approaches such as marshal or JSON are its ability to serialize most Python objects and its native compression.
-In addition, pickle writes Python objects sequentially, which preserves the temporal ordering required by subsequent trace analyses.
-
-Traces store numerical values at the granularity of function calls.
-When the application invokes a function, \pytracer saves a call input object containing contextual information (function's name, module's function, stacktrace) and the values of the function arguments.
-When the function returns, \pytracer saves a similar call output object containing the returned value.
-
-\subsubsection{Trace aggregation}
-
-Once traces are available, \pytracer sequentially parses them and computes the mean, standard deviation, and the number of significant digits (as in Equation~\ref{eq:sig-digits}) of all saved values.
-\pytracer saves these summary statistics in an HDF5 file, a hierarchical format that facilitates visual browsing since only
-required information are loaded when requested by the user. \gkmod{}{Q: Is there a reason we don't also use HDF for the raw traces? Lack of native compression?}
-This operation critically relies on the ordering of call input and output objects in the traces.
-Therefore, it assumes that the application is single-threaded and that the control flow does not depend on a random state.
-% Techniques to overcome this limitation are discussed in the discussion section.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{figure/pytracer_layout.pdf}
-    \caption{Pytracer visualization layout.}
-    \label{fig:visu-layout}
-\end{figure}
-
-To aggregate traces, \pytracer successively unpickles call objects in each trace, checks
-that the call objects refer to the same function and stacktrace, and terminates the parsing otherwise.
-PyTracer stores function arguments or returned values in a NumPy array for each matching call object to compute statistics.
-For compound objects such as tuples, dictionaries, or objects, it recursively parses the fields until finding
-numeric types or NumPy arrays of numeric types.
-
-\subsection{Interactive visualization}
-The third main component of \pytracer is its interactive trace visualizer built with Plotly Dash~\cite{plotly}, a Python framework for web visualization.
-Plotly Dash abstracts the low-level details of web applications in a highly customizable development interface allowing to offload heavy computations to a server \gkmod{}{Q: does it support using a remote server with forwarding, in the event that your local system isn't that beefy?}.
-Figure~\ref{fig:visu-layout} presents the general layout of the \pytracer visualizer, divided into five sub-components:
-\begin{enumerate}
- \item Timeline view: This view displays the values of each input and output for a given function at a given invocation.
-By default, \pytracer shows the number of significant digits computed across the traces.
-The user can switch to the mean or the standard deviation \gkmod{}{Q: mean/stdev of what?
-the inputs/outputs?
-But what if they are on a totally different scale (e.g.
-log(0.0001)}.
-The visualizer uses an upper triangle for inputs and a lower triangle for outputs.
-\pytracer internally represents all values as NumPy arrays.
-In the case of non-scalar values or types that cannot be trivially cast into NumPy arrays, \pytracer splits the value into several variables.
-Hence, \pytracer will transform a class containing $n$ floating-point parameters into $n$ variables.
-Each variable is prefixed with the original value and postfixed with the name of the parameter.
-\gkmod{}{Q: how is this managed for the sake of interpretability?
-E.g.
-if one of the components has very low significance and another few are fine, how can I easily identify where in my sequence we have the drop in precision?}
-    Finally, non-scalar values (vectors or matrices) are represented by their average and can be inspected with the Zoom view (see below).
- \item Gantt chart view: This view displays the call graph as a Gantt chart representing the instrumented functions. Each function call is represented with a bar.
-    The time overlaps reflect the caller/callee relation.
-    For example, in the figure, \texttt{function1} calls \texttt{function2} that itself calls \texttt{function4} and \texttt{function5}. 
-    This view provides insights on the calling context for each function, which may influence numerical stability.
-\gkmod{}{Note: this is a non-standard layout for gantt charts...
-normally the width/overlap is determined by time of start + duration.
-Is that information contained somewhere in here?
-If not, will a very fast function that calls sub-functions, say, 1000 times look longer than a very slow function that doesn't call any subfunctions?}
- \item  Source code view: This view displays \gkmod{}{a local snapshot of} the source code file of the variable hovered in the timeline view. 
- \item Zoom view: This view provide details about non-scalar values. For example, a matrix may have instabilities around its diagonal but not in other regions.
-    The visualizer also provides additional metrics such as array shape, infinite norm, or condition number.
-\item  Functions list view: This view allows the user to select the functions plotted in the timeline view.
-\end{enumerate}
-
-\section{Numerical evaluations}
-
-We evaluated \pytracer on two widely-used Python libraries: SciPy~\cite{virtanen2020scipy}, the main library for scientific computing in Python, and  scikit-learn~\cite{pedregosa2011scikit}, a reference machine-learning framework that
- implements a wide range of state-of-the-art algorithms.
-For each library, we executed the software examples provided in their respective GitHub repositories.
-We traced each example five times, having activated MCA in the Python interpreter, BLAS, LAPACK, NumPy, SciPy, and scikit-learn.
-We repeated the experiment with two MCA modes, Random Rounding (RR) and Full MCA, resulting in 2 experiments for each example.
-We used the default virtual precision in Verificarlo, namely 24 bits for single-precision floating-point values and 53 bits for double-precision values, which simulates machine error.
-We used Python-3.8.5, NummPy-1.19.1, SciPy-1.5.4, and scikit-learn-0.23.2.
-%  \tristan{Report scipy and sklearn versions used.}
-
-\subsection{Results overview}
-
-Table~\ref{tab:pytracer_results_summary} summarizes
-\pytracer's outcome on SciPy and scikit-learn examples.
-Columns \textit{trace} and \textit{parse} report on the tracing and aggregation steps with three possible outcomes: green for success, red for numerical error in the application, and orange for errors due to the fuzzy noise injection
-that are not considered numerical errors. \gkmod{}{Q: What does "success" or the other labels actually mean? What is the threshold for numerical errors, e.g.}
-% , like for instance index errors due to an index shift.
-% \tristan{Explain what this is, in a setence here or with a subsubsection if it requires more}. 
-Overall, the tracing and parsing of SciPy and scikit-learn examples in Random Rounding mode was entirely successful \gkmod{}{, indicating on average XX loss in numerical precision,} for 32/40 examples.
-The remaining examples failed due to numerical errors in the libraries, which we discuss hereafter.
-The instrumentation with Full MCA is more invasive and reduced the number of successful \gkmod{}{Q: Does this mean the 28 failed, or completed but poorly?
-In general, the way the states are being referred to so far in the results are rather ambiguous} executions to 12/40.
-
-Column \textit{sigbits} in Table~\ref{tab:pytracer_results_summary} summarizes the precision for the main outputs of SciPy and scikit-learn examples. 
-We measured the precision in significant bits on the \gkmod{main}{final primary} example output by taking the element-wise mean for non-scalar values and, if the example produces many outputs, the average value among all of them.
-The numerical quality across all examples varies from 0 to 52, with an average of 44 significant bits.
-For both modes, we note that only two examples failed due to a numerical error
-% \tristan{can we see that in the table? if not, don't comment on it, it is puzzling. Could you show that in the table by using the same error symbols as in Table 2?} 
-(\texttt{face\_recognition} for RR and \texttt{Bayesian Ridge Regression} for Full MCA) even though this number is underestimated since Full MCA mode is more intrusive than RR mode and most of the examples produce error caused by the fuzzy noise injection.
-\gkmod{}{Note: I don't understand what is being said in the rest of the sentence following the parentheses}
-
-\begin{table}[]
-    \centering
-    \small
-    \begin{subfigure}[t]{\linewidth}
-    \centering
-    \begin{tabular}{|lll|c|c|c|c|c|c|}
-    \hline
-    \multicolumn{3}{|c}{ \multirow{2}{*}{Application} } & \multicolumn{3}{|c|}{Random Rounding (RR)} & \multicolumn{3}{c|}{Full MCA} \\
-    \cline{4-9}
-    & & & trace & parse & sigbits & trace & parse & sigbits \\
-    \hline
-    %        &               RR                 &                 MCA               \\
-    %        &  numpy         &   no numpy      &      numpy      &     no numpy    \\
-    %        & run   & parse  &  run   &  parse &  run   & parse  & run    & parse  \\
-
-    \multicolumn{1}{|c|}{ \multirow{20}{2em}{ \rotatebox{90}{SciPy} } } &   
-    \multicolumn{1}{c|}{ \multirow{3}{2em}{ \rotatebox{90}{FFT} }}  & \discreteCosineRF &  \valid & \valid & \s{52} & \warn & \cross & \s{47} \\ 
-    \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \fftOneDRf & \valid & \valid & 41 & \warn  & \cross & - \\
-    \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \fftTwoDRf & \valid & \valid & \s{52} & \valid & \valid & \s{52} \\
-    \cline{2-9}
-    \multicolumn{1}{|c|}{} &  \multicolumn{1}{c|}{  \multirow{5}{*}{ \rotatebox{90}{Interpolation} } }
-    & \interOneDRf & \valid & \valid & 51 & \warn & \cross &  - \\
-    \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \multiRf      & \valid & \valid & \s{51} & \warn  & \cross & \s{-} \\
-    \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{}  & \bsplineRf    & \valid & \valid &10 &  \valid & \valid & 10\\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} &     \splineOneDRf & \valid & \cross & \s{52} & \warn  & \cross & \s{52} \\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} &     \splineTwoDRf & \valid & \valid & 10 &  \warn  & \cross & - \\
-    \cline{2-9}
-    \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{ \multirow{12}{2em}{ \rotatebox{90}{Optimization} } }
-    & \bfgsRf & \valid & \valid & \s{48}  & \valid & \valid & \s{46} \\
-\cline{3-9}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \globalRf & \valid & \cross & 17 & \warn  & \cross & - \\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & | SHGO\footnote{Simplicial Homology Global Optimization} & \na & \na  & \s{25} & \na  & \na & \s{-} \\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & | Dual Annealing & \na & \na  & 4 & \na & \na  & - \\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & | Differential Evolution & \na & \na & \s{0} & \na & \na & \s{-} \\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & | Basin Hopping & \na  & \na & 40 & \na  & \na & - \\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & | SHGO Sobol    & \na  & \na  & \s{45} & \na  & \na & \s{-} \\
-\cline{3-9}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \slsqpRf  & \valid & \valid & 45 & \valid & \valid & 44 \\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \lsmRf    & \valid & \valid &\s{48} & \warn  & \cross & \s{-} \\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \nelderRf & \valid & \valid & 44 & \valid & \valid & 42 \\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \ncgRf    & \valid & \valid & \s{48} & \valid & \cross & \s{47} \\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \rootRf   & \valid & \cross & 52 & \warn  & \cross & 50 \\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \rootLargRf      & \valid & \cross & \s{29} & \valid & \cross & \s{26} \\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \rootLargePredRf & \valid & \cross & 42 & \valid & \cross & 42 \\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \trustExactRf & \valid & \valid & \s{48}  & \valid & \valid & \s{46} \\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \trustTruncRf & \valid & \valid & 48  & \valid & \valid & 46 \\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \trustNCGRf   & \valid & \valid & \s{52}  & \valid & \valid & \s{47} \\
-    \hline
-%     \end{tabular}
-% \end{subfigure}
-%     \label{tab:pytracer_scipy_results_summary}
-% % \end{table}
-% % \begin{table}[]
-%     \centering
-% \begin{subfigure}[t]{.8\linewidth}
-%     \begin{tabular}{|c|c|c|c|c|c|c|}
-%     \hline
-%     \multirow{2}{5em}{Application} & \multicolumn{3}{c|}{RR} & \multicolumn{3}{c|}{MCA} \\\cline{2-7}
-%                                 & trace & parse & result &  trace & parse & result \\
-%     \hline
-    %        &               RR                 &                 MCA               \\
-    %        &  numpy         &   no numpy      &      numpy      &     no numpy    \\
-    %        & run   & parse  &  run   &  parse &  run   & parse  & run    & parse  \\
-
-    \multicolumn{2}{|c|}{ \multirow{20}{2em}{ \rotatebox{90}{Scikit-learn} } }
-    & \AdaboostRf   & \valid & \valid & 48 & \warn  & \cross & - \\
-    \cline{3-9}
-    \multicolumn{2}{|c|}{} & \brrRf        & \valid & \valid & \s{25} & \cross & \cross & \s{-} \\
-    \multicolumn{2}{|c|}{} & | $1^{st}$ dataset & \na  & \na & 25 & \na  & \na  & - \\
-    \multicolumn{2}{|c|}{} & | $2^{nd}$ dataset & \na & \na  & \s{nan} & \na  & \na & \s{-} \\
-    \cline{3-9}
-    \multicolumn{2}{|c|}{} & \onlineClassifierComparisonRf & \valid & \valid & 20 & \warn & \cross & -  \\
-    \multicolumn{2}{|c|}{} & \kmeansRf     & \valid & \valid & \s{52} & \valid & \cross & \s{-} \\
-    \multicolumn{2}{|c|}{} & \covarianceRf & \valid & \cross & 48 & \warn  & \cross & - \\
-    \multicolumn{2}{|c|}{} & \decisionRf   & \valid & \valid & \s{50} & \valid & \valid & \s{50} \\
-    \multicolumn{2}{|c|}{} & \digitsRf     & \valid & \valid & 52 & \warn  & \cross & 52 \\
-    \multicolumn{2}{|c|}{} & \faceRf       & \cross & \valid & \s{-}  & \warn  & \cross & \s{-} \\
-    \multicolumn{2}{|c|}{} & \penaltyRf    & \valid & \valid & -  & \valid & \valid & - \\
-    \multicolumn{2}{|c|}{} & \lassoRf      & \valid & \valid & \s{48} & \warn  & \cross & \s{47} \\
-    \multicolumn{2}{|c|}{} & \hyperplaneRf & \valid & \valid & 3  & \valid & \cross & - \\
-    \multicolumn{2}{|c|}{} & \mnistRf      & \valid & \valid & \s{43} & \warn  & \valid & \s{-} \\
-    \multicolumn{2}{|c|}{} & \multitaskRf  & \valid & \valid & 50 & \warn  & \valid & 48 \\
-    \multicolumn{2}{|c|}{} & \ompRf        & \valid & \valid & \s{52} & \valid & \valid & \s{52} \\
-    \multicolumn{2}{|c|}{} & \pcaRf        & \valid & \valid & 48 & \valid & \valid & 48 \\
-\cline{3-9}
-    \multicolumn{2}{|c|}{} & \robustRf     & \valid & \valid & \s{50} & \warn  & \cross & \s{48} \\
-    \multicolumn{2}{|c|}{} & | Linear        & \na & \na & 48 & \na  & \na & 46 \\
-    \multicolumn{2}{|c|}{} & | RANSAC        & \na  & \na & \s{50} & \na  & \na  & \s{48} \\
-\cline{3-9}
-    \multicolumn{2}{|c|}{} & \toyRf        & \valid & \valid & 35 & \warn  & \cross & - \\
-\cline{3-9}
-    \multicolumn{2}{|c|}{} & \svmRf        & \valid & \valid & \s{43.5} & \valid & \cross & \s{-} \\
-    \multicolumn{2}{|c|}{} & | Non-weighted  & \na & \na & 43 & \na & \na  & - \\
-    \multicolumn{2}{|c|}{} & | Weighted      & \na  & \na & \s{44} & \na  & \na  & \s{-} \\
-\cline{3-9}
-    \multicolumn{2}{|c|}{} & \tomographyRf & \valid & \cross & - & \warn  & \cross & - \\
-    \multicolumn{2}{|c|}{} & \weightedRf   & \valid & \valid & \s{44} & \valid & \cross & \s{-} \\
-    \hline
-    \end{tabular}
-    \end{subfigure}
-    \caption{\pytracer execution summary on SciPy and Scikit-learn examples. 
-    % \tristan{Replace FFT with SciPy FFT, Interpolation with SciPy Interpolation and Optimization with SciPy Optimization, or add a SciPy header to these rows.} \tristan{Nitpick: you could add a color scheme to sigbits (for instance shades of blue), to make the column more easily readable.} \\
-    \emph{trace}: outcome of \pytracer tracing, \emph{parse}: outcome of \pytracer trace parsing and aggregation, \emph{result}: precision for main outputs in significant bits.
-\valid: successful run, \warn: error from invalid noise injection, \cross: numerical error or divergent traces.
-\textit{nan} stands for (\texttt{Not-A-Number}).
-Example names are linked to their source code.}
-    \label{tab:pytracer_results_summary}
-\end{table}
-
-    % \caption{
-    % \pytracer execution summary on SciPy examples.\\RR: Random Rounding.
-trace: outcome of \pytracer tracing, parse: outcome of \pytracer trace parsing and aggregation.
-\valid: successful run, \warn: error in fuzzy noise injection, \cross: numerical error or divergent traces.
-    % }
-
-\subsection{Effect of MCA modes}
-\label{sec:impact_mca_modes}
-Random Rounding perturbs only the result of a floating-point operation while Full MCA perturbs both the inputs and the result. 
-Therefore, Full MCA may trigger catastrophic cancellations while Random Rounding only introduces round-off errors which generally have a lesser impact.
-Moreover, Random Rounding preserves exact operations --- operations where the result can be exactly represented at the virtual precision --- while Full MCA does not.
-
-\pytracer can only aggregate traces obtained from the same control flow path.
-In particular, program branches triggered by an unstable floating-point comparison lead to different control flows and result in parsing errors.
-For example, comparing a residual error or the distance between two points to a strict threshold in an iterative scheme generally results in unstable branches. 
-Full MCA even perturbs exact values such as integers represented with floating-point values, leading to many execution failures.
-For instance, the \texttt{fft1} example from SciPy raised an \texttt{ValueError: operands could not be broadcast together with shapes (601,) (600,)} error due to an array shape mismatch.
-A closer inspection showed that one of the arrays involved in the error was created with the NumPy function \texttt{linspace} that itself calls function \texttt{arange} (Listing~\ref{fig:pyarray_range_code}).
-Lines 3174-3178 show that the function stores the array size in a floating-point value that will be perturbed by Full MCA, as shown in Table~\ref{tab:mca_result_linspace}, resulting in array sizes that fluctuate between N and N+1.
-It is worth noting that 78\% of execution issues encountered in Full MCA mode instrumentation
-are due to this type of ``typing" errors.  
-Those code regions should not be perturbed by MCA since the injected noise does not make sense\gkmod{}{; however, given the typing errors in the source code, they are still susceptible to naturally occurring floating point errors}.
-% \tristan{conclusion: ces regions du code ne devraient pas etre bruitees car le bruit n'a pas de sens ici (exemple du spin dans -1/2,1/2. Ca correspond aux ?}
-% While they do not lead to any numerical issue, typing errors should still be fixed
-% by improving the Full MCA mode instrumentation in order to preserve code correctness.
-% \tristan{do we really mean that given your answer to my comment below?}. 
-% \Yohan{By reading again this sentence, I agree that it is confusing. 
-% It suggests that we should fixed the code while my idea was to fix the MCA instrumentation.}
-% We provide solutions to help MCA better work with those cases in the discussion section.
-
-% \tristan{Check this last sentence, we need to provide some sort of recommendations}. \tristan{how about opening a PR in numpy to fix this error?}
-% \Yohan{For this case, they use the math.ceil to correctly round the number, I think the fix is more on the MCA side to
-% correctly handle exact number than on the NumPy side.}
-
-% \begin{figure}
-%     \begin{lstlisting}[language=Python,style=customPython,numbers=left, firstnumber=11]
-% # Number of sample points
-% N = 600
-% # sample spacing
-% T = 1.0 / 800.0
-% x = np.linspace(0.0, N*T, N, endpoint=False)
-% y = np.sin(50.0 * 2.0*np.pi*x) + 0.5*np.sin(80.0 * 2.0*np.pi*x)
-% yf = fft(y)
-% w = blackman(N)
-% ywf = fft(y*w)
-%     \end{lstlisting}
-%     \label{fig:fft1_code}
-% \caption{Code snippet from \texttt{fft\_1D} illustrating issue arising when using Full MCA mode.
-% Line 19 raises \texttt{ValueError: operands could not be broadcast together with shapes (601,) (600,)} since
-% arrays \texttt{y} and \texttt{w} do not have the same shape. This is due to random errors introduces by 
-% Full MCA mode in the \texttt{linspace} function.
-% }
-% \end{figure}
-
-% \begin{figure}
-%     \begin{lstlisting}[language=Python,style=customPython,numbers=left, firstnumber=1, mathescape=true]
-% def linspace(start, stop, num=50, endpoint=True, retstep=False, dtype=None,
-%              axis=0):
-%     num = operator.index(num) // 3 $\lstsetnumber{\ldots}$
-%     ...$\lstresetnumber\setcounter{lstnumber}{5}$
-%     div = (num - 1) if endpoint else num // 6  $\lstsetnumber{\ldots}$
-%     ...$\lstresetnumber\setcounter{lstnumber}{13}$
-%     delta = stop - start // 14
-%     y = _nx.arange(0, num, dtype=dt).reshape((-1,) + (1,) * ndim(delta)) // 15
-%     \end{lstlisting}
-%     \label{fig:linspace_code}
-% \caption{Code snippet from \texttt{linspace} function from numpy package. 
-%     It uses the \textit{arange} function implemented as a Cython function (fig.~\ref{fig:pyarray_range_code}) to create the array. 
-% }
-% \end{figure}
-
-\begin{listing}
-    \begin{lstlisting}[language=C,style=customC,numbers=left, firstnumber=3163, mathescape=true]
-/*NUMPY_API
-  Arange,
-*/
-NPY_NO_EXPORT PyObject *
-PyArray_Arange(double start, double stop, double step /* default 1 */, int type_num) 
-{
-    npy_intp length; 
-    PyArrayObject *range; $\lstsetnumber{\ldots}$
-    ...$\lstresetnumber\setcounter{lstnumber}{3173}$
-    double delta, tmp_len; $\lstsetnumber{\ldots}$
-    ...$\lstresetnumber\setcounter{lstnumber}{3176}$
-    delta = stop - start; 
-    tmp_len = delta/step; $\lstsetnumber{\ldots}$
-    ...$\lstresetnumber\setcounter{lstnumber}{3189}$
-        length = _arange_safe_ceil_to_intp(tmp_len); $\lstsetnumber{\ldots}$
-    ...$\lstresetnumber\setcounter{lstnumber}{3201}$
-    range = (PyArrayObject *)PyArray_New(&PyArray_Type, 1, &length, type_num, $\lstsetnumber{}$
-                        NULL, NULL, 0, 0, NULL);
-    \end{lstlisting}
-\caption{Source code of the \texttt{PyArray\_Range} Cython function called by NumPy function \texttt{linspace} to create an array of equally-spaced elements.
-The temporary array size assigned in line 3178 is stored as a floating-point value and is therefore perturbed in Full MCA mode, leading to differences amplified by the use of ceil rounding at line 3190 and resulting in different array sizes across MCA-perturbed executions.
-See also Table~\ref{tab:mca_result_linspace}.}
-    \label{fig:pyarray_range_code}
-
-\end{listing}
-
-\begin{table}[]
-    \centering
-    \footnotesize
-    \begin{tabularx}{{\textwidth}}{cccc>{\centering\arraybackslash}X>{\centering\arraybackslash}X>{\centering\arraybackslash}X}
-                \thickhline
-    \textbf{Mode}  & \textbf{start} & \textbf{stop} & \textbf{step} & \textbf{delta} & \textbf{tmp\_len} & \textbf{ceil(tmp\_len)}  \\
-    \hline
-    Exact & 0 & 600  & 1 & 600                             & 600                            & 600             \\
-    RR    & 0 & 600  & 1 & 600 $\pm$ 0.0                   & 600 $\pm$ 0.0                  & 600 $\pm$ 0.0   \\
-    MCA    & 0 & 600  & 1 & 599.9999999999999 $\pm$ 8e-14  & 600.0 $\pm$ 8e-14 &  600.01 $\pm$ 0.0995\\
-            \thickhline
-
-    \end{tabularx}
-    \caption{Results obtained through lines 3177-3190 in Listing~\ref{fig:pyarray_range_code}.
-In contrast with RR, Full MCA does not preserve exact operations which leads to an array length oscillating between 600 and 601.}
-    \label{tab:mca_result_linspace}
-\end{table}
-
-% \subsubsection{Overall numerical quality}
-
-% \begin{table}
-% \small
-% \begin{subfigure}[t]{.5\linewidth}
-%     \centering
-%     \begin{tabular}{|l|c|c|}
-%     \hline 
-%     Example & RR & MCA \\
-%     \hline
-%     \discreteCosineRF & 52 & 47 \\ 
-%     \fftOneDRf & 41 & \swarn \\
-%     \fftTwoDRf & 52 & 52  \\
-%     \hline
-%     \interOneDRf & 51 & \swarn   \\
-%     \multiRf & 51 & \swarn \\
-%     \bsplineRf & 10 & 10  \\
-%     \splineOneDRf & 52 & 52 \\
-%     \splineTwoDRf & 10 & \swarn \\
-%     \hline
-%     \bfgsRf & 48 & 46 \\
-%     \globalRf & 17 & \swarn \\
-%     | SHGO\footnote{Simplicial Homology Global Optimization} & 25 & \swarn \\
-%     | Dual Annealing & 4 & \swarn \\
-%     | Differential Evolution & 0 & \swarn \\
-%     | Basin Hopping & 40 & \swarn \\
-%     | SHGO Sobol & 45 & \swarn \\
-%     \slsqpRf & 45 & 44 \\
-%     \lsmRf & 48 & \swarn \\
-%     \nelderRf & 44 & 42  \\
-%     \ncgRf & 48 & 47 \\
-%     \rootRf & 52 & 50 \\
-%     \rootLargRf & 29 & 26   \\
-%     \rootLargePredRf & 42 & 42 \\
-%     \trustExactRf & 48 & 46  \\
-%     \trustTruncRf & 48 & 46  \\
-%     \trustNCGRf & 52 & 47 \\
-%     \hline
-%     \end{tabular}
-% \end{subfigure}
-% \hspace{1cm}
-% \begin{subfigure}[t]{.5\linewidth}
-%     \begin{tabular}{|l|c|c|}
-%     \hline 
-%     Example & RR & MCA \\
-%     \hline
-%     \AdaboostRf & 48 & \swarn \\
-%     \brrRf & 25 & \scross  \\
-%     | $1^{st}$ dataset & nan & \scross \\
-%     | $2^{nd}$ dataset & 20 & \scross \\
-%     \onlineClassifierComparisonRf & 48 & \swarn  \\
-%     \kmeansRf & 52 & \swarn   \\
-%     \covarianceRf & 48 & \swarn   \\
-%     \decisionRf & 50 & 50  \\
-%     \digitsRf & 52 & 52 \\
-%     \faceRf & \scross & \scross \\
-%     \penaltyRf & - & -   \\
-%     \lassoRf & 48 & 47  \\
-%     \hyperplaneRf & 3 & \swarn  \\
-%     \mnistRf & 43 & \swarn \\
-%     \multitaskRf & 50 & 48   \\
-%     \ompRf & 52 & 52  \\
-%     \pcaRf & 48 & 48   \\
-%     \robustRf & 50 & 48   \\
-%     | Linear & 48 & 46 \\
-%     | RANSAC & 50 & 48 \\
-%     \toyRf & 35 & \swarn \\
-%     \svmRf & 43.5 &  \swarn  \\
-%     | Non-weighted & 44 & \swarn \\
-%     | Weighted & 43 & \swarn \\
-%     \tomographyRf & \swarn & \swarn  \\
-%     \weightedRf & 44 & \swarn   \\
-%     \hline
-%     \end{tabular}
-% \end{subfigure}
-%     \caption{Summary of examples precision for main outputs of SciPy (left) and scikit-learn (right) examples. 
-%     \textit{\swarn} values indicate runtime errors or an impossible traces aggregation,
-%     \scross values indicate numerical errors, and \textit{nan} stands for (\texttt{Not-A-Number}).
-%     The names example are linked to their source code.
-%     % \tristan{explain the meaning of nans here}
-%     \tristan{let's discuss the possibility to merge Table 4 in Tables 1 and 2}
-%     }
-%     \label{tab:pytracer_test_precision_summary}
-% \end{table}
-
-\subsection{SciPy}
-\label{sec:scipy_tests}
-
+\section{SciPy}
 We tested \pytracer on SciPy examples provided in the tutorial website section.
-% \tristan{Are these tests? If not we need to reword the begining of this section (I can do it, just let me know).}.
-% \Yohan{No you right, these are examples, not tests, I used the two words interchangeably.}
-SciPy is organized in several libraries targeting specific computing domains.
-We focused on \texttt{fftpack} (Fast Fourier Transform routines), \texttt{interpolate} (interpolation and smoothing splines), and \texttt{optimize} (Optimization and root-finding routines).
-
-\subsubsection{FFT}
-
-This package has three examples : \texttt{discrete\_cosine\_transform}, \texttt{fft\_1D}, and \texttt{fft\_2D}. All computations are done in double precision.
-The results for \texttt{discrete\_cosine\_transform},\texttt{fft\_1D} and  \texttt{fft\_2D} show
-precise numerical results with 48 significant bits on average. 
-We observe that the FFT computation is stable to noisy inputs. Figures~\ref{fig:fft1D_inputs} (inputs) and~\ref{fig:fft1D_outputs} (outputs)
-show the mean and standard deviation of the MCA samples. 
-The three columns correspond to the FFT computations of: 
-\begin{enumerate}
-\item $z_1 = \sin(50 . 2\pi . x_i) + \dfrac{1}{2} \sin(80 . 2\pi . x_i),\; x_i = \frac{i}{600},\; i \in [0,600]$
-\item $\mathrm{blackman}(400) \times z_1$
-\item $ z_2= e^{50 . i 2\pi . x_i} + \dfrac{1}{2} e^{-80 . i2\pi .x_i },\; x_i = \frac{i}{800},\; i \in [0,400] $
-\end{enumerate}
-
-Top row in Figures~\ref{fig:fft1D_inputs} and~\ref{fig:fft1D_outputs} 
-show the input mean value while the bottom row shows the standard deviation.
-The points with low magnitude in Figure~\ref{fig:fft1D_inputs} correspond 
-to inputs near 0 when the input of $\sin$ or 
-$\exp$ is close to $k\pi$, $k \in \mathbb{Z}$.
-Indeed, since MCA introduces a slight noise, the result is not exactly 0.
-We can see in Figure~\ref{fig:fft1D_inputs} 
-% \tristan{isn't it in Figure 3?} 
-% \Yohan{No figure 4, I'm talking about the MCA noise, so we look at the std}
-that the maximal noise introduced by MCA on the
-inputs is in the order of $10^{-14}$, two orders of magnitude higher than the 
-$ulp \simeq 10^-16$ for double precision. 
-This slight noise introduced can be interpreted as white noise on the input signal. 
-We can see on the bottom row of Figure~\ref{fig:fft1D_outputs} that the frequency noise is of 
-the same order of of magnitude as the input noise, which is expected. 
-The two peaks at x=38 and x=562 corresponds to the actual frequencies of the input signal.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figure/FFT/fft_x.pdf}
-    \caption{Absolute value of the mean and standard deviation values for 
-    fft 1D inputs within RR mode (log scale). The real part is shown in blue and the imaginary part in orange.}
-    \label{fig:fft1D_inputs}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figure/FFT/fft_y.pdf}
-    \caption{Absolute value of the mean and standard deviation values 
-    for fft 1D outputs within RR mode (log scale).}
-    \label{fig:fft1D_outputs}
-\end{figure}
-
-% \begin{figure}
-% \begin{minipage}{.5\textwidth}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/FFT/fft_x_real_sig_36.png}
-%     \caption{$\Re(x)$}
-%     \label{fig:my_label}
-% \end{minipage}
-% \begin{minipage}{.5\textwidth}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/FFT/fft_x_imag_sig_36.png}
-%     \caption{$\Im(x)$}
-%     \label{fig:my_label}
-% \end{minipage}
-% \begin{minipage}{.5\textwidth}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/FFT/fft_ret_real_sig_36.png}
-%     \caption{$\Re$(fft$(x))$}
-%     \label{fig:my_label}
-% \end{minipage}
-% \begin{minipage}{.5\textwidth}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/FFT/fft_ret_imag_sig_36.png}
-%     \caption{$\Im$(fft$(x))$}
-%     \label{fig:my_label}
-% \end{minipage}
-% \end{figure}
+SciPy is organized in several libraries targeting specific computing domains. We
+focused on \texttt{fftpack} (Fast Fourier Transform routines),
+\texttt{interpolate} (interpolation and smoothing splines), and
+\texttt{optimize} (Optimization and root-finding routines).
 
@@
 
-This package has five examples: \texttt{interpolation\_1D}, \texttt{multivariate\_data}, \texttt{bspline}, \texttt{spline\_1D} and \texttt{spline\_2D}.
+This package has five examples: \texttt{interpolation\_1D},
+\texttt{multivariate\_data}, \texttt{bspline}, \texttt{spline\_1D} and
+\texttt{spline\_2D}.
 
-\texttt{interpolation\_1D} interpolates function $f(x)=\cos(\frac{-x^2}{9})$ with 11 points $x\in[0,10]$.
-For the five interpolation methods tested (linear, cubic, nearest, previous, next), the solution found is precise, up to 51 bits out of the 53 available.
+\texttt{interpolation\_1D} interpolates function $f(x)=\cos(\frac{-x^2}{9})$
+with 11 points $x\in[0,10]$. For the five interpolation methods tested (linear,
+cubic, nearest, previous, next), the solution found is precise, up to 51 bits
+out of the 53 available.
 
-\texttt{multivariate\_data} interpolates the grid $f(x,y)=x(1-x)\cos(4\pi.x)  \sin(4\pi.y^2)^2$ with $(x,y) \in [0,1] \times [0,1]$.
-It samples 1,000 points for each coordinate and uses three interpolation methods: nearest, linear and cubic.
-Our results show a precision of 51 bits on average for the three methods.
+\texttt{multivariate\_data} interpolates the grid $f(x,y)=x(1-x)\cos(4\pi.x)
+    \sin(4\pi.y^2)^2$ with $(x,y) \in [0,1] \times [0,1]$. It samples 1,000 points
+for each coordinate and uses three interpolation methods: nearest, linear and
+cubic. Our results show a precision of 51 bits on average for the three methods.
 
-\texttt{bspline} compares two edge filters: \texttt{bisplev} evaluates a bivariate B-spline and its derivative whereas \texttt{convolved2d} convolves two 2-dimensional arrays.
-Figure~\ref{fig:bspline_rr}
-shows the significant bits, mean, and standard deviation 
-% \tristan{replace the figure references with labels in the figure, it would be much clearer} 
-maps for the two methods as well as the input image (Fig.~\ref{fig:bspline_original_image}).
-The middle row shows \texttt{sepfir2d} results and the bottom row shows \texttt{convol2d} results.
-Both methods exhibit similar precision, with 11 significant bits on average.
-Standard deviations maps on Figures~\ref{fig:bspline_bisplev_std} and~\ref{fig:bspline_convol2d_std} show that regions with low spatial frequencies correspond to regions with low standard deviation, similar to the FFT results.
-The SciPy tutorial mentions that \texttt{bisplev} is faster than \texttt{convol2d}.
-The comparable numerical precision observed in our experiments reinforce the use of \texttt{bisplev} over \texttt{convol2d} in this example.
+\texttt{bspline} compares two edge filters: \texttt{bisplev} evaluates a
+bivariate B-spline and its derivative whereas \texttt{convolved2d} convolves two
+2-dimensional arrays. Figure~\ref{fig:bspline_rr} shows the significant bits,
+mean, and standard deviation maps for the two methods as well as the input image
+(Fig.~\ref{fig:bspline_original_image}). The middle row shows \texttt{sepfir2d}
+results and the bottom row shows \texttt{convol2d} results. Both methods exhibit
+similar precision, with 11 significant bits on average. Standard deviations maps
+on Figures~\ref{fig:bspline_bisplev_std} and~\ref{fig:bspline_convol2d_std} show
+that regions with low spatial frequencies correspond to regions with low
+standard deviation, similar to the FFT results. The SciPy tutorial mentions that
+\texttt{bisplev} is faster than \texttt{convol2d}. The comparable numerical
+precision observed in our experiments reinforce the use of \texttt{bisplev} over
+\texttt{convol2d} in this example.
 
-\texttt{spline\_1D} computes the 1D spline interpolation for $f(x)=\sin(x)$ on points $x=\frac{2\pi k}{8}, k \in [0, 10]$.
-The spline interpolation uses \texttt{splrep} to build the spline representation and \texttt{splrev} to evaluate the spline at any point.
-It also computes the integral by using \texttt{splint} and the root finder \texttt{sproot}.
-Although the traces diverge, we can analyze the partial aggregation for the \texttt{splrep}, \texttt{splev} and \texttt{splint}.
-The three functions show results with an average precision of 51 bits with RR mode.
+\texttt{spline\_1D} computes the 1D spline interpolation for $f(x)=\sin(x)$ on
+points $x=\frac{2\pi k}{8}, k \in [0, 10]$. The spline interpolation uses
+\texttt{splrep} to build the spline representation and \texttt{splrev} to
+evaluate the spline at any point. It also computes the integral by using
+\texttt{splint} and the root finder \texttt{sproot}. Although the traces
+diverge, we can analyze the partial aggregation for the \texttt{splrep},
+\texttt{splev} and \texttt{splint}. The three functions show results with an
+average precision of 51 bits with RR mode.
 
-\texttt{spline\_2D} computes the 2D spline interpolation for function $z=(x+y)e^{-6(x^2+y^2)}$, with $(x,y) \in [-1,1]\times[-1,1]$ and a sampling of 21 points for each coordinate.
-\texttt{bisplrep} builds the spline representation with the $21 \times 21$ points of $z$ over 71 grid sampling points for $(x,y)$.
-Figure~\ref{fig:spline2d_rr} shows the results of the spline evaluation with \texttt{bisplev}.
-We observe a significant loss of precision in places, which follows
-an interesting pattern that could be further investigated.
-
-% \begin{figure}
-% \begin{minipage}{.3\textwidth}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/multivariate_data/nearest_ret_mean_log.png}
-% \end{minipage}
-% \begin{minipage}{.3\textwidth}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/multivariate_data/linear_ret_mean_log.png}
-% \end{minipage}
-% \begin{minipage}{.3\textwidth}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/multivariate_data/cubic_ret_mean_log.png}
-% \end{minipage}
-
-% \begin{minipage}{.3\textwidth}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/multivariate_data/nearest_ret_std_log.png}
-% \end{minipage}
-% \begin{minipage}{.3\textwidth}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/multivariate_data/linear_ret_std_log.png}
-% \end{minipage}
-% \begin{minipage}{.3\textwidth}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/multivariate_data/cubic_ret_std_log.png}
-% \end{minipage}
-%     \label{fig:multivariate_data_RR}
-%     \caption{\texttt{multivariate\_data} results within RR mode. Each column represents an 
-%     interpolation scheme, with from left to right, the nearest, linear and cubic method.
-%     Top row shows the log of the absolute mean value value while bottom row shows the log of the
-%     standard deviation. We can see that precision drops between local extremum when the 
-%     mean value is close to 0.}
-% \end{figure}
+\texttt{spline\_2D} computes the 2D spline interpolation for function
+$z=(x+y)e^{-6(x^2+y^2)}$, with $(x,y) \in [-1,1]\times[-1,1]$ and a sampling of
+21 points for each coordinate. \texttt{bisplrep} builds the spline
+representation with the $21 \times 21$ points of $z$ over 71 grid sampling
+points for $(x,y)$. Figure~\ref{fig:spline2d_rr} shows the results of the spline
+evaluation with \texttt{bisplev}.  We observe a significant loss of precision in
+places, which follows an interesting pattern that could be further investigated.
 
@@
 
-\begin{figure}
-\begin{subfigure}{.3\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure/spline_2d/bisplev_mean.pdf}
-    \caption{Mean value}
-    \label{fig:bisplev_mean}
-\end{subfigure}
-\begin{subfigure}{.3\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure/spline_2d/bisplev_mean_log.pdf}
-    \caption{Absolute mean value (log)}
-    \label{fig:bisplev_mean_log}
-\end{subfigure}
-\begin{subfigure}{.3\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure/spline_2d/bisplev_std_log.pdf}
-    \caption{Standard deviation (log)}
-    \label{fig:bisplev_std_log}
-\end{subfigure}
-    \caption{2D Spline interpolation results. Figure~\ref{fig:bisplev_mean} shows the mean result
-    of the 2D-spline interpolation. Figures~\ref{fig:bisplev_mean_log} and~\ref{fig:bisplev_std_log}
-    show respectively in the logarithmic scale the absolute mean value and the standard deviation 
-    of the 5 samples run within RR mode. 
-    % \tristan{any reason why you are showing the ieee result?} \tristan{can you use the same color maps as in figure 8?}
-    }
-    \label{fig:spline2d_rr}
-\end{figure}
+\subsection{FFT}
 
-\subsubsection{Optimization}
+This package has three examples : \texttt{discrete\_cosine\_transform},
+\texttt{fft\_1D}, and \texttt{fft\_2D}. All computations are done in double
+precision. The results for \texttt{discrete\_cosine\_transform},\texttt{fft\_1D}
+and  \texttt{fft\_2D} show precise numerical results with 48 significant bits on
+average. We observe that the FFT computation is stable to noisy inputs.
+Figures~\ref{fig:fft1D_inputs} (inputs) and~\ref{fig:fft1D_outputs} (outputs)
+show the mean and standard deviation of the MCA samples. The three columns
+correspond to the FFT computations of:
+\begin{enumerate}
+    \item $z_1 = \sin(50 . 2\pi . x_i) + \dfrac{1}{2} \sin(80 . 2\pi . x_i),\; x_i = \frac{i}{600},\; i \in [0,600]$
+    \item $\mathrm{blackman}(400) \times z_1$
+    \item $ z_2= e^{50 . i 2\pi . x_i} + \dfrac{1}{2} e^{-80 . i2\pi .x_i },\; x_i = \frac{i}{800},\; i \in [0,400] $
+\end{enumerate}
 
-This package has eleven examples. Seven examples involve the same optimization problem 
-solved with and without constraints using different methods.
-One example optimizes a chemical problem under constraints.
-The last three examples solve a different problem each.
+\add{The} top row in Figures~\ref{fig:fft1D_inputs} and~\ref{fig:fft1D_outputs} show the
+input mean value while the bottom row shows the standard deviation. The points
+with low magnitude in Figure~\ref{fig:fft1D_inputs} correspond to inputs near 0
+when the input of $\sin$ or $\exp$ is close to $k\pi$, $k \in \mathbb{Z}$.
+Indeed, since MCA introduces a slight noise, the result is not exactly 0. We can
+see in Figure~\ref{fig:fft1D_inputs} that the maximal noise introduced by MCA on
+the inputs is in the order of $10^{-14}$, two orders of magnitude higher than
+the $ulp \simeq 10^-16$ for double precision. This slight noise introduced can
+be interpreted as white noise on the input signal. We can see on the bottom row
+of Figure~\ref{fig:fft1D_outputs} that the frequency noise is of the same order
+of of magnitude as the input noise, which is expected. The two peaks at x=38 and
+x=562 corresponds to the actual frequencies of the input signal.
 
-\paragraph{Unconstrained minimization of multivariate scalar functions:}
-Four Quasi-Newton-Raphson methods minimize function $f$ by using Newton's step: $x_{k+1} = x_{k} - B^{-1}(x_k)\nabla f(x_k)$, where $\nabla$ and $B$ are the gradient and the approximation of the Hessian matrix of $f$.
-The \texttt{Broyden-Fletcher-Goldfarb-Shanno}~\cite{BFGS} (BFGS) and \texttt{Newton-Conjugate-Gradient}~\cite{nocedal2006numerical} (NCG) are line search methods that approximate $H$ by adding two symmetric rank-one matrices and by using the Conjugate-Gradient method.
-The \texttt{Trust-Region Truncated Generalized Lanczos / Conjugate Gradient}~\cite{gould1999solving} (TR-Krylov), \texttt{Trust-Region Newton-Conjugate-Gradient} (TR-NCG), and \texttt{Trust-Region Nearly Exact}~\cite{nocedal2006numerical} (TR-Exact) are trust-region methods approximating $H$ by solving the trust-region subproblem restricted to a truncated Krylov subspace and by solving nonlinear equations for each quadratic subproblem.
-In addition, the \texttt{Nelder-Mead}~\cite{singer2009nelder} simplex-based method iteratively transforms a simplex until its vertices are getting closer to a local minima of the function.
-All methods are applied to the Rosenbrock function.
+\subsection{Optimization}
 
-\paragraph{Constrained minimization of multivariate scalar functions:}
+This package has eleven examples. Seven examples involve the same optimization
+problem solved with and without constraints using different methods. One example
+optimizes a chemical problem under constraints. The last three examples solve a
+different problem each.
+
+\subsubsection{Unconstrained minimization of multivariate scalar functions}
+Four Quasi-Newton-Raphson methods minimize function $f$ by using Newton's step:
+$x_{k+1} = x_{k} - B^{-1}(x_k)\nabla f(x_k)$, where $\nabla$ and $B$ are the
+gradient and the approximation of the Hessian matrix of $f$. The
+\texttt{Broyden-Fletcher-Goldfarb-Shanno}~\cite{BFGS} (BFGS) and
+\texttt{Newton-Conjugate-Gradient}~\cite{nocedal2006numerical} (NCG) are line
+search methods that approximate $H$ by adding two symmetric rank-one matrices
+and by using the Conjugate-Gradient method. The \texttt{Trust-Region Truncated
+    Generalized Lanczos / Conjugate Gradient}~\cite{gould1999solving} (TR-Krylov),
+\texttt{Trust-Region Newton-Conjugate-Gradient} (TR-NCG), and
+\texttt{Trust-Region Nearly Exact}~\cite{nocedal2006numerical} (TR-Exact) are
+trust-region methods approximating $H$ by solving the trust-region subproblem
+restricted to a truncated Krylov subspace and by solving nonlinear equations for
+each quadratic subproblem. In addition, the
+\texttt{Nelder-Mead}~\cite{singer2009nelder} simplex-based method iteratively
+transforms a simplex until its vertices are getting closer to a local minima of
+the function. All methods are applied to the Rosenbrock function.
+
+\paragraph{Constrained minimization of multivariate scalar functions}
 Two optimizers solve an optimization problem by taking into account constraints.
-The \texttt{Sequential Least SQuares Programming} uses the SLSQP~\cite{kraft1988software} method to optimize the Rosenbrock function.
-The \texttt{Least-squares minimization} uses the Trust Region Reflective algorithm~\cite{li1993centering}
-to solve a fitting problem from an enzymatic reaction.
+The \texttt{Sequential Least SQuares Programming} uses the
+SLSQP~\cite{kraft1988software} method to optimize the Rosenbrock function. The
+\texttt{Least-squares minimization} uses the Trust Region Reflective
+algorithm~\cite{li1993centering} to solve a fitting problem from an enzymatic
+reaction.
 
-\paragraph{}
-The SLSQP and unconstrained minimization methods minimize the \textbf{Rosenbrock} function of $N$ variables
-that reaches its minimum (0) when $x_i=1,\; \forall i \leq N-1$:
-\[f(x) = \sum_{i=1}^{N-1} 100(x_{i+1}-x^2_i)^2 + (1-x_i)^2\]
-% The minimum value of this function is 0, reached when $x_i=1,\; \forall i \leq N-1$. % \tristan{for all i's?}
-
-Figure~\ref{fig:unconstrained_optimization} shows the number of significant bits of the solution for the different methods used. 
-The $(p)$ notation for the NCG, Trust-Krylov, and Trust-NCG methods in the legend refers 
-to the variant where the Hessian matrix is replaced by 
-a function computing the matrix-vector product of the Hessian and an arbitrary vector, to save memory and time.
-All the methods have a good precision ranging from 43 to 53 significant bits.
-The Nelder-Mead method is the least precise one with $\simeq$ 43 significant bits on average, while the Trust-Region-Newton-CG is the most precise one with $\simeq$ 53 significant bits, the highest precision achievable in double precision.
-The remaining methods have a similar precision.
-% \tristan{why is there only 9 methods in Fig 7 while you mentioned 10?} \Yohan{There are 11 examples whose 6 for the unconstrained minimization (presented in Fig 7).
-For 3 methods, there is a variant using the Hessian product instead of the Hessian matrix.I realized that this variant is not explained in the text.
-I will update it.}
+The SLSQP and unconstrained minimization methods minimize the
+\textbf{Rosenbrock} function of $N$ variables that reaches its minimum (0) when
+$x_i=1,\; \forall i \leq N-1$:
+$f(x) = \sum_{i=1}^{N-1} 100(x_{i+1}-x^2_i)^2 + (1-x_i)^2$.
+Figure~\ref{fig:unconstrained_optimization} shows the number of significant bits
+of the solution for the different methods used. The $(p)$ notation for the NCG,
+Trust-Krylov, and Trust-NCG methods in the legend refers to the variant where
+the Hessian matrix is replaced by a function computing the matrix-vector product
+of the Hessian and an arbitrary vector, to save memory and time. All the methods
+have a good precision ranging from 43 to 53 significant bits. The Nelder-Mead
+method is the least precise one with $\simeq$ 43 significant bits on average,
+while the Trust-Region-Newton-CG is the most precise one with $\simeq$ 53
+significant bits, the highest precision achievable in double precision. The
+remaining methods have a similar precision.
 
 The SLSQP also minimizes the Rosenbrock function with the following constraint:
-\begin{eqnarray*}
-    x_0 + 2x_1 \leq 1 \\
-    x_0^2 + x_1 \leq 1 \\
-    x_0^2 - x_1 \leq 1 \\
-    2x_0 + x_1 = 1 \\
-    0 \leq x_0 \leq 1 \\
-    -0.5 \leq x_1 \leq 2 
-\end{eqnarray*}
-The problem has a unique solution $[x_0, x_1] = [0.4149, 0.1701]$.
-Results obtained with RR show a precision of 47 and 44 significant bits for the first and the second solution. %\tristan{which method is tested?}.
+$x_0$ + $2x_1$ $\leq$ 1
+$x_0^2$ + $x_1$ $\leq$ 1
+$x_0^2$ - $x_1$ $\leq$ 1
+$2x_0$ + $x_1$ = 1
+0 $\leq$ $x_0$ $\leq$ 1
+-0.5 $\leq$ $x_1$ $\leq$ 2.
+% \begin{eqnarray*}
+%     x_0 + 2x_1 \leq 1 \\
+%     x_0^2 + x_1 \leq 1 \\
+%     x_0^2 - x_1 \leq 1 \\
+%     2x_0 + x_1 = 1 \\
+%     0 \leq x_0 \leq 1 \\
+%     -0.5 \leq x_1 \leq 2 
+% \end{eqnarray*}
+The problem has a unique solution $[x_0, x_1] = [0.4149, 0.1701]$. Results
+obtained with RR show a precision of 47 and 44 significant bits for the first
+and the second solution. %\tristan{which method is tested?}.
 
@@
 \end{eqnarray*}
-where where $y_i$ are measurement values, $u_i$ are values of the independent variable, and
-$x_i$ the unknown.
-Results within RR show a precision of 51, 46, 47, and 48 significant bits for each component of the solution respectively.% \tristan{which solver is used?}.
+where where $y_i$ are measurement values, $u_i$ are values of the independent
+variable, and $x_i$ the unknown. Results within RR show a precision of 51, 46,
+47, and 48 significant bits for each component of the solution
+respectively.% \tristan{which solver is used?}.
 
-\paragraph{Root finding:}
+\subsubsection{Root finding}
 % We tested three root finder algorithms with one for small problems using the hybrid Powell and Levenberg-Marquardt methods  (\texttt{root\_finding}) and two for large problems using a Krylov approximation for the inverse Jacobian with and without the help of a preconditioner (\texttt{root\_finding\_large\_preconditionned} and \texttt{root\_finding\_large}).
 
-The \texttt{root\_*} examples use three algorithms to 
-find the root of non-linear equations. \texttt{root\_finding}
-uses the hybrid Powell method to solve a single-variable transcendental equation and 
-the Levenberg-Marquardt method for a set of non-linear equations. 
-\texttt{root\_finding\_large} and \texttt{root\_finding\_large\_preconditioned} examples use 
-the Krylov method to approximate the inverse Jacbian with and without the help of a preconditioner. 
-They solve an integrodifferential equation on a square
- $(x,y) \in [0,1] \times [0,1]$, $P(x,1)=1$, and $P=0$ elsewhere on the boundary.
-The function $P$ is discretized with a Cartesian grid $P_{n,n}=P(nh,nh)$, with $n=75$, and its derivatives are approximated by $\partial_x^2P(x,y) \simeq (P(x+h,y) - 2P(x,y) + P(x-h,y))/h^2$.
+The \texttt{root\_*} examples use three algorithms to find the root of
+non-linear equations. \texttt{root\_finding} uses the hybrid Powell method to
+solve a single-variable transcendental equation and the Levenberg-Marquardt
+method for a set of non-linear equations. \texttt{root\_finding\_large} and
+\texttt{root\_finding\_large\_preconditioned} examples use the Krylov method to
+approximate the inverse Jac\add{o}bian with and without the help of a preconditioner.
+They solve an integrodifferential equation on a square $(x,y) \in [0,1] \times
+    [0,1]$, $P(x,1)=1$, and $P=0$ elsewhere on the boundary. The function $P$ is
+discretized with a Cartesian grid $P_{n,n}=P(nh,nh)$, with $n=75$, and its
+derivatives are approximated by $\partial_x^2P(x,y) \simeq (P(x+h,y) - 2P(x,y) +
+    P(x-h,y))/h^2$.
 
@@
 
-% \begin{itemize}
-% \item broyden: RR 47 bits solution / MCA divergence 
-% \item global\_optimization: RR divergence / MCA issues
-% \item sqlsp: RR 46 bits solution / MCA 46 bits solution
-% \item least\_square\_minimization : RR 48 bits solution / MCA index issue
-% \item nelder\_mean\_simplex : RR 43 bits solution / MCA stable
-% \item newton\_conjugate\_gradient: RR 48 bits solution / MCA divergence
-% \item root\_finding\_large\_preconditionned : RR divergence / MCA divergence 3/5 converged
-% \item root\_finding\_large : RR divergence / MCA divergence (fgmres very low!) 3/5 converged
-% \item trust\_region\_exact : RR 47 bit solution / RR 45 bit solution
-% \item trust\_region\_truncated\_generalized\_lanczos : RR 48 bits solution / MCA 46 bits solution
-% \end{itemize}
-
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/nelder_mead/timeline_sig.png}
-%     \caption{Nelder-Mead: average of number of significant bits over time. 
-%     Solver ends when accuracy is reaching the tolerance.
-%     }
-%     \label{fig:my_label}
-% \end{figure}
-
 \subsection{Scikit learn}
@@
 
-Scikit-learn offers a well-supplied and documented list of examples 
-% \tristan{examples ou tests? Si ce sont des tests, utilisons "test" partout a la place de "examples" ou "applications", pour sklearn comme pour scipy.} 
-that facilitates its use with Pytracer.
-Among the several available examples, we choose the following representative set
-listed in Table~\ref{tab:pytracer_results_summary}. The following paragraphs 
-focus on the most interesting stability results observed across all experiments.
-% \tristan{Shall we just refer to Table 4 and remove this lengthy list? You could add the links in the table and mention in the table caption that the tests are linked to their source code}:
+Scikit-learn offers a well-supplied and documented list of examples that
+facilitates its use with Pytracer. Among the several available examples, we
+choose the following representative set listed in
+Table~\ref{tab:pytracer_results_summary}. The following paragraphs focus on the
+most interesting stability results observed across all experiments.
 
-% \subsubsection{Classifier comparisions}
+\subsubsection{Separating hyperplane}
 
-% This test compares the performance of 6 online solvers on the hand-written digits dataset.
-% These 6 solvers are:
-% \begin{itemize}
-%     \item Stochastic Gradient Descent 
-%     \item Averaged Stochastic Gradient Decent
-%     \item Perceptron
-%     \item Passive-Aggressive I \& II
-%     \item SAG: Minimizing Finite Sums with the Stochastic Average Gradient
-% \end{itemize}
-
-% Each solver is trained and predicts 20 times on 6 different training size ratio.
-% Figure~\ref{fig:classifier_comparisons_general} shows the all functions
-% traced by Pytracer over time. We can see the estimated number of significant digits varies a lot between 
-% values from 1 to 80 bits. Figure~\ref{fig:classifier_comparisons_mean_predictions} shows 
-% the average prediction score for each classifiers. The yellow points 
-% represent the average correct prediction score for one round and one classifier (line. 48) while blue points
-% tshows average predictions over the 20 rounds (line. 49).
-% We can see that precision is pretty low with an average solution below 10 significant bits, with 
-% an exception for values between the 24k and 32k invocation that correspond to the Perceptron
-% classifier. Indeed, this classifier is pretty stable with an average number of significant digits around 52 bits.
-
-% \begin{figure}
-%     \begin{lstlisting}[language=Python,style=customPython,numbers=left, firstnumber=19]
-% heldout = [0.95, 0.90, 0.75, 0.50, 0.01]
-% rounds = 20
-% X, y = datasets.load_digits(return_X_y=True)
-
-% classifiers = [
-%     ("SGD", SGDClassifier(max_iter=100)),
-%     ("ASGD", SGDClassifier(average=True)),
-%     ("Perceptron", Perceptron()),
-%     ("Passive-Aggressive I", PassiveAggressiveClassifier(loss='hinge',C=1.0, tol=1e-4)),
-%     ("Passive-Aggressive II", PassiveAggressiveClassifier(loss='squared_hinge',C=1.0, tol=1e-4)),
-%     ("SAG", LogisticRegression(solver='sag', tol=1e-1, C=1.e4 / X.shape[0]))
-% ]
-
-% xx = 1. - np.array(heldout)
-
-% for name, clf in classifiers:
-%     print("training %s" % name)
-%     rng = np.random.RandomState(42)
-%     yy = []
-%     for i in heldout:
-%         yy_ = []
-%         for r in range(rounds):
-%             X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=i, random_state=rng)
-%             clf.fit(X_train, y_train)
-%             y_pred = clf.predict(X_test)
-%             yy_.append(1 - np.mean(y_pred == y_test))
-%         yy.append(np.mean(yy_))
-%     plt.plot(xx, yy, label=name)
-%     \end{lstlisting}
-%     \label{fig:wrapper_code}
-% \caption{}
-% \end{figure}
-
-% \begin{figure}
-%     \centering
-%     \caption{Caption}
-%     \includegraphics[width=\linewidth]{figure/classifier_comparisons/SAG_predicition_s.png}
-%     \caption{Number of significant digits (General view).}
-%     \label{fig:classifier_comparisons_general}
-% \end{figure}
-
-% \begin{figure}
-%     \centering
-%     \caption{Caption}
-%     \includegraphics[width=\linewidth]{figure/classifier_comparisons/zoom_SAG_fit_coef_s.png}
-%     \caption{Number of significant digits (General view).}
-%     \label{fig:classifier_comparisons_general}
-% \end{figure}
-
-% \subsubsection{Adaboost}
-
-% \tristan{For all the paragraphs below, add a sentence to describe the results as you did for scipy.
-If you have nothing more to say than what is reported in Table 4, then remove the paragraphs describing the algorithms and just refer to the sklearn doc linked from the table.
-If you have interesting things to discuss only for some examples, mention in the section intro that the text focuses on the most interesting stability patterns observed across all experiments.}
-
-% \paragraph{Adaboost}
-% This test compares a decision tree boosted with 300 estimators using the AdaBoost.R2~\cite{drucker1997improving} algorithm with
-% a single decision tree regressor on a 1D sinusoidal dataset with a small amount of Gaussian noise and a depth fixed at 4. 
-% The example shows that as the number of boosts is increased the regressor can fit more detail.
-
-% RR Good 48 \\
-% MCA: arange issue /  bootstrap\_idx = random\_state.choice(a=np.arange(\_num\_samples(X)), size=\_num\_samples(X), replace=True, p=sample\_weight) / len(a) != len(p)
-
-% \paragraph{Online classifier comparison}
-% This example compares how the following online solvers perform on the hand-written digits dataset:
-% Stochastic Gradient Descent (SGD) with maximum iterations fixed to 100, 
-% Averaged Stochastic Gradient Descent (ASGD),
-% Perceptron, Passive-Aggressive I with the hinge loss function, tolerance 
-% and regularization fixed at $10^{-4}$ and $1$,
-% Passive-Aggressive II with the squared hinge loss function, tolerance 
-% and regularization fixed at $10^{-4}$ and $1$, and Stochastic Average Gradient (SAG)
-% with the tolerance and regularization fixed at $10^{-4}$ and $5.10^{-8}$.
-
-% RR: stable 48 bits. \\
-% MCA: Index issue
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\linewidth]{figure/BRR/call_path.pdf}
-    \caption{Call paths of the Bayesian Ridge Regression (BRR) and 
-    Ordinary Least Square (OLS) function. Color represents the calling library:
-    orange for scikit-learn, blue for SciPy and yellow for LAPACK.
-    Dashed color represents the original path in red and the alternative one in green.
-    Figure~\ref{fig:brr_svd_sig} shows the original method  leads to numerical instabilities while the alternative one converges.
-    }
-    \label{fig:call_path_brr}
-\end{figure}
-
-\paragraph{Bayesian Ridge Regression}
-
-This example compares a Bayesian Ridge Regression (BRR) to the Ordinary Least Squares (OLS) estimator on a synthetic dataset and for one-dimensional regression using polynomial feature expansion.
-Although the example does not raise a runtime error, the regression coefficients computed from the fitting are
-non-significant. \pytracer traces reveal that the SVD solver used is the root cause for this error. 
-Figure~\ref{fig:call_path_brr} shows the two call paths for BRR and OLS. 
-The LAPACK library has two main methods for computing the SVD: \texttt{gesdd} and \texttt{gesvd}.
-The former uses a Divide \& Conquer approach, while the latter uses a QR decomposition. 
-While both methods are expected to have the same accuracy~\cite{nakatsukasa2013stable}, Figure~\ref{fig:brr_svd_sig} shows that \texttt{gesdd} is totally imprecise, with an average number of significant digits of 0 for BRR and even \texttt{Not-a-Number} (\texttt{NaN}) values for OLS.
-On the same figure, we can see that 
-using the \texttt{gesvd} (dgelsd) method instead of the \texttt{gesdd} (dgelss) one, 
-the SVD converges for RR and Full MCA, with a number of significant bits of 44 on average. 
-This observation supports the on-going discussion among LAPACK developers on the instability of \texttt{gesdd} (see  \href{https://github.com/Reference-LAPACK/lapack/issues/316}{github.com/Reference-LAPACK/lapack/issues/316}).
-
-% \tristan{t'es sur que c'est pas l'inverse? Sur la fig 9 on voit que dgelsd n'est pas precise du tout, ca suggere qu'elle utiliserait gesdd}. 
-% \tristan{ce paragraph est difficile a lire (mais neanmoins super interessant !).
-tu devrais le restructurer en expliquant (1) quelle methode utilise quel solver de quelle librairie, (2) la performance observee sur la fig 9 (tu pourais d'ailleurs ajouter le nom du solver (gesdd ou gesvd) entre parenthese dans la legende pour rendre l'explication plus claire, (3) le fait que ca confirme la discussion sur github et autres commentaires.}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figure/BRR/BRR_coefs_sig.pdf}
-    \caption{Precision of Bayesian Ridge Regression coefficients in RR mode.
-     \texttt{BRR\_*} show the \texttt{BayesianRidge} results
-    using the \texttt{gesdd} and \texttt{gesvd} methods. 
-    \texttt{OLS\_*} show the \texttt{LinearRegression} results
-    with the \texttt{dgelsd} and \texttt{dgelss} methods.
-   The Divide \& Conquer method 
-    (\texttt{gesdd} and  \texttt{dgelsd})
-    has low precision
-    for \textit{BRR} and results in \texttt{NaN} values (star points) for \textit{OLS}. By switching to the \texttt{gesvd} method, 
-    results have a precision of 42 bits on average.
-    }
-    \label{fig:brr_svd_sig}
-\end{figure}
-
-% the coefficient weights are slightly shifted toward zeros, which stabilises them.
-% As the prior on the weights is a Gaussian prior, the histogram of the estimated weights is Gaussian.
-% The estimation of the model is done by iteratively maximizing the marginal log-likelihood of the observations.
-% We also plot predictions and uncertainties for Bayesian Ridge Regression for one dimensional regression using polynomial feature expansion.
-Note the uncertainty starts going up on the right side of the plot.
-This is because these test samples are outside of the range of the training samples.
-
-% RR: solution mean 15-24 / std 20-30 \\
-% MCA: SVD did not converge
-
-% \paragraph{K-Means Clustering}
-% This test uses the K-means to cluster the IRIS dataset.
-% The plots display firstly what a K-means algorithm would yield using three clusters.
-It is then shown what the effect of a bad initialization is on the classification process: By setting n\_{init} to only 1 (default is 10), the amount of times that the algorithm will be run with different centroid seeds is reduced.
-The next plot displays what using eight clusters would deliver and finally the ground truth.
-
-% RR Very stable (labels with highest precision) \\
-% MCA: Divergence
-
-% \paragraph{Covariance estimation}
-% This example shows covariance estimation with Mahalanobis distances on Gaussian distributed data.
-
-% For Gaussian distributed data, the distance of an observation xi to the mode of the distribution can be computed using its Mahalanobis distance:
-
-% d(μ,Σ)(xi)2=(xi−μ)TΣ−1(xi−μ)
-% where μ and Σ are the location and the covariance of the underlying Gaussian distributions.
-
-% In practice, μ and Σ are replaced by some estimates.
-The standard covariance maximum likelihood estimate (MLE) is very sensitive to the presence of outliers in the data set and therefore, the downstream Mahalanobis distances also are.
-It would be better to use a robust estimator of covariance to guarantee that the estimation is resistant to “erroneous” observations in the dataset and that the calculated Mahalanobis distances accurately reflect the true organization of the observations.
-
-% The Minimum Covariance Determinant estimator (MCD) is a robust, high-breakdown point (i.e. it can be used to estimate the covariance matrix of highly contaminated datasets, up to
-
-% nsamples−nfeatures−12 outliers) estimator of covariance. The idea behind the MCD is to find
-
-% nsamples+nfeatures+12 observations whose empirical covariance has the smallest determinant, yielding a “pure” subset of observations from which to compute standards estimates of location and covariance.
-The MCD was introduced by P.J.Rousseuw in 1.
-
-% This example illustrates how the Mahalanobis distances are affected by outlying data.
-Observations drawn from a contaminating distribution are not distinguishable from the observations coming from the real, Gaussian distribution when using standard covariance MLE based Mahalanobis distances.
-Using MCD-based Mahalanobis distances, the two populations become distinguishable.
-Associated applications include outlier detection, observation ranking and clustering.
-
-% RR: Traces diverge but precision seems stable (~48bits) \\
-% Main computation is in a loop that might be take extra steps to ends. \\
-% MCA: arange issue
-
-% \paragraph{Decision Tree Regression}
-% This test uses a decision tree to fit a sine curve with added noise.
-
-% A 1D regression with decision tree.
-% The decision trees is used to fit a sine curve with addition noisy observation. As a result, it learns local linear regressions approximating the sine curve.
-% We can see that if the maximum depth of the tree (controlled by the max\_depth parameter) is set too high, the decision trees learn too fine details of the training data and learn from the noise, i.e.
-they overfit.
-
-% RR Fit ok (50bits) , missing predict \\
-% MCA Fit ok (50bits) , missing predict
-
-% \paragraph{Digits Classification}
-% This test uses a Support Vector Classifier to recognize images of hand-written
-% digits. The digits dataset consists of 8x8 pixel images of digits.
-
-% RR Very stable (highest precision) \\
-% MCA: Very stable (highest precision)
-
-\paragraph{Face Recognition}
-
-The face recognition example uses eigenfaces (eigenvectors) and Support Vector Machines (SVMs) to classify faces from the Labeled Faces in the Wild dataset.
-This example uses a Principal Component Analysis (PCA) to extract the eigenfaces and then trains an SVM classifier to predict the name associated with a face.
-This example is the only one to raise an error with RR due to the non-convergence of the Singular Value Decomposition (SVD) performed in the PCA.
-
-In this example, the PCA uses the Randomized SVD~\cite{halko2011finding} method that first computes a low-rank approximation of the input matrix using a stochastic algorithm and then uses this approximation as input for the SVD.
-The example raises an error during the computation of the SVD.
-The \texttt{randomized\_svd} scikit-learn function uses the Divide \& Conquer SVD method \texttt{gesdd} mentioned previously.
-Replacing \texttt{gesdd} for \texttt{gesvd} solves the SVD convergence issue.
-Figure~\ref{fig:randomized_svd_S} shows the precision of the eigenvalues computed with gesvd, which varies between 15 and 20 significant bits out of the 24 available in single precision.
-The classifier metrics (precision, recall, F1-score, and support) are identical to the IEEE execution for all MCA samples.
-
-In conclusion, \pytracer and the MCA model were helpful to detect the instability of the \texttt{gesdd} method mentioned in several GitHub issues, including the LAPACK repository.
-Furthermore, it is worth mentioning that a Pull Request has recently been submitted to let the user select the SVD method and avoid this kind of issue.
-Thus, \pytracer can detect instabilities that affect fundamental scientific computing components such as the LAPACK library.
-% The Pytracer findings can therefore be extended to many application domains.
-% % \tristan{conclusion needs to be discussed.
-Note to self: generaliser un peu la conclusion: pytracer permet de se rendre compte de problemes de stabilite dont plusieurs librairies sont dependantes.}
-
-\begin{figure}
-    \centering
-    \begin{subfigure}{0.3\linewidth}
-    \includegraphics[width=\linewidth]{figure/face_recognition/randomized_svd_ret_U_sig_zoom.png}
-    \caption{Left matrix $U$ of the SVD decomposition}
-    \label{fig:randomized_svd_U}
-    \end{subfigure}
-    \begin{subfigure}{0.3\linewidth}
-    \includegraphics[width=\linewidth]{figure/face_recognition/randomized_svd_ret_S_sig.png}
-    \caption{Singular values $\Sigma$ of the SVD decomposition}
-    \label{fig:randomized_svd_S}
-    \end{subfigure}
-    \begin{subfigure}{0.3\linewidth}
-    \includegraphics[width=\linewidth]{figure/face_recognition/randomized_svd_ret_V_sig_zoom.png}
-    \caption{Right matrix $V$ of the SVD decomposition}
-    \label{fig:randomized_svd_V}
-    \end{subfigure}
-    \caption{Precision of the \texttt{randomized\_svd} function in the 
-    \texttt{face\_recognition} example using the \texttt{gesvd} SVD method and RR.
-    Figures~\ref{fig:randomized_svd_U},~\ref{fig:randomized_svd_S}, and~\ref{fig:randomized_svd_V}
-    show respectively the values $U$, $\Sigma$ and $V$.
-     Numerical precision is lower for smaller singular values and this loss of precision translates to singular vectors.
-It would be interesting to investigate the use of numerical precision for dimensionality reduction.
-    }
-    \label{fig:face_recognition_svd}
-\end{figure}
-
-% RR: Crash due to FP32 use. Does FP64 converge? No. Does sgsvd converge? Yes
-
-% MCA: arange issue
-
-% File "/usr/local/lib/python3.8/site-packages/sklearn/datasets/\_lfw.py", line 169, in \_load\_imgs
-%     faces[i, ...] = face
-% ValueError: could not broadcast input array from shape (49,37) into shape (50,37)
-
-% \paragraph{L1 Penalty}
-% This test compares the percentage of zero coefficients for logistic regression
-% by varying the penalty (L1, L2 and Elastic-Net) and regularization (1, 0.1, 0.01) parameters. 
-% A large regularization value gives the model more freedom than a small value, which puts more constraints on the model.
-
-% of L1, L2 and Elastic-Net penalty.
-
-% Comparison of the sparsity (percentage of zero coefficients) of solutions when L1, L2 and Elastic-Net penalty are used for different values of C.
-We can see that large values of C give more freedom to the model.
-Conversely, smaller values of C constrain the model more.
-In the L1 penalty case, this leads to sparser solutions.
-As expected, the Elastic-Net penalty sparsity is between that of L1 and L2.
-% We classify 8x8 images of digits into two classes: 0-4 against 5-9. The visualization shows coefficients of the models for varying C.
-
-% RR: ok \\
-% MCA: stable for L1 and L2, not for Len but coef have less zeroes.
-
-% \paragraph{Lasso and Elastic-Net}
-% This test compares the Lasso and Elastic-Net regression models
-% on a corrupted signal.
-
-% Estimates Lasso and Elastic-Net regression models on a manually generated sparse signal corrupted with an additive noise. Estimated coefficients are compared with the ground-truth.
-
-% RR: Good (48 bits on coefs) \\
-% MCA: Good like RR if we exclude one trace that fails due to arange issue
-
-\paragraph{Separating hyperplane}
-
-This example uses a linear Support Vector Machine (SVM) classifier trained using the Stochastic Gradient Descent (SGD) method to find the maximum separating hyperplane between sets of 2D points.
-The example trains the SVM with 50 random points separated in 2 clusters with hyperparameter $\alpha=0.01$ and using the hinge loss function.
-Once the model is trained, the example generates a $[-1,5]\times[-1,5]$ Cartesian grid
-discretized with 100 points and predicts the class label for each point with integer coordinates.
-Figure~\ref{fig:hyperplan_sig_zoom} shows the number of significant bits %\tristan{isn't it significant bits?} \tristan{aren't the class predctions integers?}
-% \Yohan{No its floating point values}1
-obtained with RR for each point of the grid. %(squares \tristan{not sure where the squares are}) 
-We can see that yellow regions %\tristan{I don't see any white point} 
-close to the separating hyperplane are highly unstable with a number of significant bits below 0, meaning that
-the classifier is unsure about the predicted class. 
+This example uses a linear Support Vector Machine (SVM) classifier trained using
+the Stochastic Gradient Descent (SGD) method to find the maximum separating
+hyperplane between sets of 2D points. The example trains the SVM with 50 random
+points separated in 2 clusters with hyperparameter $\alpha=0.01$ and using the
+hinge loss function. Once the model is trained, the example generates a
+$[-1,5]\times[-1,5]$ Cartesian grid discretized with 100 points and predicts the
+class label for each point with integer coordinates.
+Figure~\ref{fig:hyperplan_sig_zoom} shows the number of significant bits
+obtained with RR for each point of the grid.
+We can see that yellow regions
+close to the separating hyperplane are highly unstable with a number of
+significant bits below 0, meaning that the classifier is unsure about the
+predicted class.
 %\tristan{Describe and comment on the other 2 tests, why are they more stable? Is it because the training set has more points?}
@@
 
-% \paragraph{MNIST classification}
-% This test fits a logistic regression with the SAGA solver with the L1 penalty on the MNIST digits classification task subset.
+\subsubsection{SVM}
+This example uses a plain Support Vector
+Classification~\cite{Platt99probabilisticoutputs} (SVC) to find the best
+hyperplane separating an unbalanced dataset with two classes of 1000 and 100
+points. This example tests two SVC configurations using a linear kernel with and
+without a class weight parameter. The SVC predicts the class label for each
+coordinate over a $[-5,5] \times [-5,5]$ grid discretized with 900 points.
+Figures~\ref{fig:SVM_nw_sig} and~\ref{fig:SVM_w_sig} show the result within RR
+of the classification with and without taking into account the unbalancing. We
+can see that the number of significant bits is lower on the separating line and
+that taking into account class imbalance allows for a better separation.
 
-% Here we fit a multinomial logistic regression with L1 penalty on a subset of the MNIST digits classification task.
-We use the SAGA algorithm for this purpose: this a solver that is fast when the number of samples is significantly larger than the number of features and is able to finely optimize non-smooth objective functions which is the case with the l1-penalty.
-Test accuracy reaches > 0.8, while weight vectors remains sparse and therefore more easily interpretable.
-% Note that this accuracy of this l1-penalized linear model is significantly below what can be reached by an l2-penalized linear model or a non-linear multi-layer perceptron model on this dataset.
-
-% RR: Very stable \\
-% MCA: Parse by excluding a trace that failed due to an arange issue
-
-% \paragraph{Multitask Lasso}
-% This test compares the Lasso and MultiTaskLasso regression models
-% on a corrupted signal.
-
-% The multi-task lasso allows to fit multiple regression problems jointly enforcing the selected features to be the same across tasks.
-This example simulates sequential measurements, each task is a time instant, and the relevant features vary in amplitude over time while being the same.
-The multi-task lasso imposes that features that are selected at one time point are select for all time point.
-This makes feature selection by the Lasso more stable.
-
-% RR: Stable (44~53 bits for coef) \\
-% MCA: Stable like RR if we exclude a trace that failed due index issue
-
-% \paragraph{Orthogonal matching}
-% This test uses the Orthogonal Matching Pursuit algorithm
-% for recovering a sparse signal from a noisy measurement encoded with a dictionary.
-
-% RR: Very stable \\
-% MCA: Very stable
-
-% \paragraph{PCA decomposition}
-% This test makes a PCA decomposition on a synthetic dataset.
-% These figures aid in illustrating how a point cloud can be very flat in one direction–which is where PCA comes in to choose a direction that is not flat.
-
-% rr: stable (48 bits on components) \\
-% mca: stable (48 bits on components)
-
-% \paragraph{Robust Linear Regression}
-% This test compares the linear and  RANSAC regression methods on noisy data.
-% In this example we see how to robustly fit a linear model to faulty data using the RANSAC algorithm.
-
-% RR: Very stable \\
-% MCA: Very stable if we exclude two traces that failed due to arange/index issues
-
-% \paragraph{Segmentation Toy}
-% This test uses spectral clustering to separate connected circles in an image.
-
-% In this example, an image with connected circles is generated and spectral clustering is used to separate the circles.
-
-% In these settings, the Spectral clustering approach solves the problem know as ‘normalized graph cuts’: the image is seen as a graph of connected voxels, and the spectral clustering algorithm amounts to choosing graph cuts defining regions while minimizing the ratio of the gradient along the cut, and the volume of the region.
-
-% As the algorithm tries to balance the volume (ie balance the region sizes), if we take circles with different sizes, the segmentation fails.
-
-% In addition, as there is no useful information in the intensity of the image, or its gradient, we choose to perform the spectral clustering on a graph that is only weakly informed by the gradient.
-This is close to performing a Voronoi partition of the graph.
-
-% In addition, we use the mask of the objects to restrict the graph to the outline of the objects.
-In this example, we are interested in separating the objects one from the other, and not from the background.
-
-% RR Stable \\
-% MCA: Stable if we exclude three traces that failed due to index issue
-
-\paragraph{SVM}
-This example uses a plain Support Vector Classification~\cite{Platt99probabilisticoutputs} (SVC) 
-to find the best hyperplane separating an unbalanced dataset with two classes of 1000 and 100 points.
-This example tests two SVC configurations using a linear kernel with and without a class weight parameter.
-The SVC predicts the class label for each coordinate over a $[-5,5] \times [-5,5]$ grid discretized
-with 900 points.
-Figures~\ref{fig:SVM_nw_sig} and~\ref{fig:SVM_w_sig} show the result within RR of the classification with
-and without taking into account the unbalancing.
-We can see that the number of significant bits is lower on the separating line and
-that taking into account class imbalance allows for a better separation.
-% Find the optimal separating hyperplane using an SVC for classes that are unbalanced.
-
-% We first find the separating plane with a plain SVC and then plot (dashed) the separating hyperplane with automatically correction for unbalanced classes.
-
-% RR: stable (48 bits) \\
-% MCA: stable (48 bits)
-
-% \paragraph{Tomography}
-% This test compares the LASSO and Ridge regression models to 
-% reconstruct an image from  projections for a dataset
-% acquired from computed tomography.
-
-% This test shows the reconstruction of an image from a set of parallel projections, acquired along different angles. Such a dataset is acquired in computed tomography (CT).
-
-% Without any prior information on the sample, the number of projections required to reconstruct the image is of the order of the linear size l of the image (in pixels).
-For simplicity we consider here a sparse image, where only pixels on the boundary of objects have a non-zero value.
-Such data could correspond for example to a cellular material.
-Note however that most images are sparse in a different basis, such as the Haar wavelets.
-Only l/7 projections are acquired, therefore it is necessary to use prior information available on the sample (its sparsity): this is an example of compressive sensing.
-
-% The tomography projection operation is a linear transformation.
-In addition to the data-fidelity term corresponding to a linear regression, we penalize the L1 norm of the image to account for its sparsity.
-The resulting optimization problem is called the Lasso.
-We use the class Lasso, that uses the coordinate descent algorithm.
-Importantly, this implementation is more computationally efficient on a sparse matrix, than the projection operator used here.
-
-% The reconstruction with L1 penalization gives a result with zero error (all pixels are successfully labeled with 0 or 1), even if noise was added to the projections.
-In comparison, an L2 penalization (Ridge) produces a large number of labeling errors for the pixels.
-Important artifacts are observed on the reconstructed image, contrary to the L1 penalization.
-Note in particular the circular artifact separating the pixels in the corners, that have contributed to fewer projections than the central disk.
-
-% RR Divergence \\
-% MCA Index issue
-
-\paragraph{SGD weighted samples}
-This example uses an SGD to separate weighted points.
-It divides the training set into two classes of 10 points with a bigger weight for the second class.
-The SGD is trained with hyperparameters $\alpha=0.01$ and a maximum number of iterations to 100.
-The prediction is made on a $[-4,5]\times[-4,5]$ grid discretized with 250 000 points.
-Figures~\ref{fig:weighted_nw_sig} and~\ref{fig:weighted_w_sig} show the number of significant bits
-of prediction within RR along with dataset points in blue and violet.
-We can see that the separating plane corresponds to a region of lower precision, similar to the previous examples. 
-% Finally, taking into account the points' weight allows for a better separation \tristan{is this related to numerical stability? If not, you can ommit the comment.}.
-
-% RR Stable (30~48 bits on coef) \\
-% MCA Unstable (0 bits on coef)
-
-% \subsection{PyAFQ}
-
-% PyAFQ is a Python package for Automated Fiber Quantification.
-% It aims to find delineation of the major fiber tracts in individual human brains and quantify the tissue properties within the tracts.
-PyAFQ \pytracer tracing produces traces of 1TB with an average slowdown $\times 6$ compared to the actual execution.
-Moreover, \pytracer was able to visualize the aggregated traces, demonstrating its scalability fluently.
-
-\subsection{Overhead evaluation}
-\pytracer's tracing overhead consists of (1) module instrumentation time (initialization overhead) and (2) data write time during the execution (runtime overhead).
-The initialization overhead is proportional to the number of functions and classes traced.
-For example, we measured an average initialization time of 8 seconds during our experiments with  NumPy, SciPy, and Scikit-learn.
-This overhead can be reduced by excluding intensively used functions such as \texttt{numpy.array} from the instrumentation.
-Figure~\ref{fig:performance_tracing} summarizes \pytracer's tracing overhead for SciPy and scikit-learn examples. 
-\textit{Slowdown} represents the slowdown of \pytracer without fuzzy measured as the ratio between the actual execution time (without \pytracer) and the execution time using \pytracer.
-The \textit{Slowdown RR} and \textit{Slowdown MCA} show the slowdown within the fuzzy environment. 
-Without fuzzy, \pytracer introduces an average slowdown of $17\times$ high for the examples running less than 8 seconds because \pytracer spends most of its time in the initialization step.
-Since this step is a constant factor of the number of functions instrumented, we also measured the instrumentation cost itself (\textit{Slowdown (Instrumentation)}) calculated by subtracting the initialization time to \textit{Slowdown}.
-We then obtain an average slowdown of $3.5\times$.
-Finally, the fuzzy instrumentation increases the average slowdown to $37\times$ for RR and $43\times$ for Full MCA.
-
-% \pytracer's tracing overhead consists of (1) module instrumentation time (initialization overhead), and (2) data write time during the execution (runtime overhead).
-The initialization overhead is proportional to the number of functions and classes traced.
-However, the initialization overhead is amortized \tristan{what do you mean by amortized?
-I don't get this sentence} when traced applications are above 8 seconds,  proportional to
-% the number of functions and classes traced.
-Figure~\ref{fig:performance_tracing} summaries \pytracer's tracing overhead for SciPy and scikit-learn examples.
-We can see that \pytracer introduces a slowdown of reduced toif we subtract the initialization step
-% \tristan{not sure where to get these numbers from the table, to be clarified. Are these average values? Why are there two values?}. 
-% Fuzzy instrumentation increases the slowdown to for RR and   for Full MCA.
-% \tristan{Figure 13 is not referred in the text. Choose between the figure and the table, no need to put both.}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figure/performance.pdf}
-    \caption{
-    \pytracer tracing overheads.
-\textit{Slowdown} represents the slowdown of \pytracer without fuzzy measured as the ratio between the actual execution time (without \pytracer) and the execution time using \pytracer.
-    \textit{Slowdown (Instrumentation)} show the actual instrumentation cost computed by subtracting the initialization step.
-    The \textit{Slowdown (RR)} and \textit{Slowdown (MCA)} are the slowdown of \pytracer 
-    using the fuzzy environment with RR and Full MCA modes.
-    The first four examples measure the initialization steps depending on the modules instrumented. 
-    % \tristan{there's too much text in this caption, move some of it to the text, the caption should just explain the difference between the 4 slowdowns.
-From the text I'm not sure what is the difference between slowdown and slowdown(RR)/slowdown(MCA).}
-    }
-    \label{fig:performance_tracing}
-\end{figure}
+\subsubsection{SGD weighted samples}
+This example uses an SGD to separate weighted points. It divides the training
+set into two classes of 10 points with a bigger weight for the second class. The
+SGD is trained with hyperparameters $\alpha=0.01$ and a maximum number of
+iterations to 100. The prediction is made on a $[-4,5]\times[-4,5]$ grid
+discretized with 250\add{,}000 points. Figures~\ref{fig:weighted_nw_sig}
+and~\ref{fig:weighted_w_sig} show the number of significant bits of prediction
+within RR along with dataset points in blue and \remove{violet} \add{purple}. We can see that the
+separating plane corresponds to a region of lower precision, similar to the
+previous examples.
 
@@
 %     \centering
-%     \includegraphics[width=\linewidth]{figure/parsing_time.pdf}
-%     \caption{\pytracer time to aggregate traces.}
-%     \label{fig:performance_parsing_time}
+%     \includegraphics[width=0.5\linewidth]{figure/BRR/call_path.pdf}
+%     \caption{Call paths of the Bayesian Ridge Regression (BRR) and Ordinary
+%         Least Square (OLS) function. Color represents the calling library:
+%         orange for scikit-learn, blue for SciPy and yellow for LAPACK. Dashed
+%         color represents the original path in red and the alternative one in
+%         green. Figure~\ref{fig:brr_svd_sig} shows the original method  leads to
+%         numerical instabilities while the alternative one converges. }
+%     \label{fig:call_path_brr}
 % \end{figure}
@@
 %     \centering
-%     \includegraphics[width=\linewidth]{figure/parsing.pdf}
-%     \caption{\pytracer trace and aggregation files size.
-%     The figure presents the size measured for the trace and the aggregation size files.}
-%     \label{fig:performance_parsing_size}
+%     \includegraphics[width=\linewidth]{figure/BRR/BRR_coefs_sig.pdf}
+%     \caption{Precision of Bayesian Ridge Regression coefficients in RR mode.
+%         \texttt{BRR\_*} show the \texttt{BayesianRidge} results using the
+%         \texttt{gesdd} and \texttt{gesvd} methods. \texttt{OLS\_*} show the
+%         \texttt{LinearRegression} results with the \texttt{dgelsd} and
+%         \texttt{dgelss} methods. The Divide \& Conquer method (\texttt{gesdd}
+%         and  \texttt{dgelsd}) has low precision for \textit{BRR} and results in
+%         \texttt{NaN} values (star points) for \textit{OLS}. By switching to the
+%         \texttt{gesvd} method, results have a precision of 42 bits on average. }
+%     \label{fig:brr_svd_sig}
 % \end{figure}
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figure/performance_parsing.pdf}
-    \caption{\pytracer aggregation performance. 
-    % \tristan{change xlabel to "Trace size (bytes) and ylabel to "Aggregation time (seconds)}
-    }
-    \label{fig:performance_parsing}
-\end{figure}
-
-% \begin{table}
-% \centering
-% \begin{subfigure}[t]{.75\linewidth}
-%     \centering
-%     \begin{tabular}{|l|c|c|c|c|}
-%     \hline 
-%     Application & Original & Pytracer only & RR & MCA \\
-%     \hline 
-%     Loading & 0.456 & 8.152 & - & - \\
-%     \hline
-%     discrete\_cosine\_transform & 0.280 & 8.176 & 10.203 & - \\ 
-%     fft\_1D & 0.650 & 9.075 & 11.345 & - \\
-%     fft\_2D & 0.311 & 9.500 & 11.929  & 16.433   \\
-%     \hline
-%     interpolation\_1D & 0.377 & 8.803  & 11.954  & -   \\
-%     multivariate\_data &0.626 & 8.648 &  12.711  & - \\
-%     bspline & 0.109  & 9.050 & 13.396  & 16.830   \\
-%     spline\_1D & 0.111 & 8.618 & 10.960   & - \\
-%     spline\_2D & 0.655 & 8.649 & 19.424  & - \\
-%     \hline
-%     broyden\_fletcher\_goldfarb\_shanno &0.475 & 8.292 & 11.033 & 13.685 \\
-%     global\_optimization &1.257 & 55.916  & 93.322  & - \\
-%     slsqp & 0.469 & 8.192 & 10.795 & 12.439  \\
-%     least\_square\_minimization & 0.505 & 10.151  & 13.888 & -  \\
-%     nelder\_mead\_simplex & 0.471 & 8.418  & 11.382  & 12.792  \\
-%     newton\_conjugate\_gradient & 0.487 & 8.548  & 11.956  & 14.281 \\
-%     root\_findings & 0.462 & 8.198  & 10.787   & - \\
-%     root\_finding\_large & 0.801 & 11.525 & 41.493   &  82.701  \\
-%     root\_finding\_large\_preconditioned & 0.702 & 10.580 & 33.199   & 57.579  \\
-%     trust\_region\_exact & 0.482 & 8.170 & 10.400  & 12.524 \\
-%     trust\_region\_truncated\_generalized\_lanczos & 0.459 & 8.457 & 11.216 & 13.245  \\
-%     trust\_region\_newton\_conjugate\_gradient & 0.479 & 8.538 & 11.179 & 13.488 \\
-%     \hline
-%     Adaboost &1.388 &14.553 &  20.999 & - \\
-%     Bayesian Ridge Regression & 1.086 & 10.344 & 90.299 & -  \\
-%     Online classifier comparison & 15.964 & 72.691 & 2104.114 & -  \\
-%     K-Means Clustering & 1.621 & 17.614  & 34.005 & 52.902   \\
-%     Covariance estimation & 1.357 & 11.755 & 23.964  & -   \\
-%     Decision Tree Regression & 1.185 & 11.194 & 15.760 & 15.918  \\
-%     Digits Classification & 1.672 & 12.725 & 40.634 & - \\
-%     Face Recognition & 32.159  & 74.356 & - & - \\
-%     L1 Penalty & 1.568 & 12.591 & 65.547 & 128.220 \\
-%     Lasso and elastic net & 1.057 & 9.903 & 17.078 & -  \\
-%     Separating hyperplan & 1.376 & 11.532  & 22.333 & 25.036 \\
-%     MNIST classification & 19.650 & 37.838 & 402.389  & - \\
-%     Multitask Lasso & 1.090 &10.196 & 15.025  & - \\
-%     Orthogonal matching & 1.161 & 12.129 & 21.779   & 31.135 \\
-%     PCA decomposition & 1.239 & 10.642 & 15.520 & 17.952    \\
-%     Robust Linear Regression & 1.370 & 11.144  & 14.280  & - \\
-%     Segmentation toy &1.679 & 22.385 & 87.811  & - \\
-%     SVM & 1.403 & 11.737 & 23.203 & 24.126   \\
-%     Tomography & 11.108 & 40.177  & 1376.134 & -  \\
-%     Weighted samples & 1.358 & 11.768 & 21.255 & 20.541   \\
-%     \hline
-%     \end{tabular}
-% \end{subfigure}
-%     \caption{\pytracer tracing overhead in seconds. \tristan{what is the unit in this table?}}
-%     \label{tab:pytracer_overhead}
-% \end{table}
-
-% \begin{table}[]
-%     \centering
-%     \begin{tabular}{c|c|c|c|c}
-%          Pytracer & Verificarlo Instrumentation & Backend & Time (hours:minutes:seconds) & Overhead \\
-%          \hline 
-%          No & No & - & 00:30:51 & 1 \\
-%          No & Yes & IEEE & 01:32:56 & 3 \\
-%          No & Yes & RR & 16:52:08 & 32 \\
-%          Yes & No & - & 03:11:07 & 6  \\
-%          Yes & Yes & IEEE & 11:14:33 & 22 \\
-%          Yes & Yes & RR & 25:05:54 & 48 \\
-%     \end{tabular}
-%     \caption{Overheads of \pytracer on PyAFQ experiment with and without fuzzy.}
-%     \label{tab:pytracer_overhead}
-% \end{table}
-
-% \begin{table}[]
-%     \centering
-%     \begin{tabular}{c|c|c|c|c}
-%          Pytracer & Verificarlo Instrumentation & Backend & Time (hours:minutes:seconds) & Overhead \\
-%          \hline 
-%          No & No & - & 15 & 1 \\
-%          No & Yes & IEEE & 49 & 3 \\
-%          No & Yes & RR &  & 441 & 29 \\
-%          Yes & No & - & 03:11:07 & 6  \\
-%          Yes & Yes & IEEE & 11:14:33 & 22 \\
-%          Yes & Yes & RR & 25:05:54 & 48 \\
-%     \end{tabular}
-%     \caption{Caption}
-%     \label{tab:pytracer_overhead}
-% \end{table}
-
-Figure~\ref{fig:performance_parsing} shows
-the postprocessing time and trace sizes produced by \pytracer. 
-The linear correlation between the log of the size and the log of the time shows a significant correlation 
-(p-value $\leq 10^{-8}$ for RR and p-value $\leq 10^{-3}$ for MCA).
-% \tristan{Mention linear correlation with p-value here.}
-
-In conclusion, while \pytracer's overhead is substantial, it remains tractable for real-life examples.
-
-\section{Discussion}
-
-% Numpy   2509 (2403 not tests) (1848) functions, 1196 (1154) (817) classes (pure Python)
-% Scipy   4031 (2187) (506) functions, 1532 (472) (109) classes (pure Python)
-% Sklearn 4807 (1010) (81) functions, 546 (417) (41) classes (pure Python)
-
-% \pytracer is a tool for visualizing the numerical quality of function inputs and outputs along the execution of a Python program.
-It generates numerical traces and post-processes them to measure numerical discrepancies between executions.
-\pytracer does not require any particular noise model to estimate uncertainties.
-We tested it with MCA through the fuzzy ecosystem on two broadly used Python libraries.
-
-Through our analysis of SciPy and scikit-learn, we demonstrated \pytracer's scalability, automaticity, and applicability to a wide range of Python program.
-The relatively low instrumentation overhead of 3.5$\times$ on average enables the analysis of real-scale applications.
-\pytracer's instrumentation is fully automatic and does not require manual intervention from the user.
-Furthermore, \pytracer works on any Python libraries, with any data format supported by pickle and any numerical noise model.
-
-\pytracer is the first tool to enable a systematic numerical analysis of Python codes.
-Existing tools focus on traditional languages of the HPC community, such as C, C++, and FORTRAN.
-However, Python's high-level abstraction allows for quick application implementations while maintaining high-performance thanks to specialized libraries such as NumPy.
-Therefore, \pytracer meets the numerical analysis needs of an ever-increasing number of applications.
-
-\pytracer allows users to pinpoint the root causes of numerical instabilities by working at the function level.
-Numerical stability evaluations are complex since calculations are strongly interdependent.
-Function-level instrumentation limits the size of the traces since only inputs and outputs of a function are dumped.
-Moreover, it decreases instrumentation overhead and helps the user identify instabilities quickly.
-Working at the function level is thus a suitable compromise between analysis conducted at the floating-point operation level and user debug prints.
-Indeed,  fine-grained analyses are costly and hard to interpret as they overwhelm users with information.
-In contrast, looking at intermediate results through print statements
-is lightweight but not reliable since developers may not systematically instrument unstable functions.
-Finally, the SciPy environment wraps many computation kernels written in C, such as BLAS or LAPACK.
-By working at the function level, \pytracer allows the user to evaluate the numerical precision of such kernels and their impact on the code without getting deep into technical implementation aspects.
-
-Integrating \pytracer at the early stages of the development cycle would improve the overall numerical quality of the developed code.
-\pytracer's automaticity facilitates its usage and enables its integration in unit testing.
-For example, \pytracer could be used in regression tests to ensure that updates do not degrade the numerical quality of a calculation.
-
-\pytracer can also be useful for selecting hyperparameters, as is the case in machine learning.
-Indeed, it is common for data scientists to explore a range of hyperparameters and select the ones giving the best scores.
-With \pytracer, the user has a practical way to quantify numerical quality and understand why hyperparameters produce inconsistent results instead of tweaking hyperparameters to make solvers converge.
-For instance, the Face Recognition example  (Figure~\ref{fig:face_recognition_svd}) shows how numerical precision could inform the selection of the number of components in dimensionality reduction.
-
-The visualization provides a global view of the code and interactions between computations.
-In addition, the Plotly dashboard helps navigate through the code easily, without the need for ad-hoc scripts to visualize data.
-Finally, the dashboard can be extended to support other data formats to visualize.
-At this stage, \pytracer currently supports n-dimensional NumPy arrays as well as native Python data.
-
-As we showed in Section~\ref{sec:impact_mca_modes}, using Full MCA mode leads to runtime errors that have a considerable impact on the proper functioning of the execution, which is unfortunate since these errors do not reflect actual numerical errors but are related to perturbations that should not occur.
-Conversely, RR mode is far more conservative since it preserves exact operations and is easier to use even though it does not simulate all perturbations.
-Therefore, from our experiments, we recommend the use of RR over Full MCA.
-More research is required to address the issues encountered with Full MCA.
-
-Finally, the wide range of results precision obtained from our experiments demonstrate that looking at the numerical variability is essential and that such analyses would benefit from being conducted systematically.
-We showed that well-known scientific libraries are prone to numerical error even though they have been well tested for decades.
-The omnipresence of these libraries in scientific codes should thus impel users to integrate numerical analysis in their development workflow in addition to testing their implementation.
-
-% Through our analysis of SciPy and Scikit-learn, we demonstrated \pytracer's scalability, automaticity, and applicability to any Python program.
-The relatively low instrumentation overhead of $3.5\times$ on average enables the analysis of real applications.
-\pytracer's instrumentation is fully automatic and does not require manual intervention from the user.
-\pytracer works on any Python libraries, with any data format supported by Pickle and any numerical noise model.
-
-% \pytracer is the first tool to enable a systematic numerical analysis of Python codes.
-Existing tools focus on traditional languages of the HPC community such as C, C++, and FORTRAN.
-However, Python's high-level abstraction allows for quickly developing applications while maintaining high performance thanks to specialized libraries such as NumPy.
-Therefore, \pytracer meets the numerical analysis needs of an ever-increasing number of applications.
-
-% Furthermore, \pytracer allows users to pinpoint numerical instabilities root causes precisely by working at the function level.
-Indeed, evaluating the numerical stability is complex since calculations
-% are strongly correlated between them. 
-% The instrumentation at the function level limits the size of the traces since only inputs and outputs of a function are dumped.
-It moreover decreases the overhead of the instrumentation and helps the user to identify instabilities quickly.
-% Working at function level is thus a suitable compromise between (1) analyzing at the floating-point operation level and (2) user debug prints.
-% (1) Indeed, the fine-grained analysis is costly and hard to analyze due to the large amount of computations evolved in HPC codes.
-It overwhelms the user with too much information, making analysis more difficult but can be interesting at the final step of the understanding.
-% (2) Looking at intermediate results through print statements focuses on valuable information
-% (like residuals or norms) but may miss numerically unstable functions unsuspected by the developer.
-% Finally, the SciPy environment wraps a lot of computation kernels written in C, like BLAS or LAPACK.
-% By working at function level, \pytracer allows the user to evaluate the numerical precision of such kernels
-% and their impact on the code without getting deep into technical implementation aspects.
-
-% Python is a popular language to prototype proof-of-concept. Integrating \pytracer at early stages of the development cycle allows identifying numerical instabilities to write code of better quality.
-% \pytracer's automaticity facilitates the usage and enables its integration in unit testing.
-% It can be for example used in a non-regression test to ensure that the numerical quality of a calculation
-% is not degraded by updates. Moreover, the Plotly dashboard offers a quick visualization to 
-% analyze more finely the potential issues.
-
-% \pytracer can also be useful to select the hyperparameters of a code, as it is the case in machine learning.
-% Indeed, we find many cases in the literature where users explore a range of hyperparameters
-% to select the ones giving the best scores. With \pytracer, 
-% the user has a practical way to quantify the numerical quality and to understand why hyperparameters
-% lead to unstable outputs, instead of tweaking hyperparameters to make solvers converge,
-
-% The visualization permits a global view of the code and to understand interactions between 
-% computations. The Plotly dashboard help to easily navigate through the code.
-% It moreover removes the need for ad-hoc scripts to visualize data. 
-% Finally, the dashboard can be extended to support other data format to visualize.
-% \pytracer currently supports n-dimensional NumPy arrays as well as native Python data.
-
-% As we showed in Section~\ref{sec:impact_mca_modes}, using Full MCA mode leads to runtime errors that have a considerable impact on the proper functioning of the execution.
-This is unfortunate since these errors do not reflect actual numerical errors but errors related to perturbations that should not occur.
-% Conversely, RR mode is far more conservative since it preserves exact operations and is easier to use even though it does not simulate all perturbations.
-% From our experiments, we do not recommend the Full MCA mode for now and more researches are needed 
-% to help fixing issues we encountered.
-
-% Fixing this issue would enable the study of catastrophic cancellations, which are common sources of numerical errors. 
-% In addition to the runtime errors it raises, mismatching shapes is also a problem when aggregating traces as \pytracer will not compute statistics for a set of arrays with different shapes \tristan{So do you conclude that Full MCA is not usable while RR is?
-If so, you should recommend to use Pytracer with RR only.} \tristan{are you still talking about Full MCA here?
-if not, make another paragraph.
-If so, make it clearer.}.
-Two solutions exist to overcome this issue: the first is not to instrument the \texttt{PyArray\_Arange} function with MCA.
-The advantage is that it is easy to set up since it requires one extra line in the exclusion file.
-However, the same kind of problem may appear somewhere else because, as we have seen, the evolved operations are elementary.
-Therefore, the chances that developers reproduce the same pattern are very probable.
-Therefore, the second solution is to ensure that the Full MCA mode preserves the exact operations.
-This solution has the advantage of not worrying about which functions should be instrumented or not with MCA, but it is hard to achieve it in practice.
-Indeed, we rely on the MCA implementation provided by Verificarlo that uses an internal precision to add the random perturbation that is higher than the working precision for applying the random noise.
-Verificarlo then rounds the result to the working precision before returning it, so any residual noise lower than the working precision is lost.
-Keeping track of that noise would require recording each intermediate computation in a shadow memory or keeping a tag about their exactness.
-This option would require more extra works than the first one but would ensure more consistent results.
-\tristan{I find this paragraph too verbose, you should contract it to a few key sentences.}
-
-% \tristan{The following paragraphs are future work, not discussion. I'd remove them and flesh out the discussion from the ideas mentioned in the current 3rd paragraph}
-
-% Also, we would like to extend the post-process analysis to aggregate traces where the execution flow path diverges.
-Therefore, a posteriori reconstruction is challenging as one must precisely identify the flow path taken and find synchronization points to pursue the analysis.
-We retrieve, for example, this divergence behavior in two general classes of numerical schemes: iterative methods and optimization processes.
-One solution is to integrate methods used in code coverage analysis to keep track of flow paths taken and the backtraces.
-However, this would increase the complexity of the postprocess analysis as well as an extra slowdown factor.
-However, by coupling the Gantt chart with static analysis, \pytracer would catch some divergence patterns occurring within a function.
-Indeed, by instrumenting at the function level, \pytracer views the function's callees (i.e., the functions called within a function) and thus should partially detect flow divergences.
-
-% By design principle, \pytracer is flexible on the noise model used, although we only tested it with the MCA model in our experiments.
-Nevertheless, we would like to compare different models against MCA in future works to see the resulting differences.
-Furthermore, we would like to test \pytracer on parallel codes.
-
-% Finally, we would extend \pytracer to instrument elementary arithmetic operations which can be helpful to more profound analyses.
-We nevertheless believe that instrumentation at the function level presents two advantages: it first limits the size of the traces since only inputs and outputs of a function are saved instead of a full report which, on the one hand, decreases the overhead of the instrumentation and, on the other hand, help the user to identify instabilities quickly.
-Indeed, full reporting can overwhelm the user with too much information, making analysis more difficult at first.
-Second, the analysis at fine granularity is interesting at the final step of the understanding.
-Such an analysis would require a different instrumentation approach by, for example, working at the Abstract Syntax Tree (AST) level since it is trivial to get it in Python.
-% Moreover, working at the AST level allows doing dependency analysis.
-Another extension would be to extract and replay a function, in the same vein as the CERE tool does but for Python, and to use an AST instrumentation to analyze the numerical quality of elementary operations step by step within the fuzzy environment.
-
-% \pytracer is a tool for visualizing the numerical quality of function inputs/outputs over time.
-% It generates numerical traces that are aggregated in postprocessing to measure numerical discrepancies between executions.
-% \pytracer does not assume the noise model used to estimate uncertainties but has been tested with the MCA 
-% through the fuzzy ecosystem on two broadly used scientific libraries for Python with partial success.
-
-% We demonstrated the Pytracer's capabilities to analyze intensively used Python libraries such as NumPy or Scikit-learn, such as 
-% 1) Scalability. The low instrumentation overhead of 3.5x enables analysis of real applications and permits having a global representation of the numerical quality of an application. 
-% 2) Automaticity. Pytracer instrumentation is fully automatic and does not require manual intervention from the user, allowing the instrumentation of 
-% the NumPy, SciPy and Scikit-learn libraries.
-% // that cumulate 5600 and 2043 pure Python functions and classes. 
-% 3) Agnosticity. Pytracer works on any python libraries, with any data format supported by pickle, and any numerical noise model flavor.
-
-% Pytracer is the first tool to bring numerical analysis of Python codes available to everyone.
-Indeed, existing tools developed in the last years focused on traditional HPC languages community such as C,C++, and FORTRAN.
-However, the Python high-level abstraction allows you to quickly develop applications while maintaining high performance with the help of specialized libraries like NumPy.
-Therefore, it is quite natural to see more fields systematically using Python, as is the case in neuroimaging.
-Thus, Pytracer meets the numerical analysis needs of an ever increasing number of applications writing in Python.
-
-% By working at function level, Pytracer allows users to precisely pinpoint numerical instabilities root causes.
-Furthermore, the automaticity facilitates the usage and its integration in unit testing.
-Hence, instead of tweaking hyperparameters to make solvers converging, the user has a practical way with Pytracer to quantify the numerical quality of its computations.
-
-% As we showed in section~\ref{sec:impact_mca_modes}, using the Full MCA mode leads to runtime errors that have a considerable impact on the proper functioning of the execution, which is unfortunate since these
-% errors do not reflect actual numerical errors but errors related to perturbations that should not occur.
-% Fixing this misbehavior would greatly help use Full MCA mode since this mode allows simulating catastrophic cancellations, which are familiar sources of numerical errors.
-By preserving exact operations, RR mode is far more conservative and so easy to use even though it does not simulate all perturbations that might be encountered.
-
-% Also, using a post-process analysis to aggregate traces, \pytracer falls in the same pitfalls as veritracer and is limited to aggregate traces where the execution flow path extremely diverges.
-Therefore, a posteriori reconstruction
-% is challenging as one must precisely identify the flow path taken and find synchronization points to pursue the analysis.
-We retrieve, for example, this divergence behavior in two general classes of numerical schemes: iterative methods and optimization processes.
-One solution to overcome this issue is to integrate methods used in code coverage analysis to keep track of flow paths taken and the backtraces.
-% However, this would increase the complexity of the postprocess analysis as well as an extra slowdown factor.
-% However, by coupling the Gantt chart with static analysis, \pytracer would catch some divergence patterns occurring within a function.
-Indeed, by instrumenting at the function level, \pytracer views the function's callees (i.e., the functions called within a function) and thus should partially detect flow divergences.
-
-% By design principle, \pytracer is flexible on the noise model used, although we only tested it with the MCA model in our experiments.
-% Nevertheless, we would like to compare different models against MCA in future works to see the resulting differences. 
-% In particular, although \pytracer only works on a sequential application for the moment, it can be used to analyze parallel sections internal to a function.
-% The only restriction is that the section does not call other functions traced by \pytracer; we would fall into the previous issue of divergence if it would not be the case.
-% Since \pytracer only cares about inputs and outputs of a function, the order of internal operations is transparent for it and thus should be able to handle those cases.
-
-% Finally, \pytracer does not instrument elementary arithmetic operations, and it can be a barrier to more profound analysis.
-%Such an analysis would require a different instrumentation approach by, for example, working at the Abstract Syntax Tree (AST) level since it is trivial to get it in Python.
-% An ideal way to do that would be to extract and replay a function, in the same vein as the CERE~\cite{castro2015cere} tool does but for Python, and use an AST instrumentation to analyze the numerical quality of elementary operations step by step within the fuzzy environment.
-% Lastly, AST analysis can serve as a basis for finding relationships between variables, valuable information for the user.
-
-% In addition to the runtime errors it raises, mismatching shapes is also a problem when aggregating traces as PyTracer will not compute statistics for a set of arrays with different shapes.
-% Two solutions exist to overcome this issue: the first is not to instrument the \texttt{PyArray\_Arange} function with MCA.
-The advantage is that it is easy to set up since it requires one extra line in the exclusion file.
-% However, the same kind of problem may appear somewhere else
-% because, as we have seen, the operations being evolved are elementary.
-Therefore, the chances that developers reproduce the same pattern are very probable.
-The second solution is to ensure that the Full MCA mode preserves the exact operations.
-% This solution has the advantage of not worrying about which functions should be instrumented or not with MCA, but it is hard to achieve it in practice.
-Indeed, we rely on the MCA implementation provided by Verificarlo that uses an internal precision to add the random perturbation that is higher than the working precision for applying the random noise.
-Verificarlo then rounds the result to the working precision before returning it, so any residual noise lower than the working precision is lost.
-% Keeping track of that noise would require recording each intermediate computation in a shadow memory or keeping a tag about their exactness.
-% \Yohan{This idea emerged by discussing with Verificarlo's team. 
-% I must find a way to express that and not give the impression that we discovered or suggest it.}
-% This option would require more extra works than the first one but would ensure more consistent results.
-
-\section{Conclusion}
-
-% \tristan{I moved this from the opening of Section 4, as this reads more like a summary of \pytracer's features than an experiment description.
-It should be refactored in 1-2 paragraphs summarizing the main properties of \\pytracer.}
-
-Evaluating the numerical stability of scientific Python programs is a tedious task that requires substantial expertise.
-Automatic tools to help users understand the behavior of their code are therefore crucial.
-In this perspective, \pytracer is the first tool to offer a complete framework for analyzing and visualizing the numerical stability of Python codes.
-It works by automatically instrumenting Python libraries to produce numerical traces visualized through an interactive Plotly Dash server.
-\pytracer does not require manual code modification, and we tested it with major scientific libraries such as NumPy, SciPy, and Scikit-learn.
-Our results show that \pytracer is scalable, with an average instrumentation slowdown of $3.5\times$.
-Moreover, \pytracer's visualization interface remains responsive even with traces of up to 1TB.
-In our experiments, \pytracer enabled the systematic evaluation of 40 examples from the SciPy and scikit-learn libraries.
-
-In future work, we plan to extend the post-processing analysis to aggregate traces when the execution flow path diverges by leveraging techniques used in code coverage analysis.
-Moreover, we would like to extend \pytracer to instrument elementary arithmetic operations which can be helpful to more profound analyses.
-Finally, although \pytracer supports multiple noise models, we only tested it with Monte Carlo Arithmetic.
-Therefore, we would like to compare different models against MCA.
-\pytracer is available at \href{https://github.com/big-data-lab-team/pytracer}{github://big-data-lab-team/pytracer} under MIT License.
-
-% Evaluating the numerical stability of scientific Python codes is a tedious task
-% and requires an expertise to be conducted. Automatic tools to help the users 
-% understanding what's going on in their codes is therefore crucial.
-% In this perspective, \pytracer is the first tool to offer a complete framework
-% for analyzing and visualizing the numerical stability of Python codes.
-% It works by automatically instrumenting Python libraries to produce numerical
-% traces visualized through an interactive Plotly Dash server.
-% \pytracer does not require manual code modification, and has been tested with 
-% major scientific libraries such as NumPy, SciPy, and Scikit-learn.
-Our results show that \pytracer is scalable, with an average instrumentation slowdown of $3.5\times$.
-\pytracer's visualization interface remains responsive even with traces of up to 1TB.
-Moreover,
-% \pytracer is by construction agnostic to the noise model used 
-% to evaluate the numerical stability. We have demonstrated 
-% that \pytracer can be used with the Monte Carlo Arithmetic 
-% through the fuzzy environment. 
-% The experiments conducted in this paper are the first largest application of the fuzzy ecosystem by the wide range of applications covered.
-
-% In future work, we would like to extend the post-process analysis to aggregate traces 
-% when the execution flow path diverges by leveraging techniques used in code coverage analysis.
-% Moreover, we would like to extend \pytracer to instrument elementary arithmetic operations 
-% which can be helpful to more profound analyses. Finally, although \pytracer is flexible on the noise
-% model used, we only tested it with the Monte Carlo Arithmetic. We would like to compare different 
-% models against MCA.
-
-% We also have to provide feedback about pitfalls and benefits encountered to shed light on first-time users' good and bad practices and democratize MCA's usage.
-
-% \begin{itemize}
-
-%     \item Domain agnostic: \pytracer is intended to work on any scientific Python applications, without specific domain-specific languages or needs to rely on specific libraries.
-%     We target two of the most common libraries used in scientific computing within Python, SciPy and Scikit-learn, and a domain-specific application in neuroimaging.
-We show that \pytracer works well on these libraries, capturing most of the functions' module targeted.
-
-%     \item Automatic: \pytracer objective is to offer automatic instrumentation for Python applications,
-%     from small prototypes to state-of-the-art scientific libraries.
-
-%     \item Scalable: \pytracer goal is to trace real-world application and use case.
-%     In that perspective, we use \pytracer on PyAFQ, a domain-specific neuroimaging application to compute tractograms, generating \pytracer traces up to 1TB.
-We demonstrate that \pytracer can handle this volume of data and offer the user an interactive and fluent visualization.
-%     We also show that \pytracer instrumentation gives a slowdown of $\times 6$.
-
-%     \item Fuzzy compatible: \pytracer aims at evaluating numerical stability by using an injection noise model.
-%     Although the noise model used is orthogonal to \pytracer tracing mechanism, we emphasize in these experiments the MCA model through the fuzzy environment and discuss its compatibility with \pytracer tracing mechanism to point out limitations of the trace-based approach and to propose research tracks to overcome them.
-%     The experiments conducted in this paper are the first largest application of the fuzzy ecosystem by the wide range of applications covered.
-We, therefore, found it interesting to give feedback about pitfalls and benefits encountered
-%     in order to shed light on the good and bad practices for first-time users and democratize MCA's usage.
-%     Moreover, these analyses will help the fuzzy developers to increase the overall stability of fuzzy.
-
-% \end{itemize}
-
-\bibliographystyle{abbrv}
-\bibliography{biblio}
-
-%%
-%% If your work has an appendix, this is the place to put it.
-\appendix
-
-\end{document}
-\endinput
-%%
-%% End of file `sample-authordraft.tex'.
+% This example compares a Bayesian Ridge Regression (BRR) to the Ordinary Least
+% Squares (OLS) estimator on a synthetic dataset and for one-dimensional
+% regression using polynomial feature expansion. Although the example does not
+% raise a runtime error, the regression coefficients computed from the fitting are
+% non-significant. \pytracer traces reveal that the SVD solver used is the root
+% cause for this error. Figure~\ref{fig:call_path_brr} shows the two call paths
+% for BRR and OLS. The LAPACK library has two main methods for computing the SVD:
+% \texttt{gesdd} and \texttt{gesvd}. The former uses a Divide \& Conquer approach,
+% while the latter uses a QR decomposition. While both methods are expected to
+% have the same accuracy~\cite{nakatsukasa2013stable},
+% Figure~\ref{fig:brr_svd_sig} shows that \texttt{gesdd} is totally imprecise,
+% with an average number of significant digits of 0\footnote{Following
+%     Equation~\ref*{eq:sig-digits}, a number of significant digits below 0 means that
+%     the variability ($\sigma$) is higher than the avarage value ($\mu$).} for BRR
+% and even \texttt{Not-a-Number} (\texttt{NaN}) values for OLS. On the same
+% figure, we can see that using the \texttt{gesvd} (\remove{dgelsd} \add{dgelss})
+% method instead of the \texttt{gesdd} (\remove{dgelss} \add{dgelsd}) one, the SVD
+% converges for RR and Full MCA, with a number of significant bits of 44 on
+% average. This observation supports the on-going discussion among LAPACK
+% developers on the instability of \texttt{gesdd} (see
+% \href{https://github.com/Reference-LAPACK/lapack/issues/316}{github.com/Reference-LAPACK/lapack/issues/316}).

### 2022-05-12 IEEEtran/paper-annotated.tex
Some edits

@@
 \newcommand{\pytracer}[0]{PyTracer\xspace}
+\newcommand{\TG}[1]{\color{red}\textsc{From Tristan}: #1\xspace\color{black}}
 
@@
         modeling. Through these evaluations, we demonstrate \pytracer as a
-        scalable, automatic, and generic framework for numerical profiling in
+        scalable, automated, and generic framework for numerical profiling in
         Python.
@@
 executions, and (\add{c}\remove{3}) visualizing stability evaluations.
-\add{PyTracer uses the ``fuzzy" Python environment instrumented with Monte-Carlo
-    arithmetic to address the requirement (a). \mbox{\pytracer} addresses the
-    remaining requirements with (b) a dynamic instrumentation of Python functions,
-    modules, and classes through meta-programming, (c) an interactive Plotly
-    dashboard to visualize stability measures throughout program executions.
+\add{PyTracer addresses (a) by relying on the ``fuzzy" Python environment instrumented with Monte-Carlo
+    arithmetic, (b) by dynamically instrumenting Python functions,
+    modules, and classes through meta-programming, and (c) by visualizing stability measures throughout program executions
+    with an interactive Plotly
+    dashboard.
     \mbox{\pytracer} is available at
@@
 
-\section{Philosophy of \pytracer}
-
+\section{\pytracer design}
+
+\TG{I'm still unsure what to do with this part, it looks out of place.}
 \add{PyTracer follows a three steps approach:}
 \begin{enumerate}
-    \item \add{Automatic instrumentation of Python programs to save the value of inputs and outputs of function in a file.}
-    \item \add{Aggregation of the traces generated to produce a statistics summary.}
-    \item \add{Interactive visualization to navigate through the code execution.}
+    \item \add{Automatic instrumentation of Python programs to save traces containing input and output values of all functions.}
+    \item \add{Traces aggregation to produce a statistics summary.}
+    \item \add{Interactive visualization to navigate through code execution.}
 \end{enumerate}
@@
 \add{
-    The main goal of PyTracer is to help the developper visualizing the numerical
+    The main goal of PyTracer is to help developpers visualize the numerical
     stability of Python applications. PyTracer saves time for the user by
@@
 \add{
-    The main challenge addresses by PyTracer is the transparent instrumentation of Python 
-    applications. Indeed, since Python is interpreted language, one has no complete 
+    The main challenge addressed by PyTracer is the transparent instrumentation of Python 
+    applications. Indeed, since Python is an interpreted language, one has no complete 
     view of the function that will be executed by a given program. 
-    Moreover, since we target Python application used in HPC environments, one has
+    Moreover, for Python applications used in HPC environments, one has
     most of the time no access to source codes or with limited write access.
@@
 \add{
-    The based-trace approach used by PyTracer permits to limit the 
+    The trace-based approach used by PyTracer permits to limit the 
     overhead at runtime since the statistics computation is reported to the postprocess analysis.
@@
 }
-
-\section{\pytracer design}
 
@@
 contrast with \remove{decorator-based approaches} \add{a decorator-based
-    approache~\mbox{\cite{hunt2019decorators}}}. In addition, this technique is
+    approach~\mbox{\cite{hunt2019decorators}}}. In addition, this technique is
 scalable and applicable in read-only environments such as Singularity containers
@@
 precision and $\xi \in (-\frac{1}{2},\frac{1}{2})$ is a random uniform variable.
-Virtual precision allows for the simulation of reduced working precision. MCA
-can be applied in three modes \add{but we only used the} Random Rounding (RR) \add{in our
-    experiments} \remove{, Precision Bounding (PB), and full MCA,} which apply
-function $inexact$ to the output. \remove{, the inputs, or both, respectively.
-    While the RR mode is equivalent to stochastic rounding, the PB mode can also
-    identify catastrophic cancellations.} \add{Random Rounding simulates roundoff errors.}
+Virtual precision allows for the simulation of reduced working precision.
+\add{In our experiments, we used MCA in Random Rounding (RR) mode, which
+simulates roundoff errors by applying function $inexact$ only to the
+outputs returned by functions. The Precision Bounding (PB) mode can
+identify other types of instabilities, in particular catastrophic
+cancellations, however, it is more difficult to apply to large code bases
+as it often leads to execution errors that require human intervention.}
 
@@
 
-We enable MCA in Python programs via Verificarlo~\cite{verificarlo}, a
+We enabled MCA in Python programs via Verificarlo~\cite{verificarlo}, a
 clang-based compiler~\cite{lattner2008llvm} that replaces floating-point
@@
 
+\add{Monte Carlo Arithmetic samples the floating-point variability of a given
+    program, and hence the more MCA repetitions we have, the more accurate the
+    distribution will be. In theory, an infinite number of MCA repetitions
+    should give the exact distribution. While in practice low sample sizes (3 to 30)
+    can give good estimates, the issue is to capture ``rare events" that could make the
+    computation strongly diverge from the mean. Determining the number of
+    MCA samples to use for a given instrumented code is still an open research question. 
+    Recent theoretical works}~\cite{sohier2021confidence}
+\add{on the estimation of significant digits allow computing an associated
+    confidence interval depending on the sample size and the underlying distribution.}
+
 \subsubsection{Trace format}
@@
 single-threaded and that the control flow does not depend on a random state.
-\add{Therefore, \mbox{\pytracer} cannot merge traces resulting from a different
-    control flow path and will stop the parsing when encountering one.}
+\add{Therefore, \mbox{\pytracer} cannot merge traces resulting from different
+    control flow paths and will stop the parsing when encountering such a situation.}
 
@@
 activated MCA in the Python interpreter \add{as well as} BLAS, LAPACK, NumPy,
-SciPy, and scikit-learn. \add{Only instrumented the Python interpreter would
-    lead to only perturbe pure Python floating-point operations and thus to miss
-    operations in compiled codes (i.e. Cython and shared libraries).} \add{We
-    repeated the experiment with two MCA modes, Random Rounding (RR) and Full MCA,
-    resulting in 2 experiments for each example}. We used the default virtual
+SciPy, and scikit-learn. \add{Instrumenting only the Python interpreter would
+    lead to only perturb pure Python floating-point operations and thus miss
+    operations in compiled codes (i.e., Cython and shared libraries).} \add{We
+    used MCA in Random Rounding (RR) mode, with 5 repetitions}. We used the default virtual
 precision in Verificarlo, namely 24 bits for single-precision floating-point
@@
 We used Python-3.8.5, NumPy-1.19.1, SciPy-1.5.4, and scikit-learn-0.23.2.
-
-\add{Monte Carlo Arithmetic samples the floating-point variability of a given
-    program, and hence the more MCA repetitions we have, the more accurate will be
-    the sampling distribution. In theory, an infinite number of MCA repetitions
-    should give the exact distribution. While in practice low sample size (3$\simeq$30)
-    can give a good estimate, the issue is to capture "rare events" that could make the
-    computation strongly diverge from the mean. For now, determining the number of
-    MCA samples to use is still an open research question. 
-    Recent theoretical works}~\cite{sohier2021confidence}
-\add{on the significant digits computation allow computing an associated
-    confidence interval depending on the sample size and the underlying distribution of the outputs.}
 
@@
 
-\subsection{Pytracer is applicable to scientific computation libraries of reference}
+\subsection{\pytracer is applicable to reference scientific computating libraries}
 
@@
 Overall, the tracing and parsing of SciPy and scikit-learn examples in Random
-Rounding mode was entirely successful for 32/40 examples and showed an average
-precision loss of 8 bits. The remaining examples failed due to numerical errors
+Rounding mode was entirely successful for 32/40 examples\remove{ and showed an average
+precision loss of 8 bits}. The remaining examples failed due to numerical errors
 in the libraries, which we discuss hereafter. 
@@
 by taking the element-wise mean for non-scalar values and, if the example
-produces many outputs, the average value among all of them. The numerical
-quality across all examples varies from 0 to 52, with an average of 44
+produces many outputs, the average value among them. The numerical
+quality across all examples varied from 0 to 52, with an average of 44
 significant bits. We note that only one example failed due to a
@@
 
-\subsection{\pytracer supports the visualization of compound data type}
-
-\add{PyTracer supports native floating point formats as well as compound data type,
+\subsection{\pytracer supports the profiling of compound data types}
+
+\add{PyTracer supports native floating point formats as well as compound data types,
     such as complex floating point values, N-dimensional arrays and arbitrary Python
-    classes. For the Python classes, PyTracer recursively parses the class attributes to
-    extract scalar and N-dimensional arrays floating-points values.}
-
+    classes.}
 Figures~\ref{fig:fft1D_inputs} and~\ref{fig:fft1D_outputs} \add{show the
-    visualization of the \texttt{fft\_1D} inputs and outputs values. Results are
-    complex value encoded on double precision. PyTracer allows visualizing the
+    visualization of the \texttt{fft\_1D} input and output values. Results are
+    complex values encoded in double precision. PyTracer allows visualizing the
     numerical precision of real (blue points) and imaginary (orange points) parts.}
@@
         [-1,1]\times[-1,1]$. The result is a 2D-array that is natively supported by
-    PyTracer. We observe a significant loss of precision in places, which follows
+    PyTracer. We observe a significant loss of precision in some regions, which follows
     an interesting pattern that could be further investigated.}
@@
 
-\subsection{\pytracer allows visualizing numerical stability at a fine grained level}
+\subsection{\pytracer allows visualizing numerical stability at a fine-grained level}
 
 \add{We illustrate on two examples how PyTracer is effective for analyzing
-    the numerical stability at a fine grained level: Face recognition and Bayesian Ridge Regression.}
+    numerical stability in complex codes at a fine-grained level: Face recognition and Bayesian Ridge Regression.}
 The face recognition example uses eigenfaces (eigenvectors) and Support Vector
@@
 This example uses a Principal Component Analysis (PCA) to extract the eigenfaces
-and then trains an SVM classifier to predict the name associated with a face.
-\add{When executing within fuzzy environment, this example crashed with the following
-    Python error raised: \texttt{"SVD did not converge"}.}
+and then trains an SVM classifier to predict the label associated with a face.
+\add{When executing in PyTracer, this example crashed because the Singular Value Decomposition (SVD) did not converge.}
 This example is the only one to raise an error due to the
-non-convergence of the Singular Value Decomposition (SVD) performed in the PCA.
+non-convergence of the SVD performed in the PCA.
 The PCA uses the Randomized SVD~\cite{halko2011finding} method
@@
 have the same accuracy~\cite{nakatsukasa2013stable}, the Divide \& Conquer
-makes the SVD to not converge with MCA.
-
-Replacing \texttt{gesdd} for \texttt{gesvd} solves the SVD convergence issue.
+does not converge with MCA.
+
+Replacing \texttt{gesdd} for \texttt{gesvd} solved the SVD convergence issue.
 \pytracer allows to quickly visualize the new precision of the result.
-Figure~\ref{fig:randomized_svd_S} shows the precision of the eigenvalues
+Figure~\ref{fig:face_recognition_svd} shows the precision of the eigenvalues
 computed displayed in decreasing order with \texttt{gesvd} \add{in single precision}, 
@@
 metrics (precision, recall, F1-score, and support) are identical to the IEEE
-execution for all MCA samples. \add{We can note that even with using the \texttt{gesvd},
-    the precision of the singular values (vectors) is not uniform. 
-    Indeed, we can see that the precision of the lowest singular values (vectors) decreases 
+execution for all MCA samples. \add{We can note that even with the \texttt{gesvd} method,
+    the precision of the singular values and eigenvectors is not uniform. 
+    Indeed, we can see that the precision of the lowest singular values and eigenvectors decreases 
     until reaching 0 significant bits.}
 
-The second example, compares a Bayesian Ridge Regression (BRR) to the Ordinary
+The second example compares a Bayesian Ridge Regression (BRR) to the Ordinary
 Least Squares (OLS) estimator on a synthetic dataset and for one-dimensional
@@
 raise a runtime error, the regression coefficients computed from the fitting are
-non-significant. \pytracer traces reveal that the SVD solver used is the root
+non-significant. \pytracer traces reveal that the SVD solver used is once again the root
 cause for this error. \add{Indeed, the BayesianRidge model first computes an SVD
     before iteratively updating the coefficients until reaching the convergence
-    criterion. However, PyTracer reveals an issue in the singular values computed.}
-\add{We can see on Figure}~\ref{fig:BRR_svd} \add{that the last singular values is
-    \texttt{NaN} due to numerical error during the SVD although the remaining
+    criterion. However, PyTracer shows an issue in the singular values computed.}
+\add{We can see in Figure}~\ref{fig:BRR_svd} \add{that the last singular values is
+    \texttt{NaN} due to numerical errors in the SVD, although the remaining
     singular values exhibit high numerical precision (between 44 and 50 bits).
-    Surprinsingly, this \texttt{NaN} value does not raise issue and is silently
-    propagated. Indeed, the stopping criterion compares that the sum of the absolute
-    differences between coefficients of two successive iterations but coefficients
-    contain \texttt{NaN} since they are computed from singular values. Hence, the
-    following condition is never met \texttt{if iter\_ != 0 and
-        np.sum(np.abs(coef\_old\_ - coef\_)) < self.tol:} since the comparison with a
-    \texttt{NaN} is always false.}
-
-\add{The OLS uses the Least Square to fit the model. PyTracer shows that the
-    coefficients fitted are \texttt{NaN} values. By looking at the callgraph, we can
+    Surprinsingly, this \texttt{NaN} value does not raise an exception and is silently
+    propagated. Indeed, the stopping criterion is never verified and the 
+    optimization stops after reaching the maximal number of iterations.}
+
+\add{Similarly, for OLS, PyTracer tracers show that the
+    regression coefficients fitted are \texttt{NaN} values. By looking at the callgraph, we can
     see that the scipy calls the \texttt{lstsq} method from the
-    \texttt{scipy.linalg} package which uses the \texttt{gelsd} LAPACK function.
-    Figure}~\ref{fig:OLS_svd} \add{shows the singular values returned by the
-    \texttt{lstsq} method shows that one singular value has a \texttt{NaN} value
-    that corrupted the calculation of the coefficients. By using the \texttt{gelss},
-    PyTracer shows that the \texttt{NaN} value disapeared from the singular values
-    (fig.}~\ref{fig:OLS_svd_fixed}\add{) and thus does not contaminated the computation of
-    the coefficients that exhibit a precision of 42 bits in average. We can see that
-    the full access to all values computed by the application with PyTracer allows
-    the user to quickly identify the issue.}
+    \texttt{scipy.linalg} package which uses the \texttt{gesdd} LAPACK function.
+    Figure}~\ref{fig:OLS_svd} \add{shows that one singular value is a \texttt{NaN} value,
+    which corrupted the calculation of the coefficients. When using the \texttt{gesvd} method, 
+     the \texttt{NaN} value disapears 
+    (Fig.}~\ref{fig:OLS_svd_fixed}\add{), resulting in a precision of 
+    42 bits in average in the coefficients. We can see that having
+    access to all the values computed by the application with PyTracer allows
+    the user to efficiently identify numerical issues.}
 
@@
 fundamental scientific computing components such as the LAPACK library. \add{The
-    unify view of all traces allows the user to quickly navigate through the
-    different numerical precision of variables which saves time for the developer
-    compare to the print statement debugging.}
+    unified view of all traces allows the user to quickly navigate through the
+     numerical precision of different variables.}
 % The Pytracer findings can therefore be extended to many application domains. %
@@
         \includegraphics[width=\linewidth]{figure/BRR_singular_values.png}
-        \caption{BRR}
+        \caption{BRR (\texttt{gesdd})}
         \label{fig:BRR_svd}
@@
         \includegraphics[width=\linewidth]{figure/OLS_singular_values.png}
-        \caption{OLS}
+        \caption{OLS (\texttt{gesdd})}
         \label{fig:OLS_svd}
@@
         \includegraphics[width=\linewidth]{figure/BRR_singular_values_fixed.png}
-        \caption{BRR (fixed)}
+        \caption{BRR (\texttt{gesvd})}
         \label{fig:BRR_svd_fixed}
@@
         \includegraphics[width=\linewidth]{figure/OLS_singular_values_fixed.png}
-        \caption{OLS (fixed)}
+        \caption{OLS (\texttt{gesvd})}
         \label{fig:OLS_svd_fixed}
@@
             Bayesian Ridge model fitting (left) and from the Ordinary Least Square model
-            fitting (right) in the Bayesian Ridge Regression example. Red star
-            represents \texttt{NaN} value. Both SVD give \texttt{NaN} coefficients.
-            Switching from Divide \& Conquer to QR factorization improve numerical precision.
-            PyTracer helps to quickly visualize improvements.}}
+            fitting (right) in the Bayesian Ridge Regression example. Red stars
+            represent \texttt{NaN} values. 
+            Switching from Divide \& Conquer (\texttt{gesdd}) to QR (\texttt{gesvd}) factorization improves numerical precision.
+            PyTracer helps visualizing improvements.}}
 \end{figure}
@@
     RR} \remove{and \textit{Slowdown MCA}} shows the slowdown within the fuzzy environment.
-Without fuzzy, \pytracer introduces an average slowdown of $17\times$ high for
+Without fuzzy, \pytracer introduces an average slowdown of $17\times$ for
 the examples running less than 8 seconds because \pytracer spends most of its
@@
 $3.5\times$. Finally, the \remove{fuzzy instrumentation} \add{using MCA
-    operations (throuhg fuzzy) instead of the native ones} increases the average
+    operations (through fuzzy) instead of the native ones} increases the average
 slowdown to $37\times$ for RR\remove{and $43\times$ for Full MCA}.
@@
         of \pytracer using the fuzzy environment with \add{the} RR \remove{and Full MCA} mode\remove{s}. The
-        first \remove{first} \add{last} four examples measure the initialization
+        \remove{first} \add{last} four examples measure the initialization
         steps depending on the modules instrumented. 
@@
 the MPFR~\cite{fousse2007mpfr} library. \add{ADAPT \mbox{~\cite{menon2018adapt}} uses
-    Automatic Differentiation to compute a sensitivity profile for each variable of
-    given program}. Finally, the work in~\cite{tang2016software} proposed a
+    Automatic Differentiation to compute a sensitivity profile for each variable in a
+    program}. Finally, the work in~\cite{tang2016software} proposed a
 source-to-source framework for executing targeted code in infinite and fixed

### 2022-05-12 IEEEtran/paper-annotated.tex
removed annex
Update

@@
 \TG{I'm still unsure what to do with this part, it looks out of place.}
-\add{PyTracer follows a three steps approach:}
-\begin{enumerate}
-    \item \add{Automatic instrumentation of Python programs to save traces containing input and output values of all functions.}
-    \item \add{Traces aggregation to produce a statistics summary.}
-    \item \add{Interactive visualization to navigate through code execution.}
-\end{enumerate}
+% \add{PyTracer follows a three steps approach:}
+% \begin{enumerate}
+%     \item \add{Automatic instrumentation of Python programs to save traces containing input and output values of all functions.}
+%     \item \add{Traces aggregation to produce a statistics summary.}
+%     \item \add{Interactive visualization to navigate through code execution.}
+% \end{enumerate}
+
+\pytracer adopts the three-step workflow shown in Figure~\ref{fig:workflow}.
+First, \pytracer uses \textit{monkey patching} to replace the functions called
+by the application with a wrapper that saves their arguments and returned values
+in a trace file.
+Second, it executes the application multiple times with noise injection, and
+aggregates the resulting trace files to compute summary statistics about each
+traced variable. Finally, a Plotly dashboard provides interactive visualizations
+highlighting unstable code sections.
 
@@
     although control-flow analysis can help to merge divergent execution paths.
+    Hence, PyTracer is restricted to single-threaded applications even if its usage
+    is limited in Python due to the Global Interperter Lock (GIL) mechanism
+    that allows only one thread to hold the control of the Python interpreter.
 }
@@
 % \subsection{Pytracer workflow}
-\pytracer adopts the three-step workflow shown in Figure~\ref{fig:workflow}.
-First, \pytracer uses \textit{monkey patching} to replace the functions called
-by the application with a wrapper that saves their arguments and returned values
-in a trace file.
-Second, it executes the application multiple times with noise injection, and
-aggregates the resulting trace files to compute summary statistics about each
-traced variable. Finally, a Plotly dashboard provides interactive visualizations
-highlighting unstable code sections.
 
@@
     simulates roundoff errors by applying function $inexact$ only to the
-outputs returned by functions. The Precision Bounding (PB) mode can
+    output returned by a function. The Precision Bounding (PB) mode can
     identify other types of instabilities, in particular catastrophic
@@
     propagated. Indeed, the stopping criterion is never verified and the 
-    optimization stops after reaching the maximal number of iterations.}
+    optimization stops after reaching the maximal number of iterations.
+    Figure}~\ref{fig:BRR_svd_fixed} \add{shows that uses
+    the \texttt{gesvd} instead of the \texttt{gesdd} method removes the \texttt{NaN} value
+    although the last singular values stills have a low precision (below 0).
+    Following Equation}~\ref{eq:sig-digits}, \add{a number of significant digits below 0 means that the
+    variability ($\sigma$) is higher than the average value ($\mu$)}.
 
@@
 % demonstrating its scalability fluently.
+
+\subsection{\pytracer instrumentation limitations}
+
+\add{
+    The limitations of the PyTracer's instrumentation have little impact in practice
+    since we have encountered few classes having non-writeable attributes in practice.
+    Moreover, those classes are generally used in higher-level classes written in
+    pure Python. For instance, the SGD class that implements the Stochastic Gradient
+    Descent in scikit-learn takes a loss function as a parameter. Loss functions are
+    implemented in Cython in scikit-learn and Pytracer is not able to instrument
+    them. However, Pytracer can dump the instance of LossFunction if they are used
+    by the SGD class as arguments, which is a frequently observed pattern in
+    Scikit-learn for instance. So one still has an estimation of variability for the
+    attributes of the class. Finally, one can use Veritracer to trace the methods of
+    those Cython classes for an in-depth analysis since it is the C language
+    underhood. We have encountered few iterators and none of them involved floating
+    point values so we were able to safely ignore them. 
+}
 
@@
 
-\appendix
-
-\include{annex}
+% \appendix
+% \include{annex}
 

### 2022-05-12 IEEEtran/paper.tex
Merge .tex files, now only use paper.tex to generate both final and annotated version

@@
 
+\usepackage{ifthen}
+\newif\ifANNOTATED
+\ifthenelse{\equal{\detokenize{annotated}}{\jobname}}{
+\ANNOTATEDtrue
+}{
+\ANNOTATEDfalse
+}
+
+\ifANNOTATED
+\DeclareRobustCommand{\add}[1]{\sethlcolor{lightgreen}\hl{#1}}
+\DeclareRobustCommand{\remove}[1]{\textcolor{lightred}{\sout{#1}}}
+\DeclareRobustCommand{\addCite}[1]{\textcolor{lightgreen}{\mbox{#1}}}
+\newcommand{\TG}[1]{\color{red}\textsc{From Tristan}: #1\xspace\color{black}}
+\else
 \DeclareRobustCommand{\add}[1]{#1}
 \DeclareRobustCommand{\remove}[1]{}
-
-\DeclareRobustCommand{\addCite}[1]{\textcolor{lightgreen}{\mbox{#1}}}
+\DeclareRobustCommand{\addCite}[1]{#1}
+\newcommand{\TG}[1]{}
+\fi
 
@@
 valuable in contrast to theoretical approaches based on condition numbers or
-backward error analysis~\cite{higham2002accuracy}, which require
+backward error analysis~\addCite{\cite{higham2002accuracy}}, which require
 detailed modeling of the program and its numerical implementation. Similarly,
-static code analysis techniques~\cite{goubault2006static} hardly scale
+static code analysis techniques~\addCite{\cite{goubault2006static}} hardly scale
 to large code bases, particularly in dynamically-typed languages such as Python.
@@
 
-\section{Philosophy of \pytracer}
-
-\add{PyTracer follows a three steps approach:}
-\begin{enumerate}
-    \item \add{Automatic instrumentation of Python programs to save the value of inputs and outputs of function in a file.}
-    \item \add{Aggregation of the traces generated to produce a statistics summary.}
-    \item \add{Interactive visualization to navigate through the code execution.}
-\end{enumerate}
+\section{\pytracer design}
+
+\TG{I'm still unsure what to do with this part, it looks out of place.}
+% \add{PyTracer follows a three steps approach:}
+% \begin{enumerate}
+%     \item \add{Automatic instrumentation of Python programs to save traces containing input and output values of all functions.}
+%     \item \add{Traces aggregation to produce a statistics summary.}
+%     \item \add{Interactive visualization to navigate through code execution.}
+% \end{enumerate}
+
+\pytracer adopts the three-step workflow shown in Figure~\ref{fig:workflow}.
+First, \pytracer uses \textit{monkey patching} to replace the functions called
+by the application with a wrapper that saves their arguments and returned values
+in a trace file.
+Second, it executes the application multiple times with noise injection, and
+aggregates the resulting trace files to compute summary statistics about each
+traced variable. Finally, a Plotly dashboard provides interactive visualizations
+highlighting unstable code sections.
 
 \add{
-    The main goal of PyTracer is to help the developper visualizing the numerical
+    The main goal of PyTracer is to help developpers visualize the numerical
     stability of Python applications. PyTracer saves time for the user by
@@
     although control-flow analysis can help to merge divergent execution paths.
+    Hence, PyTracer is restricted to single-threaded applications even if its usage
+    is limited in Python due to the Global Interperter Lock (GIL) mechanism
+    that allows only one thread to hold the control of the Python interpreter.
 }
 
-\section{\pytracer design}
-
 % \subsection{Pytracer workflow}
-\pytracer adopts the three-step workflow shown in Figure~\ref{fig:workflow}.
-First, \pytracer uses \textit{monkey patching} to replace the functions called
-by the application with a wrapper that saves their arguments and returned values
-in a trace file.
-Second, it executes the application multiple times with noise injection, and
-aggregates the resulting trace files to compute summary statistics about each
-traced variable. Finally, a Plotly dashboard provides interactive visualizations
-highlighting unstable code sections.
 
@@
 numerical noise, we experimented primarily with Monte-Carlo Arithmetic (MCA) as
-it is an accurate model for floating-point errors~\cite{verificarlo}.
+it is an accurate model for floating-point errors~\addCite{\cite{verificarlo}}.
 
@@
 precision and $\xi \in (-\frac{1}{2},\frac{1}{2})$ is a random uniform variable.
-Virtual precision allows for the simulation of reduced working precision. MCA
-can be applied in three modes \add{but we only used the} Random Rounding (RR) \add{in our
-    experiments} \remove{, Precision Bounding (PB), and full MCA,} which apply
-function $inexact$ to the output. \remove{, the inputs, or both, respectively.
-    While the RR mode is equivalent to stochastic rounding, the PB mode can also
-    identify catastrophic cancellations.} \add{Random Rounding simulates roundoff errors.}
+Virtual precision allows for the simulation of reduced working precision.
+\add{In our experiments, we used MCA in Random Rounding (RR) mode, which
+    simulates roundoff errors by applying function $inexact$ only to the
+    output returned by a function. The Precision Bounding (PB) mode can
+    identify other types of instabilities, in particular catastrophic
+    cancellations, however, it is more difficult to apply to large code bases
+    as it often leads to execution errors that require human intervention.}
 
@@
 where $\mu$ and $\sigma$ are the sample mean and standard deviation of a
-variable sampled with MCA.
+variable sampled with MCA. \add{This can be seen as the ratio signal over noise.}
 Sohier et al.~\cite{sohier2021confidence} recently provided a generalization of
@@
 \pytracer stores traces in the pickle format, a binary format to serialize
-Python objects. The main advantage of the pickle format compared to other
-serialization approaches such as marshal or JSON is the ability to serialize
-most Python objects with a native compression. In addition, pickle writes
+Python objects. The main advantages of the pickle format compared to other
+serialization approaches such as marshal or JSON are its ability to serialize
+most Python objects and its native compression.  In addition, pickle writes
 Python objects sequentially, which preserves the temporal ordering required by
@@
 single-threaded and that the control flow does not depend on a random state.
-\add{Therefore, \mbox{\pytracer} cannot merge traces resulting from a different
-    control flow path and stops the parsing when encountering one.}
+\add{Therefore, \mbox{\pytracer} cannot merge traces resulting from different
+    control flow paths and will stop the parsing when encountering such a situation.}
 
@@
 activated MCA in the Python interpreter \add{as well as} BLAS, LAPACK, NumPy,
-SciPy, and scikit-learn. \add{Only instrumented the Python interpreter would
-    lead to only perturbe pure Python floating-point operations and thus to miss
-    operations in compiled codes (i.e. Cython and shared libraries).} We used the default virtual
+SciPy, and scikit-learn. \add{Instrumenting only the Python interpreter would
+    lead to only perturb pure Python floating-point operations and thus miss
+    operations in compiled codes (i.e., Cython and shared libraries).} \add{We
+    used MCA in Random Rounding (RR) mode, with 5 repetitions}. We used the default virtual
 precision in Verificarlo, namely 24 bits for single-precision floating-point
@@
 Overall, the tracing and parsing of SciPy and scikit-learn examples in Random
-Rounding mode was entirely successful for 32/40 examples and showed an average
-precision loss of 8 bits. The remaining examples failed due to numerical errors
+Rounding mode was entirely successful for 32/40 examples\remove{ and showed an average
+    precision loss of 8 bits}. The remaining examples failed due to numerical errors
 in the libraries, which we discuss hereafter. 
@@
 raise a runtime error, the regression coefficients computed from the fitting are
-non-significant. \pytracer traces reveal that the SVD solver used is the root
+non-significant. \pytracer traces reveal that the SVD solver used is once again the root
 cause for this error. \add{Indeed, the BayesianRidge model first computes an SVD
     before iteratively updating the coefficients until reaching the convergence
-    criterion. However, PyTracer reveals an issue in the singular values computed.}
-\add{We can see on Figure}~\ref{fig:BRR_svd} \add{that the last singular values is
-    \texttt{NaN} due to numerical error during the SVD although the remaining
+    criterion. However, PyTracer shows an issue in the singular values computed.}
+\add{We can see in Figure}~\ref{fig:BRR_svd} \add{that the last singular values is
+    \texttt{NaN} due to numerical errors in the SVD, although the remaining
     singular values exhibit high numerical precision (between 44 and 50 bits).
-    Surprinsingly, this \texttt{NaN} value does not raise issue and is silently
-    propagated. Indeed, the stopping criterion compares that the sum of the absolute
-    differences between coefficients of two successive iterations but coefficients
-    contain \texttt{NaN} since they are computed from singular values. Hence, the
-    following right condition is never met \texttt{if iter\_!=0 and np.sum(np.abs(coef\_old\_-coef\_))<self.tol:} since the comparison with a
-    \texttt{NaN} is always false.}
-
-\add{The OLS uses the Least Square to fit the model. PyTracer shows that the
-    coefficients fitted are \texttt{NaN} values. By looking at the callgraph, we can
+    Surprinsingly, this \texttt{NaN} value does not raise an exception and is silently
+    propagated. Indeed, the stopping criterion is never verified and the 
+    optimization stops after reaching the maximal number of iterations.
+    Figure}~\ref{fig:BRR_svd_fixed} \add{shows that uses
+    the \texttt{gesvd} instead of the \texttt{gesdd} method removes the \texttt{NaN} value
+    although the last singular values stills have a low precision (below 0).
+    Following Equation}~\ref{eq:sig-digits}, \add{a number of significant digits below 0 means that the
+    variability ($\sigma$) is higher than the average value ($\mu$)}.
+
+\add{Similarly, for OLS, PyTracer tracers show that the
+    regression coefficients fitted are \texttt{NaN} values. By looking at the callgraph, we can
     see that the scipy calls the \texttt{lstsq} method from the
-    \texttt{scipy.linalg} package which uses the \texttt{gelsd} LAPACK function.
-    Figure}~\ref{fig:OLS_svd} \add{shows the singular values returned by the
-    \texttt{lstsq} method shows that one singular value has a \texttt{NaN} value
-    that corrupted the calculation of the coefficients. By using the \texttt{gelss},
-    PyTracer shows that the \texttt{NaN} value disapeared from the singular values
-    (fig.}~\ref{fig:OLS_svd_fixed}\add{) and thus does not contaminated the computation of
-    the coefficients that exhibit a precision of 42 bits in average. We can see that
-    the full access to all values computed by the application with PyTracer allows
-    the user to quickly identify the issue.}
+    \texttt{scipy.linalg} package which uses the \texttt{gesdd} LAPACK function.
+    Figure}~\ref{fig:OLS_svd} \add{shows that one singular value is a \texttt{NaN} value,
+    which corrupted the calculation of the coefficients. When using the \texttt{gesvd} method, 
+    the \texttt{NaN} value disapears 
+    (Fig.}~\ref{fig:OLS_svd_fixed}\add{), resulting in a precision of
+    42 bits in average in the coefficients. We can see that having
+    access to all the values computed by the application with PyTracer allows
+    the user to efficiently identify numerical issues.}
 
@@
 fundamental scientific computing components such as the LAPACK library. \add{The
-    unify view of all traces allows the user to quickly navigate through the
-    different numerical precision of variables which saves time for the developer
-    compare to the print statement debugging.}
+    unified view of all traces allows the user to quickly navigate through the
+    numerical precision of different variables.}
 % The Pytracer findings can therefore be extended to many application domains. %
@@
 
-\clearpage
-\appendix
-
-\include{annex}
+% \appendix
+% \include{annex}
 

### 2022-05-13 IEEEtran/paper.tex
Fixed makefile
Fixed section 2 intro

@@
 
-\TG{I'm still unsure what to do with this part, it looks out of place.}
 % \add{PyTracer follows a three steps approach:}
@@
 
-\pytracer adopts the three-step workflow shown in Figure~\ref{fig:workflow}.
-First, \pytracer uses \textit{monkey patching} to replace the functions called
+\add{To detect numerical instabilities, \pytracer works in three main steps:}
+\begin{enumerate}
+\item It instruments Python programs and their module dependencies automatically, to save the input and output values of functions in a trace file.
+\item It executes the instrumented program several times using Monte-Carlo Arithmetic to inject perturbations in function outputs.
+\item It aggregates all trace files to compute statistics about the traced values, and visualize them in a GUI.
+\end{enumerate}
+\add{
+    To implement these steps, \pytracer adopts the workflow shown in Figure~\ref{fig:workflow}.
+At step 1, \pytracer uses \textit{monkey patching} to replace the functions called
 by the application with a wrapper that saves their arguments and returned values
-in a trace file.
-Second, it executes the application multiple times with noise injection, and
-aggregates the resulting trace files to compute summary statistics about each
-traced variable. Finally, a Plotly dashboard provides interactive visualizations
+in a trace file. At step 2, it executes the application multiple times with Monte-Carlo Arithmetic as implemented in Fuzzy, a collection 
+of scientific computing libraries recompiled with the Verificarlo tool. It then
+aggregates the resulting trace files to compute summary statistics on
+traced variable. At step 3, a Plotly dashboard provides interactive visualizations
 highlighting unstable code sections.
-
-\add{
-    The main goal of PyTracer is to help developpers visualize the numerical
-    stability of Python applications. PyTracer saves time for the user by
-    instrumenting and aggregating values. In the same way that GDB makes the user
-    save time when debugging an application by providing all information in one
-    layout, PyTracer allows the user to visualize the overall numerical quality to
-    quickly detect instabilities. The PyTracer visualization layout improves result
-    analysis in any case since 1) the user does not have to manually instrument its
-    code to dump raw data and creates specific post-processing scripts to visualize
-    it 2) PyTracer allows the user to export the raw data traced to extend the
-    analysis. 
 }
 
-\add{
-    The main challenge addressed by PyTracer is the transparent instrumentation of Python 
-    applications. Indeed, since Python is an interpreted language, one has no complete 
-    view of the function that will be executed by a given program. 
-    Moreover, for Python applications used in HPC environments, one has
-    most of the time no access to source codes or with limited write access.
-    Therefore, PyTracer tackles this issue by instrumenting the function dynamically 
-    thanks to the Python introspection.
-}
-
-\add{
-    The trace-based approach used by PyTracer permits to limit the 
-    overhead at runtime since the statistics computation is reported to the postprocess analysis.
-    However, it limits the aggregation to deterministic executions,
-    although control-flow analysis can help to merge divergent execution paths.
-    Hence, PyTracer is restricted to single-threaded applications even if its usage
-    is limited in Python due to the Global Interperter Lock (GIL) mechanism
-    that allows only one thread to hold the control of the Python interpreter.
-}
+% \add{
+%     The main goal of PyTracer is to help developpers visualize the numerical
+%     stability of Python applications. PyTracer saves time for the user by
+%     instrumenting and aggregating values. In the same way that GDB makes the user
+%     save time when debugging an application by providing all information in one
+%     layout, PyTracer allows the user to visualize the overall numerical quality to
+%     quickly detect instabilities. The PyTracer visualization layout improves result
+%     analysis in any case since 1) the user does not have to manually instrument its
+%     code to dump raw data and creates specific post-processing scripts to visualize
+%     it 2) PyTracer allows the user to export the raw data traced to extend the
+%     analysis. 
+% }
+
+% \add{
+%     The main challenge addressed by PyTracer is the transparent instrumentation of Python 
+%     applications. Indeed, since Python is an interpreted language, one has no complete 
+%     view of the function that will be executed by a given program. 
+%     Moreover, for Python applications used in HPC environments, one has
+%     most of the time no access to source codes or with limited write access.
+%     Therefore, PyTracer tackles this issue by instrumenting the function dynamically 
+%     thanks to the Python introspection.
+% }
+
+% \add{
+%     The trace-based approach used by PyTracer permits to limit the 
+%     overhead at runtime since the statistics computation is reported to the postprocess analysis.
+%     However, it limits the aggregation to deterministic executions,
+%     although control-flow analysis can help to merge divergent execution paths.
+%     Hence, PyTracer is restricted to single-threaded applications even if its usage
+%     is limited in Python due to the Global Interperter Lock (GIL) mechanism
+%     that allows only one thread to hold the control of the Python interpreter.
+% }
 

### 2022-05-16 IEEEtran/paper.tex

@@
 
-\ifANNOTATED
-\DeclareRobustCommand{\add}[1]{\sethlcolor{lightgreen}\hl{#1}}
+% \ifANNOTATED
+\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
+\DeclareRobustCommand{\add}[1]{\textcolor{ao(english)}{#1}}%\sethlcolor{lightgreen}\hl{#1}}
 \DeclareRobustCommand{\remove}[1]{\textcolor{lightred}{\sout{#1}}}
@@
 \newcommand{\TG}[1]{\color{red}\textsc{From Tristan}: #1\xspace\color{black}}
-\else
-\DeclareRobustCommand{\add}[1]{#1}
-\DeclareRobustCommand{\remove}[1]{}
-\DeclareRobustCommand{\addCite}[1]{#1}
-\newcommand{\TG}[1]{}
-\fi
+% \else
+% \DeclareRobustCommand{\add}[1]{#1}
+% \DeclareRobustCommand{\remove}[1]{}
+% \DeclareRobustCommand{\addCite}[1]{#1}
+% \newcommand{\TG}[1]{}
+% \fi
 
@@
 
-\pytracer estimates the variability of floating-point variables by combining
-program traces obtained with different numerical perturbations, which requires
-(\add{a}\remove{1}) generating numerically-perturbed executions,
-(\add{b}\remove{2}) tracing floating-point computations along program
-executions, and (\add{c}\remove{3}) visualizing stability evaluations.
-\add{PyTracer addresses (a) by relying on the ``fuzzy" Python environment instrumented with Monte-Carlo
-    arithmetic, (b) by dynamically instrumenting Python functions,
-    modules, and classes through meta-programming, and (c) by visualizing stability measures throughout program executions
-    with an interactive Plotly
-    dashboard.
-    \mbox{\pytracer} is available at
+\pytracer estimates the variability of floating-point variables by
+combining program traces obtained with different numerical perturbations,
+which requires (\add{a}\remove{1}) generating numerically-perturbed
+executions, (\add{b}\remove{2}) tracing floating-point computations along
+program executions, and (\add{c}\remove{3}) visualizing stability
+evaluations. \add{PyTracer addresses (a) by relying on
+Fuzzy~\addCite{\cite{kiar2020comparing}}, a pre-existing collection of scientific
+computing libraries instrumented with Monte-Carlo arithmetic through the
+Verificarlo tool~\cite{verificarlo}, (b) by dynamically instrumenting
+Python functions, modules, and classes through meta-programming, and (c) by
+visualizing stability measures throughout program executions with an
+interactive Plotly dashboard. \mbox{\pytracer} is available at
 \mbox{\href{https://github.com/big-data-lab-team/pytracer.git}{github.com/big-data-lab-team/pytracer.git}}
-    under MIT License.} \remove{\mbox{\pytracer} addresses these requirements with
-    (1) a ``fuzzy" Python interpreter instrumented with Monte-Carlo arithmetic, (2)
-    a dynamic instrumentation of Python functions, modules, and classes through
-    meta-programming, (3) an interactive Plotly dashboard to visualize stability
-    measures throughout program executions. }
+under MIT License.} \remove{\mbox{\pytracer} addresses these requirements
+with (1) a Fuzzy Python interpreter instrumented with Monte-Carlo
+arithmetic, (2) a dynamic instrumentation of Python functions, modules, and
+classes through meta-programming, (3) an interactive Plotly dashboard to
+visualize stability measures throughout program executions. }
 
@@
 
-% \add{PyTracer follows a three steps approach:}
-% \begin{enumerate}
-%     \item \add{Automatic instrumentation of Python programs to save traces containing input and output values of all functions.}
-%     \item \add{Traces aggregation to produce a statistics summary.}
-%     \item \add{Interactive visualization to navigate through code execution.}
-% \end{enumerate}
-
-\add{To detect numerical instabilities, \pytracer works in three main steps:}
+\add{
+    To detect numerical instabilities, \pytracer works in three main steps:
 \begin{enumerate}
-\item It instruments Python programs and their module dependencies automatically, to save the input and output values of functions in a trace file.
-\item It executes the instrumented program several times using Monte-Carlo Arithmetic to inject perturbations in function outputs.
-\item It aggregates all trace files to compute statistics about the traced values, and visualize them in a GUI.
+\item It instruments Python programs and their module dependencies
+automatically, to save the input and output values of functions in a trace
+file.
+\item It executes the instrumented program several times using Monte-Carlo
+Arithmetic to inject perturbations in function outputs.
+\item It aggregates all trace files to compute statistics about the traced
+values, and visualize them in a GUI.
 \end{enumerate}
-\add{
-    To implement these steps, \pytracer adopts the workflow shown in Figure~\ref{fig:workflow}.
-At step 1, \pytracer uses \textit{monkey patching} to replace the functions called
-by the application with a wrapper that saves their arguments and returned values
-in a trace file. At step 2, it executes the application multiple times with Monte-Carlo Arithmetic as implemented in Fuzzy, a collection 
-of scientific computing libraries recompiled with the Verificarlo tool. It then
+\pytracer adopts the workflow shown in Figure~\ref{fig:workflow}.
+At step 1, \pytracer uses monkey patching to replace the functions called
+by the application with a wrapper that saves their arguments and returned
+values in a trace file. At step 2, it executes the application multiple
+times with Monte-Carlo Arithmetic as implemented in the
+Fuzzy~\cite{kiar2020comparing} environment. It then
 aggregates the resulting trace files to compute summary statistics on
-traced variable. At step 3, a Plotly dashboard provides interactive visualizations
-highlighting unstable code sections.
+traced variable. At step 3, a Plotly dashboard provides interactive
+visualizations highlighting unstable code sections.
 }
-
-% \add{
-%     The main goal of PyTracer is to help developpers visualize the numerical
-%     stability of Python applications. PyTracer saves time for the user by
-%     instrumenting and aggregating values. In the same way that GDB makes the user
-%     save time when debugging an application by providing all information in one
-%     layout, PyTracer allows the user to visualize the overall numerical quality to
-%     quickly detect instabilities. The PyTracer visualization layout improves result
-%     analysis in any case since 1) the user does not have to manually instrument its
-%     code to dump raw data and creates specific post-processing scripts to visualize
-%     it 2) PyTracer allows the user to export the raw data traced to extend the
-%     analysis. 
-% }
-
-% \add{
-%     The main challenge addressed by PyTracer is the transparent instrumentation of Python 
-%     applications. Indeed, since Python is an interpreted language, one has no complete 
-%     view of the function that will be executed by a given program. 
-%     Moreover, for Python applications used in HPC environments, one has
-%     most of the time no access to source codes or with limited write access.
-%     Therefore, PyTracer tackles this issue by instrumenting the function dynamically 
-%     thanks to the Python introspection.
-% }
-
-% \add{
-%     The trace-based approach used by PyTracer permits to limit the 
-%     overhead at runtime since the statistics computation is reported to the postprocess analysis.
-%     However, it limits the aggregation to deterministic executions,
-%     although control-flow analysis can help to merge divergent execution paths.
-%     Hence, PyTracer is restricted to single-threaded applications even if its usage
-%     is limited in Python due to the Global Interperter Lock (GIL) mechanism
-%     that allows only one thread to hold the control of the Python interpreter.
-% }
-
-% \subsection{Pytracer workflow}
-
-% \tristan{mention monkey patching}
 
@@
 
-% \begin{listing}
-%     \centering
-%     \begin{lstlisting}[language=Python,style=customPython]
-% def get_wrapper_function(module, qualname, name, function):
-%     """Returns the instrumented function as a string.
-%     This string will be compiled with the compile builtin function
-
-%     Parameters:
-%         module: Name of the function module
-%         qualname: Qualified name of the function
-%         name: Name of the function
-%         function: Python object function
-
-%     Returns:
-%         wrapper_code: The code source of the wrapper
-%     """
-%     info = (id(function), function_module, qualname)
-%     wrapper_code = f"""
-%     def {function_wrapper_name}(*args, **kwargs):
-%         return generic_wrapper({info},*args,**kwargs)"""
-%     return wrapper_code
-% \end{lstlisting}
-%     \caption{Function to create the instrumented version of a function.
-%         \pytracer uses the identifier of the function instead of the 
-%         actual function to handle aliases and avoid duplicate instrumentation.}
-%     \label{fig:wrapper_creation}
-% \end{listing}
-
-% \begin{listing}
-%     \centering
-%     \begin{lstlisting}[language=Python,style=customPython,]
-% def generic_wrapper(self, info, *args, **kwargs):
-%     """Generic wrapper saving inputs and outputs of the wrapped function.
-%     The id_dict dict keeps a mapping between the original function identifier
-%     and itself. Arguments are binded to avoid mispositioning.
-%     Returns the actual output of the wrapped function.
-
-%     Parameters:
-%         info: Tuple with the function's id, function's module and function's name
-%         *args: Positional calling arguments
-%         **kwargs: Keyword calling arguments
-
-%     Returns:
-%         outputs: Outputs of the wrapped function
-%     """
-%     fid, module_name, function_name = info
-%     function = original_function_cache.id_dict[fid]
-%     bind = Binding(function, *args, **kwargs)
-%     stack = self.backtrace()
-%     time = elements()
-%     self.inputs(time, module_name, function_name, function, bind.arguments, stack)
-%     outputs = function(*bind.args, **bind.kwargs)
-%     self.outputs(time, module_name, function_name, function, outputs, stack)
-%     return outputs
-% \end{lstlisting}
-%     \caption{\pytracer's generic wrapper function that saves
-%         the inputs and outputs of the wrapped function.}
-%     \label{fig:generic_wrapper}
-% \end{listing}
-
 \subsubsection{Instrumenting classes}
@@
 stochastic  arithmetic,  uncertainty  or  sensitivity analysis [23], and random
-seed analysis [11].  \add{PyTracer is agnostic to the noise model used and therefore
-    works for all methods mentioned}.  For our use cases, we focus on stochastic
+seed analysis [11].  \add{PyTracer is agnostic to the noise model used and can therefore
+be used for all these methods}.  For our use cases, we focus on stochastic
 arithmetic since it does not make any assumption about the noise model, in
@@
 available~\cite{chatelain2019automatic,chatelain2019outils}, also called
-backends. \pytracer leverages ``fuzzy"~\cite{kiar2020comparing}, a collection of
-software tools compiled with Verificarlo. In particular, fuzzy provides
+backends. \pytracer leverages Fuzzy~\cite{kiar2020comparing}, a collection of
+software tools compiled with Verificarlo. In particular, Fuzzy provides
 MCA-instrumented versions of the Python interpreter as well as the BLAS, LAPACK,
@@
 their respective GitHub repositories. We traced each example five times, having
-activated MCA in the Python interpreter \add{as well as} BLAS, LAPACK, NumPy,
-SciPy, and scikit-learn. \add{Instrumenting only the Python interpreter would
-    lead to only perturb pure Python floating-point operations and thus miss
-    operations in compiled codes (i.e., Cython and shared libraries).} \add{We
-    used MCA in Random Rounding (RR) mode, with 5 repetitions}. We used the default virtual
+activated MCA through Fuzzy in the Python interpreter \add{as well as} BLAS, LAPACK, NumPy,
+SciPy, and scikit-learn. \add{These libraries are written in large parts in a 
+compiled language other than Python (such as C or Cython) and their execution is not 
+perturbed by the sole use of Fuzzy Python. We chose to activate MCA in these libraries 
+to provide an overall picture of numerical uncertainty in the tested examples. 
+Depending on the use-case of interest, one might choose to use MCA only in 
+a subset of these libraries or even just in the Python interpreter.} \add{We
+    used MCA in Random Rounding (RR) mode}. We used the default virtual
 precision in Verificarlo, namely 24 bits for single-precision floating-point
@@
 We used Python-3.8.5, NumPy-1.19.1, SciPy-1.5.4, and scikit-learn-0.23.2.
-
-% \subsection{Results overview}
-
-% Table~\ref{tab:pytracer_results_summary} summarizes \pytracer's outcome on SciPy
-% and scikit-learn examples. Columns \textit{trace} and \textit{parse} report on
-% the tracing and aggregation steps with three possible outcomes: 1) green for
-% success, meaning that the execution ended well and no issues were raised by the
-% application, 2) red for numerical error in the application, meaning that the
-% execution raised a Python error before the end, and 3) orange for errors due to
-% the fuzzy noise injection that are not considered numerical errors, meaning that
-% the execution raised a Python error but due to a perturbation that should not
-% have been introduced (i.e. a floating-point value representing an integer).
-% Overall, the tracing and parsing of SciPy and scikit-learn examples in Random
-% Rounding mode was entirely successful for 32/40 examples and showed an average
-% precision loss of 8 bits. The remaining examples failed due to numerical errors
-% in the libraries, which we discuss hereafter. The instrumentation with Full MCA
-% is more invasive and reduced the number of successful executions to 12/40. Among
-% the 28/40 failed executions, one failed due to an actual numerical error
-% (\texttt{Bayesian Ridge Regression} example) and the other ones failed due to
-% perturbations that should not have been introduced.
-
-% Column \textit{sigbits} in Table~\ref{tab:pytracer_results_summary} summarizes
-% the precision for the main outputs of SciPy and scikit-learn examples. We
-% measured the precision in significant bits on the final primary example output
-% by taking the element-wise mean for non-scalar values and, if the example
-% produces many outputs, the average value among all of them. The numerical
-% quality across all examples varies from 0 to 52, with an average of 44
-% significant bits. For both modes, we note that only two examples failed due to a
-% numerical error (\texttt{face\_recognition} for RR and \texttt{Bayesian Ridge
-%     Regression} for Full MCA).
 
@@
 execution raised a Python error before the end. \remove{, and 3)
-    orange for errors due to the fuzzy noise injection that are
+    orange for errors due to the Fuzzy noise injection that are
     not considered numerical errors, meaning that the execu-
@@
 
-% RR: Crash due to FP32 use. Does FP64 converge? No. Does sgsvd converge? Yes
-
-% MCA: arange issue
-
-% File "/usr/local/lib/python3.8/site-packages/sklearn/datasets/\_lfw.py", line
-%     169, in \_load\_imgs faces[i, ...] = face ValueError: could not broadcast
-%     input array from shape (49,37) into shape (50,37)
-
-% \paragraph{L1 Penalty} This test compares the percentage of zero coefficients
-% for logistic regression by varying the penalty (L1, L2 and Elastic-Net) and
-% regularization (1, 0.1, 0.01) parameters. A large regularization value gives
-% the model more freedom than a small value, which puts more constraints on the
-% model.
-
-% of L1, L2 and Elastic-Net penalty.
-
-% Comparison of the sparsity (percentage of zero coefficients) of solutions when
-% L1, L2 and Elastic-Net penalty are used for different values of C. We can see
-% that large values of C give more freedom to the model. Conversely, smaller
-% values of C constrain the model more. In the L1 penalty case, this leads to
-% sparser solutions. As expected, the Elastic-Net penalty sparsity is between
-% that of L1 and L2. We classify 8x8 images of digits into two classes: 0-4
-% against 5-9. The visualization shows coefficients of the models for varying C.
-
-% RR: ok \\
-% MCA: stable for L1 and L2, not for Len but coef have less zeroes.
-
-% \paragraph{Lasso and Elastic-Net} This test compares the Lasso and Elastic-Net
-% regression models on a corrupted signal.
-
-% Estimates Lasso and Elastic-Net regression models on a manually generated
-% sparse signal corrupted with an additive noise. Estimated coefficients are
-% compared with the ground-truth.
-
-% RR: Good (48 bits on coefs) \\
-% MCA: Good like RR if we exclude one trace that fails due to arange issue
-
-% \paragraph{MNIST classification} This test fits a logistic regression with the
-% SAGA solver with the L1 penalty on the MNIST digits classification task
-% subset.
-
-% Here we fit a multinomial logistic regression with L1 penalty on a subset of
-% the MNIST digits classification task. We use the SAGA algorithm for this
-% purpose: this a solver that is fast when the number of samples is
-% significantly larger than the number of features and is able to finely
-% optimize non-smooth objective functions which is the case with the l1-penalty.
-% Test accuracy reaches > 0.8, while weight vectors remains sparse and therefore
-% more easily interpretable. Note that this accuracy of this l1-penalized linear
-% model is significantly below what can be reached by an l2-penalized linear
-% model or a non-linear multi-layer perceptron model on this dataset.
-
-% RR: Very stable \\
-% MCA: Parse by excluding a trace that failed due to an arange issue
-
-% \paragraph{Multitask Lasso} This test compares the Lasso and MultiTaskLasso
-% regression models on a corrupted signal.
-
-% The multi-task lasso allows to fit multiple regression problems jointly
-% enforcing the selected features to be the same across tasks. This example
-% simulates sequential measurements, each task is a time instant, and the
-% relevant features vary in amplitude over time while being the same. The
-% multi-task lasso imposes that features that are selected at one time point are
-% select for all time point. This makes feature selection by the Lasso more
-% stable.
-
-% RR: Stable (44~53 bits for coef) \\
-% MCA: Stable like RR if we exclude a trace that failed due index issue
-
-% \paragraph{Orthogonal matching} This test uses the Orthogonal Matching Pursuit
-% algorithm for recovering a sparse signal from a noisy measurement encoded with
-% a dictionary.
-
-% RR: Very stable \\
-% MCA: Very stable
-
-% \paragraph{PCA decomposition} This test makes a PCA decomposition on a
-% synthetic dataset. These figures aid in illustrating how a point cloud can be
-% very flat in one direction–which is where PCA comes in to choose a direction
-% that is not flat.
-
-% rr: stable (48 bits on components) \\
-% mca: stable (48 bits on components)
-
-% \paragraph{Robust Linear Regression} This test compares the linear and  RANSAC
-% regression methods on noisy data. In this example we see how to robustly fit a
-% linear model to faulty data using the RANSAC algorithm.
-
-% RR: Very stable \\
-% MCA: Very stable if we exclude two traces that failed due to arange/index
-% issues
-
-% \paragraph{Segmentation Toy} This test uses spectral clustering to separate
-% connected circles in an image.
-
-% In this example, an image with connected circles is generated and spectral
-% clustering is used to separate the circles.
-
-% In these settings, the Spectral clustering approach solves the problem know as
-% ‘normalized graph cuts’: the image is seen as a graph of connected voxels, and
-% the spectral clustering algorithm amounts to choosing graph cuts defining
-% regions while minimizing the ratio of the gradient along the cut, and the
-% volume of the region.
-
-% As the algorithm tries to balance the volume (ie balance the region sizes), if
-% we take circles with different sizes, the segmentation fails.
-
-% In addition, as there is no useful information in the intensity of the image,
-% or its gradient, we choose to perform the spectral clustering on a graph that
-% is only weakly informed by the gradient. This is close to performing a Voronoi
-% partition of the graph.
-
-% In addition, we use the mask of the objects to restrict the graph to the
-% outline of the objects. In this example, we are interested in separating the
-% objects one from the other, and not from the background.
-
-% RR Stable \\
-% MCA: Stable if we exclude three traces that failed due to index issue
-
-% Find the optimal separating hyperplane using an SVC for classes that are
-% unbalanced.
-
-% We first find the separating plane with a plain SVC and then plot (dashed) the
-% separating hyperplane with automatically correction for unbalanced classes.
-
-% RR: stable (48 bits) \\
-% MCA: stable (48 bits)
-
-% \paragraph{Tomography} This test compares the LASSO and Ridge regression
-% models to reconstruct an image from  projections for a dataset acquired from
-% computed tomography.
-
-% This test shows the reconstruction of an image from a set of parallel
-% projections, acquired along different angles. Such a dataset is acquired in
-% computed tomography (CT).
-
-% Without any prior information on the sample, the number of projections
-% required to reconstruct the image is of the order of the linear size l of the
-% image (in pixels). For simplicity we consider here a sparse image, where only
-% pixels on the boundary of objects have a non-zero value. Such data could
-% correspond for example to a cellular material. Note however that most images
-% are sparse in a different basis, such as the Haar wavelets. Only l/7
-% projections are acquired, therefore it is necessary to use prior information
-% available on the sample (its sparsity): this is an example of compressive
-% sensing.
-
-% The tomography projection operation is a linear transformation. In addition to
-% the data-fidelity term corresponding to a linear regression, we penalize the
-% L1 norm of the image to account for its sparsity. The resulting optimization
-% problem is called the Lasso. We use the class Lasso, that uses the coordinate
-% descent algorithm. Importantly, this implementation is more computationally
-% efficient on a sparse matrix, than the projection operator used here.
-
-% The reconstruction with L1 penalization gives a result with zero error (all
-% pixels are successfully labeled with 0 or 1), even if noise was added to the
-% projections. In comparison, an L2 penalization (Ridge) produces a large number
-% of labeling errors for the pixels. Important artifacts are observed on the
-% reconstructed image, contrary to the L1 penalization. Note in particular the
-% circular artifact separating the pixels in the corners, that have contributed
-% to fewer projections than the central disk.
-
-% RR Divergence \\
-% MCA Index issue
-
-% Finally, taking into account the points' weight allows for a better separation
-% \tristan{is this related to numerical stability? If not, you can ommit the
-% comment.}.
-
-% RR Stable (30~48 bits on coef) \\
-% MCA Unstable (0 bits on coef)
-
-% \subsection{PyAFQ}
-
-% PyAFQ is a Python package for Automated Fiber Quantification. It aims to find
-% delineation of the major fiber tracts in individual human brains and quantify
-% the tissue properties within the tracts. PyAFQ \pytracer tracing produces
-% traces of 1TB with an average slowdown $\times 6$ compared to the actual
-% execution. Moreover, \pytracer was able to visualize the aggregated traces,
-% demonstrating its scalability fluently.
-
 \subsection{\pytracer instrumentation limitations}
@@
 (without \pytracer) and the execution time using \pytracer. The \textit{Slowdown
-    RR} \remove{and \textit{Slowdown MCA}} shows the slowdown within the fuzzy environment.
-Without fuzzy, \pytracer introduces an average slowdown of $17\times$ for
+    RR} \remove{and \textit{Slowdown MCA}} shows the slowdown within the Fuzzy environment.
+Without Fuzzy, \pytracer introduces an average slowdown of $17\times$ for
 the examples running less than 8 seconds because \pytracer spends most of its
@@
 initialization time to \textit{Slowdown}. We then obtain an average slowdown of
-$3.5\times$. Finally, the \remove{fuzzy instrumentation} \add{using MCA
-    operations (through fuzzy) instead of the native ones} increases the average
+$3.5\times$. Finally, the \remove{Fuzzy instrumentation} \add{using MCA
+    operations (through Fuzzy) instead of the native ones} increases the average
 slowdown to $37\times$ for RR\remove{and $43\times$ for Full MCA}.
@@
         \pytracer tracing overheads. \textit{Slowdown} represents the slowdown
-        of \pytracer without fuzzy measured as the ratio between the actual
+        of \pytracer without Fuzzy measured as the ratio between the actual
         execution time (without \pytracer) and the execution time using
@@
         The \textit{Slowdown (RR)} \remove{and \textit{Slowdown (MCA)} are} \add{is} the slowdown
-        of \pytracer using the fuzzy environment with \add{the} RR \remove{and Full MCA} mode\remove{s}. The
+        of \pytracer using the Fuzzy environment with \add{the} RR \remove{and Full MCA} mode\remove{s}. The
         \remove{first} \add{last} four examples measure the initialization
@@
 Through our analysis of SciPy and scikit-learn, we demonstrated \pytracer's
-scalability, automaticity, and applicability to a wide range of Python program.
+scalability, automaticity, and applicability to a wide range of Python programs.
 The relatively low instrumentation overhead of 3.5$\times$ on average enables
@@
 automatic and does not require manual intervention from the user. Furthermore,
-\pytracer works on any Python libraries, with any data format supported by
+\pytracer works with any Python libraries, with any data format supported by
 pickle and any numerical noise model.
@@
 \pytracer allows users to pinpoint the root causes of numerical instabilities by
-working at the function level. Numerical stability evaluations are complex since
+working at the level of Python functions. Numerical stability evaluations are complex since
 calculations are strongly interdependent. Function-level instrumentation limits
@@
 instabilities quickly. Working at the function level is thus a suitable
-compromise between analysis conducted at the floating-point operation level and
-user debug prints. Indeed,  fine-grained analyses are costly and hard to
+compromise between analyses conducted at the floating-point operation level and
+user debug prints. Indeed, operation-level analyses are costly and hard to
 interpret as they overwhelm users with information. In contrast, looking at
 intermediate results through print statements is lightweight but not reliable
-since developers may not systematically instrument unstable functions. Finally,
-the SciPy environment wraps many computation kernels written in C, such as BLAS
-or LAPACK. By working at the function level, \pytracer allows the user to
-evaluate the numerical precision of such kernels and their impact on the code
-without getting deep into technical implementation aspects.
+since developers may not systematically instrument unstable functions.
+
+\add{\pytracer can be used with different types of numerical perturbations,
+including random seeds, data noise, or stochastic arithmetic. The
+use of Verificarlo to implement stochastic arithmetic through the Fuzzy
+environment enables to study the impact of numerical perturbations
+introduced in non-Python dependencies while preserving the high-level view
+of Python variables and functions. For instance, the SciPy environment
+wraps many computation kernels written in C, such as BLAS or LAPACK, which
+have a considerable impact on the stability of applications using them.}
+
+\add{
+Enabling Monte-Carlo arithmetic in such non-Python dependencies requires
+their recompilation with Verificarlo, which usually requires human
+intervention. The Fuzzy environment provides pre-instrumented version of
+NumPy, BLAS, LAPACK, GNU libmath, SciPy, and Scikit-learn, which, given the
+prevalence of these libraries in scientific Python codes, should cover a
+large ground of non-Python dependencies encountered in scientific Python programs.
+}
 
@@
 
-\pytracer can also be useful for selecting hyperparameters, as is the case in
+\pytracer might also be useful for selecting hyperparameters, as is the case in
 machine learning. Indeed, it is common for data scientists to explore a range of
@@
 
-The visualization provides a global view of the code and interactions between
+\pytracer's visualization provides a global view of the code and interactions between
 computations. In addition, the Plotly dashboard helps navigate through the code
-easily, without the need for ad-hoc scripts to visualize data. Finally, the
+easily, without the need for ad-hoc scripts to visualize data. The
 dashboard can be extended to support other data formats to visualize. At this
@@
 
-Finally, the wide range of results precision obtained from our experiments
-demonstrate that looking at the numerical variability is essential and that such
+Finally, the wide range of results precision observed in our experiments
+suggests that such
 analyses would benefit from being conducted systematically. We showed that
-well-known scientific libraries are prone to numerical error even though they
-have been well tested for decades. The omnipresence of these libraries in
+well-known scientific libraries are prone to numerical errors even though they
+have been well tested for decades. The prevalence of these libraries in
 scientific codes should thus impel users to integrate numerical analysis in
@@
 
-% \label{sec:detecting-instabilities} \paragraph{Dynamically detecting numerical
-% instabilities} \label{sec:mca}
-% :
-%  \Yohan{Either detail this section with UA/SA or remove it since MCA is
-%  introduced in 'noise injection' subsection. } \tristan{I agree, let's just
-%  remove it, the core of the contribution is on the tracing, not in the
-%  detection of instabilities.}
-
-% % We review here the existing theoretical framework that might be used to
-% detect numerical instabilities. % Our experiments rely on the Monte Carlo
-% Arithmetic (MCA), a stochastic arithmetic allowing % to detect numerical
-% errors by adding random perturbations in the floating-point computations. %
-% However, Pytracer do not rely on any assumption about the perturbation model
-% used and thus leaves the user free to use % an alternative model. As such, we
-% describe two others options that we thought might be beneficial and
-% complementary to MCA: % input data uncertainty analysis and random seed
-% sensitivity.
-
-% % \subsubsection{Stochastic Arithmetic}
-
-% % The Monte Carlo Arithmetic is a variant of so-called stochastic arithmetic,
-% whose purpose is to model round-off errors by a random variable.
-
-% Three main approaches exist to detect numerical instabilities dynamically:
-% stochastic arithmetic, uncertainty or sensitivity
-% analysis~\cite{helton2006survey}, and random seed
-% analysis~\cite{click2011quality}. Stochastic arithmetic leverages randomness
-% to estimate numerical instabilities coming from the use of floating-point
-% representations. The main idea is to treat round-off errors as random
-% variables and characterize them statistically. The first published complete
-% stochastic arithmetic framework was CESTAC~\cite{vignes1993stochastic}. In
-% CESTAC, each floating-point computation is performed multiple times with
-% different rounding modes: round-up or round-down. From these stochastic
-% samples, one can then derive the number of significant digits in the computed
-% result. Discrete Stochastic Arithmetic~\cite{vignes2004discrete} extends
-% CESTAC with comparison operators implemented in the CADNA library. Monte Carlo
-% Arithmetic (MCA)~\cite{parker1997monte} uses the same principle but introduces
-% two differences: (i) a virtual precision parameter, allowing to simulate
-% reduced working precision, and (ii) different perturbation modes to introduce
-% perturbations on function inputs or output. Stochastic arithmetic quantifies
-% numerical error using the number of significant digits $s$ estimated among the
-% sampled values. A common formula to determine this number from MCA samples is
-% presented in~\cite{parker1997monte}. Sohier et al.~\cite{sohier2018confidence}
-% recently provided a generalization of this formula to include confidence
-% intervals.
-
-% % \subsubsection{Uncertainty, sensitivity, and random seed analysis} %
-% \tristan{I'm wondering if we could remove this sub-section, as it doesn't seem
-% to be critical to the understanding of the paper, wdyt?} % Uncertainty
-% analysis (UA) is a method to estimate the output distribution given an input
-% distribution. % Sensitivity analysis (SA) is a variation of UA that measures
-% the local response to a small perturbation~\cite{loucks2017water}. % Several
-% approaches for UA and SA exist, among them differential analysis, response
-% surface methodology, Monte Carlo analysis, and variance decomposition
-% (see~\cite{helton2006survey} for a review). In particular, Monte Carlo
-% analysis is a sampling-based technique that samples inputs space to estimate
-% output response. Monte Carlo analysis shares similarities with Monte Carlo
-% Arithmetic. For instance, the PRECISE framework~\cite{chaitin1996lectures}
-% shares with MCA the idea of varying virtual precision to estimate output
-% sensitivity.
-
-% % Furthermore, the quality of a Random Number Generator is a crucial
-% characteristic when dealing with stochastic model and differ from cryptography
-% requirements. A good RNG provides a tradeoff between performance, period,
-% correlation, or uniformity~\cite{james2020review} for numerical simulation.  
-% On the other hand, poor-quality RNGs may have a substantial impact on
-% results~\cite{click2011quality}. First, measuring variation induced by seed is
-% a good indicator of program stability that we can compare against variability
-% induced by floating-point arithmetic.
-
-% \paragraph{Visualization of numerical data} \tristan{now that it's here, I'm
-% not sure if this section really adds to the paper. It could also go.}
-
-% Floating-point values approximate real number in the computer arithmetic but
-% data manipulated by scientific applications include a large variety of
-% mathematical objects beyond scalar values. Indeed, scientific visualization
-% \gkmod{}{Note: You kind of jump right in to this section. Visualization of
-% what in particular? Why do we want (need?) to visualize this sort of data?}
-% covers a wide range of numerical simulation domains, from general-purpose
-% numerical visualization with tools such as VTK~\cite{schroeder2000visualizing}
-% to topological data analysis~\cite{tierny2018topological}, including
-% matrix~\cite{wu2008matrix} or tensor~\cite{kindlmann2006diffusion}
-% visualization. To be able to visualize those objects is crucial for the
-% practitioner as information about the structure of the object may be as
-% important as the basic elements that constitute it (i.e. vectors or matrices).
-% Despite the large number of existing tools to identify numerically unstable
-% sections of source code, few allow the user to have a global view of the
-% numerical precision of their computations or to compare several executions of
-% the same program under various perturbations.
-
-% Veritracer~\cite{chatelain2018veritracer} was the first tool to propose an
-% embedded visualizer of numerical stability over the execution of C, C++, and
-% Fortran code. Veritracer extends Verificarlo~\cite{verificarlo} with
-% contextual information about traced variables, which allows the user to
-% identify instabilities quickly. However, Veritracer neither offers a dynamic
-% interface nor includes information about high-level structures such as
-% \texttt{struct} or \texttt{array}. FPAvizual~\cite{gu2014fpavisual} visualizes
-% the effects of floating-point arithmetic but only for educational purposes and
-% so does not target computational intensive applications\gkmod{}{Q: What does
-% this mean?}. Anteater~\cite{faust2019anteater} proposes a visualizer for
-% Python code, but as mentioned previously, it only deals with native Python
-% types, and the user needs to select variables to trace manually. Anteater
-% provides an insightful reflection around visual debugging beyond
-% floating-point analysis, which has inspired the design of \pytracer's
-% visualization interface.
-
-% Through our analysis of SciPy and Scikit-learn, we demonstrated \pytracer's
-% scalability, automaticity, and applicability to any Python program. The
-% relatively low instrumentation overhead of $3.5\times$ on average enables the
-% analysis of real applications. \pytracer's instrumentation is fully automatic
-% and does not require manual intervention from the user. \pytracer works on any
-% Python libraries, with any data format supported by Pickle and any numerical
-% noise model.
-
-% \pytracer is the first tool to enable a systematic numerical analysis of
-% Python codes. Existing tools focus on traditional languages of the HPC
-% community such as C, C++, and FORTRAN. However, Python's high-level
-% abstraction allows for quickly developing applications while maintaining high
-% performance thanks to specialized libraries such as NumPy. Therefore,
-% \pytracer meets the numerical analysis needs of an ever-increasing number of
-% applications.
-
-% Furthermore, \pytracer allows users to pinpoint numerical instabilities root
-% causes precisely by working at the function level. Indeed, evaluating the
-% numerical stability is complex since calculations are strongly correlated
-% between them. The instrumentation at the function level limits the size of the
-% traces since only inputs and outputs of a function are dumped. It moreover
-% decreases the overhead of the instrumentation and helps the user to identify
-% instabilities quickly. Working at function level is thus a suitable compromise
-% between (1) analyzing at the floating-point operation level and (2) user debug
-% prints. (1) Indeed, the fine-grained analysis is costly and hard to analyze
-% due to the large amount of computations evolved in HPC codes. It overwhelms
-% the user with too much information, making analysis more difficult but can be
-% interesting at the final step of the understanding. (2) Looking at
-% intermediate results through print statements focuses on valuable information
-% (like residuals or norms) but may miss numerically unstable functions
-% unsuspected by the developer. Finally, the SciPy environment wraps a lot of
-% computation kernels written in C, like BLAS or LAPACK. By working at function
-% level, \pytracer allows the user to evaluate the numerical precision of such
-% kernels and their impact on the code without getting deep into technical
-% implementation aspects.
-
-% Python is a popular language to prototype proof-of-concept. Integrating
-% \pytracer at early stages of the development cycle allows identifying
-% numerical instabilities to write code of better quality. \pytracer's
-% automaticity facilitates the usage and enables its integration in unit
-% testing. It can be for example used in a non-regression test to ensure that
-% the numerical quality of a calculation is not degraded by updates. Moreover,
-% the Plotly dashboard offers a quick visualization to analyze more finely the
-% potential issues.
-
-% \pytracer can also be useful to select the hyperparameters of a code, as it is
-% the case in machine learning. Indeed, we find many cases in the literature
-% where users explore a range of hyperparameters to select the ones giving the
-% best scores. With \pytracer, the user has a practical way to quantify the
-% numerical quality and to understand why hyperparameters lead to unstable
-% outputs, instead of tweaking hyperparameters to make solvers converge,
-
-% The visualization permits a global view of the code and to understand
-% interactions between computations. The Plotly dashboard help to easily
-% navigate through the code. It moreover removes the need for ad-hoc scripts to
-% visualize data. Finally, the dashboard can be extended to support other data
-% format to visualize. \pytracer currently supports n-dimensional NumPy arrays
-% as well as native Python data.
-
-% As we showed in Section~\ref{sec:impact_mca_modes}, using Full MCA mode leads
-% to runtime errors that have a considerable impact on the proper functioning of
-% the execution. This is unfortunate since these errors do not reflect actual
-% numerical errors but errors related to perturbations that should not occur.
-% Conversely, RR mode is far more conservative since it preserves exact
-% operations and is easier to use even though it does not simulate all
-% perturbations. From our experiments, we do not recommend the Full MCA mode for
-% now and more researches are needed to help fixing issues we encountered.
-
-% Fixing this issue would enable the study of catastrophic cancellations, which
-% are common sources of numerical errors. In addition to the runtime errors it
-% raises, mismatching shapes is also a problem when aggregating traces as
-% \pytracer will not compute statistics for a set of arrays with different
-% shapes \tristan{So do you conclude that Full MCA is not usable while RR is? If
-% so, you should recommend to use Pytracer with RR only.} \tristan{are you still
-% talking about Full MCA here? if not, make another paragraph. If so, make it
-% clearer.}. Two solutions exist to overcome this issue: the first is not to
-% instrument the \texttt{PyArray\_Arange} function with MCA. The advantage is
-% that it is easy to set up since it requires one extra line in the exclusion
-% file. However, the same kind of problem may appear somewhere else because, as
-% we have seen, the evolved operations are elementary. Therefore, the chances
-% that developers reproduce the same pattern are very probable. Therefore, the
-% second solution is to ensure that the Full MCA mode preserves the exact
-% operations. This solution has the advantage of not worrying about which
-% functions should be instrumented or not with MCA, but it is hard to achieve it
-% in practice. Indeed, we rely on the MCA implementation provided by Verificarlo
-% that uses an internal precision to add the random perturbation that is higher
-% than the working precision for applying the random noise. Verificarlo then
-% rounds the result to the working precision before returning it, so any
-% residual noise lower than the working precision is lost. Keeping track of that
-% noise would require recording each intermediate computation in a shadow memory
-% or keeping a tag about their exactness. This option would require more extra
-% works than the first one but would ensure more consistent results. \tristan{I
-% find this paragraph too verbose, you should contract it to a few key
-% sentences.}
-
-% \tristan{The following paragraphs are future work, not discussion. I'd remove
-% them and flesh out the discussion from the ideas mentioned in the current 3rd
-% paragraph}
-
-% Also, we would like to extend the post-process analysis to aggregate traces
-% where the execution flow path diverges. Therefore, a posteriori reconstruction
-% is challenging as one must precisely identify the flow path taken and find
-% synchronization points to pursue the analysis. We retrieve, for example, this
-% divergence behavior in two general classes of numerical schemes: iterative
-% methods and optimization processes. One solution is to integrate methods used
-% in code coverage analysis to keep track of flow paths taken and the
-% backtraces. However, this would increase the complexity of the postprocess
-% analysis as well as an extra slowdown factor. However, by coupling the Gantt
-% chart with static analysis, \pytracer would catch some divergence patterns
-% occurring within a function. Indeed, by instrumenting at the function level,
-% \pytracer views the function's callees (i.e., the functions called within a
-% function) and thus should partially detect flow divergences.
-
-% By design principle, \pytracer is flexible on the noise model used, although
-% we only tested it with the MCA model in our experiments. Nevertheless, we
-% would like to compare different models against MCA in future works to see the
-% resulting differences. Furthermore, we would like to test \pytracer on
-% parallel codes.
-
-% Finally, we would extend \pytracer to instrument elementary arithmetic
-% operations which can be helpful to more profound analyses. We nevertheless
-% believe that instrumentation at the function level presents two advantages: it
-% first limits the size of the traces since only inputs and outputs of a
-% function are saved instead of a full report which, on the one hand, decreases
-% the overhead of the instrumentation and, on the other hand, help the user to
-% identify instabilities quickly. Indeed, full reporting can overwhelm the user
-% with too much information, making analysis more difficult at first. Second,
-% the analysis at fine granularity is interesting at the final step of the
-% understanding. Such an analysis would require a different instrumentation
-% approach by, for example, working at the Abstract Syntax Tree (AST) level
-% since it is trivial to get it in Python. Moreover, working at the AST level
-% allows doing dependency analysis. Another extension would be to extract and
-% replay a function, in the same vein as the CERE tool does but for Python, and
-% to use an AST instrumentation to analyze the numerical quality of elementary
-% operations step by step within the fuzzy environment.
-
-% \pytracer is a tool for visualizing the numerical quality of function
-% inputs/outputs over time. It generates numerical traces that are aggregated in
-% postprocessing to measure numerical discrepancies between executions.
-% \pytracer does not assume the noise model used to estimate uncertainties but
-% has been tested with the MCA through the fuzzy ecosystem on two broadly used
-% scientific libraries for Python with partial success.
-
-% We demonstrated the Pytracer's capabilities to analyze intensively used Python
-% libraries such as NumPy or Scikit-learn, such as 
-% 1) Scalability. The low instrumentation overhead of 3.5x enables analysis of
-%    real applications and permits having a global representation of the
-%    numerical quality of an application. 
-% 2) Automaticity. Pytracer instrumentation is fully automatic and does not
-%    require manual intervention from the user, allowing the instrumentation of
-%    the NumPy, SciPy and Scikit-learn libraries. // that cumulate 5600 and 2043
-%    pure Python functions and classes. 
-% 3) Agnosticity. Pytracer works on any python libraries, with any data format
-%    supported by pickle, and any numerical noise model flavor.
-
-% Pytracer is the first tool to bring numerical analysis of Python codes
-% available to everyone. Indeed, existing tools developed in the last years
-% focused on traditional HPC languages community such as C,C++, and FORTRAN.
-% However, the Python high-level abstraction allows you to quickly develop
-% applications while maintaining high performance with the help of specialized
-% libraries like NumPy. Therefore, it is quite natural to see more fields
-% systematically using Python, as is the case in neuroimaging. Thus, Pytracer
-% meets the numerical analysis needs of an ever increasing number of
-% applications writing in Python.
-
-% By working at function level, Pytracer allows users to precisely pinpoint
-% numerical instabilities root causes. Furthermore, the automaticity facilitates
-% the usage and its integration in unit testing. Hence, instead of tweaking
-% hyperparameters to make solvers converging, the user has a practical way with
-% Pytracer to quantify the numerical quality of its computations.
-
-% As we showed in section~\ref{sec:impact_mca_modes}, using the Full MCA mode
-% leads to runtime errors that have a considerable impact on the proper
-% functioning of the execution, which is unfortunate since these errors do not
-% reflect actual numerical errors but errors related to perturbations that
-% should not occur. Fixing this misbehavior would greatly help use Full MCA mode
-% since this mode allows simulating catastrophic cancellations, which are
-% familiar sources of numerical errors. By preserving exact operations, RR mode
-% is far more conservative and so easy to use even though it does not simulate
-% all perturbations that might be encountered.
-
-% Also, using a post-process analysis to aggregate traces, \pytracer falls in
-% the same pitfalls as veritracer and is limited to aggregate traces where the
-% execution flow path extremely diverges. Therefore, a posteriori reconstruction
-% is challenging as one must precisely identify the flow path taken and find
-% synchronization points to pursue the analysis. We retrieve, for example, this
-% divergence behavior in two general classes of numerical schemes: iterative
-% methods and optimization processes. One solution to overcome this issue is to
-% integrate methods used in code coverage analysis to keep track of flow paths
-% taken and the backtraces. However, this would increase the complexity of the
-% postprocess analysis as well as an extra slowdown factor. However, by coupling
-% the Gantt chart with static analysis, \pytracer would catch some divergence
-% patterns occurring within a function. Indeed, by instrumenting at the function
-% level, \pytracer views the function's callees (i.e., the functions called
-% within a function) and thus should partially detect flow divergences.
-
-% By design principle, \pytracer is flexible on the noise model used, although
-% we only tested it with the MCA model in our experiments. Nevertheless, we
-% would like to compare different models against MCA in future works to see the
-% resulting differences. In particular, although \pytracer only works on a
-% sequential application for the moment, it can be used to analyze parallel
-% sections internal to a function. The only restriction is that the section does
-% not call other functions traced by \pytracer; we would fall into the previous
-% issue of divergence if it would not be the case. Since \pytracer only cares
-% about inputs and outputs of a function, the order of internal operations is
-% transparent for it and thus should be able to handle those cases.
-
-% Finally, \pytracer does not instrument elementary arithmetic operations, and
-%it can be a barrier to more profound analysis. Such an analysis would require a
-%different instrumentation approach by, for example, working at the Abstract
-%Syntax Tree (AST) level since it is trivial to get it in Python. An ideal way
-%to do that would be to extract and replay a function, in the same vein as the
-%CERE~\cite{castro2015cere} tool does but for Python, and use an AST
-%instrumentation to analyze the numerical quality of elementary operations step
-%by step within the fuzzy environment. Lastly, AST analysis can serve as a basis
-%for finding relationships between variables, valuable information for the user.
-
-% In addition to the runtime errors it raises, mismatching shapes is also a
-% problem when aggregating traces as PyTracer will not compute statistics for a
-% set of arrays with different shapes. Two solutions exist to overcome this
-% issue: the first is not to instrument the \texttt{PyArray\_Arange} function
-% with MCA. The advantage is that it is easy to set up since it requires one
-% extra line in the exclusion file. However, the same kind of problem may appear
-% somewhere else because, as we have seen, the operations being evolved are
-% elementary. Therefore, the chances that developers reproduce the same pattern
-% are very probable. The second solution is to ensure that the Full MCA mode
-% preserves the exact operations. This solution has the advantage of not
-% worrying about which functions should be instrumented or not with MCA, but it
-% is hard to achieve it in practice. Indeed, we rely on the MCA implementation
-% provided by Verificarlo that uses an internal precision to add the random
-% perturbation that is higher than the working precision for applying the random
-% noise. Verificarlo then rounds the result to the working precision before
-% returning it, so any residual noise lower than the working precision is lost.
-% Keeping track of that noise would require recording each intermediate
-% computation in a shadow memory or keeping a tag about their exactness.
-% \Yohan{This idea emerged by discussing with Verificarlo's team. I must find a
-% way to express that and not give the impression that we discovered or suggest
-% it.} This option would require more extra works than the first one but would
-% ensure more consistent results.
-
 \section{Conclusion}
@@
 task that requires substantial expertise. Automatic tools to help users
-understand the behavior of their code are therefore crucial. In this
-perspective, \pytracer is the first tool to offer a complete framework for
+understand the behavior of their code are therefore crucial. \pytracer is the first tool to offer a complete framework for
 analyzing and visualizing the numerical stability of Python codes. It works by
-automatically instrumenting Python libraries to produce numerical traces
-visualized through an interactive Plotly Dash server. \pytracer does not require
-manual code modification, and we tested it with major scientific libraries such
-as NumPy, SciPy, and Scikit-learn. Our results show that \pytracer is scalable,
+automatically instrumenting Python programs to produce traces \add{of numerically-perturbed 
+executions and}
+visualize these traces through an interactive Plotly Dash server. \pytracer does not require
+manual code modification. We tested it with \add{Python programs involving} major scientific libraries such
+as NumPy, SciPy, and Scikit-learn. \pytracer enabled the systematic evaluation of 40 examples from the
+SciPy and scikit-learn libraries. Our results show that \pytracer is scalable,
 with an average instrumentation slowdown of $3.5\times$. Moreover, \pytracer's
-visualization interface remains responsive even with traces of up to 1TB. In our
-experiments, \pytracer enabled the systematic evaluation of 40 examples from the
-SciPy and scikit-learn libraries.
-
-In future work, we plan to extend the post-processing analysis to aggregate
+visualization interface remains responsive even with traces of up to 1TB.
+
+In the future, we plan to extend the post-processing analysis to aggregate
 traces when the execution flow path diverges by leveraging techniques used in
 code coverage analysis. Moreover, we would like to extend \pytracer to
-instrument elementary arithmetic operations which can be helpful to more
-profound analyses. Finally, although \pytracer supports multiple noise models,
-we only tested it with Monte Carlo Arithmetic. Therefore, we would like to
-compare different models against MCA. \pytracer is available at
+instrument elementary arithmetic operations. \remove{Finally, although \pytracer supports multiple noise models,
+we only tested it with Monte-Carlo arithmetic. Therefore, we would like to
+compare different models against MCA.} \pytracer is available at
 \href{https://github.com/big-data-lab-team/pytracer}{github://big-data-lab-team/pytracer}

### 2022-05-16 IEEEtran/paper.tex
More edits

@@
 \DeclareRobustCommand{\add}[1]{\textcolor{ao(english)}{#1}}%\sethlcolor{lightgreen}\hl{#1}}
-\DeclareRobustCommand{\remove}[1]{\textcolor{lightred}{\sout{#1}}}
+\DeclareRobustCommand{\remove}[1]{}
 \DeclareRobustCommand{\addCite}[1]{\textcolor{lightgreen}{\mbox{#1}}}
@@
 
+\add{
+The remainder of this section assumes some knowledge of Python concepts
+such as classes, functions, modules, decorators, callables, and iterators.
+We refer to~\cite{beazley2013python} for a detailed presentation of these
+concepts.
+}
+
 \begin{figure*}
@@
 this technique does not apply to callable class instances, i.e., class instances
-that have a \texttt{\_\_call\_\_} attribute and are not of type
+\add{that can be called directly with the () operator, because they,} are not of type
 \texttt{FunctionType}. Indeed, applying the wrapper technique would 1) modify
@@
         \emph{trace}: outcome of \pytracer tracing, \emph{parse}: outcome of
-        \pytracer trace parsing and aggregation, \emph{result}: precision for
-        main outputs in significant bits. \valid: successful run, \remove{\warn: error
-            from invalid noise injection,} \cross: numerical error or divergent
-        traces. \textit{nan} stands for (\texttt{Not-A-Number}). Example names
+        \pytracer trace parsing and aggregation, \emph{result}: \add{result} precision
+         in number of significant bits. \valid: successful run, \remove{\warn: error
+            from invalid noise injection,} \cross: numerical error \add{(tracing)} or 
+            \add{different control flow paths (parsing).} \textit{nan} stands for (\texttt{Not-A-Number}). Example names
         are linked to their source code.}
@@
 
-Table~\ref{tab:pytracer_results_summary} summarizes \pytracer's outcome on SciPy
-and scikit-learn examples. Columns \textit{trace} and \textit{parse} report on
-the tracing and aggregation steps with two possible outcomes: 1) green for
-success, meaning that the execution ended well and no issues were raised by the
-application, and 2) red for numerical error in the application, meaning that the
-execution raised a Python error before the end. \remove{, and 3)
+Table~\ref{tab:pytracer_results_summary} summarizes \pytracer's outcome on
+SciPy and scikit-learn examples. Columns \textit{trace} and \textit{parse}
+report on the tracing and aggregation steps with two possible outcomes:
+\add{green \valid\xspace for success and red \cross\xspace for error. Tracing errors 
+occur in the application as a result of 
+numerical perturbations, whereas parsing errors occur in \pytracer when traces result from different 
+control flow paths. 
+} \remove{, and 3)
     orange for errors due to the Fuzzy noise injection that are
@@
 Column \textit{sigbits} in Table~\ref{tab:pytracer_results_summary} summarizes
-the precision for the main outputs of SciPy and scikit-learn examples. We
-measured the precision in significant bits on the final primary example output
+the \add{result} precision for the main outputs of SciPy and scikit-learn examples. We
+measured the \add{result} precision in significant bits on the final primary example output
 by taking the element-wise mean for non-scalar values and, if the example
-produces many outputs, the average value among them. The numerical
+produces many outputs, the average value among them. \add{Significant bits are computed on the final program output 
+and can therefore be computed even when parsing fails.} \add{We use the term ``result precision"
+to denote a statistical variability measured in number of significant bits, in 
+contrast with the other meanings of the word precision used in expressions
+``virtual precision" or ``single/double precision'' in this paper.} The numerical
 quality across all examples varied from 0 to 52, with an average of 44
@@
     complex values encoded in double precision. PyTracer allows visualizing the
-    numerical precision of real (blue points) and imaginary (orange points) parts.}
+    \add{result} precision of real (blue points) and imaginary (orange points) parts.}
 \add{The} top row in Figures~\ref{fig:fft1D_inputs} and~\ref{fig:fft1D_outputs}
-show the input mean value while the bottom row shows the standard deviation. The
+show the input mean value while the bottom row shows the standard deviation. \add{Even though we 
+used Random Rounding (RR), function inputs are perturbed since they result from multiple intermediate 
+computations perturbed with RR.} The
 points with low magnitude in Figure~\ref{fig:fft1D_inputs} correspond to inputs
 near 0 when the input of $\sin$ or $\exp$ is close to $k\pi$, $k \in
-    \mathbb{Z}$. Indeed, since MCA introduces a slight noise, the result is not
+    \mathbb{Z}$. Indeed, since MCA introduces noise, the result is not
 exactly 0. We can see in Figure~\ref{fig:fft1D_inputs} that the maximal noise
@@
         [-1,1]\times[-1,1]$. The result is a 2D-array that is natively supported by
-    PyTracer. We observe a significant loss of precision in some regions, which follows
+    PyTracer. We observe a significant loss of \add{result} precision in some regions, which follows
     an interesting pattern that could be further investigated.}
@@
 Replacing \texttt{gesdd} for \texttt{gesvd} solved the SVD convergence issue.
-\pytracer allows to quickly visualize the new precision of the result.
-Figure~\ref{fig:face_recognition_svd} shows the precision of the eigenvalues
-computed displayed in decreasing order with \texttt{gesvd} \add{in single precision}, 
-which varies between 15 and 20
+\pytracer allows to quickly visualize the new \add{result} precision.
+Figure~\ref{fig:face_recognition_svd} shows the \add{result} precision of the eigenvalues
+computed with \texttt{gesvd} \add{in single precision}. \add{The result precision}
+varies between 15 and 20
 significant bits out of the 24 available in single precision. The classifier
@@
 execution for all MCA samples. \add{We can note that even with the \texttt{gesvd} method,
-    the precision of the singular values and eigenvectors is not uniform. 
-    Indeed, we can see that the precision of the lowest singular values and eigenvectors decreases 
+    the \add{result} precision of the singular values and eigenvectors is not uniform. 
+    Indeed, we can see that the \add{result} precision of the lowest singular values and eigenvectors decreases 
     until reaching 0 significant bits.}
@@
     \texttt{NaN} due to numerical errors in the SVD, although the remaining
-    singular values exhibit high numerical precision (between 44 and 50 bits).
+    singular values exhibit high \add{result} precision (between 44 and 50 bits).
     Surprinsingly, this \texttt{NaN} value does not raise an exception and is silently
@@
     the \texttt{gesvd} instead of the \texttt{gesdd} method removes the \texttt{NaN} value
-    although the last singular values stills have a low precision (below 0).
+    although the last singular values stills have a low \add{result} precision (below 0).
     Following Equation}~\ref{eq:sig-digits}, \add{a number of significant digits below 0 means that the
@@
     the \texttt{NaN} value disapears 
-    (Fig.}~\ref{fig:OLS_svd_fixed}\add{), resulting in a precision of
+    (Fig.}~\ref{fig:OLS_svd_fixed}\add{), resulting in a \add{result} precision of
     42 bits in average in the coefficients. We can see that having
@@
     unified view of all traces allows the user to quickly navigate through the
-    numerical precision of different variables.}
+    \add{result} precision of different variables.}
 % The Pytracer findings can therefore be extended to many application domains. %
@@
         and~\ref{fig:randomized_svd_V} show respectively the values $U$,
-        $\Sigma$ and $V$. Numerical precision is lower for smaller singular
+        $\Sigma$ and $V$. \add{Result} precision is lower for smaller singular
         values and this loss of precision translates to singular vectors. It
@@
     \end{subfigure}
-    \caption{\add{Numerical precision of the singular values of the SVD from the
+    \caption{\add{Result} precision of the singular values of the SVD from the
             Bayesian Ridge model fitting (left) and from the Ordinary Least Square model
@@
             Switching from Divide \& Conquer (\texttt{gesdd}) to QR (\texttt{gesvd}) factorization improves numerical precision.
-            PyTracer helps visualizing improvements.}}
+            PyTracer helps visualizing improvements.}
 \end{figure}
@@
 initialization time to \textit{Slowdown}. We then obtain an average slowdown of
-$3.5\times$. Finally, the \remove{Fuzzy instrumentation} \add{using MCA
-    operations (through Fuzzy) instead of the native ones} increases the average
-slowdown to $37\times$ for RR\remove{and $43\times$ for Full MCA}.
+$3.5\times$. Finally, \remove{the Fuzzy instrumentation} \add{using MCA
+    operations (through Fuzzy) instead of the native ones} increased the average
+slowdown to $37\times$\remove{for RR and $43\times$ for Full MCA}.
 
@@
 
-Finally, the wide range of results precision observed in our experiments
+Finally, the wide range of result precision observed in our experiments
 suggests that such
@@
 In the future, we plan to extend the post-processing analysis to aggregate
-traces when the execution flow path diverges by leveraging techniques used in
+traces \add{obtained with different control flow paths,} by leveraging techniques used in
 code coverage analysis. Moreover, we would like to extend \pytracer to

### 2022-05-16 IEEEtran/paper.tex
More edits

@@
 Pytracer does not instrument the class and returns a warning. 
+\add{
+    This limitation is expected to have a minor impact since non-writable
+    classes are usually called from pure Python classes that can be
+    instrumented. PyTracer reports information about the stability of
+    non-writable classes through the instrumentation of the pure Python
+    classes that use them.
+}
 
@@
 iterators into explicit containers, however, this would increase the memory
-footprint significantly. \pytracer, therefore, does not instrument non-builtin
+footprint significantly. \pytracer, therefore, does not instrument
 iterators.
+
+\add{
+We do not expect this limitation to have a critical impact on the
+applicability of \pytracer. 
+In general, iterators involve simple computations that are unlikely to be
+unstable. In particular, we encountered only a few iterators in our
+experiments and none of them involved floating point values. Should
+instabilities occur in iterators, \pytracer would detect them through the
+inputs of the functions consuming these iterators. 
+}
 
@@
 This operation critically relies on the ordering of call input and output
-objects in the traces. Therefore, it assumes that the application is
+objects in the traces. It assumes that the application is
 single-threaded and that the control flow does not depend on a random state.
@@
     although the last singular values stills have a low \add{result} precision (below 0).
-    Following Equation}~\ref{eq:sig-digits}, \add{a number of significant digits below 0 means that the
+    According to Equation}~\ref{eq:sig-digits}, \add{a number of significant bits less than 0 means that the
     variability ($\sigma$) is higher than the average value ($\mu$)}.
@@
 \end{figure}
-
-\subsection{\pytracer instrumentation limitations}
-
-\add{
-    The limitations of the PyTracer's instrumentation have little impact in practice
-    since we have encountered few classes having non-writeable attributes in practice.
-    Moreover, those classes are generally used in higher-level classes written in
-    pure Python. For instance, the SGD class that implements the Stochastic Gradient
-    Descent in scikit-learn takes a loss function as a parameter. Loss functions are
-    implemented in Cython in scikit-learn and Pytracer is not able to instrument
-    them. However, Pytracer can dump the instance of LossFunction if they are used
-    by the SGD class as arguments, which is a frequently observed pattern in
-    Scikit-learn for instance. So one still has an estimation of variability for the
-    attributes of the class. Finally, one can use Veritracer to trace the methods of
-    those Cython classes for an in-depth analysis since it is the C language
-    underhood. We have encountered few iterators and none of them involved floating
-    point values so we were able to safely ignore them. 
-}
 
@@
 In the future, we plan to extend the post-processing analysis to aggregate
-traces \add{obtained with different control flow paths,} by leveraging techniques used in
-code coverage analysis. Moreover, we would like to extend \pytracer to
-instrument elementary arithmetic operations. \remove{Finally, although \pytracer supports multiple noise models,
-we only tested it with Monte-Carlo arithmetic. Therefore, we would like to
-compare different models against MCA.} \pytracer is available at
+traces \add{obtained with different control flow paths,} by leveraging
+techniques used in code coverage analysis. \add{This would also enable a larger support 
+of multi-threaded applications.} Moreover, we would like to
+extend \pytracer to instrument elementary arithmetic operations \add{(+,-,*,/), to allow for more detailed analyses}.
+\remove{Finally, although \pytracer supports multiple noise models, we only
+tested it with Monte-Carlo arithmetic. Therefore, we would like to compare
+different models against MCA.} \pytracer is available at
 \href{https://github.com/big-data-lab-team/pytracer}{github://big-data-lab-team/pytracer}

### 2022-05-16 IEEEtran/paper.tex
Missing sigdigits result in Table 1 for L1 Penalty
Edits and comments

@@
         in a Plotly dashboard. We designed \pytracer to be agnostic to numerical
-        noise model , allowing for tool evaluation through Monte-Carlo
+        noise model, allowing for \add{numerical profiling} through Monte-Carlo
         Arithmetic, random rounding, random data perturbation, or structured
@@
 valuable in contrast to theoretical approaches based on condition numbers or
-backward error analysis~\addCite{\cite{higham2002accuracy}}, which require
+backward error analysis~\cite{higham2002accuracy}, which require
 detailed modeling of the program and its numerical implementation. Similarly,
-static code analysis techniques~\addCite{\cite{goubault2006static}} hardly scale
+static code analysis techniques~\cite{goubault2006static} hardly scale
 to large code bases, particularly in dynamically-typed languages such as Python.
@@
 evaluations. \add{PyTracer addresses (a) by relying on
-Fuzzy~\addCite{\cite{kiar2020comparing}}, a pre-existing collection of scientific
+Fuzzy~\cite{kiar2020comparing}, an existing collection of scientific
 computing libraries instrumented with Monte-Carlo arithmetic through the
@@
 interactive Plotly dashboard. \mbox{\pytracer} is available at
-\mbox{\href{https://github.com/big-data-lab-team/pytracer.git}{github.com/big-data-lab-team/pytracer.git}}
+\mbox{\href{https://github.com/big-data-lab-team/pytracer}{github.com/big-data-lab-team/pytracer}}
 under MIT License.} \remove{\mbox{\pytracer} addresses these requirements
@@
 
-This manuscript presents the design of \pytracer and demonstrates its potential
+This manuscript presents the design of \pytracer and \add{highlights} its potential
 in various use cases. Through stability evaluations of the SciPy and
@@
 Python methods. However, some attributes are not writable. In this case,
-\pytracer \remove{preservers} \add{preserves} the original attributes and warns
+\pytracer \add{preserves} the original attributes and warns
 the user. The user can also restrict the list of traced attributes through an
@@
 this technique does not apply to callable class instances, i.e., class instances
-\add{that can be called directly with the () operator, because they,} are not of type
+\add{that can be called directly with the () operator, because they} are not of type
 \texttt{FunctionType}. Indeed, applying the wrapper technique would 1) modify
@@
 \add{
-    This limitation is expected to have a minor impact since non-writable
+    This limitation is expected to have a minor impact in practice since non-writable
     classes are usually called from pure Python classes that can be
-    instrumented. PyTracer reports information about the stability of
+    instrumented. Therefore, \pytracer reports information about the stability of
     non-writable classes through the instrumentation of the pure Python
@@
 Three  main  approaches  exist  to  detect  numerical  instabilities:
-stochastic  arithmetic,  uncertainty  or  sensitivity analysis [23], and random
-seed analysis [11].  \add{PyTracer is agnostic to the noise model used and can therefore
+stochastic  arithmetic,  uncertainty  or  sensitivity analysis \TG{[23] fix ref}, and random
+seed analysis \TG{fix ref [11]}.  \add{PyTracer is agnostic to the noise model used and can therefore
 be used for all these methods}.  For our use cases, we focus on stochastic
@@
 a subset of these libraries or even just in the Python interpreter.} \add{We
-    used MCA in Random Rounding (RR) mode}. We used the default virtual
+    used MCA in Random Rounding (RR) mode, with} the default virtual
 precision in Verificarlo, namely 24 bits for single-precision floating-point
@@
 occur in the application as a result of 
-numerical perturbations, whereas parsing errors occur in \pytracer when traces result from different 
-control flow paths. 
-} \remove{, and 3)
-    orange for errors due to the Fuzzy noise injection that are
-    not considered numerical errors, meaning that the execu-
-    tion raised a Python error but due to a perturbation that
-    should not have been introduced (i.e. a floating-point value
-    representing an integer).}
+numerical perturbations, whereas parsing errors occur when traces result from different 
+control flow paths.} 
 Overall, the tracing and parsing of SciPy and scikit-learn examples in Random
 Rounding mode was entirely successful for 32/40 examples\remove{ and showed an average
-    precision loss of 8 bits}. The remaining examples failed due to numerical errors
-in the libraries, which we discuss hereafter. 
+    precision loss of 8 bits}. 
 \remove{The instrumentation with Full MCA is
@@
 by taking the element-wise mean for non-scalar values and, if the example
-produces many outputs, the average value among them. \add{Significant bits are computed on the final program output 
-and can therefore be computed even when parsing fails.} \add{We use the term ``result precision"
-to denote a statistical variability measured in number of significant bits, in 
+produce\add{d multiple} outputs, the average value among them. \add{Significant bits were computed on the final program output 
+and could therefore be computed even when parsing failed.} \add{We use the term ``result precision"
+to denote the statistical variability measured in number of significant bits, in 
 contrast with the other meanings of the word precision used in expressions
@@
 
-\noindent \remove{\textbf{3.2 Effect of MCA modes}}
-
-\remove{
-    Random Rounding perturbs only the result of a floating-point operation while
-    Full MCA perturbs both the inputs and the result. Therefore, Full MCA may
-    trigger catastrophic cancellations while Random Rounding only introduces
-    round-off errors which generally have a lesser impact. Moreover, Random Rounding
-    preserves exact operations --- operations where the result can be exactly
-    represented at the virtual precision --- while Full MCA does not.}
-
-\remove{\pytracer can only aggregate traces obtained from the same control flow path. In
-    particular, program branches triggered by an unstable floating-point comparison
-    lead to different control flows and result in parsing errors. For example,
-    comparing a residual error or the distance between two points to a strict
-    threshold in an iterative scheme generally results in unstable branches. Full
-    MCA even perturbs exact values such as integers represented with floating-point
-    values, leading to many execution failures. For instance, the \texttt{fft1}
-    example from SciPy raised an \texttt{ValueError: operands could not be broadcast
-        together with shapes (601,) (600,)} error due to an array shape mismatch. A
-    closer inspection showed that one of the arrays involved in the error was
-    created with the NumPy function \texttt{linspace} that itself calls function
-    \texttt{arange} (Listing~\ref{fig:pyarray_range_code}). Lines 3174-3178 show
-    that the function stores the array size in a floating-point value that will be
-    perturbed by Full MCA, as shown in Table~\ref{tab:mca_result_linspace},
-    resulting in array sizes that fluctuate between N and N+1. It is worth noting
-    that 78\% of execution issues encountered in Full MCA mode instrumentation are
-    due to this type of ``typing" errors.  
-    Those code regions should not be perturbed by MCA since the injected noise does
-    not make sense.}
-
 \subsection{\pytracer supports the profiling of compound data types}
 
-\add{PyTracer supports native floating point formats as well as compound data types,
-    such as complex floating point values, N-dimensional arrays and arbitrary Python
-    classes.}
-Figures~\ref{fig:fft1D_inputs} and~\ref{fig:fft1D_outputs} \add{show the
-    visualization of the \texttt{fft\_1D} input and output values. Results are
-    complex values encoded in double precision. PyTracer allows visualizing the
-    \add{result} precision of real (blue points) and imaginary (orange points) parts.}
-\add{The} top row in Figures~\ref{fig:fft1D_inputs} and~\ref{fig:fft1D_outputs}
-show the input mean value while the bottom row shows the standard deviation. \add{Even though we 
-used Random Rounding (RR), function inputs are perturbed since they result from multiple intermediate 
-computations perturbed with RR.} The
-points with low magnitude in Figure~\ref{fig:fft1D_inputs} correspond to inputs
+\add{PyTracer supports native floating point formats as well as compound
+    data types, such as complex floating point values, N-dimensional arrays
+    and arbitrary Python classes.} Figures~\ref{fig:fft1D_inputs}
+    and~\ref{fig:fft1D_outputs} \add{show the visualization of the
+    \texttt{fft\_1D} input and output values. Results are complex values
+    encoded in double precision. PyTracer allows visualizing the
+    \add{result} precision of real (blue points) and imaginary (orange
+    points) parts.} \add{The} top row in Figures~\ref{fig:fft1D_inputs}
+    and~\ref{fig:fft1D_outputs} show the input mean value while the bottom
+    row shows the standard deviation. \add{Even though Random Rounding
+    (RR) was used, function inputs were perturbed since they result from
+    multiple intermediate computations perturbed with RR.} The points with
+    low magnitude in Figure~\ref{fig:fft1D_inputs} correspond to inputs
     near 0 when the input of $\sin$ or $\exp$ is close to $k\pi$, $k \in
     \mathbb{Z}$. Indeed, since MCA introduces noise, the result is not
-exactly 0. We can see in Figure~\ref{fig:fft1D_inputs} that the maximal noise
-introduced by MCA on the inputs is in the order of $10^{-14}$, two orders of
+    exactly 0. We can see in Figure~\ref{fig:fft1D_inputs} that the maximal
+    noise introduced by MCA on the inputs is in the order of $10^{-14}$,
+    two orders of
 magnitude higher than the $ulp \simeq 10^-16$ for double precision. This slight
@@
 stochastic algorithm and then uses this approximation as input for the SVD. 
-\add{When walking through the code with PyTracer, we see that}
+\add{When walking through the code with PyTracer, we observed that}
 the \texttt{randomized\_svd} scikit-learn function uses the Divide \& Conquer SVD
@@
 raise a runtime error, the regression coefficients computed from the fitting are
-non-significant. \pytracer traces reveal that the SVD solver used is once again the root
+not significant. \pytracer traces reveal that the SVD solver used is once again the root
 cause for this error. \add{Indeed, the BayesianRidge model first computes an SVD
@@
 
-\add{Similarly, for OLS, PyTracer tracers show that the
+\add{Similarly, for OLS, PyTracer traces show that the
     regression coefficients fitted are \texttt{NaN} values. By looking at the callgraph, we can
@@
 In conclusion, \pytracer and the MCA model were helpful to detect the
-instability of the \texttt{gesdd} method mentioned in several GitHub issues,
+instability of the \texttt{gesdd} method mentioned in several GitHub issues \TG{(such as ...)},
 including the LAPACK repository. Furthermore, it is worth mentioning that a Pull
-Request has recently been submitted to let the user select the SVD method and
+Request has recently been submitted \TG{in the ... repo} to let the user select the SVD method and
 avoid this kind of issue. Thus, \pytracer can detect instabilities that affect
@@
 
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/parsing_time.pdf}
-%     \caption{\pytracer time to aggregate traces.}
-%     \label{fig:performance_parsing_time}
-% \end{figure}
-
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=\linewidth]{figure/parsing.pdf}
-%     \caption{\pytracer trace and aggregation files size.
-%     The figure presents the size measured for the trace and the aggregation size files.}
-%     \label{fig:performance_parsing_size}
-% \end{figure}
-
 \begin{figure}
@@
 
-% \begin{table}
-% \centering
-% \begin{subfigure}[t]{.75\linewidth}
-%     \centering
-%     \begin{tabular}{|l|c|c|c|c|}
-%     \hline 
-%     Application & Original & Pytracer only & RR & MCA \\
-%     \hline 
-%     Loading & 0.456 & 8.152 & - & - \\
-%     \hline
-%     discrete\_cosine\_transform & 0.280 & 8.176 & 10.203 & - \\ 
-%     fft\_1D & 0.650 & 9.075 & 11.345 & - \\
-%     fft\_2D & 0.311 & 9.500 & 11.929  & 16.433   \\
-%     \hline
-%     interpolation\_1D & 0.377 & 8.803  & 11.954  & -   \\
-%     multivariate\_data &0.626 & 8.648 &  12.711  & - \\
-%     bspline & 0.109  & 9.050 & 13.396  & 16.830   \\
-%     spline\_1D & 0.111 & 8.618 & 10.960   & - \\
-%     spline\_2D & 0.655 & 8.649 & 19.424  & - \\
-%     \hline
-%     broyden\_fletcher\_goldfarb\_shanno &0.475 & 8.292 & 11.033 & 13.685 \\
-%     global\_optimization &1.257 & 55.916  & 93.322  & - \\
-%     slsqp & 0.469 & 8.192 & 10.795 & 12.439  \\
-%     least\_square\_minimization & 0.505 & 10.151  & 13.888 & -  \\
-%     nelder\_mead\_simplex & 0.471 & 8.418  & 11.382  & 12.792  \\
-%     newton\_conjugate\_gradient & 0.487 & 8.548  & 11.956  & 14.281 \\
-%     root\_findings & 0.462 & 8.198  & 10.787   & - \\
-%     root\_finding\_large & 0.801 & 11.525 & 41.493   &  82.701  \\
-%     root\_finding\_large\_preconditioned & 0.702 & 10.580 & 33.199   & 57.579  \\
-%     trust\_region\_exact & 0.482 & 8.170 & 10.400  & 12.524 \\
-%     trust\_region\_truncated\_generalized\_lanczos & 0.459 & 8.457 & 11.216 & 13.245  \\
-%     trust\_region\_newton\_conjugate\_gradient & 0.479 & 8.538 & 11.179 & 13.488 \\
-%     \hline
-%     Adaboost &1.388 &14.553 &  20.999 & - \\
-%     Bayesian Ridge Regression & 1.086 & 10.344 & 90.299 & -  \\
-%     Online classifier comparison & 15.964 & 72.691 & 2104.114 & -  \\
-%     K-Means Clustering & 1.621 & 17.614  & 34.005 & 52.902   \\
-%     Covariance estimation & 1.357 & 11.755 & 23.964  & -   \\
-%     Decision Tree Regression & 1.185 & 11.194 & 15.760 & 15.918  \\
-%     Digits Classification & 1.672 & 12.725 & 40.634 & - \\
-%     Face Recognition & 32.159  & 74.356 & - & - \\
-%     L1 Penalty & 1.568 & 12.591 & 65.547 & 128.220 \\
-%     Lasso and elastic net & 1.057 & 9.903 & 17.078 & -  \\
-%     Separating hyperplan & 1.376 & 11.532  & 22.333 & 25.036 \\
-%     MNIST classification & 19.650 & 37.838 & 402.389  & - \\
-%     Multitask Lasso & 1.090 &10.196 & 15.025  & - \\
-%     Orthogonal matching & 1.161 & 12.129 & 21.779   & 31.135 \\
-%     PCA decomposition & 1.239 & 10.642 & 15.520 & 17.952    \\
-%     Robust Linear Regression & 1.370 & 11.144  & 14.280  & - \\
-%     Segmentation toy &1.679 & 22.385 & 87.811  & - \\
-%     SVM & 1.403 & 11.737 & 23.203 & 24.126   \\
-%     Tomography & 11.108 & 40.177  & 1376.134 & -  \\
-%     Weighted samples & 1.358 & 11.768 & 21.255 & 20.541   \\
-%     \hline
-%     \end{tabular}
-% \end{subfigure}
-%     \caption{\pytracer tracing overhead in seconds. \tristan{what is the unit in this table?}}
-%     \label{tab:pytracer_overhead}
-% \end{table}
-
-% \begin{table}[]
-%     \centering
-%     \begin{tabular}{c|c|c|c|c}
-%          Pytracer & Verificarlo Instrumentation & Backend & Time (hours:minutes:seconds) & Overhead \\
-%          \hline 
-%          No & No & - & 00:30:51 & 1 \\
-%          No & Yes & IEEE & 01:32:56 & 3 \\
-%          No & Yes & RR & 16:52:08 & 32 \\
-%          Yes & No & - & 03:11:07 & 6  \\
-%          Yes & Yes & IEEE & 11:14:33 & 22 \\
-%          Yes & Yes & RR & 25:05:54 & 48 \\
-%     \end{tabular}
-%     \caption{Overheads of \pytracer on PyAFQ experiment with and without fuzzy.}
-%     \label{tab:pytracer_overhead}
-% \end{table}
-
-% \begin{table}[]
-%     \centering
-%     \begin{tabular}{c|c|c|c|c}
-%          Pytracer & Verificarlo Instrumentation & Backend & Time (hours:minutes:seconds) & Overhead \\
-%          \hline 
-%          No & No & - & 15 & 1 \\
-%          No & Yes & IEEE & 49 & 3 \\
-%          No & Yes & RR &  & 441 & 29 \\
-%          Yes & No & - & 03:11:07 & 6  \\
-%          Yes & Yes & IEEE & 11:14:33 & 22 \\
-%          Yes & Yes & RR & 25:05:54 & 48 \\
-%     \end{tabular}
-%     \caption{Caption}
-%     \label{tab:pytracer_overhead}
-% \end{table}
-
 Figure~\ref{fig:performance_parsing} shows the postprocessing time and trace
@@
 \section{Discussion}
-
-% Numpy   2509 (2403 not tests) (1848) functions, 1196 (1154) (817) classes (pure Python)
-% Scipy   4031 (2187) (506) functions, 1532 (472) (109) classes (pure Python)
-% Sklearn 4807 (1010) (81) functions, 546 (417) (41) classes (pure Python)
-
-% \pytracer is a tool for visualizing the numerical quality of function inputs
-% and outputs along the execution of a Python program. It generates numerical
-% traces and post-processes them to measure numerical discrepancies between
-% executions. \pytracer does not require any particular noise model to estimate
-% uncertainties. We tested it with MCA through the fuzzy ecosystem on two
-% broadly used Python libraries.
 
@@
 tested it with Monte-Carlo arithmetic. Therefore, we would like to compare
-different models against MCA.} \pytracer is available at
-\href{https://github.com/big-data-lab-team/pytracer}{github://big-data-lab-team/pytracer}
-under MIT License.
+different models against MCA.}
 

### 2022-05-16 IEEEtran/paper.tex
Fix typos

@@
 processing. In unstable analyses, small numerical perturbations introduced by
-data noise, software and hardware updates, or parallelization have potential to
+data noise, software and hardware updates, or parallelization have the potential to
 introduce substantial deviations in final results, leading to potentially
@@
 Python programs. \pytracer adopts a dynamic approach that evaluates numerical
-stability using program execution traces, and is applicable to large programs
+stability using program execution traces and applies to large programs
 without manual intervention. The transparent nature of \pytracer is particularly
@@
 static code analysis techniques~\cite{goubault2006static} hardly scale
-to large code bases, particularly in dynamically-typed languages such as Python.
+to large codebases, particularly in dynamically-typed languages such as Python.
 
@@
 which requires (\add{a}\remove{1}) generating numerically-perturbed
-executions, (\add{b}\remove{2}) tracing floating-point computations along
+executions, (\add{b}\remove{2}) tracing floating-point computations along with
 program executions, and (\add{c}\remove{3}) visualizing stability
@@
     visualizing stability measures throughout program executions with an
-interactive Plotly dashboard. \mbox{\pytracer} is available at
+    interactive Plotly dashboard. \mbox{\pytracer} is available
     \mbox{\href{https://github.com/big-data-lab-team/pytracer}{github.com/big-data-lab-team/pytracer}}
@@
     \pytracer adopts the workflow shown in Figure~\ref{fig:workflow}.
-At step 1, \pytracer uses monkey patching to replace the functions called
+    In step 1, \pytracer uses monkey patching to replace the functions called
     by the application with a wrapper that saves their arguments and returned
-values in a trace file. At step 2, it executes the application multiple
+    values in a trace file. In step 2, it executes the application multiple
     times with Monte-Carlo Arithmetic as implemented in the
@@
     aggregates the resulting trace files to compute summary statistics on
-traced variable. At step 3, a Plotly dashboard provides interactive
+    traced variables. In step 3, a Plotly dashboard provides interactive
     visualizations highlighting unstable code sections.
@@
 namespaces\footnote{Python distinguishes between \texttt{regular} and
-    \texttt{namespace} packages. A regular package is a directory that contains a
+    \texttt{namespace} packages. A regular package is a directory that contains an
     \_\_init\_\_.py file and potentially subdirectories (sub-packages) that contain
-    themselves a \texttt{\_\_init\_\_.py} file and so on recursively. The package
+    themselves an \texttt{\_\_init\_\_.py} file and so on recursively. The package
     hierarchy follows those of the directory. Namespace packages introduced in
@@
 
-\pytracer's \texttt{loader} class first loads the original module, then copies
+\pytracer's \texttt{loader} class first loads the original module and then copies
 it as a new instance of the \texttt{ModuleType} class. It then calls the
@@
     \mbox{\pytracer}'s function instrumentation mechanism.}
-For each function to instrument, \pytracer's \texttt{loader} class creates a
+For each function to be instrumented, \pytracer's \texttt{loader} class creates a
 wrapper function, dynamically compiles it with the \texttt{compile} builtin
@@
     unstable. In particular, we encountered only a few iterators in our
-experiments and none of them involved floating point values. Should
+    experiments and none of them involved floating-point values. Should
     instabilities occur in iterators, \pytracer would detect them through the
@@
 Carlo Arithmetic (MCA)~\cite{parker1997monte} uses this principle by introducing
-two improvements: (i) a virtual precision parameter, allowing to simulate
+two improvements: (i) a virtual precision parameter, allowing for simulating
 reduced working precision, and (ii) different perturbation modes to introduce
@@
 where $\mu$ and $\sigma$ are the sample mean and standard deviation of a
-variable sampled with MCA. \add{This can be seen as the ratio signal over noise.}
+variable sampled with MCA. \add{This can be seen as the ratio of signal over noise.}
 Sohier et al.~\cite{sohier2021confidence} recently provided a generalization of
@@
 
-We enabled MCA in Python programs via Verificarlo~\cite{verificarlo}, a
+We enabled MCA in Python programs via Verificarlo~\cite{verificarlo} a
 clang-based compiler~\cite{lattner2008llvm} that replaces floating-point
-operations by a generic call to a configurable floating-point model. Several
+operations with a generic call to a configurable floating-point model. Several
 floating-point models are
@@
 
-\pytracer stores traces in the pickle format, a binary format to serialize
+\pytracer stores trace in the pickle format, a binary format to serialize
 Python objects. The main advantages of the pickle format compared to other
@@
 statistics in an HDF5 file, a hierarchical format that facilitates visual
-browsing since only required information are loaded when requested by the user.
+browsing since only required information is loaded when requested by the user.
 This operation critically relies on the ordering of call input and output
@@
           relation. For example, in the figure, \texttt{function1} calls
-          \texttt{function2} that itself calls \texttt{function4} and
-          \texttt{function5}. This view provides insights on the calling context
+          \texttt{function2} which itself calls \texttt{function4} and
+          \texttt{function5}. This view provides insights into the calling context
           for each function, which may influence numerical stability.
@@
           code file of the variable hovered in the timeline view.
-    \item Zoom view: This view provide details about non-scalar values. For
+    \item Zoom view: This view provides details about non-scalar values. For
           example, a matrix may have instabilities around its diagonal but not
@@
     to provide an overall picture of numerical uncertainty in the tested examples. 
-Depending on the use-case of interest, one might choose to use MCA only in 
+    Depending on the use case of interest, one might choose to use MCA only in 
     a subset of these libraries or even just in the Python interpreter.} \add{We
@@
             \multicolumn{2}{|c|}{}                                              & \faceRf                                                                   & \cross                                                   & \valid & \s{-}              \\
-            \multicolumn{2}{|c|}{}                                              & \penaltyRf                                                                & \valid                                                   & \valid & -                  \\
+            \multicolumn{2}{|c|}{}                                              & \penaltyRf                                                                & \valid                                                   & \valid & 52                 \\
             \multicolumn{2}{|c|}{}                                              & \lassoRf                                                                  & \valid                                                   & \valid & \s{48}             \\
@@
 
-\subsection{\pytracer is applicable to reference scientific computating libraries}
+\subsection{\pytracer is applicable to reference scientific computing libraries}
 
@@
     and could therefore be computed even when parsing failed.} \add{We use the term ``result precision"
-to denote the statistical variability measured in number of significant bits, in 
-contrast with the other meanings of the word precision used in expressions
+    to denote the statistical variability measured in the number of significant bits, in 
+    contrast with the other meanings of the word precision used in the expressions
     ``virtual precision" or ``single/double precision'' in this paper.} The numerical
@@
 
-\add{PyTracer supports native floating point formats as well as compound
-    data types, such as complex floating point values, N-dimensional arrays
+\add{PyTracer supports native floating-point formats as well as compound
+    data types, such as complex floating-point values, N-dimensional arrays,
     and arbitrary Python classes.} Figures~\ref{fig:fft1D_inputs}
@@
 noise introduced by MCA on the inputs is in the order of $10^{-14}$,
-    two orders of
-magnitude higher than the $ulp \simeq 10^-16$ for double precision. This slight
+two orders of magnitude higher than the $ulp \simeq 10^-16$ for double precision. This slight
 noise introduced can be interpreted as white noise on the input signal. We can
 see on the bottom row of Figure~\ref{fig:fft1D_outputs} that the frequency noise
-is of the same order of of magnitude as the input noise, which is expected. The
-two peaks at x=38 and x=562 corresponds to the actual frequencies of the input
+is of the same order of magnitude as the input noise, which is expected. The
+two peaks at x=38 and x=562 correspond to the actual frequencies of the input
 signal.
@@
     interpolation for function $z=(x+y)e^{-6(x^2+y^2)}$, with $(x,y) \in
-        [-1,1]\times[-1,1]$. The result is a 2D-array that is natively supported by
+        [-1,1]\times[-1,1]$. The result is a 2D array that is natively supported by
     PyTracer. We observe a significant loss of \add{result} precision in some regions, which follows
@@
     criterion. However, PyTracer shows an issue in the singular values computed.}
-\add{We can see in Figure}~\ref{fig:BRR_svd} \add{that the last singular values is
+\add{We can see in Figure}~\ref{fig:BRR_svd} \add{that the last singular value is
     \texttt{NaN} due to numerical errors in the SVD, although the remaining
     singular values exhibit high \add{result} precision (between 44 and 50 bits).
-    Surprinsingly, this \texttt{NaN} value does not raise an exception and is silently
+    Surprisingly, this \texttt{NaN} value does not raise an exception and is silently
     propagated. Indeed, the stopping criterion is never verified and the 
     optimization stops after reaching the maximal number of iterations.
-    Figure}~\ref{fig:BRR_svd_fixed} \add{shows that uses
+    Figure}~\ref{fig:BRR_svd_fixed} \add{shows that using
     the \texttt{gesvd} instead of the \texttt{gesdd} method removes the \texttt{NaN} value
@@
     which corrupted the calculation of the coefficients. When using the \texttt{gesvd} method, 
-    the \texttt{NaN} value disapears 
+    the \texttt{NaN} value disappears 
     (Fig.}~\ref{fig:OLS_svd_fixed}\add{), resulting in a \add{result} precision of
-    42 bits in average in the coefficients. We can see that having
+    42 bits on average in the coefficients. We can see that having
     access to all the values computed by the application with PyTracer allows
@@
     use of Verificarlo to implement stochastic arithmetic through the Fuzzy
-environment enables to study the impact of numerical perturbations
+    environment enables to study of the impact of numerical perturbations
     introduced in non-Python dependencies while preserving the high-level view
@@
     their recompilation with Verificarlo, which usually requires human
-intervention. The Fuzzy environment provides pre-instrumented version of
+    intervention. The Fuzzy environment provides a pre-instrumented version of
     NumPy, BLAS, LAPACK, GNU libmath, SciPy, and Scikit-learn, which, given the
@@
 
-Several tools have been developed to assess numerical quality, and can be
+Several tools have been developed to assess the numerical quality and can be
 divided into static and dynamic approaches. Static approaches typically analyze
@@
 % \label{sec:soa} \paragraph{Numerical tracing techniques}
-Numerous tools exists to trace floating-point computations for C, C++, or
+Numerous tools exist to trace floating-point computations for C, C++, or
 FORTRAN programs due to the prevalence of these languages in High-Performance
@@
 The source-to-source technique requires a rewriting of the application to modify
-floating-point types and provides a fine-grained control on the analyzed code.
+floating-point types and provides fine-grained control of the analyzed code.
 CADNA~\cite{jezequel2008cadna} is a library for C, C++, and Fortran implementing
@@
 Shaman~\cite{demeure_phd} is a C++ library that uses a first-order error model
-to propagate numerical error. MCAlib~\cite{frechtling2015mcalib} is a C library
+to propagate numerical errors. MCAlib~\cite{frechtling2015mcalib} is a C library
 that implements the Monte Carlo Arithmetic (MCA)~\cite{parker1997monte} using
@@
 precision with and without stochastic arithmetic. The main drawback of the
-source-to-source approach is its lacks of scalability since rewriting large
+source-to-source approach is its lack of scalability since rewriting large
 codes can be a tedious task.
@@
 PFPSanitizer~\cite{chowdhary2020debugging,chowdhary2021parallel} \add{and
-    NSan~\mbox{\cite{courbet2021nsan}} are compiler based approaches}
+    NSan~\mbox{\cite{courbet2021nsan}} are compiler-based approaches}
 that use shadow execution to detect numerical issues using higher
@@
 Dynamic Binary Instrumentation (DBI) operates directly on executables, without
-the need for recompilation or manual changes. Therefore, it is applicable to any
+the need for recompilation or manual changes. Therefore, it applies to any
 programming language. CraftHPC~\cite{lam2013dynamic} uses DBI to detect
@@
 that computing with a large number of bits is sufficient to obtain an accurate
-result, which is not always true (see for example, the famous Muller's
-sequence~\cite{bajard1996introduction}). Although versatile, the DBI looses
+result, which is not always true (see, for example, the famous Muller's
+sequence~\cite{bajard1996introduction}). Although versatile, the DBI loses
 high-level information useful to understand the source-code logic.
@@
 to debug and understand the source-code logic. Conversely, the source-to-source
-approach provides a fine-grained control on the analyzed code, but it lacks
+approach provides fine-grained control of the analyzed code, but it lacks
 scalability, as rewriting large codes can be a tedious task. Finally, the
@@
 task that requires substantial expertise. Automatic tools to help users
-understand the behavior of their code are therefore crucial. \pytracer is the first tool to offer a complete framework for
-analyzing and visualizing the numerical stability of Python codes. It works by
-automatically instrumenting Python programs to produce traces \add{of numerically-perturbed 
-executions and}
-visualize these traces through an interactive Plotly Dash server. \pytracer does not require
-manual code modification. We tested it with \add{Python programs involving} major scientific libraries such
-as NumPy, SciPy, and Scikit-learn. \pytracer enabled the systematic evaluation of 40 examples from the
-SciPy and scikit-learn libraries. Our results show that \pytracer is scalable,
-with an average instrumentation slowdown of $3.5\times$. Moreover, \pytracer's
+understand the behavior of their code are therefore crucial. \pytracer is the
+first tool to offer a complete framework for analyzing and visualizing the
+numerical stability of Python codes. It works by automatically instrumenting
+Python programs to produce traces \add{of numerically-perturbed executions and}
+visualize these traces through an interactive Plotly Dash server. \pytracer does
+not require manual code modification. We tested it with \add{Python programs
+    involving} major scientific libraries such as NumPy, SciPy, and Scikit-learn.
+\pytracer enabled the systematic evaluation of 40 examples from the SciPy and
+scikit-learn libraries. Our results show that \pytracer is scalable, with an
+average instrumentation slowdown of $3.5\times$. Moreover, \pytracer's
 visualization interface remains responsive even with traces of up to 1TB.
@@
 traces \add{obtained with different control flow paths,} by leveraging
-techniques used in code coverage analysis. \add{This would also enable a larger support 
-of multi-threaded applications.} Moreover, we would like to
-extend \pytracer to instrument elementary arithmetic operations \add{(+,-,*,/), to allow for more detailed analyses}.
-\remove{Finally, although \pytracer supports multiple noise models, we only
-tested it with Monte-Carlo arithmetic. Therefore, we would like to compare
-different models against MCA.}
+techniques used in code coverage analysis. \add{This would also enable larger
+    support for multi-threaded applications.} Moreover, we would like to extend
+\pytracer to instrument elementary arithmetic operations \add{(+,-,*,/), to
+    allow for more detailed analyses}. \remove{Finally, although \pytracer supports
+    multiple noise models, we only tested it with Monte-Carlo arithmetic. Therefore,
+    we would like to compare different models against MCA.}
 

### 2022-10-17 IEEEtran/paper.tex
Final edit before minor rewiews

@@
 
-% \ifANNOTATED
+\ifANNOTATED
 \definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
@@
 \newcommand{\TG}[1]{\color{red}\textsc{From Tristan}: #1\xspace\color{black}}
-% \else
-% \DeclareRobustCommand{\add}[1]{#1}
-% \DeclareRobustCommand{\remove}[1]{}
-% \DeclareRobustCommand{\addCite}[1]{#1}
-% \newcommand{\TG}[1]{}
-% \fi
+\else
+\DeclareRobustCommand{\add}[1]{#1}
+\DeclareRobustCommand{\remove}[1]{}
+\DeclareRobustCommand{\addCite}[1]{#1}
+\newcommand{\TG}[1]{}
+\fi
 
@@
 program executions, and (\add{c}\remove{3}) visualizing stability
-evaluations. \add{PyTracer addresses (a) by relying on
+evaluations. \add{PyTracer addresses this work (a) by relying on
     Fuzzy~\cite{kiar2020comparing}, an existing collection of scientific
@@
     visualizing stability measures throughout program executions with an
-    interactive Plotly dashboard. \mbox{\pytracer} is available
+    interactive Plotly dashboard. \mbox{\pytracer} is available at
     \mbox{\href{https://github.com/big-data-lab-team/pytracer}{github.com/big-data-lab-team/pytracer}}
@@
     \pytracer adopts the workflow shown in Figure~\ref{fig:workflow}.
-    In step 1, \pytracer uses monkey patching to replace the functions called
+    In Step 1, \pytracer uses monkey patching to replace the functions called
     by the application with a wrapper that saves their arguments and returned
-    values in a trace file. In step 2, it executes the application multiple
+    values in a trace file. In Step 2, it executes the application multiple
     times with Monte-Carlo Arithmetic as implemented in the
@@
     aggregates the resulting trace files to compute summary statistics on
-    traced variables. In step 3, a Plotly dashboard provides interactive
+    traced variables. In Step 3, a Plotly dashboard provides interactive
     visualizations highlighting unstable code sections.
@@
 Three  main  approaches  exist  to  detect  numerical  instabilities:
-stochastic  arithmetic,  uncertainty  or  sensitivity analysis \TG{[23] fix ref}, and random
-seed analysis \TG{fix ref [11]}.  \add{PyTracer is agnostic to the noise model used and can therefore
+stochastic  arithmetic,  uncertainty  or  sensitivity analysis~\cite{helton2006survey}, and random
+seed analysis~\cite{hellekalek1998good}. \add{PyTracer is agnostic to the noise model used and can therefore
     be used for all these methods}.  For our use cases, we focus on stochastic
@@
     simulates roundoff errors by applying function $inexact$ only to the
-    output returned by a function. The Precision Bounding (PB) mode can
+    output returned by a function. The Precision Bounding (PB) mode that applies
+    the $inexact$ function on inputs can
     identify other types of instabilities, in particular catastrophic
@@
     MCA samples to use for a given instrumented code is still an open research question. 
-    Recent theoretical works}~\cite{sohier2021confidence}
-\add{on the estimation of significant digits allow computing an associated
-    confidence interval depending on the sample size and the underlying distribution.}
+%%     Recent theoretical works}~\cite{sohier2021confidence}
+%% \add{on the estimation of significant digits allow computing an associated
+%%   confidence interval depending on the sample size and the underlying distribution.
+}
 
@@
     PyTracer. We observe a significant loss of \add{result} precision in some regions, which follows
-    an interesting pattern that could be further investigated.}
+    an interesting pattern that could be further investigated.
+    This example shows that \pytracer workds on 2D inputs and the importance of
+    visualizing complex data and not only reporting the values.}
 
@@
 
-Replacing \texttt{gesdd} for \texttt{gesvd} solved the SVD convergence issue.
-\pytracer allows to quickly visualize the new \add{result} precision.
+Replacing \texttt{gesdd} with\texttt{gesvd} solved the SVD convergence issue.
+\pytracer allows us to quickly visualize the new \add{result} precision.
 Figure~\ref{fig:face_recognition_svd} shows the \add{result} precision of the eigenvalues
@@
 In conclusion, \pytracer and the MCA model were helpful to detect the
-instability of the \texttt{gesdd} method mentioned in several GitHub issues \TG{(such as ...)},
+instability of the \texttt{gesdd} method mentioned in several GitHub issues such as
+\href{https://github.com/google/TensorNetwork/pull/962}{github.com/google/TensorNetwork/pull/962} or
+\href{https://github.com/scipy/scipy/issues/15024}{github.com/scipy/scipy/issues/15024}
 including the LAPACK repository. Furthermore, it is worth mentioning that a Pull
-Request has recently been submitted \TG{in the ... repo} to let the user select the SVD method and
+Request at \href{https://github.com/scikit-learn/scikit-learn/pull/20617}{github.com/scikit-learn/scikit-learn/pull/20617}
+has recently been submitted in the scikit-learn repository to let the user select the SVD method and
 avoid this kind of issue. Thus, \pytracer can detect instabilities that affect
@@
     use of Verificarlo to implement stochastic arithmetic through the Fuzzy
-    environment enables to study of the impact of numerical perturbations
+    environment enables us to study the impact of numerical perturbations
     introduced in non-Python dependencies while preserving the high-level view
@@
     Automatic Differentiation to compute a sensitivity profile for each variable in a
-    program}. Finally, the work in~\cite{tang2016software} proposed a
+    program}. Finally, the work in~\cite{tang2016software} proposes a
 source-to-source framework for executing targeted code in infinite and fixed
@@
 (AST) level to rewrite parts of code with higher precision.
-PFPSanitizer~\cite{chowdhary2020debugging,chowdhary2021parallel} \add{and
+FPSanitizer~\cite{chowdhary2020debugging,chowdhary2021parallel} \add{and
     NSan~\mbox{\cite{courbet2021nsan}} are compiler-based approaches}

### 2022-10-17 IEEEtran/paper.tex
Remove \add of first review

@@
         in a Plotly dashboard. We designed \pytracer to be agnostic to numerical
-        noise model, allowing for \add{numerical profiling} through Monte-Carlo
+        noise model, allowing for numerical profiling through Monte-Carlo
         Arithmetic, random rounding, random data perturbation, or structured
@@
 combining program traces obtained with different numerical perturbations,
-which requires (\add{a}\remove{1}) generating numerically-perturbed
-executions, (\add{b}\remove{2}) tracing floating-point computations along with
-program executions, and (\add{c}\remove{3}) visualizing stability
-evaluations. \add{PyTracer addresses this work (a) by relying on
+which requires (a) generating numerically-perturbed
+executions, (b) tracing floating-point computations along with
+program executions, and (c) visualizing stability
+evaluations. PyTracer addresses this work (a) by relying on
 Fuzzy~\cite{kiar2020comparing}, an existing collection of scientific
@@
 \mbox{\href{https://github.com/big-data-lab-team/pytracer}{github.com/big-data-lab-team/pytracer}}
-    under MIT License.} \remove{\mbox{\pytracer} addresses these requirements
-    with (1) a Fuzzy Python interpreter instrumented with Monte-Carlo
-    arithmetic, (2) a dynamic instrumentation of Python functions, modules, and
-    classes through meta-programming, (3) an interactive Plotly dashboard to
-    visualize stability measures throughout program executions. }
-
-This manuscript presents the design of \pytracer and \add{highlights} its potential
+under MIT License.
+
+This manuscript presents the design of \pytracer and highlights its potential
 in various use cases. Through stability evaluations of the SciPy and
@@
 
-\add{
 To detect numerical instabilities, \pytracer works in three main steps:
@@
 visualizations highlighting unstable code sections.
-}
-
-\add{
+
 The remainder of this section assumes some knowledge of Python concepts
@@
 concepts.
-}
 
@@
 Python methods. However, some attributes are not writable. In this case,
-\pytracer \add{preserves} the original attributes and warns
+\pytracer preserves the original attributes and warns
 the user. The user can also restrict the list of traced attributes through an
@@
 approach is the lack of required modification in the application source code, in
-contrast with \remove{decorator-based approaches} \add{a decorator-based
-    approach~\mbox{\cite{hunt2019decorators}}}. In addition, this technique is
+contrast with  a decorator-based approach~\mbox{\cite{hunt2019decorators}}. 
+In addition, this technique is
 scalable and applicable in read-only environments such as Singularity containers
@@
 this technique does not apply to callable class instances, i.e., class instances
-\add{that can be called directly with the () operator, because they} are not of type
+that can be called directly with the () operator, because they are not of type
 \texttt{FunctionType}. Indeed, applying the wrapper technique would 1) modify
@@
 Pytracer does not instrument the class and returns a warning. 
-\add{
 This limitation is expected to have a minor impact in practice since non-writable
@@
 classes that use them.
-}
 
@@
 
-\add{
 We do not expect this limitation to have a critical impact on the
@@
 inputs of the functions consuming these iterators.
-}
 
@@
 stochastic  arithmetic,  uncertainty  or  sensitivity analysis~\cite{helton2006survey}, and random
-seed analysis~\cite{hellekalek1998good}. \add{PyTracer is agnostic to the noise model used and can therefore
-    be used for all these methods}.  For our use cases, we focus on stochastic
+seed analysis~\cite{hellekalek1998good}. PyTracer is agnostic to the noise model used and can therefore
+be used for all these methods.  For our use cases, we focus on stochastic
 arithmetic since it does not make any assumption about the noise model, in
-contrast to sensitivity analysis\add{.}
+contrast to sensitivity analysis.
 
@@
 Virtual precision allows for the simulation of reduced working precision.
-\add{In our experiments, we used MCA in Random Rounding (RR) mode, which
+In our experiments, we used MCA in Random Rounding (RR) mode, which
 simulates roundoff errors by applying function $inexact$ only to the
@@
 cancellations, however, it is more difficult to apply to large code bases
-    as it often leads to execution errors that require human intervention.}
+as it often leads to execution errors that require human intervention.
 
@@
 where $\mu$ and $\sigma$ are the sample mean and standard deviation of a
-variable sampled with MCA. \add{This can be seen as the ratio of signal over noise.}
+variable sampled with MCA. This can be seen as the ratio of signal over noise.
 Sohier et al.~\cite{sohier2021confidence} recently provided a generalization of
@@
 
-\add{Monte Carlo Arithmetic samples the floating-point variability of a given
+Monte Carlo Arithmetic samples the floating-point variability of a given
 program, and hence the more MCA repetitions we have, the more accurate the
@@
 MCA samples to use for a given instrumented code is still an open research question.
-%%     Recent theoretical works}~\cite{sohier2021confidence}
-%% \add{on the estimation of significant digits allow computing an associated
-%%   confidence interval depending on the sample size and the underlying distribution.
-}
 
@@
 single-threaded and that the control flow does not depend on a random state.
-\add{Therefore, \mbox{\pytracer} cannot merge traces resulting from different
-    control flow paths and will stop the parsing when encountering such a situation.}
+Therefore, \mbox{\pytracer} cannot merge traces resulting from different
+control flow paths and will stop the parsing when encountering such a situation.
 
@@
 their respective GitHub repositories. We traced each example five times, having
-activated MCA through Fuzzy in the Python interpreter \add{as well as} BLAS, LAPACK, NumPy,
-SciPy, and scikit-learn. \add{These libraries are written in large parts in a
+activated MCA through Fuzzy in the Python interpreter as well as BLAS, LAPACK, NumPy,
+SciPy, and scikit-learn. These libraries are written in large parts in a
 compiled language other than Python (such as C or Cython) and their execution is not 
@@
 Depending on the use case of interest, one might choose to use MCA only in 
-    a subset of these libraries or even just in the Python interpreter.} \add{We
-    used MCA in Random Rounding (RR) mode, with} the default virtual
+a subset of these libraries or even just in the Python interpreter. We
+used MCA in Random Rounding (RR) mode, with the default virtual
 precision in Verificarlo, namely 24 bits for single-precision floating-point
@@
             \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{  \multirow{5}{*}{ \rotatebox{90}{Interpolation} } }
+
                                                                                 & \interOneDRf                                                              & \valid                                                   & \valid & 51                 \\
@@
             \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{ \multirow{12}{2em}{ \rotatebox{90}{Optimization} } }
+
                                                                                 & \bfgsRf                                                                   & \valid                                                   & \valid & \s{48}             \\
@@
     \caption{\pytracer execution summary on SciPy and Scikit-learn examples.
-        % \tristan{Replace FFT with SciPy FFT, Interpolation with SciPy
-        % Interpolation and Optimization with SciPy Optimization, or add a SciPy
-        % header to these rows.} \tristan{Nitpick: you could add a color scheme
-        % to sigbits (for instance shades of blue), to make the column more
-        % easily readable.} \\
         \emph{trace}: outcome of \pytracer tracing, \emph{parse}: outcome of
-        \pytracer trace parsing and aggregation, \emph{result}: \add{result} precision
-        in number of significant bits. \valid: successful run, \remove{\warn: error
-            from invalid noise injection,} \cross: numerical error \add{(tracing)} or 
-        \add{different control flow paths (parsing).} \textit{nan} stands for (\texttt{Not-A-Number}). Example names
-        are linked to their source code.}
+        \pytracer trace parsing and aggregation, \emph{result}: result precision
+        in number of significant bits. \valid: successful run, \cross: numerical error (tracing) or 
+        different control flow paths (parsing). \textit{nan} stands for (\texttt{Not-A-Number}). 
+        Example names are linked to their source code.}
     \label{tab:pytracer_results_summary}
@@
 report on the tracing and aggregation steps with two possible outcomes:
-\add{green \valid\xspace for success and red \cross\xspace for error. Tracing errors
+green \valid\xspace for success and red \cross\xspace for error. Tracing errors
 occur in the application as a result of 
 numerical perturbations, whereas parsing errors occur when traces result from different 
-    control flow paths.}
+control flow paths.
 Overall, the tracing and parsing of SciPy and scikit-learn examples in Random
-Rounding mode was entirely successful for 32/40 examples\remove{ and showed an average
-    precision loss of 8 bits}. 
-\remove{The instrumentation with Full MCA is
-    more invasive and reduced the number of successful exe-
-    cutions to 12/40. Among the 28/40 failed executions, one
-    failed due to an actual numerical error (Bayesian Ridge
-    Regression example) and the other ones failed due to
-    perturbations that should not have been introduced.}
+Rounding mode was entirely successful for 32/40 examples.
 
 Column \textit{sigbits} in Table~\ref{tab:pytracer_results_summary} summarizes
-the \add{result} precision for the main outputs of SciPy and scikit-learn examples. We
-measured the \add{result} precision in significant bits on the final primary example output
+the result precision for the main outputs of SciPy and scikit-learn examples. We
+measured the result precision in significant bits on the final primary example output
 by taking the element-wise mean for non-scalar values and, if the example
-produce\add{d multiple} outputs, the average value among them. \add{Significant bits were computed on the final program output
-    and could therefore be computed even when parsing failed.} \add{We use the term ``result precision"
+produced multiple outputs, the average value among them. Significant bits were computed on the final program output
+and could therefore be computed even when parsing failed. We use the term ``result precision"
 to denote the statistical variability measured in the number of significant bits, in 
 contrast with the other meanings of the word precision used in the expressions
-    ``virtual precision" or ``single/double precision'' in this paper.} The numerical
+``virtual precision" or ``single/double precision'' in this paper. The numerical
 quality across all examples varied from 0 to 52, with an average of 44
@@
 numerical error (\texttt{face\_recognition}
-\remove{for RR and \texttt{Bayesian Ridge Regression} for full MCA}).
+for RR and \texttt{Bayesian Ridge Regression} for full MCA).
 
@@
 
-\add{PyTracer supports native floating-point formats as well as compound
+PyTracer supports native floating-point formats as well as compound
 data types, such as complex floating-point values, N-dimensional arrays,
-    and arbitrary Python classes.} Figures~\ref{fig:fft1D_inputs}
-and~\ref{fig:fft1D_outputs} \add{show the visualization of the
+and arbitrary Python classes. Figures~\ref{fig:fft1D_inputs}
+and~\ref{fig:fft1D_outputs} show the visualization of the
 \texttt{fft\_1D} input and output values. Results are complex values
 encoded in double precision. PyTracer allows visualizing the
-    \add{result} precision of real (blue points) and imaginary (orange
-    points) parts.} \add{The} top row in Figures~\ref{fig:fft1D_inputs}
+result precision of real (blue points) and imaginary (orange
+points) parts. The top row in Figures~\ref{fig:fft1D_inputs}
 and~\ref{fig:fft1D_outputs} show the input mean value while the bottom
-row shows the standard deviation. \add{Even though Random Rounding
+row shows the standard deviation. Even though Random Rounding
 (RR) was used, function inputs were perturbed since they result from
-    multiple intermediate computations perturbed with RR.} The points with
+multiple intermediate computations perturbed with RR. The points with
 low magnitude in Figure~\ref{fig:fft1D_inputs} correspond to inputs
@@
 
-Figure~\ref{fig:spline2d_rr} \add{shows the results of the spline evaluation with
+Figure~\ref{fig:spline2d_rr} shows the results of the spline evaluation with
 \texttt{bisplev} from the \texttt{spline\_2D} example. It computes the 2D spline
@@
     [-1,1]\times[-1,1]$. The result is a 2D array that is natively supported by
-    PyTracer. We observe a significant loss of \add{result} precision in some regions, which follows
+PyTracer. We observe a significant loss of result precision in some regions, which follows
 an interesting pattern that could be further investigated.
-    This example shows that \pytracer workds on 2D inputs and the importance of
+\add{This example shows that \pytracer workds on 2D inputs and the importance of
     visualizing complex data and not only reporting the values.}
@@
 
-\add{We illustrate on two examples how PyTracer is effective for analyzing
-    numerical stability in complex codes at a fine-grained level: Face recognition and Bayesian Ridge Regression.}
+We illustrate on two examples how PyTracer is effective for analyzing
+numerical stability in complex codes at a fine-grained level: Face recognition and Bayesian Ridge Regression.
 The face recognition example uses eigenfaces (eigenvectors) and Support Vector
@@
 and then trains an SVM classifier to predict the label associated with a face.
-\add{When executing in PyTracer, this example crashed because the Singular Value Decomposition (SVD) did not converge.}
+When executing in PyTracer, this example crashed because the Singular Value Decomposition (SVD) did not converge.
 This example is the only one to raise an error due to the
@@
 stochastic algorithm and then uses this approximation as input for the SVD. 
-\add{When walking through the code with PyTracer, we observed that}
+When walking through the code with PyTracer, we observed that
 the \texttt{randomized\_svd} scikit-learn function uses the Divide \& Conquer SVD
@@
 Replacing \texttt{gesdd} with\texttt{gesvd} solved the SVD convergence issue.
-\pytracer allows us to quickly visualize the new \add{result} precision.
-Figure~\ref{fig:face_recognition_svd} shows the \add{result} precision of the eigenvalues
-computed with \texttt{gesvd} \add{in single precision}. \add{The result precision}
+\pytracer allows us to quickly visualize the new result precision.
+Figure~\ref{fig:face_recognition_svd} shows the result precision of the eigenvalues
+computed with \texttt{gesvd} in single precision. The result precision
 varies between 15 and 20
@@
 metrics (precision, recall, F1-score, and support) are identical to the IEEE
-execution for all MCA samples. \add{We can note that even with the \texttt{gesvd} method,
-    the \add{result} precision of the singular values and eigenvectors is not uniform. 
-    Indeed, we can see that the \add{result} precision of the lowest singular values and eigenvectors decreases 
-    until reaching 0 significant bits.}
+execution for all MCA samples. We can note that even with the \texttt{gesvd} method,
+the result precision of the singular values and eigenvectors is not uniform. 
+Indeed, we can see that the result precision of the lowest singular values and eigenvectors decreases 
+until reaching 0 significant bits.
 
@@
 not significant. \pytracer traces reveal that the SVD solver used is once again the root
-cause for this error. \add{Indeed, the BayesianRidge model first computes an SVD
+cause for this error. Indeed, the BayesianRidge model first computes an SVD
 before iteratively updating the coefficients until reaching the convergence
-    criterion. However, PyTracer shows an issue in the singular values computed.}
-\add{We can see in Figure}~\ref{fig:BRR_svd} \add{that the last singular value is
+criterion. However, PyTracer shows an issue in the singular values computed.
+We can see in Figure~\ref{fig:BRR_svd} that the last singular value is
 \texttt{NaN} due to numerical errors in the SVD, although the remaining
-    singular values exhibit high \add{result} precision (between 44 and 50 bits).
+singular values exhibit high result precision (between 44 and 50 bits).
 Surprisingly, this \texttt{NaN} value does not raise an exception and is silently
@@
 optimization stops after reaching the maximal number of iterations.
-    Figure}~\ref{fig:BRR_svd_fixed} \add{shows that using
+Figure~\ref{fig:BRR_svd_fixed} shows that using
 the \texttt{gesvd} instead of the \texttt{gesdd} method removes the \texttt{NaN} value
-    although the last singular values stills have a low \add{result} precision (below 0).
-    According to Equation}~\ref{eq:sig-digits}, \add{a number of significant bits less than 0 means that the
-    variability ($\sigma$) is higher than the average value ($\mu$)}.
-
-\add{Similarly, for OLS, PyTracer traces show that the
+although the last singular values stills have a low result precision (below 0).
+According to Equation~\ref{eq:sig-digits}, a number of significant bits less than 0 means that the
+variability ($\sigma$) is higher than the average value ($\mu$).
+
+Similarly, for OLS, PyTracer traces show that the
 regression coefficients fitted are \texttt{NaN} values. By looking at the callgraph, we can
@@
 \texttt{scipy.linalg} package which uses the \texttt{gesdd} LAPACK function.
-    Figure}~\ref{fig:OLS_svd} \add{shows that one singular value is a \texttt{NaN} value,
+Figure~\ref{fig:OLS_svd} shows that one singular value is a \texttt{NaN} value,
 which corrupted the calculation of the coefficients. When using the \texttt{gesvd} method, 
 the \texttt{NaN} value disappears 
-    (Fig.}~\ref{fig:OLS_svd_fixed}\add{), resulting in a \add{result} precision of
+(Fig.~\ref{fig:OLS_svd_fixed}), resulting in a result precision of
 42 bits on average in the coefficients. We can see that having
 access to all the values computed by the application with PyTracer allows
-    the user to efficiently identify numerical issues.}
+the user to efficiently identify numerical issues.
 
@@
 avoid this kind of issue. Thus, \pytracer can detect instabilities that affect
-fundamental scientific computing components such as the LAPACK library. \add{The
+fundamental scientific computing components such as the LAPACK library. The
 unified view of all traces allows the user to quickly navigate through the
-    \add{result} precision of different variables.}
-% The Pytracer findings can therefore be extended to many application domains. %
-% \tristan{conclusion needs to be discussed. Note to self: generaliser un peu la
-% conclusion: pytracer permet de se rendre compte de problemes de stabilite dont
-% plusieurs librairies sont dependantes.}
+result precision of different variables.
 
@@
         and~\ref{fig:randomized_svd_V} show respectively the values $U$,
-        $\Sigma$ and $V$. \add{Result} precision is lower for smaller singular
+        $\Sigma$ and $V$. Result precision is lower for smaller singular
         values and this loss of precision translates to singular vectors. It
@@
     \end{subfigure}
-    \caption{\add{Result} precision of the singular values of the SVD from the
+    \caption{Result precision of the singular values of the SVD from the
         Bayesian Ridge model fitting (left) and from the Ordinary Least Square model
@@
 initialization time to \textit{Slowdown}. We then obtain an average slowdown of
-$3.5\times$. Finally, \remove{the Fuzzy instrumentation} \add{using MCA
-    operations (through Fuzzy) instead of the native ones} increased the average
+$3.5\times$. Finally, \remove{the Fuzzy instrumentation} using MCA
+operations (through Fuzzy) instead of the native ones increased the average
 slowdown to $37\times$\remove{for RR and $43\times$ for Full MCA}.
@@
         instrumentation cost computed by subtracting the initialization step.
-        The \textit{Slowdown (RR)} \remove{and \textit{Slowdown (MCA)} are} \add{is} the slowdown
-        of \pytracer using the Fuzzy environment with \add{the} RR \remove{and Full MCA} mode\remove{s}. The
-        \remove{first} \add{last} four examples measure the initialization
+        The \textit{Slowdown (RR)} is the slowdown
+        of \pytracer using the Fuzzy environment with the RR mode. The
+        last four examples measure the initialization
         steps depending on the modules instrumented. 
@@
 
-\add{\pytracer can be used with different types of numerical perturbations,
+\pytracer can be used with different types of numerical perturbations,
 including random seeds, data noise, or stochastic arithmetic. The
@@
 wraps many computation kernels written in C, such as BLAS or LAPACK, which
-    have a considerable impact on the stability of applications using them.}
-
-\add{
+have a considerable impact on the stability of applications using them.
+
 Enabling Monte-Carlo arithmetic in such non-Python dependencies requires
@@
 large ground of non-Python dependencies encountered in scientific Python programs.
-}
 
@@
 that implements the Monte Carlo Arithmetic (MCA)~\cite{parker1997monte} using
-the MPFR~\cite{fousse2007mpfr} library. \add{ADAPT \mbox{~\cite{menon2018adapt}} uses
+the MPFR~\cite{fousse2007mpfr} library. ADAPT \mbox{~\cite{menon2018adapt}} uses
 Automatic Differentiation to compute a sensitivity profile for each variable in a
-    program}. Finally, the work in~\cite{tang2016software} proposes a
+program. Finally, the work in~\cite{tang2016software} proposes a
 source-to-source framework for executing targeted code in infinite and fixed
@@
 (AST) level to rewrite parts of code with higher precision.
-FPSanitizer~\cite{chowdhary2020debugging,chowdhary2021parallel} \add{and
-    NSan~\mbox{\cite{courbet2021nsan}} are compiler-based approaches}
+FPSanitizer~\cite{chowdhary2020debugging,chowdhary2021parallel} and
+NSan~\mbox{\cite{courbet2021nsan}} are compiler-based approaches
 that use shadow execution to detect numerical issues using higher
@@
 using shadow computations with higher precision.
-Herbgrin\remove{g}\add{d}~\cite{sanchez2017finding} is a Valgrind-based tool to
+Herbgrind~\cite{sanchez2017finding} is a Valgrind-based tool to
 detect numerical instabilities. It uses a shadow memory to detect  precision
-losses by comparison with results obtained \remove{at} \add{in} higher
+losses by comparison with results obtained in higher
 precision. It is combined with symbolic computation to backtrack the root of the
@@
 numerical stability of Python codes. It works by automatically instrumenting
-Python programs to produce traces \add{of numerically-perturbed executions and}
+Python programs to produce traces of numerically-perturbed executions and
 visualize these traces through an interactive Plotly Dash server. \pytracer does
-not require manual code modification. We tested it with \add{Python programs
-    involving} major scientific libraries such as NumPy, SciPy, and Scikit-learn.
+not require manual code modification. We tested it with Python programs
+involving major scientific libraries such as NumPy, SciPy, and Scikit-learn.
 \pytracer enabled the systematic evaluation of 40 examples from the SciPy and
@@
 In the future, we plan to extend the post-processing analysis to aggregate
-traces \add{obtained with different control flow paths,} by leveraging
-techniques used in code coverage analysis. \add{This would also enable larger
-    support for multi-threaded applications.} Moreover, we would like to extend
-\pytracer to instrument elementary arithmetic operations \add{(+,-,*,/), to
-    allow for more detailed analyses}. \remove{Finally, although \pytracer supports
-    multiple noise models, we only tested it with Monte-Carlo arithmetic. Therefore,
-    we would like to compare different models against MCA.}
+traces obtained with different control flow paths, by leveraging
+techniques used in code coverage analysis. This would also enable larger
+support for multi-threaded applications. Moreover, we would like to extend
+\pytracer to instrument elementary arithmetic operations (+,-,*,/), to
+allow for more detailed analyses.
 

### 2022-10-17 IEEEtran/paper.tex
Remove \remove of first review

@@
 
-\remove{Listings~\mbox{\ref{fig:wrapper_creation}} and~\mbox{\ref{fig:generic_wrapper}} show
-    \mbox{\pytracer}'s function instrumentation mechanism.}
 For each function to be instrumented, \pytracer's \texttt{loader} class creates a
@@
 (without \pytracer) and the execution time using \pytracer. The \textit{Slowdown
-    RR} \remove{and \textit{Slowdown MCA}} shows the slowdown within the Fuzzy environment.
+    RR} shows the slowdown within the Fuzzy environment.
 Without Fuzzy, \pytracer introduces an average slowdown of $17\times$ for
@@
 initialization time to \textit{Slowdown}. We then obtain an average slowdown of
-$3.5\times$. Finally, \remove{the Fuzzy instrumentation} using MCA
+$3.5\times$. Finally, using MCA
 operations (through Fuzzy) instead of the native ones increased the average
-slowdown to $37\times$\remove{for RR and $43\times$ for Full MCA}.
+slowdown to $37\times$.
 
@@
 and the log of the time shows a significant correlation (p-value $\leq 10^{-8}$
-\remove{for RR and p-value $\leq 10^{-3}$ for MCA}).
+).
 % \tristan{Mention linear correlation with p-value here.}
@@
 Python data.
-
-\remove{
-    As we showed in Section~\ref{sec:impact_mca_modes}, using Full MCA mode leads to
-    runtime errors that have a considerable impact on the proper functioning of the
-    execution, which is unfortunate since these errors do not reflect actual
-    numerical errors but are related to perturbations that should not occur.
-    Conversely, RR mode is far more conservative since it preserves exact operations
-    and is easier to use even though it does not simulate all perturbations.
-    Therefore, from our experiments, we recommend the use of RR over Full MCA. More
-    research is required to address the issues encountered with Full MCA. 
-}
 

### 2022-10-17 IEEEtran/paper.tex
First edit for 2nd round

@@
 program executions, and (c) visualizing stability
-evaluations. PyTracer addresses this work (a) by relying on
+evaluations. PyTracer addresses \add{this work} (a) by relying on
 Fuzzy~\cite{kiar2020comparing}, an existing collection of scientific
@@
 visualizing stability measures throughout program executions with an
-interactive Plotly dashboard. \mbox{\pytracer} is available at
+interactive Plotly dashboard. \mbox{\pytracer} is available \add{at}
 \mbox{\href{https://github.com/big-data-lab-team/pytracer}{github.com/big-data-lab-team/pytracer}}
-under MIT License.
+(MIT License).
 
@@
 \begin{enumerate}
-    \item It instruments Python programs and their module dependencies
+    \item Instruments Python programs and their module dependencies
           automatically, to save the input and output values of functions in a trace
           file.
-    \item It executes the instrumented program several times using Monte-Carlo
+    \item Executes the instrumented program several times using Monte-Carlo
           Arithmetic to inject perturbations in function outputs.
-    \item It aggregates all trace files to compute statistics about the traced
+    \item Aggregates all trace files to compute statistics about the traced
           values, and visualize them in a GUI.
@@
 \pytracer adopts the workflow shown in Figure~\ref{fig:workflow}.
-In Step 1, \pytracer uses monkey patching to replace the functions called
+In \add{S}tep 1, \pytracer uses monkey patching to replace the functions called
 by the application with a wrapper that saves their arguments and returned
-values in a trace file. In Step 2, it executes the application multiple
+values in a trace file. In \add{S}tep 2, it executes the application multiple
 times with Monte-Carlo Arithmetic as implemented in the
@@
 aggregates the resulting trace files to compute summary statistics on
-traced variables. In Step 3, a Plotly dashboard provides interactive
+traced variables. In \add{S}tep 3, a Plotly dashboard provides interactive
 visualizations highlighting unstable code sections.
@@
 create module objects, initialize them, and fill import-related attributes such
-as \texttt{\_\_spec\_\_}. \texttt{Loaders} then execute modules and populate
+as \texttt{\_\_spec\_\_}; then execute modules and populate
 their namespace. Finally, modules are bound to their import name in the
@@
 returned by an iterator exists in memory since the application computes each
-element on the fly. Therefore, iterators are not serializable which implies that
+element on the fly. Hence, iterators are not serializable which implies that
 \pytracer cannot save them to output traces. A workaround would be to convert
-iterators into explicit containers, however, this would increase the memory
+iterators into explicit containers but this would increase the memory
 footprint significantly. \pytracer, therefore, does not instrument
@@
 applicability of \pytracer. 
-In general, iterators involve simple computations that are unlikely to be
-unstable. In particular, we encountered only a few iterators in our
+Iterators generally involve simple computations that are unlikely to be
+unstable. Besides, we encountered only a few iterators in our
 experiments and none of them involved floating-point values. Should
@@
 simulates roundoff errors by applying function $inexact$ only to the
-output returned by a function. The Precision Bounding (PB) mode that applies
-the $inexact$ function on inputs can
-identify other types of instabilities, in particular catastrophic
+output returned by a function. The Precision Bounding (PB) mode 
+\add{that applies the $inexact$ function on inputs}
+can identify other types of instabilities, in particular catastrophic
 cancellations, however, it is more difficult to apply to large code bases
@@
 variable sampled with MCA. This can be seen as the ratio of signal over noise.
-Sohier et al.~\cite{sohier2021confidence} recently provided a generalization of
-this formula to include confidence intervals.
+\remove{Sohier et al.~\cite{sohier2021confidence} recently provided a generalization of
+    this formula to include confidence intervals.}
 
@@
 should give the exact distribution. While in practice low sample sizes (3 to 30)
-can give good estimates, the issue is to capture ``rare events" that could make the
-computation strongly diverge from the mean. Determining the number of
-MCA samples to use for a given instrumented code is still an open research question.
+can give good estimates, the issue is to capture ``rare events" 
+making the computation to strongly diverge from the mean. 
+Determining the number of MCA samples to use is still an open research question. 
+Recent theoretical works~\cite{sohier2021confidence} on the estimation of 
+significant digits allow computing an associated confidence
+interval depending on the sample size and the underlying
+distribution.
 
@@
 \begin{enumerate}
-    \item Timeline view: This view displays the values of each input and output
+    \item Timeline view: displays the values of each input and output
           for a given function at a given invocation. By default, \pytracer
@@
           (see below).
-    \item Gantt chart view: This view displays the call graph as a Gantt chart
+    \item Gantt chart view: displays the call graph as a Gantt chart
           representing the instrumented functions. Each function call is
@@
           \texttt{function5}. This view provides insights into the calling context
-          for each function, which may influence numerical stability.
-    \item  Source code view: This view displays a local snapshot of the source
+          for each function that may influence numerical stability.
+    \item  Source code view: displays a local snapshot of the source
           code file of the variable hovered in the timeline view.
-    \item Zoom view: This view provides details about non-scalar values. For
+    \item Zoom view: provides details about non-scalar values. For
           example, a matrix may have instabilities around its diagonal but not
@@
           as array shape, infinite norm, or condition number.
-    \item  Functions list view: This view allows the user to select the
+    \item  Functions list view: allows the user to select the
           functions plotted in the timeline view.
@@
 
-Table~\ref{tab:pytracer_results_summary} summarizes \pytracer's outcome on
-SciPy and scikit-learn examples. Columns \textit{trace} and \textit{parse}
-report on the tracing and aggregation steps with two possible outcomes:
-green \valid\xspace for success and red \cross\xspace for error. Tracing errors
-occur in the application as a result of 
-numerical perturbations, whereas parsing errors occur when traces result from different 
-control flow paths.
-Overall, the tracing and parsing of SciPy and scikit-learn examples in Random
-Rounding mode was entirely successful for 32/40 examples.
+Table~\ref{tab:pytracer_results_summary} summarizes \pytracer's outcome on SciPy
+and scikit-learn examples. Columns \textit{trace} and \textit{parse} report on
+the tracing and aggregation steps with two possible outcomes: green
+\valid\xspace for success and red \cross\xspace for error. Tracing errors occur
+in the application as a result of numerical perturbations, whereas parsing
+errors occur when traces result from different control flow paths (CFP). 
+\add{Hence, an application that consistently fails at the same instruction will
+    produce traces with equivalent CFPs which can be parsed by \pytracer as the 
+    Face Recognition shows.}
+
+Overall, the
+tracing and parsing of SciPy and scikit-learn examples in Random Rounding mode
+was entirely successful for 32/40 examples.
 
 Column \textit{sigbits} in Table~\ref{tab:pytracer_results_summary} summarizes
-the result precision for the main outputs of SciPy and scikit-learn examples. We
-measured the result precision in significant bits on the final primary example output
+the result precision for the main outputs of SciPy and scikit-learn examples. 
+We use the term ``result precision"
+to denote the statistical variability measured in the number of significant bits, in 
+contrast with the other meanings of the word precision used in the expressions
+``virtual precision" or ``single/double precision'' in this paper. 
+We measured the result precision in significant bits on the final primary example output
 by taking the element-wise mean for non-scalar values and, if the example
 produced multiple outputs, the average value among them. Significant bits were computed on the final program output
-and could therefore be computed even when parsing failed. We use the term ``result precision"
-to denote the statistical variability measured in the number of significant bits, in 
-contrast with the other meanings of the word precision used in the expressions
-``virtual precision" or ``single/double precision'' in this paper. The numerical
+and could therefore be computed even when parsing failed. 
+The numerical
 quality across all examples varied from 0 to 52, with an average of 44
@@
 and~\ref{fig:fft1D_outputs} show the visualization of the
-\texttt{fft\_1D} input and output values. Results are complex values
+\texttt{fft\_1D} input and output values \add{that} are complex values
 encoded in double precision. PyTracer allows visualizing the
@@
 points) parts. The top row in Figures~\ref{fig:fft1D_inputs}
-and~\ref{fig:fft1D_outputs} show the input mean value while the bottom
+and~\ref{fig:fft1D_outputs} show the input \add{and output} mean value while the bottom
 row shows the standard deviation. Even though Random Rounding
@@
 an interesting pattern that could be further investigated.
-\add{This example shows that \pytracer workds on 2D inputs and the importance of
+\add{This example shows that \pytracer works on 2D inputs and the importance of
     visualizing complex data and not only reporting the values.}
@@
     \centering
-    \includegraphics[width=\linewidth]{figure/FFT/fft_x.pdf}
+    \includegraphics[width=\linewidth]{figure/FFT/fft_x.png}
     \caption{Absolute value of the mean and standard deviation values for fft 1D
@@
     \centering
-    \includegraphics[width=\linewidth]{figure/FFT/fft_y.pdf}
+    \includegraphics[width=\linewidth]{figure/FFT/fft_y.png}
     \caption{Absolute value of the mean and standard deviation values
@@
 
-Replacing \texttt{gesdd} with\texttt{gesvd} solved the SVD convergence issue.
-\pytracer allows us to quickly visualize the new result precision.
+Replacing \texttt{gesdd} \add{with} \texttt{gesvd} solved the SVD convergence issue.
+\pytracer allows \add{us} to quickly visualize the new result precision.
 Figure~\ref{fig:face_recognition_svd} shows the result precision of the eigenvalues
@@
 including the LAPACK repository. Furthermore, it is worth mentioning that a Pull
-Request at \href{https://github.com/scikit-learn/scikit-learn/pull/20617}{github.com/scikit-learn/scikit-learn/pull/20617}
+Request \add{at} \href{https://github.com/scikit-learn/scikit-learn/pull/20617}{github.com/scikit-learn/scikit-learn/pull/20617}
 has recently been submitted in the scikit-learn repository to let the user select the SVD method and
@@
 Figure~\ref{fig:performance_tracing} summarizes \pytracer's tracing overhead for
-SciPy and scikit-learn examples. \textit{Slowdown} represents the slowdown of
-\pytracer without fuzzy measured as the ratio between the actual execution time
-(without \pytracer) and the execution time using \pytracer. The \textit{Slowdown
-    RR} shows the slowdown within the Fuzzy environment.
+SciPy and scikit-learn examples. \textit{Instrumentation and initialization} represents the slowdown of
+\pytracer without fuzzy \add{that corresponds to PyTracer used
+    only for instrumenting Python programs to catch values of function inputs
+    and outputs, but without instrumentation with MCA arithmetic.}
+It is measured as the ratio between the actual execution time
+(without \pytracer) and the execution time using \pytracer. 
+The \textit{Total with RR MCA} shows the slowdown within the Fuzzy environment.
 Without Fuzzy, \pytracer introduces an average slowdown of $17\times$ for
@@
 number of functions instrumented, we also measured the instrumentation cost
-itself (\textit{Slowdown (Instrumentation)}) calculated by subtracting the
-initialization time to \textit{Slowdown}. We then obtain an average slowdown of
+itself (\textit{Instrumentation only}) calculated by subtracting the
+initialization time to \textit{Instrumentation}. We then obtain an average slowdown of
 $3.5\times$. Finally, using MCA
@@
 slowdown to $37\times$.
+Figure~\ref{fig:performance_parsing} shows the postprocessing time and trace
+sizes produced by \pytracer. \add{The p-value $\leq 10^{-8}$ shows a significant
+    correlation between the log of the size and the log of the time.}
 
@@
     \centering
-    \includegraphics[width=\linewidth]{figure/performance.pdf}
+    \includegraphics[width=\linewidth]{figure/performance.png}
     \caption{
@@
 
-Figure~\ref{fig:performance_parsing} shows the postprocessing time and trace
-sizes produced by \pytracer. The linear correlation between the log of the size
-and the log of the time shows a significant correlation (p-value $\leq 10^{-8}$
-).
 % \tristan{Mention linear correlation with p-value here.}
@@
 \pytracer can be used with different types of numerical perturbations,
-including random seeds, data noise, or stochastic arithmetic. The
-use of Verificarlo to implement stochastic arithmetic through the Fuzzy
-environment enables us to study the impact of numerical perturbations
+including random seeds, data noise, or stochastic arithmetic. Using 
+Verificarlo to implement stochastic arithmetic through Fuzzy
+enables \add{us} to study the impact \remove{of} numerical perturbations
 introduced in non-Python dependencies while preserving the high-level view
@@
 \pytracer could be used in regression tests to ensure that updates do not
-degrade the numerical quality of a calculation.
+degrade the numerical quality.
 
@@
 
-% \gkmod{}{Note: this paragraph just reads like a list with no real
-% interpretation/commentary. I think it would be better to state the strengths
-% of this technique, cite examples, and then state limitations/why it isn't the
-% only technique used.}
 The source-to-source technique requires a rewriting of the application to modify
@@
 Automatic Differentiation to compute a sensitivity profile for each variable in a
-program. Finally, the work in~\cite{tang2016software} proposes a
+program. Finally, the work in~\cite{tang2016software} propose\add{s} a
 source-to-source framework for executing targeted code in infinite and fixed

### 2022-10-27 IEEEtran/paper.tex

@@
 SciPy and scikit-learn examples. \textit{Instrumentation and initialization} represents the slowdown of
-\pytracer without fuzzy \add{that corresponds to PyTracer used
-    only for instrumenting Python programs to catch values of function inputs
-    and outputs, but without instrumentation with MCA arithmetic.}
-It is measured as the ratio between the actual execution time
+\pytracer without fuzzy, \add{measured by applying PyTracer to Python programs without Monte-Carlo Arithmetic.}
+The slowdown is measured as the ratio between the actual execution time
 (without \pytracer) and the execution time using \pytracer. 
@@
 slowdown to $37\times$.
-Figure~\ref{fig:performance_parsing} shows the postprocessing time and trace
-sizes produced by \pytracer. \add{The p-value $\leq 10^{-8}$ shows a significant
-    correlation between the log of the size and the log of the time.}
+\add{As shown in Figure~\ref{fig:performance_parsing}, the log aggregation time is linearly correlated with the log trace size (\todo{$R^2$=}, p-value $\leq 10^{-8}$, \todo{Add test name}).}
 

### 2022-10-27 IEEEtran/paper.tex
Fix Tristan's comments

@@
 where $\beta$ is the number base, $e_x$ is the magnitude of $x$, $t$ the virtual
-precision and $\xi \in (-\frac{1}{2},\frac{1}{2})$ is a random uniform variable.
+precision and $\xi\! \in\! (-\frac{1}{2},\frac{1}{2})$ is a random uniform variable.
 Virtual precision allows for the simulation of reduced working precision.
@@
         in number of significant bits. \valid: successful run, \cross: numerical error (tracing) or 
-        different control flow paths (parsing). \textit{nan} stands for (\texttt{Not-A-Number}). 
+        different control flow paths (parsing). \textit{nan} stands for (\texttt{Not-A-Number})
+        \add{meaning that the output result comes from an invalid arithmetic operation}. 
         Example names are linked to their source code.}
@@
 errors occur when traces result from different control flow paths (CFP). 
-\add{Hence, an application that consistently fails at the same instruction will
-    produce traces with equivalent CFPs which can be parsed by \pytracer as the 
-    Face Recognition shows.}
+\add{Therefore, an application that consistently fails at the same function call will
+  produce traces with equivalent Control Flow Paths which can be parsed by \pytracer.
+  In our experiments, this was the case for the Face Recognition shows.}
 
@@
 \add{This example shows that \pytracer works on 2D inputs and the importance of
-    visualizing complex data and not only reporting the values.}
+    visualizing complex data types in addition to summary statistics.}
 
@@
 slowdown to $37\times$.
-\add{As shown in Figure~\ref{fig:performance_parsing}, the log aggregation time is linearly correlated with the log trace size (\todo{$R^2$=}, p-value $\leq 10^{-8}$, \todo{Add test name}).}
+\add{As shown in Figure~\ref{fig:performance_parsing}, the log aggregation time is linearly correlated with the log trace size (F-score=68, p-value $\leq 10^{-8}$, obtained with the F-test for linear regression).}
 

### 2022-10-27 IEEEtran/paper.tex
Fit on 12pages

@@
 slowdown to $37\times$.
-\add{As shown in Figure~\ref{fig:performance_parsing}, the log aggregation time is linearly correlated with the log trace size (F-score=68, p-value $\leq 10^{-8}$, obtained with the F-test for linear regression).}
+\add{As shown in Figure~\ref{fig:performance_parsing}, the log aggregation time is linearly correlated with the log trace size (F-score=68, p-value $\leq 10^{-8}$, F-test for linear regression).}
 

### 2022-11-21 IEEEtran/paper.tex
Final edit before publication

@@
-%% bare_jrnl_compsoc.tex
-%% V1.4b
-%% 2015/08/26
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
+%% bare_jrnl_compsoc.tex % V1.4b % 2015/08/26 % by Michael Shell % See: %
+%http://www.michaelshell.org/ % for current contact information.
 %%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
-%% Computer Society journal paper.
+%% This is a skeleton file demonstrating the use of IEEEtran.cls % (requires
+%IEEEtran.cls version 1.8b or later) with an IEEE % Computer Society journal
+%paper.
 %%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
+%% Support sites: % http://www.michaelshell.org/tex/ieeetran/ %
+%http://www.ctan.org/pkg/ieeetran % and % http://www.ieee.org/
 
 %%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall the IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
+%% Legal Notice: % This code is offered as-is without any warranty either
+%expressed or % implied; without even the implied warranty of MERCHANTABILITY or
+%% FITNESS FOR A PARTICULAR PURPOSE! % User assumes all risk. % In no event
+%shall the IEEE or any contributor to this code be liable for % any damages or
+%losses, including, but not limited to, incidental, % consequential, or any
+%other damages, resulting from the use or misuse % of any information contained
+%here.
 %%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
+%% All comments are the opinions of their respective authors and are not %
+%necessarily endorsed by the IEEE.
 %%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
+%% This work is distributed under the LaTeX Project Public License (LPPL) % (
+%http://www.latex-project.org/ ) version 1.3, and may be freely used, %
+%distributed and modified. A copy of the LPPL, version 1.3, is included % in the
+%base LaTeX documentation of all distributions of LaTeX released % 2003/12/01 or
+%later. % Retain all contribution notices and credits. % ** Modified files
+%should be clearly indicated as such, including  ** % ** renaming them and
+%changing author support contact information. **
 %%*************************************************************************
@@
 % *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
+% *** trigger bugs that do not appear when using other class files.       ***
+% *** The testflow support page is at: http://www.michaelshell.org/tex/testflow/
 
@@
 %
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
+% If IEEEtran.cls has not been installed into the LaTeX system files, manually
+% specify the path to it like:
 % \documentclass[10pt,journal,compsoc]{../sty/IEEEtran}
 
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
+% Some very useful LaTeX packages include: (uncomment the ones you want to load)
 
@@
 %
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
+%\usepackage{ifpdf} Heiko Oberdiek's ifpdf.sty is very useful if you need
+% conditional compilation based on whether the output is pdf or dvi. usage:
+% \ifpdf % pdf code \else % dvi code \fi The latest version of ifpdf.sty can be
+% obtained from: http://www.ctan.org/pkg/ifpdf Also, note that IEEEtran.cls V1.7
+% and later provides a builtin \ifCLASSINFOpdf conditional that works the same
+% way. When switching from latex to pdflatex and vice-versa, the compiler may
 % have to be run twice to clear warning/error messages.
@@
 \ifCLASSOPTIONcompsoc
-  % IEEE Computer Society needs nocompress option
-  % requires cite.sty v4.0 or later (November 2003)
+  % IEEE Computer Society needs nocompress option requires cite.sty v4.0 or
+  % later (November 2003)
   \usepackage[nocompress]{cite}
@@
 \fi
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of the IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/pkg/cite
-% The documentation is contained in the cite.sty file itself.
+% cite.sty was written by Donald Arseneau V1.6 and later of IEEEtran pre-defines
+% the format of the cite.sty package \cite{} output to follow that of the IEEE.
+% Loading the cite package will result in citation numbers being automatically
+% sorted and properly "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6]
+% without using cite.sty will become [1], [2], [5]--[7], [9] using cite.sty.
+% cite.sty's \cite will automatically add leading space, if needed. Use
+% cite.sty's noadjust option (cite.sty V3.8 and later) if you want to turn this
+% off such as if a citation ever needs to be enclosed in parenthesis. cite.sty
+% is already installed on most LaTeX systems. Be sure and use version 5.0
+% (2009-03-20) and later if using hyperref.sty. The latest version can be
+% obtained at: http://www.ctan.org/pkg/cite The documentation is contained in
+% the cite.sty file itself.
 %
@@
 % Society requires. In particular, Computer Society  papers do not use
-% compressed citation ranges as is done in typical IEEE papers
-% (e.g., [1]-[4]). Instead, they list every citation separately in order
-% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
-% package with the nocompress option which is supported by cite.sty v4.0
-% and later. Note also the use of a CLASSOPTION conditional provided by
-% IEEEtran.cls V1.7 and later.
+% compressed citation ranges as is done in typical IEEE papers (e.g., [1]-[4]).
+% Instead, they list every citation separately in order (e.g., [1], [2], [3],
+% [4]). To get the latter we need to load the cite package with the nocompress
+% option which is supported by cite.sty v4.0 and later. Note also the use of a
+% CLASSOPTION conditional provided by IEEEtran.cls V1.7 and later.
 
@@
 \ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
+  % \usepackage[pdftex]{graphicx} declare the path(s) where your graphic files
+  % are \graphicspath{{../pdf/}{../jpeg/}} and their extensions so you won't
+  % have to specify these with every instance of \includegraphics
   % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
 \else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
+  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx will
+  % default to the driver specified in the system graphics.cfg if no driver is
+  % specified. \usepackage[dvips]{graphicx} declare the path(s) where your
+  % graphic files are \graphicspath{{../eps/}} and their extensions so you won't
+  % have to specify these with every instance of \includegraphics
   % \DeclareGraphicsExtensions{.eps}
 \fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at: 
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
+% graphicx was written by David Carlisle and Sebastian Rahtz. It is required if
+% you want graphics, photos, etc. graphicx.sty is already installed on most
+% LaTeX systems. The latest version and documentation can be obtained at:
+% http://www.ctan.org/pkg/graphicx Another good source of documentation is
+% "Using Imported Graphics in LaTeX2e" by Keith Reckdahl which can be found at:
 % http://www.ctan.org/pkg/epslatex
 %
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
+% latex, and pdflatex in dvi mode, support graphics in encapsulated postscript
+% (.eps) format. pdflatex in pdf mode supports graphics in .pdf, .jpeg, .png and
+% .mps (metapost) formats. Users should ensure that all non-photo figures use a
+% vector format (.eps, .pdf, .mps) and not a bitmapped formats (.jpeg, .png).
+% The IEEE frowns on bitmapped formats which can result in "jaggedy"/blurry
+% rendering of lines and letters as well as large increases in file sizes.
 %
@@
 %
-%\usepackage{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-%
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
+%\usepackage{amsmath} A popular package from the American Mathematical Society
+% that provides many useful and powerful commands for dealing with mathematics.
+%
+% Note that the amsmath package sets \interdisplaylinepenalty to 10000 thus
+% preventing page breaks from occurring within multiline equations. Use:
+% \interdisplaylinepenalty=2500 after loading amsmath to restore such page
+% breaks as IEEEtran.cls normally does. amsmath.sty is already installed on most
+% LaTeX systems. The latest version and documentation can be obtained at:
 % http://www.ctan.org/pkg/amsmath
@@
 %
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
+%\usepackage{algorithmic} algorithmic.sty was written by Peter Williams and
+% Rogerio Brito. This package provides an algorithmic environment fo describing
+% algorithms. You can use the algorithmic environment in-text or within a figure
 % environment to provide for a floating algorithm. Do NOT use the algorithm
@@
 % algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
+% algorithm float types and packages that provide these will not provide correct
+% IEEE style captions. The latest version and documentation of algorithmic.sty
+% can be obtained at: http://www.ctan.org/pkg/algorithms Also of interest may be
+% the (relatively newer and more customizable) algorithmicx.sty package by Szasz
+% Janos: http://www.ctan.org/pkg/algorithmicx
 
@@
 %
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
+%\usepackage{array} Frank Mittelbach's and David Carlisle's array.sty patches
+% and improves the standard LaTeX2e array and tabular environments to provide
+% better appearance and additional user controls. As the default LaTeX2e table
+% generation code is lacking to the point of almost being broken with respect to
+% the quality of the end results, all users are strongly advised to use an
+% enhanced (at the very least that provided by array.sty) set of table tools.
+% array.sty is already installed on most systems. The latest version and
+% documentation can be obtained at: http://www.ctan.org/pkg/array
 
@@
 
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a sans serif font rather
-% than the serif font used in traditional IEEE formatting and thus the need
-% to invoke different subfig.sty package options depending on whether
-% compsoc mode has been enabled.
+% *** SUBFIGURE PACKAGES *** \ifCLASSOPTIONcompsoc
+%\usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
+%\else \usepackage[caption=false,font=footnotesize]{subfig} \fi subfig.sty,
+%written by Steven Douglas Cochran, is the modern replacement for subfigure.sty,
+%the latter of which is no longer maintained and is incompatible with some LaTeX
+%packages including fixltx2e. However, subfig.sty requires and automatically
+%loads Axel Sommerfeldt's caption.sty which will override IEEEtran.cls' handling
+%of captions and this will result in non-IEEE style figure/table captions. To
+%prevent this problem, be sure and invoke subfig.sty's "caption=false" package
+%option (available since subfig.sty version 1.3, 2005/06/28) as this is will
+%preserve IEEEtran.cls handling of captions. Note that the Computer Society
+%format requires a sans serif font rather than the serif font used in
+%traditional IEEE formatting and thus the need to invoke different subfig.sty
+%package options depending on whether compsoc mode has been enabled.
 %
@@
 %
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
+%\usepackage{fixltx2e} fixltx2e, the successor to the earlier fix2col.sty, was
+% written by Frank Mittelbach and David Carlisle. This package corrects a few
+% problems in the LaTeX2e kernel, the most notable of which is that in current
 % LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
+% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a single
+% column figure to be placed prior to an earlier double column figure. Be aware
+% that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's corrections
+% already built into the system in which case a warning will be issued if an
+% attempt is made to load fixltx2e.sty as it is no longer needed. The latest
+% version and documentation can be found at: http://www.ctan.org/pkg/fixltx2e
+
+%\usepackage{stfloats} stfloats.sty was written by Sigitas Tolusis. This package
+% gives LaTeX2e the ability to do double column floats at the bottom of the page
+% as well as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
+% LaTeX2e). It also provides a command: \fnbelowfloat to enable the placement of
+% footnotes below bottom floats (the standard LaTeX2e kernel puts them above
+% bottom floats). This is an invasive package which rewrites many portions of
+% the LaTeX2e float routines. It may not work with other packages that modify
+% the LaTeX2e float routines. The latest version and documentation can be
+% obtained at: http://www.ctan.org/pkg/stfloats Do not use the stfloats
+% baselinefloat ability as the IEEE does not allow \baselineskip to stretch.
+% Authors submitting work to the IEEE should note that the IEEE rarely uses
+% double column equations and that authors should try to avoid such use. Do not
+% be tempted to use the cuted.sty or midfloat.sty packages (also by Sigitas
+% Tolusis) as the IEEE does not format its papers in such ways. Do not attempt
+% to use stfloats with fixltx2e as they are incompatible. Instead, use Morten
+% Hogholm'a dblfloatfix which combines the features of both fixltx2e and
+% stfloats:
+%
+% \usepackage{dblfloatfix} The latest version can be found at:
 % http://www.ctan.org/pkg/dblfloatfix
 
-%\ifCLASSOPTIONcaptionsoff
-%  \usepackage[nomarkers]{endfloat}
+%\ifCLASSOPTIONcaptionsoff \usepackage[nomarkers]{endfloat}
 %  \let\MYoriglatexcaption\caption
-% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
-%\fi
-% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
-% Axel Sommerfeldt. This package may be useful when used in conjunction with 
+%  \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}} \fi
+%  endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and Axel
+%  Sommerfeldt. This package may be useful when used in conjunction with
 %  IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
 %  submissions have lists of figures/tables at the end of the paper and that
-% figures/tables without any captions are placed on a page by themselves at
-% the end of the document. If needed, the draftcls IEEEtran class option or
-% \CLASSINPUTbaselinestretch interface can be used to increase the line
-% spacing as well. Be sure and use the nomarkers option of endfloat to
-% prevent endfloat from "marking" where the figures would have been placed
-% in the text. The two hack lines of code above are a slight modification of
-% that suggested by in the endfloat docs (section 8.4.1) to ensure that
-% the full captions always appear in the list of figures/tables - even if
-% the user used the short optional argument of \caption[]{}.
-% IEEE papers do not typically make use of \caption[]'s optional argument,
-% so this should not be an issue. A similar trick can be used to disable
-% captions of packages such as subfig.sty that lack options to turn off
-% the subcaptions:
-% For subfig.sty:
+%  figures/tables without any captions are placed on a page by themselves at the
+%  end of the document. If needed, the draftcls IEEEtran class option or
+%  \CLASSINPUTbaselinestretch interface can be used to increase the line spacing
+%  as well. Be sure and use the nomarkers option of endfloat to prevent endfloat
+%  from "marking" where the figures would have been placed in the text. The two
+%  hack lines of code above are a slight modification of that suggested by in
+%  the endfloat docs (section 8.4.1) to ensure that the full captions always
+%  appear in the list of figures/tables - even if the user used the short
+%  optional argument of \caption[]{}. IEEE papers do not typically make use of
+%  \caption[]'s optional argument, so this should not be an issue. A similar
+%  trick can be used to disable captions of packages such as subfig.sty that
+%  lack options to turn off the subcaptions: For subfig.sty:
 %  \let\MYorigsubfloat\subfloat
-% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
-% However, the above trick will not work if both optional arguments of
-% the \subfloat command are used. Furthermore, there needs to be a
-% description of each subfigure *somewhere* and endfloat does not add
-% subfigure captions to its list of figures. Thus, the best approach is to
-% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
-% and instead reference/explain all the subfigures within the main caption.
-% The latest version of endfloat.sty and its documentation can obtained at:
-% http://www.ctan.org/pkg/endfloat
-%
-% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
-% later in the document, say, to conditionally put the References on a 
-% page by themselves.
+%  \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}} However, the above
+%  trick will not work if both optional arguments of the \subfloat command are
+%  used. Furthermore, there needs to be a description of each subfigure
+%  *somewhere* and endfloat does not add subfigure captions to its list of
+%  figures. Thus, the best approach is to avoid the use of subfigure captions
+%  (many IEEE journals avoid them anyway) and instead reference/explain all the
+%  subfigures within the main caption. The latest version of endfloat.sty and
+%  its documentation can obtained at: http://www.ctan.org/pkg/endfloat
+%
+% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used later in
+% the document, say, to conditionally put the References on a page by
+% themselves.
 
@@
 %
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
+%\usepackage{url} url.sty was written by Donald Arseneau. It provides better
+% support for handling and breaking URLs. url.sty is already installed on most
+% LaTeX systems. The latest version and documentation can be obtained at:
+% http://www.ctan.org/pkg/url Basically, \url{my_url_here}.
+
+% *** Do not adjust lengths that control margins, column widths, etc. *** *** Do
+% not use packages that alter fonts (such as pslatex).         *** There should
+% be no need to do such things with IEEEtran.cls V1.6 and later. (Unless
+% specifically asked to do so by the journal or conference you plan to submit
+% to, of course. )
 
@@
 \newcommand{\na}[0]{\cellcolor{gray!25}}
-\newcommand{\s}[1]{\cellcolor{cyan!25}#1}
-\newcommand{\scross}[0]{\ding{53}~}
+\newcommand{\s}[1]{\cellcolor{cyan!25}#1} \newcommand{\scross}[0]{\ding{53}~}
 \newcommand{\svalid}[0]{\ding{51}~}
@@
 \usepackage{ifthen}
-\newif\ifANNOTATED
-\ifthenelse{\equal{\detokenize{annotated}}{\jobname}}{
-\ANNOTATEDtrue
-}{
-\ANNOTATEDfalse
-}
+\newif\ifANNOTATED \ifthenelse{\equal{\detokenize{annotated}}{\jobname}}{
+\ANNOTATEDtrue }{ \ANNOTATEDfalse }
 
@@
 \else
-\DeclareRobustCommand{\add}[1]{#1}
-\DeclareRobustCommand{\remove}[1]{}
+\DeclareRobustCommand{\add}[1]{#1} \DeclareRobustCommand{\remove}[1]{}
 \DeclareRobustCommand{\addCite}[1]{#1}
@@
 \newcommand{\thickhline}{%
-    \noalign {\ifnum 0=`}\fi \hrule height 1pt
-    \futurelet \reserved@a \@xhline
-}
+    \noalign {\ifnum 0=`}\fi \hrule height 1pt \futurelet \reserved@a \@xhline }
     \newcolumntype{"}{@{\hskip\tabcolsep\vrule width 1pt\hskip\tabcolsep}}
@@
 
-\lstdefinestyle{customPython}{
-  belowcaptionskip=1\baselineskip,
-  breaklines=true,
-  xleftmargin=\parindent,
-  language=Python,
-  showstringspaces=false,
-  basicstyle=\scriptsize\ttfamily,
-  keywordstyle=\bfseries\color[rgb]{0.580, 0.000, 0.827},
+\lstdefinestyle{customPython}{ belowcaptionskip=1\baselineskip, breaklines=true,
+  xleftmargin=\parindent, language=Python, showstringspaces=false,
+  basicstyle=\scriptsize\ttfamily, keywordstyle=\bfseries\color[rgb]{0.580,
+  0.000, 0.827},
   %{purple!40!lightgray},
   commentstyle=\itshape\color{green!40!black},
-  identifierstyle=\bfseries\color{cyan!75!black},
-  stringstyle=\color{orange},
-  deletekeywords={double,float},
-  classoffset=1, % starting new class
-  otherkeywords={double,float},
-  morekeywords={double,float},
-  keywordstyle=\bfseries\color{green!55!black},
-  classoffset=0
-}
-
-\lstdefinestyle{customC}{
-  belowcaptionskip=1\baselineskip,
-  breaklines=true,
-  xleftmargin=\parindent,
-  language=C,
-  showstringspaces=false,
-  basicstyle=\scriptsize\ttfamily,
-  keywordstyle=\bfseries\color[rgb]{0.580, 0.000, 0.827},
+  identifierstyle=\bfseries\color{cyan!75!black}, stringstyle=\color{orange},
+  deletekeywords={double,float}, classoffset=1, % starting new class
+  otherkeywords={double,float}, morekeywords={double,float},
+  keywordstyle=\bfseries\color{green!55!black}, classoffset=0 }
+
+\lstdefinestyle{customC}{ belowcaptionskip=1\baselineskip, breaklines=true,
+  xleftmargin=\parindent, language=C, showstringspaces=false,
+  basicstyle=\scriptsize\ttfamily, keywordstyle=\bfseries\color[rgb]{0.580,
+  0.000, 0.827},
   %{purple!40!lightgray},
   commentstyle=\itshape\color{green!40!black},
-  identifierstyle=\bfseries\color{cyan!75!black},
-  stringstyle=\color{orange},
-  deletekeywords={double,float},
-  classoffset=1, % starting new class
-  otherkeywords={double,float},
-  morekeywords={double,float},
-  keywordstyle=\bfseries\color{green!55!black},
-  classoffset=0
-}
+  identifierstyle=\bfseries\color{cyan!75!black}, stringstyle=\color{orange},
+  deletekeywords={double,float}, classoffset=1, % starting new class
+  otherkeywords={double,float}, morekeywords={double,float},
+  keywordstyle=\bfseries\color{green!55!black}, classoffset=0 }
 
@@
 %
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
+% paper title Titles are generally capitalized except for words such as a, an,
+% and, as, at, but, by, for, in, nor, of, on, or, the, to and up, which are
+% usually not capitalized unless they are the first or last word of the title.
+% Linebreaks \\ can be used within to get better formatting as desired. Do not
+% put math or special symbols in the title.
 \title{PyTracer: Automatically Profiling Numerical Instabilities in Python}
@@
 %
-% author names and IEEE memberships
-% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
-% a structure at a ~ so this keeps an author's name from being broken across
-% two lines.
-% use \thanks{} to gain access to the first footnote area
-% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
-% was not built to handle multiple paragraphs
-%
-%
-%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
-% lists the Computer Society journals use for "first footnote" author
-% affiliations. Use \IEEEcompsocthanksitem which works much like \item
-% for each affiliation group. When not in compsoc mode,
-% \IEEEcompsocitemizethanks becomes like \thanks and
-% \IEEEcompsocthanksitem becomes a line break with idention. This
+% author names and IEEE memberships note positions of commas and nonbreaking
+% spaces ( ~ ) LaTeX will not break a structure at a ~ so this keeps an author's
+% name from being broken across two lines. use \thanks{} to gain access to the
+% first footnote area a separate \thanks must be used for each paragraph as
+% LaTeX2e's \thanks was not built to handle multiple paragraphs
+%
+%
+%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted lists
+% the Computer Society journals use for "first footnote" author affiliations.
+% Use \IEEEcompsocthanksitem which works much like \item for each affiliation
+% group. When not in compsoc mode, \IEEEcompsocitemizethanks becomes like
+% \thanks and \IEEEcompsocthanksitem becomes a line break with idention. This
 % facilitates dual compilation, although admittedly the differences in the
 % desired content of \author between the different types of papers makes a
-% one-size-fits-all approach a daunting prospect. For instance, compsoc 
-% journal papers have the author affiliations above the "Manuscript
-% received ..."  text while in non-compsoc journals this is reversed. Sigh.
-
-\author{Yohan Chatelain$^1$, Nigel Yong Sao Young$^1$,  Gregory Kiar$^2$,  Tristan Glatard$^1$\\
-    $^1$Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada\\
-    $^2$Center for the Developing Brain, Child Mind Institute, New York, NY, USA}
-%% \author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
-%%         John~Doe,~\IEEEmembership{Fellow,~OSA,}
-%%         and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
-%% \IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M. Shell was with the Department
-%% of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
-%% GA, 30332.\protect\\
-%% % note need leading \protect in front of \\ to get a newline within \thanks as
-%% % \\ is fragile and will error, could use \hfil\break instead.
-%% E-mail: see http://www.michaelshell.org/contact.html
-%% \IEEEcompsocthanksitem J. Doe and J. Doe are with Anonymous University.}% <-this % stops an unwanted space
-%% \thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
-
-% note the % following the last \IEEEmembership and also \thanks - 
-% these prevent an unwanted space from occurring between the last author name
-% and the end of the author line. i.e., if you had this:
+% one-size-fits-all approach a daunting prospect. For instance, compsoc journal
+% papers have the author affiliations above the "Manuscript received ..."  text
+% while in non-compsoc journals this is reversed. Sigh.
+
+\author{Yohan Chatelain$^1$, Nigel Yong Sao Young$^1$,  Gregory Kiar$^2$,
+    Tristan Glatard$^1$\\
+    $^1$Department of Computer Science and Software Engineering, Concordia
+    University, Montreal, Canada\\
+    $^2$Center for the Developing Brain, Child Mind Institute, New York, NY,
+    USA}
+%% \author{Michael~Shell,~\IEEEmembership{Member,~IEEE,} %
+%John~Doe,~\IEEEmembership{Fellow,~OSA,} %
+%and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space %
+%\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M. Shell was with the
+%Department % of Electrical and Computer Engineering, Georgia Institute of
+%Technology, Atlanta, % GA, 30332.\protect\\
+%% % note need leading \protect in front of \\ to get a newline within \thanks
+%as % % \\ is fragile and will error, could use \hfil\break instead. % E-mail:
+%see http://www.michaelshell.org/contact.html % \IEEEcompsocthanksitem J. Doe
+%and J. Doe are with Anonymous University.}% <-this % stops an unwanted space %
+%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
+
+% note the % following the last \IEEEmembership and also \thanks - these prevent
+% an unwanted space from occurring between the last author name and the end of
+% the author line. i.e., if you had this:
 %
@@
 % line to be shifted left slightly. This is one of those "LaTeX things". For
-% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
-% "AB" then you have to do: "\textbf{A}\textbf{B}"
-% \thanks is no different in this regard, so shield the last } of each \thanks
-% that ends a line with a % and do not let a space in before the next \thanks.
-% Spaces after \IEEEmembership other than the last one are OK (and needed) as
-% you are supposed to have spaces between the names. For what it is worth,
-% this is a minor point as most people would not even notice if the said evil
-% space somehow managed to creep in.
+% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get "AB"
+% then you have to do: "\textbf{A}\textbf{B}" \thanks is no different in this
+% regard, so shield the last } of each \thanks that ends a line with a % and do
+% not let a space in before the next \thanks. Spaces after \IEEEmembership other
+% than the last one are OK (and needed) as you are supposed to have spaces
+% between the names. For what it is worth, this is a minor point as most people
+% would not even notice if the said evil space somehow managed to creep in.
 
@@
 \markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
-{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
+{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer
+    Society Journals}
 % The only time the second header will appear is for the odd numbered pages
@@
 %
-% *** Note that you probably will NOT want to include the author's ***
-% *** name in the headers of peer review papers.                   ***
-% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
-% you desire.
+% *** Note that you probably will NOT want to include the author's *** *** name
+% in the headers of peer review papers.                   *** You can use
+% \ifCLASSOPTIONpeerreview for conditional compilation here if you desire.
 
 % The publisher's ID mark at the bottom of the page is less important with
-% Computer Society journal papers as those publications place the marks
-% outside of the main text columns and, therefore, unlike regular IEEE
-% journals, the available text space is not reduced by their presence.
-% If you want to put a publisher's ID mark on the page you can do it like
-% this:
-%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
-% or like this to get the Computer Society new two part style.
-%\IEEEpubid{\makebox[\columnwidth]{\hfill 0000--0000/00/\$00.00~\copyright~2015 IEEE}%
-%\hspace{\columnsep}\makebox[\columnwidth]{Published by the IEEE Computer Society\hfill}}
-% Remember, if you use this you must call \IEEEpubidadjcol in the second
-% column for its text to clear the IEEEpubid mark (Computer Society jorunal
-% papers don't need this extra clearance.)
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
+% Computer Society journal papers as those publications place the marks outside
+% of the main text columns and, therefore, unlike regular IEEE journals, the
+% available text space is not reduced by their presence. If you want to put a
+% publisher's ID mark on the page you can do it like this:
+% \IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE} or like this to get the
+% Computer Society new two part style. \IEEEpubid{\makebox[\columnwidth]{\hfill
+% 0000--0000/00/\$00.00~\copyright~2015 IEEE}%
+% \hspace{\columnsep}\makebox[\columnwidth]{Published by the IEEE Computer
+% Society\hfill}} Remember, if you use this you must call \IEEEpubidadjcol in
+% the second column for its text to clear the IEEEpubid mark (Computer Society
+% jorunal papers don't need this extra clearance.)
+
+% use for special paper notices \IEEEspecialpapernotice{(Invited Paper)}
 
 % for Computer Society papers, we must declare the abstract and index terms
-% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
-% command as these need to go into the title area created by \maketitle.
-% As a general rule, do not put math, special symbols or citations
-% in the abstract or keywords.
+% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran command as
+% these need to go into the title area created by \maketitle. As a general rule,
+% do not put math, special symbols or citations in the abstract or keywords.
 \IEEEtitleabstractindextext{%
@@
 % To allow for easy dual compilation without having to reenter the
-% abstract/keywords data, the \IEEEtitleabstractindextext text will
-% not be used in maketitle, but will appear (i.e., to be "transported")
-% here as \IEEEdisplaynontitleabstractindextext when the compsoc 
-% or transmag modes are not selected <OR> if conference mode is selected 
-% - because all conference papers position the abstract like regular
-% papers do.
+% abstract/keywords data, the \IEEEtitleabstractindextext text will not be used
+% in maketitle, but will appear (i.e., to be "transported") here as
+% \IEEEdisplaynontitleabstractindextext when the compsoc or transmag modes are
+% not selected <OR> if conference mode is selected
+% - because all conference papers position the abstract like regular papers do.
 \IEEEdisplaynontitleabstractindextext
-% \IEEEdisplaynontitleabstractindextext has no effect when using
-% compsoc or transmag under a non-conference mode.
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
+% \IEEEdisplaynontitleabstractindextext has no effect when using compsoc or
+% transmag under a non-conference mode.
+
+% For peer review papers, you can put extra information on the cover page as
+% needed: \ifCLASSOPTIONpeerreview \begin{center} \bfseries EDICS Category:
+% 3-BBND \end{center} \fi
+%
+% For peerreview papers, this IEEEtran command inserts a page break and creates
+% the second title. It will be ignored for other modes.
 \IEEEpeerreviewmaketitle
@@
 % with the very first section heading (almost always called "Introduction").
-% They place it ABOVE the main text! IEEEtran.cls does not automatically do
-% this for you, but you can achieve this effect with the provided
-% \IEEEraisesectionheading{} command. Note the need to keep any \label that
-% is to refer to the section immediately after \section in the above as
+% They place it ABOVE the main text! IEEEtran.cls does not automatically do this
+% for you, but you can achieve this effect with the provided
+% \IEEEraisesectionheading{} command. Note the need to keep any \label that is
+% to refer to the section immediately after \section in the above as
 % \IEEEraisesectionheading puts \section within a raised box.
@@
 processing. In unstable analyses, small numerical perturbations introduced by
-data noise, software and hardware updates, or parallelization have the potential to
-introduce substantial deviations in final results, leading to potentially
+data noise, software and hardware updates, or parallelization have the potential
+to introduce substantial deviations in final results, leading to potentially
 different scientific conclusions, ultimately threatening the reliability of
@@
 Python programs. \pytracer adopts a dynamic approach that evaluates numerical
-stability using program execution traces and applies to large programs
-without manual intervention. The transparent nature of \pytracer is particularly
+stability using program execution traces and applies to large programs without
+manual intervention. The transparent nature of \pytracer is particularly
 valuable in contrast to theoretical approaches based on condition numbers or
-backward error analysis~\cite{higham2002accuracy}, which require
-detailed modeling of the program and its numerical implementation. Similarly,
-static code analysis techniques~\cite{goubault2006static} hardly scale
-to large codebases, particularly in dynamically-typed languages such as Python.
-
-\pytracer estimates the variability of floating-point variables by
-combining program traces obtained with different numerical perturbations,
-which requires (a) generating numerically-perturbed
-executions, (b) tracing floating-point computations along with
-program executions, and (c) visualizing stability
-evaluations. PyTracer addresses \add{this work} (a) by relying on
-Fuzzy~\cite{kiar2020comparing}, an existing collection of scientific
-computing libraries instrumented with Monte-Carlo arithmetic through the
-Verificarlo tool~\cite{verificarlo}, (b) by dynamically instrumenting
-Python functions, modules, and classes through meta-programming, and (c) by
-visualizing stability measures throughout program executions with an
-interactive Plotly dashboard. \mbox{\pytracer} is available \add{at}
+backward error analysis~\cite{higham2002accuracy}, which require detailed
+modeling of the program and its numerical implementation. Similarly, static code
+analysis techniques~\cite{goubault2006static} hardly scale to large codebases,
+particularly in dynamically-typed languages such as Python.
+
+\pytracer estimates the variability of floating-point variables by combining
+program traces obtained with different numerical perturbations, which requires
+(a) generating numerically-perturbed executions, (b) tracing floating-point
+computations along with program executions, and (c) visualizing stability
+evaluations. PyTracer addresses this work (a) by relying on
+Fuzzy~\cite{kiar2020comparing}, an existing collection of scientific computing
+libraries instrumented with Monte-Carlo arithmetic through the Verificarlo
+tool~\cite{verificarlo}, (b) by dynamically instrumenting Python functions,
+modules, and classes through meta-programming, and (c) by visualizing stability
+measures throughout program executions with an interactive Plotly dashboard.
+\mbox{\pytracer} is available at
 \mbox{\href{https://github.com/big-data-lab-team/pytracer}{github.com/big-data-lab-team/pytracer}}
@@
 
-This manuscript presents the design of \pytracer and highlights its potential
-in various use cases. Through stability evaluations of the SciPy and
-scikit-learn libraries, we demonstrate \pytracer as a practical solution to
-review the numerical stability of extensive code bases.
+This manuscript presents the design of \pytracer and highlights its potential in
+various use cases. Through stability evaluations of the SciPy and scikit-learn
+libraries, we demonstrate \pytracer as a practical solution to review the
+numerical stability of extensive code bases.
 
@@
     \item Instruments Python programs and their module dependencies
-          automatically, to save the input and output values of functions in a trace
-          file.
+          automatically, to save the input and output values of functions in a
+          trace file.
     \item Executes the instrumented program several times using Monte-Carlo
@@
 \end{enumerate}
-\pytracer adopts the workflow shown in Figure~\ref{fig:workflow}.
-In \add{S}tep 1, \pytracer uses monkey patching to replace the functions called
-by the application with a wrapper that saves their arguments and returned
-values in a trace file. In \add{S}tep 2, it executes the application multiple
-times with Monte-Carlo Arithmetic as implemented in the
-Fuzzy~\cite{kiar2020comparing} environment. It then
-aggregates the resulting trace files to compute summary statistics on
-traced variables. In \add{S}tep 3, a Plotly dashboard provides interactive
-visualizations highlighting unstable code sections.
-
-The remainder of this section assumes some knowledge of Python concepts
-such as classes, functions, modules, decorators, callables, and iterators.
-We refer to~\cite{beazley2013python} for a detailed presentation of these
-concepts.
+\pytracer adopts the workflow shown in Figure~\ref{fig:workflow}. In Step
+1, \pytracer uses monkey patching to replace the functions called by the
+application with a wrapper that saves their arguments and returned values in a
+trace file. In Step 2, it executes the application multiple times with
+Monte-Carlo Arithmetic as implemented in the Fuzzy~\cite{kiar2020comparing}
+environment. It then aggregates the resulting trace files to compute summary
+statistics on traced variables. In Step 3, a Plotly dashboard provides
+interactive visualizations highlighting unstable code sections.
+
+The remainder of this section assumes some knowledge of Python concepts such as
+classes, functions, modules, decorators, callables, and iterators. We refer
+to~\cite{beazley2013python} for a detailed presentation of these concepts.
 
@@
     \caption{Pytracer workflow
-        % \gkmod{}{Note: replace "Execution" with "Multiple Independent
-        % Executions", and maybe move it to be between the gears and the pkl
-        % files.}
     }
@@
 \subsection{Python code instrumentation}
-
-%\tristan{``Instrumentation" should appear in Figure 1}
 
@@
 application can transparently use it.
-% \gkmod{}{Note: this form of monkey patching is basically global and
-% transparent decorating, right?} \Yohan{Yes}
 By default, \pytracer instruments all the attributes in a given module except
@@
 Python methods. However, some attributes are not writable. In this case,
-\pytracer preserves the original attributes and warns
-the user. The user can also restrict the list of traced attributes through an
-inclusion/exclusion mechanism. The main advantage of this instrumentation
-approach is the lack of required modification in the application source code, in
-contrast with  a decorator-based approach~\mbox{\cite{hunt2019decorators}}. 
-In addition, this technique is
-scalable and applicable in read-only environments such as Singularity containers
-or HPC clusters.
+\pytracer preserves the original attributes and warns the user. The user can
+also restrict the list of traced attributes through an inclusion/exclusion
+mechanism. The main advantage of this instrumentation approach is the lack of
+required modification in the application source code, in contrast with  a
+decorator-based approach~\mbox{\cite{hunt2019decorators}}. In addition, this
+technique is scalable and applicable in read-only environments such as
+Singularity containers or HPC clusters.
 
@@
 create module objects, initialize them, and fill import-related attributes such
-as \texttt{\_\_spec\_\_}; then execute modules and populate
-their namespace. Finally, modules are bound to their import name in the
-\texttt{sys.modules} dictionary.
+as \texttt{\_\_spec\_\_}; then execute modules and populate their namespace.
+Finally, modules are bound to their import name in the \texttt{sys.modules}
+dictionary.
 
@@
 
-\pytracer's \texttt{loader} class first loads the original module and then copies
-it as a new instance of the \texttt{ModuleType} class. It then calls the
+\pytracer's \texttt{loader} class first loads the original module and then
+copies it as a new instance of the \texttt{ModuleType} class. It then calls the
 appropriate instrumentation function for each attribute depending on its type
@@
 
-For each function to be instrumented, \pytracer's \texttt{loader} class creates a
-wrapper function, dynamically compiles it with the \texttt{compile} builtin
+For each function to be instrumented, \pytracer's \texttt{loader} class creates
+a wrapper function, dynamically compiles it with the \texttt{compile} builtin
 function, and substitutes it for the original module function.  Although simple,
@@
 overcome this issue. When the \texttt{\_\_call\_\_} attribute is not writable,
-Pytracer does not instrument the class and returns a warning. 
-This limitation is expected to have a minor impact in practice since non-writable
-classes are usually called from pure Python classes that can be
-instrumented. Therefore, \pytracer reports information about the stability of
-non-writable classes through the instrumentation of the pure Python
-classes that use them.
+Pytracer does not instrument the class and returns a warning. This limitation is
+expected to have a minor impact in practice since non-writable classes are
+usually called from pure Python classes that can be instrumented. Therefore,
+\pytracer reports information about the stability of non-writable classes
+through the instrumentation of the pure Python classes that use them.
 
@@
 \pytracer cannot save them to output traces. A workaround would be to convert
-iterators into explicit containers but this would increase the memory
-footprint significantly. \pytracer, therefore, does not instrument
-iterators.
-
-We do not expect this limitation to have a critical impact on the
-applicability of \pytracer. 
-Iterators generally involve simple computations that are unlikely to be
-unstable. Besides, we encountered only a few iterators in our
-experiments and none of them involved floating-point values. Should
-instabilities occur in iterators, \pytracer would detect them through the
-inputs of the functions consuming these iterators.
+iterators into explicit containers but this would increase the memory footprint
+significantly. \pytracer, therefore, does not instrument iterators.
+
+We do not expect this limitation to have a critical impact on the applicability
+of \pytracer. Iterators generally involve simple computations that are unlikely
+to be unstable. Besides, we encountered only a few iterators in our experiments
+and none of them involved floating-point values. Should instabilities occur in
+iterators, \pytracer would detect them through the inputs of the functions
+consuming these iterators.
 
@@
 
-Three  main  approaches  exist  to  detect  numerical  instabilities:
-stochastic  arithmetic,  uncertainty  or  sensitivity analysis~\cite{helton2006survey}, and random
-seed analysis~\cite{hellekalek1998good}. PyTracer is agnostic to the noise model used and can therefore
-be used for all these methods.  For our use cases, we focus on stochastic
-arithmetic since it does not make any assumption about the noise model, in
-contrast to sensitivity analysis.
+Three  main  approaches  exist  to  detect  numerical  instabilities: stochastic
+arithmetic,  uncertainty  or  sensitivity analysis~\cite{helton2006survey}, and
+random seed analysis~\cite{hellekalek1998good}. PyTracer is agnostic to the
+noise model used and can therefore be used for all these methods.  For our use
+cases, we focus on stochastic arithmetic since it does not make any assumption
+about the noise model, in contrast to sensitivity analysis.
 
@@
 where $\beta$ is the number base, $e_x$ is the magnitude of $x$, $t$ the virtual
-precision and $\xi\! \in\! (-\frac{1}{2},\frac{1}{2})$ is a random uniform variable.
-Virtual precision allows for the simulation of reduced working precision.
-In our experiments, we used MCA in Random Rounding (RR) mode, which
-simulates roundoff errors by applying function $inexact$ only to the
-output returned by a function. The Precision Bounding (PB) mode 
-\add{that applies the $inexact$ function on inputs}
+precision and $\xi\! \in\! (-\frac{1}{2},\frac{1}{2})$ is a random uniform
+variable. Virtual precision allows for the simulation of reduced working
+precision. In our experiments, we used MCA in Random Rounding (RR) mode, which
+simulates roundoff errors by applying function $inexact$ only to the output
+returned by a function. The Precision Bounding (PB) mode
+that applies the $inexact$ function on inputs
 can identify other types of instabilities, in particular catastrophic
-cancellations, however, it is more difficult to apply to large code bases
-as it often leads to execution errors that require human intervention.
+cancellations, however, it is more difficult to apply to large code bases as it
+often leads to execution errors that require human intervention.
 
@@
 variable sampled with MCA. This can be seen as the ratio of signal over noise.
-\remove{Sohier et al.~\cite{sohier2021confidence} recently provided a generalization of
-    this formula to include confidence intervals.}
 
@@
 program, and hence the more MCA repetitions we have, the more accurate the
-distribution will be. In theory, an infinite number of MCA repetitions
-should give the exact distribution. While in practice low sample sizes (3 to 30)
-can give good estimates, the issue is to capture ``rare events" 
-making the computation to strongly diverge from the mean. 
-Determining the number of MCA samples to use is still an open research question. 
-Recent theoretical works~\cite{sohier2021confidence} on the estimation of 
-significant digits allow computing an associated confidence
-interval depending on the sample size and the underlying
-distribution.
+distribution will be. In theory, an infinite number of MCA repetitions should
+give the exact distribution. While in practice low sample sizes (3 to 30) can
+give good estimates, the issue is to capture ``rare events" making the
+computation to strongly diverge from the mean. Determining the number of MCA
+samples to use is still an open research question. Recent theoretical
+works~\cite{sohier2021confidence} on the estimation of significant digits allow
+computing an associated confidence interval depending on the sample size and the
+underlying distribution.
 
@@
 
-\pytracer stores trace in the pickle format, a binary format to serialize
-Python objects. The main advantages of the pickle format compared to other
+\pytracer stores trace in the pickle format, a binary format to serialize Python
+objects. The main advantages of the pickle format compared to other
 serialization approaches such as marshal or JSON are its ability to serialize
@@
 This operation critically relies on the ordering of call input and output
-objects in the traces. It assumes that the application is
-single-threaded and that the control flow does not depend on a random state.
-Therefore, \mbox{\pytracer} cannot merge traces resulting from different
-control flow paths and will stop the parsing when encountering such a situation.
+objects in the traces. It assumes that the application is single-threaded and
+that the control flow does not depend on a random state. Therefore,
+\mbox{\pytracer} cannot merge traces resulting from different control flow paths
+and will stop the parsing when encountering such a situation.
 
@@
 \begin{enumerate}
-    \item Timeline view: displays the values of each input and output
-          for a given function at a given invocation. By default, \pytracer
-          shows the number of significant digits computed across the traces. The
-          mean and standard deviation across perturbed samples are also
-          available. The visualizer uses an upper triangle for inputs and a
-          lower triangle for outputs. \pytracer internally represents all values
-          as NumPy arrays. In the case of non-scalar values or types that cannot
-          be trivially cast into NumPy arrays, \pytracer splits the value into
-          several variables. Hence, \pytracer will transform a class containing
-          $n$ floating-point parameters into $n$ variables. Each variable is
+    \item Timeline view: displays the values of each input and output for a
+          given function at a given invocation. By default, \pytracer shows the
+          number of significant digits computed across the traces. The mean and
+          standard deviation across perturbed samples are also available. The
+          visualizer uses an upper triangle for inputs and a lower triangle for
+          outputs. \pytracer internally represents all values as NumPy arrays.
+          In the case of non-scalar values or types that cannot be trivially
+          cast into NumPy arrays, \pytracer splits the value into several
+          variables. Hence, \pytracer will transform a class containing $n$
+          floating-point parameters into $n$ variables. Each variable is
           prefixed with the original value and postfixed with the name of the
@@
           \texttt{function2} which itself calls \texttt{function4} and
-          \texttt{function5}. This view provides insights into the calling context
-          for each function that may influence numerical stability.
-    \item  Source code view: displays a local snapshot of the source
-          code file of the variable hovered in the timeline view.
-    \item Zoom view: provides details about non-scalar values. For
-          example, a matrix may have instabilities around its diagonal but not
-          in other regions. The visualizer also provides additional metrics such
-          as array shape, infinite norm, or condition number.
-    \item  Functions list view: allows the user to select the
-          functions plotted in the timeline view.
+          \texttt{function5}. This view provides insights into the calling
+          context for each function that may influence numerical stability.
+    \item  Source code view: displays a local snapshot of the source code file
+          of the variable hovered in the timeline view.
+    \item Zoom view: provides details about non-scalar values. For example, a
+          matrix may have instabilities around its diagonal but not in other
+          regions. The visualizer also provides additional metrics such as array
+          shape, infinite norm, or condition number.
+    \item  Functions list view: allows the user to select the functions plotted
+          in the timeline view.
 \end{enumerate}
@@
 their respective GitHub repositories. We traced each example five times, having
-activated MCA through Fuzzy in the Python interpreter as well as BLAS, LAPACK, NumPy,
-SciPy, and scikit-learn. These libraries are written in large parts in a
-compiled language other than Python (such as C or Cython) and their execution is not 
-perturbed by the sole use of Fuzzy Python. We chose to activate MCA in these libraries 
-to provide an overall picture of numerical uncertainty in the tested examples. 
-Depending on the use case of interest, one might choose to use MCA only in 
-a subset of these libraries or even just in the Python interpreter. We
-used MCA in Random Rounding (RR) mode, with the default virtual
-precision in Verificarlo, namely 24 bits for single-precision floating-point
-values and 53 bits for double-precision values, which simulates machine error.
-We used Python-3.8.5, NumPy-1.19.1, SciPy-1.5.4, and scikit-learn-0.23.2.
+activated MCA through Fuzzy in the Python interpreter as well as BLAS, LAPACK,
+NumPy, SciPy, and scikit-learn. These libraries are written in large parts in a
+compiled language other than Python (such as C or Cython) and their execution is
+not perturbed by the sole use of Fuzzy Python. We chose to activate MCA in these
+libraries to provide an overall picture of numerical uncertainty in the tested
+examples. Depending on the use case of interest, one might choose to use MCA
+only in a subset of these libraries or even just in the Python interpreter. We
+used MCA in Random Rounding (RR) mode, with the default virtual precision in
+Verificarlo, namely 24 bits for single-precision floating-point values and 53
+bits for double-precision values, which simulates machine error. We used
+Python-3.8.5, NumPy-1.19.1, SciPy-1.5.4, and scikit-learn-0.23.2.
 
@@
             \hline
-            \multicolumn{3}{|c}{ \multirow{2}{*}{Application} }                 & \multicolumn{3}{|c|}{Random Rounding (RR)}                                                                                                                         \\
+            \multicolumn{3}{|c}{ \multirow{2}{*}{Application} }
+             & \multicolumn{3}{|c|}{Random Rounding (RR)}
+
+            \\
             \cline{4-6}
-                                                                                &                                                                           &                                                          & trace  & parse    & sigbits \\
+             & 
+             & 
+             & 
+            trace
+             & 
+            parse
+             & 
+            sigbits
+            \\
             \hline
-            \multicolumn{1}{|c|}{ \multirow{20}{2em}{ \rotatebox{90}{SciPy} } } & 
-            \multicolumn{1}{c|}{ \multirow{3}{2em}{ \rotatebox{90}{FFT} }}      & \discreteCosineRF                                                         & \valid                                                   & \valid & \s{52}             \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \fftOneDRf                                               & \valid & \valid   & 41      \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \fftTwoDRf                                               & \valid & \valid   & \s{52}  \\
+            \multicolumn{1}{|c|}{ \multirow{20}{2em}{ \rotatebox{90}{SciPy} } }
+             & \multicolumn{1}{c|}{ \multirow{3}{2em}{ \rotatebox{90}{FFT} }}
+
+             & \discreteCosineRF
+             & \valid                                                         & \valid
+             & \s{52}                                                                  \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{}
+
+             & \fftOneDRf                                                     & \valid
+             & \valid                                                         & 41     \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{}
+
+             & \fftTwoDRf                                                     & \valid
+             & \valid                                                         & \s{52} \\
             \cline{2-6}
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{  \multirow{5}{*}{ \rotatebox{90}{Interpolation} } }
-
-                                                                                & \interOneDRf                                                              & \valid                                                   & \valid & 51                 \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \multiRf                                                 & \valid & \valid   & \s{51}  \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \bsplineRf                                               & \valid & \valid   & 10      \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \splineOneDRf                                            & \valid & \cross   & \s{52}  \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \splineTwoDRf                                            & \valid & \valid   & 10      \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{  \multirow{5}{*}{
+
+                    \rotatebox{90}{Interpolation} } }
+
+             & 
+            \interOneDRf
+             & 
+            \valid
+             & 
+            \valid
+             & 
+            51
+            \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{}
+
+             & \multiRf                                                       & \valid
+             & \valid                                                         & \s{51} \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{}
+
+             & \bsplineRf                                                     & \valid
+             & \valid                                                         & 10     \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{}
+
+             & \splineOneDRf                                                  & \valid
+             & \cross                                                         & \s{52} \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{}
+
+             & \splineTwoDRf                                                  & \valid
+             & \valid                                                         & 10     \\
             \cline{2-6}
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{ \multirow{12}{2em}{ \rotatebox{90}{Optimization} } }
-
-                                                                                & \bfgsRf                                                                   & \valid                                                   & \valid & \s{48}             \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{ \multirow{12}{2em}{
+
+                    \rotatebox{90}{Optimization} } }
+
+             & 
+            \bfgsRf
+             & 
+            \valid
+             & 
+            \valid
+             & 
+            \s{48}
+            \\
             \cline{3-6}
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \globalRf                                                & \valid & \cross   & 17      \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & | SHGO\footnote{Simplicial Homology Global Optimization} & \na    & \na      & \s{25}  \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & | Dual Annealing                                         & \na    & \na      & 4       \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & | Differential Evolution                                 & \na    & \na      & \s{0}   \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & | Basin Hopping                                          & \na    & \na      & 40      \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & | SHGO Sobol                                             & \na    & \na      & \s{45}  \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{}
+
+             & \globalRf                                                      & \valid
+             & \cross                                                         & 17     \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{}
+
+             & | SHGO\footnote{Simplicial Homology Global Optimization}       & \na
+             & \na                                                            & \s{25} \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{}
+
+             & | Dual Annealing                                               & \na
+             & \na                                                            & 4      \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{}
+
+             & | Differential Evolution                                       & \na
+             & \na                                                            & \s{0}  \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{}
+
+             & | Basin Hopping                                                & \na
+             & \na                                                            & 40     \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{}
+
+             & | SHGO Sobol                                                   & \na
+             & \na                                                            & \s{45} \\
             \cline{3-6}
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \slsqpRf                                                 & \valid & \valid   & 45      \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \lsmRf                                                   & \valid & \valid   & \s{48}  \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \nelderRf                                                & \valid & \valid   & 44      \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \ncgRf                                                   & \valid & \valid   & \s{48}  \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \rootRf                                                  & \valid & \cross   & 52      \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \rootLargRf                                              & \valid & \cross   & \s{29}  \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \rootLargePredRf                                         & \valid & \cross   & 42      \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \trustExactRf                                            & \valid & \valid   & \s{48}  \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \trustTruncRf                                            & \valid & \valid   & 48      \\
-            \multicolumn{1}{|c|}{}                                              & \multicolumn{1}{c|}{}                                                     & \trustNCGRf                                              & \valid & \valid   & \s{52}  \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{}
+
+             & \slsqpRf                                                       & \valid
+             & \valid                                                         & 45     \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{}
+
+             & \lsmRf                                                         & \valid
+             & \valid                                                         & \s{48} \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{}
+
+             & \nelderRf                                                      & \valid
+             & \valid                                                         & 44     \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{}
+
+             & \ncgRf                                                         & \valid
+             & \valid                                                         & \s{48} \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{}
+
+             & \rootRf                                                        & \valid
+             & \cross                                                         & 52     \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{}
+
+             & \rootLargRf                                                    & \valid
+             & \cross                                                         & \s{29} \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{}
+
+             & \rootLargePredRf                                               & \valid
+             & \cross                                                         & 42     \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{}
+
+             & \trustExactRf                                                  & \valid
+             & \valid                                                         & \s{48} \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{}
+
+             & \trustTruncRf                                                  & \valid
+             & \valid                                                         & 48     \\
+            \multicolumn{1}{|c|}{}
+             & \multicolumn{1}{c|}{}
+
+             & \trustNCGRf                                                    & \valid
+             & \valid                                                         & \s{52} \\
             \hline
-            \multicolumn{2}{|c|}{ \multirow{20}{2em}{ \rotatebox{90}{Scikit-learn} } }
-                                                                                & \AdaboostRf                                                               & \valid                                                   & \valid & 48                 \\
+            \multicolumn{2}{|c|}{ \multirow{20}{2em}{
+                    \rotatebox{90}{Scikit-learn}
+                }
+            }
+             & 
+            \AdaboostRf
+             & 
+            \valid
+             & 
+            \valid
+             & 
+            48
+            \\
             \cline{3-6}
-            \multicolumn{2}{|c|}{}                                              & \brrRf                                                                    & \valid                                                   & \valid & \s{25}             \\
-            \multicolumn{2}{|c|}{}                                              & | $1^{st}$ dataset                                                        & \na                                                      & \na    & 25                 \\
-            \multicolumn{2}{|c|}{}                                              & | $2^{nd}$ dataset                                                        & \na                                                      & \na    & \s{nan}            \\
+            \multicolumn{2}{|c|}{}
+             & \brrRf
+             & \valid                                                         & \valid
+             & \s{25}                                                                  \\
+            \multicolumn{2}{|c|}{}
+             & | $1^{st}$ dataset
+             & \na                                                            & \na
+             & 25                                                                      \\
+            \multicolumn{2}{|c|}{}
+             & | $2^{nd}$ dataset
+             & \na                                                            & \na
+             & \s{nan}                                                                 \\
             \cline{3-6}
-            \multicolumn{2}{|c|}{}                                              & \onlineClassifierComparisonRf                                             & \valid                                                   & \valid & 20                 \\
-            \multicolumn{2}{|c|}{}                                              & \kmeansRf                                                                 & \valid                                                   & \valid & \s{52}             \\
-            \multicolumn{2}{|c|}{}                                              & \covarianceRf                                                             & \valid                                                   & \cross & 48                 \\
-            \multicolumn{2}{|c|}{}                                              & \decisionRf                                                               & \valid                                                   & \valid & \s{50}             \\
-            \multicolumn{2}{|c|}{}                                              & \digitsRf                                                                 & \valid                                                   & \valid & 52                 \\
-            \multicolumn{2}{|c|}{}                                              & \faceRf                                                                   & \cross                                                   & \valid & \s{-}              \\
-            \multicolumn{2}{|c|}{}                                              & \penaltyRf                                                                & \valid                                                   & \valid & 52                 \\
-            \multicolumn{2}{|c|}{}                                              & \lassoRf                                                                  & \valid                                                   & \valid & \s{48}             \\
-            \multicolumn{2}{|c|}{}                                              & \hyperplaneRf                                                             & \valid                                                   & \valid & 3                  \\
-            \multicolumn{2}{|c|}{}                                              & \mnistRf                                                                  & \valid                                                   & \valid & \s{43}             \\
-            \multicolumn{2}{|c|}{}                                              & \multitaskRf                                                              & \valid                                                   & \valid & 50                 \\
-            \multicolumn{2}{|c|}{}                                              & \ompRf                                                                    & \valid                                                   & \valid & \s{52}             \\
-            \multicolumn{2}{|c|}{}                                              & \pcaRf                                                                    & \valid                                                   & \valid & 48                 \\
+            \multicolumn{2}{|c|}{}
+             & \onlineClassifierComparisonRf
+             & \valid                                                         & \valid
+             & 20                                                                      \\
+            \multicolumn{2}{|c|}{}
+             & \kmeansRf
+             & \valid                                                         & \valid
+             & \s{52}                                                                  \\
+            \multicolumn{2}{|c|}{}
+             & \covarianceRf
+             & \valid                                                         & \cross
+             & 48                                                                      \\
+            \multicolumn{2}{|c|}{}
+             & \decisionRf
+             & \valid                                                         & \valid
+             & \s{50}                                                                  \\
+            \multicolumn{2}{|c|}{}
+             & \digitsRf
+             & \valid                                                         & \valid
+             & 52                                                                      \\
+            \multicolumn{2}{|c|}{}
+             & \faceRf
+             & \cross                                                         & \valid
+             & \s{-}                                                                   \\
+            \multicolumn{2}{|c|}{}
+             & \penaltyRf
+             & \valid                                                         & \valid
+             & 52                                                                      \\
+            \multicolumn{2}{|c|}{}
+             & \lassoRf
+             & \valid                                                         & \valid
+             & \s{48}                                                                  \\
+            \multicolumn{2}{|c|}{}
+             & \hyperplaneRf
+             & \valid                                                         & \valid
+             & 3                                                                       \\
+            \multicolumn{2}{|c|}{}
+             & \mnistRf
+             & \valid                                                         & \valid
+             & \s{43}                                                                  \\
+            \multicolumn{2}{|c|}{}
+             & \multitaskRf
+             & \valid                                                         & \valid
+             & 50                                                                      \\
+            \multicolumn{2}{|c|}{}
+             & \ompRf
+             & \valid                                                         & \valid
+             & \s{52}                                                                  \\
+            \multicolumn{2}{|c|}{}
+             & \pcaRf
+             & \valid                                                         & \valid
+             & 48                                                                      \\
             \cline{3-6}
-            \multicolumn{2}{|c|}{}                                              & \robustRf                                                                 & \valid                                                   & \valid & \s{50}             \\
-            \multicolumn{2}{|c|}{}                                              & | Linear                                                                  & \na                                                      & \na    & 48                 \\
-            \multicolumn{2}{|c|}{}                                              & | RANSAC                                                                  & \na                                                      & \na    & \s{50}             \\
+            \multicolumn{2}{|c|}{}
+             & \robustRf
+             & \valid                                                         & \valid
+             & \s{50}                                                                  \\
+            \multicolumn{2}{|c|}{}
+             & | Linear
+             & \na                                                            & \na
+             & 48                                                                      \\
+            \multicolumn{2}{|c|}{}
+             & | RANSAC
+             & \na                                                            & \na
+             & \s{50}                                                                  \\
             \cline{3-6}
-            \multicolumn{2}{|c|}{}                                              & \toyRf                                                                    & \valid                                                   & \valid & 35                 \\
+            \multicolumn{2}{|c|}{}
+             & \toyRf
+             & \valid                                                         & \valid
+             & 35                                                                      \\
             \cline{3-6}
-            \multicolumn{2}{|c|}{}                                              & \svmRf                                                                    & \valid                                                   & \valid & \s{43.5}           \\
-            \multicolumn{2}{|c|}{}                                              & | Non-weighted                                                            & \na                                                      & \na    & 43                 \\
-            \multicolumn{2}{|c|}{}                                              & | Weighted                                                                & \na                                                      & \na    & \s{44}             \\
+            \multicolumn{2}{|c|}{}
+             & \svmRf
+             & \valid                                                         & \valid
+             & \s{43.5}                                                                \\
+            \multicolumn{2}{|c|}{}
+             & | Non-weighted
+             & \na                                                            & \na
+             & 43                                                                      \\
+            \multicolumn{2}{|c|}{}
+             & | Weighted
+             & \na                                                            & \na
+             & \s{44}                                                                  \\
             \cline{3-6}
-            \multicolumn{2}{|c|}{}                                              & \tomographyRf                                                             & \valid                                                   & \cross & -                  \\
-            \multicolumn{2}{|c|}{}                                              & \weightedRf                                                               & \valid                                                   & \valid & \s{44}             \\
+            \multicolumn{2}{|c|}{}
+             & \tomographyRf
+             & \valid                                                         & \cross
+             & -                                                                       \\
+            \multicolumn{2}{|c|}{}
+             & \weightedRf
+             & \valid                                                         & \valid
+             & \s{44}                                                                  \\
             \hline
@@
         \pytracer trace parsing and aggregation, \emph{result}: result precision
-        in number of significant bits. \valid: successful run, \cross: numerical error (tracing) or 
-        different control flow paths (parsing). \textit{nan} stands for (\texttt{Not-A-Number})
-        \add{meaning that the output result comes from an invalid arithmetic operation}. 
-        Example names are linked to their source code.}
+        in number of significant bits. \valid: successful run, \cross: numerical
+        error (tracing) or different control flow paths (parsing). \textit{nan}
+        stands for (\texttt{Not-A-Number}) meaning that the output result
+        comes from an invalid arithmetic operation. Example names are linked to
+        their source code.}
     \label{tab:pytracer_results_summary}
@@
 errors occur when traces result from different control flow paths (CFP).
-\add{Therefore, an application that consistently fails at the same function call will
-  produce traces with equivalent Control Flow Paths which can be parsed by \pytracer.
-  In our experiments, this was the case for the Face Recognition shows.}
-
-Overall, the
-tracing and parsing of SciPy and scikit-learn examples in Random Rounding mode
-was entirely successful for 32/40 examples.
+Therefore, an application that consistently fails at the same function call
+will produce traces with equivalent Control Flow Paths which can be parsed by
+\pytracer. In our experiments, this was the case for the Face Recognition
+shows.
+
+Overall, the tracing and parsing of SciPy and scikit-learn examples in Random
+Rounding mode was entirely successful for 32/40 examples.
 
 Column \textit{sigbits} in Table~\ref{tab:pytracer_results_summary} summarizes
-the result precision for the main outputs of SciPy and scikit-learn examples. 
-We use the term ``result precision"
-to denote the statistical variability measured in the number of significant bits, in 
-contrast with the other meanings of the word precision used in the expressions
-``virtual precision" or ``single/double precision'' in this paper. 
-We measured the result precision in significant bits on the final primary example output
-by taking the element-wise mean for non-scalar values and, if the example
-produced multiple outputs, the average value among them. Significant bits were computed on the final program output
-and could therefore be computed even when parsing failed. 
-The numerical
-quality across all examples varied from 0 to 52, with an average of 44
-significant bits. We note that only one example failed due to a
-numerical error (\texttt{face\_recognition}
-for RR and \texttt{Bayesian Ridge Regression} for full MCA).
+the result precision for the main outputs of SciPy and scikit-learn examples. We
+use the term ``result precision" to denote the statistical variability measured
+in the number of significant bits, in contrast with the other meanings of the
+word precision used in the expressions ``virtual precision" or ``single/double
+precision'' in this paper. We measured the result precision in significant bits
+on the final primary example output by taking the element-wise mean for
+non-scalar values and, if the example produced multiple outputs, the average
+value among them. Significant bits were computed on the final program output and
+could therefore be computed even when parsing failed. The numerical quality
+across all examples varied from 0 to 52, with an average of 44 significant bits.
+We note that only one example failed due to a numerical error
+(\texttt{face\_recognition} for RR and \texttt{Bayesian Ridge Regression} for
+full MCA).
 
@@
 
-PyTracer supports native floating-point formats as well as compound
-data types, such as complex floating-point values, N-dimensional arrays,
-and arbitrary Python classes. Figures~\ref{fig:fft1D_inputs}
-and~\ref{fig:fft1D_outputs} show the visualization of the
-\texttt{fft\_1D} input and output values \add{that} are complex values
-encoded in double precision. PyTracer allows visualizing the
-result precision of real (blue points) and imaginary (orange
-points) parts. The top row in Figures~\ref{fig:fft1D_inputs}
-and~\ref{fig:fft1D_outputs} show the input \add{and output} mean value while the bottom
-row shows the standard deviation. Even though Random Rounding
-(RR) was used, function inputs were perturbed since they result from
-multiple intermediate computations perturbed with RR. The points with
-low magnitude in Figure~\ref{fig:fft1D_inputs} correspond to inputs
-near 0 when the input of $\sin$ or $\exp$ is close to $k\pi$, $k \in
-    \mathbb{Z}$. Indeed, since MCA introduces noise, the result is not
-exactly 0. We can see in Figure~\ref{fig:fft1D_inputs} that the maximal
-noise introduced by MCA on the inputs is in the order of $10^{-14}$,
-two orders of magnitude higher than the $ulp \simeq 10^-16$ for double precision. This slight
-noise introduced can be interpreted as white noise on the input signal. We can
-see on the bottom row of Figure~\ref{fig:fft1D_outputs} that the frequency noise
-is of the same order of magnitude as the input noise, which is expected. The
-two peaks at x=38 and x=562 correspond to the actual frequencies of the input
-signal.
+PyTracer supports native floating-point formats as well as compound data types,
+such as complex floating-point values, N-dimensional arrays, and arbitrary
+Python classes. Figures~\ref{fig:fft1D_inputs} and~\ref{fig:fft1D_outputs} show
+the visualization of the \texttt{fft\_1D} input and output values that are
+complex values encoded in double precision. PyTracer allows visualizing the
+result precision of real (blue points) and imaginary (orange points) parts. The
+top row in Figures~\ref{fig:fft1D_inputs} and~\ref{fig:fft1D_outputs} show the
+input and output mean value while the bottom row shows the standard
+deviation. Even though Random Rounding (RR) was used, function inputs were
+perturbed since they result from multiple intermediate computations perturbed
+with RR. The points with low magnitude in Figure~\ref{fig:fft1D_inputs}
+correspond to inputs near 0 when the input of $\sin$ or $\exp$ is close to
+$k\pi$, $k \in \mathbb{Z}$. Indeed, since MCA introduces noise, the result is
+not exactly 0. We can see in Figure~\ref{fig:fft1D_inputs} that the maximal
+noise introduced by MCA on the inputs is in the order of $10^{-14}$, two orders
+of magnitude higher than the $ulp \simeq 10^-16$ for double precision. This
+slight noise introduced can be interpreted as white noise on the input signal.
+We can see on the bottom row of Figure~\ref{fig:fft1D_outputs} that the
+frequency noise is of the same order of magnitude as the input noise, which is
+expected. The two peaks at x=38 and x=562 correspond to the actual frequencies
+of the input signal.
 
@@
     [-1,1]\times[-1,1]$. The result is a 2D array that is natively supported by
-PyTracer. We observe a significant loss of result precision in some regions, which follows
-an interesting pattern that could be further investigated.
-\add{This example shows that \pytracer works on 2D inputs and the importance of
-    visualizing complex data types in addition to summary statistics.}
+PyTracer. We observe a significant loss of result precision in some regions,
+which follows an interesting pattern that could be further investigated.
+This example shows that \pytracer works on 2D inputs and the importance of
+visualizing complex data types in addition to summary statistics.
 
@@
     \centering
-    \includegraphics[width=\linewidth]{figure/FFT/fft_x.png}
+    \includegraphics[width=\linewidth]{figure/FFT/fft_x.pdf}
     \caption{Absolute value of the mean and standard deviation values for fft 1D
@@
     \centering
-    \includegraphics[width=\linewidth]{figure/FFT/fft_y.png}
-    \caption{Absolute value of the mean and standard deviation values
-        for fft 1D outputs within RR mode (log scale).}
+    \includegraphics[width=\linewidth]{figure/FFT/fft_y.pdf}
+    \caption{Absolute value of the mean and standard deviation values for fft 1D
+        outputs within RR mode (log scale).}
     \label{fig:fft1D_outputs}
@@
         respectively in the logarithmic scale the absolute mean value and the
-        standard deviation of the 5 samples run within RR mode. 
-    }
+        standard deviation of the 5 samples run within RR mode. }
     \label{fig:spline2d_rr}
@@
 
-We illustrate on two examples how PyTracer is effective for analyzing
-numerical stability in complex codes at a fine-grained level: Face recognition and Bayesian Ridge Regression.
-The face recognition example uses eigenfaces (eigenvectors) and Support Vector
-Machines (SVMs) to classify faces from the Labeled Faces in the Wild dataset.
-This example uses a Principal Component Analysis (PCA) to extract the eigenfaces
-and then trains an SVM classifier to predict the label associated with a face.
-When executing in PyTracer, this example crashed because the Singular Value Decomposition (SVD) did not converge.
-This example is the only one to raise an error due to the
-non-convergence of the SVD performed in the PCA.
-The PCA uses the Randomized SVD~\cite{halko2011finding} method
-that first computes a low-rank approximation of the input matrix using a
-stochastic algorithm and then uses this approximation as input for the SVD. 
-When walking through the code with PyTracer, we observed that
-the \texttt{randomized\_svd} scikit-learn function uses the Divide \& Conquer SVD
-method \texttt{gesdd}. The LAPACK library has two main methods for computing the SVD:
-\texttt{gesdd} and \texttt{gesvd}. The former uses a Divide \& Conquer approach,
-while the latter uses a QR decomposition. While both methods are expected to
-have the same accuracy~\cite{nakatsukasa2013stable}, the Divide \& Conquer
-does not converge with MCA.
-
-Replacing \texttt{gesdd} \add{with} \texttt{gesvd} solved the SVD convergence issue.
-\pytracer allows \add{us} to quickly visualize the new result precision.
-Figure~\ref{fig:face_recognition_svd} shows the result precision of the eigenvalues
-computed with \texttt{gesvd} in single precision. The result precision
-varies between 15 and 20
-significant bits out of the 24 available in single precision. The classifier
-metrics (precision, recall, F1-score, and support) are identical to the IEEE
-execution for all MCA samples. We can note that even with the \texttt{gesvd} method,
-the result precision of the singular values and eigenvectors is not uniform. 
-Indeed, we can see that the result precision of the lowest singular values and eigenvectors decreases 
-until reaching 0 significant bits.
+We illustrate on two examples how PyTracer is effective for analyzing numerical
+stability in complex codes at a fine-grained level: Face recognition and
+Bayesian Ridge Regression. The face recognition example uses eigenfaces
+(eigenvectors) and Support Vector Machines (SVMs) to classify faces from the
+Labeled Faces in the Wild dataset. This example uses a Principal Component
+Analysis (PCA) to extract the eigenfaces and then trains an SVM classifier to
+predict the label associated with a face. When executing in PyTracer, this
+example crashed because the Singular Value Decomposition (SVD) did not converge.
+This example is the only one to raise an error due to the non-convergence of the
+SVD performed in the PCA. The PCA uses the Randomized
+SVD~\cite{halko2011finding} method that first computes a low-rank approximation
+of the input matrix using a stochastic algorithm and then uses this
+approximation as input for the SVD. When walking through the code with PyTracer,
+we observed that the \texttt{randomized\_svd} scikit-learn function uses the
+Divide \& Conquer SVD method \texttt{gesdd}. The LAPACK library has two main
+methods for computing the SVD: \texttt{gesdd} and \texttt{gesvd}. The former
+uses a Divide \& Conquer approach, while the latter uses a QR decomposition.
+While both methods are expected to have the same
+accuracy~\cite{nakatsukasa2013stable}, the Divide \& Conquer does not converge
+with MCA.
+
+Replacing \texttt{gesdd} with \texttt{gesvd} solved the SVD convergence
+issue. \pytracer allows us to quickly visualize the new result precision.
+Figure~\ref{fig:face_recognition_svd} shows the result precision of the
+eigenvalues computed with \texttt{gesvd} in single precision. The result
+precision varies between 15 and 20 significant bits out of the 24 available in
+single precision. The classifier metrics (precision, recall, F1-score, and
+support) are identical to the IEEE execution for all MCA samples. We can note
+that even with the \texttt{gesvd} method, the result precision of the singular
+values and eigenvectors is not uniform. Indeed, we can see that the result
+precision of the lowest singular values and eigenvectors decreases until
+reaching 0 significant bits.
 
@@
 raise a runtime error, the regression coefficients computed from the fitting are
-not significant. \pytracer traces reveal that the SVD solver used is once again the root
-cause for this error. Indeed, the BayesianRidge model first computes an SVD
-before iteratively updating the coefficients until reaching the convergence
-criterion. However, PyTracer shows an issue in the singular values computed.
-We can see in Figure~\ref{fig:BRR_svd} that the last singular value is
-\texttt{NaN} due to numerical errors in the SVD, although the remaining
-singular values exhibit high result precision (between 44 and 50 bits).
-Surprisingly, this \texttt{NaN} value does not raise an exception and is silently
-propagated. Indeed, the stopping criterion is never verified and the 
-optimization stops after reaching the maximal number of iterations.
-Figure~\ref{fig:BRR_svd_fixed} shows that using
-the \texttt{gesvd} instead of the \texttt{gesdd} method removes the \texttt{NaN} value
-although the last singular values stills have a low result precision (below 0).
-According to Equation~\ref{eq:sig-digits}, a number of significant bits less than 0 means that the
-variability ($\sigma$) is higher than the average value ($\mu$).
-
-Similarly, for OLS, PyTracer traces show that the
-regression coefficients fitted are \texttt{NaN} values. By looking at the callgraph, we can
-see that the scipy calls the \texttt{lstsq} method from the
-\texttt{scipy.linalg} package which uses the \texttt{gesdd} LAPACK function.
-Figure~\ref{fig:OLS_svd} shows that one singular value is a \texttt{NaN} value,
-which corrupted the calculation of the coefficients. When using the \texttt{gesvd} method, 
-the \texttt{NaN} value disappears 
-(Fig.~\ref{fig:OLS_svd_fixed}), resulting in a result precision of
-42 bits on average in the coefficients. We can see that having
-access to all the values computed by the application with PyTracer allows
-the user to efficiently identify numerical issues.
+not significant. \pytracer traces reveal that the SVD solver used is once again
+the root cause for this error. Indeed, the BayesianRidge model first computes an
+SVD before iteratively updating the coefficients until reaching the convergence
+criterion. However, PyTracer shows an issue in the singular values computed. We
+can see in Figure~\ref{fig:BRR_svd} that the last singular value is \texttt{NaN}
+due to numerical errors in the SVD, although the remaining singular values
+exhibit high result precision (between 44 and 50 bits). Surprisingly, this
+\texttt{NaN} value does not raise an exception and is silently propagated.
+Indeed, the stopping criterion is never verified and the optimization stops
+after reaching the maximal number of iterations. Figure~\ref{fig:BRR_svd_fixed}
+shows that using the \texttt{gesvd} instead of the \texttt{gesdd} method removes
+the \texttt{NaN} value although the last singular values still have a low result
+precision (below 0). According to Equation~\ref{eq:sig-digits}, a number of
+significant bits less than 0 means that the variability ($\sigma$) is higher
+than the average value ($\mu$).
+
+Similarly, for OLS, PyTracer traces show that the regression coefficients fitted
+are \texttt{NaN} values. By looking at the callgraph, we can see that the scipy
+calls the \texttt{lstsq} method from the \texttt{scipy.linalg} package which
+uses the \texttt{gesdd} LAPACK function. Figure~\ref{fig:OLS_svd} shows that one
+singular value is a \texttt{NaN} value, which corrupted the calculation of the
+coefficients. When using the \texttt{gesvd} method, the \texttt{NaN} value
+disappears (Fig.~\ref{fig:OLS_svd_fixed}), resulting in a result precision of 42
+bits on average in the coefficients. We can see that having access to all the
+values computed by the application with PyTracer allows the user to efficiently
+identify numerical issues.
 
 In conclusion, \pytracer and the MCA model were helpful to detect the
-instability of the \texttt{gesdd} method mentioned in several GitHub issues such as
-\href{https://github.com/google/TensorNetwork/pull/962}{github.com/google/TensorNetwork/pull/962} or
+instability of the \texttt{gesdd} method mentioned in several GitHub issues such
+as
+\href{https://github.com/google/TensorNetwork/pull/962}{github.com/google/TensorNetwork/pull/962}
+or
 \href{https://github.com/scipy/scipy/issues/15024}{github.com/scipy/scipy/issues/15024}
 including the LAPACK repository. Furthermore, it is worth mentioning that a Pull
-Request \add{at} \href{https://github.com/scikit-learn/scikit-learn/pull/20617}{github.com/scikit-learn/scikit-learn/pull/20617}
-has recently been submitted in the scikit-learn repository to let the user select the SVD method and
-avoid this kind of issue. Thus, \pytracer can detect instabilities that affect
-fundamental scientific computing components such as the LAPACK library. The
-unified view of all traces allows the user to quickly navigate through the
-result precision of different variables.
+Request at
+\href{https://github.com/scikit-learn/scikit-learn/pull/20617}{github.com/scikit-learn/scikit-learn/pull/20617}
+has recently been submitted in the scikit-learn repository to let the user
+select the SVD method and avoid this kind of issue. Thus, \pytracer can detect
+instabilities that affect fundamental scientific computing components such as
+the LAPACK library. The unified view of all traces allows the user to quickly
+navigate through the result precision of different variables.
 
@@
         and~\ref{fig:randomized_svd_V} show respectively the values $U$,
-        $\Sigma$ and $V$. Result precision is lower for smaller singular
-        values and this loss of precision translates to singular vectors. It
-        would be interesting to investigate the use of numerical precision for
+        $\Sigma$ and $V$. Result precision is lower for smaller singular values
+        and this loss of precision translates to singular vectors. It would be
+        interesting to investigate the use of numerical precision for
         dimensionality reduction. }
@@
     \begin{subfigure}{0.49\linewidth}
-        \includegraphics[width=\linewidth]{figure/BRR_singular_values.png}
+        \includegraphics[width=\linewidth]{figure/BRR_singular_values.pdf}
         \caption{BRR (\texttt{gesdd})}
@@
     \begin{subfigure}{0.49\linewidth}
-        \includegraphics[width=\linewidth]{figure/OLS_singular_values.png}
+        \includegraphics[width=\linewidth]{figure/OLS_singular_values.pdf}
         \caption{OLS (\texttt{gesdd})}
@@
     \begin{subfigure}{0.49\linewidth}
-        \includegraphics[width=\linewidth]{figure/BRR_singular_values_fixed.png}
+        \includegraphics[width=\linewidth]{figure/BRR_singular_values_fixed.pdf}
         \caption{BRR (\texttt{gesvd})}
@@
     \begin{subfigure}{0.49\linewidth}
-        \includegraphics[width=\linewidth]{figure/OLS_singular_values_fixed.png}
+        \includegraphics[width=\linewidth]{figure/OLS_singular_values_fixed.pdf}
         \caption{OLS (\texttt{gesvd})}
@@
     \caption{Result precision of the singular values of the SVD from the
-        Bayesian Ridge model fitting (left) and from the Ordinary Least Square model
-        fitting (right) in the Bayesian Ridge Regression example. Red stars
-        represent \texttt{NaN} values. 
-        Switching from Divide \& Conquer (\texttt{gesdd}) to QR (\texttt{gesvd}) factorization improves numerical precision.
-        PyTracer helps visualizing improvements.}
+        Bayesian Ridge model fitting (left) and from the Ordinary Least Square
+        model fitting (right) in the Bayesian Ridge Regression example. Red
+        stars represent \texttt{NaN} values. Switching from Divide \& Conquer
+        (\texttt{gesdd}) to QR (\texttt{gesvd}) factorization improves numerical
+        precision. PyTracer helps visualizing improvements.}
 \end{figure}
@@
 Figure~\ref{fig:performance_tracing} summarizes \pytracer's tracing overhead for
-SciPy and scikit-learn examples. \textit{Instrumentation and initialization} represents the slowdown of
-\pytracer without fuzzy, \add{measured by applying PyTracer to Python programs without Monte-Carlo Arithmetic.}
-The slowdown is measured as the ratio between the actual execution time
-(without \pytracer) and the execution time using \pytracer. 
-The \textit{Total with RR MCA} shows the slowdown within the Fuzzy environment.
-Without Fuzzy, \pytracer introduces an average slowdown of $17\times$ for
-the examples running less than 8 seconds because \pytracer spends most of its
-time in the initialization step. Since this step is a constant factor of the
-number of functions instrumented, we also measured the instrumentation cost
-itself (\textit{Instrumentation only}) calculated by subtracting the
-initialization time to \textit{Instrumentation}. We then obtain an average slowdown of
-$3.5\times$. Finally, using MCA
-operations (through Fuzzy) instead of the native ones increased the average
-slowdown to $37\times$.
-\add{As shown in Figure~\ref{fig:performance_parsing}, the log aggregation time is linearly correlated with the log trace size (F-score=68, p-value $\leq 10^{-8}$, F-test for linear regression).}
-
-% \pytracer's tracing overhead consists of (1) module instrumentation time
-% (initialization overhead), and (2) data write time during the execution
-% (runtime overhead). The initialization overhead is proportional to the number
-% of functions and classes traced. However, the initialization overhead is
-% amortized \tristan{what do you mean by amortized? I don't get this sentence}
-% when traced applications are above 8 seconds,  proportional to the number of
-% functions and classes traced. Figure~\ref{fig:performance_tracing} summaries
-% \pytracer's tracing overhead for SciPy and scikit-learn examples. We can see
-% that \pytracer introduces a slowdown of reduced toif we subtract the
-% initialization step \tristan{not sure where to get these numbers from the
-% table, to be clarified. Are these average values? Why are there two values?}.
-% Fuzzy instrumentation increases the slowdown to for RR and   for Full MCA.
-% \tristan{Figure 13 is not referred in the text. Choose between the figure and
-% the table, no need to put both.}
+SciPy and scikit-learn examples. \textit{Instrumentation and initialization}
+represents the slowdown of \pytracer without fuzzy, measured by applying
+PyTracer to Python programs without Monte-Carlo Arithmetic. The slowdown is
+measured as the ratio between the actual execution time (without \pytracer) and
+the execution time using \pytracer. The \textit{Total with RR MCA} shows the
+slowdown within the Fuzzy environment. Without Fuzzy, \pytracer introduces an
+average slowdown of $17\times$ for the examples running less than 8 seconds
+because \pytracer spends most of its time in the initialization step. Since this
+step is a constant factor of the number of functions instrumented, we also
+measured the instrumentation cost itself (\textit{Instrumentation only})
+calculated by subtracting the initialization time to \textit{Instrumentation}.
+We then obtain an average slowdown of $3.5\times$. Finally, using MCA operations
+(through Fuzzy) instead of the native ones increased the average slowdown to
+$37\times$. As shown in Figure~\ref{fig:performance_parsing}, the log
+aggregation time is linearly correlated with the log trace size (F-score=68,
+p-value $\leq 10^{-8}$, F-test for linear regression).
 
@@
     \centering
-    \includegraphics[width=\linewidth]{figure/performance.png}
-    \caption{
-        \pytracer tracing overheads. \textit{Slowdown} represents the slowdown
-        of \pytracer without Fuzzy measured as the ratio between the actual
-        execution time (without \pytracer) and the execution time using
+    \includegraphics[width=\linewidth]{figure/performance.pdf}
+    \caption{ \pytracer tracing overheads. \textit{Slowdown} represents the
+        slowdown of \pytracer without Fuzzy measured as the ratio between the
+        actual execution time (without \pytracer) and the execution time using
         \pytracer. \textit{Slowdown (Instrumentation)} show the actual
         instrumentation cost computed by subtracting the initialization step.
-        The \textit{Slowdown (RR)} is the slowdown
-        of \pytracer using the Fuzzy environment with the RR mode. The
-        last four examples measure the initialization
-        steps depending on the modules instrumented. 
-        % \tristan{there's too much text in this caption, move some of it to the text, the caption should just explain the difference between the 4 slowdowns.
-From the text I'm not sure what is the difference between slowdown and slowdown(RR)/slowdown(MCA).}
+        The \textit{Slowdown (RR)} is the slowdown of \pytracer using the Fuzzy
+        environment with the RR mode. The last four examples measure the
+        initialization steps depending on the modules instrumented.
     }
@@
     \includegraphics[width=\linewidth]{figure/performance_parsing.pdf}
+
     \caption{\pytracer aggregation performance.
-        % \tristan{change xlabel to "Trace size (bytes) and ylabel to "Aggregation time (seconds)}
     }
@@
 \end{figure}
-
-% \tristan{Mention linear correlation with p-value here.}
 
@@
 \pytracer allows users to pinpoint the root causes of numerical instabilities by
-working at the level of Python functions. Numerical stability evaluations are complex since
-calculations are strongly interdependent. Function-level instrumentation limits
-the size of the traces since only inputs and outputs of a function are dumped.
-Moreover, it decreases instrumentation overhead and helps the user identify
-instabilities quickly. Working at the function level is thus a suitable
-compromise between analyses conducted at the floating-point operation level and
-user debug prints. Indeed, operation-level analyses are costly and hard to
-interpret as they overwhelm users with information. In contrast, looking at
-intermediate results through print statements is lightweight but not reliable
+working at the level of Python functions. Numerical stability evaluations are
+complex since calculations are strongly interdependent. Function-level
+instrumentation limits the size of the traces since only inputs and outputs of a
+function are dumped. Moreover, it decreases instrumentation overhead and helps
+the user identify instabilities quickly. Working at the function level is thus a
+suitable compromise between analyses conducted at the floating-point operation
+level and user debug prints. Indeed, operation-level analyses are costly and
+hard to interpret as they overwhelm users with information. In contrast, looking
+at intermediate results through print statements is lightweight but not reliable
 since developers may not systematically instrument unstable functions.
 
-\pytracer can be used with different types of numerical perturbations,
-including random seeds, data noise, or stochastic arithmetic. Using 
-Verificarlo to implement stochastic arithmetic through Fuzzy
-enables \add{us} to study the impact \remove{of} numerical perturbations
-introduced in non-Python dependencies while preserving the high-level view
-of Python variables and functions. For instance, the SciPy environment
-wraps many computation kernels written in C, such as BLAS or LAPACK, which
-have a considerable impact on the stability of applications using them.
-
-Enabling Monte-Carlo arithmetic in such non-Python dependencies requires
-their recompilation with Verificarlo, which usually requires human
-intervention. The Fuzzy environment provides a pre-instrumented version of
-NumPy, BLAS, LAPACK, GNU libmath, SciPy, and Scikit-learn, which, given the
-prevalence of these libraries in scientific Python codes, should cover a
-large ground of non-Python dependencies encountered in scientific Python programs.
+\pytracer can be used with different types of numerical perturbations, including
+random seeds, data noise, or stochastic arithmetic. Using Verificarlo to
+implement stochastic arithmetic through Fuzzy enables us to study the
+impact numerical perturbations introduced in non-Python dependencies
+while preserving the high-level view of Python variables and functions. For
+instance, the SciPy environment wraps many computation kernels written in C,
+such as BLAS or LAPACK, which have a considerable impact on the stability of
+applications using them.
+
+Enabling Monte-Carlo arithmetic in such non-Python dependencies requires their
+recompilation with Verificarlo, which usually requires human intervention. The
+Fuzzy environment provides a pre-instrumented version of NumPy, BLAS, LAPACK,
+GNU libmath, SciPy, and Scikit-learn, which, given the prevalence of these
+libraries in scientific Python codes, should cover a large ground of non-Python
+dependencies encountered in scientific Python programs.
 
@@
 
-\pytracer's visualization provides a global view of the code and interactions between
-computations. In addition, the Plotly dashboard helps navigate through the code
-easily, without the need for ad-hoc scripts to visualize data. The
+\pytracer's visualization provides a global view of the code and interactions
+between computations. In addition, the Plotly dashboard helps navigate through
+the code easily, without the need for ad-hoc scripts to visualize data. The
 dashboard can be extended to support other data formats to visualize. At this
@@
 
-Finally, the wide range of result precision observed in our experiments
-suggests that such
-analyses would benefit from being conducted systematically. We showed that
-well-known scientific libraries are prone to numerical errors even though they
-have been well tested for decades. The prevalence of these libraries in
+Finally, the wide range of result precision observed in our experiments suggests
+that such analyses would benefit from being conducted systematically. We showed
+that well-known scientific libraries are prone to numerical errors even though
+they have been well tested for decades. The prevalence of these libraries in
 scientific codes should thus impel users to integrate numerical analysis in
@@
 in~\cite{cherubin2020tools}.
-% \pytracer adopts the dynamic approach due to its scalability to large code
-% bases. Dynamic approaches typically trace floating-point computations, detect
-% instabilities in traces, and visualize summary statistics about instabilities.
-% This section reviews existing approaches for each of these steps.
-% \label{sec:soa} \paragraph{Numerical tracing techniques}
-Numerous tools exist to trace floating-point computations for C, C++, or
-FORTRAN programs due to the prevalence of these languages in High-Performance
-Computing (HPC). The main tracing techniques are \textit{source-to-source},
+Numerous tools exist to trace floating-point computations for C, C++, or FORTRAN
+programs due to the prevalence of these languages in High-Performance Computing
+(HPC). The main tracing techniques are \textit{source-to-source},
 \textit{compiler-based transformations}, and \textit{dynamic binary
@@
 the MPFR~\cite{fousse2007mpfr} library. ADAPT \mbox{~\cite{menon2018adapt}} uses
-Automatic Differentiation to compute a sensitivity profile for each variable in a
-program. Finally, the work in~\cite{tang2016software} propose\add{s} a
+Automatic Differentiation to compute a sensitivity profile for each variable in
+a program. Finally, the work in~\cite{tang2016software} proposes a
 source-to-source framework for executing targeted code in infinite and fixed
 precision with and without stochastic arithmetic. The main drawback of the
-source-to-source approach is its lack of scalability since rewriting large
-codes can be a tedious task.
-
-% \gkmod{}{Note: similar to the above, this is just a list rather than a
-% highlight of how the compiler-based approach can be more scalable than
-% source-to-source because it requires less manual intervention into a codebase
-% (e.g.), then have your list, and finally say why it is still limited/not a
-% global fix to this problem.}
+source-to-source approach is its lack of scalability since rewriting large codes
+can be a tedious task.
 
@@
 FPSanitizer~\cite{chowdhary2020debugging,chowdhary2021parallel} and
-NSan~\mbox{\cite{courbet2021nsan}} are compiler-based approaches
-that use shadow execution to detect numerical issues using higher
-precision.
-FLiT~\cite{sawaya2017flit} is a framework to detect variability
-induced by compilers and their optimizations. The work
-in~\cite{wang2012development} proposes a numerical debugger based on
-GDB~\cite{stallman1988debugging} for Discrete Stochastic Arithmetic (DSA) on
-FPGA as an Eclipse plugging. Similarly, Cadtrace~\cite{jezequel2008cadna} and
-Shaman propose a GDB-based tool to use the CADNA and Shaman libraries with GDB,
-respectively. The main limitation of the compiler-based approach is that one
-must have access to the source code.
+NSan~\mbox{\cite{courbet2021nsan}} are compiler-based approaches that use shadow
+execution to detect numerical issues using higher precision.
+FLiT~\cite{sawaya2017flit} is a framework to detect variability induced by
+compilers and their optimizations. The work in~\cite{wang2012development}
+proposes a numerical debugger based on GDB~\cite{stallman1988debugging} for
+Discrete Stochastic Arithmetic (DSA) on FPGA as an Eclipse plugging. Similarly,
+Cadtrace~\cite{jezequel2008cadna} and Shaman propose a GDB-based tool to use the
+CADNA and Shaman libraries with GDB, respectively. The main limitation of the
+compiler-based approach is that one must have access to the source code.
 
@@
 using shadow computations with higher precision.
-Herbgrind~\cite{sanchez2017finding} is a Valgrind-based tool to
-detect numerical instabilities. It uses a shadow memory to detect  precision
-losses by comparison with results obtained in higher
-precision. It is combined with symbolic computation to backtrack the root of the
-error. We can note that all methods based on a high-precision oracle suppose
-that computing with a large number of bits is sufficient to obtain an accurate
-result, which is not always true (see, for example, the famous Muller's
-sequence~\cite{bajard1996introduction}). Although versatile, the DBI loses
-high-level information useful to understand the source-code logic.
-
-% \gkmod{}{Note: I like this comparison here, but do think that the comments
-% above about providing some more info when each is mentioned would still help
-% this section.}
+Herbgrind~\cite{sanchez2017finding} is a Valgrind-based tool to detect numerical
+instabilities. It uses a shadow memory to detect  precision losses by comparison
+with results obtained in higher precision. It is combined with symbolic
+computation to backtrack the root of the error. We can note that all methods
+based on a high-precision oracle suppose that computing with a large number of
+bits is sufficient to obtain an accurate result, which is not always true (see,
+for example, the famous Muller's sequence~\cite{bajard1996introduction}).
+Although versatile, the DBI loses high-level information useful to understand
+the source-code logic.
+
 Being agnostic to the programming language is a serious advantage of the DBI
@@
 \section{Conclusion}
-
-% \tristan{I moved this from the opening of Section 4, as this reads more like a
-% summary of \pytracer's features than an experiment description. It should be
-% refactored in 1-2 paragraphs summarizing the main properties of \\pytracer.}
 
@@
 In the future, we plan to extend the post-processing analysis to aggregate
-traces obtained with different control flow paths, by leveraging
-techniques used in code coverage analysis. This would also enable larger
-support for multi-threaded applications. Moreover, we would like to extend
-\pytracer to instrument elementary arithmetic operations (+,-,*,/), to
-allow for more detailed analyses.
-
-% % use section* for acknowledgment
-% \ifCLASSOPTIONcompsoc
-%     % The Computer Society usually uses the plural form
-%     \section*{Acknowledgments}
-% \else
-%     % regular IEEE prefers the singular form
-%     \section*{Acknowledgment}
-% \fi
-
-% The authors would like to thank...
-
-% Can use something like this to put references on a page
-% by themselves when using endfloat and the captionsoff option.
+traces obtained with different control flow paths, by leveraging techniques used
+in code coverage analysis. This would also enable larger support for
+multi-threaded applications. Moreover, we would like to extend \pytracer to
+instrument elementary arithmetic operations (+,-,*,/), to allow for more
+detailed analyses.
+
 \ifCLASSOPTIONcaptionsoff
@@
 
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-%% \begin{thebibliography}{1}
-
-%% \bibitem{IEEEhowto:kopka}
-%% H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-%%   0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
-%% \end{thebibliography}
-
-% biography section
-% 
-% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-% needed around the contents of the optional argument to biography to prevent
-% the LaTeX parser from getting confused when it sees the complicated
-% \includegraphics command within an optional argument. (You could create
-% your own custom macro containing the \includegraphics command to make things
-% simpler here.)
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-% or if you just want to reserve a space for a photo:
-
 \vskip -2\baselineskip plus -1fil
@@
         Chatelain} received his Ph.D. degree from the University of Paris-Saclay
-    (UVSQ), Versailles, France in 2019. He is a postdoctoral researcher in the
-    Big Data Infrastructures for Neuroinformatics lab at the University of
-    Concordia, Montreal, Canada. His research topics include computer
-    arithmetic, high-performance computing, and reproducibility. Yohan aims at
-    democratizing the use of the analysis of stability for scientific computing
-    codes through automatic tools to improve numerical quality. 
+    (UVSQ), Versailles, France in 2019. He is a postdoctoral researcher in
+    the Big Data Infrastructures for Neuroinformatics lab at the University
+    of Concordia, Montreal, Canada. His research topics include computer
+    arithmetic, high-performance computing, and reproducibility. Yohan aims
+    at democratizing the use of the analysis of stability for scientific
+    computing codes through automatic tools to improve numerical quality.
 \end{IEEEbiography}
@@
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/greg_kiar.png}}]{Gregory
-        Kiar} is a research scientist at the Child Mind Institute. Throughout his
-    degrees in Biomedical Engineering, Greg has developed techniques to study
-    biosignal data, a turn-key tool that allows researchers to generate maps of
-    brain connectivity from diffusion MRI data, and techniques to assess and
-    improve the stability of research in neuroscience. Greg’s research bridges
-    the fields of numerical analysis and brain imaging to evaluate and improve
-    the trustworthiness of techniques used to study the brain. 
+        Kiar} is a research scientist at the Child Mind Institute. Throughout
+    his degrees in Biomedical Engineering, Greg has developed techniques to
+    study biosignal data, a turn-key tool that allows researchers to
+    generate maps of brain connectivity from diffusion MRI data, and
+    techniques to assess and improve the stability of research in
+    neuroscience. Greg’s research bridges the fields of numerical analysis
+    and brain imaging to evaluate and improve the trustworthiness of
+    techniques used to study the brain.
 \end{IEEEbiography}
@@
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/glatard_tristan.jpg}}]{Tristan
-        Glatard} is Associate Professor in the Department of Computer Science and
-    Software Engineering at Concordia University in Montreal, and Canada
-    Research Chair (Tier II) on Big Data Infrastructures for Neuroinformatics.
-    Before that, he was research scientist at the French National Centre for
-    Scientific Research and Visiting Scholar at McGill University. 
+        Glatard} is Associate Professor in the Department of Computer Science
+    and Software Engineering at Concordia University in Montreal, and Canada
+    Research Chair (Tier II) on Big Data Infrastructures for
+    Neuroinformatics. Before that, he was research scientist at the French
+    National Centre for Scientific Research and Visiting Scholar at McGill
+    University.
 \end{IEEEbiography}
 
-%% % insert where needed to balance the two columns on the last page with
-%% % biographies
-%% %\newpage
-
-%% \begin{IEEEbiographynophoto}{Jane Doe}
-%% Biography text here.
-%% \end{IEEEbiographynophoto}
-
-% You can push biographies down or up by placing
-% a \vfill before or after them. The appropriate
-% use of \vfill depends on what kind of text is
-% on the last page and whether or not the columns
-% are being equalized.
-
-%\vfill
-
-% Can be used to pull up biographies so that the bottom of the last one
-% is flush with the other column.
-%\enlargethispage{-5in}
-
-% \appendix
-% \include{annex}
-
-% that's all folks
 \end{document}
